### 2021-05-30 group-a/group-a-analysis.Rmd
add projects

---
title: "Group A"
output: html_notebook
---

# Setup

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
```

# Import Data

Read JSON files and bind together into a tibble.

```{r}
data.files <- list.files('data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

Get a list of subject IDs.

```{r}
subjects <- unique(all.data$subject_id)
```

# Extract Relevant Data

Get data from critical trials, select relevant columns, unnest/unpack webgazer data to get a tidy tibble,
and add gaze measurements as a percentage.

```{r}
task.data <- all.data %>%
  filter(verb_type %in% c("restricting", "non-restricting")) %>%
  select(subject_id, stimulus, response, verb_type, webgazer_data, webgazer_targets) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(`#scenes`) %>%
  select(-x,-y) %>%
  unnest(webgazer_data) %>%
  mutate(gaze.x.percent = (x - left) / width * 100) %>%
  mutate(gaze.y.percent = (y - top) / height * 100)
```

# Add Stimulus Info

Merge in info on visual ROIs and audio onsets.

```{r message=FALSE, warning=FALSE}
ref.image.height <- 1500 # height of images that were measured for ROIs
ref.image.width <- 1875 # width of images that were measured for ROIs
padding <- 20 # padding in pixels around the ROIs.

image.data <- read_csv('info/image_measurements.csv') %>%
  mutate(roi_top = (top_object_distance - padding) / ref.image.height * 100,
         roi_bottom = (bottom_object_distance + padding) / ref.image.height * 100,
         roi_left = (left_object_distance - padding) / ref.image.width * 100,
         roi_right = (right_object_distance + padding) / ref.image.width * 100) %>%
  mutate(object_class = if_else(object_type %in% c('subject', 'target.object'), object_type, 'distractor')) %>%
  select(image_name, object_type, object_class, roi_top, roi_bottom, roi_left, roi_right)

audio.data <- read_csv('info/audio_timestamps.csv') %>% filter(!is.na(stimulus))

critical.trials <- task.data %>%
  left_join(audio.data) %>%
  left_join(image.data) 
```

# Compute Gaze in ROI

Define a function for determining if `x,y` value falls in box.

```{r}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

Add a column with boolean value for whether gaze was in the ROI.

```{r}
critical.trials <- critical.trials %>%
  mutate(is.fixating = in.box(gaze.x.percent, gaze.y.percent, roi_left, roi_right, roi_top, roi_bottom, 0))
```

Check the proportion of samples that were in at least one ROI for subjects.

```{r}
prop.in.roi.by.subject <- critical.trials %>%
  group_by(subject_id, t, image_name) %>%
  summarize(fixation.in.roi = any(is.fixating)) %>%
  group_by(subject_id) %>%
  summarize(prop.of.samples.in.roi = mean(fixation.in.roi))
```
Visualize proportion of samples in ROI by subject.

```{r}
hist(prop.in.roi.by.subject$prop.of.samples.in.roi, breaks=20)
```
Exclude subjects below a threshold?

```{r}
bad.subjects <- prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi == 0) %>%
  pull(subject_id)

# to match laila's analysis
bad.subjects <- c("5f3a76043bb11c6786e731bf", "5f9c6b2def8bdf1102de5338", "607197e359bae0449ac9d4bc", "60142d5718e5943b09fd9298")

critical.trials.filtered <- critical.trials %>%
  filter(!subject_id %in% bad.subjects)
```

# Calculating cumulative fixation probability

We start by calculating cumulative fixation probability on the objects after the verb onset. (Any fixations prior to the verb onset are not relevant to the core research questions.)

First, add a column for time relative to verb onset, bin this to 50ms chunks, and filter the data to the 2,000 ms window after verb onset.

```{r}
cumulative.fixation.data <- critical.trials.filtered %>%
  mutate(t.relative.to.verb.onset = t - (verb_onset*1000)) %>%
  filter(t.relative.to.verb.onset >= 0 & t.relative.to.verb.onset <2000) %>%
  mutate(t.w = floor(t.relative.to.verb.onset/50)*50)
```

Now check every time window within a trial to account for sparse samples. This calculating is time consuming, so we cache the result in a CSV file, and load from the CSV if it already exists.

```{r}
cumulative.fixation.calculation <- function(df){
  time <- seq(0,1950,50)
  fixations <- logical(length(time))
  hit.flag <- FALSE
  for(i in 1:length(fixations)){
    if(hit.flag){
      fixations[i] <- TRUE
    } else {
      val <- df %>% filter(t.w <= time[i]) %>% pull(is.fixating) %>% any()
      if(val == TRUE) {
        hit.flag <- TRUE
      }
      fixations[i] <- val
    }
  }
  out <- tibble(t.window = time, has.fixated = fixations)
  return(out)
}

if(file.exists("data/generated/cumulative_fixation_data.csv")){
  cumulative.fixation.windows.data <- read_csv("data/generated/cumulative_fixation_data.csv")
} else {

  cumulative.fixation.windows.data <- cumulative.fixation.data %>%
    group_by(subject_id, verb_type, image_name, object_type, object_class) %>%
    summarize(cumulative.fixation.calculation(cur_data()))

  write_csv(cumulative.fixation.windows.data, path="data/generated/cumulative_fixation_data.csv")
}
```

Then group by object class to calculate fixation probability for each kind of object, normalizing by the number of objects of that type.

```{r}
cumulative.fixation.windows.grouped.data <- cumulative.fixation.windows.data %>%
  filter(!subject_id %in% bad.subjects) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

Then collapse over trials to get a cumulative probability for the whole window for each subject

```{r}
cumulative.fixation.windows.grouped.average.data <- cumulative.fixation.windows.grouped.data %>%
  group_by(subject_id, verb_type, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(cumulative.fixation.p))
```

Collapse across subjects to generate the equivalent of the figure from Altmann & Kamide.

```{r}
cumulative.fixation.data.summary <- cumulative.fixation.windows.grouped.average.data %>%
  filter(object_class %in% c('target.object', 'distractor')) %>%
  group_by(t.window, verb_type, object_class) %>%
  summarize(cumulative.fixation.m = mean(cumulative.fixation.p))
```

```{r}
ggplot(cumulative.fixation.data.summary, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset", y="Probability", shape="Verb Type", fill="Object Type")

```

# Question: Are there more pre-noun first looks to the target object than to the distractors?

First, grab the noun onset times to merge into our cumulative fixation data.

```{r}
noun.onset.times <- critical.trials.filtered %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, delay_bw_onset_of_verb_and_onset_of_target_noun) %>%
  mutate(relative.noun.onset = delay_bw_onset_of_verb_and_onset_of_target_noun * 1000) %>%
  select(-delay_bw_onset_of_verb_and_onset_of_target_noun)

trial.level.cumulative.fixation.data <- cumulative.fixation.windows.grouped.data %>%
  left_join(noun.onset.times, by=c("image_name", "verb_type"))
```

Then, grab the last time window before the noun onset for each trial. This is the critical data for this test.

```{r}
pre.noun.first.looks.data <- trial.level.cumulative.fixation.data %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.noun.onset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

Fit the model, with no covariance between random effects because the model cannot converge with full covariance matrix.

```{r}
model <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data)
summary(model)
```

# Question: Are there more pre-verb-offset first looks to the target object than to the distractors?

Verb offset times

```{r}
verb.offset.times <- critical.trials.filtered %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, duration_of_verb) %>%
  mutate(relative.verb.offset = duration_of_verb * 1000) %>%
  select(-duration_of_verb)

trial.level.cumulative.fixation.data.verb.offset <- cumulative.fixation.windows.grouped.data %>%
  left_join(verb.offset.times, by=c("image_name", "verb_type"))
```

```{r}
pre.verb.offset.first.looks.data <- trial.level.cumulative.fixation.data.verb.offset %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.verb.offset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r}
model <- lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data)
summary(model)
```

# Do people look at the target faster after a restricting verb

Relative to verb onset, when is the first fixation on the target?

```{r}
first.fixation.after.verb.onset <- critical.trials.filtered %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>%
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>%
  mutate(relative.t = t - (postverbal_noun_onset*1000))
```

```{r}
first.fixation.after.verb.onset.analysis.data <- first.fixation.after.verb.onset %>%
  ungroup() %>%
  select(subject_id, image_name, verb_type, relative.t)
```

```{r}
first.fixation.after.verb.onset.analysis.data %>%
  group_by(verb_type, subject_id) %>%
  summarize(M=mean(relative.t)) %>%
  ggplot(aes(x=verb_type, y=M, group=subject_id)) +
  geom_point()+
  geom_line()
```

```{r}
model <- lmer_alt(relative.t ~ verb_type + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data)

summary(model)
```

```{r}
first.fixation.after.verb.onset.subject.summary <- first.fixation.after.verb.onset %>%
  group_by(subject_id, verb_type) %>%
  summarize(m.t = mean(relative.t), ct = n())

first.fixation.after.verb.onset.summary <- first.fixation.after.verb.onset.subject.summary %>%
  group_by(verb_type) %>%
  summarize(m=mean(m.t), sd=sd(m.t), se=sd/sqrt(n()))
```

```{r}
ggplot(first.fixation.after.verb.onset.summary, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
  geom_col()+
  geom_errorbar(width=0.2)
```

### 2021-05-30 group-b/group-b-analysis.Rmd
add projects

---
title: "Group B Analysis"
output: html_notebook
---

```{r message=FALSE}
library(jsonlite)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ez)
```

# Import Data

Read JSON files and bind together into a tibble.

```{r}
data.files <- list.files('data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

# Extract relevant data

```{r}
task.data <- all.data %>%
  filter(!is.na(relation)) %>%
  select(subject_id, trial_index, stimulus, relation, quadrant, rt, correct_response, response, webgazer_data, webgazer_targets) %>%
  unpack(webgazer_targets) %>%
  unpack(`#screen`) %>%
  select(-top,-left,-x,-y,-bottom,-right)
```

Need to add condition information to the `task.data`

```{r}
condition.subject.info <- all.data %>%
  filter(!is.na(condition)) %>%
  select(subject_id, condition) %>%
  group_by(subject_id) %>%
  mutate(block = c(1,2)) %>%
  ungroup()

task.data <- task.data %>%
  group_by(subject_id) %>%
  mutate(block = c(rep(1,n()/2),rep(2,n()/2))) %>%
  left_join(condition.subject.info, by=c("subject_id", "block"))
```

# Question: Do people look more at the critical quadrant during free viewing?

Grab the relevant data, unnesting webgazer observations

```{r}
free.view.data <- task.data %>%
  filter(condition == "free") %>%
  unnest(webgazer_data)
```

Add quadrant information to each observation

```{r}
free.view.data <- free.view.data %>%
  mutate(x.percent = x / width * 100, y.percent = y / height * 100) %>%
  mutate(view_quadrant = case_when(
    x.percent <= 50 & y.percent <= 50 ~ 'top.left',
    x.percent > 50 & y.percent <= 50 ~ 'top.right',
    x.percent <= 50 & y.percent > 50 ~ 'bottom.left',
    x.percent > 50 & y.percent > 50 ~ 'bottom.right'
  )) %>%
  mutate(normalized_quadrant = case_when(
    quadrant == 1 & view_quadrant == 'top.left' ~ 'critical',
    quadrant == 1 & view_quadrant == 'top.right' ~ 'first',
    quadrant == 1 & view_quadrant == 'bottom.right' ~ 'second',
    quadrant == 1 & view_quadrant == 'bottom.left' ~ 'third',

    quadrant == 2 & view_quadrant == 'top.left' ~ 'third',
    quadrant == 2 & view_quadrant == 'top.right' ~ 'critical',
    quadrant == 2 & view_quadrant == 'bottom.right' ~ 'first',
    quadrant == 2 & view_quadrant == 'bottom.left' ~ 'second',

    quadrant == 3 & view_quadrant == 'top.left' ~ 'first',
    quadrant == 3 & view_quadrant == 'top.right' ~ 'second',
    quadrant == 3 & view_quadrant == 'bottom.right' ~ 'third',
    quadrant == 3 & view_quadrant == 'bottom.left' ~ 'critical',

    quadrant == 4 & view_quadrant == 'top.left' ~ 'second',
    quadrant == 4 & view_quadrant == 'top.right' ~ 'third',
    quadrant == 4 & view_quadrant == 'bottom.right' ~ 'critical',
    quadrant == 4 & view_quadrant == 'bottom.left' ~ 'first'
  ))
```

Summarize proportion of views in each quadrant for each trial
```{r}
free.view.summary.trial.data <- free.view.data %>%
  group_by(subject_id, trial_index, relation) %>%
  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
            first = sum(normalized_quadrant == 'first')/n(),
            second = sum(normalized_quadrant == 'second')/n(),
            third = sum(normalized_quadrant == 'third')/n()) %>%
  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
```
Summarize by subject
```{r}
free.view.summary.subject.data <- free.view.summary.trial.data %>%
  group_by(subject_id,relation,normalized_quadrant) %>%
  summarize(proportion = mean(proportion))
```

Summarize by condition 
```{r}
free.view.summary.condition.data <- free.view.summary.subject.data %>%
  group_by(normalized_quadrant, relation) %>%
  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
```
```{r}
ggplot(free.view.summary.condition.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill=relation)) +
  geom_col(position=position_dodge())+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  theme_classic()
```

Goal: ANOVA with quadrant and statement type as factors, gaze proportion as DV

```{r}
free.view.anova <- ezANOVA(free.view.summary.subject.data, wid=subject_id, dv=proportion, within=c(relation,normalized_quadrant))
free.view.anova$ANOVA
```
# Behavioral Analysis

First, extract relevant data and compute `correct` column

```{r}
behavioral.data <- task.data %>%
  select(subject_id, trial_index, relation, rt, response, correct_response, condition) %>%
  mutate(correct = response == correct_response)
```

Goal: ANOVA with RT as DV, condition, statement as IVs

```{r}
rt.behavioral.subject.data <- behavioral.data %>%
  group_by(subject_id, relation, condition) %>%
  filter(correct == TRUE) %>%
  summarize(rt = mean(rt))
```

```{r}
rt.anova <- ezANOVA(rt.behavioral.subject.data, dv=rt, wid=subject_id, within = c(relation, condition))
rt.anova$ANOVA
```

```{r}
rt.summary.condition.data <- rt.behavioral.subject.data %>%
  group_by(relation, condition) %>%
  summarize(M=mean(rt), SE=sd(rt)/sqrt(n()))

ggplot(rt.summary.condition.data, aes(x=relation, fill=condition, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  labs(x="Statement Type", y="Accuracy", color=NULL)+
  theme_classic()
```

Goal: ANOVA with ACC as DV, condition, statement as IVs

*note that paper computer accuracy as hit rate - false alarm rate*
```{r}
acc.behavioral.subject.data <- behavioral.data %>%
  group_by(subject_id, relation, condition) %>%
  summarize(hit.rate = sum(correct == TRUE & response == 't') / sum(correct_response == 't'),
            fa.rate = sum(correct == FALSE & response == 't') / sum(correct_response == 'f')) %>%
  mutate(accuracy = hit.rate - fa.rate)
```

```{r}
acc.anova <- ezANOVA(acc.behavioral.subject.data, dv=accuracy, wid=subject_id, within = c(relation, condition))
acc.anova$ANOVA
```

Recreate figure from paper

```{r}
acc.summary.condition.data <- acc.behavioral.subject.data %>%
  group_by(relation, condition) %>%
  summarize(M=mean(accuracy), SE=sd(accuracy)/sqrt(n()))

ggplot(acc.summary.condition.data, aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  coord_cartesian(ylim=c(0.3,0.8)) +
  labs(x="Statement Type", y="Accuracy", color=NULL)+
  theme_classic()
```

### 2021-05-30 group-c/group-c-analysis.Rmd
add projects

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

Loading data and converting it to a tibble

```{r}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

Split Part 1 and Part 2 data

```{r}
study.id.day.1.group.1 <- "6062337f1a63a6788185d0e3"
study.id.day.1.group.2 <- "607de170bb44b7e25174421f"
study.id.day.2.group.1 <- "606233c0e42b980319b6a18e"
study.id.day.2.group.2 <- "607de2837874a824e2e8c6ec"

all.data <- all.data %>%
  mutate(day = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.1.group.2), 1, 2)) %>%
  mutate(group = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.2.group.1), 1, 2))

data.day.1 <- all.data %>% filter(day == 1)
data.day.2 <- all.data %>% filter(day == 2)
```

Select the eyetracking data

```{r}
eyetracking.data <- data.day.1 %>%
  filter(phase == "part2") %>%
  select(subject_id, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
  unpack(webgazer_targets) %>%
  unpack(c("#left-img", "#right-img"), names_sep=".") %>%
  unnest(webgazer_data)
```

Add ROI information

```{r}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

```{r}
eyetracking.data <- eyetracking.data %>%
  mutate(in.left.roi = in.box(x, y,`#left-img.left`, `#left-img.right`, `#left-img.top`, `#left-img.bottom`, 50))%>%
  mutate(in.right.roi = in.box(x, y,`#right-img.left`, `#right-img.right`, `#right-img.top`, `#right-img.bottom`, 50))%>%
  mutate(in.target.roi = if_else(left_image_new == TRUE, in.left.roi, in.right.roi))%>%
  mutate(in.distractor.roi = if_else(left_image_new == TRUE, in.right.roi, in.left.roi))
```

Get looking score (proportion of samples in the target ROI vs distractor ROI)

```{r}
looking.score.data <- eyetracking.data %>% 
  group_by(subject_id, right_image, left_image, right_image_new, left_image_new) %>%
  summarise(looking.score = if_else(sum(in.target.roi, in.distractor.roi) == 0, 0, sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi))) %>%
  mutate(image = if_else(right_image_new, left_image, right_image))
```

Do subjects look at the new object more than the old object? (Is looking score statistically greater than 0.5?)

```{r}
t.test.data1 <- looking.score.data %>%
  group_by(subject_id) %>%
  summarize(M.looking.score = mean(looking.score))

t.test(t.test.data1$M.looking.score, mu = 0.5)
```

# Day 2 Performance

```{r}
day2.test.data <- data.day.2 %>%
  filter(task %in% c("recognition", "confidence")) %>%
  select(subject_id, image, old_or_new, correct, rt, response, task) %>%
  pivot_wider(names_from=task, values_from=c(correct, response, rt)) %>%
  select(-correct_confidence) %>%
  mutate(response_confidence = as.numeric(response_confidence))
```

Are people more confident after a correct response than an incorrect response?

```{r}
confidence.test.data <- day2.test.data %>%
  group_by(subject_id, correct_recognition) %>%
  summarize(M.confidence = mean(response_confidence))

subjects.100.percent.accurate <- day2.test.data %>%
  group_by(subject_id) %>%
  summarize(accuracy = mean(correct_recognition)) %>%
  filter(accuracy == 1) %>%
  pull(subject_id)

confidence.test.data.filtered <- confidence.test.data %>%
  filter(!subject_id %in% subjects.100.percent.accurate)

t.test(M.confidence ~ correct_recognition, data=confidence.test.data.filtered, paired=T)
```

Are people faster to make a correct response?

```{r}
rt.test.data <- day2.test.data %>%
  group_by(subject_id, correct_recognition) %>%
  summarize(M.rt = mean(rt_recognition))

rt.test.data.filtered <- rt.test.data %>%
  filter(!subject_id %in% subjects.100.percent.accurate)

t.test(M.rt ~ correct_recognition, data=rt.test.data.filtered, paired=T)
```

Does Looking Score Predict Confidence?

```{r}
looking.plus.behavioral <- left_join(looking.score.data, day2.test.data)

looking.confidence.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  group_by(subject_id) %>%
  summarize(pearson.r = cor(looking.score, response_confidence)) %>%
  mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

looking.confidence.correlations.subjects.filtered <- looking.confidence.correlations.subjects %>%
  filter(!is.na(pearson.r))
```

```{r}
hist(looking.confidence.correlations.subjects.filtered$r.to.z)
```

```{r}
t.test(looking.confidence.correlations.subjects.filtered$r.to.z)
```

```{r}
looking.rt.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  group_by(subject_id) %>%
  summarize(pearson.r = cor(looking.score, rt_recognition)) %>%
  mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

looking.rt.correlations.subjects.filtered <- looking.rt.correlations.subjects %>%
  filter(!is.na(pearson.r))
```

```{r}
hist(looking.rt.correlations.subjects.filtered$r.to.z)
```

```{r}
t.test(looking.rt.correlations.subjects.filtered$r.to.z)
```

### 2021-05-30 group-d/group-d-analysis.Rmd
add projects

---
title: "R Notebook"
output: html_notebook
---

# Setup

```{r message=FALSE, warning=FALSE}
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
```

# Load Data

```{r}
data.files <- list.files('data/run-2', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

# Extract Relevant Data

Start with getting the trials we care about for the main analysis.

```{r}
task.data <- all.data %>%
  filter(compatibility != 'NA', compatibility != 'filler') %>%
  select(subject, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
```

Add a column that uniquely identifies the combination of images and audio shown on the screen

```{r}
trialID.data <- task.data %>%
  group_by(audio, images) %>%
  slice(1) %>%
  select(audio, images) %>%
  ungroup() %>%
  mutate(trialID = 1:n())

task.data <- task.data %>%
  left_join(trialID.data)
```

```{r}
eyetracking.data <- task.data %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
  unnest(webgazer_data)

mousetracking.data <- task.data %>%
  unnest(mouse_events)
```

# Analyze Mouse Move Data

Is the first object that the mouse moves over biased by the verb compatibility?

First, create a data set with each trial, adding column for which object the mouse moves over first.

# WTF IS HAPPENING with TRIAL ID??

```{r}
first.move <- mousetracking.data %>%
  select(subject, trialID, object, type, compatibility, target_instrument, target_animal, images) %>%
  group_by(subject, trialID) %>%
  filter(type=="enter") %>%
  slice(1) %>%
  rowwise() %>%
  mutate(which_loc = which(images == object)-1) %>%
  ungroup() %>%
  mutate(instrument_loc = str_sub(target_instrument, start=-1, end=-1)) %>%
  mutate(animal_loc = str_sub(target_animal, start=-1, end=-1)) %>%
  mutate(first.move.type = case_when(
    which_loc == instrument_loc ~ 'instrument',
    which_loc == animal_loc ~ 'animal',
    TRUE ~ 'other')) %>%
  mutate(is.mouse.instrument = if_else(first.move.type == 'instrument', 1, 0)) %>%
  mutate(compatibility = factor(compatibility))
```

Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.

```{r}
first.move.subject.summary <- first.move %>%
  group_by(subject, compatibility) %>%
  summarize(prop.animal = mean(first.move.type == 'animal'),
            prop.instrument = mean(first.move.type == 'instrument'),
            prop.other = mean(first.move.type == 'other')) %>%
  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
```

Summarize the condition-level data for a barplot.

```{r}
first.move.summary <- first.move.subject.summary %>%
  group_by(compatibility, target_type) %>%
  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n()))
```

```{r}
ggplot(first.move.summary, aes(x=compatibility, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
  geom_col(position=position_dodge(width=0.9))+
  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
  theme_classic()
```

Run the mixed-effects logistic regression model to predict whether the first movement is on the instrument.

```{r}
contrasts(first.move$compatibility) <- cbind(c(1/3, -2/3, 1/3), c(-1/2, 0, 1/2))

model <- glmer(is.mouse.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=first.move, family="binomial")
summary(model)
```

# Analyze Eye Movement Data

First figure out which object they are looking at.

Define a function for determining if `x,y` value falls in box.

```{r}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

Calculate gaze in ROIs.

```{r}
eyetracking.data.with.roi <- eyetracking.data %>%
  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
  mutate(in.roi.0 = in.box(x,y,`#jspsych-free-sort-draggable-0.left`, `#jspsych-free-sort-draggable-0.right`, `#jspsych-free-sort-draggable-0.top`, `#jspsych-free-sort-draggable-0.bottom`, 100)) %>%
  mutate(in.roi.1 = in.box(x,y,`#jspsych-free-sort-draggable-1.left`, `#jspsych-free-sort-draggable-1.right`, `#jspsych-free-sort-draggable-1.top`, `#jspsych-free-sort-draggable-1.bottom`, 100)) %>%
  mutate(in.roi.2 = in.box(x,y,`#jspsych-free-sort-draggable-2.left`, `#jspsych-free-sort-draggable-2.right`, `#jspsych-free-sort-draggable-2.top`, `#jspsych-free-sort-draggable-2.bottom`, 100)) %>%
  mutate(in.roi.3 = in.box(x,y,`#jspsych-free-sort-draggable-3.left`, `#jspsych-free-sort-draggable-3.right`, `#jspsych-free-sort-draggable-3.top`, `#jspsych-free-sort-draggable-3.bottom`, 100)) %>%
  mutate(in.roi.instrument = case_when(
    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) %>%
  mutate(in.roi.animal = case_when(
    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) 
```

Add time window

```{r}
eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
  mutate(t.window = floor(t/50)*50)
```

Load audio info
```{r message=FALSE}
audio.info <- read_csv('info/audio_timing.csv')
```

Calculate average animal onset
```{r}
animal.onset <- audio.info %>% pull(onset_noun) %>% mean()
instrument.onset <- audio.info %>% pull(onset_instrument) %>% mean()
```

Summarize data for plotting
```{r}
eyetracking.figure.2.data <- eyetracking.data.with.roi %>%
  filter(t.window <= 4000) %>%
  group_by(subject, compatibility, t.window) %>%
  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
  group_by(compatibility, t.window, object_type) %>%
  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
```

```{r}
ggplot(eyetracking.figure.2.data, aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, shape=object_type))+
  geom_ribbon(color=NA, alpha=0.3)+
  geom_line(size=1)+
  theme_classic() +
  geom_vline(xintercept = animal.onset) + 
  geom_vline(xintercept = instrument.onset) + 
  facet_wrap(~object_type)
```
```{r}
ggplot(eyetracking.figure.2.data, aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, shape=object_type))+
  geom_point(size=3)+
  theme_classic()
```

Merge in audio timing information

```{r}
eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
  mutate(sound = str_split(audio, pattern="/", simplify = T)[,4])

eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
  left_join(audio.info, by="sound")
```

Add time window information

```{r}
eyetracking.data.with.time.windows <- eyetracking.data.with.roi %>%
  mutate(time.window = case_when(
    t < onset_verb + 200 ~ "pre-verb-onset",
    t <= onset_noun + 200~ "post-verb-onset-pre-animal-onset",
    t <= onset_instrument + 200 ~ "post-animal-onset-pre-instrument-onset",
    t <= onset_instrument + 1500 + 200 ~ "post-instrument-onset",
    TRUE ~ "end"
  ))
```

Summarize fixations on target and instrument

```{r}
eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
  group_by(subject, trialID, sound, compatibility, time.window) %>%
  summarize(prop.fixations.animal = sum(in.roi.animal) / n(),
            prop.fixations.instrument = sum(in.roi.instrument) / n()) %>%
  mutate(compatibility = factor(compatibility))
```

Add orthogonal contrasts to model

```{r}
contrasts(eyetracking.window.summary.by.trial$compatibility) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
```

# First time window: verb onset to animal onset

Fixations to the animal

```{r}
data.time.window.1 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-verb-onset-pre-animal-onset")

model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=data.time.window.1)

summary(model.time.window.1)
```

Fixations to the instrument

```{r}
model.time.window.1 <- lmer(prop.fixations.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=data.time.window.1)

summary(model.time.window.1)
```

# Second time window: animal onset to instrument onset

Animal

```{r}
data.time.window.2 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-animal-onset-pre-instrument-onset")

model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=data.time.window.2)

summary(model.time.window.2)
```

Instrument

```{r}
model.time.window.2 <- lmer(prop.fixations.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=data.time.window.2)

summary(model.time.window.2)
```

# Third window: post-instrument onset

Animal

```{r}
data.time.window.3 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-instrument-onset")

model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=data.time.window.3)
summary(model.time.window.3)
```

Instrument

```{r}
model.time.window.3 <- lmer(prop.fixations.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=data.time.window.3)
summary(model.time.window.3)
```

### 2021-05-30 group-e/group-e-analysis.Rmd
add projects

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

Loading data and converting it to a tibble

```{r}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

Excluding Subjects

```{r}
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
```

Convert data to long format for gaze measurements

```{r}
task.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, time_elapsed, trial_index, response, rt, webgazer_data, webgazer_targets) %>%
  unnest(webgazer_data) %>%
  unpack(webgazer_targets) %>%
  unpack(c('#face1', '#face2'), names_sep = ".")
```

Add condition information

```{r}
task.data <- task.data %>%
  mutate(task = if_else(study_id == '60748d36577623e2677865c6', "Attractiveness", "Roundness"))
```

Compute average trial length

```{r}
response.time.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, trial_index, response, rt)
```

```{r}
rt.summary <- response.time.data %>%
  summarize(M=mean(rt), SD=sd(rt))

cutoff.time <- rt.summary$M - rt.summary$SD
#cutoff.time <- 1670

rt.summary
```

# Eye Gaze Analysis

Normalize time to time until decision

```{r}
task.data <- task.data %>%
  mutate(time_until_decision = rt - t)
```

Normalize t measurement to time before decision

```{r}
task.data <- task.data %>%
  filter(time_until_decision <= cutoff.time)
```

Add in-the-box info

```{r}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

```{r}
task.data <- task.data %>%
  mutate(in.left.box = in.box(x,y,`#face1.left`,`#face1.right`,`#face1.top`,`#face1.bottom`,0)) %>%
  mutate(in.right.box = in.box(x,y,`#face2.left`,`#face2.right`,`#face2.top`,`#face2.bottom`,0)) %>%
  mutate(in.target.box = if_else(response == 'a', in.left.box, in.right.box)) %>%
  mutate(in.other.box = if_else(response == 'a', in.right.box, in.left.box))
```

Bin the time by 50ms

```{r}
task.data <- task.data %>%
  mutate(time.window = floor(time_until_decision/50)*50)
```

Summarize by time window

```{r}
summary.gaze.view.subject <- task.data %>%
  filter(in.target.box == TRUE | in.other.box == TRUE) %>%
  group_by(subject_id, time.window, task) %>%
  summarize(prop.in.target.subject = mean(in.target.box))
```
```{r}
summary.gaze.view <- summary.gaze.view.subject %>%
  group_by(time.window, task) %>%
  summarize(prop.in.target = mean(prop.in.target.subject), se = sd(prop.in.target.subject)/sqrt(n()))
```

KS Test?

```{r}
ks.test(summary.gaze.view %>% filter(task == "Attractiveness") %>% pull(prop.in.target),
         summary.gaze.view %>% filter(task == "Roundness") %>% pull(prop.in.target))
```

```{r}
ggplot(summary.gaze.view, aes(x=time.window, y=prop.in.target, ymin=prop.in.target-se, ymax=prop.in.target+se, color=task, fill=task))+
  geom_ribbon(color=NA, alpha=0.3)+
  geom_line()+
  scale_x_reverse()+
  theme_classic()+
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task")
```

Fit sigmoid curve

```{r}
attractiveness.curve <- summary.gaze.view %>% filter(roundness_task == FALSE)
fit <- nls(prop.in.target ~ MaxP + (MinP - MaxP)/(1+(time.window/InfP)^Slope), data = attractiveness.curve, start=list(MaxP=0.9,MinP=0.5,InfP=-500,Slope=-1))
```

### 2021-05-30 group-d/load-audio-timing.R

@@ -1,0 +1,43 @@
+library(readr)
+library(dplyr)
+library(tidyr)
+library(readtextgrid)
+
+textgridfiles <- list.files('group-d/info/audio/timing_files/', full.names = T, pattern = ".TextGrid")
+
+extract_timing <- function(file){
+  df <- read_textgrid(file)
+  
+  num_tokens <- df %>%
+    filter(tier_num == 1, text != "") %>%
+    nrow()
+  
+  if(num_tokens == 6) {
+    speech_list <- c("verb","noun_article", "noun", "with", "instrument_article", "instrument")
+    token_list <- c(1,2,3,4,5,6)
+  } else if(num_tokens == 7) {
+    speech_list <- c("verb", "verb", "noun_article", "noun", "with", "instrument_article", "instrument")
+    token_list <- c(1,1,2,3,4,5,6)
+  } else {
+    print(file)
+    return()
+  }
+  
+  out <- df %>%
+    filter(tier_num == 1, text != "") %>%
+    select(file, text, xmin, xmax) %>%
+    mutate(speech_type = speech_list, token = token_list) %>%
+    group_by(file, speech_type, token) %>%
+    summarize(duration = (max(xmax) - min(xmin))*1000, onset = min(xmin)*1000) %>%
+    ungroup() %>%
+    mutate(sound = str_replace(file, ".TextGrid", ".mp3")) %>%
+    select(sound, speech_type, onset, duration) %>%
+    pivot_wider(names_from = speech_type, values_from = c(onset, duration))
+  return(out)
+}
+
+result <- lapply(textgridfiles,extract_timing)
+
+result.df <- bind_rows(result)
+
+write_csv(result.df, 'group-d/info/audio_timing.csv')

### 2021-05-30 group-d/prep-audio-timing.R

@@ -1,0 +1,10 @@
+library(stringr)
+library(readr)
+
+audio.files <- list.files('group-d/info/audio', pattern=".mp3")
+
+for(f in audio.files){
+  p <- str_split(f, "\\.")[[1]][1]
+  words <- str_split(p, "_")[[1]]
+  write_lines(words, path=paste0('group-d/info/audio/', p,'.txt'))
+}

### 2021-05-30 group-b/group-b-analysis.Rmd
update plot

@@
 
-ggplot(rt.summary.condition.data, aes(x=relation, fill=condition, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
+ggplot(rt.summary.condition.data, aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
   geom_point(size=5)+
@@
   scale_color_manual(values=c("orange2","royalblue4"))+
-  labs(x="Statement Type", y="Accuracy", color=NULL)+
+  labs(x="Statement Type", y="Response Time (ms)", color=NULL)+
   theme_classic()

### 2021-06-24 group-a/group-a-analysis.Rmd
syncing a variety of changes

@@
 library(afex)
+library(forcats)
 ```
@@
 all.data <- bind_rows(data.tables)
+```
+
+Mutate value types as needed
+
+```{r}
+all.data <- all.data %>%
+  mutate(subject_id = factor(subject_id))
 ```
@@
 
+# Subject Exclusion Criteria
+
+We'll try this two ways.
+First if we adopt minimal exclusion criteria, removing subjects whose eye tracking data is essentially unusable.
+Second if we adopt aggressive exclusion criteria, removing subjects with obviously worse eye tracking data.
+
+Set which mode here:
+```{r}
+# 'AGGRESSIVE' or 'MINIMAL'
+exclusion.mode <- 'MINIMAL' 
+```
+
+## Proportion of measured data in an ROI.
+
 Check the proportion of samples that were in at least one ROI for subjects.
@@
 ```
-Exclude subjects below a threshold?
+Exclude subjects below a threshold
 
 ```{r}
-bad.subjects <- prop.in.roi.by.subject %>%
-  filter(prop.of.samples.in.roi == 0) %>%
+if(exclusion.mode == 'AGGRESSIVE') {
+  prop.samples.threshold <- 0.2
+}
+if(exclusion.mode == 'MINIMAL') {
+  prop.samples.threshold <- 0
+}
+
+bad.subjects.prop.samples <- prop.in.roi.by.subject %>%
+  filter(prop.of.samples.in.roi <= prop.samples.threshold) %>%
   pull(subject_id)
+```
 
-# to match laila's analysis
-bad.subjects <- c("5f3a76043bb11c6786e731bf", "5f9c6b2def8bdf1102de5338", "607197e359bae0449ac9d4bc", "60142d5718e5943b09fd9298")
+## Validation accuracy
+
+```{r}
+validation.accuracy.data <- all.data %>%
+  filter(trial_type == 'webgazer-validate')
+```
+
+What % of subjects needed to recalibrate because of poor initial calibration?
+
+```{r}
+validation.accuracy.data %>% 
+  group_by(subject_id) %>%
+  count() %>%
+  group_by(n) %>%
+  count()
+```
+
+Get final average distance for each subject
+
+```{r}
+validation.percent <- validation.accuracy.data %>%
+  group_by(subject_id) %>%
+  slice_tail() %>%
+  select(subject_id, percent_in_roi) %>%
+  unnest(percent_in_roi) %>%
+  group_by(subject_id) %>%
+  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
+  mutate(subject_id = fct_reorder(subject_id, M))
+```
+
+```{r}
+ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
+  geom_pointrange() +
+  theme_classic()
+```
+Set criteria for minimal and aggressive exclusions
+
+```{r}
+if(exclusion.mode == 'AGGRESSIVE') {
+  validation.threshold <- 50
+}
+if(exclusion.mode == 'MINIMAL') {
+  validation.threshold <- 10
+}
+
+bad.subjects.validation <- validation.percent %>%
+  filter(M <= validation.threshold) %>%
+  pull(subject_id) %>%
+  as.character()
+```
+
+## Final exclusion data
+
+```{r}
+bad.subjects <- unique(c(bad.subjects.prop.samples, bad.subjects.validation))
 
@@
 ```{r}
-first.fixation.after.verb.onset.analysis.data %>%
-  group_by(verb_type, subject_id) %>%
-  summarize(M=mean(relative.t)) %>%
-  ggplot(aes(x=verb_type, y=M, group=subject_id)) +
-  geom_point()+
-  geom_line()
-```
-
-```{r}
 model <- lmer_alt(relative.t ~ verb_type + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data)

### 2021-06-30 manuscript.Rmd
adding manuscript draft

---
title             : "Eye-tracking on the web: lessons learned from replicating 6 experiments"
shorttitle        : "Just picked a random title: feel free to change"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  ADD LATER

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

<!-- MAJOR TO DOs: 
 - get data from in-lab versions of group A (AJ) and group D (RR)
 - re-run Posner cueing (after we finish analysing the first 5)
 - replicate group D and ?? in lab

 (see bottom for notes from e-mails)
 -->

Intro stuff:

- Eye-tracking as a key method in cognitive science research

- Online data collection is more and more popular & let's us ask new questions

- But, concerns over quality + little known about eye-tracking online

_Present work_

In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the `jsPsych` platform and `webgazer.js` plug-in. The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes). ...

# Experiment 1
<!-- group a -->

The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.

```{r read_groupA_data}

```

## Methods

All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at [https://osf.io/s82kz](https://osf.io/s82kz). All participants provided informed consent and this study was approved by the Vassar College Institutional Review Board.

### Participants

Participants for this experiment were sampled from a wide pool of Prolific users who are fluent in English and were paid for their participation. Our sample size of participants was determined by the total run time of our experiment, ~10 minutes, and the allotted funding that was endowed to us by the Vassar College Cognitive Science Department. From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific, and we ended up with a sample size of 60 participants. For unknown reasons, 2 of the subjects’ results were not recorded, so in the analysis, we worked with data collected from 58 participants.

### Procedure

Participants completed the experiment remotely and entirely online on the platform Prolific. During the experiment, the participants viewed a screen and were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence. The visual stimuli were created through Canva and depict a subject accompanied by 4 to 5 objects in the scene. 16 of the devised stimuli were critical to our trial, and each of these images have 2 sentences associated with it. One of these sentences is in the restrictive condition, where the verb only applies to one object in the scene, and the other is in the nonrestrictive condition, where the verb could apply to all of the objects in the scene. To illustrate an example, reference Figure 1. This scene depicts a boy alongside a cake, ball, car, and train set. In the case of this particular image, the cake is the target object, so the two corresponding sentences to this image are, “The boy will eat the cake” (restrictive) and “The boy will move the cake” (nonrestrictive).

### Materials

Therefore, for the 16 critical images, there are 16 control sentences where the verb does not constrain the target object and 16 restrictive sentences where the verb does constrain the target object. Each participant randomly received one sentence, restrictive or nonrestrictive, per scene. Of the 16 critical trials, each participant got 8 sentences that were restrictive and 8 that were nonrestrictive and the order of these were randomized. Trials were also designed so that participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence relayed was feasible given the visual image. There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
In addition to the 16 critical images, we also devised an additional 16 filler images that are not pertinent to our data collection and analysis. The critical trials were also presented in a randomized order along with these 16 filler trials. Unlike the critical images, the filler images were accompanied by only one sentence that is unfeasible given it’s corresponding scene. This was so that when participants were asked whether or not the scene was possible, the filler trials would always elicit the answer, “no.”
Despite recording participants’ reaction time and keyboard response after each trial, we were specifically measuring for the participant’s first fixation to the target object and distractors relative to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.

### Eye-Tracking Calibration and Validation
Before initiating the experiment, participants were prompted to complete an eye-tracking calibration and validation procedure to ensure the data collected via the webcam-based eye tracking method was as accurate as possible. In order to allow the software to track where participants are looking, subjects were presented with a series of dots that appeared on the screen. Participants were then instructed to look at each dot as they appeared and click on it. By visually fixating and then clicking on one dot, it would then disappear and a new one would reappear in a different location on the screen. The calibration dots appeared in the central area of the screen where the visual stimuli would appear in order to ensure Web Gazer would be able to track eye movements to the relevant regions of interest. After completing this calibration, participants were then asked to go through the same steps of the calibration, except this time, they would have to just look at, not click, the dots as they appear on the screen in order to measure the accuracy of the calibration. This process completes the Web Gazer calibration and validation process.

### Data pre-processing and analysis
We used `r cite_r("references.bib")` for all our analyses.

## Results

### Replication

> here we will describe the analyses that are as close as possible to the original paper

### Calibration

> here we will describe the analyses that correlate calibration quality with effect size at the individual (Josh H?)

## Discussion

# Experiment 2
<!-- group b -->

The second study was a replication attempt of @johanssonLookHereEye2014.

## Methods

### Participants

### Material

### Procedure

### Data analysis

## Results

## Discussion

# Experiment 3
<!-- group c -->

The third study was a replication attempt of @Mann???.

## Methods

### Participants

### Material

### Procedure

### Data analysis

## Results

## Discussion

# Experiment 4
<!-- group d -->

The fourth study was a replication attempt of @ryskinVerbBiasesAre2017.

## Methods

### Participants

### Material

### Procedure

### Data analysis

## Results

## Discussion

# Experiment 5
<!-- group e -->

The fifth study was a replication attempt of @??.

## Methods

### Participants

### Material

### Procedure

### Data analysis

## Results

## Discussion

# Experiment 6
<!-- posner cueing task -->

The sixth study was a replication attempt of @??.

## Methods

### Participants

### Material

### Procedure

### Data analysis

## Results

## Discussion

# Combined Analyses

# General Discussion

<!-- NOTES FROM EMAILS:

JOSH DE LEEUW: For calibration quality, there are a few ways you could go about it.

As a preliminary step filtering the data to trial_type == 'webgazer-validate' should get you a data frame with just the validation trials. We ran a validation trial immediately after calibration. The trial involves showing some set of dots on the screen for a few seconds each and recording all of the samples from webgazer for each dot. Each experiment defined a different set of dots for validation, depending on where the relevant ROIs were.

The data for each of these trials includes columns for:

raw_gaze: all the raw data points recorded from webgazer, organized by which point was shown on the screen
percent_in_roi:  The jsPsych plugin also calculates the percentage of samples for each dot that are within some specified radius. I think we used 150px for all of the experiments, but I can verify that.
average_offset: The average x,y offset of the cloud of points measured for each validation point. Also includes a value r, which is the radius of the circle centered at the midpoint of the cloud that includes half the points. Basically a measure of variance.
validation_points: coordinates of each of the points on the screen, in the same order as the other columns so that you could see, e.g., if calibration tends to be better on more central points.

We also included a step where if the validation was poor after the first attempt we repeated the calibration and validation procedure one additional time. So some subjects have more validation trials than others. If you look at my R Notebook for group A (just pushed to GH now) you can see some initial attempts to extract validation info and use it to exclude subjects. -->

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-06-30 manuscript.tex
adding manuscript draft

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Eye-tracking on the web: lessons learned from replicating 6 experiments},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Just picked a random title: feel free to change}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Eye-tracking on the web: lessons learned from replicating 6 experiments}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

\abstract{
ADD LATER
}

\begin{document}
\maketitle

Intro stuff:

\begin{itemize}
\item
  Eye-tracking as a key method in cognitive science research
\item
  Online data collection is more and more popular \& let's us ask new questions
\item
  But, concerns over quality + little known about eye-tracking online
\end{itemize}

\emph{Present work}

In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the \texttt{jsPsych} platform and \texttt{webgazer.js} plug-in. The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``natural'' scenes). \ldots{}

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

The first study was a replication attempt of Altmann and Kamide (1999).

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at \url{https://osf.io/s82kz}. All participants provided informed consent and this study was approved by the Vassar College Institutional Review Board.

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

Participants for this experiment were sampled from a wide pool of Prolific users who are fluent in English and were paid for their participation. Our sample size of participants was determined by the total run time of our experiment, \textasciitilde10 minutes, and the allotted funding that was endowed to us by the Vassar College Cognitive Science Department. From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific, and we ended up with a sample size of 60 participants. For unknown reasons, 2 of the subjects' results were not recorded, so in the analysis, we worked with data collected from 58 participants.

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

Participants completed the experiment remotely and entirely online on the platform Prolific. During the experiment, the participants viewed a screen and were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence. The visual stimuli were created through Canva and depict a subject accompanied by 4 to 5 objects in the scene. 16 of the devised stimuli were critical to our trial, and each of these images have 2 sentences associated with it. One of these sentences is in the restrictive condition, where the verb only applies to one object in the scene, and the other is in the nonrestrictive condition, where the verb could apply to all of the objects in the scene. To illustrate an example, reference Figure 1. This scene depicts a boy alongside a cake, ball, car, and train set. In the case of this particular image, the cake is the target object, so the two corresponding sentences to this image are, ``The boy will eat the cake'' (restrictive) and ``The boy will move the cake'' (nonrestrictive).

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

Therefore, for the 16 critical images, there are 16 control sentences where the verb does not constrain the target object and 16 restrictive sentences where the verb does constrain the target object. Each participant randomly received one sentence, restrictive or nonrestrictive, per scene. Of the 16 critical trials, each participant got 8 sentences that were restrictive and 8 that were nonrestrictive and the order of these were randomized. Trials were also designed so that participants had to input a keyboard response indicating ``yes'' or ``no'' as to whether the sentence relayed was feasible given the visual image. There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
In addition to the 16 critical images, we also devised an additional 16 filler images that are not pertinent to our data collection and analysis. The critical trials were also presented in a randomized order along with these 16 filler trials. Unlike the critical images, the filler images were accompanied by only one sentence that is unfeasible given it's corresponding scene. This was so that when participants were asked whether or not the scene was possible, the filler trials would always elicit the answer, ``no.''
Despite recording participants' reaction time and keyboard response after each trial, we were specifically measuring for the participant's first fixation to the target object and distractors relative to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.

\hypertarget{eye-tracking-calibration-and-validation}{%
\subsubsection{Eye-Tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}}

Before initiating the experiment, participants were prompted to complete an eye-tracking calibration and validation procedure to ensure the data collected via the webcam-based eye tracking method was as accurate as possible. In order to allow the software to track where participants are looking, subjects were presented with a series of dots that appeared on the screen. Participants were then instructed to look at each dot as they appeared and click on it. By visually fixating and then clicking on one dot, it would then disappear and a new one would reappear in a different location on the screen. The calibration dots appeared in the central area of the screen where the visual stimuli would appear in order to ensure Web Gazer would be able to track eye movements to the relevant regions of interest. After completing this calibration, participants were then asked to go through the same steps of the calibration, except this time, they would have to just look at, not click, the dots as they appear on the screen in order to measure the accuracy of the calibration. This process completes the Web Gazer calibration and validation process.

\hypertarget{data-pre-processing-and-analysis}{%
\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}}

We used R {[}Version 4.1.0; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{replication}{%
\subsubsection{Replication}\label{replication}}

\begin{quote}
here we will describe the analyses that are as close as possible to the original paper
\end{quote}

\hypertarget{calibration}{%
\subsubsection{Calibration}\label{calibration}}

\begin{quote}
here we will describe the analyses that correlate calibration quality with effect size at the individual (Josh H?)
\end{quote}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

The second study was a replication attempt of Johansson and Johansson (2014).

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

\hypertarget{material}{%
\subsubsection{Material}\label{material}}

\hypertarget{procedure-1}{%
\subsubsection{Procedure}\label{procedure-1}}

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

\hypertarget{experiment-3}{%
\section{Experiment 3}\label{experiment-3}}

The third study was a replication attempt of (\textbf{Mann?})???.

\hypertarget{methods-2}{%
\subsection{Methods}\label{methods-2}}

\hypertarget{participants-2}{%
\subsubsection{Participants}\label{participants-2}}

\hypertarget{material-1}{%
\subsubsection{Material}\label{material-1}}

\hypertarget{procedure-2}{%
\subsubsection{Procedure}\label{procedure-2}}

\hypertarget{data-analysis-1}{%
\subsubsection{Data analysis}\label{data-analysis-1}}

\hypertarget{results-2}{%
\subsection{Results}\label{results-2}}

\hypertarget{discussion-2}{%
\subsection{Discussion}\label{discussion-2}}

\hypertarget{experiment-4}{%
\section{Experiment 4}\label{experiment-4}}

The fourth study was a replication attempt of Ryskin, Qi, Duff, and Brown-Schmidt (2017).

\hypertarget{methods-3}{%
\subsection{Methods}\label{methods-3}}

\hypertarget{participants-3}{%
\subsubsection{Participants}\label{participants-3}}

\hypertarget{material-2}{%
\subsubsection{Material}\label{material-2}}

\hypertarget{procedure-3}{%
\subsubsection{Procedure}\label{procedure-3}}

\hypertarget{data-analysis-2}{%
\subsubsection{Data analysis}\label{data-analysis-2}}

\hypertarget{results-3}{%
\subsection{Results}\label{results-3}}

\hypertarget{discussion-3}{%
\subsection{Discussion}\label{discussion-3}}

\hypertarget{experiment-5}{%
\section{Experiment 5}\label{experiment-5}}

The fifth study was a replication attempt of @??.

\hypertarget{methods-4}{%
\subsection{Methods}\label{methods-4}}

\hypertarget{participants-4}{%
\subsubsection{Participants}\label{participants-4}}

\hypertarget{material-3}{%
\subsubsection{Material}\label{material-3}}

\hypertarget{procedure-4}{%
\subsubsection{Procedure}\label{procedure-4}}

\hypertarget{data-analysis-3}{%
\subsubsection{Data analysis}\label{data-analysis-3}}

\hypertarget{results-4}{%
\subsection{Results}\label{results-4}}

\hypertarget{discussion-4}{%
\subsection{Discussion}\label{discussion-4}}

\hypertarget{experiment-6}{%
\section{Experiment 6}\label{experiment-6}}

The sixth study was a replication attempt of @??.

\hypertarget{methods-5}{%
\subsection{Methods}\label{methods-5}}

\hypertarget{participants-5}{%
\subsubsection{Participants}\label{participants-5}}

\hypertarget{material-4}{%
\subsubsection{Material}\label{material-4}}

\hypertarget{procedure-5}{%
\subsubsection{Procedure}\label{procedure-5}}

\hypertarget{data-analysis-4}{%
\subsubsection{Data analysis}\label{data-analysis-4}}

\hypertarget{results-5}{%
\subsection{Results}\label{results-5}}

\hypertarget{discussion-5}{%
\subsection{Discussion}\label{discussion-5}}

\hypertarget{combined-analyses}{%
\section{Combined Analyses}\label{combined-analyses}}

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-altmannIncrementalInterpretationVerbs1999}{}%
Altmann, G. T. M., \& Kamide, Y. (1999). Incremental interpretation at verbs: Restricting the domain of subsequent reference. \emph{Cognition}, \emph{73}(3), 247--264. \url{https://doi.org/10.1016/S0010-0277(99)00059-1}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-johanssonLookHereEye2014}{}%
Johansson, R., \& Johansson, M. (2014). Look {Here}, {Eye Movements Play} a {Functional Role} in {Memory Retrieval}. \emph{Psychological Science}, \emph{25}(1), 236--242. \url{https://doi.org/10.1177/0956797613498260}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-ryskinVerbBiasesAre2017}{}%
Ryskin, R., Qi, Z., Duff, M. C., \& Brown-Schmidt, S. (2017). Verb biases are shaped through lifelong learning. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(5), 781--794. \url{https://doi.org/10.1037/xlm0000341}

\end{CSLReferences}

\endgroup

\end{document}

### 2021-06-30 manuscript.Rmd
minor

@@
 
-> here we will describe the analyses that correlate calibration quality with effect size at the individual (Josh H?)
+> here we will describe the analyses that correlate calibration quality with effect size at the individual
 
@@
 
+Participants for this study were recruiting using the website Prolific.
+Specifically, participants had to be older than 18 and fluent in English, but aside from that, there was no restriction on demographic; participation was also anonymous.
+The only technology-based restriction was that each participant had to have a working webcam; we were able to accommodate for different screen sizes during data analysis.
+We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
+We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
+
 ### Material
@@
 
+After a participant began the study, they would encounter an alert that the study would use their webcam to track eye movements, then initiate Webgazer, a program that logs predicted eye positions.
+There were two possible conditions they could begin with—the free-viewing condition and the fixed-viewing condition—which they were randomly assigned to.
+For both conditions, participants began with the encoding phase before moving to the recall phase.
+After going through both conditions, participants were asked a few survey questions and the experiment ended.
+For the encoding phase, participants were asked to remember the contents of the four quadrants of a grid, each with six distinct items themed around a certain category (we used humanoids, household objects, animals, and methods of transportation, as inspired by the example in Johansson & Johansson’s original experiment).
+To do so, each of the four quadrants was presented to the participant one at a time.
+First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown.
+For each item in a quadrant, an audio file would play, asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing a distinct direction to allow for statements like “The chair is facing left” to be viable).
+After the participant identified the direction of each item, they would have an additional 30 seconds to study and remember the name and orientation of each item in the quadrant.
+Then, after repeating this for each quadrant, the participant was shown the full grid of 24 items (six per grid) and had sixty seconds to further encode the name and orientation of each item.
+For the recall phase, participants had to respond to statements presented via audio files.
+Each statement was a true or false statement that fell into either an interobject or intraobject condition.
+Interobject statements were those that compared two different items in the grid (e.g.
+“The skeleton is to the left of the robot”), while intraobject statements were those that asked about the orientation of a single item (e.g.
+“The bus is facing right”).
+There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
+Participants were able to respond by pressing the ‘F’ key for false statements and ‘T’ for true ones.
+The difference between the free-viewing and fixed-viewing conditions was in what a participant could see on screen during the recall phase.
+During fixed-viewing, participants could only see a small cross in the center of the screen, and were asked at the start of the recall phase to focus their vision on just the cross.
+During free-viewing, participants saw an empty screen and were allowed to look wherever they wanted, without any particular instruction telling them where to look.
+In both cases, the mouse was obscured from the screen, making it so that the only visual stimulus for either condition was the cross in the fixed-viewing one.
+After a participant finished the first condition, they then moved on to repeating the experiment under the second condition, this time with a new grid of images.
+After completing this second condition, the participant was finished, and was asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
+The methodology of this replication differed from Johansson & Johansson’s original study in two key ways.
+First, the original study included two more conditions that were omitted from this replication for efficiency concerns.
+Those two conditions involved prompting the participant to look to an area on screen that matched one of the original quadrants while they responded to each statement, with the key here being that sometimes the prompt was in the same quadrant as the information being recalled, while sometimes it wasn’t.
+We ended up not replicating this aspect of the study because it felt like too big of a task to program and playtest in the amount of time we had.
+The second major way this study differed from the original was that the original was conducted in- person and used an iView Red500 eye tracker, which was able to track eye movements incredibly closely.
+Due to obvious pandemic-related reasons, we conducted our replication online through Prolific, while using Webgazer, a software that tracks eye movements based on a participant’s webcam.
+There were a few other minor ways in which our study differed (we used different grids of objects and different instructions), but we tried to remain as faithful as possible in terms of variables like timing, the physical appearance of the grids, and the style of the images.
+
 ### Data analysis
@@
 ## Results
+
+### Replication
+
+> here we will describe the analyses that are as close as possible to the original paper
+
+### Calibration
+
+> here we will describe the analyses that correlate calibration quality with effect size at the individual
 
@@
 
-The third study was a replication attempt of @Mann???.
+The third study was a replication attempt of @mannsVisualPairedcomparisonTask2000.
 
@@
 ## Results
+
+### Replication
+
+> here we will describe the analyses that are as close as possible to the original paper
+
+### Calibration
+
+> here we will describe the analyses that correlate calibration quality with effect size at the individual
+
+### Effects of ROIs
+
+> here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
 

### 2021-06-30 manuscript.tex
minor

@@
 \begin{quote}
-here we will describe the analyses that correlate calibration quality with effect size at the individual (Josh H?)
+here we will describe the analyses that correlate calibration quality with effect size at the individual
 \end{quote}
@@
 
+Participants for this study were recruiting using the website Prolific.
+Specifically, participants had to be older than 18 and fluent in English, but aside from that, there was no restriction on demographic; participation was also anonymous.
+The only technology-based restriction was that each participant had to have a working webcam; we were able to accommodate for different screen sizes during data analysis.
+We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
+We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
+
 \hypertarget{material}{%
@@
 \subsubsection{Procedure}\label{procedure-1}}
+
+After a participant began the study, they would encounter an alert that the study would use their webcam to track eye movements, then initiate Webgazer, a program that logs predicted eye positions.
+There were two possible conditions they could begin with---the free-viewing condition and the fixed-viewing condition---which they were randomly assigned to.
+For both conditions, participants began with the encoding phase before moving to the recall phase.
+After going through both conditions, participants were asked a few survey questions and the experiment ended.
+For the encoding phase, participants were asked to remember the contents of the four quadrants of a grid, each with six distinct items themed around a certain category (we used humanoids, household objects, animals, and methods of transportation, as inspired by the example in Johansson \& Johansson's original experiment).
+To do so, each of the four quadrants was presented to the participant one at a time.
+First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown.
+For each item in a quadrant, an audio file would play, asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing a distinct direction to allow for statements like ``The chair is facing left'' to be viable).
+After the participant identified the direction of each item, they would have an additional 30 seconds to study and remember the name and orientation of each item in the quadrant.
+Then, after repeating this for each quadrant, the participant was shown the full grid of 24 items (six per grid) and had sixty seconds to further encode the name and orientation of each item.
+For the recall phase, participants had to respond to statements presented via audio files.
+Each statement was a true or false statement that fell into either an interobject or intraobject condition.
+Interobject statements were those that compared two different items in the grid (e.g.~``The skeleton is to the left of the robot''), while intraobject statements were those that asked about the orientation of a single item (e.g.~``The bus is facing right'').
+There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
+Participants were able to respond by pressing the `F' key for false statements and `T' for true ones.
+The difference between the free-viewing and fixed-viewing conditions was in what a participant could see on screen during the recall phase.
+During fixed-viewing, participants could only see a small cross in the center of the screen, and were asked at the start of the recall phase to focus their vision on just the cross.
+During free-viewing, participants saw an empty screen and were allowed to look wherever they wanted, without any particular instruction telling them where to look.
+In both cases, the mouse was obscured from the screen, making it so that the only visual stimulus for either condition was the cross in the fixed-viewing one.
+After a participant finished the first condition, they then moved on to repeating the experiment under the second condition, this time with a new grid of images.
+After completing this second condition, the participant was finished, and was asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
+The methodology of this replication differed from Johansson \& Johansson's original study in two key ways.
+First, the original study included two more conditions that were omitted from this replication for efficiency concerns.
+Those two conditions involved prompting the participant to look to an area on screen that matched one of the original quadrants while they responded to each statement, with the key here being that sometimes the prompt was in the same quadrant as the information being recalled, while sometimes it wasn't.
+We ended up not replicating this aspect of the study because it felt like too big of a task to program and playtest in the amount of time we had.
+The second major way this study differed from the original was that the original was conducted in- person and used an iView Red500 eye tracker, which was able to track eye movements incredibly closely.
+Due to obvious pandemic-related reasons, we conducted our replication online through Prolific, while using Webgazer, a software that tracks eye movements based on a participant's webcam.
+There were a few other minor ways in which our study differed (we used different grids of objects and different instructions), but we tried to remain as faithful as possible in terms of variables like timing, the physical appearance of the grids, and the style of the images.
 
@@
 
+\hypertarget{replication-1}{%
+\subsubsection{Replication}\label{replication-1}}
+
+\begin{quote}
+here we will describe the analyses that are as close as possible to the original paper
+\end{quote}
+
+\hypertarget{calibration-1}{%
+\subsubsection{Calibration}\label{calibration-1}}
+
+\begin{quote}
+here we will describe the analyses that correlate calibration quality with effect size at the individual
+\end{quote}
+
 \hypertarget{discussion-1}{%
@@
 
-The third study was a replication attempt of (\textbf{Mann?})???.
+The third study was a replication attempt of Manns, Stark, and Squire (2000).
 
@@
 \subsection{Results}\label{results-3}}
+
+\hypertarget{replication-2}{%
+\subsubsection{Replication}\label{replication-2}}
+
+\begin{quote}
+here we will describe the analyses that are as close as possible to the original paper
+\end{quote}
+
+\hypertarget{calibration-2}{%
+\subsubsection{Calibration}\label{calibration-2}}
+
+\begin{quote}
+here we will describe the analyses that correlate calibration quality with effect size at the individual
+\end{quote}
+
+\hypertarget{effects-of-rois}{%
+\subsubsection{Effects of ROIs}\label{effects-of-rois}}
+
+\begin{quote}
+here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
+\end{quote}
 
@@
 
+\leavevmode\hypertarget{ref-mannsVisualPairedcomparisonTask2000}{}%
+Manns, J.
+R., Stark, C.
+E.
+L., \& Squire, L.
+R.
+(2000).
+The visual paired-comparison task as a measure of declarative memory.
+\emph{Proceedings of the National Academy of Sciences}, \emph{97}(22), 12375--12379.
+\url{https://doi.org/10.1073/pnas.220398097}
+
 \leavevmode\hypertarget{ref-R-base}{}%

### 2021-07-01 manuscript.Rmd
edited E1 methods

@@
 The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.
+Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
+For example, when looking at the display in Figure 1 and listening to a sentence like “The boy will eat the…,” participants are more likely to look at the cake than when they hear “The boy will move the…,” in which case they tend to look at the train, presumably because cakes are edible and trains are not.
+Semantic information available at the verb is used to anticipate upcoming linguistic input.
 
@@
 
+<!-- insert Figure 1 -->
+
 ### Participants
@@
 From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific, and we ended up with a sample size of 60 participants.
+Note that the sample size of the original study was 24.
 For unknown reasons, 2 of the subjects’ results were not recorded, so in the analysis, we worked with data collected from 58 participants.
@@
 Participants completed the experiment remotely and entirely online on the platform Prolific.
-During the experiment, the participants viewed a screen and were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
-The visual stimuli were created through Canva and depict a subject accompanied by 4 to 5 objects in the scene.
-16 of the devised stimuli were critical to our trial, and each of these images have 2 sentences associated with it.
-One of these sentences is in the restrictive condition, where the verb only applies to one object in the scene, and the other is in the nonrestrictive condition, where the verb could apply to all of the objects in the scene.
-To illustrate an example, reference Figure 1.
-This scene depicts a boy alongside a cake, ball, car, and train set.
-In the case of this particular image, the cake is the target object, so the two corresponding sentences to this image are, “The boy will eat the cake” (restrictive) and “The boy will move the cake” (nonrestrictive).
 
-### Materials
+#### Eye-Tracking Calibration and Validation
 
-Therefore, for the 16 critical images, there are 16 control sentences where the verb does not constrain the target object and 16 restrictive sentences where the verb does constrain the target object.
-Each participant randomly received one sentence, restrictive or nonrestrictive, per scene.
-Of the 16 critical trials, each participant got 8 sentences that were restrictive and 8 that were nonrestrictive and the order of these were randomized.
-Trials were also designed so that participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence relayed was feasible given the visual image.
+Before initiating the experiment, participants were prompted to complete an eye-tracking calibration and validation procedure.
+Participants were first presented with a series of dots that appeared on the screen.
+They were instructed to look at each dot as it appeared and click on it.
+Once they visually fixated and clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
+The calibration dots appeared in the central area of the screen where the visual stimuli would appear in order to ensure Web Gazer would be able to track eye movements to the relevant regions of interest.
+After the calibration was completed, the validation began.
+Participants were asked to go through the same steps as the calibration, except this time, they only fixated the dots as they appeared in different locations on the screen.
+
+<!-- Qs:
+-what was the threshold for letting people start the experiment? 
+- were they given the option to start over? -->
+
+#### Experiment Procedure
+
+During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
+Participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence they heard was feasible given the visual image.
 There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
-In addition to the 16 critical images, we also devised an additional 16 filler images that are not pertinent to our data collection and analysis.
-The critical trials were also presented in a randomized order along with these 16 filler trials.
-Unlike the critical images, the filler images were accompanied by only one sentence that is unfeasible given it’s corresponding scene.
-This was so that when participants were asked whether or not the scene was possible, the filler trials would always elicit the answer, “no.”
-Despite recording participants’ reaction time and keyboard response after each trial, we were specifically measuring for the participant’s first fixation to the target object and distractors relative to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
+Participants’ reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.
 
-### Eye-Tracking Calibration and Validation
-Before initiating the experiment, participants were prompted to complete an eye-tracking calibration and validation procedure to ensure the data collected via the webcam-based eye tracking method was as accurate as possible.
-In order to allow the software to track where participants are looking, subjects were presented with a series of dots that appeared on the screen.
-Participants were then instructed to look at each dot as they appeared and click on it.
-By visually fixating and then clicking on one dot, it would then disappear and a new one would reappear in a different location on the screen.
-The calibration dots appeared in the central area of the screen where the visual stimuli would appear in order to ensure Web Gazer would be able to track eye movements to the relevant regions of interest.
-After completing this calibration, participants were then asked to go through the same steps of the calibration, except this time, they would have to just look at, not click, the dots as they appear on the screen in order to measure the accuracy of the calibration.
-This process completes the Web Gazer calibration and validation process.
+<!-- Qs: 
+-keyboard keys? what was the exact phrasing of the instruction? 
+-Any delay between when visual scene appears and the audio starts? 
+-Does trial end as soon as participant responds?-->
+
+### Materials & Design
+
+The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure 1).
+On critical trials, participants heard one of two sentences associated with the scene.
+In the restrictive condition, the sentence (e.g., "The boy will eat the cake") contained a verb (e.g., "eat") which restricts the set of possible subsequent referents (e.g., to edible things).
+Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
+In the non-restrictive condition, the sentence (e.g., "The boy will move the cake") contained a verb (e.g., "move") which does not restrict the set of possible subsequent referents.
+The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
+Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was "yes." Filler trials consisted of scenes that looked similar to critical scenes but were paired with inappropriate sentences.
+The correct keyboard response for the filler trials was "no."
+
+Each participant was presented with sixteen critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and sixteen fillers for a total of 32 trials.
+The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.<!-- right?-->
 
@@
 We used `r cite_r("references.bib")` for all our analyses.
+
+looks to the objects in the scene time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
 
@@
 > here we will describe the analyses that are as close as possible to the original paper
+
+### Comparison to in-lab data
+
+> here we will describe a direct comparison to data collected in the lab
 
@@
 
-### Material
+The participants were volunteers recruited from Prolific who were over 18 years of age and fluent in English.
+Our initial sample size was 51 participants for the first day of our experiment and 48 of them came back for the second day.
+We excluded 3 participants due to perfect performance on the recognition memory test, which Manns et
+al. (2000) did as well. Our final sample size was 45 participants.
 
 ### Procedure
+
+The experiment was administered over the course of two consecutive days.
+It consisted of three sections: a presentation phase, a test phase, and a recognition test.
+The first two phases occurred on the first day, while the recognition test occurred on the second day.
+There were two modifications we made to the methods of the original experiment.
+As we are only replicating the declarative memory component of the original experiment, we did not have a “priming group.” Therefore, we followed only the procedure for the “looking group.” Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.
+
+Eye-Tracking Calibration
+
+Before the presentation phase began, participants were instructed to complete a two-part eye-tracking test to calibrate their eye movements with the webcam camera.
+During the first part of the test, the calibration stage, black dots appeared on the screen one at a time and remained there until the participants clicked it.
+Each dot appeared at a different location on the screen.
+There were a total of 7 dots, each presented three times in random order for a total of 21 dots.
+Their locations were designed to focus calibration on the middle box of the screen and also the two sides of the screen.
+The second part, which was the validation stage, consisted of a similar design, except participants simply viewed each black dot, which remained on the screen for 2 seconds, instead of clicking on it.
+There were a total of 3 dots, each presented once.
+The entire two-stage procedure was then repeated a second time to ensure accurate calibration.
+
+Presentation Phase
+
+During the presentation phase, participants viewed through a computer screen 24 pairs of identical color photographs depicting common objects.
+Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
+The order of the photographs was randomized and therefore different for each participant.
+After completion of the presentation phase, participants were given a 5-minute pause to disengage from the screen.
+When the pause was over, they were prompted to complete the eye-tracking calibration again to re-calibrate their eye movements.
+Afterward, the test phase began.
+
+Testing Phase
+
+During this phase, participants again viewed 24 pairs of photographs with the same stimuli and interstimulus durations of 5 seconds.
+In each pair, one photograph was previously seen before in the presentation phase, while the other was completely new.
+The test phase had a counterbalanced design, where the pictures that were old or new were counterbalanced across the participants.
+For half of the participants in each counterbalanced group, the foil and old photographs were reversed.
+
+Recognition Test
+
+ After roughly 24 hours, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
+It consisted of 48 photographs, presented one at a time.
+Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
+Half of them had been viewed twice on the previous day and were deemed the “targets.” The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed “foils.” Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing ‘y’ for yes and ‘n’ for no.
+After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a “pure guess” to 5 as “very sure.” by clicking on the corresponding number on the screen.
+No feedback on their responses was given during the test.
+The experimental design is visually depicted in Figure 1.1
+
+### Materials
 
@@
 
+The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, https://osf.io/x3c49/ (https://osf.io/x3c49/).
+The pre-registration for the study can be found at https://osf.io/3v4pg (https://osf.io/3v4pg).
+ Code
+
 ### Participants
 
-### Material
+Our study collected participants from Prolific who were 18 and up. A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power.
 
 ### Procedure
+
+When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
+They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and have their face lit from the front.
+The webcam’s view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
+The experiment became full screen, and participants began the eye-tracking calibration and validation so the camera on the computer could accurately track the participant’s eye movements.
+For the calibration, dots appeared on the screen one at a time in different locations, and the participants had to click on each one.
+The location of the dots created a box (one dot in each corner) with one dot in the center.
+For the validation, the dots appeared in the same locations as the calibration, but participants simply looked at the dots to test the accuracy.
+After the eye tracking was set up, participants went through an audio test so they could adjust the audio on their computer to a comfortable level.
+Before beginning the actual experiment, they were given instructions that four objects will appear, an audio prompt will play, and they should do their best to use their mouse to act out the instructions.
+They then went through three practice trials which were followed by 54 critical trials and 24 filler trials that were randomly presented.
+For the trials, they were shown four objects (target animal, target instrument, distractor animal, distractor instrument) in each corner of the screen while they heard an audio prompt that contained instructions about the action they needed to act out (see Figure 1).
+Using their cursor, the participants could act out the instructions by clicking on objects and moving them or motioning over the objects.
+After the action was completed, the participants were instructed to press the space bar which led to a screen that said “Click Here” in the middle in order to remove bias in the eye and mouse movements from the previous trial.
+The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had entered at least one object.
+After completing all of the trials, the participants were explained the meaning of the experiment and sent back to Prolific.
+
+Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+
+### Stimuli/Materials
+
+In order to track the eye movements of the participants, the participants’ web cameras on their computers were used with the jsPsych 6.1.3 eye tracking software.
+The images and audios presented to the participants were the same stimuli used in the original study.
+The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
+Two lists of critical trials were made with different verb and instrument combinations (e.g., “rub” could be paired with “panda” and “crayon” in one list and “panda” and “violin” in the second list).
+Within each list, the same verb was presented twice but each time with a different target instrument and animal.
+The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
+The list of verbs used can be found in appendix A of the original study.
+
+### Other
+
+Our experiment differed from the original study in a few ways.
+Besides the use of webcameras instead of an advanced eye tracker, we also analyzed mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
+For example, the sentence “locate the camel with the straw” may not involve any clicking but rather only mousing over the camel.
+We used Javascript with jsPsych packages instead of MatLab’s Psychophysics Toolbox 3, and our experiment was conducted through Prolific instead of in a lab.
+Lastly, the original study recited the names of objects on the screen at the beginning of each trial, but we took this audio out of our experiment.
 
@@
 
-The fifth study was a replication attempt of @??.
+The fifth study was a replication attempt of @shimojoGazeBiasBoth2003.
 
@@
 ## Results
+
+### Replication
+
+### Calibration
+
+### ROIs
+
+### Item Numbers
 

### 2021-07-07 manuscript.Rmd
all methods + results for E4 rep

--- 2021-06-30 manuscript.Rmd
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 
-```{r setup, include = FALSE}
-library("papaja")
+```{r setup, include = FALSE, message=FALSE, warning=FALSE}
+library(papaja)
+library(jsonlite)
+library(dplyr)
+library(readr)
+library(tidyr)
+library(ggplot2)
+library(stringr)
+library(lmerTest)
+library(afex)
+library(forcats)
+library(broom.mixed)
 r_refs("references.bib")
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+```{r in-box-function}
+#Define a function for determining if `x,y` value falls in box.
+in.box <- function(x, y, left, right, top, bottom, padding){
+  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
+  return(is.in.the.box)
+}
 ```
@@
 
-In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the `jsPsych` platform and `webgazer.js` plug-in.
+In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
+The plug-in relies on the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer].
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
@@
 ...
+
+# General Methods
+
+## Participants
+
+Participants completed the experiment remotely and were recruited through the Prolific platform.
+In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
+All participants provided informed consent.
+The studies were approved by the Vassar College Institutional Review Board.
+
+## Eye-tracking Calibration and Validation
+<!--took paragraph below from group D's methods -->
+When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
+They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
+The webcam’s view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
+The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
+
+During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
+Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
+The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
+After the calibration was completed, the validation began.
+Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
+If accuracy on the validation was too low (fewer than 50% of looks landed within a 200 px radius of the validation points<!--check!-->), participants were given an opportunity to re-start the calibration and validation steps.
+If the second attempt also lead to low validation accuracy, participants were informed that they could not participate in the study.
+
+## Data pre-processing
+We used `r cite_r("references.bib")` for all our analyses.
 
@@
 The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.
+Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
+For example, when looking at the display in Figure XX and listening to a sentence like “The boy will eat the…,” participants are more likely to look at the cake than when they hear “The boy will move the…,” in which case they tend to look at the train, presumably because cakes are edible and trains are not.
+Semantic information available at the verb is used to anticipate upcoming linguistic input.
 
@@
 ## Methods
-
+<!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->
 All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at [https://osf.io/s82kz](https://osf.io/s82kz).
-All participants provided informed consent and this study was approved by the Vassar College Institutional Review Board.
 
@@
 
-Participants for this experiment were sampled from a wide pool of Prolific users who are fluent in English and were paid for their participation.
-Our sample size of participants was determined by the total run time of our experiment, ~10 minutes, and the allotted funding that was endowed to us by the Vassar College Cognitive Science Department.
-From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific, and we ended up with a sample size of 60 participants.
+60 participants were paid $XX for their participation.
+Our sample size of participants was determined by the total run time of our experiment, ~10 minutes, and the allotted funding from the Vassar College Cognitive Science Department.
+From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific.
+Note that the sample size of the original study was 24.
 For unknown reasons, 2 of the subjects’ results were not recorded, so in the analysis, we worked with data collected from 58 participants.
@@
 
-Participants completed the experiment remotely and entirely online on the platform Prolific.
-During the experiment, the participants viewed a screen and were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
-The visual stimuli were created through Canva and depict a subject accompanied by 4 to 5 objects in the scene.
-16 of the devised stimuli were critical to our trial, and each of these images have 2 sentences associated with it.
-One of these sentences is in the restrictive condition, where the verb only applies to one object in the scene, and the other is in the nonrestrictive condition, where the verb could apply to all of the objects in the scene.
-To illustrate an example, reference Figure 1.
-This scene depicts a boy alongside a cake, ball, car, and train set.
-In the case of this particular image, the cake is the target object, so the two corresponding sentences to this image are, “The boy will eat the cake” (restrictive) and “The boy will move the cake” (nonrestrictive).
+The task began with an <number of points>-point eye-tracker calibration and validation.
+During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
+Participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence they heard was feasible given the visual image.
+There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
+Participants’ reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.
 
-### Materials
+<!-- Qs: 
+-keyboard keys? what was the exact phrasing of the instruction? 
+-Any delay between when visual scene appears and the audio starts? 
+-Does trial end as soon as participant responds?-->
 
-Therefore, for the 16 critical images, there are 16 control sentences where the verb does not constrain the target object and 16 restrictive sentences where the verb does constrain the target object.
-Each participant randomly received one sentence, restrictive or nonrestrictive, per scene.
-Of the 16 critical trials, each participant got 8 sentences that were restrictive and 8 that were nonrestrictive and the order of these were randomized.
-Trials were also designed so that participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence relayed was feasible given the visual image.
-There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
-In addition to the 16 critical images, we also devised an additional 16 filler images that are not pertinent to our data collection and analysis.
-The critical trials were also presented in a randomized order along with these 16 filler trials.
-Unlike the critical images, the filler images were accompanied by only one sentence that is unfeasible given it’s corresponding scene.
-This was so that when participants were asked whether or not the scene was possible, the filler trials would always elicit the answer, “no.”
-Despite recording participants’ reaction time and keyboard response after each trial, we were specifically measuring for the participant’s first fixation to the target object and distractors relative to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
+### Materials & Design
 
-### Eye-Tracking Calibration and Validation
-Before initiating the experiment, participants were prompted to complete an eye-tracking calibration and validation procedure to ensure the data collected via the webcam-based eye tracking method was as accurate as possible.
-In order to allow the software to track where participants are looking, subjects were presented with a series of dots that appeared on the screen.
-Participants were then instructed to look at each dot as they appeared and click on it.
-By visually fixating and then clicking on one dot, it would then disappear and a new one would reappear in a different location on the screen.
-The calibration dots appeared in the central area of the screen where the visual stimuli would appear in order to ensure Web Gazer would be able to track eye movements to the relevant regions of interest.
-After completing this calibration, participants were then asked to go through the same steps of the calibration, except this time, they would have to just look at, not click, the dots as they appear on the screen in order to measure the accuracy of the calibration.
-This process completes the Web Gazer calibration and validation process.
+The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure XX).
+On critical trials, participants heard one of two sentences associated with the scene.
+In the restrictive condition, the sentence (e.g., "The boy will eat the cake") contained a verb (e.g., "eat") which restricts the set of possible subsequent referents (e.g., to edible things).
+Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
+In the non-restrictive condition, the sentence (e.g., "The boy will move the cake") contained a verb (e.g., "move") which does not restrict the set of possible subsequent referents.
+The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
+Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was "yes." Filler trials consisted of scenes that looked similar to critical scenes but were paired with inappropriate sentences.
+The correct keyboard response for the filler trials was "no."
+
+Each participant was presented with sixteen critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and sixteen fillers for a total of 32 trials.
+The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.<!-- right?-->
+
+*TO DO:* add figure
 
 ### Data pre-processing and analysis
-We used `r cite_r("references.bib")` for all our analyses.
+
+Looks to the objects in the scene were time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
 
@@
 
-> here we will describe the analyses that are as close as possible to the original paper
+* here we will describe the analyses that are as close as possible to the original paper with a minimal validation cutoff
+
+* same analysis but with stricter validation cutoff
+
+### Comparison to in-lab data
+
+* here we will describe a direct comparison to data collected in the lab
 
@@
 
-> here we will describe the analyses that correlate calibration quality with effect size at the individual (Josh H?)
+* here we will describe the analyses that correlate calibration quality with effect size at the individual level
 
@@
 The second study was a replication attempt of @johanssonLookHereEye2014.
+They examined how visuospatial information is integrated into memories for objects.
+They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding [see @spiveyOculomotorMechanismsActivated2001] and that this spatial reinstatement facilitates retrieval of the picture.
 
@@
 
-### Material
+60 participants were paid $XX for their participation <!--right?-->.
+We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
+We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
 
 ### Procedure
+
+The task began with an <number of points>-point eye-tracker calibration and validation.
+The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
+During the encoding phase, participants saw a grid indicating the four quadrants of the screen.
+Each quadrant contained six images of items belonging to the same category (see Figure XX).
+The four possible categories were humanoids, household objects, animals, and methods of transportation.
+Participants were asked to remember the contents of the four quadrants.
+Different images were used in each block.
+
+Each of the four quadrants was presented one at a time.
+First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown (??).
+For each item, an audio file would play ("???") asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing either left or right (right??)).
+After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
+Then, after all four quadrants were presented in this way, the participant was shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
+
+During the recall phase, participants listened to statements and responded by pressing the ‘F’ key for false statements and ‘T’ for true ones.
+Each statement fell into either an interobject or intraobject condition.
+Interobject statements were those that compared two different items in the grid (e.g.
+“The skeleton is to the left of the robot”), while intraobject statements were those that asked about the orientation of a single item (e.g.
+“The bus is facing right”).
+There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
+While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
+During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
+In both cases, the mouse was obscured from the screen.
+Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
+
+ After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
+
+The primary methodological difference between this replication and Johansson and Johansson’s study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
+In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
 
@@
 ## Results
+
+### Replication
+
+* here we will describe the analyses that are as close as possible to the original paper
+
+* same but stricter validation cutoff
+
+### Calibration
+
+* here we will describe the analyses that correlate calibration quality with effect size at the individual level
 
@@
 
-The third study was a replication attempt of @Mann???.
+The third study was a replication attempt of @mannsVisualPairedcomparisonTask2000 which aimed to show that the visual paired-comparison task, widely used in the patient literature, tapped into declarative memory.
+In the visual paired-comparison task, two identical pictures were presented side by side for a brief viewing period.
+After a delay, one of the previously viewed pictures was presented along with a new picture.
+Individuals looked more at the new picture than the old picture and the time spent looking was correlated with later recognition memory performance.
+On the other hand perceptual priming, thought to recruit non-declarative memory, was not linked to later recognition.
+(The perceptual priming arm of the design was not included in this replication.)
 
@@
 
-### Material
+ Our initial sample size was 51 participants for the first day of our experiment and 48 of them came back for the second day.
+Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test.
+Our final sample size was 45 participants.
 
 ### Procedure
+
+The task began with a 7-point eye-tracker calibration (each point was presented 3 times in a random order) and validation with 3 points (each presented once).
+The point locations were designed to focus calibration on the center of the screen and the middle of the left and right halves of the screen.
+The experiment was administered over the course of two consecutive days.
+It consisted of three sections: a presentation phase, a test phase, and a recognition test.
+The first two phases occurred on the first day, while the recognition test occurred on the second day.
+
+During the presentation phase, participants viewed 24 pairs of identical color photographs depicting common objects.
+Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
+The order of the photographs was randomized and different for each participant.
+After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
+
+After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
+During this phase, participants again viewed 24 pairs of photographs with an interstimulus duration of 5 seconds.
+In each pair, one photograph was previously seen during the presentation phase, while the other was new.
+Which pictures were old or new was counterbalanced across participants.<!-- 2 lists?--> For half of the participants in each counterbalancing group, the new and old photographs were reversed.<!-- not sure what that last sentence means: is it about the side of the screen?
+or still just describing that there were 2 lists-->
+
+ Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
+It consisted of 48 photographs, presented one at a time.
+Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
+Half of the pohotographs had been viewed twice on the previous day and were deemed the “targets.” The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed “foils.” Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing ‘y’ for yes and ‘n’ for no.
+After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a “pure guess” to 5 as “very sure.” by clicking on the corresponding number on the screen.
+No feedback on their responses was given during the test.
+
+The experimental design is visually depicted in Figure XX
+
+### Materials
+
+Images were selected XXX...
+
+There were two modifications we made to the methods of the original experiment.
+As we are only replicating the declarative memory component of the original experiment, we did not have a “priming group.” Therefore, we followed only the procedure for the “looking group.” Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.
 
@@
 
-The fourth study was a replication attempt of @ryskinVerbBiasesAre2017.
+The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a.
+These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
+For example, in a sentence like “Feel the frog with the feather,” the phrase “with the feather” could be describing the frog, or it could be describing the instrument that should be used to do the “feeling.” When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb’s “bias” (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
+.
 
@@
 
+The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, https://osf.io/x3c49/ (https://osf.io/x3c49/).
+The pre-registration for the study can be found at https://osf.io/3v4pg (https://osf.io/3v4pg).
+
 ### Participants
 
-### Material
+58 (??) participants were paid $XX for their participation <!--right?-->.
+A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power.
+Note that the original study had a sample size of 24.
 
@@
 
-### Data analysis
+- *TO DO:* add details of calibration point locations
+
+After the eye-tracking calibration, participants went through an audio test so they could adjust the audio on their computer to a comfortable level.
+Before beginning the experiment, they were given instructions that four objects would appear, an audio prompt would play, and they should do their best to use their mouse to act out the instructions.
+They then went through three practice trials which were followed by 54 critical trials and 24 filler trials presented in a random order.
+
+During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure XX)^[In the original study, the pictures appeared one by one on the screen and their names were played as they appeared.
+We removed this introductory portion of the trial to save time].
+Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects^[ As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
+For example, the sentence “locate the camel with the straw” may not involve any clicking but rather only mousing over the camel.].
+After the action was completed, the participants were instructed to press the space bar which led to a screen that said “Click Here” in the middle in order to remove bias in the eye and mouse movements from the previous trial.
+The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
+
+*TO DO*: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+
+### Materials
+
+The images and audios presented to the participants were the same stimuli used in the original study (available here <link>).
+The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
+Two lists of critical trials were made with different verb and instrument combinations (e.g., “rub” could be paired with “panda” and “crayon” in one list and “panda” and “violin” in the second list).
+Within each list, the same verb was presented twice but each time with a different target instrument and animal.
+The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
+The list of verbs used can be found in Appendix A of the original study.
 
 ## Results
+
+```{r E4-load-data}
+data.files <- list.files('group-d/data/run-2', full.names = TRUE)
+data.tables <- lapply(data.files, function(file){
+  data.table <- fromJSON(file)
+  return(data.table)
+})
+all.data <- bind_rows(data.tables)
+```
+
+### Replication
+
+```{r E4-filter-data-for-replication-analysis}
+task.data <- all.data %>%
+  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
+  dplyr::select(subject, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
+
+# Add a column that uniquely identifies the combination of images and audio shown on the screen
+trialID.data <- task.data %>%
+  group_by(audio, images) %>%
+  slice(1) %>%
+  select(audio, images) %>%
+  ungroup() %>%
+  mutate(trialID = 1:n())
+
+task.data <- task.data %>%
+  left_join(trialID.data)
+
+eyetracking.data <- task.data %>%
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
+  unnest(webgazer_data)
+
+mousetracking.data <- task.data %>%
+  unnest(mouse_events)
+```
+
+The location of initial mouse movements was used to assess whether the final interpretation of ambiguous sentences was biased by the verb.
+Figure \@ref(fig:E4-mouse-moves-fig) suggests that listeners were more likely to move their mouse first over the target instrument when the verb was equi-biased than when the verb was modifier-biased and even more so when the verb was instrument-biased.
+The opposite graded pattern can be observed for mouse movements over the target animal.
+
+```{r E4-categorizing-first-mouse-moves}
+#First, create a data set with each trial, adding column for which object the mouse moves over first.
+# WTF IS HAPPENING with TRIAL ID?? 
+first.move <- mousetracking.data %>%
+  select(subject, trialID, object, type, compatibility, target_instrument, target_animal, images) %>%
+  group_by(subject, trialID) %>%
+  filter(type=="enter") %>%
+  slice(1) %>%
+  rowwise() %>%
+  mutate(which_loc = which(images == object)-1) %>%
+  ungroup() %>%
+  mutate(instrument_loc = str_sub(target_instrument, start=-1, end=-1)) %>%
+  mutate(animal_loc = str_sub(target_animal, start=-1, end=-1)) %>%
+  mutate(first.move.type = case_when(
+    which_loc == instrument_loc ~ 'instrument',
+    which_loc == animal_loc ~ 'animal',
+    TRUE ~ 'other')) %>%
+  mutate(is.mouse.instrument = if_else(first.move.type == 'instrument', 1, 0)) %>%
+  mutate(compatibility = factor(compatibility))
+```
+
+```{r E4-summarizing-first-mouse-moves-for-plotting}
+# Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.
+first.move.subject.summary <- first.move %>%
+  group_by(subject, compatibility) %>%
+  summarize(prop.animal = mean(first.move.type == 'animal'),
+            prop.instrument = mean(first.move.type == 'instrument'),
+            prop.other = mean(first.move.type == 'other')) %>%
+  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
+
+# Summarize the condition-level data for a barplot.
+first.move.summary <- first.move.subject.summary %>%
+  group_by(compatibility, target_type) %>%
+  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
+  mutate(bias = factor(compatibility, levels = c("instrument", "equibiased", "modifier") ))
+```
+
+```{r E4-mouse-moves-fig, fig.cap = "Proportion of first mouse movements by location and verb bias."}
+
+ggplot(first.move.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
+  geom_col(position=position_dodge(width=0.9), color = "black")+
+  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
+  theme_classic()+
+  labs(y = "Proportion of first mouse movements")
+```
+
+```{r E4-mouse-moves-analysis}
+contrasts(first.move$compatibility) <- cbind(c(1/3, -2/3, 1/3), c(-1/2, 0, 1/2))
+
+E4_mouse_moves_model <- glmer(is.mouse.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=first.move, family="binomial",
+                              glmerControl(optimizer = "bobyqa"))
+
+```
+
+```{r E4-mouse-moves-analysis-table}
+E4_mouse_moves_model_tab = broom.mixed::tidy(E4_mouse_moves_model) 
+E4_mouse_moves_model_c1 = E4_mouse_moves_model_tab %>% filter(term == "compatibility1")
+E4_mouse_moves_model_c2 = E4_mouse_moves_model_tab %>% filter(term == "compatibility2")
+```
+
+A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.
+equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
+modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
+Participants and items were entered as varying intercepts with by-participant varying slopes for verb bias condition^[`lme4` syntax: `glmer(is.mouse.over.instrument ~ verb_bias + (1 + verb_bias | participant) + (1 | item), family="binomial", data=d)`].
+Participants were more likely to first move their mouse over target instruments in the instrument-biased condition relative to the equi-biased and modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01).
+Further, participants were more likely to first move their mouse over target instruments in the equi-biased condition relative to the modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01)
+
+Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
+Figure \@ref(fig:E4-gaze-timecourse-fig) suggests that the participants made more fixations to the target animal when the verb was modifier-biased...
+
+```{r E4-categorizing-gaze-location}
+#First figure out which object they are looking at.
+#Calculate gaze in ROIs.
+eyetracking.data.with.roi <- eyetracking.data %>%
+  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
+  mutate(in.roi.0 = in.box(x,y,`#jspsych-free-sort-draggable-0.left`, `#jspsych-free-sort-draggable-0.right`, `#jspsych-free-sort-draggable-0.top`, `#jspsych-free-sort-draggable-0.bottom`, 100)) %>%
+  mutate(in.roi.1 = in.box(x,y,`#jspsych-free-sort-draggable-1.left`, `#jspsych-free-sort-draggable-1.right`, `#jspsych-free-sort-draggable-1.top`, `#jspsych-free-sort-draggable-1.bottom`, 100)) %>%
+  mutate(in.roi.2 = in.box(x,y,`#jspsych-free-sort-draggable-2.left`, `#jspsych-free-sort-draggable-2.right`, `#jspsych-free-sort-draggable-2.top`, `#jspsych-free-sort-draggable-2.bottom`, 100)) %>%
+  mutate(in.roi.3 = in.box(x,y,`#jspsych-free-sort-draggable-3.left`, `#jspsych-free-sort-draggable-3.right`, `#jspsych-free-sort-draggable-3.top`, `#jspsych-free-sort-draggable-3.bottom`, 100)) %>%
+  mutate(in.roi.instrument = case_when(
+    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
+    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
+    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
+    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
+  )) %>%
+  mutate(in.roi.animal = case_when(
+    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
+    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
+    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
+    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
+  )) 
+```
+
+```{r E4-load-audio-timing-data, message=FALSE}
+# load audio data
+audio.info <- read_csv('group-d/info/audio_timing.csv')
+```
+
+```{r E4-average-onsets-of-critical-words}
+#Calculate average animal onset
+animal.onset <- audio.info %>% pull(onset_noun) %>% mean()
+instrument.onset <- audio.info %>% pull(onset_instrument) %>% mean()
+```
+
+```{r E4-timelocking-gaze-data}
+# Merge in audio timing information
+eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
+  mutate(sound = str_split(audio, pattern="/", simplify = T)[,4])
+
+eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
+  left_join(audio.info, by="sound")
+
+# Add time window information
+eyetracking.data.with.time.windows <- eyetracking.data.with.roi %>%
+  mutate(time.window = case_when(
+    t < onset_verb + 200 ~ "pre-verb-onset",
+    t <= onset_noun + 200 ~ "post-verb-onset-pre-animal-onset",
+    t <= onset_instrument + 200 ~ "post-animal-onset-pre-instrument-onset",
+    t <= onset_instrument + 1500 + 200 ~ "post-instrument-onset",
+    TRUE ~ "end"
+  ),
+  time.from.verb = t - onset_verb)
+```
+
+```{r E4-downsampling-gaze-data-for-plotting}
+#Add time window
+eyetracking.data.with.time.windows <- eyetracking.data.with.time.windows %>%
+  mutate(t.window = floor(time.from.verb/50)*50)
+```
+
+```{r E4-summarizing-gaze-data-for-plotting}
+#Summarize data for plotting
+eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
+  filter(between(t.window , -200, 4000)) %>%
+  group_by(subject, compatibility, t.window) %>%
+  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
+  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
+  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
+  group_by(compatibility, t.window, object_type) %>%
+  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
+```
+
+```{r E4-gaze-timecourse-fig, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
+vertical lines indicate average onsets of animal and instrument offset by 200ms."}
+
+ggplot(eyetracking.figure.2.data, aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, linetype=object_type))+
+  geom_ribbon(color=NA, alpha=0.3)+
+  geom_line(size=1)+
+  theme_classic() +
+  geom_vline(xintercept = animal.onset + 200) + 
+  geom_vline(xintercept = instrument.onset + 200)+
+  labs(y = "Proportion of fixations", x = "Time window relative to verb onset (ms)")
+```
+
+```{r E4-compute-proportion-gaze-data-by-trial}
+#Summarize fixations on target and instrument
+eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
+  group_by(subject, trialID, sound, compatibility, time.window) %>%
+  summarize(prop.fixations.animal = sum(in.roi.animal) / n(),
+            prop.fixations.instrument = sum(in.roi.instrument) / n()) %>%
+  mutate(compatibility = factor(compatibility))
+```
+
+```{r E4-set-contrasts-for-ET-analysis}
+# Add orthogonal contrasts to model
+contrasts(eyetracking.window.summary.by.trial$compatibility) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
+```
+
+```{r E4-ET-analysis-verb-to-animal-window}
+data.time.window.1 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-verb-onset-pre-animal-onset")
+
+model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.1,
+                            control = lmerControl(optimizer = "bobyqa",
+                                                  optCtrl = list(maxfun = 2e6)))
+
+```
+```{r E4-ET-analysis-animal-to-inst-window}
+data.time.window.2 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-animal-onset-pre-instrument-onset")
+
+model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)
+```
+
+```{r E4-ET-analysis-post-inst-window}
+data.time.window.3 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-instrument-onset")
+
+model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 | subject) + (1 | trialID), data=data.time.window.3)
+```
+```{r E4-ET-analysis-tables}
+E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
+E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
+E4_ET_model3_tab = broom.mixed::tidy(model.time.window.3)
+
+E4_ET_model1_c1 = E4_ET_model1_tab %>% filter(term == "compatibility1")
+E4_ET_model1_c2 = E4_ET_model1_tab %>% filter(term == "compatibility2")
+
+E4_ET_model2_c1 = E4_ET_model2_tab %>% filter(term == "compatibility1")
+E4_ET_model2_c2 = E4_ET_model2_tab %>% filter(term == "compatibility2")
+
+E4_ET_model3_c1 = E4_ET_model3_tab %>% filter(term == "compatibility1")
+E4_ET_model3_c2 = E4_ET_model3_tab %>% filter(term == "compatibility2")
+```
+
+In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
+Mixed-effects linear regression models were used to predict the proportions of fixations to the target animal within each time window with the verb bias condition as an orthogonally contrast-coded (instrument vs.
+equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
+modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
+Participants and items were entered as varying intercepts^[`lme4` syntax: `lmer(prop.fix.target.animal ~ verb_bias + (1 + verb_bias | participant) + (1 | item), data=d)`.
+A model with by-participant varying slopes for verb bias condition was first attempted but did not converge.].
+In the _verb-to-noun_ window, participants did not look more at the target animal in any of the verb bias conditions (Instrument vs.
+Equi and Modifier: _b_ =  `r E4_ET_model1_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model1_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`; Equi vs.
+Modifier: _b_ =  `r E4_ET_model1_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model1_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c2 %>% pull(p.value) %>% round(digits = 2)` ).
+In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
+In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`).
+
+### Comparison to in-lab data
+
+* here we will describe a direct comparison to data collected in the lab
+
+### Calibration
+
+* here we will describe the analyses that correlate calibration quality with effect size at the level of the individual
+
+### Effects of ROIs
+
+* here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
 
@@
 
-The fifth study was a replication attempt of @??.
+The fifth study was a replication attempt of @shimojoGazeBiasBoth2003, which found that human gaze is actively involved in preference formation.
+Participants were shown pairs of human faces and were asked to choose the face which they found more attractive.
+Prior to making their explicit selection, participants spent more time looking at the face that was ultimately judged more attractive.
+This bias was not as large when the task was face shape discrimination rather than a preference-based choice.
 
@@
 
+All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at https://osf.io/eubsc/ (https://osf.io/eubsc/).
+The study pre-registration is available at https://osf.io/tv57s (https://osf.io/tv57s).
+
 ### Participants
 
-### Material
+27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They were paid $XX for completing the experiment.
+Data from 3 participants was excluded because their mode response made up more than 50% of their total responses <!-- is this a cutoff from Shimojo?-->, for a total of 24 participants in the norming.
 
-### Procedure
+50 participants for the main task were recruited on Prolific and were paid $XX.
+8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
+<!-- they were able to proceed despite bad validation?--> After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.The original sample size in Shimojo et al.
+(2003) was 10 participants total.
+
+### Procedure and Design
+
+At the beginning of the experimental task, participants completed a 9-point eye-tracker calibration (each point appeared 3 times in random order) and 3-point validation.
+The validation point appeared once at center, middle left, and middle right locations in random order.
+<!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total?
+If the latter, why is the coverage denser than for Experiment 4?
+-->
+
+During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure XX).
+Participants were randomly assigned to one of two tasks: attractiveness or shape judgment.
+In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
+They pressed the "a" key on their keyboard to select the face on the left and the “d” key to select the face on the right.
+A fixation cross appeared in the center of the screen between each set of faces.
+Participants were asked to look at this fixation cross in order to reset their gaze in between trials (???).
+The order of the 19 face pairs was random for each participant.
+
+### Materials and Norming
+
+The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset.
+(The face images used in Shimojo et al.
+were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
+Participants in the norming study viewed 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+Faces were presented one at a time and in a random order for each participant.
+Following Shimojo et al., 19 face pairs were made by matching two faces that had a difference in mean attractiveness ratings that was 0.25 points or lower and that matched in gender, race, and age group (young adult, adult, or older adult).
 
 ### Data analysis
+
+In the original study, a video-based eye tracker was used.
+The eye movements of participants were recorded with a digital camera, and eye position was then tracked using MediaAnalyzer software.
+This eye tracker was able to collect 30 samples per second.
+In our study, the camera on the device used by the participant and the jsPsych WebGazer package were used to determine where a participant’s gaze was directed.
+Since our eye tracking method did not have the same sample collection rate as the eye tracker in Shimojo et al., time windows of 50 milliseconds were used when looking at the likelihood of gazing at the chosen face at a given point between a cutoff time and when the decision was made.
 
@@
 
-The sixth study was a replication attempt of @??.
+The sixth study was a replication attempt of Posner et al. ??.
 
@@
 
-### Material
-
-### Procedure
+### Procedure and Design
 
@@
 
+### Replication
+
+### Calibration
+
+### ROIs
+
+### Item Numbers
+
 ## Discussion
@@
 # Combined Analyses
+
+- Pooling data from all experiments we can look at patterns in the calibration and validation data
 

### 2021-07-07 group-d/E4-analysis-replication.Rmd
moved E4 analysis to child Rmd in group-d folder

--- 2021-07-07 manuscript.Rmd
@@
 ---
-title             : "Eye-tracking on the web: lessons learned from replicating 6 experiments"
-shorttitle        : "Just picked a random title: feel free to change"
-
-author: 
-  - name          : "First Author"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - Writing - Review & Editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
-  - id            : "2"
-    institution   : "Konstanz Business School"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  ADD LATER
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["references.bib"]
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
+title: "E4-analysis-replication"
+author: "Rachel Ryskin"
+date: "7/7/2021"
+output: pdf_document
 ---
 
-```{r setup, include = FALSE, message=FALSE, warning=FALSE}
+```{r , include=FALSE}
 library(papaja)
@@
 library(broom.mixed)
-r_refs("references.bib")
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
 ```
@@
 
-<!-- MAJOR TO DOs: 
- - get data from in-lab versions of group A (AJ) and group D (RR)
- - re-run Posner cueing (after we finish analysing the first 5)
- - replicate group D and ?? in lab
-
- (see bottom for notes from e-mails)
- -->
-
-Intro stuff:
-
-- Eye-tracking as a key method in cognitive science research
-
-- Online data collection is more and more popular & let's us ask new questions
-
-- But, concerns over quality + little known about eye-tracking online
-
-_Present work_
-
-In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
-The plug-in relies on the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer].
-The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes).
-...
-
-# General Methods
-
-## Participants
-
-Participants completed the experiment remotely and were recruited through the Prolific platform.
-In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
-All participants provided informed consent.
-The studies were approved by the Vassar College Institutional Review Board.
-
-## Eye-tracking Calibration and Validation
-<!--took paragraph below from group D's methods -->
-When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
-They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
-The webcam’s view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
-The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
-
-During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
-Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
-The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
-After the calibration was completed, the validation began.
-Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
-If accuracy on the validation was too low (fewer than 50% of looks landed within a 200 px radius of the validation points<!--check!-->), participants were given an opportunity to re-start the calibration and validation steps.
-If the second attempt also lead to low validation accuracy, participants were informed that they could not participate in the study.
-
-## Data pre-processing
-We used `r cite_r("references.bib")` for all our analyses.
-
-# Experiment 1
-<!-- group a -->
-
-The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.
-Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
-For example, when looking at the display in Figure XX and listening to a sentence like “The boy will eat the…,” participants are more likely to look at the cake than when they hear “The boy will move the…,” in which case they tend to look at the train, presumably because cakes are edible and trains are not.
-Semantic information available at the verb is used to anticipate upcoming linguistic input.
-
-```{r read_groupA_data}
-
-```
-
-## Methods
-<!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->
-All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at [https://osf.io/s82kz](https://osf.io/s82kz).
-
-### Participants
-
-60 participants were paid $XX for their participation.
-Our sample size of participants was determined by the total run time of our experiment, ~10 minutes, and the allotted funding from the Vassar College Cognitive Science Department.
-From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific.
-Note that the sample size of the original study was 24.
-For unknown reasons, 2 of the subjects’ results were not recorded, so in the analysis, we worked with data collected from 58 participants.
-
-### Procedure
-
-The task began with an <number of points>-point eye-tracker calibration and validation.
-During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
-Participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence they heard was feasible given the visual image.
-There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
-Participants’ reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.
-
-<!-- Qs: 
--keyboard keys? what was the exact phrasing of the instruction? 
--Any delay between when visual scene appears and the audio starts? 
--Does trial end as soon as participant responds?-->
-
-### Materials & Design
-
-The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure XX).
-On critical trials, participants heard one of two sentences associated with the scene.
-In the restrictive condition, the sentence (e.g., "The boy will eat the cake") contained a verb (e.g., "eat") which restricts the set of possible subsequent referents (e.g., to edible things).
-Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
-In the non-restrictive condition, the sentence (e.g., "The boy will move the cake") contained a verb (e.g., "move") which does not restrict the set of possible subsequent referents.
-The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
-Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was "yes." Filler trials consisted of scenes that looked similar to critical scenes but were paired with inappropriate sentences.
-The correct keyboard response for the filler trials was "no."
-
-Each participant was presented with sixteen critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and sixteen fillers for a total of 32 trials.
-The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.<!-- right?-->
-
-*TO DO:* add figure
-
-### Data pre-processing and analysis
-
-Looks to the objects in the scene were time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
-
-## Results
-
-### Replication
-
-* here we will describe the analyses that are as close as possible to the original paper with a minimal validation cutoff
-
-* same analysis but with stricter validation cutoff
-
-### Comparison to in-lab data
-
-* here we will describe a direct comparison to data collected in the lab
-
-### Calibration
-
-* here we will describe the analyses that correlate calibration quality with effect size at the individual level
-
-## Discussion
-
-# Experiment 2
-<!-- group b -->
-
-The second study was a replication attempt of @johanssonLookHereEye2014.
-They examined how visuospatial information is integrated into memories for objects.
-They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding [see @spiveyOculomotorMechanismsActivated2001] and that this spatial reinstatement facilitates retrieval of the picture.
-
-## Methods
-
-### Participants
-
-60 participants were paid $XX for their participation <!--right?-->.
-We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
-We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
-
-### Procedure
-
-The task began with an <number of points>-point eye-tracker calibration and validation.
-The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
-During the encoding phase, participants saw a grid indicating the four quadrants of the screen.
-Each quadrant contained six images of items belonging to the same category (see Figure XX).
-The four possible categories were humanoids, household objects, animals, and methods of transportation.
-Participants were asked to remember the contents of the four quadrants.
-Different images were used in each block.
-
-Each of the four quadrants was presented one at a time.
-First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown (??).
-For each item, an audio file would play ("???") asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing either left or right (right??)).
-After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
-Then, after all four quadrants were presented in this way, the participant was shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
-
-During the recall phase, participants listened to statements and responded by pressing the ‘F’ key for false statements and ‘T’ for true ones.
-Each statement fell into either an interobject or intraobject condition.
-Interobject statements were those that compared two different items in the grid (e.g.
-“The skeleton is to the left of the robot”), while intraobject statements were those that asked about the orientation of a single item (e.g.
-“The bus is facing right”).
-There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
-While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
-During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
-In both cases, the mouse was obscured from the screen.
-Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
-
- After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
-
-The primary methodological difference between this replication and Johansson and Johansson’s study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
-In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
-
-### Data analysis
-
-## Results
-
-### Replication
-
-* here we will describe the analyses that are as close as possible to the original paper
-
-* same but stricter validation cutoff
-
-### Calibration
-
-* here we will describe the analyses that correlate calibration quality with effect size at the individual level
-
-## Discussion
-
-# Experiment 3
-<!-- group c -->
-
-The third study was a replication attempt of @mannsVisualPairedcomparisonTask2000 which aimed to show that the visual paired-comparison task, widely used in the patient literature, tapped into declarative memory.
-In the visual paired-comparison task, two identical pictures were presented side by side for a brief viewing period.
-After a delay, one of the previously viewed pictures was presented along with a new picture.
-Individuals looked more at the new picture than the old picture and the time spent looking was correlated with later recognition memory performance.
-On the other hand perceptual priming, thought to recruit non-declarative memory, was not linked to later recognition.
-(The perceptual priming arm of the design was not included in this replication.)
-
-## Methods
-
-### Participants
-
- Our initial sample size was 51 participants for the first day of our experiment and 48 of them came back for the second day.
-Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test.
-Our final sample size was 45 participants.
-
-### Procedure
-
-The task began with a 7-point eye-tracker calibration (each point was presented 3 times in a random order) and validation with 3 points (each presented once).
-The point locations were designed to focus calibration on the center of the screen and the middle of the left and right halves of the screen.
-The experiment was administered over the course of two consecutive days.
-It consisted of three sections: a presentation phase, a test phase, and a recognition test.
-The first two phases occurred on the first day, while the recognition test occurred on the second day.
-
-During the presentation phase, participants viewed 24 pairs of identical color photographs depicting common objects.
-Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
-The order of the photographs was randomized and different for each participant.
-After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
-
-After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
-During this phase, participants again viewed 24 pairs of photographs with an interstimulus duration of 5 seconds.
-In each pair, one photograph was previously seen during the presentation phase, while the other was new.
-Which pictures were old or new was counterbalanced across participants.<!-- 2 lists?--> For half of the participants in each counterbalancing group, the new and old photographs were reversed.<!-- not sure what that last sentence means: is it about the side of the screen?
-or still just describing that there were 2 lists-->
-
- Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
-It consisted of 48 photographs, presented one at a time.
-Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
-Half of the pohotographs had been viewed twice on the previous day and were deemed the “targets.” The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed “foils.” Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing ‘y’ for yes and ‘n’ for no.
-After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a “pure guess” to 5 as “very sure.” by clicking on the corresponding number on the screen.
-No feedback on their responses was given during the test.
-
-The experimental design is visually depicted in Figure XX
-
-### Materials
-
-Images were selected XXX...
-
-There were two modifications we made to the methods of the original experiment.
-As we are only replicating the declarative memory component of the original experiment, we did not have a “priming group.” Therefore, we followed only the procedure for the “looking group.” Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.
-
-### Data analysis
-
-## Results
-
-## Discussion
-
-# Experiment 4
-<!-- group d -->
-
-The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a.
-These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
-For example, in a sentence like “Feel the frog with the feather,” the phrase “with the feather” could be describing the frog, or it could be describing the instrument that should be used to do the “feeling.” When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb’s “bias” (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
-.
-
-## Methods
-
-The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, https://osf.io/x3c49/ (https://osf.io/x3c49/).
-The pre-registration for the study can be found at https://osf.io/3v4pg (https://osf.io/3v4pg).
-
-### Participants
-
-58 (??) participants were paid $XX for their participation <!--right?-->.
-A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power.
-Note that the original study had a sample size of 24.
-
-### Procedure
-
-- *TO DO:* add details of calibration point locations
-
-After the eye-tracking calibration, participants went through an audio test so they could adjust the audio on their computer to a comfortable level.
-Before beginning the experiment, they were given instructions that four objects would appear, an audio prompt would play, and they should do their best to use their mouse to act out the instructions.
-They then went through three practice trials which were followed by 54 critical trials and 24 filler trials presented in a random order.
-
-During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure XX)^[In the original study, the pictures appeared one by one on the screen and their names were played as they appeared.
-We removed this introductory portion of the trial to save time].
-Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects^[ As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
-For example, the sentence “locate the camel with the straw” may not involve any clicking but rather only mousing over the camel.].
-After the action was completed, the participants were instructed to press the space bar which led to a screen that said “Click Here” in the middle in order to remove bias in the eye and mouse movements from the previous trial.
-The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
-
-*TO DO*: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
-
-### Materials
-
-The images and audios presented to the participants were the same stimuli used in the original study (available here <link>).
-The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
-Two lists of critical trials were made with different verb and instrument combinations (e.g., “rub” could be paired with “panda” and “crayon” in one list and “panda” and “violin” in the second list).
-Within each list, the same verb was presented twice but each time with a different target instrument and animal.
-The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
-The list of verbs used can be found in Appendix A of the original study.
-
-## Results
-
 ```{r E4-load-data}
-data.files <- list.files('group-d/data/run-2', full.names = TRUE)
+data.files <- list.files('data/run-2', full.names = TRUE)
 data.tables <- lapply(data.files, function(file){
@@
 # load audio data
-audio.info <- read_csv('group-d/info/audio_timing.csv')
+audio.info <- read_csv('info/audio_timing.csv')
 ```
@@
 In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`).
-
-### Comparison to in-lab data
-
-* here we will describe a direct comparison to data collected in the lab
-
-### Calibration
-
-* here we will describe the analyses that correlate calibration quality with effect size at the level of the individual
-
-### Effects of ROIs
-
-* here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
-
-## Discussion
-
-# Experiment 5
-<!-- group e -->
-
-The fifth study was a replication attempt of @shimojoGazeBiasBoth2003, which found that human gaze is actively involved in preference formation.
-Participants were shown pairs of human faces and were asked to choose the face which they found more attractive.
-Prior to making their explicit selection, participants spent more time looking at the face that was ultimately judged more attractive.
-This bias was not as large when the task was face shape discrimination rather than a preference-based choice.
-
-## Methods
-
-All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at https://osf.io/eubsc/ (https://osf.io/eubsc/).
-The study pre-registration is available at https://osf.io/tv57s (https://osf.io/tv57s).
-
-### Participants
-
-27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They were paid $XX for completing the experiment.
-Data from 3 participants was excluded because their mode response made up more than 50% of their total responses <!-- is this a cutoff from Shimojo?-->, for a total of 24 participants in the norming.
-
-50 participants for the main task were recruited on Prolific and were paid $XX.
-8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
-<!-- they were able to proceed despite bad validation?--> After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.The original sample size in Shimojo et al.
-(2003) was 10 participants total.
-
-### Procedure and Design
-
-At the beginning of the experimental task, participants completed a 9-point eye-tracker calibration (each point appeared 3 times in random order) and 3-point validation.
-The validation point appeared once at center, middle left, and middle right locations in random order.
-<!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total?
-If the latter, why is the coverage denser than for Experiment 4?
--->
-
-During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure XX).
-Participants were randomly assigned to one of two tasks: attractiveness or shape judgment.
-In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
-They pressed the "a" key on their keyboard to select the face on the left and the “d” key to select the face on the right.
-A fixation cross appeared in the center of the screen between each set of faces.
-Participants were asked to look at this fixation cross in order to reset their gaze in between trials (???).
-The order of the 19 face pairs was random for each participant.
-
-### Materials and Norming
-
-The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset.
-(The face images used in Shimojo et al.
-were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
-Participants in the norming study viewed 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
-Faces were presented one at a time and in a random order for each participant.
-Following Shimojo et al., 19 face pairs were made by matching two faces that had a difference in mean attractiveness ratings that was 0.25 points or lower and that matched in gender, race, and age group (young adult, adult, or older adult).
-
-### Data analysis
-
-In the original study, a video-based eye tracker was used.
-The eye movements of participants were recorded with a digital camera, and eye position was then tracked using MediaAnalyzer software.
-This eye tracker was able to collect 30 samples per second.
-In our study, the camera on the device used by the participant and the jsPsych WebGazer package were used to determine where a participant’s gaze was directed.
-Since our eye tracking method did not have the same sample collection rate as the eye tracker in Shimojo et al., time windows of 50 milliseconds were used when looking at the likelihood of gazing at the chosen face at a given point between a cutoff time and when the decision was made.
-
-## Results
-
-## Discussion
-
-# Experiment 6
-<!-- posner cueing task -->
-
-The sixth study was a replication attempt of Posner et al. ??.
-
-## Methods
-
-### Participants
-
-### Procedure and Design
-
-### Data analysis
-
-## Results
-
-### Replication
-
-### Calibration
-
-### ROIs
-
-### Item Numbers
-
-## Discussion
-
-# Combined Analyses
-
-- Pooling data from all experiments we can look at patterns in the calibration and validation data
-
-# General Discussion
-
-<!-- NOTES FROM EMAILS:
-
-JOSH DE LEEUW: For calibration quality, there are a few ways you could go about it.
-
-As a preliminary step filtering the data to trial_type == 'webgazer-validate' should get you a data frame with just the validation trials.
-We ran a validation trial immediately after calibration.
-The trial involves showing some set of dots on the screen for a few seconds each and recording all of the samples from webgazer for each dot.
-Each experiment defined a different set of dots for validation, depending on where the relevant ROIs were.
-
-The data for each of these trials includes columns for:
-
-raw_gaze: all the raw data points recorded from webgazer, organized by which point was shown on the screen
-percent_in_roi:  The jsPsych plugin also calculates the percentage of samples for each dot that are within some specified radius.
-I think we used 150px for all of the experiments, but I can verify that.
-average_offset: The average x,y offset of the cloud of points measured for each validation point.
-Also includes a value r, which is the radius of the circle centered at the midpoint of the cloud that includes half the points.
-Basically a measure of variance.
-validation_points: coordinates of each of the points on the screen, in the same order as the other columns so that you could see, e.g., if calibration tends to be better on more central points.
-
-We also included a step where if the validation was poor after the first attempt we repeated the calibration and validation procedure one additional time.
-So some subjects have more validation trials than others.
-If you look at my R Notebook for group A (just pushed to GH now) you can see some initial attempts to extract validation info and use it to exclude subjects.
--->
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2021-07-07 manuscript.Rmd
moved E4 analysis to child Rmd in group-d folder

@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-```{r in-box-function}
-#Define a function for determining if `x,y` value falls in box.
-in.box <- function(x, y, left, right, top, bottom, padding){
-  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
-  return(is.in.the.box)
-}
 ```
@@
 
-```{r E4-load-data}
-data.files <- list.files('group-d/data/run-2', full.names = TRUE)
-data.tables <- lapply(data.files, function(file){
-  data.table <- fromJSON(file)
-  return(data.table)
-})
-all.data <- bind_rows(data.tables)
-```
-
-### Replication
-
-```{r E4-filter-data-for-replication-analysis}
-task.data <- all.data %>%
-  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
-  dplyr::select(subject, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
-
-# Add a column that uniquely identifies the combination of images and audio shown on the screen
-trialID.data <- task.data %>%
-  group_by(audio, images) %>%
-  slice(1) %>%
-  select(audio, images) %>%
-  ungroup() %>%
-  mutate(trialID = 1:n())
-
-task.data <- task.data %>%
-  left_join(trialID.data)
-
-eyetracking.data <- task.data %>%
-  tidyr::unpack(webgazer_targets) %>%
-  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
-  unnest(webgazer_data)
-
-mousetracking.data <- task.data %>%
-  unnest(mouse_events)
-```
-
-The location of initial mouse movements was used to assess whether the final interpretation of ambiguous sentences was biased by the verb.
-Figure \@ref(fig:E4-mouse-moves-fig) suggests that listeners were more likely to move their mouse first over the target instrument when the verb was equi-biased than when the verb was modifier-biased and even more so when the verb was instrument-biased.
-The opposite graded pattern can be observed for mouse movements over the target animal.
-
-```{r E4-categorizing-first-mouse-moves}
-#First, create a data set with each trial, adding column for which object the mouse moves over first.
-# WTF IS HAPPENING with TRIAL ID?? 
-first.move <- mousetracking.data %>%
-  select(subject, trialID, object, type, compatibility, target_instrument, target_animal, images) %>%
-  group_by(subject, trialID) %>%
-  filter(type=="enter") %>%
-  slice(1) %>%
-  rowwise() %>%
-  mutate(which_loc = which(images == object)-1) %>%
-  ungroup() %>%
-  mutate(instrument_loc = str_sub(target_instrument, start=-1, end=-1)) %>%
-  mutate(animal_loc = str_sub(target_animal, start=-1, end=-1)) %>%
-  mutate(first.move.type = case_when(
-    which_loc == instrument_loc ~ 'instrument',
-    which_loc == animal_loc ~ 'animal',
-    TRUE ~ 'other')) %>%
-  mutate(is.mouse.instrument = if_else(first.move.type == 'instrument', 1, 0)) %>%
-  mutate(compatibility = factor(compatibility))
-```
-
-```{r E4-summarizing-first-mouse-moves-for-plotting}
-# Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.
-first.move.subject.summary <- first.move %>%
-  group_by(subject, compatibility) %>%
-  summarize(prop.animal = mean(first.move.type == 'animal'),
-            prop.instrument = mean(first.move.type == 'instrument'),
-            prop.other = mean(first.move.type == 'other')) %>%
-  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
-
-# Summarize the condition-level data for a barplot.
-first.move.summary <- first.move.subject.summary %>%
-  group_by(compatibility, target_type) %>%
-  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
-  mutate(bias = factor(compatibility, levels = c("instrument", "equibiased", "modifier") ))
-```
-
-```{r E4-mouse-moves-fig, fig.cap = "Proportion of first mouse movements by location and verb bias."}
-
-ggplot(first.move.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
-  geom_col(position=position_dodge(width=0.9), color = "black")+
-  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
-  theme_classic()+
-  labs(y = "Proportion of first mouse movements")
-```
-
-```{r E4-mouse-moves-analysis}
-contrasts(first.move$compatibility) <- cbind(c(1/3, -2/3, 1/3), c(-1/2, 0, 1/2))
-
-E4_mouse_moves_model <- glmer(is.mouse.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=first.move, family="binomial",
-                              glmerControl(optimizer = "bobyqa"))
+```{r E4-analysis-replication, child='group-d/E4-analysis-replication.Rmd'}
 
 ```
-
-```{r E4-mouse-moves-analysis-table}
-E4_mouse_moves_model_tab = broom.mixed::tidy(E4_mouse_moves_model) 
-E4_mouse_moves_model_c1 = E4_mouse_moves_model_tab %>% filter(term == "compatibility1")
-E4_mouse_moves_model_c2 = E4_mouse_moves_model_tab %>% filter(term == "compatibility2")
-```
-
-A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.
-equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
-modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
-Participants and items were entered as varying intercepts with by-participant varying slopes for verb bias condition^[`lme4` syntax: `glmer(is.mouse.over.instrument ~ verb_bias + (1 + verb_bias | participant) + (1 | item), family="binomial", data=d)`].
-Participants were more likely to first move their mouse over target instruments in the instrument-biased condition relative to the equi-biased and modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01).
-Further, participants were more likely to first move their mouse over target instruments in the equi-biased condition relative to the modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01)
-
-Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
-Figure \@ref(fig:E4-gaze-timecourse-fig) suggests that the participants made more fixations to the target animal when the verb was modifier-biased...
-
-```{r E4-categorizing-gaze-location}
-#First figure out which object they are looking at.
-#Calculate gaze in ROIs.
-eyetracking.data.with.roi <- eyetracking.data %>%
-  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
-  mutate(in.roi.0 = in.box(x,y,`#jspsych-free-sort-draggable-0.left`, `#jspsych-free-sort-draggable-0.right`, `#jspsych-free-sort-draggable-0.top`, `#jspsych-free-sort-draggable-0.bottom`, 100)) %>%
-  mutate(in.roi.1 = in.box(x,y,`#jspsych-free-sort-draggable-1.left`, `#jspsych-free-sort-draggable-1.right`, `#jspsych-free-sort-draggable-1.top`, `#jspsych-free-sort-draggable-1.bottom`, 100)) %>%
-  mutate(in.roi.2 = in.box(x,y,`#jspsych-free-sort-draggable-2.left`, `#jspsych-free-sort-draggable-2.right`, `#jspsych-free-sort-draggable-2.top`, `#jspsych-free-sort-draggable-2.bottom`, 100)) %>%
-  mutate(in.roi.3 = in.box(x,y,`#jspsych-free-sort-draggable-3.left`, `#jspsych-free-sort-draggable-3.right`, `#jspsych-free-sort-draggable-3.top`, `#jspsych-free-sort-draggable-3.bottom`, 100)) %>%
-  mutate(in.roi.instrument = case_when(
-    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
-    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
-    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
-    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
-  )) %>%
-  mutate(in.roi.animal = case_when(
-    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
-    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
-    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
-    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
-  )) 
-```
-
-```{r E4-load-audio-timing-data, message=FALSE}
-# load audio data
-audio.info <- read_csv('group-d/info/audio_timing.csv')
-```
-
-```{r E4-average-onsets-of-critical-words}
-#Calculate average animal onset
-animal.onset <- audio.info %>% pull(onset_noun) %>% mean()
-instrument.onset <- audio.info %>% pull(onset_instrument) %>% mean()
-```
-
-```{r E4-timelocking-gaze-data}
-# Merge in audio timing information
-eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
-  mutate(sound = str_split(audio, pattern="/", simplify = T)[,4])
-
-eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
-  left_join(audio.info, by="sound")
-
-# Add time window information
-eyetracking.data.with.time.windows <- eyetracking.data.with.roi %>%
-  mutate(time.window = case_when(
-    t < onset_verb + 200 ~ "pre-verb-onset",
-    t <= onset_noun + 200 ~ "post-verb-onset-pre-animal-onset",
-    t <= onset_instrument + 200 ~ "post-animal-onset-pre-instrument-onset",
-    t <= onset_instrument + 1500 + 200 ~ "post-instrument-onset",
-    TRUE ~ "end"
-  ),
-  time.from.verb = t - onset_verb)
-```
-
-```{r E4-downsampling-gaze-data-for-plotting}
-#Add time window
-eyetracking.data.with.time.windows <- eyetracking.data.with.time.windows %>%
-  mutate(t.window = floor(time.from.verb/50)*50)
-```
-
-```{r E4-summarizing-gaze-data-for-plotting}
-#Summarize data for plotting
-eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
-  filter(between(t.window , -200, 4000)) %>%
-  group_by(subject, compatibility, t.window) %>%
-  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
-  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
-  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
-  group_by(compatibility, t.window, object_type) %>%
-  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
-```
-
-```{r E4-gaze-timecourse-fig, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-vertical lines indicate average onsets of animal and instrument offset by 200ms."}
-
-ggplot(eyetracking.figure.2.data, aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, linetype=object_type))+
-  geom_ribbon(color=NA, alpha=0.3)+
-  geom_line(size=1)+
-  theme_classic() +
-  geom_vline(xintercept = animal.onset + 200) + 
-  geom_vline(xintercept = instrument.onset + 200)+
-  labs(y = "Proportion of fixations", x = "Time window relative to verb onset (ms)")
-```
-
-```{r E4-compute-proportion-gaze-data-by-trial}
-#Summarize fixations on target and instrument
-eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
-  group_by(subject, trialID, sound, compatibility, time.window) %>%
-  summarize(prop.fixations.animal = sum(in.roi.animal) / n(),
-            prop.fixations.instrument = sum(in.roi.instrument) / n()) %>%
-  mutate(compatibility = factor(compatibility))
-```
-
-```{r E4-set-contrasts-for-ET-analysis}
-# Add orthogonal contrasts to model
-contrasts(eyetracking.window.summary.by.trial$compatibility) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
-```
-
-```{r E4-ET-analysis-verb-to-animal-window}
-data.time.window.1 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-verb-onset-pre-animal-onset")
-
-model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.1,
-                            control = lmerControl(optimizer = "bobyqa",
-                                                  optCtrl = list(maxfun = 2e6)))
-
-```
-```{r E4-ET-analysis-animal-to-inst-window}
-data.time.window.2 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-animal-onset-pre-instrument-onset")
-
-model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)
-```
-
-```{r E4-ET-analysis-post-inst-window}
-data.time.window.3 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-instrument-onset")
-
-model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 | subject) + (1 | trialID), data=data.time.window.3)
-```
-```{r E4-ET-analysis-tables}
-E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
-E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
-E4_ET_model3_tab = broom.mixed::tidy(model.time.window.3)
-
-E4_ET_model1_c1 = E4_ET_model1_tab %>% filter(term == "compatibility1")
-E4_ET_model1_c2 = E4_ET_model1_tab %>% filter(term == "compatibility2")
-
-E4_ET_model2_c1 = E4_ET_model2_tab %>% filter(term == "compatibility1")
-E4_ET_model2_c2 = E4_ET_model2_tab %>% filter(term == "compatibility2")
-
-E4_ET_model3_c1 = E4_ET_model3_tab %>% filter(term == "compatibility1")
-E4_ET_model3_c2 = E4_ET_model3_tab %>% filter(term == "compatibility2")
-```
-
-In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
-Mixed-effects linear regression models were used to predict the proportions of fixations to the target animal within each time window with the verb bias condition as an orthogonally contrast-coded (instrument vs.
-equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
-modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
-Participants and items were entered as varying intercepts^[`lme4` syntax: `lmer(prop.fix.target.animal ~ verb_bias + (1 + verb_bias | participant) + (1 | item), data=d)`.
-A model with by-participant varying slopes for verb bias condition was first attempted but did not converge.].
-In the _verb-to-noun_ window, participants did not look more at the target animal in any of the verb bias conditions (Instrument vs.
-Equi and Modifier: _b_ =  `r E4_ET_model1_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model1_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`; Equi vs.
-Modifier: _b_ =  `r E4_ET_model1_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model1_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c2 %>% pull(p.value) %>% round(digits = 2)` ).
-In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
-In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`).
 

### 2021-07-07 manuscript.tex
moved E4 analysis to child Rmd in group-d folder

--- 2021-06-30 manuscript.tex
@@
   english,
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 
-In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the \texttt{jsPsych} platform and \texttt{webgazer.js} plug-in.
+In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from \texttt{jsPsych}, a Javascript library for running behavioral experiments in a web browser (de Leeuw, 2015).
+The plug-in relies on the \texttt{webgazer.js} library for webcam eye-tracking (Papoutsaki et al., 2016).
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
@@
 \ldots{}
+
+\hypertarget{general-methods}{%
+\section{General Methods}\label{general-methods}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Participants completed the experiment remotely and were recruited through the Prolific platform.
+In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
+All participants provided informed consent.
+The studies were approved by the Vassar College Institutional Review Board.
+
+\hypertarget{eye-tracking-calibration-and-validation}{%
+\subsection{Eye-tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}}
+
+When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
+They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
+The webcam's view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
+The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
+
+During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
+Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
+The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
+After the calibration was completed, the validation began.
+Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
+If accuracy on the validation was too low (fewer than 50\% of looks landed within a 200 px radius of the validation points), participants were given an opportunity to re-start the calibration and validation steps.
+If the second attempt also lead to low validation accuracy, participants were informed that they could not participate in the study.
+
+\hypertarget{data-pre-processing}{%
+\subsection{Data pre-processing}\label{data-pre-processing}}
+
+We used R {[}Version 4.1.0; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 0.28.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.6; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.4; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.3; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.6.0; Chang et al.
+(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, and \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]} for all our analyses.
 
@@
 The first study was a replication attempt of Altmann and Kamide (1999).
+Altmann and Kamide used the visual world eye-tracking paradigm (Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995) to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
+For example, when looking at the display in Figure XX and listening to a sentence like ``The boy will eat the\ldots,'' participants are more likely to look at the cake than when they hear ``The boy will move the\ldots,'' in which case they tend to look at the train, presumably because cakes are edible and trains are not.
+Semantic information available at the verb is used to anticipate upcoming linguistic input.
 
@@
 All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at \url{https://osf.io/s82kz}.
-All participants provided informed consent and this study was approved by the Vassar College Institutional Review Board.
 
-\hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
 
-Participants for this experiment were sampled from a wide pool of Prolific users who are fluent in English and were paid for their participation.
-Our sample size of participants was determined by the total run time of our experiment, \textasciitilde10 minutes, and the allotted funding that was endowed to us by the Vassar College Cognitive Science Department.
-From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific, and we ended up with a sample size of 60 participants.
+60 participants were paid \$XX for their participation.
+Our sample size of participants was determined by the total run time of our experiment, \textasciitilde10 minutes, and the allotted funding from the Vassar College Cognitive Science Department.
+From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific.
+Note that the sample size of the original study was 24.
 For unknown reasons, 2 of the subjects' results were not recorded, so in the analysis, we worked with data collected from 58 participants.
@@
 
-Participants completed the experiment remotely and entirely online on the platform Prolific.
-During the experiment, the participants viewed a screen and were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
-The visual stimuli were created through Canva and depict a subject accompanied by 4 to 5 objects in the scene.
-16 of the devised stimuli were critical to our trial, and each of these images have 2 sentences associated with it.
-One of these sentences is in the restrictive condition, where the verb only applies to one object in the scene, and the other is in the nonrestrictive condition, where the verb could apply to all of the objects in the scene.
-To illustrate an example, reference Figure 1.
-This scene depicts a boy alongside a cake, ball, car, and train set.
-In the case of this particular image, the cake is the target object, so the two corresponding sentences to this image are, ``The boy will eat the cake'' (restrictive) and ``The boy will move the cake'' (nonrestrictive).
+The task began with an -point eye-tracker calibration and validation.
+During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
+Participants had to input a keyboard response indicating ``yes'' or ``no'' as to whether the sentence they heard was feasible given the visual image.
+There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
+Participants' reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.
 
-\hypertarget{materials}{%
-\subsubsection{Materials}\label{materials}}
+\hypertarget{materials-design}{%
+\subsubsection{Materials \& Design}\label{materials-design}}
 
-Therefore, for the 16 critical images, there are 16 control sentences where the verb does not constrain the target object and 16 restrictive sentences where the verb does constrain the target object.
-Each participant randomly received one sentence, restrictive or nonrestrictive, per scene.
-Of the 16 critical trials, each participant got 8 sentences that were restrictive and 8 that were nonrestrictive and the order of these were randomized.
-Trials were also designed so that participants had to input a keyboard response indicating ``yes'' or ``no'' as to whether the sentence relayed was feasible given the visual image.
-There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
-In addition to the 16 critical images, we also devised an additional 16 filler images that are not pertinent to our data collection and analysis.
-The critical trials were also presented in a randomized order along with these 16 filler trials.
-Unlike the critical images, the filler images were accompanied by only one sentence that is unfeasible given it's corresponding scene.
-This was so that when participants were asked whether or not the scene was possible, the filler trials would always elicit the answer, ``no.''
-Despite recording participants' reaction time and keyboard response after each trial, we were specifically measuring for the participant's first fixation to the target object and distractors relative to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
+The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure XX).
+On critical trials, participants heard one of two sentences associated with the scene.
+In the restrictive condition, the sentence (e.g., ``The boy will eat the cake'') contained a verb (e.g., ``eat'') which restricts the set of possible subsequent referents (e.g., to edible things).
+Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
+In the non-restrictive condition, the sentence (e.g., ``The boy will move the cake'') contained a verb (e.g., ``move'') which does not restrict the set of possible subsequent referents.
+The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
+Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was ``yes.'' Filler trials consisted of scenes that looked similar to critical scenes but were paired with inappropriate sentences.
+The correct keyboard response for the filler trials was ``no.''
 
-\hypertarget{eye-tracking-calibration-and-validation}{%
-\subsubsection{Eye-Tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}}
+Each participant was presented with sixteen critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and sixteen fillers for a total of 32 trials.
+The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.
 
-Before initiating the experiment, participants were prompted to complete an eye-tracking calibration and validation procedure to ensure the data collected via the webcam-based eye tracking method was as accurate as possible.
-In order to allow the software to track where participants are looking, subjects were presented with a series of dots that appeared on the screen.
-Participants were then instructed to look at each dot as they appeared and click on it.
-By visually fixating and then clicking on one dot, it would then disappear and a new one would reappear in a different location on the screen.
-The calibration dots appeared in the central area of the screen where the visual stimuli would appear in order to ensure Web Gazer would be able to track eye movements to the relevant regions of interest.
-After completing this calibration, participants were then asked to go through the same steps of the calibration, except this time, they would have to just look at, not click, the dots as they appear on the screen in order to measure the accuracy of the calibration.
-This process completes the Web Gazer calibration and validation process.
+\emph{TO DO:} add figure
 
@@
 
-We used R {[}Version 4.1.0; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
+Looks to the objects in the scene were time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
 
@@
 
-\begin{quote}
-here we will describe the analyses that are as close as possible to the original paper
-\end{quote}
+\begin{itemize}
+\item
+  here we will describe the analyses that are as close as possible to the original paper with a minimal validation cutoff
+\item
+  same analysis but with stricter validation cutoff
+\end{itemize}
+
+\hypertarget{comparison-to-in-lab-data}{%
+\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}}
+
+\begin{itemize}
+\tightlist
+\item
+  here we will describe a direct comparison to data collected in the lab
+\end{itemize}
 
@@
 
-\begin{quote}
-here we will describe the analyses that correlate calibration quality with effect size at the individual (Josh H?)
-\end{quote}
+\begin{itemize}
+\tightlist
+\item
+  here we will describe the analyses that correlate calibration quality with effect size at the individual level
+\end{itemize}
 
@@
 The second study was a replication attempt of Johansson and Johansson (2014).
+They examined how visuospatial information is integrated into memories for objects.
+They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding (see Spivey \& Geng, 2001) and that this spatial reinstatement facilitates retrieval of the picture.
 
@@
 
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
+\hypertarget{participants-2}{%
+\subsubsection{Participants}\label{participants-2}}
 
-\hypertarget{material}{%
-\subsubsection{Material}\label{material}}
+60 participants were paid \$XX for their participation .
+We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
+We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
 
@@
 \subsubsection{Procedure}\label{procedure-1}}
+
+The task began with an -point eye-tracker calibration and validation.
+The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
+During the encoding phase, participants saw a grid indicating the four quadrants of the screen.
+Each quadrant contained six images of items belonging to the same category (see Figure XX).
+The four possible categories were humanoids, household objects, animals, and methods of transportation.
+Participants were asked to remember the contents of the four quadrants.
+Different images were used in each block.
+
+Each of the four quadrants was presented one at a time.
+First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown (??).
+For each item, an audio file would play (``???'') asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing either left or right (right??)).
+After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
+Then, after all four quadrants were presented in this way, the participant was shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
+
+During the recall phase, participants listened to statements and responded by pressing the `F' key for false statements and `T' for true ones.
+Each statement fell into either an interobject or intraobject condition.
+Interobject statements were those that compared two different items in the grid (e.g.~``The skeleton is to the left of the robot''), while intraobject statements were those that asked about the orientation of a single item (e.g.~``The bus is facing right'').
+There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
+While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
+During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
+In both cases, the mouse was obscured from the screen.
+Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
+
+After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
+
+The primary methodological difference between this replication and Johansson and Johansson's study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
+In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
 
@@
 
+\hypertarget{replication-1}{%
+\subsubsection{Replication}\label{replication-1}}
+
+\begin{itemize}
+\item
+  here we will describe the analyses that are as close as possible to the original paper
+\item
+  same but stricter validation cutoff
+\end{itemize}
+
+\hypertarget{calibration-1}{%
+\subsubsection{Calibration}\label{calibration-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  here we will describe the analyses that correlate calibration quality with effect size at the individual level
+\end{itemize}
+
 \hypertarget{discussion-1}{%
@@
 
-The third study was a replication attempt of (\textbf{Mann?})???.
+The third study was a replication attempt of Manns, Stark, and Squire (2000) which aimed to show that the visual paired-comparison task, widely used in the patient literature, tapped into declarative memory.
+In the visual paired-comparison task, two identical pictures were presented side by side for a brief viewing period.
+After a delay, one of the previously viewed pictures was presented along with a new picture.
+Individuals looked more at the new picture than the old picture and the time spent looking was correlated with later recognition memory performance.
+On the other hand perceptual priming, thought to recruit non-declarative memory, was not linked to later recognition.
+(The perceptual priming arm of the design was not included in this replication.)
 
@@
 
-\hypertarget{participants-2}{%
-\subsubsection{Participants}\label{participants-2}}
+\hypertarget{participants-3}{%
+\subsubsection{Participants}\label{participants-3}}
 
-\hypertarget{material-1}{%
-\subsubsection{Material}\label{material-1}}
+Our initial sample size was 51 participants for the first day of our experiment and 48 of them came back for the second day.
+Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test.
+Our final sample size was 45 participants.
 
@@
 \subsubsection{Procedure}\label{procedure-2}}
+
+The task began with a 7-point eye-tracker calibration (each point was presented 3 times in a random order) and validation with 3 points (each presented once).
+The point locations were designed to focus calibration on the center of the screen and the middle of the left and right halves of the screen.
+The experiment was administered over the course of two consecutive days.
+It consisted of three sections: a presentation phase, a test phase, and a recognition test.
+The first two phases occurred on the first day, while the recognition test occurred on the second day.
+
+During the presentation phase, participants viewed 24 pairs of identical color photographs depicting common objects.
+Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
+The order of the photographs was randomized and different for each participant.
+After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
+
+After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
+During this phase, participants again viewed 24 pairs of photographs with an interstimulus duration of 5 seconds.
+In each pair, one photograph was previously seen during the presentation phase, while the other was new.
+Which pictures were old or new was counterbalanced across participants.
+For half of the participants in each counterbalancing group, the new and old photographs were reversed.
+
+Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
+It consisted of 48 photographs, presented one at a time.
+Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
+Half of the pohotographs had been viewed twice on the previous day and were deemed the ``targets.'' The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed ``foils.'' Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing `y' for yes and `n' for no.
+After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a ``pure guess'' to 5 as ``very sure.'' by clicking on the corresponding number on the screen.
+No feedback on their responses was given during the test.
+
+The experimental design is visually depicted in Figure XX
+
+\hypertarget{materials}{%
+\subsubsection{Materials}\label{materials}}
+
+Images were selected XXX\ldots{}
+
+There were two modifications we made to the methods of the original experiment.
+As we are only replicating the declarative memory component of the original experiment, we did not have a ``priming group.'' Therefore, we followed only the procedure for the ``looking group.'' Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.
 
@@
 
-The fourth study was a replication attempt of Ryskin, Qi, Duff, and Brown-Schmidt (2017).
+The fourth study was a replication attempt of Experiment 1 in Ryskin, Qi, Duff, and Brown-Schmidt (2017), which was closely modeled on Snedeker and Trueswell (2004).
+These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
+For example, in a sentence like ``Feel the frog with the feather,'' the phrase ``with the feather'' could be describing the frog, or it could be describing the instrument that should be used to do the ``feeling.'' When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb's ``bias'' (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
+.
 
@@
 
-\hypertarget{participants-3}{%
-\subsubsection{Participants}\label{participants-3}}
+The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, \url{https://osf.io/x3c49/} (\url{https://osf.io/x3c49/}).
+The pre-registration for the study can be found at \url{https://osf.io/3v4pg} (\url{https://osf.io/3v4pg}).
 
-\hypertarget{material-2}{%
-\subsubsection{Material}\label{material-2}}
+\hypertarget{participants-4}{%
+\subsubsection{Participants}\label{participants-4}}
+
+58 (??) participants were paid \$XX for their participation .
+A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power.
+Note that the original study had a sample size of 24.
 
@@
 
-\hypertarget{data-analysis-2}{%
-\subsubsection{Data analysis}\label{data-analysis-2}}
+\begin{itemize}
+\tightlist
+\item
+  \emph{TO DO:} add details of calibration point locations
+\end{itemize}
+
+After the eye-tracking calibration, participants went through an audio test so they could adjust the audio on their computer to a comfortable level.
+Before beginning the experiment, they were given instructions that four objects would appear, an audio prompt would play, and they should do their best to use their mouse to act out the instructions.
+They then went through three practice trials which were followed by 54 critical trials and 24 filler trials presented in a random order.
+
+During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., ``Rub the butterfly with the crayon''; see Figure XX)\footnote{In the original study, the pictures appeared one by one on the screen and their names were played as they appeared.
+We removed this introductory portion of the trial to save time}.
+Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects\footnote{ As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
+For example, the sentence ``locate the camel with the straw'' may not involve any clicking but rather only mousing over the camel.}.
+After the action was completed, the participants were instructed to press the space bar which led to a screen that said ``Click Here'' in the middle in order to remove bias in the eye and mouse movements from the previous trial.
+The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
+
+\emph{TO DO}: ADD FIGURES Figure 1: An example of a critical trial for the sentence ``Rub the butterfly with the crayon.'' The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+
+\hypertarget{materials-1}{%
+\subsubsection{Materials}\label{materials-1}}
+
+The images and audios presented to the participants were the same stimuli used in the original study (available here ).
+The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
+Two lists of critical trials were made with different verb and instrument combinations (e.g., ``rub'' could be paired with ``panda'' and ``crayon'' in one list and ``panda'' and ``violin'' in the second list).
+Within each list, the same verb was presented twice but each time with a different target instrument and animal.
+The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
+The list of verbs used can be found in Appendix A of the original study.
 
@@
 \subsection{Results}\label{results-3}}
+
+\hypertarget{replication-2}{%
+\subsubsection{Replication}\label{replication-2}}
+
+The location of initial mouse movements was used to assess whether the final interpretation of ambiguous sentences was biased by the verb.
+Figure \ref{fig:E4-mouse-moves-fig} suggests that listeners were more likely to move their mouse first over the target instrument when the verb was equi-biased than when the verb was modifier-biased and even more so when the verb was instrument-biased.
+The opposite graded pattern can be observed for mouse movements over the target animal.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-1.pdf}
+\caption{\label{fig:E4-mouse-moves-fig}Proportion of first mouse movements by location and verb bias.}
+\end{figure}
+
+A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.~equi \& modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.~modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
+Participants and items were entered as varying intercepts with by-participant varying slopes for verb bias condition\footnote{\texttt{lme4} syntax: \texttt{glmer(is.mouse.over.instrument\ \textasciitilde{}\ verb\_bias\ +\ (1\ +\ verb\_bias\ \textbar{}\ participant)\ +\ (1\ \textbar{}\ item),\ family="binomial",\ data=d)}}.
+Participants were more likely to first move their mouse over target instruments in the instrument-biased condition relative to the equi-biased and modifier-biased condition (\emph{b} = -1.50, \emph{SE} = 0.25, \emph{p} \textless{} 0.01).
+Further, participants were more likely to first move their mouse over target instruments in the equi-biased condition relative to the modifier-biased condition (\emph{b} = -1.10, \emph{SE} = 0.29, \emph{p} \textless{} 0.01)
+
+Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
+Figure \ref{fig:E4-gaze-timecourse-fig} suggests that the participants made more fixations to the target animal when the verb was modifier-biased\ldots{}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-1.pdf}
+\caption{\label{fig:E4-gaze-timecourse-fig}Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
+vertical lines indicate average onsets of animal and instrument offset by 200ms.}
+\end{figure}
+
+In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
+Mixed-effects linear regression models were used to predict the proportions of fixations to the target animal within each time window with the verb bias condition as an orthogonally contrast-coded (instrument vs.~equi \& modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.~modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
+Participants and items were entered as varying intercepts\footnote{\texttt{lme4} syntax: \texttt{lmer(prop.fix.target.animal\ \textasciitilde{}\ verb\_bias\ +\ (1\ +\ verb\_bias\ \textbar{}\ participant)\ +\ (1\ \textbar{}\ item),\ data=d)}.
+A model with by-participant varying slopes for verb bias condition was first attempted but did not converge.}.
+In the \emph{verb-to-noun} window, participants did not look more at the target animal in any of the verb bias conditions (Instrument vs.~Equi and Modifier: \emph{b} = -0.01, \emph{SE} = 0.02, \emph{p} = 0.59; Equi vs.~Modifier: \emph{b} = 0, \emph{SE} = 0.02, \emph{p} = 1 ).
+In the \emph{noun-to-instrument} window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( \emph{b} = 0.03, \emph{SE} = 0.01, \emph{p} \textless{} 0.01) and in the equi-biased relative to the instrument-biased condition ( \emph{b} = 0.02, \emph{SE} = 0.01, \emph{p} \textless{} 0.05).
+In the \emph{post-instrument} window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( \emph{b} = 0.08, \emph{SE} = 0.02, \emph{p} \textless{} 0.01) but not significantly so in the equi-biased relative to the instrument-biased condition ( \emph{b} = 0.03, \emph{SE} = 0.02, \emph{p} = 0.59).
+
+\hypertarget{comparison-to-in-lab-data-1}{%
+\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  here we will describe a direct comparison to data collected in the lab
+\end{itemize}
+
+\hypertarget{calibration-2}{%
+\subsubsection{Calibration}\label{calibration-2}}
+
+\begin{itemize}
+\tightlist
+\item
+  here we will describe the analyses that correlate calibration quality with effect size at the level of the individual
+\end{itemize}
+
+\hypertarget{effects-of-rois}{%
+\subsubsection{Effects of ROIs}\label{effects-of-rois}}
+
+\begin{itemize}
+\tightlist
+\item
+  here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
+\end{itemize}
 
@@
 
-The fifth study was a replication attempt of @??.
+The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003), which found that human gaze is actively involved in preference formation.
+Participants were shown pairs of human faces and were asked to choose the face which they found more attractive.
+Prior to making their explicit selection, participants spent more time looking at the face that was ultimately judged more attractive.
+This bias was not as large when the task was face shape discrimination rather than a preference-based choice.
 
@@
 
-\hypertarget{participants-4}{%
-\subsubsection{Participants}\label{participants-4}}
+All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at \url{https://osf.io/eubsc/} (\url{https://osf.io/eubsc/}).
+The study pre-registration is available at \url{https://osf.io/tv57s} (\url{https://osf.io/tv57s}).
 
-\hypertarget{material-3}{%
-\subsubsection{Material}\label{material-3}}
+\hypertarget{participants-5}{%
+\subsubsection{Participants}\label{participants-5}}
 
-\hypertarget{procedure-4}{%
-\subsubsection{Procedure}\label{procedure-4}}
+27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They were paid \$XX for completing the experiment.
+Data from 3 participants was excluded because their mode response made up more than 50\% of their total responses , for a total of 24 participants in the norming.
 
-\hypertarget{data-analysis-3}{%
-\subsubsection{Data analysis}\label{data-analysis-3}}
+50 participants for the main task were recruited on Prolific and were paid \$XX.
+8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
+After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.The original sample size in Shimojo et al.~(2003) was 10 participants total.
+
+\hypertarget{procedure-and-design}{%
+\subsubsection{Procedure and Design}\label{procedure-and-design}}
+
+At the beginning of the experimental task, participants completed a 9-point eye-tracker calibration (each point appeared 3 times in random order) and 3-point validation.
+The validation point appeared once at center, middle left, and middle right locations in random order.
+
+During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure XX).
+Participants were randomly assigned to one of two tasks: attractiveness or shape judgment.
+In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
+They pressed the ``a'' key on their keyboard to select the face on the left and the ``d'' key to select the face on the right.
+A fixation cross appeared in the center of the screen between each set of faces.
+Participants were asked to look at this fixation cross in order to reset their gaze in between trials (???).
+The order of the 19 face pairs was random for each participant.
+
+\hypertarget{materials-and-norming}{%
+\subsubsection{Materials and Norming}\label{materials-and-norming}}
+
+The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset.
+(The face images used in Shimojo et al.~were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
+Participants in the norming study viewed 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+Faces were presented one at a time and in a random order for each participant.
+Following Shimojo et al., 19 face pairs were made by matching two faces that had a difference in mean attractiveness ratings that was 0.25 points or lower and that matched in gender, race, and age group (young adult, adult, or older adult).
+
+\hypertarget{data-analysis-2}{%
+\subsubsection{Data analysis}\label{data-analysis-2}}
+
+In the original study, a video-based eye tracker was used.
+The eye movements of participants were recorded with a digital camera, and eye position was then tracked using MediaAnalyzer software.
+This eye tracker was able to collect 30 samples per second.
+In our study, the camera on the device used by the participant and the jsPsych WebGazer package were used to determine where a participant's gaze was directed.
+Since our eye tracking method did not have the same sample collection rate as the eye tracker in Shimojo et al., time windows of 50 milliseconds were used when looking at the likelihood of gazing at the chosen face at a given point between a cutoff time and when the decision was made.
 
@@
 
-The sixth study was a replication attempt of @??.
+The sixth study was a replication attempt of Posner et al.~??.
 
@@
 
-\hypertarget{participants-5}{%
-\subsubsection{Participants}\label{participants-5}}
+\hypertarget{participants-6}{%
+\subsubsection{Participants}\label{participants-6}}
 
-\hypertarget{material-4}{%
-\subsubsection{Material}\label{material-4}}
+\hypertarget{procedure-and-design-1}{%
+\subsubsection{Procedure and Design}\label{procedure-and-design-1}}
 
-\hypertarget{procedure-5}{%
-\subsubsection{Procedure}\label{procedure-5}}
-
-\hypertarget{data-analysis-4}{%
-\subsubsection{Data analysis}\label{data-analysis-4}}
+\hypertarget{data-analysis-3}{%
+\subsubsection{Data analysis}\label{data-analysis-3}}
 
@@
 \subsection{Results}\label{results-5}}
+
+\hypertarget{replication-3}{%
+\subsubsection{Replication}\label{replication-3}}
+
+\hypertarget{calibration-3}{%
+\subsubsection{Calibration}\label{calibration-3}}
+
+\hypertarget{rois}{%
+\subsubsection{ROIs}\label{rois}}
+
+\hypertarget{item-numbers}{%
+\subsubsection{Item Numbers}\label{item-numbers}}
 
@@
 \section{Combined Analyses}\label{combined-analyses}}
+
+\begin{itemize}
+\tightlist
+\item
+  Pooling data from all experiments we can look at patterns in the calibration and validation data
+\end{itemize}
 
@@
 
+\leavevmode\hypertarget{ref-R-Matrix}{}%
+Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\hypertarget{ref-R-lme4}{}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using {lme4}.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\hypertarget{ref-R-broom.mixed}{}%
+Bolker, B., \& Robinson, D. (2020). \emph{Broom.mixed: Tidying methods for mixed models}. Retrieved from \url{https://CRAN.R-project.org/package=broom.mixed}
+
+\leavevmode\hypertarget{ref-R-shiny}{}%
+Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
+(2021).
+\emph{Shiny: Web application framework for r}.
+Retrieved from \url{https://CRAN.R-project.org/package=shiny}
+
+\leavevmode\hypertarget{ref-deleeuwJsPsychJavaScriptLibrary2015}{}%
+de Leeuw, J.
+R.
+(2015).
+{jsPsych}: {A JavaScript} library for creating behavioral experiments in a {Web} browser.
+\emph{Behavior Research Methods}, \emph{47}(1), 1--12.
+\url{https://doi.org/10.3758/s13428-014-0458-y}
+
 \leavevmode\hypertarget{ref-johanssonLookHereEye2014}{}%
@@
 \url{https://doi.org/10.1177/0956797613498260}
+
+\leavevmode\hypertarget{ref-R-lmerTest}{}%
+Kuznetsova, A., Brockhoff, P.
+B., \& Christensen, R.
+H.
+B.
+(2017).
+{lmerTest} package: Tests in linear mixed effects models.
+\emph{Journal of Statistical Software}, \emph{82}(13), 1--26.
+\url{https://doi.org/10.18637/jss.v082.i13}
+
+\leavevmode\hypertarget{ref-mannsVisualPairedcomparisonTask2000}{}%
+Manns, J.
+R., Stark, C.
+E.
+L., \& Squire, L.
+R.
+(2000).
+The visual paired-comparison task as a measure of declarative memory.
+\emph{Proceedings of the National Academy of Sciences}, \emph{97}(22), 12375--12379.
+\url{https://doi.org/10.1073/pnas.220398097}
+
+\leavevmode\hypertarget{ref-R-jsonlite}{}%
+Ooms, J. (2014). The jsonlite package: A practical and consistent mapping between JSON data and r objects. \emph{arXiv:1403.2805 {[}Stat.CO{]}}. Retrieved from \url{https://arxiv.org/abs/1403.2805}
+
+\leavevmode\hypertarget{ref-papoutsaki2016webgazer}{}%
+Papoutsaki, A., Sangkloy, P., Laskey, J., Daskalova, N., Huang, J., \& Hays, J.
+(2016).
+{WebGazer}: {Scalable} webcam eye tracking using user interactions.
+In \emph{Proceedings of the 25th international joint conference on artificial intelligence ({IJCAI})} (pp.
+3839--3845).
+{AAAI}.
 
@@
 
+\leavevmode\hypertarget{ref-shimojoGazeBiasBoth2003}{}%
+Shimojo, S., Simion, C., Shimojo, E., \& Scheier, C.
+(2003).
+Gaze bias both reflects and influences preference.
+\emph{Nature Neuroscience}, \emph{6}(12), 1317--1322.
+\url{https://doi.org/10.1038/nn1150}
+
+\leavevmode\hypertarget{ref-R-afex}{}%
+Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
+
+\leavevmode\hypertarget{ref-snedekerDevelopingConstraintsParsing2004a}{}%
+Snedeker, J., \& Trueswell, J.
+C.
+(2004).
+The developing constraints on parsing decisions: {The} role of lexical-biases and referential scenes in child and adult sentence processing.
+\emph{Cognitive Psychology}, \emph{49}(3), 238--299.
+\url{https://doi.org/10.1016/j.cogpsych.2004.03.001}
+
+\leavevmode\hypertarget{ref-spiveyOculomotorMechanismsActivated2001}{}%
+Spivey, M.
+J., \& Geng, J.
+J.
+(2001).
+Oculomotor mechanisms activated by imagery and memory: Eye movements to absent objects.
+\emph{Psychological Research}, \emph{65}(4), 235--241.
+\url{https://doi.org/10.1007/s004260100059}
+
+\leavevmode\hypertarget{ref-tanenhaus1995}{}%
+Tanenhaus, M.
+K., Spivey-Knowlton, M.
+J., Eberhard, K.
+M., \& Sedivy, J.
+C.
+(1995).
+Integration of visual and linguistic information in spoken language comprehension.
+\emph{Science}, \emph{268}(5217), 1632--1634.
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
 \end{CSLReferences}

### 2021-11-11 conference/CDS-abstract-figure.Rmd
working on figure for CDS abstract

---
title: "CDS-abstract-figure"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(patchwork)
library(magick)
library(ggpubr)
```

```{r }

displayA<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.001.jpeg'))+coord_fixed() + ggtitle('A')
displayB<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.002.jpeg'))+coord_fixed() + ggtitle('B')
displayC<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.003.jpeg'))+coord_fixed() + ggtitle('C')
displayD<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.004.jpeg'))+coord_fixed() + ggtitle('D')
displayE<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.005.jpeg'))+coord_fixed() + ggtitle('E')

figA<-read_rds('../group-d/output/ETfig.rds')
figB<-read_rds('../group-d/output/ETfig.rds')
figC<-read_rds('../group-d/output/ETfig.rds')
figD<-read_rds('../group-d/output/ETfig.rds')
figE<-read_rds('../group-d/output/ETfig.rds')

```

```{r}
A <- displayA + figA 
B <- displayA + figB 
C <- displayA + figC 
D <- displayD + figD 
E <- displayA + figE

```

```{r}
(A | B)/(C | D ) / ( E | (grid::textGrob('Figure 1. ADD CAPTION HERE')) ) 
```

```{r}
ggsave('CDS-abstract-figure.pdf', scale = 1, width = 11, height = 7)

```

### 2021-11-11 group-d/E4-analysis-replication.Rmd
working on figure for CDS abstract

@@
 ```{r E4-gaze-timecourse-fig, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-vertical lines indicate average onsets of animal and instrument offset by 200ms."}
+Vertical lines indicate average onsets of animal and instrument offset by 200ms."}
 
-ggplot(eyetracking.figure.2.data, aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, linetype=object_type))+
+fig2<-ggplot(eyetracking.figure.2.data %>% 
+  mutate(compatibility = factor(compatibility, 
+                                levels = c("modifier", "equibiased", "instrument" ), 
+                                labels = c("Modifier", "Equi-biased", "Instrument" ))), 
+  aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, linetype=object_type))+
   geom_ribbon(color=NA, alpha=0.3)+
   geom_line(size=1)+
+  scale_color_brewer(palette = "Set1")+
+  scale_fill_brewer(palette = "Set1")+
+  scale_linetype(labels = c("Animal", "Instrument") )+
   theme_classic() +
@@
   geom_vline(xintercept = instrument.onset + 200)+
-  labs(y = "Proportion of fixations", x = "Time window relative to verb onset (ms)")
+  labs(y = "Proportion of looks", x = "Time relative to verb onset (ms)")+
+  guides(color = guide_legend("Verb bias"),fill = guide_legend("Verb bias"), linetype = guide_legend("Gaze location"))
+fig2
+```
+```{r, eval=FALSE}
+saveRDS(fig2, "output/ETfig.rds")
+
 ```

### 2021-11-11 manuscript.tex
working on figure for CDS abstract

@@
   man,floatsintext]{apa6}
+\title{Eye-tracking on the web: lessons learned from replicating 6 experiments}
+\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Eye-tracking on the web: lessons learned from replicating 6 experiments}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
-\date{}
 
@@
 
-We used R {[}Version 4.1.0; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 0.28.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.6; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.4; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.3; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.6.0; Chang et al.
-(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, and \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]} for all our analyses.
+We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 1.0.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.7; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.4; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 2.0.2; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.7.1; Chang et al.
+(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, and \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]} for all our analyses.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-altmannIncrementalInterpretationVerbs1999}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-altmannIncrementalInterpretationVerbs1999}{}}%
 Altmann, G.
@@
 
-\leavevmode\hypertarget{ref-R-papaja}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-R-Matrix}{}%
-Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
-
-\leavevmode\hypertarget{ref-R-lme4}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
 Bates, D., Mächler, M., Bolker, B., \& Walker, S.
@@
 
-\leavevmode\hypertarget{ref-R-broom.mixed}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-broom.mixed}{}}%
 Bolker, B., \& Robinson, D. (2020). \emph{Broom.mixed: Tidying methods for mixed models}. Retrieved from \url{https://CRAN.R-project.org/package=broom.mixed}
 
-\leavevmode\hypertarget{ref-R-shiny}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-shiny}{}}%
 Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
@@
 
-\leavevmode\hypertarget{ref-deleeuwJsPsychJavaScriptLibrary2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-deleeuwJsPsychJavaScriptLibrary2015}{}}%
 de Leeuw, J.
@@
 
-\leavevmode\hypertarget{ref-johanssonLookHereEye2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-johanssonLookHereEye2014}{}}%
 Johansson, R., \& Johansson, M.
@@
 
-\leavevmode\hypertarget{ref-R-lmerTest}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-lmerTest}{}}%
 Kuznetsova, A., Brockhoff, P.
@@
 
-\leavevmode\hypertarget{ref-mannsVisualPairedcomparisonTask2000}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mannsVisualPairedcomparisonTask2000}{}}%
 Manns, J.
@@
 
-\leavevmode\hypertarget{ref-R-jsonlite}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-jsonlite}{}}%
 Ooms, J. (2014). The jsonlite package: A practical and consistent mapping between JSON data and r objects. \emph{arXiv:1403.2805 {[}Stat.CO{]}}. Retrieved from \url{https://arxiv.org/abs/1403.2805}
 
-\leavevmode\hypertarget{ref-papoutsaki2016webgazer}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-papoutsaki2016webgazer}{}}%
 Papoutsaki, A., Sangkloy, P., Laskey, J., Daskalova, N., Huang, J., \& Hays, J.
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-ryskinVerbBiasesAre2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ryskinVerbBiasesAre2017}{}}%
 Ryskin, R., Qi, Z., Duff, M.
@@
 
-\leavevmode\hypertarget{ref-shimojoGazeBiasBoth2003}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-shimojoGazeBiasBoth2003}{}}%
 Shimojo, S., Simion, C., Shimojo, E., \& Scheier, C.
@@
 
-\leavevmode\hypertarget{ref-R-afex}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-afex}{}}%
 Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
 
-\leavevmode\hypertarget{ref-snedekerDevelopingConstraintsParsing2004a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-snedekerDevelopingConstraintsParsing2004a}{}}%
 Snedeker, J., \& Trueswell, J.
@@
 
-\leavevmode\hypertarget{ref-spiveyOculomotorMechanismsActivated2001}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-spiveyOculomotorMechanismsActivated2001}{}}%
 Spivey, M.
@@
 
-\leavevmode\hypertarget{ref-tanenhaus1995}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tanenhaus1995}{}}%
 Tanenhaus, M.
@@
 
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
 Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\hypertarget{ref-R-stringr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
 Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\hypertarget{ref-R-forcats}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
 Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\hypertarget{ref-R-tidyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
 Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\hypertarget{ref-R-dplyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
 Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\hypertarget{ref-R-readr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
 Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}

### 2021-11-11 manuscript.Rmd
adding expt example displays

@@
 
-The second study was a replication attempt of @johanssonLookHereEye2014.
-They examined how visuospatial information is integrated into memories for objects.
+The second study was a replication attempt of @johanssonLookHereEye2014, which examined how visuospatial information is integrated into memory for objects.
 They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding [see @spiveyOculomotorMechanismsActivated2001] and that this spatial reinstatement facilitates retrieval of the picture.
@@
 60 participants were paid $XX for their participation <!--right?-->.
-We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
-We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
+The sample size was motivated in part by budget constraints, but was nonetheless 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
+Data from 1 participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.
 
@@
 
-The task began with an <number of points>-point eye-tracker calibration and validation.
 The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
@@
 Each quadrant contained six images of items belonging to the same category (see Figure XX).
-The four possible categories were humanoids, household objects, animals, and methods of transportation.
+The four categories were humanoids, household objects, animals, and methods of transportation.
 Participants were asked to remember the contents of the four quadrants.

### 2021-11-11 conference/CDS-abstract-figure.Rmd
added fig for E2

@@
 figA<-read_rds('../group-d/output/ETfig.rds')
-figB<-read_rds('../group-d/output/ETfig.rds')
+figB<-read_rds('../group-b/output/ETfig.rds')
 figC<-read_rds('../group-d/output/ETfig.rds')
@@
 A <- displayA + figA 
-B <- displayA + figB 
-C <- displayA + figC 
+B <- displayB + figB 
+C <- displayC + figC 
 D <- displayD + figD 
-E <- displayA + figE
+E <- displayE + figE
 
@@
 ```{r}
-ggsave('CDS-abstract-figure.pdf', scale = 1, width = 11, height = 7)
+ggsave('CDS-abstract-figure.pdf', scale = 1, width = 12, height = 7)
 

### 2021-11-11 group-b/E2-analysis-replication.Rmd
adding expt example displays
added fig for E2

--- 2021-05-30 group-b/group-b-analysis.Rmd
@@
 title: "Group B Analysis"
-output: html_notebook
+output: pdf
 ---
@@
 library(ggplot2)
-library(ez)
+#library(ez)
 ```
 
-# Import Data
-
-Read JSON files and bind together into a tibble.
+<!--Read JSON files and bind together into a tibble.-->
 
@@
 
-# Extract relevant data
+<!--Extract relevant data-->
 
@@
 
-Need to add condition information to the `task.data`
+<!-- add condition information to the `task.data`-->
 
@@
 
-# Question: Do people look more at the critical quadrant during free viewing?
+<!-- Question: Do people look more at the critical quadrant during free viewing?-->
 
-Grab the relevant data, unnesting webgazer observations
+<!--Grab the relevant data, unnesting webgazer observations-->
 
@@
 
-Add quadrant information to each observation
+<!--Add quadrant information to each observation-->
 
@@
 
-Summarize proportion of views in each quadrant for each trial
+<!--Summarize proportion of views in each quadrant for each trial-->
 ```{r}
@@
 ```
-Summarize by subject
+<!--Summarize by subject-->
 ```{r}
@@
 
-Summarize by condition 
+<!--Summarize by between condition -->
+```{r}
+free.view.summary.condition1.data <- free.view.summary.subject.data %>%
+  group_by(normalized_quadrant) %>%
+  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
+```
+
+```{r}
+fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
+  geom_col(position=position_dodge(), color = "black")+
+  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
+  scale_fill_brewer(palette="Set1",)+
+  theme_classic()+
+  labs(x = "Quadrant", y = "Mean proportion of looks")+
+  theme(legend.position = "none")
+fig
+```
+```{r, eval=FALSE}
+saveRDS(fig, "output/ETfig.rds")
+
+```
+
+<!--Summarize by between and within conditions -->
 ```{r}
@@
 ```
+
 ```{r}
 ggplot(free.view.summary.condition.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill=relation)) +
-  geom_col(position=position_dodge())+
+  geom_col(position=position_dodge(), color = "black")+
   geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
-  theme_classic()
+  theme_classic()+
+  labs(x = "Quadrant", y = "Mean proportion of looks")
 ```

### 2021-11-12 group-b/E2-analysis-replication.Rmd
added E2 replication analyses

@@
 title: "Group B Analysis"
-output: pdf
+output: pdf_document
 ---
@@
 library(ggplot2)
-#library(ez)
+library(patchwork)
+library(lmerTest)
+library(broom.mixed)
 ```
@@
   select(subject_id, trial_index, stimulus, relation, quadrant, rt, correct_response, response, webgazer_data, webgazer_targets) %>%
-  unpack(webgazer_targets) %>%
-  unpack(`#screen`) %>%
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(`#screen`) %>%
   select(-top,-left,-x,-y,-bottom,-right)
@@
 
+### Replication
 <!--Summarize proportion of views in each quadrant for each trial-->
@@
 
+__Eye-gaze__.
+Looks during the retrieval period were categorized as belonging to one of four quadrants based on the x,y coordinates.
+The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding.
+The other three quadrants were semi-randomly labeled "first", "second," third" (e.g., when the critical quadrant was in the top left, the "first" quadrant was the top right quadrant, but when the critical quadrant was in the top right, "first" corresponded to bottom right, etc.).
+In the free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \@ref(fig:E2-gaze-fig)).
+
 <!--Summarize by between condition -->
@@
 
-```{r}
+```{r E2-gaze-fig, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval."}
 fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
@@
 ```
-```{r, eval=FALSE}
+```{r saving plot, eval=FALSE}
 saveRDS(fig, "output/ETfig.rds")
@@
 
-<!--Summarize by between and within conditions -->
-```{r}
-free.view.summary.condition.data <- free.view.summary.subject.data %>%
-  group_by(normalized_quadrant, relation) %>%
-  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
+```{r E2-gaze-model}
+E2_gaze_model<-lmer(proportion ~ normalized_quadrant + (1+normalized_quadrant|subject_id), data = free.view.summary.subject.data)
+#summary(m1)
+E2_gaze_model_tab = broom.mixed::tidy(E2_gaze_model) 
+E2_gaze_model_q1 = E2_gaze_model_tab %>% filter(term == "normalized_quadrantfirst")
+E2_gaze_model_q2 = E2_gaze_model_tab %>% filter(term == "normalized_quadrantsecond")
+E2_gaze_model_q3 = E2_gaze_model_tab %>% filter(term == "normalized_quadrantthird")
 ```
 
-```{r}
-ggplot(free.view.summary.condition.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill=relation)) +
-  geom_col(position=position_dodge(), color = "black")+
-  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
-  theme_classic()+
-  labs(x = "Quadrant", y = "Mean proportion of looks")
-```
+The proportion of looks across quadrant was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
+The model included random intercepts and slopes for participants^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`.
+Among other limitations, this approach may violate the independence assumptions of the linear model because looks to the four locations are not independent.
+This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.] Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )
 
-Goal: ANOVA with quadrant and statement type as factors, gaze proportion as DV
-
-```{r}
-free.view.anova <- ezANOVA(free.view.summary.subject.data, wid=subject_id, dv=proportion, within=c(relation,normalized_quadrant))
-free.view.anova$ANOVA
-```
-# Behavioral Analysis
-
-First, extract relevant data and compute `correct` column
-
-```{r}
+```{r E2-compute-accuracy}
 behavioral.data <- task.data %>%
@@
 
-Goal: ANOVA with RT as DV, condition, statement as IVs
+```{r E2-compute-acc-v2}
+# *note that paper computer accuracy as hit rate - false alarm rate*
+acc.behavioral.subject.data <- behavioral.data %>%
+  group_by(subject_id, relation, condition) %>%
+  summarize(hit.rate = sum(correct == TRUE & response == 't') / sum(correct_response == 't'),
+            fa.rate = sum(correct == FALSE & response == 't') / sum(correct_response == 'f')) %>%
+  mutate(accuracy = hit.rate - fa.rate)
+```
 
-```{r}
+```{r E2-average-RT}
 rt.behavioral.subject.data <- behavioral.data %>%
@@
 
-```{r}
-rt.anova <- ezANOVA(rt.behavioral.subject.data, dv=rt, wid=subject_id, within = c(relation, condition))
-rt.anova$ANOVA
+```{r E2-acc-fig}
+acc.summary.condition.data <- acc.behavioral.subject.data %>%
+  group_by(relation, condition) %>%
+  summarize(M=mean(accuracy), SE=sd(accuracy)/sqrt(n()))
+
+acc_fig<-ggplot(acc.summary.condition.data %>% 
+                 mutate(relation = factor(relation, levels = c("intra", "inter"))), 
+                        aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
+  geom_point(size=5)+
+  geom_line()+
+  geom_errorbar(width=0.2)+
+  scale_color_manual(values=c("orange2","royalblue4"))+
+  coord_cartesian(ylim=c(0.3,0.8)) +
+  labs(x="Statement Type", y="Accuracy", color=NULL)+
+  theme_classic()
 ```
 
-```{r}
+```{r E2-rt-fig}
 rt.summary.condition.data <- rt.behavioral.subject.data %>%
@@
 
-ggplot(rt.summary.condition.data, aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
+rt_fig<-ggplot(rt.summary.condition.data %>% 
+                 mutate(relation = factor(relation, levels = c("intra", "inter"))), 
+               aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
   geom_point(size=5)+
@@
 
-Goal: ANOVA with ACC as DV, condition, statement as IVs
-
-*note that paper computer accuracy as hit rate - false alarm rate*
-```{r}
-acc.behavioral.subject.data <- behavioral.data %>%
-  group_by(subject_id, relation, condition) %>%
-  summarize(hit.rate = sum(correct == TRUE & response == 't') / sum(correct_response == 't'),
-            fa.rate = sum(correct == FALSE & response == 't') / sum(correct_response == 'f')) %>%
-  mutate(accuracy = hit.rate - fa.rate)
+```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval."}
+acc_rt_fig<-acc_fig + rt_fig + plot_layout(guides = "collect")
+acc_rt_fig
 ```
 
-```{r}
+```{r E2-acc-model}
+acc.behavioral.subject.data$relation = factor(acc.behavioral.subject.data$relation)
+contrasts(acc.behavioral.subject.data$relation)<-c(-0.5,0.5)
+#contrasts(acc.behavioral.subject.data$relation)
+
+acc.behavioral.subject.data$condition = factor(acc.behavioral.subject.data$condition)
+contrasts(acc.behavioral.subject.data$condition)<-c(-0.5,0.5)
+#contrasts(acc.behavioral.subject.data$condition)
+
+E2_acc_model<-lmer(accuracy ~ relation*condition + (1|subject_id), data = acc.behavioral.subject.data)
+#summary(m1)
+E2_acc_model_tab = broom.mixed::tidy(E2_acc_model) 
+E2_acc_model_rel = E2_acc_model_tab %>% filter(term == "relation1")
+E2_acc_model_cond = E2_acc_model_tab %>% filter(term == "condition1")
+```
+
+```{r E2-rt-model}
+rt.behavioral.subject.data$relation = factor(rt.behavioral.subject.data$relation)
+contrasts(rt.behavioral.subject.data$relation)<-c(-0.5,0.5)
+#contrasts(rt.behavioral.subject.data$relation)
+
+rt.behavioral.subject.data$condition = factor(rt.behavioral.subject.data$condition)
+contrasts(rt.behavioral.subject.data$condition)<-c(-0.5,0.5)
+#contrasts(rt.behavioral.subject.data$condition)
+
+E2_RT_model<-lmer(rt ~ relation*condition + (1|subject_id), data = rt.behavioral.subject.data)
+#summary(m1)
+E2_RT_model_tab = broom.mixed::tidy(E2_RT_model) 
+E2_RT_model_rel = E2_RT_model_tab %>% filter(term == "relation1")
+E2_RT_model_cond = E2_RT_model_tab %>% filter(term == "condition")
+```
+
+__Response Time and Accuracy__.
+Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig).
+Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
+The model included random intercepts for participants^[ `lme4` syntax: `lmer(DV ~ relation_type*viewing_condition + (1|subject_id))`].
+Response times were slower for interobject (e.g., "The train is to the right of the taxi.") than intraobject (e.g., "The train is facing right.") questions (_b_ =  `r E2_RT_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
+Response times were slower in the free viewing condition than the fixed condition (_b_ =  `r E2_RT_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
+Accuracy did not differ significantly between interobject and intraobject questions (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`).
+Participants were less accurate in the free viewing condition than the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`).
+The interaction ws not a signficant predictor for response times or accuracy.
+
+```{r, eval = F}
+#Goal: ANOVA with RT as DV, condition, statement as IVs
+rt.anova <- ezANOVA(rt.behavioral.subject.data, dv=rt, wid=subject_id, within = c(relation, condition))
+rt.anova$ANOVA
+```
+
+```{r, eval = F}
 acc.anova <- ezANOVA(acc.behavioral.subject.data, dv=accuracy, wid=subject_id, within = c(relation, condition))
@@
 ```
-
-Recreate figure from paper
-
-```{r}
-acc.summary.condition.data <- acc.behavioral.subject.data %>%
-  group_by(relation, condition) %>%
-  summarize(M=mean(accuracy), SE=sd(accuracy)/sqrt(n()))
-
-ggplot(acc.summary.condition.data, aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
-  geom_point(size=5)+
-  geom_line()+
-  geom_errorbar(width=0.2)+
-  scale_color_manual(values=c("orange2","royalblue4"))+
-  coord_cartesian(ylim=c(0.3,0.8)) +
-  labs(x="Statement Type", y="Accuracy", color=NULL)+
-  theme_classic()
-```
+*Q: Can we recover item IDs to do crossed random effects*

### 2021-11-12 group-d/E4-analysis-replication.Rmd
added E2 replication analyses

@@
   geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
+  scale_fill_brewer(palette = "Set1")+
   theme_classic()+
-  labs(y = "Proportion of first mouse movements")
+  labs(y = "Proportion of first mouse movements")+
+  guides(color = guide_legend("Click location"))
 ```

### 2021-11-12 manuscript.tex
added E2 replication analyses

@@
 
-The second study was a replication attempt of Johansson and Johansson (2014).
-They examined how visuospatial information is integrated into memories for objects.
+The second study was a replication attempt of Johansson and Johansson (2014), which examined how visuospatial information is integrated into memory for objects.
 They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding (see Spivey \& Geng, 2001) and that this spatial reinstatement facilitates retrieval of the picture.
@@
 60 participants were paid \$XX for their participation .
-We analyzed the data of 59 participants, a number that was limited by budget constraints, but still 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
-We ended up excluding the data of 1 participant whose eye tracking data seemed to be blank, rendering us unable to analyze it.
+The sample size was motivated in part by budget constraints, but was nonetheless 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
+Data from 1 participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.
 
@@
 
-The task began with an -point eye-tracker calibration and validation.
 The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
@@
 \subsubsection{Replication}\label{replication-1}}
+
+\textbf{Eye-gaze}.
+Looks during the retrieval period were categorized as belonging to one of four quadrants based on the x,y coordinates.
+The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding.
+The other three quadrants were semi-randomly labeled ``first,'' ``second,'' third'' (e.g., when the critical quadrant was in the top left, the ``first'' quadrant was the top right quadrant, but when the critical quadrant was in the top right, ``first'' corresponded to bottom right, etc.).
+In the free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \ref{fig:E2-gaze-fig}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E2-gaze-fig-1.pdf}
+\caption{\label{fig:E2-gaze-fig}Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.}
+\end{figure}
+
+The proportion of looks across quadrant was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
+The model included random intercepts and slopes for participants\footnote{ \texttt{lme4} syntax: \texttt{lmer(proportion\ \textasciitilde{}\ quadrant\ +\ (1+quadrant\textbar{}subject\_id))}.
+Among other limitations, this approach may violate the independence assumptions of the linear model because looks to the four locations are not independent.
+This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.} Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E2-rt-acc-fig-1.pdf}
+\caption{\label{fig:E2-rt-acc-fig}Accuracy and response times during memory retrieval.}
+\end{figure}
+
+\textbf{Response Time and Accuracy}.
+Participants' response times and accuracies on memory questions are summarized in Figure \ref{fig:E2-rt-acc-fig}.
+Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing\_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
+The model included random intercepts for participants\footnote{ \texttt{lme4} syntax: \texttt{lmer(DV\ \textasciitilde{}\ relation\_type*viewing\_condition\ +\ (1\textbar{}subject\_id))}}.
+Response times were slower for interobject (e.g., ``The train is to the right of the taxi.'') than intraobject (e.g., ``The train is facing right.'') questions (\emph{b} = -555.60, \emph{SE} = 105.24, \emph{p}\textless0.001).
+Response times were slower in the free viewing condition than the fixed condition (\emph{b} = , \emph{SE} = , \emph{p}\textless0.001).
+Accuracy did not differ significantly between interobject and intraobject questions (\emph{b} = -0.05, \emph{SE} = 0.03, \emph{p}=0.05).
+Participants were less accurate in the free viewing condition than the fixed condition (\emph{b} = -0.06, \emph{SE} = 0.03, \emph{p}=0.03).
+The interaction ws not a signficant predictor for response times or accuracy.
+
+\emph{Q: Can we recover item IDs to do crossed random effects}
 
@@
 \caption{\label{fig:E4-gaze-timecourse-fig}Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-vertical lines indicate average onsets of animal and instrument offset by 200ms.}
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
 \end{figure}

### 2021-11-13 group-e/group-e-analysis.Rmd
added fig for E3

@@
   unnest(webgazer_data) %>%
-  unpack(webgazer_targets) %>%
-  unpack(c('#face1', '#face2'), names_sep = ".")
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(c('#face1', '#face2'), names_sep = ".")
 ```

### 2021-11-13 conference/CDS-abstract-figure.Rmd
all figures added for CDS

@@
 
-figA<-read_rds('../group-d/output/ETfig.rds')
+figA<-read_rds('../group-a/output/exp1_plot.rds')
 figB<-read_rds('../group-b/output/ETfig.rds')
-figC<-read_rds('../group-d/output/ETfig.rds')
+figC<-read_rds('../group-c/output/exp3_plot.rds')+scale_color_brewer(palette = "Set1")
 figD<-read_rds('../group-d/output/ETfig.rds')
-figE<-read_rds('../group-d/output/ETfig.rds')
+figE<-read_rds('../group-e/output/exp5_plot.rds')+scale_color_brewer(palette = "Set1")
 
+figA.1<-ggplot(figA$data, 
+               aes(x=t.window, y=cumulative.fixation.m, shape = object_class, color = verb_type))+
+  geom_point(size=1)+
+  geom_line()+
+  scale_color_brewer(palette = "Set1", name = "Verb type")+
+  scale_shape_manual(name = "Gaze location", values = c(1,4), labels = c("distractor", "target"))+
+  theme_classic()+
+  labs(x = "Time from Verb Onset", y="Cumulative Look Probability")
+figA.1
 ```
@@
 ```{r}
-A <- displayA + figA 
-B <- displayB + figB 
-C <- displayC + figC 
-D <- displayD + figD 
-E <- displayE + figE
+A <- displayA + figA.1 + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
+B <- displayB + figB + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
+C <- displayC + figC + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
+D <- displayD + figD + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
+E <- displayE + figE + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
 
@@
 ```{r}
-ggsave('CDS-abstract-figure.pdf', scale = 1, width = 12, height = 7)
+ggsave('CDS-abstract-figure.pdf', width = 11.5, height = 7)
 

### 2021-11-14 conference/CDS-abstract-figure.Rmd
added png and updated fig for CDS
added caption to CDS figure

@@
 ```{r} 
-(A | B)/(C | D ) / ( E | (grid::textGrob('Figure 1. ADD CAPTION HERE')) ) 
+caption<-"Figure 1.
+Schematic of trials and key figures for 5 replications attempts.
+(A) E1: Participants'\ncumulative proportion of looks to the target (e.g.
+cake) and distractor (e.g., train) do not differ\nsignificantly by verb type.
+(B) E2: When free viewing a blank screen during memory retrieval,\nparticipants look more to the critical quadrant where the to-be-remembered object was during\nencoding.
+(C) E3: Participants did not look significantly more to the side of the screen with\na new image (vs.
+old).
+(D) E4: Participants looked least at the target animal and most at the\ninstrument when the verb was syntactically biased toward an instrument interpretation.\n(E) E5: Participants' bias to look at the chosen face was not signficantly higher in the\nattractiveness condition (vs.
+roundness)."
+
+(A | B)/(C | D ) / ( E | (ggpubr::text_grob(caption,
+                                            hjust = "left",
+                                            vjust = "top",
+                                            size = 10)) ) 
 ```
@@
 ```{r}
-ggsave('CDS-abstract-figure.pdf', width = 11.5, height = 7)
+ggsave('CDS-abstract-figure.png', width = 11.5, height = 7)
 

### 2021-11-19 conference/CDS-abstract-figure.Rmd
minor updates to CDS abstract fig

--- 2021-11-13 conference/CDS-abstract-figure.Rmd
@@
 
-displayA<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.001.jpeg'))+coord_fixed() + ggtitle('A')
-displayB<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.002.jpeg'))+coord_fixed() + ggtitle('B')
-displayC<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.003.jpeg'))+coord_fixed() + ggtitle('C')
-displayD<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.004.jpeg'))+coord_fixed() + ggtitle('D')
-displayE<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.005.jpeg'))+coord_fixed() + ggtitle('E')
+displayA<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.001.jpeg'))+coord_fixed() + 
+  ggtitle('A') + theme(plot.title=element_text(hjust = 0.15))
+displayB<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.002.jpeg'))+coord_fixed() + 
+  ggtitle('B')+ theme(plot.title=element_text(hjust = 0.15))
+displayC<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.003.jpeg'))+coord_fixed() + 
+  ggtitle('C')+ theme(plot.title=element_text(hjust = 0.15))
+displayD<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.004.jpeg'))+coord_fixed() + 
+  ggtitle('D')+ theme(plot.title=element_text(hjust = 0.15))
+displayE<-ggplot() + background_image(image_read('expt-example-displays/expt-example-displays.005.jpeg'))+coord_fixed() + 
+  ggtitle('E')+ theme(plot.title=element_text(hjust = 0.15))
 
@@
 figB<-read_rds('../group-b/output/ETfig.rds')
-figC<-read_rds('../group-c/output/exp3_plot.rds')+scale_color_brewer(palette = "Set1")
+figC<-read_rds('../group-c/output/exp3_plot.rds')+scale_color_brewer(palette = "Set1")+
+  theme(plot.title=element_text(margin=margin(t=20,b=-15)))
 figD<-read_rds('../group-d/output/ETfig.rds')
@@
   labs(x = "Time from Verb Onset", y="Cumulative Look Probability")
-figA.1
+figC
 ```
@@
 ```{r} 
-(A | B)/(C | D ) / ( E | (grid::textGrob('Figure 1. ADD CAPTION HERE')) ) 
+caption<-"Figure 1.
+Schematic of trials and key figures for 5 replications attempts.
+(A) AK99:\nParticipants' cumulative proportion of looks to the target (e.g.
+cake) and distractor\n(e.g., train) do not differ significantly by verb type.
+(B) JJ14: When free viewing a\nblank screen during memory retrieval, participants look more to the critical quadrant\nwhere the to-be-remembered object was during encoding.
+(C) M00: Participants did\nnot look significantly more to the side of the screen with a new image (vs.
+old).\n(D) ST04: Participants looked least at the target animal and most at the instrument\nwhen the verb was syntactically biased toward an instrument interpretation.
+(E) S03:\nParticipants' bias to look at the chosen face was not signficantly higher in the\nattractiveness condition (vs.
+roundness)."
+
+(A | B)/(C | D ) / ( E | (ggpubr::text_grob(caption,
+                                            hjust = "left",
+                                            vjust = "top",
+                                            size = 11)) ) 
 ```

### 2021-11-20 group-e/group-e-analysis.Rmd
minor updates to CDS abstract fig
minor addition to grp E analysis

@@
 
+<!--re-reading the paper, I think the KS test is over fitted parameters? -RR-->
+
 ```{r}
@@
 ```
+
+alternative analyses with mixed effects models:
+<!--added these when working on CDS abstract -RR-->
+
+```{r}
+summary.gaze.view.subject$time.window.c<-scale(summary.gaze.view.subject$time.window, center=T, scale=F )
+summary(lmer(prop.in.target.subject ~ task*time.window.c + (1 + time.window.c|subject_id), data = summary.gaze.view.subject))
+```
+
+regression with lag predictor
+
+```{r}
+summary.gaze.view.subject = summary.gaze.view.subject %>% 
+  group_by(subject_id,task) %>% 
+  mutate(lag1_prop = lag(prop.in.target.subject))
+```
+
+```{r}
+summary(lmer(prop.in.target.subject ~ task + lag1_prop + (1 + lag1_prop |subject_id), data = summary.gaze.view.subject))
+```

### 2022-01-09 group-d/E4-analysis-comparison-to-original.Rmd
added data from ryskin et al 2017 for comparison to group d

---
title: "E4-analysis-comparison-to-original"
author: "Rachel Ryskin"
output: pdf_document
---

```{r , include=FALSE}
library(papaja)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)
```

```{r E4-load-web-data}
first.move = read_csv("output/E4_mouse_data.csv")
eyetracking.window.summary.by.trial = read_csv( "output/E4_eye-tracking_data.csv")
```

```{r load-data-from-original-study}

first.move.orig = read_tsv("original_study_data/Experiment1_clickData.txt")
eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_FirstTimeWindow.txt")
eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_SecondTimeWindow.txt")
eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_ThirdTimeWindow.txt")
```

```{r E4-summarizing-first-mouse-moves-for-plotting-orig}
# Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.
first.move.orig.subject.summary <- first.move.orig %>%
  group_by(subject, condition) %>%
  summarize(prop.animal = mean(clickedTargetAnimalFirst),
            prop.instrument = mean(clickedTargetInstrumentFirst),
            prop.other = mean(clickedTargetAnimalFirst == 0 & clickedTargetInstrumentFirst == 0 )) %>%
  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")

# Summarize the condition-level data for a barplot.
first.move.orig.summary <- first.move.orig.subject.summary %>%
  group_by(condition, target_type) %>%
  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
  mutate(bias = factor(condition, levels = c("Inst", "Equi", "mod") ))
```

```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in original dataset (Ryskin et al., 2017) ."}

ggplot(first.move.orig.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
  geom_col(position=position_dodge(width=0.9), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
  coord_cartesian(ylim = c(0,1))+
  theme_classic()+
  labs(y = "Proportion of first mouse movements", x = NULL)
```

### 2022-01-09 group-d/E4-analysis-replication.Rmd
added data from ryskin et al 2017 for comparison to group d

--- 2021-11-11 group-d/E4-analysis-replication.Rmd
@@
   geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
+  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
+  coord_cartesian(ylim = c(0,1))+
   theme_classic()+
-  labs(y = "Proportion of first mouse movements")
+  labs(y = "Proportion of first mouse movements", x = NULL)
+```
+
+```{r, eval=FALSE}
+write_csv(first.move, "output/E4_mouse_data.csv")
 ```
@@
 
+```{r, eval=FALSE}
+write_csv(eyetracking.window.summary.by.trial, "output/E4_eye-tracking_data.csv")
+```
+
 ```{r E4-set-contrasts-for-ET-analysis}

### 2022-01-09 manuscript.Rmd
added E2 replication analyses
added data from ryskin et al 2017 for comparison to group d

@@
 ---
-title             : "Eye-tracking on the web: lessons learned from replicating 6 experiments"
+title             : "Eye-tracking on the web: lessons learned from replicating 5 experiments"
 shorttitle        : "Just picked a random title: feel free to change"
@@
 author: 
-  - name          : "First Author"
+  - name          : "Josh de Leeuw"
     affiliation   : "1"
@@
       - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
+  - name          : "et al."
     affiliation   : "1,2"
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Vassar College"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "XX"
 
@@
  - get data from in-lab versions of group A (AJ) and group D (RR)
- - re-run Posner cueing (after we finish analysing the first 5)
- - replicate group D and ?? in lab
+ - replicate group D and A in lab
 
@@
 
-- Online data collection is more and more popular & let's us ask new questions
+- Online data collection is more and more popular & let's us ask new questions, test more diverse populations
 
@@
 
-In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
+In the present work, we attempted to replicate five eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
 The plug-in relies on the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer].
@@
 
-### Replication
+```{r E2-analysis-replication, child='group-b/E2-analysis-replication.Rmd'}
+
+```
 
@@
 
-* here we will describe a direct comparison to data collected in the lab
+```{r E4-analysis-comparsion-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}
+
+```
 

### 2022-01-09 manuscript.tex
added data from ryskin et al 2017 for comparison to group d

@@
   man,floatsintext]{apa6}
-\title{Eye-tracking on the web: lessons learned from replicating 6 experiments}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\title{Eye-tracking on the web: lessons learned from replicating 5 experiments}
+\author{Josh de Leeuw\textsuperscript{1} \& et al.\textsuperscript{1,2}}
 \date{}
@@
 \hypersetup{
-  pdftitle={Eye-tracking on the web: lessons learned from replicating 6 experiments},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
+  pdfauthor={Josh de Leeuw1 \& et al.1,2},
   pdflang={en-EN},
@@
 
-The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
+The authors made the following contributions. Josh de Leeuw: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; et al.: Writing - Review \& Editing.
 
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+Correspondence concerning this article should be addressed to Josh de Leeuw, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Vassar College\\\textsuperscript{2} XX}
 
@@
 \item
-  Online data collection is more and more popular \& let's us ask new questions
+  Online data collection is more and more popular \& let's us ask new questions, test more diverse populations
 \item
@@
 
-In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from \texttt{jsPsych}, a Javascript library for running behavioral experiments in a web browser (de Leeuw, 2015).
+In the present work, we attempted to replicate five eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from \texttt{jsPsych}, a Javascript library for running behavioral experiments in a web browser (de Leeuw, 2015).
 The plug-in relies on the \texttt{webgazer.js} library for webcam eye-tracking (Papoutsaki et al., 2016).
@@
 
-\begin{itemize}
-\tightlist
-\item
-  here we will describe a direct comparison to data collected in the lab
-\end{itemize}
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-web-and-orig-1.pdf}
+\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in original dataset (Ryskin et al., 2017) .}
+\end{figure}
 

### 2022-01-09 group-d/E4-analysis-comparison-to-original.Rmd
added graphs for comparison

@@
 first.move = read_csv("output/E4_mouse_data.csv")
-eyetracking.window.summary.by.trial = read_csv( "output/E4_eye-tracking_data.csv")
+eyetracking.window.summary.by.trial = read_csv( "output/E4_eye-tracking_data.csv") %>% 
+  rename("condition" = compatibility) %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal) %>% 
+  mutate(study = "web")
 ```
@@
 first.move.orig = read_tsv("original_study_data/Experiment1_clickData.txt")
-eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_FirstTimeWindow.txt")
-eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_SecondTimeWindow.txt")
-eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_ThirdTimeWindow.txt")
+
+eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_FirstTimeWindow.txt") %>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         #sum_dur = TA+TI+CA+CI,
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-verb-onset-pre-animal-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_SecondTimeWindow.txt")%>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-animal-onset-pre-instrument-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_ThirdTimeWindow.txt")%>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-instrument-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+```
+
+```{r E4-summarizing-first-mouse-moves-for-plotting-web}
+# Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.
+first.move.web.subject.summary <- first.move %>%
+  group_by(subject, compatibility) %>%
+  summarize(prop.animal = mean(first.move.type == 'animal'),
+            prop.instrument = mean(first.move.type == 'instrument'),
+            prop.other = mean(first.move.type == 'other')) %>%
+  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
+
+# Summarize the condition-level data for a barplot.
+first.move.web.summary <- first.move.web.subject.summary %>%
+  group_by(compatibility, target_type) %>%
+  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
+  mutate(bias = factor(compatibility, levels = c("instrument", "equibiased", "modifier") ),
+         study = "web")
 ```
@@
   summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
-  mutate(bias = factor(condition, levels = c("Inst", "Equi", "mod") ))
+  mutate(bias = factor(condition, levels = c("Inst", "Equi", "mod"), labels = c("instrument", "equibiased", "modifier") ),
+         study = "original")
 ```
 
-```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in original dataset (Ryskin et al., 2017) ."}
+In addition to qualitatively replicating the action and eye-tracking results, the quantitative patterns were similar to those observed in the dataset which was the target of replication.
 
-ggplot(first.move.orig.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
+```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online."}
+
+ggplot(bind_rows(first.move.orig.summary, first.move.web.summary), 
+       aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE, alpha = study))+
   geom_col(position=position_dodge(width=0.9), color = "black")+
@@
   scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
+  scale_alpha_manual(values = c(0.5,1))+
   coord_cartesian(ylim = c(0,1))+
   theme_classic()+
-  labs(y = "Proportion of first mouse movements", x = NULL)
+  labs(y = "Proportion of first mouse movements", x = "Bias")
 ```
+
+```{r}
+eyetracking.window.summary.by.trial.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>%
+   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" )
+```
+
+```{r}
+eyetracking.window.summary.by.subj.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>%
+   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" ) %>% 
+  group_by(study, condition, time.window, subject) %>% 
+  summarize(M = mean(prop.fixations.animal)) %>% 
+  mutate(time.window = factor(time.window, 
+                            levels = c("post-verb-onset-pre-animal-onset",
+                                       "post-animal-onset-pre-instrument-onset",
+                                       "post-instrument-onset")))
+```
+
+```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online."}
+
+ggplot(eyetracking.window.summary.by.subj.both)+
+  stat_summary(aes(x=time.window, fill=condition, y = M, alpha = study), 
+               geom = 'point', fun = 'mean', shape = 21, size = 5)+
+  stat_summary(aes(x=as.numeric(time.window), fill=condition, y = M, linetype = study), geom = 'line', fun = 'mean', alpha = 0.5)+
+  #facet_wrap(~time.window)+
+  #geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
+  #scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
+  scale_alpha_manual(values = c(0.5,1))+
+  scale_linetype_manual(values = c("dashed","solid"))+
+  coord_cartesian(ylim = c(0,1))+
+  theme_classic()+
+  labs(y = "Proportion of fixations", x = NULL)
+```
+Something funky going on with this graph...

### 2022-01-09 group-d/E4-analysis-ROIs.Rmd
started calibration and ROI analyses

---
title: "E4-analysis-ROIs"
output: pdf_document
---

```{r , include=FALSE}
library(papaja)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)
```

```{r in-box-function-ROIs}
#Define a function for determining if `x,y` value falls in box.
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

```{r E4-load-data-ROIs}
data.files <- list.files('data/run-2', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r }
task.data <- all.data %>%
  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
  dplyr::select(subject, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)

screen.data <- all.data %>%
  dplyr::select(subject, screen_height, screen_width) %>% 
  filter(!is.na(screen_height)) %>% 
  unique() %>% 
  group_by(subject) %>% 
  mutate(n()) %>% # one subject has 2 rows because width is different by less than a pixel. I'll just keep one
  sample_n(size=1)

# Add a column that uniquely identifies the combination of images and audio shown on the screen
trialID.data <- task.data %>%
  group_by(audio, images) %>%
  slice(1) %>%
  select(audio, images) %>%
  ungroup() %>%
  mutate(trialID = 1:n())

task.data <- task.data %>%
  left_join(trialID.data)

eyetracking.data <- task.data %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
  unnest(webgazer_data)

mousetracking.data <- task.data %>%
  unnest(mouse_events)
```

Coordinates need to be fixed!

```{r E4-categorizing-gaze-location-ROIs}
#First figure out which object they are looking at.
#Calculate gaze in ROIs.
eyetracking.data.with.roi <- eyetracking.data %>%
  left_join(screen.data, by = 'subject') %>% 
  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
  mutate(in.roi.0 = in.box(x,y, 0, screen_width/2, 0, screen_height/2, 0)) %>%
  mutate(in.roi.1 = in.box(x,y, screen_width/2, screen_width, 0, screen_height/2, 0)) %>%
  mutate(in.roi.2 = in.box(x,y, 0, screen_width/2, screen_height/2 , screen_height, 0)) %>%
  mutate(in.roi.3 = in.box(x,y, screen_width/2, screen_width, screen_height/2 , screen_height, 0)) %>% 
  mutate(in.roi.instrument = case_when(
    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) %>%
  mutate(in.roi.animal = case_when(
    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) 
```

```{r E4-load-audio-timing-data-ROIs, message=FALSE}
# load audio data
audio.info <- read_csv('info/audio_timing.csv')
```

```{r E4-average-onsets-of-critical-words-ROIs}
#Calculate average animal onset
animal.onset <- audio.info %>% pull(onset_noun) %>% mean()
instrument.onset <- audio.info %>% pull(onset_instrument) %>% mean()
```

```{r E4-timelocking-gaze-data-ROIs}
# Merge in audio timing information
eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
  mutate(sound = str_split(audio, pattern="/", simplify = T)[,4])

eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
  left_join(audio.info, by="sound")

# Add time window information
eyetracking.data.with.time.windows <- eyetracking.data.with.roi %>%
  mutate(time.window = case_when(
    t < onset_verb + 200 ~ "pre-verb-onset",
    t <= onset_noun + 200 ~ "post-verb-onset-pre-animal-onset",
    t <= onset_instrument + 200 ~ "post-animal-onset-pre-instrument-onset",
    t <= onset_instrument + 1500 + 200 ~ "post-instrument-onset",
    TRUE ~ "end"
  ),
  time.from.verb = t - onset_verb)
```

```{r E4-downsampling-gaze-data-for-plotting-ROIs}
#Add time window
eyetracking.data.with.time.windows <- eyetracking.data.with.time.windows %>%
  mutate(t.window = floor(time.from.verb/50)*50)
```

```{r E4-summarizing-gaze-data-for-plotting-ROIs}
#Summarize data for plotting
eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
  filter(between(t.window , -200, 4000)) %>%
  group_by(subject, compatibility, t.window) %>%
  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
  group_by(compatibility, t.window, object_type) %>%
  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
```

```{r E4-gaze-timecourse-fig-ROIs, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition. Vertical lines indicate average onsets of animal and instrument offset by 200ms."}

fig2<-ggplot(eyetracking.figure.2.data %>% 
  mutate(compatibility = factor(compatibility, 
                                levels = c("modifier", "equibiased", "instrument" ), 
                                labels = c("Modifier", "Equi-biased", "Instrument" ))), 
  aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, linetype=object_type))+
  geom_ribbon(color=NA, alpha=0.3)+
  geom_line(size=1)+
  scale_color_brewer(palette = "Set1")+
  scale_fill_brewer(palette = "Set1")+
  scale_linetype(labels = c("Animal", "Instrument") )+
  theme_classic() +
  geom_vline(xintercept = animal.onset + 200) + 
  geom_vline(xintercept = instrument.onset + 200)+
  labs(y = "Proportion of looks", x = "Time relative to verb onset (ms)")+
  guides(color = guide_legend("Verb bias"),fill = guide_legend("Verb bias"), linetype = guide_legend("Gaze location"))
fig2
```

```{r }
#Summarize fixations on target and instrument
eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
  group_by(subject, trialID, sound, compatibility, time.window) %>%
  summarize(prop.fixations.animal = sum(in.roi.animal) / n(),
            prop.fixations.instrument = sum(in.roi.instrument) / n()) %>%
  mutate(compatibility = factor(compatibility))
```

```{r }
# Add orthogonal contrasts to model
contrasts(eyetracking.window.summary.by.trial$compatibility) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
```

```{r }
data.time.window.1 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-verb-onset-pre-animal-onset")

model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.1,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))

```

```{r }
data.time.window.2 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-animal-onset-pre-instrument-onset")

model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)
```

```{r }
data.time.window.3 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-instrument-onset")

model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 | subject) + (1 | trialID), data=data.time.window.3)
```
```{r E4-ET-analysis-tables}
E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
E4_ET_model3_tab = broom.mixed::tidy(model.time.window.3)

E4_ET_model1_c1 = E4_ET_model1_tab %>% filter(term == "compatibility1")
E4_ET_model1_c2 = E4_ET_model1_tab %>% filter(term == "compatibility2")

E4_ET_model2_c1 = E4_ET_model2_tab %>% filter(term == "compatibility1")
E4_ET_model2_c2 = E4_ET_model2_tab %>% filter(term == "compatibility2")

E4_ET_model3_c1 = E4_ET_model3_tab %>% filter(term == "compatibility1")
E4_ET_model3_c2 = E4_ET_model3_tab %>% filter(term == "compatibility2")
```

### 2022-01-09 group-d/E4-analysis-calibration.Rmd
started calibration and ROI analyses

---
title: "E4-analysis-calibration"
author: "Rachel Ryskin"
output: pdf_document
---

```{r , include=FALSE}
library(papaja)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)
```

```{r }
data.files <- list.files('data/run-2', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r}

all.data.calib = all.data %>% 
  filter(trial_type == "webgazer-validate") %>% 
  dplyr::select(subject, trial_index,  percent_in_roi, average_offset) %>% 
  tidyr::unnest(percent_in_roi)

summary.data.calib = all.data.calib %>% 
  group_by(subject, trial_index) %>% 
  summarize(mean_percent_in_roi = mean(percent_in_roi)) %>% 
  group_by(subject) %>% 
  mutate(calib_num = row_number())
```

```{r}
ggplot(summary.data.calib)+
  geom_line(aes(x = calib_num, y = mean_percent_in_roi, color=subject))+
  theme_bw()+
  theme(legend.position = "none") 
```
```{r}
summary.data.calib.wide = summary.data.calib %>% 
  select(-trial_index) %>% 
  pivot_wider(id_cols = subject, names_from=calib_num, values_from = mean_percent_in_roi )

# correlation between initial and halfway calibration
ggplot(summary.data.calib.wide %>% filter(is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between 2 successive calibration attempts
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between second attempt calibration and halfway
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `2`, y = `3`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none") 
```

```{r}

calib.by.subj = summary.data.calib %>% 
  group_by(subject) %>% 
  summarize(mean_percent_in_roi = mean(mean_percent_in_roi))

eyetracking.effects.by.subj = read_csv( "output/E4_eye-tracking_data.csv") %>% 
  rename("condition" = compatibility) %>% 
  filter(time.window == "post-instrument-onset", condition != "filler" ) %>% 
  group_by(condition, time.window, subject) %>% 
  summarize(M = mean(prop.fixations.animal)) %>% 
  pivot_wider(names_from = condition, values_from = M) %>% 
  mutate(bias_effect = modifier - instrument) %>% 
  left_join(calib.by.subj, by = "subject")
```

```{r}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm")
```
```{r}
eyetracking.window.3 = read_csv( "output/E4_eye-tracking_data.csv") %>% 
  filter(time.window == "post-instrument-onset", compatibility != "filler" ) %>% 
  mutate(condition = factor(compatibility, levels = c('instrument', 'equibiased', 'modifier'))) %>% 
  left_join(calib.by.subj, by = "subject")
```

```{r }
# Add orthogonal contrasts to model
contrasts(eyetracking.window.3$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
```

```{r }

model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3)
```

```{r}
eyetracking.window.3.good.calib = eyetracking.window.3 %>% 
  filter(mean_percent_in_roi >= 50)
```

```{r }
# Add orthogonal contrasts to model
contrasts(eyetracking.window.3.good.calib$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
```

```{r }

model.time.window.3.good.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.good.calib,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3.good.calib)
```

```{r}
eyetracking.window.3.great.calib = eyetracking.window.3 %>% 
  filter(mean_percent_in_roi >= 75)
```

```{r }
# Add orthogonal contrasts to model
contrasts(eyetracking.window.3.great.calib$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
```

```{r }

model.time.window.3.great.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.great.calib,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3.great.calib)
```

### 2022-01-09 group-d/E4-analysis-comparison-to-original.Rmd
started calibration and ROI analyses

@@
 
-eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_FirstTimeWindow.txt") %>% 
+eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_verb.txt") %>% 
   mutate(subject = as.character(subj), 
@@
 
-eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_SecondTimeWindow.txt")%>% 
+eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_animal.txt")%>% 
   mutate(subject = as.character(subj), 
@@
 
-eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_ThirdTimeWindow.txt")%>% 
+eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_instrument.txt")%>% 
   mutate(subject = as.character(subj), 
@@
   stat_summary(aes(x=time.window, fill=condition, y = M, alpha = study), 
-               geom = 'point', fun = 'mean', shape = 21, size = 5)+
+               geom = 'point', fun = 'mean', shape = 21, size = 3)+
   stat_summary(aes(x=as.numeric(time.window), fill=condition, y = M, linetype = study), geom = 'line', fun = 'mean', alpha = 0.5)+
@@
   scale_linetype_manual(values = c("dashed","solid"))+
-  coord_cartesian(ylim = c(0,1))+
+  coord_cartesian(ylim = c(0,.8))+
   theme_classic()+
@@
 Something funky going on with this graph...
+
+```{r}
+orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
+  filter(condition != "filler") %>% 
+  mutate(condition = fct_drop(condition))
+contrasts(orig.data.time.window.1$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
+
+model.time.window.1 <- lmer(prop.fixations.animal ~ condition + (1 | subject) + (1 | trialID), data=orig.data.time.window.1 )
+summary(model.time.window.1)
+```
+
+```{r}
+orig.data.time.window.2 <- eyetracking.window2.summary.by.trial.orig %>% 
+  filter(condition != "filler") %>% 
+  mutate(condition = fct_drop(condition))
+contrasts(orig.data.time.window.2$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
+
+model.time.window.2 <- lmer(prop.fixations.animal ~ condition + (1 | subject) + (1 | trialID), data=orig.data.time.window.2 )
+summary(model.time.window.2)
+```
+
+```{r}
+orig.data.time.window.3 <- eyetracking.window3.summary.by.trial.orig %>% 
+  filter(condition != "filler") %>% 
+  mutate(condition = fct_drop(condition))
+contrasts(orig.data.time.window.3$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
+
+model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1 | subject) + (1 | trialID), data=orig.data.time.window.3 )
+summary(model.time.window.3)
+```
+```

### 2022-01-09 group-d/E4-analysis-replication.Rmd
started calibration and ROI analyses

@@
 Modifier: _b_ =  `r E4_ET_model1_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model1_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c2 %>% pull(p.value) %>% round(digits = 2)` ).
-In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
-In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the equi-biased relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`).
+In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition and equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the  modifier biased relative to the equi-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
+In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`).

### 2022-01-09 manuscript.Rmd
started calibration and ROI analyses

@@
 
-```{r E4-analysis-comparsion-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}
+```{r E4-analysis-comparison-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}
 
@@
 
+```{r E4-analysis-calibration, child='group-d/E4-analysis-calibration.Rmd'}
+
+```
+
 ### Effects of ROIs
@@
 * here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
+
+```{r E4-analysis-ROIs, child='group-d/E4-analysis-ROIs.Rmd'}
+
+```
 

### 2022-01-09 group-d/E4-analysis-ROIs.Rmd
new ROIs

@@
 library(jsonlite)
-library(dplyr)
-library(readr)
-library(tidyr)
-library(ggplot2)
-library(stringr)
+library(tidyverse)
 library(lmerTest)
@@
 #Calculate gaze in ROIs.
+
 eyetracking.data.with.roi <- eyetracking.data %>%
@@
   #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
-  mutate(in.roi.0 = in.box(x,y, 0, screen_width/2, 0, screen_height/2, 0)) %>%
-  mutate(in.roi.1 = in.box(x,y, screen_width/2, screen_width, 0, screen_height/2, 0)) %>%
-  mutate(in.roi.2 = in.box(x,y, 0, screen_width/2, screen_height/2 , screen_height, 0)) %>%
-  mutate(in.roi.3 = in.box(x,y, screen_width/2, screen_width, screen_height/2 , screen_height, 0)) %>% 
+  filter(x >= 0, y >= 0) %>% # negative values indicate something's incorrect (drops about 12,000 rows!!)
+  mutate(in.roi.0 = in.box(x,y, left = 0, right = screen_width/2, top = 0, bottom = screen_height/2, padding = -25)) %>%
+  mutate(in.roi.1 = in.box(x,y, left = screen_width/2, right = screen_width, top = 0, bottom = screen_height/2, padding = -25)) %>%
+  mutate(in.roi.2 = in.box(x,y, left = 0, right = screen_width/2, top = screen_height/2 , bottom = screen_height, padding = -25)) %>%
+  mutate(in.roi.3 = in.box(x,y, left = screen_width/2, right = screen_width, top = screen_height/2 , bottom = screen_height, padding = -25)) %>% 
   mutate(in.roi.instrument = case_when(
@@
     target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
-  )) 
+  )) %>% 
+  #sample_n(100) %>% 
+  rowwise() %>% 
+  mutate(roi_vec = list(c(in.roi.0, in.roi.1, in.roi.2, in.roi.3)),
+         which_roi = ifelse(sum(roi_vec)==1, which(unlist(roi_vec) == TRUE), 99 ) ) 
+```
+
+```{r}
+
+ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
+  scale_y_reverse()
+```
+```{r}
+
+ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_point(aes(x = x, y = y, color = as.factor(which_roi)), alpha = 0.5)+
+  facet_grid(compatibility~target_animal)+
+  scale_y_reverse()
 ```
@@
 eyetracking.data.with.time.windows <- eyetracking.data.with.roi %>%
+  ungroup() %>% 
+  #dplyr::slice_sample(n=100) %>% 
   mutate(time.window = case_when(
@@
   time.from.verb = t - onset_verb)
+```
+
+```{r}
+
+ggplot(eyetracking.data.with.time.windows %>% filter( time.window == "post-animal-onset-pre-instrument-onset"))+
+  geom_vline(aes(xintercept=screen_width/2))+
+  geom_hline(aes(yintercept=screen_height/2))+
+  geom_point(aes(x = x, y = y, color = as.factor(in.roi.animal)), alpha=0.5)+
+  facet_grid(compatibility~target_animal)+
+  scale_y_reverse()
+```
 ```

### 2022-01-10 group-d/E4-analysis-ROIs.Rmd
fixed ROI coordinates

--- 2022-01-09 group-d/E4-analysis-ROIs.Rmd
@@
 
-Coordinates need to be fixed!
-
 ```{r E4-categorizing-gaze-location-ROIs}
@@
   #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
-  mutate(in.roi.0 = in.box(x,y, 0, screen_width/2, 0, screen_height/2, 0)) %>%
-  mutate(in.roi.1 = in.box(x,y, screen_width/2, screen_width, 0, screen_height/2, 0)) %>%
-  mutate(in.roi.2 = in.box(x,y, 0, screen_width/2, screen_height/2 , screen_height, 0)) %>%
-  mutate(in.roi.3 = in.box(x,y, screen_width/2, screen_width, screen_height/2 , screen_height, 0)) %>% 
+  #filter(x >= 0, y >= 0) %>% # negative values indicate something's incorrect (drops about 12,000 rows!!)
+  mutate(in.roi.0 = in.box(x,y,`#jspsych-free-sort-draggable-0.left`, `#jspsych-free-sort-draggable-0.right`, `#jspsych-free-sort-draggable-0.top`, `#jspsych-free-sort-draggable-0.bottom`, 100)) %>%
+  mutate(in.roi.1 = in.box(x,y,`#jspsych-free-sort-draggable-1.left`, `#jspsych-free-sort-draggable-1.right`, `#jspsych-free-sort-draggable-1.top`, `#jspsych-free-sort-draggable-1.bottom`, 100)) %>%
+  mutate(in.roi.2 = in.box(x,y,`#jspsych-free-sort-draggable-2.left`, `#jspsych-free-sort-draggable-2.right`, `#jspsych-free-sort-draggable-2.top`, `#jspsych-free-sort-draggable-2.bottom`, 100)) %>%
+  mutate(in.roi.3 = in.box(x,y,`#jspsych-free-sort-draggable-3.left`, `#jspsych-free-sort-draggable-3.right`, `#jspsych-free-sort-draggable-3.top`, `#jspsych-free-sort-draggable-3.bottom`, 100)) %>% 
   mutate(in.roi.instrument = case_when(
@@
     target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
-  )) 
+  )) %>% 
+  #sample_n(100) %>% 
+  rowwise() %>% 
+  mutate(roi_vec = list(c(in.roi.0, in.roi.1, in.roi.2, in.roi.3)),
+         which_roi = ifelse(sum(roi_vec)==1, which(unlist(roi_vec) == TRUE), 99 ) )
+
+padding = -50
+eyetracking.data.with.quadrant.roi <- eyetracking.data %>%
+  left_join(screen.data, by = 'subject') %>% 
+  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
+  #filter(x >= 0, y >= 0) %>% # negative values indicate something's incorrect (drops about 12,000 rows!!)
+  mutate(in.roi.0 = in.box(x,y, left = 0, right = screen_width/2, top = 0, bottom = screen_height/2, padding )) %>%
+  mutate(in.roi.1 = in.box(x,y, left = screen_width/2, right = screen_width, top = 0, bottom = screen_height/2, padding )) %>%
+  mutate(in.roi.2 = in.box(x,y, left = screen_width/2, right = screen_width, top = screen_height/2 , bottom = screen_height, padding )) %>%
+  mutate(in.roi.3 = in.box(x,y, left = 0, right = screen_width/2, top = screen_height/2 , bottom = screen_height, padding )) %>% 
+  mutate(in.roi.instrument = case_when(
+    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
+    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
+    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
+    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
+  )) %>%
+  mutate(in.roi.animal = case_when(
+    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
+    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
+    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
+    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
+  )) %>% 
+  #sample_n(100) %>% 
+  rowwise() %>% 
+  mutate(roi_vec = list(c(in.roi.0, in.roi.1, in.roi.2, in.roi.3)),
+         which_roi = ifelse(sum(roi_vec)==1, which(unlist(roi_vec) == TRUE), 99 ) ) 
+```
+
+```{r}
+
+ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_text(aes(x = `#jspsych-free-sort-draggable-0.x`, y = `#jspsych-free-sort-draggable-0.y`), color = "red", label = "0")+
+  geom_text(aes(x = `#jspsych-free-sort-draggable-1.x`, y = `#jspsych-free-sort-draggable-1.y`), color = "blue", label = "1")+
+  geom_text(aes(x = `#jspsych-free-sort-draggable-2.x`, y = `#jspsych-free-sort-draggable-2.y`), color = "green", label = "2")+
+  geom_text(aes(x = `#jspsych-free-sort-draggable-3.x`, y = `#jspsych-free-sort-draggable-3.y`), color = "black", , label = "3")+
+  scale_y_reverse()
+```
+
+```{r}
+
+ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
+  scale_y_reverse()
+```
+
+```{r}
+
+ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
+  scale_y_reverse()
+```
+```{r}
+
+ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_point(aes(x = x, y = y, color = as.factor(which_roi)), alpha = 0.5)+
+  facet_grid(compatibility~target_animal)+
+  scale_y_reverse()
 ```
@@
   ),
-  time.from.verb = t - onset_verb)
+  time.from.verb = t - onset_verb, 
+  time.window = factor(time.window, levels = c("pre-verb-onset", "post-verb-onset-pre-animal-onset","post-animal-onset-pre-instrument-onset","post-instrument-onset", "end")))
+```
+
+```{r E4-timelocking-gaze-data-quadrant-ROIs}
+# Merge in audio timing information
+eyetracking.data.with.quadrant.roi <- eyetracking.data.with.quadrant.roi %>%
+  mutate(sound = str_split(audio, pattern="/", simplify = T)[,4]) %>%
+  left_join(audio.info, by="sound")
+
+# Add time window information
+eyetracking.data.with.time.windows.quadrant <- eyetracking.data.with.quadrant.roi %>%
+  ungroup() %>% 
+  #dplyr::slice_sample(n=100) %>% 
+  mutate(time.window = case_when(
+    t < onset_verb + 200 ~ "pre-verb-onset",
+    t <= onset_noun + 200 ~ "post-verb-onset-pre-animal-onset",
+    t <= onset_instrument + 200 ~ "post-animal-onset-pre-instrument-onset",
+    t <= onset_instrument + 1500 + 200 ~ "post-instrument-onset",
+    TRUE ~ "end"
+  ),
+  time.from.verb = t - onset_verb, 
+  time.window = factor(time.window, levels = c("pre-verb-onset", "post-verb-onset-pre-animal-onset","post-animal-onset-pre-instrument-onset","post-instrument-onset", "end")))
+```
+
+```{r}
+
+ggplot(eyetracking.data.with.time.windows.quadrant %>%filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>75,]$subject) %>%
+         filter(in.roi.animal)) +
+                # calib_by_subj comes from the calibration analysis rmd          
+  geom_vline(aes(xintercept=screen_width/2))+
+  geom_hline(aes(yintercept=screen_height/2))+
+  geom_point(aes(x = x, y = y), alpha=0.2)+
+  facet_grid(time.window~target_animal)+
+  scale_y_reverse()
 ```
@@
 
+```{r E4-downsampling-gaze-data-for-plotting-quadrants}
+#Add time window
+eyetracking.data.with.time.windows.quadrant <- eyetracking.data.with.time.windows.quadrant %>%
+  mutate(t.window = floor(time.from.verb/50)*50)
+```
+
 ```{r E4-summarizing-gaze-data-for-plotting-ROIs}
@@
 eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
+               filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd %>%
   filter(between(t.window , -200, 4000)) %>%
@@
 
+```{r E4-summarizing-gaze-data-for-plotting-quadrants}
+#Summarize data for plotting
+eyetracking.figure.3.data <- eyetracking.data.with.time.windows.quadrant %>%
+               filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd
+  filter(between(t.window , -200, 4000)) %>%
+  group_by(subject, compatibility, t.window) %>%
+  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
+  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
+  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
+  group_by(compatibility, t.window, object_type) %>%
+  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
+```
+
+```{r E4-gaze-timecourse-fig-ROIs, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
+Vertical lines indicate average onsets of animal and instrument offset by 200ms."}
+
+fig3<-ggplot(eyetracking.figure.3.data %>% 
+  mutate(compatibility = factor(compatibility, 
+                                levels = c("modifier", "equibiased", "instrument" ), 
+                                labels = c("Modifier", "Equi-biased", "Instrument" ))), 
+  aes(x=t.window, y=M, ymin=M-SE, ymax=M+SE, color=compatibility, fill=compatibility, linetype=object_type))+
+  geom_ribbon(color=NA, alpha=0.3)+
+  geom_line(size=1)+
+  scale_color_brewer(palette = "Set1")+
+  scale_fill_brewer(palette = "Set1")+
+  scale_linetype(labels = c("Animal", "Instrument") )+
+  theme_classic() +
+  geom_vline(xintercept = animal.onset + 200) + 
+  geom_vline(xintercept = instrument.onset + 200)+
+  labs(y = "Proportion of looks", x = "Time relative to verb onset (ms)")+
+  guides(color = guide_legend("Verb bias"),fill = guide_legend("Verb bias"), linetype = guide_legend("Gaze location"))
+fig3
+```
+
 ```{r }
 #Summarize fixations on target and instrument
-eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
+eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows.quadrant %>%
   group_by(subject, trialID, sound, compatibility, time.window) %>%
@@
 
+summary(model.time.window.1)
 ```
@@
 model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)
+
+summary(model.time.window.2)
 ```
@@
 model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 | subject) + (1 | trialID), data=data.time.window.3)
+
+summary(model.time.window.3)
 ```
+
 ```{r E4-ET-analysis-tables}

### 2022-03-29 group-c/E3-analysis-replication.Rmd
adding experiment 3 analysis markdown

---
title: "Experiment 3: Replication Analysis"
output: html_notebook
---

```{r E3 load libraries, include=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

```{r E3 load all data, include=FALSE}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r Split into day 1 and day 2, include=FALSE}
study.id.day.1.group.1 <- "6062337f1a63a6788185d0e3"
study.id.day.1.group.2 <- "607de170bb44b7e25174421f"
study.id.day.2.group.1 <- "606233c0e42b980319b6a18e"
study.id.day.2.group.2 <- "607de2837874a824e2e8c6ec"

all.data <- all.data %>%
  mutate(day = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.1.group.2), 1, 2)) %>%
  mutate(group = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.2.group.1), 1, 2))

data.day.1 <- all.data %>% filter(day == 1)
data.day.2 <- all.data %>% filter(day == 2)
```

```{r Select eyetracking data, include=FALSE}
eyetracking.data <- data.day.1 %>%
  filter(phase == "part2") %>%
  select(subject_id, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
  unpack(webgazer_targets) %>%
  unpack(c("#left-img", "#right-img"), names_sep=".") %>%
  unnest(webgazer_data)
```

```{r Add ROI information, include=FALSE}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}

eyetracking.data <- eyetracking.data %>%
  mutate(in.left.roi = in.box(x, y,`#left-img.left`, `#left-img.right`, `#left-img.top`, `#left-img.bottom`, 50))%>%
  mutate(in.right.roi = in.box(x, y,`#right-img.left`, `#right-img.right`, `#right-img.top`, `#right-img.bottom`, 50))%>%
  mutate(in.target.roi = if_else(left_image_new == TRUE, in.left.roi, in.right.roi))%>%
  mutate(in.distractor.roi = if_else(left_image_new == TRUE, in.right.roi, in.left.roi))
```

```{r Calculate looking score, include=FALSE}
looking.score.data <- eyetracking.data %>% 
  group_by(subject_id, right_image, left_image, right_image_new, left_image_new) %>%
  summarise(looking.score = if_else(sum(in.target.roi, in.distractor.roi) == 0, 0, sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi))) %>%
  mutate(image = if_else(right_image_new, left_image, right_image))
```

```{r Day 1 t-test looking scores, include=FALSE}
t.test.data1 <- looking.score.data %>%
  group_by(subject_id) %>%
  summarize(M.looking.score = mean(looking.score))

t.test.day1 <- t.test(t.test.data1$M.looking.score, mu = 0.5)
```

#### Day 1

During day 1 of the experiment, participants viewed pairs of images, one of which was always familiar and the other unfamiliar. We calculated a looking score for each participant, defined as the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI. Gaze samples that were not in either ROI were not included in this analysis. A looking score of 0.5 indicates that participants looked equally often at the familiar and unfamiliar images, while a looking score above 0.5 indicates a preference for the unfamiliar object and a looking score below 0.5 indicate a preference for the familiar object. The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`). This was not significantly different from 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.

#### Day 2

```{r Prepare Day 2 data, include=FALSE}
day2.test.data <- data.day.2 %>%
  filter(task %in% c("recognition", "confidence")) %>%
  select(subject_id, image, old_or_new, correct, rt, response, task) %>%
  pivot_wider(names_from=task, values_from=c(correct, response, rt)) %>%
  select(-correct_confidence) %>%
  mutate(response_confidence = as.numeric(response_confidence)) %>%
```

```{r Calculate accuracy of subjects, include=FALSE}
day2.accuracy <- day2.test.data %>%
  group_by(subject_id) %>%
  filter(rt_recognition <= 10000) %>%
  summarize(accuracy = mean(correct_recognition))
```

```{r Compute confidence data, include=FALSE}
confidence.test.data <- day2.test.data %>%
  filter(rt_recognition <= 10000) %>%
  group_by(subject_id, correct_recognition) %>%
  summarize(M.confidence = mean(response_confidence))

subjects.100.percent.accurate <- day2.test.data %>%
  filter(rt_recognition <= 10000) %>%
  group_by(subject_id) %>%
  summarize(accuracy = mean(correct_recognition)) %>%
  filter(accuracy == 1) %>%
  pull(subject_id)

confidence.test.data.filtered <- confidence.test.data %>%
  filter(!subject_id %in% subjects.100.percent.accurate)

confidence.t.test <- t.test(M.confidence ~ correct_recognition, data=confidence.test.data.filtered, paired=T)
```

```{r Compute RT data, include=FALSE}
rt.test.data <- day2.test.data %>%
  filter(rt_recognition <= 10000) %>%
  group_by(subject_id, correct_recognition) %>%
  summarize(M.rt = mean(rt_recognition))

rt.test.data.filtered <- rt.test.data %>%
  filter(!subject_id %in% subjects.100.percent.accurate)

rt.t.test <- t.test(M.rt ~ correct_recognition, data=rt.test.data.filtered, paired=T)
```

In all of these analyses, we excluded the `r day2.test.data %>% filter(rt_recognition > 10000) %>% nrow()` (out of `r day2.test.data %>% nrow()`) trials where the response time for the recognition judgment was greater than 10 seconds.

Participants correctly identified whether the image was familiar or unfamiliar `r mean(day2.accuracy$accuracy)*100`% (*SD* = `r sd(day2.accuracy$accuracy*100)`) of the time. After excluding the `r length(subjects.100.percent.accurate)` participants who responded correctly to all images, the average confidence rating for correct responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% sd()`) was significantly higher than their average confidence ratings for incorrect responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% sd()`), t(`r confidence.t.test$parameter`) = `r confidence.t.test$statistic`, p = `r confidence.t.test$p.value` . Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`.

```{r Calculate Looking Score Correlations, include=FALSE}
looking.plus.behavioral <- left_join(looking.score.data, day2.test.data)

looking.confidence.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  filter(rt_recognition <= 10000) %>%
  group_by(subject_id) %>%
  summarize(pearson.r = cor(looking.score, response_confidence)) %>%
  mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

looking.confidence.correlations.subjects.filtered <- looking.confidence.correlations.subjects %>%
  filter(!is.na(pearson.r))

looking.confidence.correlation.t.test <- t.test(looking.confidence.correlations.subjects.filtered$r.to.z)

looking.rt.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  filter(rt_recognition <= 10000) %>%
  group_by(subject_id) %>%
  summarize(pearson.r = cor(looking.score, rt_recognition)) %>%
  mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

looking.rt.correlations.subjects.filtered <- looking.rt.correlations.subjects %>%
  filter(!is.na(pearson.r))

looking.rt.correlation.t.test <-t.test(looking.rt.correlations.subjects.filtered$r.to.z)
```

To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on day 2, we computed the correlation coefficient between day 1 looking scores and day 2 confidence/RT for each participant. Following the original analysis, we transformed these values using the Fisher p-to-z transformation. Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

```{r Plot Looking Score Correlations, echo=FALSE}
ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
  geom_point()+
  theme_bw()
```

### 2022-04-01 group-d/E4-analysis-ROIs.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

@@
 library(broom.mixed)
+library(patchwork)
 ```
@@
 
-padding = -50
+padding = 0
 eyetracking.data.with.quadrant.roi <- eyetracking.data %>%
@@
 
-```{r}
+```{r, eval = F}
 
@@
 
-```{r}
+Eye-tracking on the web differs critically from in-lab eye-tracking in that the size of the display differs across participants.
+Thus the size of the ROIs differs across participants.
+The current version of the web experiment used a bounding box around each image to determine the ROI.
+This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as show in Figure \@ref(fig:E4-example-subj-looks-ROI)a.
+Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \@ref(fig:E4-example-subj-looks-ROI)b).
 
-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
+Magenta points indicate looks that were not categorized into an ROI"}
+p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
   geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
-  scale_y_reverse()
+  scale_y_reverse()+
+  theme_bw()+
+  theme(legend.position = "none")
+p_quad<-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
+  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
+  scale_y_reverse()+ 
+  theme_bw()+
+  theme(legend.position = "none")
+
+p_box + p_quad + plot_annotation(tag_levels = 'a')
 ```
 
-```{r}
-
-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
-  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
-  scale_y_reverse()
-```
-```{r}
+```{r, eval = F}
 
@@
 
-```{r E4-average-onsets-of-critical-words-ROIs}
+```{r }
 #Calculate average animal onset
@@
 
-```{r}
+```{r, eval = F}
 
-ggplot(eyetracking.data.with.time.windows.quadrant %>%filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>75,]$subject) %>%
+ggplot(eyetracking.data.with.time.windows.quadrant %>%
+         # filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>75,]$subject) %>%
          filter(in.roi.animal)) +
@@
 eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
-               filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd %>%
+              # filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd %>%
   filter(between(t.window , -200, 4000)) %>%
@@
 
-```{r E4-gaze-timecourse-fig-ROIs, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-Vertical lines indicate average onsets of animal and instrument offset by 200ms."}
+```{r , eval = F}
 
@@
 eyetracking.figure.3.data <- eyetracking.data.with.time.windows.quadrant %>%
-               filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd
+             #  filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd
   filter(between(t.window , -200, 4000)) %>%
@@
 
-```{r E4-gaze-timecourse-fig-ROIs, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
+```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
 Vertical lines indicate average onsets of animal and instrument offset by 200ms."}
@@
 ```{r }
-data.time.window.1 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-verb-onset-pre-animal-onset")
-
-model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.1,
-                            control = lmerControl(optimizer = "bobyqa",
-                                                  optCtrl = list(maxfun = 2e6)))
-
-summary(model.time.window.1)
-```
-
-```{r }
-data.time.window.2 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-animal-onset-pre-instrument-onset")
-
-model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)
-
-summary(model.time.window.2)
-```
-
-```{r }
 data.time.window.3 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-instrument-onset")
@@
 
-summary(model.time.window.3)
+#summary(model.time.window.3)
 ```
 
-```{r E4-ET-analysis-tables}
-E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
-E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
+```{r }
+#E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
+#E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
 E4_ET_model3_tab = broom.mixed::tidy(model.time.window.3)
-
-E4_ET_model1_c1 = E4_ET_model1_tab %>% filter(term == "compatibility1")
-E4_ET_model1_c2 = E4_ET_model1_tab %>% filter(term == "compatibility2")
-
-E4_ET_model2_c1 = E4_ET_model2_tab %>% filter(term == "compatibility1")
-E4_ET_model2_c2 = E4_ET_model2_tab %>% filter(term == "compatibility2")
 
@@
 ```
+
+Categorizing gaze location based on which of the four quadrants of the screen the coordinates fell in, increases the overall proportions of fixations (see Figure \@ref(fig:E4-gaze-timecourse-fig-quadrants)).
+In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).
+Effect size estimates appeared somewhat larger and noise was somewhat reduced when using the quadrant categorization relative to the bounding box-based ROIs.

### 2022-04-01 group-d/E4-analysis-calibration.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

@@
 
-```{r}
+```{r, eval = F}
 ggplot(summary.data.calib)+
@@
 ```
-```{r}
+```{r, eval=F}
 summary.data.calib.wide = summary.data.calib %>% 
@@
   left_join(calib.by.subj, by = "subject")
+
 ```
-
-```{r}
+```{r, eval = F}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
@@
 
+```{r,eval=F}
+write_csv(calib.by.subj,"output/calib_by_subj.csv")
+```
+
 ```{r}
+
+m_calib = broom::tidy(lm(bias_effect ~ mean_percent_in_roi, data = eyetracking.effects.by.subj))
+#m_calib 
+```
+
+```{r}
+m_calib_b = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(estimate ) %>% round(digits = 3)
+m_calib_se = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(std.error ) %>% round(digits = 3)
+m_calib_p = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(p.value ) %>% round(digits = 3)
+```
+
+```{r, eval = F}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
@@
 ```
+Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)`).
+The quality of a participant's calibration significantly predicted the participant's effect size. 
+The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration ($b=$`r m_calib_b`,$SE=$`r m_calib_se`, $p=$`r m_calib_p`).
+
 ```{r}
@@
 
-```{r }
+```{r , eval = F}
 
-model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3,
+model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1 +condition | subject) + (1 | trialID), data=eyetracking.window.3,
                             control = lmerControl(optimizer = "bobyqa",
@@
 
-model.time.window.3.good.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.good.calib,
+m.good.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.good.calib,
                             control = lmerControl(optimizer = "bobyqa",
                                                   optCtrl = list(maxfun = 2e6)))
-summary(model.time.window.3.good.calib)
+#summary(m.good.calib)
+
+m_calib_good = broom.mixed::tidy(m.good.calib)
+
+m_calib_good_c1 = m_calib_good %>% filter(term == "condition1")
+m_calib_good_c2 = m_calib_good %>% filter(term == "condition2")
+
 ```
+
+Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
+Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 
-model.time.window.3.great.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.great.calib,
+m.great.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.great.calib,
                             control = lmerControl(optimizer = "bobyqa",
                                                   optCtrl = list(maxfun = 2e6)))
-summary(model.time.window.3.great.calib)
+#summary(m.great.calib)
+m_calib_great = broom.mixed::tidy(m.great.calib)
+
+m_calib_great_c1 = m_calib_great %>% filter(term == "condition1")
+m_calib_great_c2 = m_calib_great %>% filter(term == "condition2")
 ```
+
+Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 19 participants with calibration quality >75% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
+Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_great_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_great_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_great_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_great_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_great_c2 %>% pull(p.value) %>% round(digits = 2)`).

### 2022-04-01 group-d/E4-analysis-comparison-to-original.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

@@
 
-In addition to qualitatively replicating the action and eye-tracking results, the quantitative patterns were similar to those observed in the dataset which was the target of replication.
+The web version of the study qualitatively replicates the action and eye-tracking results of the original dataset [@ryskinVerbBiasesAre2017]. 
+The mouse click results from both studies are summarized in Figure \@ref(fig:E4-mouse-moves-fig-web-and-orig).
+The quantitative patterns of clicks were similar to those observed in the original dataset, though for Instrument-biased verbs, clicks were closer to evenly split between the animal and the instrument relative to the in-lab study where they were very clearly biased toward the instrument.
 
@@
 
+The eye-tracking results from both studies are summarized in Figure \@ref(fig:E4-proportion-fix-by-window-both). 
+For simplicity, and to reflect the dependent variable used in analyses, we average the proportion of fixations to the target animal within each time window.
+Though the qualitative patterns are replicated, proportions of fixations to the target animal were much lower in the web version of the study. 
+This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.
+
 ```{r}
@@
   group_by(study, condition, time.window, subject) %>% 
-  summarize(M = mean(prop.fixations.animal)) %>% 
+  summarize(mean_prop = mean(prop.fixations.animal, na.rm = T)) %>% 
   mutate(time.window = factor(time.window, 
@@
                                        "post-animal-onset-pre-instrument-onset",
-                                       "post-instrument-onset")))
+                                       "post-instrument-onset"),
+                            labels = c('Verb to animal \n("Rub the")',
+                                       'Animal onset\n("frog with the")',
+                                       'Instrument+1500ms\n(feather...")')),
+         condition  = factor(condition, 
+                             levels = c("modifier", "equibiased", "instrument"), 
+                             labels = c("Modifier", "Equi-biased", "Instrument"))
+         ) %>% 
+  ungroup()
+
+eyetracking.window.summary.both = eyetracking.window.summary.by.subj.both %>% 
+  group_by(study, condition, time.window) %>% 
+  summarize(mean_prop = mean(mean_prop, na.rm = T), 
+            se_prop = sd(mean_prop, na.rm = T)/sqrt(n()))
+
 ```
 
-```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online."}
+```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
+Error bars reflect bootstrapped 95% CIs over subject means"}
 
 ggplot(eyetracking.window.summary.by.subj.both)+
-  stat_summary(aes(x=time.window, fill=condition, y = M, alpha = study), 
-               geom = 'point', fun = 'mean', shape = 21, size = 3)+
-  stat_summary(aes(x=as.numeric(time.window), fill=condition, y = M, linetype = study), geom = 'line', fun = 'mean', alpha = 0.5)+
+  stat_summary(aes(x=time.window, color=condition, y = mean_prop, shape = study), 
+               geom = 'point', fun = 'mean', size = 3)+
+ stat_summary(aes(x=as.numeric(time.window), y = mean_prop, linetype = study, group=paste(condition, study) ),
+             geom = 'line', fun = 'mean', alpha = 0.5, color = "grey")+
+  stat_summary(aes(x=as.numeric(time.window), y = mean_prop, color = condition, group = paste(condition , study)), 
+                geom = 'errorbar', fun.data = 'mean_cl_boot', width = 0.05)+
   #facet_wrap(~time.window)+
-  #geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
-  #scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
-  scale_alpha_manual(values = c(0.5,1))+
+  scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values = c(1,16))+
   scale_linetype_manual(values = c("dashed","solid"))+
@@
 ```
-Something funky going on with this graph...
-
-```{r}
+```{r, eval  = F}
 orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
@@
 
-```{r}
+```{r, eval  = F}
 orig.data.time.window.2 <- eyetracking.window2.summary.by.trial.orig %>% 
@@
 
-```{r}
+```{r, eval  = F}
 orig.data.time.window.3 <- eyetracking.window3.summary.by.trial.orig %>% 
@@
 ```
-```

### 2022-04-01 group-d/E4-analysis-replication.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

@@
 Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
-Figure \@ref(fig:E4-gaze-timecourse-fig) suggests that the participants made more fixations to the target animal when the verb was modifier-biased...
+Figure \@ref(fig:E4-gaze-timecourse-fig) suggests that the participants made more fixations to the target animal when the verb was modifier-biased compared to when the the verb was equi-biased and they looked at the target animal least when the verb was instrument-biased.
+The pattern was reversed for looks to the target instrument.
 
@@
 In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition and equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the  modifier biased relative to the equi-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
-In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c1 %>% pull(p.value) %>% round(digits = 2)`).
+In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).

### 2022-04-01 manuscript.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

@@
 r_refs("references.bib")
+
+colorize <- function(x, color) { # for adding colored text (e.g., for notes to self)
+  if (knitr::is_latex_output()) {
+    sprintf("\\textcolor{%s}{%s}", color, x)
+  } else if (knitr::is_html_output()) {
+    sprintf("<span style='color: %s;'>%s</span>", color,
+      x)
+  } else x
+}
 ```
@@
 
-*TO DO*: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+`r colorize("TO DO: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.", color = "red")`
 
@@
 
-* here we will describe the analyses that correlate calibration quality with effect size at the level of the individual
-
 ```{r E4-analysis-calibration, child='group-d/E4-analysis-calibration.Rmd'}
@@
 ### Effects of ROIs
-
-* here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
 

### 2022-04-01 manuscript.tex
added calibration, comparison to original, and ROI analysis for E4 to manuscript

@@
 
-We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 1.0.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.7; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.4; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 2.0.2; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.7.1; Chang et al.
-(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, and \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]} for all our analyses.
+We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 1.0.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.7; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.4; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 2.1.1; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.7.1; Chang et al.
+(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]}, and \emph{tinylabels} (Barth, 2022) for all our analyses.
 
@@
 
-\emph{TO DO}: ADD FIGURES Figure 1: An example of a critical trial for the sentence ``Rub the butterfly with the crayon.'' The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+\textcolor{red}{TO DO: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}
 
@@
 Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
-Figure \ref{fig:E4-gaze-timecourse-fig} suggests that the participants made more fixations to the target animal when the verb was modifier-biased\ldots{}
+Figure \ref{fig:E4-gaze-timecourse-fig} suggests that the participants made more fixations to the target animal when the verb was modifier-biased compared to when the the verb was equi-biased and they looked at the target animal least when the verb was instrument-biased.
+The pattern was reversed for looks to the target instrument.
 
@@
 In the \emph{verb-to-noun} window, participants did not look more at the target animal in any of the verb bias conditions (Instrument vs.~Equi and Modifier: \emph{b} = -0.01, \emph{SE} = 0.02, \emph{p} = 0.59; Equi vs.~Modifier: \emph{b} = 0, \emph{SE} = 0.02, \emph{p} = 1 ).
-In the \emph{noun-to-instrument} window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( \emph{b} = 0.03, \emph{SE} = 0.01, \emph{p} \textless{} 0.01) and in the equi-biased relative to the instrument-biased condition ( \emph{b} = 0.02, \emph{SE} = 0.01, \emph{p} \textless{} 0.05).
-In the \emph{post-instrument} window, participants looked more at the target animal in the modifier-biased condition relative to the equi-biased and instrument-biased condition ( \emph{b} = 0.08, \emph{SE} = 0.02, \emph{p} \textless{} 0.01) but not significantly so in the equi-biased relative to the instrument-biased condition ( \emph{b} = 0.03, \emph{SE} = 0.02, \emph{p} = 0.59).
+In the \emph{noun-to-instrument} window, participants looked more at the target animal in the modifier-biased condition and equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.03, \emph{SE} = 0.01, \emph{p} \textless{} 0.01) and in the modifier biased relative to the equi-biased condition ( \emph{b} = 0.02, \emph{SE} = 0.01, \emph{p} \textless{} 0.05).
+In the \emph{post-instrument} window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.08, \emph{SE} = 0.02, \emph{p} \textless{} 0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition ( \emph{b} = 0.03, \emph{SE} = 0.02, \emph{p} = 0.15).
 
@@
 
+The web version of the study qualitatively replicates the action and eye-tracking results of the original dataset (Ryskin et al., 2017).
+The mouse click results from both studies are summarized in Figure \ref{fig:E4-mouse-moves-fig-web-and-orig}.
+The quantitative patterns of clicks were similar to those observed in the original dataset, though for Instrument-biased verbs, clicks were closer to evenly split between the animal and the instrument relative to the in-lab study where they were very clearly biased toward the instrument.
+
 \begin{figure}
@@
 \includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-web-and-orig-1.pdf}
-\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in original dataset (Ryskin et al., 2017) .}
+\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.}
+\end{figure}
+
+The eye-tracking results from both studies are summarized in Figure \ref{fig:E4-proportion-fix-by-window-both}.
+For simplicity, and to reflect the dependent variable used in analyses, we average the proportion of fixations to the target animal within each time window.
+Though the qualitative patterns are replicated, proportions of fixations to the target animal were much lower in the web version of the study.
+This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-proportion-fix-by-window-both-1.pdf}
+\caption{\label{fig:E4-proportion-fix-by-window-both}Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
+Error bars reflect bootstrapped 95\% CIs over subject means}
 \end{figure}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  here we will describe the analyses that correlate calibration quality with effect size at the level of the individual
-\end{itemize}
+Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (2.22 and 97.36).
+The quality of a participant's calibration significantly predicted the participant's effect size.
+The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (\$b=\(0.00,\)SE=\$0.00, \$p=\$0.03).
+
+Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality \textgreater50\% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
+Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.10, \emph{SE} = 0.02, \emph{p} \textless{} 0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( \emph{b} = 0.02, \emph{SE} = 0.02, \emph{p} = 0.29).
+
+Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 19 participants with calibration quality \textgreater75\% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
+Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.11, \emph{SE} = 0.03, \emph{p} \textless{} 0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( \emph{b} = 0.05, \emph{SE} = 0.03, \emph{p} = 0.13).
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  here we will describe how results change depending on the size of the ROIs (using the image vs the screen quadrant)
-\end{itemize}
+Eye-tracking on the web differs critically from in-lab eye-tracking in that the size of the display differs across participants.
+Thus the size of the ROIs differs across participants.
+The current version of the web experiment used a bounding box around each image to determine the ROI.
+This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as show in Figure \ref{fig:E4-example-subj-looks-ROI}a.
+Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \ref{fig:E4-example-subj-looks-ROI}b).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-example-subj-looks-ROI-1.pdf}
+\caption{\label{fig:E4-example-subj-looks-ROI}Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
+Magenta points indicate looks that were not categorized into an ROI}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-quadrants-1.pdf}
+\caption{\label{fig:E4-gaze-timecourse-fig-quadrants}Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
+\end{figure}
+
+Categorizing gaze location based on which of the four quadrants of the screen the coordinates fell in, increases the overall proportions of fixations (see Figure \ref{fig:E4-gaze-timecourse-fig-quadrants}).
+In the \emph{post-instrument} window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.08, \emph{SE} = 0.02, \emph{p} \textless{} 0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( \emph{b} = 0.04, \emph{SE} = 0.02, \emph{p} = 0.05).
+Effect size estimates appeared somewhat larger and noise was somewhat reduced when using the quadrant categorization relative to the bounding box-based ROIs.
 
@@
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
 

### 2022-04-01 group-d/E4-analysis-calibration.Rmd
minor fix to  manuscript

@@
 
-m_calib = broom::tidy(lm(bias_effect ~ mean_percent_in_roi, data = eyetracking.effects.by.subj))
+m_calib = broom::tidy(cor.test(eyetracking.effects.by.subj$mean_percent_in_roi, eyetracking.effects.by.subj$bias_effect))
 #m_calib 
@@
 ```{r}
-m_calib_b = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(estimate ) %>% round(digits = 3)
-m_calib_se = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(std.error ) %>% round(digits = 3)
-m_calib_p = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(p.value ) %>% round(digits = 3)
+m_calib_r = m_calib %>% pull(estimate )
+
 ```
@@
 ```
-Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)`).
-The quality of a participant's calibration significantly predicted the participant's effect size. 
-The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration ($b=$`r m_calib_b`,$SE=$`r m_calib_se`, $p=$`r m_calib_p`).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %).
+The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
+The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration
 

### 2022-04-01 manuscript.tex
minor fix to  manuscript

@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (2.22 and 97.36).
-The quality of a participant's calibration significantly predicted the participant's effect size.
-The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (\$b=\(0.00,\)SE=\$0.00, \$p=\$0.03).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within \textcolor{red}{XX} pixels of the calibration point, varied substantially (between 2.22 and 97.36 \%).
+The quality of a participant's calibration significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.29, \emph{p} \textless{} 0.05).
+The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration
 

### 2022-04-02 group-b/E2-analysis-calibration.Rmd
added E2 analyses to manuscript

---
title: "Group B Analysis - Calibration"
output: pdf_document
---

```{r message=FALSE}
library(jsonlite)
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(lmerTest)
library(broom.mixed)
```

<!--Read JSON files and bind together into a tibble.-->

```{r}
data.files <- list.files('data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r}

all.data.calib = all.data %>% 
  filter(trial_type == "webgazer-validate") %>% 
  dplyr::select(subject_id, trial_index,  percent_in_roi, average_offset) %>% 
  tidyr::unnest(percent_in_roi)

summary.data.calib = all.data.calib %>% 
  group_by(subject_id, trial_index) %>% 
  summarize(mean_percent_in_roi = mean(percent_in_roi)) %>% 
  group_by(subject_id) %>% 
  mutate(calib_num = row_number())
```

```{r, eval = F}
ggplot(summary.data.calib)+
  geom_line(aes(x = calib_num, y = mean_percent_in_roi, color=subject_id))+
  theme_bw()+
  theme(legend.position = "none") 
```
```{r, eval=F}
summary.data.calib.wide = summary.data.calib %>% 
  select(-trial_index) %>% 
  pivot_wider(id_cols = subject_id, names_from=calib_num, values_from = mean_percent_in_roi )

# correlation between initial and halfway calibration
ggplot(summary.data.calib.wide %>% filter(is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between 2 successive calibration attempts
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between second attempt calibration and halfway
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `2`, y = `3`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none") 
```

```{r}

calib.by.subj = summary.data.calib %>% 
  group_by(subject_id) %>% 
  summarize(mean_percent_in_roi = mean(mean_percent_in_roi))

eyetracking.effects.by.subj = read_csv( "output/E2_eye-tracking_data_subj.csv") %>% 
 # rename("condition" = compatibility) %>% 
  filter(condition == "fixed" ) %>% 
  group_by(subject_id, normalized_quadrant) %>% 
  summarize(M = mean(proportion)) %>% 
  pivot_wider(names_from = normalized_quadrant, values_from = M) %>% 
  mutate(crit_bias = critical - (first+second+third)/3 ) %>% 
  left_join(calib.by.subj, by = "subject_id")

```

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+
  geom_point()+
  geom_smooth(method = "lm")
```
```{r}

m_calib = broom::tidy(cor.test(eyetracking.effects.by.subj$mean_percent_in_roi, eyetracking.effects.by.subj$crit_bias))
#m_calib 
```

```{r}
m_calib_r = m_calib %>% pull(estimate ) 
m_calib_p = m_calib %>% pull(p.value )

```

Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.

### 2022-04-02 group-b/E2-analysis-replication.Rmd
added E2 analyses to manuscript

@@
 
+<!--Checking what was up in the fixed viewing condition-->
+<!--Grab the relevant data, unnesting webgazer observations-->
+
+```{r}
+fixed.view.data <- task.data %>%
+  filter(condition == "fixed") %>%
+  unnest(webgazer_data)
+```
+
+<!--Add quadrant information to each observation-->
+
+```{r}
+#Define a function for determining if `x,y` value falls in box.
+in.box <- function(x, y, left, right, top, bottom, padding=0){
+  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
+  return(is.in.the.box)}
+
+fixed.view.data <- fixed.view.data %>%
+  mutate(x.percent = x / width * 100, y.percent = y / height * 100) %>%
+  mutate(view_quadrant = case_when(
+    x.percent <= 50 & y.percent <= 50 ~ 'top.left',
+    x.percent > 50 & y.percent <= 50 ~ 'top.right',
+    x.percent <= 50 & y.percent > 50 ~ 'bottom.left',
+    x.percent > 50 & y.percent > 50 ~ 'bottom.right'
+  )) %>%
+  mutate(central_fix = in.box(x.percent, y.percent, 40, 60, 40, 60)) %>% 
+  mutate(normalized_quadrant = case_when(
+    quadrant == 1 & view_quadrant == 'top.left' ~ 'critical',
+    quadrant == 1 & view_quadrant == 'top.right' ~ 'first',
+    quadrant == 1 & view_quadrant == 'bottom.right' ~ 'second',
+    quadrant == 1 & view_quadrant == 'bottom.left' ~ 'third',
+
+    quadrant == 2 & view_quadrant == 'top.left' ~ 'third',
+    quadrant == 2 & view_quadrant == 'top.right' ~ 'critical',
+    quadrant == 2 & view_quadrant == 'bottom.right' ~ 'first',
+    quadrant == 2 & view_quadrant == 'bottom.left' ~ 'second',
+
+    quadrant == 3 & view_quadrant == 'top.left' ~ 'first',
+    quadrant == 3 & view_quadrant == 'top.right' ~ 'second',
+    quadrant == 3 & view_quadrant == 'bottom.right' ~ 'third',
+    quadrant == 3 & view_quadrant == 'bottom.left' ~ 'critical',
+
+    quadrant == 4 & view_quadrant == 'top.left' ~ 'second',
+    quadrant == 4 & view_quadrant == 'top.right' ~ 'third',
+    quadrant == 4 & view_quadrant == 'bottom.right' ~ 'critical',
+    quadrant == 4 & view_quadrant == 'bottom.left' ~ 'first'
+  ))
+```
+
+```{r, eval = F}
+ggplot(fixed.view.data %>% filter(subject_id == '5f7c9ab9b52d920f0aa8ab4e'))+
+  geom_point(aes(x = x, y = y, color = view_quadrant))+
+  geom_point(data = fixed.view.data %>% filter(subject_id == '5f7c9ab9b52d920f0aa8ab4e' & central_fix),
+             aes(x = x, y = y ), color = "black")+
+  scale_y_reverse()+
+  theme_bw()+
+  theme(legend.position = "none")
+
+```
+<!--Summarize how well each subject was able to follow the instructions in fixed condition-->
+
+```{r}
+fixed.view.summary.by.subj <- fixed.view.data %>%
+  group_by(subject_id) %>%
+  summarize(prop_fixed = mean(central_fix, na.rm=T))
+
+successful_fixed = fixed.view.summary.by.subj %>% filter(prop_fixed>=0.25) %>% pull(subject_id)
+#ggplot(fixed.view.summary.by.subj)+geom_histogram(aes(x=prop_fixed))
+```
+
+<!--Summarize proportion of views in each quadrant for each trial-->
+```{r}
+fixed.view.summary.trial.data <- fixed.view.data %>%
+  group_by(subject_id, trial_index, relation) %>%
+  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
+            first = sum(normalized_quadrant == 'first')/n(),
+            second = sum(normalized_quadrant == 'second')/n(),
+            third = sum(normalized_quadrant == 'third')/n()) %>%
+  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
+```
+<!--Summarize by subject-->
+```{r}
+fixed.view.summary.subject.data <- fixed.view.summary.trial.data %>%
+  group_by(subject_id,relation,normalized_quadrant) %>%
+  summarize(proportion = mean(proportion))
+```
+
+<!-- all data together -->
+```{r}
+view.data <- task.data %>%
+  #filter(condition == "fixed") %>%
+  unnest(webgazer_data)
+```
+
+<!--Add quadrant information to each observation-->
+
+```{r}
+#Define a function for determining if `x,y` value falls in box.
+in.box <- function(x, y, left, right, top, bottom, padding=0){
+  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
+  return(is.in.the.box)}
+
+view.data <- view.data %>%
+  mutate(x.percent = x / width * 100, y.percent = y / height * 100) %>%
+  mutate(view_quadrant = case_when(
+    x.percent <= 50 & y.percent <= 50 ~ 'top.left',
+    x.percent > 50 & y.percent <= 50 ~ 'top.right',
+    x.percent <= 50 & y.percent > 50 ~ 'bottom.left',
+    x.percent > 50 & y.percent > 50 ~ 'bottom.right'
+  )) %>%
+  mutate(central_fix = in.box(x.percent, y.percent, 40, 60, 40, 60)) %>% 
+  mutate(normalized_quadrant = case_when(
+    quadrant == 1 & view_quadrant == 'top.left' ~ 'critical',
+    quadrant == 1 & view_quadrant == 'top.right' ~ 'first',
+    quadrant == 1 & view_quadrant == 'bottom.right' ~ 'second',
+    quadrant == 1 & view_quadrant == 'bottom.left' ~ 'third',
+
+    quadrant == 2 & view_quadrant == 'top.left' ~ 'third',
+    quadrant == 2 & view_quadrant == 'top.right' ~ 'critical',
+    quadrant == 2 & view_quadrant == 'bottom.right' ~ 'first',
+    quadrant == 2 & view_quadrant == 'bottom.left' ~ 'second',
+
+    quadrant == 3 & view_quadrant == 'top.left' ~ 'first',
+    quadrant == 3 & view_quadrant == 'top.right' ~ 'second',
+    quadrant == 3 & view_quadrant == 'bottom.right' ~ 'third',
+    quadrant == 3 & view_quadrant == 'bottom.left' ~ 'critical',
+
+    quadrant == 4 & view_quadrant == 'top.left' ~ 'second',
+    quadrant == 4 & view_quadrant == 'top.right' ~ 'third',
+    quadrant == 4 & view_quadrant == 'bottom.right' ~ 'critical',
+    quadrant == 4 & view_quadrant == 'bottom.left' ~ 'first'
+  ))
+```
+
+<!--Summarize proportion of views in each quadrant for each trial-->
+```{r}
+view.summary.trial.data <- view.data %>%
+  group_by(subject_id, condition, trial_index, relation) %>%
+  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
+            first = sum(normalized_quadrant == 'first')/n(),
+            second = sum(normalized_quadrant == 'second')/n(),
+            third = sum(normalized_quadrant == 'third')/n()) %>%
+  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
+```
+<!--Summarize by subject-->
+```{r}
+view.summary.subject.data <- view.summary.trial.data %>%
+  group_by(subject_id,relation,condition, normalized_quadrant) %>%
+  summarize(proportion = mean(proportion))
+```
+
+```{r, eval=F}
+write_csv(view.summary.subject.data, 'output/E2_eye-tracking_data_subj.csv')
+```
+
 __Eye-gaze__.
@@
 The other three quadrants were semi-randomly labeled "first", "second," third" (e.g., when the critical quadrant was in the top left, the "first" quadrant was the top right quadrant, but when the critical quadrant was in the top right, "first" corresponded to bottom right, etc.).
-In the free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \@ref(fig:E2-gaze-fig)).
+In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \@ref(fig:E2-gaze-fig-both-conds)).
+This bias appeared larger in the free-viewing condition, suggesting that the manipulation was (somewhat) effective.
 
-<!--Summarize by between condition -->
 ```{r}
@@
 
-```{r E2-gaze-fig, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval."}
+```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE}
 fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
@@
 
+```{r}
+view.summary.condition1.data <- view.summary.subject.data %>%
+  group_by(normalized_quadrant, condition) %>%
+  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
+```
+```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions."}
+
+ggplot(view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
+  geom_col(position=position_dodge(), color = "black")+
+  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
+  facet_wrap(~condition)+
+  scale_fill_brewer(palette="Set1",)+
+  theme_classic()+
+  labs(x = "Quadrant", y = "Mean proportion of looks")+
+  theme(legend.position = "none")
+
+```
+
+<!--Summarize by between condition -->
+```{r}
+fixed.view.summary.condition1.data <- fixed.view.summary.subject.data %>%
+  group_by(normalized_quadrant) %>%
+  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
+```
+
+```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F}
+fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
+  geom_col(position=position_dodge(), color = "black")+
+  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
+  scale_fill_brewer(palette="Set1",)+
+  theme_classic()+
+  labs(x = "Quadrant", y = "Mean proportion of looks")+
+  theme(legend.position = "none")
+fig.fixed
+```
+
 ```{r E2-gaze-model}
@@
 
-The proportion of looks across quadrant was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
+The proportion of looks across quadrants in the free-viewing condition was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
 The model included random intercepts and slopes for participants^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`.
-Among other limitations, this approach may violate the independence assumptions of the linear model because looks to the four locations are not independent.
+Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent.
 This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.] Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )
@@
 E2_RT_model_rel = E2_RT_model_tab %>% filter(term == "relation1")
-E2_RT_model_cond = E2_RT_model_tab %>% filter(term == "condition")
+E2_RT_model_cond = E2_RT_model_tab %>% filter(term == "condition1")
 ```
 
-__Response Time and Accuracy__.
-Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig).
+__Response Time and Accuracy__. Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig). 
 Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
 The model included random intercepts for participants^[ `lme4` syntax: `lmer(DV ~ relation_type*viewing_condition + (1|subject_id))`]. 
+Accuracy did not differ significantly between interobject and intraobject questions (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`).
+Participants were less accurate in the free viewing condition than the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`).
 Response times were slower for interobject (e.g., "The train is to the right of the taxi.") than intraobject (e.g., "The train is facing right.") questions (_b_ =  `r E2_RT_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
 Response times were slower in the free viewing condition than the fixed condition (_b_ =  `r E2_RT_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
-Accuracy did not differ significantly between interobject and intraobject questions (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`).
-Participants were less accurate in the free viewing condition than the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`).
-The interaction ws not a signficant predictor for response times or accuracy.
+The interaction was not a significant predictor for response times or accuracy.
+These behavioral results are inconsistent with the original findings.
+
+```{r E2-acc-model-good-subs}
+
+E2_acc_model2<-lmer(accuracy ~ relation*condition + (1|subject_id), 
+                   data = acc.behavioral.subject.data %>% 
+                     filter(subject_id %in% successful_fixed))
+#summary(m1)
+E2_acc_model2_tab = broom.mixed::tidy(E2_acc_model) 
+E2_acc_model2_rel = E2_acc_model_tab %>% filter(term == "relation1")
+E2_acc_model2_cond = E2_acc_model_tab %>% filter(term == "condition1")
+```
+
+```{r E2-rt-model-good-subs}
+
+E2_RT_model2<-lmer(rt ~ relation*condition + (1|subject_id), 
+                  data = rt.behavioral.subject.data %>% 
+                     filter(subject_id %in% successful_fixed))
+#summary(m1)
+E2_RT_model2_tab = broom.mixed::tidy(E2_RT_model) 
+E2_RT_model2_rel = E2_RT_model_tab %>% filter(term == "relation1")
+E2_RT_model2_cond = E2_RT_model_tab %>% filter(term == "condition1")
+```
+
+One possibility is that in-lab participants were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
+When  analyzing results from the subset of participants (N = `r length(successful_fixed)`) who were most compliant during the fixed-viewing block (at least 25% of their looks fell within 20% of the center of the display), the viewing condition effects and the interactions were not signficant.
+Given the smaller sample size we do not interpret these results further.
 
@@
 ```
-*Q: Can we recover item IDs to do crossed random effects*
+*Q: Can we recover item IDs to do crossed random effects?*

### 2022-04-02 manuscript.tex
added E2 analyses to manuscript

@@
 The other three quadrants were semi-randomly labeled ``first,'' ``second,'' third'' (e.g., when the critical quadrant was in the top left, the ``first'' quadrant was the top right quadrant, but when the critical quadrant was in the top right, ``first'' corresponded to bottom right, etc.).
-In the free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \ref{fig:E2-gaze-fig}).
+In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \ref{fig:E2-gaze-fig-both-conds}).
+This bias appeared larger in the free-viewing condition, suggesting that the manipulation was (somewhat) effective.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/E2-gaze-fig-1.pdf}
-\caption{\label{fig:E2-gaze-fig}Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.}
+\includegraphics{manuscript_files/figure-latex/E2-gaze-fig-both-conds-1.pdf}
+\caption{\label{fig:E2-gaze-fig-both-conds}Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.}
 \end{figure}
 
-The proportion of looks across quadrant was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
+The proportion of looks across quadrants in the free-viewing condition was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
 The model included random intercepts and slopes for participants\footnote{ \texttt{lme4} syntax: \texttt{lmer(proportion\ \textasciitilde{}\ quadrant\ +\ (1+quadrant\textbar{}subject\_id))}.
-Among other limitations, this approach may violate the independence assumptions of the linear model because looks to the four locations are not independent.
+Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent.
 This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.} Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
@@
 
-\textbf{Response Time and Accuracy}.
-Participants' response times and accuracies on memory questions are summarized in Figure \ref{fig:E2-rt-acc-fig}.
+\textbf{Response Time and Accuracy}. Participants' response times and accuracies on memory questions are summarized in Figure \ref{fig:E2-rt-acc-fig}.
 Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing\_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
 The model included random intercepts for participants\footnote{ \texttt{lme4} syntax: \texttt{lmer(DV\ \textasciitilde{}\ relation\_type*viewing\_condition\ +\ (1\textbar{}subject\_id))}}.
-Response times were slower for interobject (e.g., ``The train is to the right of the taxi.'') than intraobject (e.g., ``The train is facing right.'') questions (\emph{b} = -555.60, \emph{SE} = 105.24, \emph{p}\textless0.001).
-Response times were slower in the free viewing condition than the fixed condition (\emph{b} = , \emph{SE} = , \emph{p}\textless0.001).
 Accuracy did not differ significantly between interobject and intraobject questions (\emph{b} = -0.05, \emph{SE} = 0.03, \emph{p}=0.05).
 Participants were less accurate in the free viewing condition than the fixed condition (\emph{b} = -0.06, \emph{SE} = 0.03, \emph{p}=0.03).
-The interaction ws not a signficant predictor for response times or accuracy.
+Response times were slower for interobject (e.g., ``The train is to the right of the taxi.'') than intraobject (e.g., ``The train is facing right.'') questions (\emph{b} = -555.60, \emph{SE} = 105.24, \emph{p}\textless0.001).
+Response times were slower in the free viewing condition than the fixed condition (\emph{b} = 260.98, \emph{SE} = 105.24, \emph{p}\textless0.001).
+The interaction was not a significant predictor for response times or accuracy.
+These behavioral results are inconsistent with the original findings.
 
-\emph{Q: Can we recover item IDs to do crossed random effects}
+One possibility is that in-lab participants were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
+When analyzing results from the subset of participants (N = 25) who were most compliant during the fixed-viewing block (at least 25\% of their looks fell within 20\% of the center of the display), the viewing condition effects and the interactions were not signficant.
+Given the smaller sample size we do not interpret these results further.
 
-\begin{itemize}
-\item
-  here we will describe the analyses that are as close as possible to the original paper
-\item
-  same but stricter validation cutoff
-\end{itemize}
+\emph{Q: Can we recover item IDs to do crossed random effects?}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  here we will describe the analyses that correlate calibration quality with effect size at the individual level
-\end{itemize}
+Participants' calibration quality, measured as the mean percentage of fixations that landed within \textcolor{red}{XX} pixels of the calibration point, varied substantially (between 17.78 and 100 \%).
+The quality of a participant's calibration was not significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.20, \emph{p} = 0.14) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.
 
@@
 
-\hypertarget{experiment-6}{%
-\section{Experiment 6}\label{experiment-6}}
-
-The sixth study was a replication attempt of Posner et al.~??.
-
-\hypertarget{methods-5}{%
-\subsection{Methods}\label{methods-5}}
-
-\hypertarget{participants-6}{%
-\subsubsection{Participants}\label{participants-6}}
-
-\hypertarget{procedure-and-design-1}{%
-\subsubsection{Procedure and Design}\label{procedure-and-design-1}}
-
-\hypertarget{data-analysis-3}{%
-\subsubsection{Data analysis}\label{data-analysis-3}}
-
-\hypertarget{results-5}{%
-\subsection{Results}\label{results-5}}
-
-\hypertarget{replication-3}{%
-\subsubsection{Replication}\label{replication-3}}
-
-\hypertarget{calibration-3}{%
-\subsubsection{Calibration}\label{calibration-3}}
-
-\hypertarget{rois}{%
-\subsubsection{ROIs}\label{rois}}
-
-\hypertarget{item-numbers}{%
-\subsubsection{Item Numbers}\label{item-numbers}}
-
-\hypertarget{discussion-5}{%
-\subsection{Discussion}\label{discussion-5}}
-
 \hypertarget{combined-analyses}{%

### 2022-04-04 group-c/E3-analysis-roi.Rmd
add E3 ROI analysis

--- 2022-03-29 group-c/E3-analysis-replication.Rmd
@@
 ---
+
+In the original experiment, the two objects on day 1 were presented on two separate monitors and gaze was coded by manually coding video recordings.
+In our replication analysis, we analyzed eye movement data using ROIs.
+In this section we explore an alternative coding of the eye movement data by coding simply left half vs.
+right half of the screen.
 
@@
 eyetracking.data <- eyetracking.data %>%
-  mutate(in.left.roi = in.box(x, y,`#left-img.left`, `#left-img.right`, `#left-img.top`, `#left-img.bottom`, 50))%>%
-  mutate(in.right.roi = in.box(x, y,`#right-img.left`, `#right-img.right`, `#right-img.top`, `#right-img.bottom`, 50))%>%
+  mutate(midpoint.x = `#left-img.right` + (`#right-img.left` - `#left-img.right`)/2) %>%
+  mutate(in.left.roi = x < midpoint.x) %>%
+  mutate(in.right.roi = x > midpoint.x)%>%
   mutate(in.target.roi = if_else(left_image_new == TRUE, in.left.roi, in.right.roi))%>%
@@
 
-#### Day 1
+#### Looking Scores
 
-During day 1 of the experiment, participants viewed pairs of images, one of which was always familiar and the other unfamiliar.
-We calculated a looking score for each participant, defined as the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI.
-Gaze samples that were not in either ROI were not included in this analysis.
-A looking score of 0.5 indicates that participants looked equally often at the familiar and unfamiliar images, while a looking score above 0.5 indicates a preference for the unfamiliar object and a looking score below 0.5 indicate a preference for the familiar object.
+When looking scores are coded as left vs.
+right half of the screen, we do find that participants looked more at the novel object.
 The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
-This was not significantly different from 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.
+This was significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.
 
-#### Day 2
+#### Correlations with Day 2 Performance
 
@@
   select(-correct_confidence) %>%
-  mutate(response_confidence = as.numeric(response_confidence)) %>%
+  mutate(response_confidence = as.numeric(response_confidence))
 ```
-
-```{r Calculate accuracy of subjects, include=FALSE}
-day2.accuracy <- day2.test.data %>%
-  group_by(subject_id) %>%
-  filter(rt_recognition <= 10000) %>%
-  summarize(accuracy = mean(correct_recognition))
-```
-
-```{r Compute confidence data, include=FALSE}
-confidence.test.data <- day2.test.data %>%
-  filter(rt_recognition <= 10000) %>%
-  group_by(subject_id, correct_recognition) %>%
-  summarize(M.confidence = mean(response_confidence))
-
-subjects.100.percent.accurate <- day2.test.data %>%
-  filter(rt_recognition <= 10000) %>%
-  group_by(subject_id) %>%
-  summarize(accuracy = mean(correct_recognition)) %>%
-  filter(accuracy == 1) %>%
-  pull(subject_id)
-
-confidence.test.data.filtered <- confidence.test.data %>%
-  filter(!subject_id %in% subjects.100.percent.accurate)
-
-confidence.t.test <- t.test(M.confidence ~ correct_recognition, data=confidence.test.data.filtered, paired=T)
-```
-
-```{r Compute RT data, include=FALSE}
-rt.test.data <- day2.test.data %>%
-  filter(rt_recognition <= 10000) %>%
-  group_by(subject_id, correct_recognition) %>%
-  summarize(M.rt = mean(rt_recognition))
-
-rt.test.data.filtered <- rt.test.data %>%
-  filter(!subject_id %in% subjects.100.percent.accurate)
-
-rt.t.test <- t.test(M.rt ~ correct_recognition, data=rt.test.data.filtered, paired=T)
-```
-
-In all of these analyses, we excluded the `r day2.test.data %>% filter(rt_recognition > 10000) %>% nrow()` (out of `r day2.test.data %>% nrow()`) trials where the response time for the recognition judgment was greater than 10 seconds.
-
-Participants correctly identified whether the image was familiar or unfamiliar `r mean(day2.accuracy$accuracy)*100`% (*SD* = `r sd(day2.accuracy$accuracy*100)`) of the time.
-After excluding the `r length(subjects.100.percent.accurate)` participants who responded correctly to all images, the average confidence rating for correct responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% sd()`) was significantly higher than their average confidence ratings for incorrect responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% sd()`), t(`r confidence.t.test$parameter`) = `r confidence.t.test$statistic`, p = `r confidence.t.test$p.value` .
-Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`.
 
@@
 
-To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on day 2, we computed the correlation coefficient between day 1 looking scores and day 2 confidence/RT for each participant.
-Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
-Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
-
-```{r Plot Looking Score Correlations, echo=FALSE}
-ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
-  geom_point()+
-  theme_bw()
-```
+Performance on day 2 remained uncorrelated with day 1 looking scores after switching the coding of gaze.
+We found no significant different from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

### 2022-04-05 group-c/E3-analysis-replication.Rmd
add cumulative looking plot; fix looking score calculation

@@
   group_by(subject_id, right_image, left_image, right_image_new, left_image_new) %>%
-  summarise(looking.score = if_else(sum(in.target.roi, in.distractor.roi) == 0, 0, sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi))) %>%
+  summarise(looking.score = sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi)) %>%
   mutate(image = if_else(right_image_new, left_image, right_image))
@@
   group_by(subject_id) %>%
+  filter(!is.nan(looking.score)) %>%
   summarize(M.looking.score = mean(looking.score))
@@
 A looking score of 0.5 indicates that participants looked equally often at the familiar and unfamiliar images, while a looking score above 0.5 indicates a preference for the unfamiliar object and a looking score below 0.5 indicate a preference for the familiar object.
+
+Of the `r looking.score.data %>% nrow()` trials in the experiment, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI, and so the looking score was unknown.
+We removed these trials from this analysis.
+
 The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
-This was not significantly different from 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.
+This significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`, indicating that participants did show a preference for looking at the novel objects.
+
+```{r Create looking over time curve data, include=FALSE}
+
+day.1.looking.by.time <- expand.grid(subject_id = unique(eyetracking.data$subject_id), t = seq(100, 5000, 100))
+
+cumulative.looking.score <- function(subj, time){
+  return(eyetracking.data %>%
+    filter(subject_id == subj, t <= time) %>%
+    summarize(cl = sum(in.target.roi) / (sum(in.target.roi) + sum(in.distractor.roi))) %>%
+    pull(cl))
+}
+
+day.1.looking.by.time <- day.1.looking.by.time %>%
+  rowwise() %>%
+  mutate(cumulative.looks.new = cumulative.looking.score(subject_id, t))
+
+day.1.looking.by.time.summary <- day.1.looking.by.time %>%
+  group_by(t) %>%
+  filter(!is.nan(cumulative.looks.new)) %>%
+  summarize(M = mean(cumulative.looks.new), SE=sd(cumulative.looks.new) / sqrt(n()))
+```
+
+```{r Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
+  geom_pointrange()+
+  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
+```
 
@@
   select(-correct_confidence) %>%
-  mutate(response_confidence = as.numeric(response_confidence)) %>%
+  mutate(response_confidence = as.numeric(response_confidence))
 ```
@@
   filter(rt_recognition <= 10000) %>%
+  filter(!is.nan(looking.score)) %>%
   group_by(subject_id) %>%

### 2022-04-05 group-c/E3-analysis-roi.Rmd
add cumulative looking plot; fix looking score calculation

@@
 In the original experiment, the two objects on day 1 were presented on two separate monitors and gaze was coded by manually coding video recordings.
-In our replication analysis, we analyzed eye movement data using ROIs.
+In our replication analysis, we analyzed eye movement data using ROIs defined around the two images.
 In this section we explore an alternative coding of the eye movement data by coding simply left half vs.
 right half of the screen.
+The coarser coding may be more appropriate for webcam-based eyetracking.
 
@@
 This was significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.
+
+```{r Create looking over time curve data, include=FALSE}
+
+day.1.looking.by.time <- expand.grid(subject_id = unique(eyetracking.data$subject_id), t = seq(100, 5000, 100))
+
+cumulative.looking.score <- function(subj, time){
+  return(eyetracking.data %>%
+    filter(subject_id == subj, t <= time) %>%
+    summarize(cl = sum(in.target.roi) / (sum(in.target.roi) + sum(in.distractor.roi))) %>%
+    pull(cl))
+}
+
+day.1.looking.by.time <- day.1.looking.by.time %>%
+  rowwise() %>%
+  mutate(cumulative.looks.new = cumulative.looking.score(subject_id, t))
+
+day.1.looking.by.time.summary <- day.1.looking.by.time %>%
+  group_by(t) %>%
+  filter(!is.nan(cumulative.looks.new)) %>%
+  summarize(M = mean(cumulative.looks.new), SE=sd(cumulative.looks.new) / sqrt(n()))
+```
+
+```{r Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
+  geom_pointrange()+
+  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
+```
 

### 2022-04-11 group-c/E3-analysis-calibration.Rmd
update E3 analysis

---
title: "Experiment 3: Calibration Analysis"
output: html_notebook
---

```{r E3-cal load libraries, include=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

```{r E3-cal load all data, include=FALSE}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r E3-cal Split into day 1 and day 2, include=FALSE}
study.id.day.1.group.1 <- "6062337f1a63a6788185d0e3"
study.id.day.1.group.2 <- "607de170bb44b7e25174421f"
study.id.day.2.group.1 <- "606233c0e42b980319b6a18e"
study.id.day.2.group.2 <- "607de2837874a824e2e8c6ec"

all.data <- all.data %>%
  mutate(day = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.1.group.2), 1, 2)) %>%
  mutate(group = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.2.group.1), 1, 2))

data.day.1 <- all.data %>% filter(day == 1)
data.day.2 <- all.data %>% filter(day == 2)
```

```{r E3-cal Select calibration data, include=FALSE}
eyetracking.calibration.data <- data.day.1 %>%
  filter(trial_type == "webgazer-validate") %>%
  select(subject_id, trial_index, phase,  percent_in_roi, average_offset) %>% 
  unnest(percent_in_roi)

eyetracking.calibration.summary <- eyetracking.calibration.data %>% 
  group_by(subject_id, trial_index, phase) %>% 
  summarize(mean_percent_in_roi = mean(percent_in_roi)) %>% 
  group_by(subject_id) %>% 
  mutate(calib_num = row_number())

subject.calibration.score <- eyetracking.calibration.summary %>%
  filter(phase=="boost-calibration") %>%
  select(subject_id, mean_percent_in_roi)
```

```{r E3-cal Select eyetracking data, include=FALSE}
eyetracking.data <- data.day.1 %>%
  filter(phase == "part2") %>%
  select(subject_id, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c("#left-img", "#right-img"), names_sep=".") %>%
  tidyr::unnest(webgazer_data)
```

```{r E3-cal Add ROI information, include=FALSE}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}

eyetracking.data <- eyetracking.data %>%
  mutate(midpoint.x = `#left-img.right` + (`#right-img.left` - `#left-img.right`)/2) %>%
  mutate(in.left.half = x < midpoint.x) %>%
  mutate(in.right.half = x > midpoint.x)%>%
  mutate(in.target.half = if_else(left_image_new == TRUE, in.left.half, in.right.half))%>%
  mutate(in.distractor.half = if_else(left_image_new == TRUE, in.right.half, in.left.half)) %>%
  mutate(in.left.roi = in.box(x, y,`#left-img.left`, `#left-img.right`, `#left-img.top`, `#left-img.bottom`, 50))%>%
  mutate(in.right.roi = in.box(x, y,`#right-img.left`, `#right-img.right`, `#right-img.top`, `#right-img.bottom`, 50))%>%
  mutate(in.target.roi = if_else(left_image_new == TRUE, in.left.roi, in.right.roi))%>%
  mutate(in.distractor.roi = if_else(left_image_new == TRUE, in.right.roi, in.left.roi))
```

```{r E3-cal Calculate looking score, include=FALSE}
looking.score.data <- eyetracking.data %>% 
  group_by(subject_id, right_image, left_image, right_image_new, left_image_new) %>%
  summarise(looking.score.roi = sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi),
            looking.score.half = sum(in.target.half) / sum(in.target.half, in.distractor.half)) %>%
  mutate(image = if_else(right_image_new, left_image, right_image))
```

```{r E3-cal Join looking score with calibration, include=FALSE}
merged.eyetracking <- looking.score.data %>%
  group_by(subject_id) %>%
  summarize(looking.score.M.roi = mean(looking.score.roi),
            looking.score.M.half = mean(looking.score.half))%>%
  left_join(subject.calibration.score, by=c("subject_id"))
```

To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant. The calibration score was the average proportion of samples within XXX pixels of the validation points during the final validation phase before the eye tracking is performed.

Calibration scores were not correlated with looking scores, regardless of which method was used to calculate looking scores.

```{r E3-cal Plot looking score (halves) by calibration, echo=FALSE}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (Halves)")
```

```{r E3-cal Plot looking score (roi) by calibration, echo=FALSE, warning=FALSE}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (ROIs)")
```

```{r E3-cal Prepare Day 2 data, include=FALSE}
day2.test.data <- data.day.2 %>%
  filter(task %in% c("recognition", "confidence")) %>%
  select(subject_id, image, old_or_new, correct, rt, response, task) %>%
  pivot_wider(names_from=task, values_from=c(correct, response, rt)) %>%
  select(-correct_confidence) %>%
  mutate(response_confidence = as.numeric(response_confidence))
```

```{r E3-cal Calculate Looking Score Correlations, include=FALSE}
looking.plus.behavioral <- left_join(looking.score.data, day2.test.data)

looking.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  filter(rt_recognition <= 10000) %>%
  group_by(subject_id) %>%
  summarize(pearson.r.conf.roi = cor(looking.score.roi, response_confidence),
            pearson.r.rt.roi = cor(looking.score.roi, rt_recognition),
            pearson.r.conf.half = cor(looking.score.half, response_confidence),
            pearson.r.rt.half = cor(looking.score.half, rt_recognition)
            ) %>%
  mutate(r.to.z.conf.roi = .5*(log(1+pearson.r.conf.roi) - log(1 - pearson.r.conf.roi)),
         r.to.z.rt.roi = .5*(log(1+pearson.r.rt.roi) - log(1 - pearson.r.rt.roi)),
         r.to.z.conf.half = .5*(log(1+pearson.r.conf.half) - log(1 - pearson.r.conf.half)),
         r.to.z.rt.half = .5*(log(1+pearson.r.rt.half) - log(1 - pearson.r.rt.half)))

looking.correlations.subjects.tidy <- looking.correlations.subjects %>%
  select(subject_id, r.to.z.conf.half, r.to.z.conf.roi, r.to.z.rt.roi, r.to.z.rt.half) %>%
  pivot_longer(2:5, names_to = "measure", values_to = "z") %>%
  mutate(behavioral_measure = case_when(
    measure %in% c("r.to.z.conf.half", "r.to.z.conf.roi") ~ "confidence",
    measure %in% c("r.to.z.rt.half", "r.to.z.rt.roi") ~ "rt",
  )) %>%
  mutate(looking_measure = case_when(
    measure %in% c("r.to.z.conf.roi", "r.to.z.rt.roi") ~ "roi",
    measure %in% c("r.to.z.rt.half", "r.to.z.conf.half") ~ "half",
  )) %>%
  select(subject_id, behavioral_measure, looking_measure, z) %>%
  left_join(subject.calibration.score, by=c("subject_id"))
```

We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures. None of the four relationships showed a significant correlation.

```{r E3-cal Plot correlations with calibration.score, echo=FALSE, warning=FALSE}
ggplot(looking.correlations.subjects.tidy, aes(x=mean_percent_in_roi, y=z))+
  geom_point()+
  geom_smooth(method="lm", formula=y~x)+
  facet_grid(behavioral_measure ~ looking_measure)

```

### 2022-04-11 group-c/E3-analysis-replication.Rmd
update E3 analysis

@@
   select(subject_id, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
-  unpack(webgazer_targets) %>%
-  unpack(c("#left-img", "#right-img"), names_sep=".") %>%
-  unnest(webgazer_data)
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(c("#left-img", "#right-img"), names_sep=".") %>%
+  tidyr::unnest(webgazer_data)
 ```

### 2022-04-11 group-c/E3-analysis-roi.Rmd
update E3 analysis

@@
 ---
-title: "Experiment 3: Replication Analysis"
+title: "Experiment 3: ROI Analysis"
 output: html_notebook
@@
 
-```{r E3 load libraries, include=FALSE}
+```{r E3-roi load libraries, include=FALSE}
 library(dplyr)
@@
 
-```{r E3 load all data, include=FALSE}
+```{r E3-roi load all data, include=FALSE}
 data.files <- list.files('data', full.names = TRUE)
@@
 
-```{r Split into day 1 and day 2, include=FALSE}
+```{r E3-roi Split into day 1 and day 2, include=FALSE}
 study.id.day.1.group.1 <- "6062337f1a63a6788185d0e3"
@@
 
-```{r Select eyetracking data, include=FALSE}
+```{r E3-roi Select eyetracking data, include=FALSE}
 eyetracking.data <- data.day.1 %>%
@@
   select(subject_id, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
-  unpack(webgazer_targets) %>%
-  unpack(c("#left-img", "#right-img"), names_sep=".") %>%
-  unnest(webgazer_data)
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(c("#left-img", "#right-img"), names_sep=".") %>%
+  tidyr::unnest(webgazer_data)
 ```
 
-```{r Add ROI information, include=FALSE}
+```{r E3-roi Add ROI information, include=FALSE}
 in.box <- function(x, y, left, right, top, bottom, padding){
@@
   mutate(midpoint.x = `#left-img.right` + (`#right-img.left` - `#left-img.right`)/2) %>%
-  mutate(in.left.roi = x < midpoint.x) %>%
-  mutate(in.right.roi = x > midpoint.x)%>%
+  mutate(in.left.half = x < midpoint.x) %>%
+  mutate(in.right.half = x > midpoint.x)%>%
+  mutate(in.target.half = if_else(left_image_new == TRUE, in.left.half, in.right.half))%>%
+  mutate(in.distractor.half = if_else(left_image_new == TRUE, in.right.half, in.left.half)) %>%
+  mutate(in.left.roi = in.box(x, y,`#left-img.left`, `#left-img.right`, `#left-img.top`, `#left-img.bottom`, 50))%>%
+  mutate(in.right.roi = in.box(x, y,`#right-img.left`, `#right-img.right`, `#right-img.top`, `#right-img.bottom`, 50))%>%
   mutate(in.target.roi = if_else(left_image_new == TRUE, in.left.roi, in.right.roi))%>%
@@
 
-```{r Calculate looking score, include=FALSE}
+```{r E3-roi Calculate looking score, include=FALSE}
 looking.score.data <- eyetracking.data %>% 
   group_by(subject_id, right_image, left_image, right_image_new, left_image_new) %>%
-  summarise(looking.score = sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi)) %>%
+  summarise(looking.score.roi = sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi),
+            looking.score.half = sum(in.target.half) / sum(in.target.half, in.distractor.half)) %>%
   mutate(image = if_else(right_image_new, left_image, right_image))
@@
 
-```{r Day 1 t-test looking scores, include=FALSE}
+```{r E3-roi Calculate correlation between LS methods, include=FALSE}
+looking.score.correlation.data <- looking.score.data %>%
+  filter(!is.nan(looking.score.roi)) %>%
+  select(subject_id, looking.score.half, looking.score.roi)
+
+ls.cor <- cor(looking.score.correlation.data$looking.score.half, looking.score.correlation.data$looking.score.roi)
+```
+
+The correlation between looking scores using the ROI method and the halves method is `r ls.cor`.
+
+```{r E3-roi correlation of looking score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
+ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
+  geom_point()+
+  geom_smooth(method="lm", formula = y~x)+
+  labs(x="Looking Score (ROIs)", y="Looking Score (Halves)")+
+  theme_bw()+
+  coord_fixed()+
+  theme(panel.grid=element_blank())
+```
+
+#### Looking Scores
+
+```{r E3-roi Day 1 t-test looking scores, include=FALSE}
 t.test.data1 <- looking.score.data %>%
   group_by(subject_id) %>%
-  filter(!is.nan(looking.score)) %>%
-  summarize(M.looking.score = mean(looking.score))
+  filter(!is.nan(looking.score.half)) %>%
+  summarize(M.looking.score = mean(looking.score.half))
 
@@
 
-#### Looking Scores
-
 When looking scores are coded as left vs.
-right half of the screen, we do find that participants looked more at the novel object.
+right half of the screen, we find that participants looked more at the novel object.
 The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
@@
 
-```{r Create looking over time curve data, include=FALSE}
+```{r E3-roi Create looking over time curve data, include=FALSE}
 
@@
     filter(subject_id == subj, t <= time) %>%
-    summarize(cl = sum(in.target.roi) / (sum(in.target.roi) + sum(in.distractor.roi))) %>%
+    summarize(cl = sum(in.target.half) / (sum(in.target.half) + sum(in.distractor.half))) %>%
     pull(cl))
@@
 
-```{r Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+```{r E3-roi Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
 ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
   geom_pointrange()+
-  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
+  labs(x = "Time (ms)", y = "Cumulative Looking Score (Halves)")+
   theme_bw()+
@@
 
-```{r Prepare Day 2 data, include=FALSE}
+```{r E3-roi Prepare Day 2 data, include=FALSE}
 day2.test.data <- data.day.2 %>%
@@
 
-```{r Calculate Looking Score Correlations, include=FALSE}
+```{r E3-roi Calculate Looking Score Correlations, include=FALSE}
 looking.plus.behavioral <- left_join(looking.score.data, day2.test.data)
@@
   group_by(subject_id) %>%
-  summarize(pearson.r = cor(looking.score, response_confidence)) %>%
+  summarize(pearson.r = cor(looking.score.half, response_confidence)) %>%
   mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))
@@
   group_by(subject_id) %>%
-  summarize(pearson.r = cor(looking.score, rt_recognition)) %>%
+  summarize(pearson.r = cor(looking.score.half, rt_recognition)) %>%
   mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

### 2022-04-11 manuscript.Rmd
added E2 analyses to manuscript
update E3 analysis

@@
 
-* here we will describe the analyses that are as close as possible to the original paper
-
-* same but stricter validation cutoff
-
 ### Calibration
 
-* here we will describe the analyses that correlate calibration quality with effect size at the individual level
+```{r E2-analysis-calibration, child='group-b/E2-analysis-calibration.Rmd'}
+
+```
 
@@
 ## Results
+
+```{r E3-analysis-replication, child='group-c/E3-analysis-replication.Rmd'}
+
+```
+
+### Effects of ROIs
+
+```{r E3-analysis-ROIs, child='group-c/E3-analysis-roi.Rmd'}
+
+```
+
+### Calibration
+
+```{r E3-analysis-calibration, child='group-c/E3-analysis-calibration.Rmd'}
+
+```
 
@@
 
+<!-- posner cueing task
 # Experiment 6
-<!-- posner cueing task -->
 
@@
 ## Discussion
+ -->
 

### 2022-04-11 manuscript.tex
update E3 analysis

@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
-\title{Eye-tracking on the web: lessons learned from replicating 5 experiments}
-\author{Josh de Leeuw\textsuperscript{1} \& et al.\textsuperscript{1,2}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \makeatother
-\shorttitle{Just picked a random title: feel free to change}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 \fi
+
+\title{Eye-tracking on the web: lessons learned from replicating 5 experiments}
+\author{Josh de Leeuw\textsuperscript{1} \& et al.\textsuperscript{1,2}}
+\date{}
+
+\shorttitle{Just picked a random title: feel free to change}
 
@@
 
-\abstract{
+\abstract{%
 ADD LATER
@@
 
-We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 1.0.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.7; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.4; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 2.1.1; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.7.1; Chang et al.
-(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]}, and \emph{tinylabels} (Barth, 2022) for all our analyses.
+We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.3; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.28; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.3.4; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 
+\begin{verbatim}
+## Warning: package 'patchwork' was built under R version 4.1.3
+\end{verbatim}
+
 \hypertarget{replication-1}{%
@@
 The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding.
-The other three quadrants were semi-randomly labeled ``first,'' ``second,'' third'' (e.g., when the critical quadrant was in the top left, the ``first'' quadrant was the top right quadrant, but when the critical quadrant was in the top right, ``first'' corresponded to bottom right, etc.).
+The other three quadrants were semi-randomly labeled ``first'', ``second,'' third'' (e.g., when the critical quadrant was in the top left, the ``first'' quadrant was the top right quadrant, but when the critical quadrant was in the top right, ``first'' corresponded to bottom right, etc.).
 In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \ref{fig:E2-gaze-fig-both-conds}).
@@
 \subsection{Results}\label{results-2}}
+
+\hypertarget{day-1}{%
+\paragraph{Day 1}\label{day-1}}
+
+During day 1 of the experiment, participants viewed pairs of images, one of which was always familiar and the other unfamiliar.
+We calculated a looking score for each participant, defined as the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI.
+Gaze samples that were not in either ROI were not included in this analysis.
+A looking score of 0.5 indicates that participants looked equally often at the familiar and unfamiliar images, while a looking score above 0.5 indicates a preference for the unfamiliar object and a looking score below 0.5 indicate a preference for the familiar object.
+
+Of the 1248 trials in the experiment, 78 had no fixations in either ROI, and so the looking score was unknown. We removed these trials from this analysis.
+
+The mean looking score was 0.55 (\emph{SD} = 0.10).
+This significantly greater than 0.5, \emph{t}(49) = 3.29, \emph{p} = 0.00, indicating that participants did show a preference for looking at the novel objects.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/Plot of cumulative looking score-1.pdf}
+\caption{(\#fig:Plot of cumulative looking score)Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
+\end{figure}
+
+\hypertarget{day-2}{%
+\paragraph{Day 2}\label{day-2}}
+
+In all of these analyses, we excluded the 16 (out of 2304) trials where the response time for the recognition judgment was greater than 10 seconds.
+
+Participants correctly identified whether the image was familiar or unfamiliar 87.09\% (\emph{SD} = 10.49) of the time.
+After excluding the 3 participants who responded correctly to all images, the average confidence rating for correct responses (M = 3.51; SD = 0.41) was significantly higher than their average confidence ratings for incorrect responses (M = 2.55; SD = 0.75), t(44) = -9.36, p = 0.00 .
+Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = 3.43 , p = 0.00.
+
+To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on day 2, we computed the correlation coefficient between day 1 looking scores and day 2 confidence/RT for each participant.
+Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
+Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(38) = 0.46, p = 0.65 (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(46) = 0.49, p = 0.63.
+
+\begin{verbatim}
+## Warning: Removed 75 rows containing missing values (geom_point).
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/Plot Looking Score Correlations-1.pdf}
+
+\hypertarget{effects-of-rois}{%
+\subsubsection{Effects of ROIs}\label{effects-of-rois}}
+
+In the original experiment, the two objects on day 1 were presented on two separate monitors and gaze was coded by manually coding video recordings.
+In our replication analysis, we analyzed eye movement data using ROIs defined around the two images.
+In this section we explore an alternative coding of the eye movement data by coding simply left half vs.~right half of the screen.
+The coarser coding may be more appropriate for webcam-based eyetracking.
+
+The correlation between looking scores using the ROI method and the halves method is 0.76.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-roi correlation of looking score-1.pdf}
+\caption{(\#fig:E3-roi correlation of looking score)Correlation between looking scores calculated using ROIs and using screen halves.}
+\end{figure}
+
+\hypertarget{looking-scores}{%
+\paragraph{Looking Scores}\label{looking-scores}}
+
+When looking scores are coded as left vs.~right half of the screen, we find that participants looked more at the novel object.
+The mean looking score was 0.54 (\emph{SD} = 0.08).
+This was significantly greater than 0.5, \emph{t}(50) = 3.51, \emph{p} = 0.00.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-roi Plot of cumulative looking score-1.pdf}
+\caption{(\#fig:E3-roi Plot of cumulative looking score)Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
+\end{figure}
+
+\hypertarget{correlations-with-day-2-performance}{%
+\paragraph{Correlations with Day 2 Performance}\label{correlations-with-day-2-performance}}
+
+Performance on day 2 remained uncorrelated with day 1 looking scores after switching the coding of gaze.
+We found no significant different from 0 for the correlation between looking score and confidence ratings, t(39) = 0.74, p = 0.47 (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(47) = 0.28, p = 0.78.
+
+\hypertarget{calibration-2}{%
+\subsubsection{Calibration}\label{calibration-2}}
+
+To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant.
+The calibration score was the average proportion of samples within XXX pixels of the validation points during the final validation phase before the eye tracking is performed.
+
+Calibration scores were not correlated with looking scores, regardless of which method was used to calculate looking scores.
+
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (halves) by calibration-1.pdf}
+
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (roi) by calibration-1.pdf}
+
+We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
+None of the four relationships showed a significant correlation.
+
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot correlations with calibration.score-1.pdf}
 
@@
 
+\begin{verbatim}
+## Warning: Computation failed in `stat_summary()`:
+\end{verbatim}
+
 \begin{figure}
@@
 
-\hypertarget{calibration-2}{%
-\subsubsection{Calibration}\label{calibration-2}}
+\hypertarget{calibration-3}{%
+\subsubsection{Calibration}\label{calibration-3}}
 
@@
 
-\hypertarget{effects-of-rois}{%
-\subsubsection{Effects of ROIs}\label{effects-of-rois}}
+\hypertarget{effects-of-rois-1}{%
+\subsubsection{Effects of ROIs}\label{effects-of-rois-1}}
 
@@
 {WebGazer}: {Scalable} webcam eye tracking using user interactions.
-In \emph{Proceedings of the 25th international joint conference on artificial intelligence ({IJCAI})} (pp.
-3839--3845).
+\emph{Proceedings of the 25th International Joint Conference on Artificial Intelligence ({IJCAI})}, 3839--3845.
 {AAAI}.

### 2022-04-13 group-c/E3-analysis-calibration.Rmd
add calibration histogram, reknit manuscript

@@
 
+#### Calibration Accuracy
+
+```{r E3-cal Plot Calibration Accuracy, echo=FALSE}
+ggplot(subject.calibration.score, aes(x=mean_percent_in_roi))+
+  stat_bin(binwidth = 10)+
+  labs(x="Calibration Accuracy\n(% of samples within 200px of calibration point)")+
+  theme_minimal()+
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        axis.title.y = element_blank())
+```
+
+#### Correlation with Effects
+
 To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant.

### 2022-04-14 group-e/group-e-analysis.Rmd
improved gitignore to ignore pdfs and pngs in figure-latex

@@
 title: "R Notebook"
-output: html_notebook
+output:
+  pdf_document: default
+  html_notebook: default
 ---
@@
 library(ggplot2)
+library(lme4)
 ```
@@
 ```{r}
-attractiveness.curve <- summary.gaze.view %>% filter(roundness_task == FALSE)
+attractiveness.curve <- summary.gaze.view %>% filter(task != "Roundness")
 fit <- nls(prop.in.target ~ MaxP + (MinP - MaxP)/(1+(time.window/InfP)^Slope), data = attractiveness.curve, start=list(MaxP=0.9,MinP=0.5,InfP=-500,Slope=-1))

### 2022-04-17 group-b/E2-analysis-calibration.Rmd
Finished group e

@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
 The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.

### 2022-04-17 group-c/E3-analysis-calibration.Rmd
Finished group e

@@
 
-```{r E3-cal Plot correlations with calibration.score, echo=FALSE, warning=FALSE}
+```{r E3-cal Plot correlations with calibration score, echo=FALSE, warning=FALSE}
 ggplot(looking.correlations.subjects.tidy, aes(x=mean_percent_in_roi, y=z))+

### 2022-04-17 group-d/E4-analysis-calibration.Rmd
Finished group e

@@
 ```
-Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
 The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).

### 2022-04-17 group-e/E5-analysis-calibration.Rmd
Finished group e

---
title: "Experiment 5: Calibration Analysis"
output: html_notebook
---

```{r E5-cal load libraries, include=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

```{r E5-cal load all data, include=FALSE, warning=FALSE, echo=FALSE}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)

# Excluding Subjects
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
E5.excluded.n = 8

# Code condition information
all.data <- all.data %>%
  mutate(task = if_else(study_id == '60748d36577623e2677865c6', "Attractiveness", "Roundness"))

# Convert data to long format for gaze measurements
task.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, task, time_elapsed, trial_index, response, rt, webgazer_data, webgazer_targets) %>%
  unnest(webgazer_data) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c('#face1', '#face2'), names_sep = ".")

# restrict to time points 1 sd before the decision
rt.summary <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, trial_index, response, rt) %>%
  summarize(M=mean(rt), SD=sd(rt))
task.data <- task.data %>%
  mutate(time_until_decision = rt - t) %>%
  filter(time_until_decision <= rt.summary$SD)

# Bin in 50 ms bins (not 30 as in the original study, because we are using webcams)
task.data <- task.data %>%
  mutate(time.window = floor(time_until_decision/50)*50+25) #make sure bin is centered

# define ROIs
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}

#analyze with respect to ROIs
task.data <- task.data %>%
  mutate(in.left.box = in.box(x,y,`#face1.left`,`#face1.right`,`#face1.top`,`#face1.bottom`,0)) %>%
  mutate(in.right.box = in.box(x,y,`#face2.left`,`#face2.right`,`#face2.top`,`#face2.bottom`,0)) %>%
  mutate(in.target.box = if_else(response == 'a', in.left.box, in.right.box)) %>%
  mutate(in.other.box = if_else(response == 'a', in.right.box, in.left.box))

summary.gaze.view <- task.data %>%
  filter(in.target.box == TRUE | in.other.box == TRUE) %>%
  group_by(subject_id, task) %>%
  summarize(prop.in.target.subject = mean(in.target.box))

subject.calibration.score <- all.data %>%
  filter(trial_type == "webgazer-validate") %>%
  select(subject_id, trial_index, phase,  percent_in_roi, average_offset) %>% 
  unnest(percent_in_roi) %>%
  group_by(subject_id, trial_index, phase) %>% 
  summarize(mean_percent_in_roi = mean(percent_in_roi)) %>% 
  group_by(subject_id) %>% 
  mutate(calib_num = row_number()) %>%
  group_by(subject_id) %>%
  filter(calib_num == max(calib_num)) %>%
  select(subject_id, mean_percent_in_roi)

scores <- subject.calibration.score %>%
  merge(summary.gaze.view)

scorescorrs.A <- cor.test(scores$mean_percent_in_roi[scores$task=="Attractiveness"], scores$prop.in.target.subject[scores$task=="Attractiveness"])
scorescorrs.R <- cor.test(scores$mean_percent_in_roi[scores$task=="Roundness"], scores$prop.in.target.subject[scores$task=="Roundness"])

```

As in the previous experiments, calibration score was defined as the average proportion of samples within 200 pixels of the validation point during the final validation phase before the eye tracking is performed. The distribution across participants is shown in Fig. \@ref(fig:E5cal). 
(ref:E5cal-caption) Histogram of calibration success in Exp. 5. Where participants required more than one calibration (N=8), only the final calibration was considered.

```{r E5cal, fig.show="hold", out.width="45%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5cal-caption)"}
ggplot(subject.calibration.score, aes(x=mean_percent_in_roi)) +
  stat_bin(binwidth = 10) +
  labs(x="Calibration Accuracy\n(% of samples within 200px of calibration point)") +
  theme_classic()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title.y = element_blank())
```

To determine whether calibration accuracy influenced our key effects, we calculated the percentage of samples during the task in which the participant was fixating the face they ultimately chose. There was a significant correlation for both the attractiveness judgments (r = `r round(scorescorrs.A$estimate, 2)` [`r round(scorescorrs.A$conf.int, 2)[1]`, `r round(scorescorrs.A$conf.int, 2)[2]`], p = `r round(scorescorrs.A$p.value, 2)`) and the roundness judgments (r = `r round(scorescorrs.R$estimate, 2)` [`r round(scorescorrs.R$conf.int, 2)[1]`, `r round(scorescorrs.R$conf.int, 2)[2]`], p = `r round(scorescorrs.R$p.value, 2)`). Inspection of Fig. \@ref(fig:E5calcorr) reveals that this correlation is due to a handful of particpiants with calibration values below 50%.

(ref:E5calcorr-caption) Correlation between calibration accuracy (x-axis) and percentage of samples fixating target (y-axis) in Exp. 5.

```{r E5calcorr, fig.show="hold", out.width="80%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5calcorr-caption)"}
ggplot(scores, aes(x=mean_percent_in_roi, y=prop.in.target.subject, group=task, color=task))+
  geom_point() + geom_smooth(method="lm") +
  labs(x="calibration accuracy", y="looking at chosen face") +
  theme_classic() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title.y = element_blank())
```

```{r reanalyzedat, echo=FALSE, warning=FALSE, include=FALSE}

#re-aggregate data, removing subjects with calibration scores =< 50%.
rescore <- task.data %>%
  filter(in.target.box == TRUE | in.other.box == TRUE) %>%
  group_by(subject_id, time_until_decision, task) %>%
  summarize(prop.in.target.subject = mean(in.target.box)) %>%
  merge(subject.calibration.score) %>%
  filter(mean_percent_in_roi > 50) %>%
  mutate(time.window = floor(time_until_decision/50)*50+25) %>% #make sure bin is centered
  group_by(time.window, task) %>%
  summarize(prop.in.target = mean(prop.in.target.subject), se = sd(prop.in.target.subject)/sqrt(n()))

KS <- ks.test(rescore %>% filter(task == "Attractiveness") %>% pull(prop.in.target),
         rescore %>% filter(task == "Roundness") %>% pull(prop.in.target))

# Fitting a sigmoid as described in original

sigmoid<-function(x, a, b, c, d){
  return(d + (a - d) / (1 + (x / c)^b))
}

error <- function(x,y, pars){
  a <- pars[1]
  b <- pars[2]
  c <- pars[3]
  d <- pars[4]
  sum(sapply(1:length(x), function(i){
    return(y[i] - sigmoid(x[i], a, b, c, d))
  })^2)
}

fitsig<-function(x, y){
  pars <- c(0,0,200,0)
  return(optim(pars, fn=function(pars){error(x,y,pars)}, method="Nelder-Mead"))
}

fit.A <- fitsig(rescore$time.window[rescore$task=="Attractiveness"], rescore$prop.in.target[rescore$task=="Attractiveness"])
fit.R <- fitsig(rescore$time.window[rescore$task=="Roundness"], rescore$prop.in.target[rescore$task=="Roundness"])

fit.A.dat<-data.frame(x=rescore$time.window[rescore$task=="Attractiveness"], y=sigmoid(rescore$time.window[rescore$task=="Attractiveness"], fit.A$par[1], fit.A$par[2], fit.A$par[3], fit.A$par[4]))

fit.R.dat<-data.frame(x=rescore$time.window[rescore$task=="Roundness"], y=sigmoid(rescore$time.window[rescore$task=="Roundness"], fit.R$par[1], fit.R$par[2], fit.R$par[3], fit.R$par[4]))

# calculate R^2
R2 <- function(fit, y){
  return(1 - fit$value / sum((y - mean(y))^2))
}
R2.A<-R2(fit.A, rescore$prop.in.target[rescore$task=="Attractiveness"])
R2.R<-R2(fit.R, rescore$prop.in.target[rescore$task=="Roundness"])

plot.A<-ggplot(rescore[rescore$task=="Attractiveness",], aes(x=time.window, y=prop.in.target)) +
  geom_point(color="red") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)

plot.R<-ggplot(rescore[rescore$task=="Roundness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="turquoise4") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "dashed") + 
  geom_line(data=fit.R.dat, aes(x=x, y=y), color="turquoise4", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)

```

Thus, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50%. This slightly improved the fits of the sigmoids (Attractiveness: R^2^ = `r round(R2.A,2)`; Roundness: R^2^ = `r round(R2.R,2)`). However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = `r round(KS$statistic, 2)`, p = `r round(KS$p.value, 2)`). Descriptively, the results do not look substantially different (Fig. \@ref(fig:groupEMainrev)).

(ref:groupEMainrev-caption) Revised results for Exp. 5 after removing low-calibration accuracy participants. *Left*: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid. *Right*: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).

```{r groupEMainrev, fig.show="hold", out.width="45%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:groupEMainrev-caption)"}
plot.A
plot.R
```

### 2022-04-17 group-e/E5-analysis-replication.Rmd
Finished group e

---
title: "Experiment 5: Replication Analysis"
output: html_notebook
---

```{r E5 load libraries, include=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(knitr)
```

```{r E5 load all data, include=FALSE}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r}
# Excluding Subjects
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
E5.excluded.n = 8

# Convert data to long format for gaze measurements
task.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, time_elapsed, trial_index, response, rt, webgazer_data, webgazer_targets) %>%
  unnest(webgazer_data) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c('#face1', '#face2'), names_sep = ".")

# Code condition information
task.data <- task.data %>%
  mutate(task = if_else(study_id == '60748d36577623e2677865c6', "Attractiveness", "Roundness"))

# restrict to time points 1 sd before the decision
rt.summary <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, trial_index, response, rt) %>%
  summarize(M=mean(rt), SD=sd(rt))
task.data <- task.data %>%
  mutate(time_until_decision = rt - t) %>%
  filter(time_until_decision <= rt.summary$SD)

# Bin in 50 ms bins (not 30 as in the original study, because we are using webcams)
task.data <- task.data %>%
  mutate(time.window = floor(time_until_decision/50)*50+25) #make sure bin is centered

```

Due to large variation in response time latency, Shimojo and colleagues analyzed eye gaze for the 1.67 seconds prior to the response. This duration was one standard deviation of the mean response time, ensuring that all timepoints analyzed have data from at least 67% of trials. In our dataset, one standard deviation amounts to `r round(rt.summary$SD/1000, 2)` seconds. We then binned eyegaze data into 50 ms bins rather than the 30 ms bins used by Shimojo and colleagues, reflecting the different sampling rates.

```{r importdat, echo=FALSE, warning=FALSE, include=FALSE}
# define ROIs
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}

#analyze with respect to ROIs
task.data <- task.data %>%
  mutate(in.left.box = in.box(x,y,`#face1.left`,`#face1.right`,`#face1.top`,`#face1.bottom`,0)) %>%
  mutate(in.right.box = in.box(x,y,`#face2.left`,`#face2.right`,`#face2.top`,`#face2.bottom`,0)) %>%
  mutate(in.target.box = if_else(response == 'a', in.left.box, in.right.box)) %>%
  mutate(in.other.box = if_else(response == 'a', in.right.box, in.left.box))

summary.gaze.view <- task.data %>%
  filter(in.target.box == TRUE | in.other.box == TRUE) %>%
  group_by(subject_id, time.window, task) %>%
  summarize(prop.in.target.subject = mean(in.target.box)) %>%
  group_by(time.window, task) %>%
  summarize(prop.in.target = mean(prop.in.target.subject), se = sd(prop.in.target.subject)/sqrt(n()))

# Two-sample Kolmogorov-Smirnov test
KS<-ks.test(summary.gaze.view %>% filter(task == "Attractiveness") %>% pull(prop.in.target),
         summary.gaze.view %>% filter(task == "Roundness") %>% pull(prop.in.target))

# Fitting a sigmoid as described in original

sigmoid<-function(x, a, b, c, d){
  return(d + (a - d) / (1 + (x / c)^b))
}

error <- function(x,y, pars){
  a <- pars[1]
  b <- pars[2]
  c <- pars[3]
  d <- pars[4]
  sum(sapply(1:length(x), function(i){
    return(y[i] - sigmoid(x[i], a, b, c, d))
  })^2)
}

fitsig<-function(x, y){
  pars <- c(0,0,200,0)
  return(optim(pars, fn=function(pars){error(x,y,pars)}, method="Nelder-Mead"))
}

fit.A <- fitsig(summary.gaze.view$time.window[summary.gaze.view$task=="Attractiveness"], summary.gaze.view$prop.in.target[summary.gaze.view$task=="Attractiveness"])
fit.R <- fitsig(summary.gaze.view$time.window[summary.gaze.view$task=="Roundness"], summary.gaze.view$prop.in.target[summary.gaze.view$task=="Roundness"])

fit.A.dat<-data.frame(x=summary.gaze.view$time.window[summary.gaze.view$task=="Attractiveness"], y=sigmoid(summary.gaze.view$time.window[summary.gaze.view$task=="Attractiveness"], fit.A$par[1], fit.A$par[2], fit.A$par[3], fit.A$par[4]))

fit.R.dat<-data.frame(x=summary.gaze.view$time.window[summary.gaze.view$task=="Roundness"], y=sigmoid(summary.gaze.view$time.window[summary.gaze.view$task=="Roundness"], fit.R$par[1], fit.R$par[2], fit.R$par[3], fit.R$par[4]))

# calculate R^2
R2 <- function(fit, y){
  return(1 - fit$value / sum((y - mean(y))^2))
}
R2.A<-R2(fit.A, summary.gaze.view$prop.in.target[summary.gaze.view$task=="Attractiveness"])
R2.R<-R2(fit.R, summary.gaze.view$prop.in.target[summary.gaze.view$task=="Roundness"])

plot.A<-ggplot(summary.gaze.view[summary.gaze.view$task=="Attractiveness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="red") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)

plot.R<-ggplot(summary.gaze.view[summary.gaze.view$task=="Roundness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="turquoise4") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "dashed") + 
  geom_line(data=fit.R.dat, aes(x=x, y=y), color="turquoise4", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)

```

(ref:groupEMain-caption) Primary results from Exp. 5. *Top* shows the original results from Shimojo and colleagues (Figures reprinted with permission[TODO]). The attractiveness judgment along with the best-fitting sigmoid  is shown in the *top left*. Results for the roundness judgment are show in the *top right*, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison (*top right*). (*Bottom*) shows the analogous results from the replication, with the attractiveness judgments on the *bottom left* and the roundness judgments on the *bottom right*. Again, the best-fitting sigmoid for the attractiveness judgments are plotted with a dashed line alongside the roundness results, for purposes of comparison.

```{r groupEMain, fig.show="hold", out.width="45%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:groupEMain-caption)"}
# All defaults
include_graphics("figGroupEOrigA")
include_graphics("figGroupEOrigB")
plot.A
plot.R
```

Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig. \@ref(fig:Shimojo)). These fit less well than in the original paper for both the attractiveness judgment (R^2^ = `r round(R2.A,2)` vs. 0.91) and the roundness judgment (R^2^ = `r round(R2.R,2)` vs. 0.91).

From these curves, Shimojo and colleagues focus on two qualitative findings. First, they note a higher asymptote for the attractiveness discrimination task relative to roundness discrimination. Qualitatively, this appears to replicate. However, their statistical analysis -- a Kolmogorov-Smirnov test for distance between two distributions -- is not significant (D = `r round(KS$statistic, 2)`, p = `r round(KS$p.value, 2)`), though it should be noted that this is a very indirect statistical test of the hypothesis and probably not very sensitive.

The second qualitative finding they note is that the curve for the roundness judgment "saturates" (asymptotes) earlier than the curve for the attractiveness judgment. They do not present any statistical analyses, but it is clear qualitatively that the result does not replicate.

### 2022-04-17 group-e/E5-analysis-roi.Rmd
Finished group e

---
title: "Experiment 5: ROI Analysis"
output: html_notebook
---

In the original experiment, eye gazes that did not directly fixate one or other of the faces were excluded. In this section we explore an alternative coding of the eye movement data by coding simply left half vs. right half of the screen. The coarser coding may be more appropriate for webcam-based eyetracking.

```{r E5-roi load all data, include=FALSE, warning=FALSE, echo=FALSE}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)

# Excluding Subjects
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
E5.excluded.n = 8

# Code condition information
all.data <- all.data %>%
  mutate(task = if_else(study_id == '60748d36577623e2677865c6', "Attractiveness", "Roundness"))

# Convert data to long format for gaze measurements
task.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, task, time_elapsed, trial_index, response, rt, webgazer_data, webgazer_targets) %>%
  unnest(webgazer_data) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c('#face1', '#face2'), names_sep = ".")

# restrict to time points 1 sd before the decision
rt.summary <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, trial_index, response, rt) %>%
  summarize(M=mean(rt), SD=sd(rt))
task.data <- task.data %>%
  mutate(time_until_decision = rt - t) %>%
  filter(time_until_decision <= rt.summary$SD)

# Bin in 50 ms bins (not 30 as in the original study, because we are using webcams)
task.data <- task.data %>%
  mutate(time.window = floor(time_until_decision/50)*50+25) #make sure bin is centered

# define ROIs
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}

#analyze with respect to ROIs
task.data <- task.data %>%
  mutate(midpoint.x = `#face1.right` + (`#face2.left` - `#face1.right`)/2) %>%
  mutate(in.left.half = x < midpoint.x) %>%
  mutate(in.right.half = x > midpoint.x) %>%
  mutate(in.target.half = if_else(response == 'a', in.left.half, in.right.half)) %>%
  mutate(in.distractor.half = if_else(response == 'a', in.right.half, in.left.half)) %>%
  mutate(in.left.roi = in.box(x, y,`#face1.left`, `#face1.right`, `#face1.top`, `#face1.bottom`, 50))%>%
  mutate(in.right.roi = in.box(x, y,`#face2.left`, `#face2.right`, `#face2.top`, `#face2.bottom`, 50))%>%
  mutate(in.target.roi = if_else(response == 'a', in.left.roi, in.right.roi)) %>%
  mutate(in.distractor.roi = if_else(response == 'a', in.right.roi, in.left.roi))

looking.score.data <- task.data %>% 
  group_by(subject_id, task, time.window) %>%
  summarise(looking.score.roi = sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi),
            looking.score.half = sum(in.target.half) / sum(in.target.half, in.distractor.half))

looking.score.correlation.data <- looking.score.data %>%
  filter(!is.nan(looking.score.roi)) %>%
  select(subject_id, looking.score.half, looking.score.roi)

ls.cor <- cor.test(looking.score.correlation.data$looking.score.half, looking.score.correlation.data$looking.score.roi)
```

Only a small percentage of samples (`r round(mean(task.data$in.target.roi==0 &  task.data$in.distractor.roi==0), 2)*100`%) involved looks to anything other than one of the two faces. Thus, not surprisingly, the correlation between percentage of time spent fixating the to-be-chosen face using the ROI method and the halves method was near ceiling (r = `r round(ls.cor$estimate, 2)` [`r round(ls.cor$conf.int[1], 2)`, `r round(ls.cor$conf.int[2], 2)`], p = `r ls.cor$p.value`). Since the choice of method had almost no effect on whether participants were coded as fixating one face or the other, we did not further investigate the effect of method choice on the analytic results.

### 2022-04-17 manuscript.Rmd
Finished group e

@@
 The fifth study was a replication attempt of @shimojoGazeBiasBoth2003, which found that human gaze is actively involved in preference formation.
-Participants were shown pairs of human faces and were asked to choose the face which they found more attractive.
-Prior to making their explicit selection, participants spent more time looking at the face that was ultimately judged more attractive.
-This bias was not as large when the task was face shape discrimination rather than a preference-based choice.
+Separate sets of participants were shown pairs of human faces and asked either to choose which one they found more attractive or which they felt was rounder.
+Prior to making their explicit selection, participants were increasingly likely to be fixating the face they ultimately chose, though this effect was significantly weaker for roundness discrimination.
+
+Note that Shimojo and colleagues compare five conditions, of which we replicate only the two that figure most prominently in their conclusions: the "face-attractiveness-difficult task" and the "face-roundness task".
 
@@
 
-27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They were paid $XX for completing the experiment.
-Data from 3 participants was excluded because their mode response made up more than 50% of their total responses <!-- is this a cutoff from Shimojo?-->, for a total of 24 participants in the norming.
-
 50 participants for the main task were recruited on Prolific and were paid $XX.
 8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
-<!-- they were able to proceed despite bad validation?--> After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.The original sample size in Shimojo et al.
+<!-- they were able to proceed despite bad validation?--> After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.
+The original sample size in Shimojo et al.
 (2003) was 10 participants total.
-
 ### Procedure and Design
@@
 were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
-Participants in the norming study viewed 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They were paid $XX for completing the experiment.
+Data from 3 participants was excluded because their mode response made up more than 50% of their total responses <!-- is this a cutoff from Shimojo?-->, for a total of 24 participants in the norming.
+They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
 Faces were presented one at a time and in a random order for each participant.
@@
 In the original study, a video-based eye tracker was used.
-The eye movements of participants were recorded with a digital camera, and eye position was then tracked using MediaAnalyzer software.
-This eye tracker was able to collect 30 samples per second.
-In our study, the camera on the device used by the participant and the jsPsych WebGazer package were used to determine where a participant’s gaze was directed.
-Since our eye tracking method did not have the same sample collection rate as the eye tracker in Shimojo et al., time windows of 50 milliseconds were used when looking at the likelihood of gazing at the chosen face at a given point between a cutoff time and when the decision was made.
+The eye movements of participants were recorded with a digital camera downsampled to 33.3 Hz, with eye position was then determined automatically with MediaAnalyzer software.
+In our study, subjects supplied their own cameras, so hardware sampling rate varied.
+However, data was collected at 20 Hz.[TODO - CONFIRM]
 
 ## Results
+
+```{r E5-analysis-replication, child='group-e/E5-analysis-replication.Rmd'}
+
+```
+
+### Calibration
+
+```{r E5-analysis-calibration, child='group-e/E5-analysis-calibration.Rmd'}
+
+```
+
+### Effects of ROIs
+
+```{r E5-analysis-roi, child='group-e/E5-analysis-roi.Rmd'}
+
+```
 

### 2022-04-17 manuscript.tex
Finished group e

@@
 \documentclass[
+  english,
   man,floatsintext]{apa6}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
 
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{Just picked a random title: feel free to change}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
+\ifXeTeX
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
 \ifLuaTeX
@@
 
-\shorttitle{Just picked a random title: feel free to change}
-
 \authornote{
@@
 
-\abstract{%
+\abstract{
 ADD LATER
@@
 
-We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.3; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.28; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.3.4; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R {[}Version 4.0.3; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 1.0.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.7; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.26; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.2; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.6.0; Chang et al.
+(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, and \emph{tinylabels} (Barth, 2022) for all our analyses.
 
@@
 \subsection{Results}\label{results-1}}
-
-\begin{verbatim}
-## Warning: package 'patchwork' was built under R version 4.1.3
-\end{verbatim}
 
@@
 
+\hypertarget{calibration-accuracy}{%
+\paragraph{Calibration Accuracy}\label{calibration-accuracy}}
+
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot Calibration Accuracy-1.pdf}
+
+\hypertarget{correlation-with-effects}{%
+\paragraph{Correlation with Effects}\label{correlation-with-effects}}
+
 To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant.
@@
 
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot correlations with calibration.score-1.pdf}
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot correlations with calibration score-1.pdf}
 
@@
 
-\begin{verbatim}
-## Warning: Computation failed in `stat_summary()`:
-\end{verbatim}
-
 \begin{figure}
@@
 The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003), which found that human gaze is actively involved in preference formation.
-Participants were shown pairs of human faces and were asked to choose the face which they found more attractive.
-Prior to making their explicit selection, participants spent more time looking at the face that was ultimately judged more attractive.
-This bias was not as large when the task was face shape discrimination rather than a preference-based choice.
+Separate sets of participants were shown pairs of human faces and asked either to choose which one they found more attractive or which they felt was rounder.
+Prior to making their explicit selection, participants were increasingly likely to be fixating the face they ultimately chose, though this effect was significantly weaker for roundness discrimination.
+
+Note that Shimojo and colleagues compare five conditions, of which we replicate only the two that figure most prominently in their conclusions: the ``face-attractiveness-difficult task'' and the ``face-roundness task''.
 
@@
 
-27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They were paid \$XX for completing the experiment.
-Data from 3 participants was excluded because their mode response made up more than 50\% of their total responses , for a total of 24 participants in the norming.
-
 50 participants for the main task were recruited on Prolific and were paid \$XX.
 8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
-After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.The original sample size in Shimojo et al.~(2003) was 10 participants total.
-
-\hypertarget{procedure-and-design}{%
-\subsubsection{Procedure and Design}\label{procedure-and-design}}
+After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.
+The original sample size in Shimojo et al.~(2003) was 10 participants total.
+\#\#\# Procedure and Design
 
@@
 (The face images used in Shimojo et al.~were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
-Participants in the norming study viewed 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They were paid \$XX for completing the experiment.
+Data from 3 participants was excluded because their mode response made up more than 50\% of their total responses , for a total of 24 participants in the norming.
+They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
 Faces were presented one at a time and in a random order for each participant.
@@
 In the original study, a video-based eye tracker was used.
-The eye movements of participants were recorded with a digital camera, and eye position was then tracked using MediaAnalyzer software.
-This eye tracker was able to collect 30 samples per second.
-In our study, the camera on the device used by the participant and the jsPsych WebGazer package were used to determine where a participant's gaze was directed.
-Since our eye tracking method did not have the same sample collection rate as the eye tracker in Shimojo et al., time windows of 50 milliseconds were used when looking at the likelihood of gazing at the chosen face at a given point between a cutoff time and when the decision was made.
+The eye movements of participants were recorded with a digital camera downsampled to 33.3 Hz, with eye position was then determined automatically with MediaAnalyzer software.
+In our study, subjects supplied their own cameras, so hardware sampling rate varied.
+However, data was collected at 20 Hz.{[}TODO - CONFIRM{]}
 
@@
 \subsection{Results}\label{results-4}}
+
+Due to large variation in response time latency, Shimojo and colleagues analyzed eye gaze for the 1.67 seconds prior to the response.
+This duration was one standard deviation of the mean response time, ensuring that all timepoints analyzed have data from at least 67\% of trials.
+In our dataset, one standard deviation amounts to 1.85 seconds.
+We then binned eyegaze data into 50 ms bins rather than the 30 ms bins used by Shimojo and colleagues, reflecting the different sampling rates.
+
+\begin{figure}
+\includegraphics[width=0.45\linewidth]{figGroupEOrigA} \includegraphics[width=0.45\linewidth]{figGroupEOrigB} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMain-3} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMain-4} \caption{Primary results from Exp.
+5.
+\emph{Top} shows the original results from Shimojo and colleagues (Figures reprinted with permission{[}TODO{]}).
+The attractiveness judgment along with the best-fitting sigmoid is shown in the \emph{top left}.
+Results for the roundness judgment are show in the \emph{top right}, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison (\emph{top right}).
+(\emph{Bottom}) shows the analogous results from the replication, with the attractiveness judgments on the \emph{bottom left} and the roundness judgments on the \emph{bottom right}.
+Again, the best-fitting sigmoid for the attractiveness judgments are plotted with a dashed line alongside the roundness results, for purposes of comparison.}\label{fig:groupEMain}
+\end{figure}
+
+Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig.
+\ref{fig:Shimojo}).
+These fit less well than in the original paper for both the attractiveness judgment (R\textsuperscript{2} = 0.84 vs.~0.91) and the roundness judgment (R\textsuperscript{2} = 0.54 vs.~0.91).
+
+From these curves, Shimojo and colleagues focus on two qualitative findings.
+First, they note a higher asymptote for the attractiveness discrimination task relative to roundness discrimination.
+Qualitatively, this appears to replicate.
+However, their statistical analysis -- a Kolmogorov-Smirnov test for distance between two distributions -- is not significant (D = 0.19, p = 0.53), though it should be noted that this is a very indirect statistical test of the hypothesis and probably not very sensitive.
+
+The second qualitative finding they note is that the curve for the roundness judgment ``saturates'' (asymptotes) earlier than the curve for the attractiveness judgment.
+They do not present any statistical analyses, but it is clear qualitatively that the result does not replicate.
+
+\hypertarget{calibration-4}{%
+\subsubsection{Calibration}\label{calibration-4}}
+
+As in the previous experiments, calibration score was defined as the average proportion of samples within 200 pixels of the validation point during the final validation phase before the eye tracking is performed.
+The distribution across participants is shown in Fig.
+\ref{fig:E5cal}.
+
+\begin{figure}
+\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/E5cal-1} \caption{Histogram of calibration success in Exp.
+5.
+Where participants required more than one calibration (N=8), only the final calibration was considered.}\label{fig:E5cal}
+\end{figure}
+
+To determine whether calibration accuracy influenced our key effects, we calculated the percentage of samples during the task in which the participant was fixating the face they ultimately chose.
+There was a significant correlation for both the attractiveness judgments (r = 0.47 {[}0.04, 0.75{]}, p = 0.03) and the roundness judgments (r = 0.60 {[}0.23, 0.82{]}, p = 0).
+Inspection of Fig.
+\ref{fig:E5calcorr} reveals that this correlation is due to a handful of particpiants with calibration values below 50\%.
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{manuscript_files/figure-latex/E5calcorr-1} \caption{Correlation between calibration accuracy (x-axis) and percentage of samples fixating target (y-axis) in Exp.
+5.}\label{fig:E5calcorr}
+\end{figure}
+
+Thus, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50\%.
+This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.79; Roundness: R\textsuperscript{2} = 0.60).
+However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.35).
+Descriptively, the results do not look substantially different (Fig.
+\ref{fig:groupEMainrev}).
+
+\begin{figure}
+\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMainrev-1} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMainrev-2} \caption{Revised results for Exp.
+5 after removing low-calibration accuracy participants.
+\emph{Left}: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid.
+\emph{Right}: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).}\label{fig:groupEMainrev}
+\end{figure}
+
+\hypertarget{effects-of-rois-2}{%
+\subsubsection{Effects of ROIs}\label{effects-of-rois-2}}
+
+In the original experiment, eye gazes that did not directly fixate one or other of the faces were excluded.
+In this section we explore an alternative coding of the eye movement data by coding simply left half vs.~right half of the screen.
+The coarser coding may be more appropriate for webcam-based eyetracking.
+
+Only a small percentage of samples (7.00\%) involved looks to anything other than one of the two faces.
+Thus, not surprisingly, the correlation between percentage of time spent fixating the to-be-chosen face using the ROI method and the halves method was near ceiling (r = 0.97 {[}0.97, 0.98{]}, p = 0).
+Since the choice of method had almost no effect on whether participants were coded as fixating one face or the other, we did not further investigate the effect of method choice on the analytic results.
 
@@
 {WebGazer}: {Scalable} webcam eye tracking using user interactions.
-\emph{Proceedings of the 25th International Joint Conference on Artificial Intelligence ({IJCAI})}, 3839--3845.
+In \emph{Proceedings of the 25th international joint conference on artificial intelligence ({IJCAI})} (pp.
+3839--3845).
 {AAAI}.

### 2022-04-21 group-b/E2-analysis-calibration.Rmd
minor

--- 2022-04-02 group-b/E2-analysis-calibration.Rmd
@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
 The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.

### 2022-04-21 group-d/E4-analysis-calibration.Rmd
minor

--- 2022-04-01 group-d/E4-analysis-calibration.Rmd
@@
 ```
-Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
 The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).

### 2022-04-21 group-d/E4-analysis-replication.Rmd
minor

@@
   geom_line(size=1)+
-  scale_color_brewer(palette = "Set1")+
-  scale_fill_brewer(palette = "Set1")+
+  scale_color_manual(values = c( "#377eb8", "#e41a1c","#4daf4a"))+
+  scale_fill_manual(values = c("#377eb8", "#e41a1c", "#4daf4a"))+
   scale_linetype(labels = c("Animal", "Instrument") )+
@@
 saveRDS(fig2, "output/ETfig.rds")
-
+ggsave("output/ETfig.png", plot = fig2, height = 4, width = 6)
 ```

### 2022-04-21 manuscript.Rmd
minor reknit manuscript

@@
 
+```{=html}
 <!-- MAJOR TO DOs: 
@@
  -->
-
+```
 Intro stuff:
@@
 
-- Online data collection is more and more popular & let's us ask new questions, test more diverse populations
+-   Online data collection is more and more popular & let's us ask new
+    questions, test more diverse populations
 
@@
 
-_Present work_
+*Present work*
 
-In the present work, we attempted to replicate five eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
-The plug-in relies on the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer].
-The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes).
-...
+In the present work, we attempted to replicate five eye-tracking studies
+from the cognitive science literature using the eye-tracking plug-in
+from `jsPsych`, a Javascript library for running behavioral experiments
+in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. The plug-in
+relies on the `webgazer.js` library for webcam eye-tracking
+[@papoutsaki2016webgazer]. The goal was to examine the strengths and
+weaknesses of webcam eye-tracking for common paradigms in cognitive
+science. The studies were chosen to cover a variety of topic areas
+(e.g., memory, decision-making, psycholinguistics) and paradigms (two
+halves of the screen, visual world paradigm with four quadrants, visual
+world paradigm with "natural" scenes). ...
 
@@
 
-Participants completed the experiment remotely and were recruited through the Prolific platform.
-In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
-All participants provided informed consent.
-The studies were approved by the Vassar College Institutional Review Board.
+Participants completed the experiment remotely and were recruited
+through the Prolific platform. In order to have access to the
+experiment, participants had to meet the following criteria: 18 years of
+age or older, fluency in English, and access to a webcam. All
+participants provided informed consent. The studies were approved by the
+Vassar College Institutional Review Board.
 
 ## Eye-tracking Calibration and Validation
+
 <!--took paragraph below from group D's methods -->
-When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
-They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
-The webcam’s view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
-The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
 
-During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
-Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
-The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
-After the calibration was completed, the validation began.
-Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
-If accuracy on the validation was too low (fewer than 50% of looks landed within a 200 px radius of the validation points<!--check!-->), participants were given an opportunity to re-start the calibration and validation steps.
-If the second attempt also lead to low validation accuracy, participants were informed that they could not participate in the study.
+When participants began the experiment, they were notified the webcam
+would be used for eye tracking but no video would be saved. They were
+asked to remove glasses if possible, close any other tabs or apps, turn
+off notifications, and make sure their face was lit from the front. The
+webcam's view of the participant popped up on the screen, and
+participants were asked to center their face in the box and keep their
+head still. The experiment window then expanded to full screen, and
+participants began the eye-tracking calibration.
+
+During the calibration, dots appeared on the screen one at a time in
+different locations, and the participants had to fixate them and click
+on each one. Once they clicked on a dot, it would disappear and a new
+one would appear in a different location on the screen. The locations of
+calibration dots were specific to each experiment (details below) and
+appeared in the areas of the screen where the visual stimuli would
+appear during the main task in order to ensure that eye movements were
+accurately recorded in the relevant regions of interest. After the
+calibration was completed, the validation began. Participants were asked
+to go through the same steps as the calibration, except that they only
+fixated the dots as they appeared in different locations on the screen.
+If accuracy on the validation was too low (fewer than 50% of looks
+landed within a 200 px radius of the validation points<!--check!-->),
+participants were given an opportunity to re-start the calibration and
+validation steps. If the second attempt also lead to low validation
+accuracy, participants were informed that they could not participate in
+the study.
 
 ## Data pre-processing
+
 We used `r cite_r("references.bib")` for all our analyses.
@@
 # Experiment 1
+
 <!-- group a -->
 
-The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.
-Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
-For example, when looking at the display in Figure XX and listening to a sentence like “The boy will eat the…,” participants are more likely to look at the cake than when they hear “The boy will move the…,” in which case they tend to look at the train, presumably because cakes are edible and trains are not.
-Semantic information available at the verb is used to anticipate upcoming linguistic input.
+The first study was a replication attempt of
+@altmannIncrementalInterpretationVerbs1999. Altmann and Kamide used the
+visual world eye-tracking paradigm [@tanenhaus1995] to show that
+meanings of verbs rapidly constrain the set of potential subsequent
+referents in sentence processing. For example, when looking at the
+display in Figure XX and listening to a sentence like "The boy will eat
+the...," participants are more likely to look at the cake than when they
+hear "The boy will move the...," in which case they tend to look at the
+train, presumably because cakes are edible and trains are not. Semantic
+information available at the verb is used to anticipate upcoming
+linguistic input.
 
@@
 ## Methods
+
 <!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->
-All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at [https://osf.io/s82kz](https://osf.io/s82kz).
+
+All stimuli, experiment scrips, data, analysis scripts, and
+pre-registration are available on the Open Science Framework at
+<https://osf.io/s82kz>.
 
@@
 
-60 participants were paid $XX for their participation.
-Our sample size of participants was determined by the total run time of our experiment, ~10 minutes, and the allotted funding from the Vassar College Cognitive Science Department.
-From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific.
-Note that the sample size of the original study was 24.
-For unknown reasons, 2 of the subjects’ results were not recorded, so in the analysis, we worked with data collected from 58 participants.
+60 participants were paid \$XX for their participation. Our sample size
+of participants was determined by the total run time of our experiment,
+\~10 minutes, and the allotted funding from the Vassar College Cognitive
+Science Department. From this information, we calculated a reasonable
+number of participants we could afford to compensate on Prolific. Note
+that the sample size of the original study was 24. For unknown reasons,
+2 of the subjects' results were not recorded, so in the analysis, we
+worked with data collected from 58 participants.
 
@@
 
-The task began with an <number of points>-point eye-tracker calibration and validation.
-During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
-Participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence they heard was feasible given the visual image.
-There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
-Participants’ reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.
+The task began with an <number of points>-point eye-tracker calibration
+and validation. During the experiment, the participants were
+simultaneously presented with a visual image and a corresponding audio
+recording of a spoken sentence. Participants had to input a keyboard
+response indicating "yes" or "no" as to whether the sentence they heard
+was feasible given the visual image. There were two practice trials to
+ensure that participants had a sound understanding of the instructions
+before they undertook the main portion of the experiment. Participants'
+reaction times, keyboard responses, and looks to objects in the scene
+were recorded for each trial.
 
+```{=html}
 <!-- Qs: 
@@
 -Does trial end as soon as participant responds?-->
-
+```
 ### Materials & Design
 
-The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure XX).
-On critical trials, participants heard one of two sentences associated with the scene.
-In the restrictive condition, the sentence (e.g., "The boy will eat the cake") contained a verb (e.g., "eat") which restricts the set of possible subsequent referents (e.g., to edible things).
-Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
-In the non-restrictive condition, the sentence (e.g., "The boy will move the cake") contained a verb (e.g., "move") which does not restrict the set of possible subsequent referents.
-The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
-Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was "yes." Filler trials consisted of scenes that looked similar to critical scenes but were paired with inappropriate sentences.
-The correct keyboard response for the filler trials was "no."
+The visual stimuli were created through Canva and depicted an agent
+accompanied by four to five objects in the scene (see Figure XX). On
+critical trials, participants heard one of two sentences associated with
+the scene. In the restrictive condition, the sentence (e.g., "The boy
+will eat the cake") contained a verb (e.g., "eat") which restricts the
+set of possible subsequent referents (e.g., to edible things). Only the
+target object (e.g., the cake) was semantically consistent with the
+verb's meaning. In the non-restrictive condition, the sentence (e.g.,
+"The boy will move the cake") contained a verb (e.g., "move") which does
+not restrict the set of possible subsequent referents. The target object
+(e.g., the cake) as well as the distractor objects (e.g., the train, the
+ball, etc.) were semantically consistent with the verb's meaning. Both
+sentences were compatible with the scene, such that the correct keyboard
+response for the critical trials was "yes." Filler trials consisted of
+scenes that looked similar to critical scenes but were paired with
+inappropriate sentences. The correct keyboard response for the filler
+trials was "no."
 
-Each participant was presented with sixteen critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and sixteen fillers for a total of 32 trials.
-The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.<!-- right?-->
+Each participant was presented with sixteen critical trials (eight in
+the restrictive condition, eight in the non-restrictive condition) and
+sixteen fillers for a total of 32 trials. The order of trials and the
+assignment of critical scene to condition was random on a
+subject-by-subject basis.<!-- right?-->
 
@@
 
-Looks to the objects in the scene were time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
+Looks to the objects in the scene were time-locked to the onset of the
+verb, the offset of the verb, onset of the post-verbal determiner, and
+onset of the target noun.
 
@@
 
-* here we will describe the analyses that are as close as possible to the original paper with a minimal validation cutoff
+-   here we will describe the analyses that are as close as possible to
+    the original paper with a minimal validation cutoff
 
-* same analysis but with stricter validation cutoff
+-   same analysis but with stricter validation cutoff
 
@@
 
-* here we will describe a direct comparison to data collected in the lab
+-   here we will describe a direct comparison to data collected in the
+    lab
 
@@
 
-* here we will describe the analyses that correlate calibration quality with effect size at the individual level
+-   here we will describe the analyses that correlate calibration
+    quality with effect size at the individual level
 
@@
 # Experiment 2
+
 <!-- group b -->
 
-The second study was a replication attempt of @johanssonLookHereEye2014, which examined how visuospatial information is integrated into memory for objects.
-They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding [see @spiveyOculomotorMechanismsActivated2001] and that this spatial reinstatement facilitates retrieval of the picture.
+The second study was a replication attempt of @johanssonLookHereEye2014,
+which examined how visuospatial information is integrated into memory
+for objects. They found that, during memory retrieval, learners
+spontaneously look to blank screen locations where pictures were located
+during encoding [see @spiveyOculomotorMechanismsActivated2001] and that
+this spatial reinstatement facilitates retrieval of the picture.
 
@@
 
-60 participants were paid $XX for their participation <!--right?-->.
-The sample size was motivated in part by budget constraints, but was nonetheless 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
-Data from 1 participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.
+60 participants were paid \$XX for their participation <!--right?-->.
+The sample size was motivated in part by budget constraints, but was
+nonetheless 2.5x larger than the original sample size of 24, as
+suggested by Simonsohn (2015). Data from 1 participant were not properly
+recorded due to unknown technical issues, so data from 59 participants
+were included in all analyses to follow.
 
@@
 
-The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
-During the encoding phase, participants saw a grid indicating the four quadrants of the screen.
-Each quadrant contained six images of items belonging to the same category (see Figure XX).
-The four categories were humanoids, household objects, animals, and methods of transportation.
-Participants were asked to remember the contents of the four quadrants.
-Different images were used in each block.
+The experiment consisted of two blocks each composed of an encoding
+phase and a recall phase. During the encoding phase, participants saw a
+grid indicating the four quadrants of the screen. Each quadrant
+contained six images of items belonging to the same category (see Figure
+XX). The four categories were humanoids, household objects, animals, and
+methods of transportation. Participants were asked to remember the
+contents of the four quadrants. Different images were used in each
+block.
 
-Each of the four quadrants was presented one at a time.
-First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown (??).
-For each item, an audio file would play ("???") asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing either left or right (right??)).
-After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
-Then, after all four quadrants were presented in this way, the participant was shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
+Each of the four quadrants was presented one at a time. First, a list of
+the items in the quadrant were shown, then the items in the actual
+quadrant were shown (??). For each item, an audio file would play
+("???") asking the participant to use their arrow keys to identify which
+direction each item was facing (every item was facing either left or
+right (right??)). After the participant identified the direction of each
+item, they would have an additional 30 seconds to encode the name and
+orientation of each item in the quadrant. Then, after all four quadrants
+were presented in this way, the participant was shown the full grid of
+24 items and had 60 seconds to further encode the name and orientation
+of each item.
 
-During the recall phase, participants listened to statements and responded by pressing the ‘F’ key for false statements and ‘T’ for true ones.
-Each statement fell into either an interobject or intraobject condition.
-Interobject statements were those that compared two different items in the grid (e.g.
-“The skeleton is to the left of the robot”), while intraobject statements were those that asked about the orientation of a single item (e.g.
-“The bus is facing right”).
-There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
-While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
-During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
-In both cases, the mouse was obscured from the screen.
-Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
+During the recall phase, participants listened to statements and
+responded by pressing the 'F' key for false statements and 'T' for true
+ones. Each statement fell into either an interobject or intraobject
+condition. Interobject statements were those that compared two different
+items in the grid (e.g. "The skeleton is to the left of the robot"),
+while intraobject statements were those that asked about the orientation
+of a single item (e.g. "The bus is facing right"). There were 48 total
+statements, with 24 interobject and 24 intraobject statements split
+evenly among the four quadrants. While listening to these statements, in
+the free-viewing block, participants saw a blank screen and were allowed
+to freely gaze around the screen. During the fixed-viewing block,
+participants were asked to fixate a small cross in the center of the
+screen throughout the recall phase. In both cases, the mouse was
+obscured from the screen. Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first.
 
- After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
+After completing both encoding-recall blocks, participants were asked to
+answer a few survey questions (such as whether they wore glasses or
+encountered any distractions).
 
-The primary methodological difference between this replication and Johansson and Johansson’s study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
-In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
+The primary methodological difference between this replication and
+Johansson and Johansson's study was that the original study included two
+additional viewing conditions that were omitted from this replication
+due to time constraints. In those two conditions, participant were
+prompted to look to a specific quadrant (rather than free viewing or
+central fixation) which either matched or mismatched the original
+location of the to-be-remembered item.
 
@@
 # Experiment 3
+
 <!-- group c -->
 
-The third study was a replication attempt of @mannsVisualPairedcomparisonTask2000 which aimed to show that the visual paired-comparison task, widely used in the patient literature, tapped into declarative memory.
-In the visual paired-comparison task, two identical pictures were presented side by side for a brief viewing period.
-After a delay, one of the previously viewed pictures was presented along with a new picture.
-Individuals looked more at the new picture than the old picture and the time spent looking was correlated with later recognition memory performance.
-On the other hand perceptual priming, thought to recruit non-declarative memory, was not linked to later recognition.
-(The perceptual priming arm of the design was not included in this replication.)
+The third study was a replication attempt of
+@mannsVisualPairedcomparisonTask2000 which aimed to show that the visual
+paired-comparison task, widely used in the patient literature, tapped
+into declarative memory. In the visual paired-comparison task, two
+identical pictures were presented side by side for a brief viewing
+period. After a delay, one of the previously viewed pictures was
+presented along with a new picture. Individuals looked more at the new
+picture than the old picture and the time spent looking was correlated
+with later recognition memory performance. On the other hand perceptual
+priming, thought to recruit non-declarative memory, was not linked to
+later recognition. (The perceptual priming arm of the design was not
+included in this replication.)
 
@@
 
- Our initial sample size was 51 participants for the first day of our experiment and 48 of them came back for the second day.
-Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test.
-Our final sample size was 45 participants.
+Our initial sample size was 51 participants for the first day of our
+experiment and 48 of them came back for the second day. Following Manns
+et al., we excluded 3 participants due to perfect performance on the
+recognition memory test. Our final sample size was 45 participants.
 
@@
 
-The task began with a 7-point eye-tracker calibration (each point was presented 3 times in a random order) and validation with 3 points (each presented once).
-The point locations were designed to focus calibration on the center of the screen and the middle of the left and right halves of the screen.
-The experiment was administered over the course of two consecutive days.
-It consisted of three sections: a presentation phase, a test phase, and a recognition test.
-The first two phases occurred on the first day, while the recognition test occurred on the second day.
+The task began with a 7-point eye-tracker calibration (each point was
+presented 3 times in a random order) and validation with 3 points (each
+presented once). The point locations were designed to focus calibration
+on the center of the screen and the middle of the left and right halves
+of the screen. The experiment was administered over the course of two
+consecutive days. It consisted of three sections: a presentation phase,
+a test phase, and a recognition test. The first two phases occurred on
+the first day, while the recognition test occurred on the second day.
 
-During the presentation phase, participants viewed 24 pairs of identical color photographs depicting common objects.
-Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
-The order of the photographs was randomized and different for each participant.
-After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
+During the presentation phase, participants viewed 24 pairs of identical
+color photographs depicting common objects. Each pair was presented for
+5 seconds and an interval of 5 seconds elapsed before the next pair was
+shown. The order of the photographs was randomized and different for
+each participant. After completion of the presentation phase,
+participants were given a 5-minute break during which they could look
+away from the screen.
 
-After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
-During this phase, participants again viewed 24 pairs of photographs with an interstimulus duration of 5 seconds.
-In each pair, one photograph was previously seen during the presentation phase, while the other was new.
-Which pictures were old or new was counterbalanced across participants.<!-- 2 lists?--> For half of the participants in each counterbalancing group, the new and old photographs were reversed.<!-- not sure what that last sentence means: is it about the side of the screen?
-or still just describing that there were 2 lists-->
+After the break, they were prompted to complete the eye-tracking
+calibration again before beginning the test phase. During this phase,
+participants again viewed 24 pairs of photographs with an interstimulus
+duration of 5 seconds. In each pair, one photograph was previously seen
+during the presentation phase, while the other was new. Which pictures
+were old or new was counterbalanced across participants.<!-- 2 lists?-->
+For half of the participants in each counterbalancing group, the new and
+old photographs were
+reversed.<!-- not sure what that last sentence means: is it about the side of the screen? or still just describing that there were 2 lists-->
 
- Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
-It consisted of 48 photographs, presented one at a time.
-Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
-Half of the pohotographs had been viewed twice on the previous day and were deemed the “targets.” The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed “foils.” Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing ‘y’ for yes and ‘n’ for no.
-After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a “pure guess” to 5 as “very sure.” by clicking on the corresponding number on the screen.
-No feedback on their responses was given during the test.
+Approximately 24 hours after completing the first session, with a leeway
+interval of 12 hours to accommodate busy schedules, participants were
+given the recognition test. It consisted of 48 photographs, presented
+one at a time. Each was shown on the screen for 1 second, followed by a
+1 second interstimulus interval. Half of the pohotographs had been
+viewed twice on the previous day and were deemed the "targets." The
+other half depicted an object with the same name as an object in one of
+the old photographs, but had not been viewed before, deemed "foils."
+Each photograph remained on the screen until the participants indicated
+whether or not they had seen it before by pressing 'y' for yes and 'n'
+for no. After they pressed one of the two keys, a prompt on the screen
+asked them to rate their confidence in their answer from 1 as a "pure
+guess" to 5 as "very sure." by clicking on the corresponding number on
+the screen. No feedback on their responses was given during the test.
 
@@
 
-There were two modifications we made to the methods of the original experiment.
-As we are only replicating the declarative memory component of the original experiment, we did not have a “priming group.” Therefore, we followed only the procedure for the “looking group.” Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.
+There were two modifications we made to the methods of the original
+experiment. As we are only replicating the declarative memory component
+of the original experiment, we did not have a "priming group."
+Therefore, we followed only the procedure for the "looking group."
+Additionally, for each section of the study, the stimuli was presented
+on a single screen instead of two screens due to the constraints of the
+online experiment format.
 
@@
 # Experiment 4
+
 <!-- group d -->
 
-The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a.
-These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
-For example, in a sentence like “Feel the frog with the feather,” the phrase “with the feather” could be describing the frog, or it could be describing the instrument that should be used to do the “feeling.” When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb’s “bias” (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
-.
+The fourth study was a replication attempt of Experiment 1 in
+@ryskinVerbBiasesAre2017, which was closely modeled on
+@snedekerDevelopingConstraintsParsing2004a. These studies used the
+visual world paradigm to show that listeners use knowledge of the
+co-occurrence statistics of verbs and syntactic structures to resolve
+ambiguity. For example, in a sentence like "Feel the frog with the
+feather," the phrase "with the feather" could be describing the frog, or
+it could be describing the instrument that should be used to do the
+"feeling." When both options (a frog holding a feather and a feather by
+itself) are available in the visual display, listeners rely on the
+verb's "bias" (statistical co-occurrence either in norming or corpora)
+to rapidly choose an action while the sentence is unfolding. .
 
@@
 
-The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, https://osf.io/x3c49/ (https://osf.io/x3c49/).
-The pre-registration for the study can be found at https://osf.io/3v4pg (https://osf.io/3v4pg).
+The stimuli, experimental code, and data and analysis scripts can be
+found on the Open Science Framework at the following link,
+<https://osf.io/x3c49/> (<https://osf.io/x3c49/>). The pre-registration
+for the study can be found at <https://osf.io/3v4pg>
+(<https://osf.io/3v4pg>).
 
@@
 
-58 (??) participants were paid $XX for their participation <!--right?-->.
-A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power.
-Note that the original study had a sample size of 24.
+58 (??) participants were paid \$XX for their participation
+<!--right?-->. A sample size of 58 was chosen because we wanted to
+replicate the experiment with greater statistical power. Note that the
+original study had a sample size of 24.
 
@@
 
-After the eye-tracking calibration, participants went through an audio test so they could adjust the audio on their computer to a comfortable level.
-Before beginning the experiment, they were given instructions that four objects would appear, an audio prompt would play, and they should do their best to use their mouse to act out the instructions.
-They then went through three practice trials which were followed by 54 critical trials and 24 filler trials presented in a random order.
+After the eye-tracking calibration, participants went through an audio
+test so they could adjust the audio on their computer to a comfortable
+level. Before beginning the experiment, they were given instructions
+that four objects would appear, an audio prompt would play, and they
+should do their best to use their mouse to act out the instructions.
+They then went through three practice trials which were followed by 54
+critical trials and 24 filler trials presented in a random order.
 
-During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure XX)^[In the original study, the pictures appeared one by one on the screen and their names were played as they appeared.
-We removed this introductory portion of the trial to save time].
-Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects^[ As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
-For example, the sentence “locate the camel with the straw” may not involve any clicking but rather only mousing over the camel.].
-After the action was completed, the participants were instructed to press the space bar which led to a screen that said “Click Here” in the middle in order to remove bias in the eye and mouse movements from the previous trial.
-The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
+During a trial, four pictures were displayed (target animal, target
+instrument, distractor animal, distractor instrument), one in each
+corner of the screen, and participants heard an audio prompt that
+contained instructions about the action they needed to act out (e.g.,
+"Rub the butterfly with the crayon"; see Figure XX)[^1]. Using their
+cursor, participants could act out the instructions by clicking on
+objects and moving them or motioning over the objects[^2]. After the
+action was completed, the participants were instructed to press the
+space bar which led to a screen that said "Click Here" in the middle in
+order to remove bias in the eye and mouse movements from the previous
+trial. The experiment only allowed the participants to move on to the
+next trial once the audio was completely done playing and the mouse had
+been moved over at least one object.
+
+[^1]: In the original study, the pictures appeared one by one on the
+    screen and their names were played as they appeared. We removed this
+    introductory portion of the trial to save time
+
+[^2]:  As opposed to the original study we recorded mouse movement
+    instead of clicking behavior since not all of the audio prompts
+    required clicking. For example, the sentence "locate the camel with
+    the straw" may not involve any clicking but rather only mousing over
+    the camel.
 
@@
 
-The images and audios presented to the participants were the same stimuli used in the original study (available here <link>).
-The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
-Two lists of critical trials were made with different verb and instrument combinations (e.g., “rub” could be paired with “panda” and “crayon” in one list and “panda” and “violin” in the second list).
-Within each list, the same verb was presented twice but each time with a different target instrument and animal.
-The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
-The list of verbs used can be found in Appendix A of the original study.
+The images and audios presented to the participants were the same
+stimuli used in the original study (available here <link>). The critical
+trials were divided into modifier-biased, instrument-biased, and
+equibiased conditions, and the filler trials did not contain ambiguous
+instructions. Two lists of critical trials were made with different verb
+and instrument combinations (e.g., "rub" could be paired with "panda"
+and "crayon" in one list and "panda" and "violin" in the second list).
+Within each list, the same verb was presented twice but each time with a
+different target instrument and animal. The lists were randomly assigned
+to the participants to make sure the effects were not caused by the
+properties of the animal or instrument images used. The list of verbs
+used can be found in Appendix A of the original study.
 
@@
 # Experiment 5
+
 <!-- group e -->
 
-The fifth study was a replication attempt of @shimojoGazeBiasBoth2003, which found that human gaze is actively involved in preference formation.
-Separate sets of participants were shown pairs of human faces and asked either to choose which one they found more attractive or which they felt was rounder.
-Prior to making their explicit selection, participants were increasingly likely to be fixating the face they ultimately chose, though this effect was significantly weaker for roundness discrimination.
+The fifth study was a replication attempt of @shimojoGazeBiasBoth2003,
+which found that human gaze is actively involved in preference
+formation. Separate sets of participants were shown pairs of human faces
+and asked either to choose which one they found more attractive or which
+they felt was rounder. Prior to making their explicit selection,
+participants were increasingly likely to be fixating the face they
+ultimately chose, though this effect was significantly weaker for
+roundness discrimination.
 
-Note that Shimojo and colleagues compare five conditions, of which we replicate only the two that figure most prominently in their conclusions: the "face-attractiveness-difficult task" and the "face-roundness task".
+Note that Shimojo and colleagues compare five conditions, of which we
+replicate only the two that figure most prominently in their
+conclusions: the "face-attractiveness-difficult task" and the
+"face-roundness task".
 
@@
 
-All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at https://osf.io/eubsc/ (https://osf.io/eubsc/).
-The study pre-registration is available at https://osf.io/tv57s (https://osf.io/tv57s).
+All stimuli, experiment scripts, data, and analysis scripts are
+available on the Open Science Framework at <https://osf.io/eubsc/>
+(<https://osf.io/eubsc/>). The study pre-registration is available at
+<https://osf.io/tv57s> (<https://osf.io/tv57s>).
 
@@
 
-50 participants for the main task were recruited on Prolific and were paid $XX.
-8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
-<!-- they were able to proceed despite bad validation?--> After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.
-The original sample size in Shimojo et al.
-(2003) was 10 participants total.
-### Procedure and Design
+50 participants for the main task were recruited on Prolific and were
+paid \$XX. 8 subjects, 4 from the attractiveness task group and 4 from
+the roundness task group, were excluded for incorrect validations.
+<!-- they were able to proceed despite bad validation?--> After this
+data exclusion, we ended up with 21 participants each for the
+attractiveness task and the roundness task. The original sample size in
+Shimojo et al. (2003) was 10 participants total. \### Procedure and
+Design
 
-At the beginning of the experimental task, participants completed a 9-point eye-tracker calibration (each point appeared 3 times in random order) and 3-point validation.
-The validation point appeared once at center, middle left, and middle right locations in random order.
+At the beginning of the experimental task, participants completed a
+9-point eye-tracker calibration (each point appeared 3 times in random
+order) and 3-point validation. The validation point appeared once at
+center, middle left, and middle right locations in random order.
 <!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total?
@@
 
-During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure XX).
-Participants were randomly assigned to one of two tasks: attractiveness or shape judgment.
-In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
-They pressed the "a" key on their keyboard to select the face on the left and the “d” key to select the face on the right.
-A fixation cross appeared in the center of the screen between each set of faces.
-Participants were asked to look at this fixation cross in order to reset their gaze in between trials (???).
-The order of the 19 face pairs was random for each participant.
+During each trial of the main task, two faces were displayed on the two
+halves of the screen, one on the left and one on the right (as in Figure
+XX). Participants were randomly assigned to one of two tasks:
+attractiveness or shape judgment. In the attractiveness task,
+participants were asked to chose the more attractice face in the pair
+and in the shape judgment task participants were asked to pick the face
+that appeared rounder. They pressed the "a" key on their keyboard to
+select the face on the left and the "d" key to select the face on the
+right. A fixation cross appeared in the center of the screen between
+each set of faces. Participants were asked to look at this fixation
+cross in order to reset their gaze in between trials (???). The order of
+the 19 face pairs was random for each participant.
 
@@
 
-The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset.
-(The face images used in Shimojo et al.
-were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
-27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They were paid $XX for completing the experiment.
-Data from 3 participants was excluded because their mode response made up more than 50% of their total responses <!-- is this a cutoff from Shimojo?-->, for a total of 24 participants in the norming.
-They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
-Faces were presented one at a time and in a random order for each participant.
-Following Shimojo et al., 19 face pairs were made by matching two faces that had a difference in mean attractiveness ratings that was 0.25 points or lower and that matched in gender, race, and age group (young adult, adult, or older adult).
+The faces in our replication were selected from a set of 1,000 faces
+within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et
+al. were from the Ekman face database and the AR face database.) These
+images were chosen because the person in each image was looking at the
+camera with a fairly neutral facial expression and appeared to be over
+the age of 18. 27 participants were recruited on Prolific to participate
+in stimulus norming (for attractiveness). They were paid \$XX for
+completing the experiment. Data from 3 participants was excluded because
+their mode response made up more than 50% of their total responses
+<!-- is this a cutoff from Shimojo?-->, for a total of 24 participants
+in the norming. They each viewed all 172 faces and were asked to rate
+them on a scale from 1 (less attractive) to 7 (more attractive) using a
+slider. Faces were presented one at a time and in a random order for
+each participant. Following Shimojo et al., 19 face pairs were made by
+matching two faces that had a difference in mean attractiveness ratings
+that was 0.25 points or lower and that matched in gender, race, and age
+group (young adult, adult, or older adult).
 
@@
 
-In the original study, a video-based eye tracker was used.
-The eye movements of participants were recorded with a digital camera downsampled to 33.3 Hz, with eye position was then determined automatically with MediaAnalyzer software.
-In our study, subjects supplied their own cameras, so hardware sampling rate varied.
-However, data was collected at 20 Hz.[TODO - CONFIRM]
+In the original study, a video-based eye tracker was used. The eye
+movements of participants were recorded with a digital camera
+downsampled to 33.3 Hz, with eye position was then determined
+automatically with MediaAnalyzer software. In our study, subjects
+supplied their own cameras, so hardware sampling rate varied. However,
+data was collected at 20 Hz.[TODO - CONFIRM]
 
@@
 
+```{=html}
 <!-- posner cueing task
@@
  -->
-
+```
 # Combined Analyses
 
-- Pooling data from all experiments we can look at patterns in the calibration and validation data
+-   Pooling data from all experiments we can look at patterns in the
+    calibration and validation data
 
@@
 
+```{=html}
 <!-- NOTES FROM EMAILS:
@@
 -->
-
+```
 \newpage
@@
 
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
 
-<div id="refs" custom-style="Bibliography"></div>
+```{=tex}
 \endgroup
+```

### 2022-04-21 manuscript.tex
minor reknit manuscript

@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
 
@@
 
+\shorttitle{Just picked a random title: feel free to change}
+
 \authornote{
@@
 \item
-  Online data collection is more and more popular \& let's us ask new questions, test more diverse populations
+  Online data collection is more and more popular \& let's us ask new
+  questions, test more diverse populations
 \item
@@
 
-In the present work, we attempted to replicate five eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from \texttt{jsPsych}, a Javascript library for running behavioral experiments in a web browser (de Leeuw, 2015).
-The plug-in relies on the \texttt{webgazer.js} library for webcam eye-tracking (Papoutsaki et al., 2016).
-The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``natural'' scenes).
-\ldots{}
+In the present work, we attempted to replicate five eye-tracking studies
+from the cognitive science literature using the eye-tracking plug-in
+from \texttt{jsPsych}, a Javascript library for running behavioral experiments
+in a web browser (de Leeuw, 2015). The plug-in
+relies on the \texttt{webgazer.js} library for webcam eye-tracking
+(Papoutsaki et al., 2016). The goal was to examine the strengths and
+weaknesses of webcam eye-tracking for common paradigms in cognitive
+science. The studies were chosen to cover a variety of topic areas
+(e.g., memory, decision-making, psycholinguistics) and paradigms (two
+halves of the screen, visual world paradigm with four quadrants, visual
+world paradigm with ``natural'' scenes). \ldots{}
 
@@
 
-Participants completed the experiment remotely and were recruited through the Prolific platform.
-In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
-All participants provided informed consent.
-The studies were approved by the Vassar College Institutional Review Board.
+Participants completed the experiment remotely and were recruited
+through the Prolific platform. In order to have access to the
+experiment, participants had to meet the following criteria: 18 years of
+age or older, fluency in English, and access to a webcam. All
+participants provided informed consent. The studies were approved by the
+Vassar College Institutional Review Board.
 
@@
 
-When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
-They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
-The webcam's view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
-The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
-
-During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
-Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
-The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
-After the calibration was completed, the validation began.
-Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
-If accuracy on the validation was too low (fewer than 50\% of looks landed within a 200 px radius of the validation points), participants were given an opportunity to re-start the calibration and validation steps.
-If the second attempt also lead to low validation accuracy, participants were informed that they could not participate in the study.
+When participants began the experiment, they were notified the webcam
+would be used for eye tracking but no video would be saved. They were
+asked to remove glasses if possible, close any other tabs or apps, turn
+off notifications, and make sure their face was lit from the front. The
+webcam's view of the participant popped up on the screen, and
+participants were asked to center their face in the box and keep their
+head still. The experiment window then expanded to full screen, and
+participants began the eye-tracking calibration.
+
+During the calibration, dots appeared on the screen one at a time in
+different locations, and the participants had to fixate them and click
+on each one. Once they clicked on a dot, it would disappear and a new
+one would appear in a different location on the screen. The locations of
+calibration dots were specific to each experiment (details below) and
+appeared in the areas of the screen where the visual stimuli would
+appear during the main task in order to ensure that eye movements were
+accurately recorded in the relevant regions of interest. After the
+calibration was completed, the validation began. Participants were asked
+to go through the same steps as the calibration, except that they only
+fixated the dots as they appeared in different locations on the screen.
+If accuracy on the validation was too low (fewer than 50\% of looks
+landed within a 200 px radius of the validation points),
+participants were given an opportunity to re-start the calibration and
+validation steps. If the second attempt also lead to low validation
+accuracy, participants were informed that they could not participate in
+the study.
 
@@
 
-We used R {[}Version 4.0.3; R Core Team (2021){]} and the R-packages \emph{afex} {[}Version 1.0.1; Singmann, Bolker, Westfall, Aust, and Ben-Shachar (2021){]}, \emph{broom.mixed} {[}Version 0.2.7; Bolker and Robinson (2020){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{jsonlite} {[}Version 1.7.2; Ooms (2014){]}, \emph{lme4} {[}Version 1.1.26; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{lmerTest} {[}Version 3.1.3; Kuznetsova, Brockhoff, and Christensen (2017){]}, \emph{Matrix} {[}Version 1.3.2; Bates and Maechler (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{shiny} {[}Version 1.6.0; Chang et al.
-(2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, and \emph{tinylabels} (Barth, 2022) for all our analyses.
+We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.3; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.7; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jsonlite} (Version 1.7.2; Ooms, 2014), \emph{lme4} (Version 1.1.27.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.3.4; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.1; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.1; Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 
-The first study was a replication attempt of Altmann and Kamide (1999).
-Altmann and Kamide used the visual world eye-tracking paradigm (Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995) to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
-For example, when looking at the display in Figure XX and listening to a sentence like ``The boy will eat the\ldots,'' participants are more likely to look at the cake than when they hear ``The boy will move the\ldots,'' in which case they tend to look at the train, presumably because cakes are edible and trains are not.
-Semantic information available at the verb is used to anticipate upcoming linguistic input.
+The first study was a replication attempt of
+Altmann and Kamide (1999). Altmann and Kamide used the
+visual world eye-tracking paradigm (Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995) to show that
+meanings of verbs rapidly constrain the set of potential subsequent
+referents in sentence processing. For example, when looking at the
+display in Figure XX and listening to a sentence like ``The boy will eat
+the\ldots,'' participants are more likely to look at the cake than when they
+hear ``The boy will move the\ldots,'' in which case they tend to look at the
+train, presumably because cakes are edible and trains are not. Semantic
+information available at the verb is used to anticipate upcoming
+linguistic input.
 
@@
 
-All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at \url{https://osf.io/s82kz}.
+All stimuli, experiment scrips, data, analysis scripts, and
+pre-registration are available on the Open Science Framework at
+\url{https://osf.io/s82kz}.
 
@@
 
-60 participants were paid \$XX for their participation.
-Our sample size of participants was determined by the total run time of our experiment, \textasciitilde10 minutes, and the allotted funding from the Vassar College Cognitive Science Department.
-From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific.
-Note that the sample size of the original study was 24.
-For unknown reasons, 2 of the subjects' results were not recorded, so in the analysis, we worked with data collected from 58 participants.
+60 participants were paid \$XX for their participation. Our sample size
+of participants was determined by the total run time of our experiment,
+\textasciitilde10 minutes, and the allotted funding from the Vassar College Cognitive
+Science Department. From this information, we calculated a reasonable
+number of participants we could afford to compensate on Prolific. Note
+that the sample size of the original study was 24. For unknown reasons,
+2 of the subjects' results were not recorded, so in the analysis, we
+worked with data collected from 58 participants.
 
@@
 
-The task began with an -point eye-tracker calibration and validation.
-During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence.
-Participants had to input a keyboard response indicating ``yes'' or ``no'' as to whether the sentence they heard was feasible given the visual image.
-There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment.
-Participants' reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.
+The task began with an -point eye-tracker calibration
+and validation. During the experiment, the participants were
+simultaneously presented with a visual image and a corresponding audio
+recording of a spoken sentence. Participants had to input a keyboard
+response indicating ``yes'' or ``no'' as to whether the sentence they heard
+was feasible given the visual image. There were two practice trials to
+ensure that participants had a sound understanding of the instructions
+before they undertook the main portion of the experiment. Participants'
+reaction times, keyboard responses, and looks to objects in the scene
+were recorded for each trial.
 
@@
 
-The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure XX).
-On critical trials, participants heard one of two sentences associated with the scene.
-In the restrictive condition, the sentence (e.g., ``The boy will eat the cake'') contained a verb (e.g., ``eat'') which restricts the set of possible subsequent referents (e.g., to edible things).
-Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
-In the non-restrictive condition, the sentence (e.g., ``The boy will move the cake'') contained a verb (e.g., ``move'') which does not restrict the set of possible subsequent referents.
-The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
-Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was ``yes.'' Filler trials consisted of scenes that looked similar to critical scenes but were paired with inappropriate sentences.
-The correct keyboard response for the filler trials was ``no.''
-
-Each participant was presented with sixteen critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and sixteen fillers for a total of 32 trials.
-The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.
+The visual stimuli were created through Canva and depicted an agent
+accompanied by four to five objects in the scene (see Figure XX). On
+critical trials, participants heard one of two sentences associated with
+the scene. In the restrictive condition, the sentence (e.g., ``The boy
+will eat the cake'') contained a verb (e.g., ``eat'') which restricts the
+set of possible subsequent referents (e.g., to edible things). Only the
+target object (e.g., the cake) was semantically consistent with the
+verb's meaning. In the non-restrictive condition, the sentence (e.g.,
+``The boy will move the cake'') contained a verb (e.g., ``move'') which does
+not restrict the set of possible subsequent referents. The target object
+(e.g., the cake) as well as the distractor objects (e.g., the train, the
+ball, etc.) were semantically consistent with the verb's meaning. Both
+sentences were compatible with the scene, such that the correct keyboard
+response for the critical trials was ``yes.'' Filler trials consisted of
+scenes that looked similar to critical scenes but were paired with
+inappropriate sentences. The correct keyboard response for the filler
+trials was ``no.''
+
+Each participant was presented with sixteen critical trials (eight in
+the restrictive condition, eight in the non-restrictive condition) and
+sixteen fillers for a total of 32 trials. The order of trials and the
+assignment of critical scene to condition was random on a
+subject-by-subject basis.
 
@@
 \item
-  here we will describe the analyses that are as close as possible to the original paper with a minimal validation cutoff
+  here we will describe the analyses that are as close as possible to
+  the original paper with a minimal validation cutoff
 \item
@@
 \item
-  here we will describe a direct comparison to data collected in the lab
+  here we will describe a direct comparison to data collected in the
+  lab
 \end{itemize}
@@
 \item
-  here we will describe the analyses that correlate calibration quality with effect size at the individual level
+  here we will describe the analyses that correlate calibration
+  quality with effect size at the individual level
 \end{itemize}
@@
 
-The second study was a replication attempt of Johansson and Johansson (2014), which examined how visuospatial information is integrated into memory for objects.
-They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding (see Spivey \& Geng, 2001) and that this spatial reinstatement facilitates retrieval of the picture.
+The second study was a replication attempt of Johansson and Johansson (2014),
+which examined how visuospatial information is integrated into memory
+for objects. They found that, during memory retrieval, learners
+spontaneously look to blank screen locations where pictures were located
+during encoding (see Spivey \& Geng, 2001) and that
+this spatial reinstatement facilitates retrieval of the picture.
 
@@
 60 participants were paid \$XX for their participation .
-The sample size was motivated in part by budget constraints, but was nonetheless 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015).
-Data from 1 participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.
+The sample size was motivated in part by budget constraints, but was
+nonetheless 2.5x larger than the original sample size of 24, as
+suggested by Simonsohn (2015). Data from 1 participant were not properly
+recorded due to unknown technical issues, so data from 59 participants
+were included in all analyses to follow.
 
@@
 
-The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
-During the encoding phase, participants saw a grid indicating the four quadrants of the screen.
-Each quadrant contained six images of items belonging to the same category (see Figure XX).
-The four categories were humanoids, household objects, animals, and methods of transportation.
-Participants were asked to remember the contents of the four quadrants.
-Different images were used in each block.
-
-Each of the four quadrants was presented one at a time.
-First, a list of the items in the quadrant were shown, then the items in the actual quadrant were shown (??).
-For each item, an audio file would play (``???'') asking the participant to use their arrow keys to identify which direction each item was facing (every item was facing either left or right (right??)).
-After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
-Then, after all four quadrants were presented in this way, the participant was shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
-
-During the recall phase, participants listened to statements and responded by pressing the `F' key for false statements and `T' for true ones.
-Each statement fell into either an interobject or intraobject condition.
-Interobject statements were those that compared two different items in the grid (e.g.~``The skeleton is to the left of the robot''), while intraobject statements were those that asked about the orientation of a single item (e.g.~``The bus is facing right'').
-There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants.
-While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
-During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
-In both cases, the mouse was obscured from the screen.
-Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
-
-After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
-
-The primary methodological difference between this replication and Johansson and Johansson's study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
-In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
+The experiment consisted of two blocks each composed of an encoding
+phase and a recall phase. During the encoding phase, participants saw a
+grid indicating the four quadrants of the screen. Each quadrant
+contained six images of items belonging to the same category (see Figure
+XX). The four categories were humanoids, household objects, animals, and
+methods of transportation. Participants were asked to remember the
+contents of the four quadrants. Different images were used in each
+block.
+
+Each of the four quadrants was presented one at a time. First, a list of
+the items in the quadrant were shown, then the items in the actual
+quadrant were shown (??). For each item, an audio file would play
+(``???'') asking the participant to use their arrow keys to identify which
+direction each item was facing (every item was facing either left or
+right (right??)). After the participant identified the direction of each
+item, they would have an additional 30 seconds to encode the name and
+orientation of each item in the quadrant. Then, after all four quadrants
+were presented in this way, the participant was shown the full grid of
+24 items and had 60 seconds to further encode the name and orientation
+of each item.
+
+During the recall phase, participants listened to statements and
+responded by pressing the `F' key for false statements and `T' for true
+ones. Each statement fell into either an interobject or intraobject
+condition. Interobject statements were those that compared two different
+items in the grid (e.g.~``The skeleton is to the left of the robot''),
+while intraobject statements were those that asked about the orientation
+of a single item (e.g.~``The bus is facing right''). There were 48 total
+statements, with 24 interobject and 24 intraobject statements split
+evenly among the four quadrants. While listening to these statements, in
+the free-viewing block, participants saw a blank screen and were allowed
+to freely gaze around the screen. During the fixed-viewing block,
+participants were asked to fixate a small cross in the center of the
+screen throughout the recall phase. In both cases, the mouse was
+obscured from the screen. Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first.
+
+After completing both encoding-recall blocks, participants were asked to
+answer a few survey questions (such as whether they wore glasses or
+encountered any distractions).
+
+The primary methodological difference between this replication and
+Johansson and Johansson's study was that the original study included two
+additional viewing conditions that were omitted from this replication
+due to time constraints. In those two conditions, participant were
+prompted to look to a specific quadrant (rather than free viewing or
+central fixation) which either matched or mismatched the original
+location of the to-be-remembered item.
 
@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within \textcolor{red}{XX} pixels of the calibration point, varied substantially (between 17.78 and 100 \%).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between 17.78 and 100 \%).
 The quality of a participant's calibration was not significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.20, \emph{p} = 0.14) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.
@@
 
-The third study was a replication attempt of Manns, Stark, and Squire (2000) which aimed to show that the visual paired-comparison task, widely used in the patient literature, tapped into declarative memory.
-In the visual paired-comparison task, two identical pictures were presented side by side for a brief viewing period.
-After a delay, one of the previously viewed pictures was presented along with a new picture.
-Individuals looked more at the new picture than the old picture and the time spent looking was correlated with later recognition memory performance.
-On the other hand perceptual priming, thought to recruit non-declarative memory, was not linked to later recognition.
-(The perceptual priming arm of the design was not included in this replication.)
+The third study was a replication attempt of
+Manns, Stark, and Squire (2000) which aimed to show that the visual
+paired-comparison task, widely used in the patient literature, tapped
+into declarative memory. In the visual paired-comparison task, two
+identical pictures were presented side by side for a brief viewing
+period. After a delay, one of the previously viewed pictures was
+presented along with a new picture. Individuals looked more at the new
+picture than the old picture and the time spent looking was correlated
+with later recognition memory performance. On the other hand perceptual
+priming, thought to recruit non-declarative memory, was not linked to
+later recognition. (The perceptual priming arm of the design was not
+included in this replication.)
 
@@
 
-Our initial sample size was 51 participants for the first day of our experiment and 48 of them came back for the second day.
-Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test.
-Our final sample size was 45 participants.
+Our initial sample size was 51 participants for the first day of our
+experiment and 48 of them came back for the second day. Following Manns
+et al., we excluded 3 participants due to perfect performance on the
+recognition memory test. Our final sample size was 45 participants.
 
@@
 
-The task began with a 7-point eye-tracker calibration (each point was presented 3 times in a random order) and validation with 3 points (each presented once).
-The point locations were designed to focus calibration on the center of the screen and the middle of the left and right halves of the screen.
-The experiment was administered over the course of two consecutive days.
-It consisted of three sections: a presentation phase, a test phase, and a recognition test.
-The first two phases occurred on the first day, while the recognition test occurred on the second day.
-
-During the presentation phase, participants viewed 24 pairs of identical color photographs depicting common objects.
-Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
-The order of the photographs was randomized and different for each participant.
-After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
-
-After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
-During this phase, participants again viewed 24 pairs of photographs with an interstimulus duration of 5 seconds.
-In each pair, one photograph was previously seen during the presentation phase, while the other was new.
-Which pictures were old or new was counterbalanced across participants.
-For half of the participants in each counterbalancing group, the new and old photographs were reversed.
-
-Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
-It consisted of 48 photographs, presented one at a time.
-Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
-Half of the pohotographs had been viewed twice on the previous day and were deemed the ``targets.'' The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed ``foils.'' Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing `y' for yes and `n' for no.
-After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a ``pure guess'' to 5 as ``very sure.'' by clicking on the corresponding number on the screen.
-No feedback on their responses was given during the test.
+The task began with a 7-point eye-tracker calibration (each point was
+presented 3 times in a random order) and validation with 3 points (each
+presented once). The point locations were designed to focus calibration
+on the center of the screen and the middle of the left and right halves
+of the screen. The experiment was administered over the course of two
+consecutive days. It consisted of three sections: a presentation phase,
+a test phase, and a recognition test. The first two phases occurred on
+the first day, while the recognition test occurred on the second day.
+
+During the presentation phase, participants viewed 24 pairs of identical
+color photographs depicting common objects. Each pair was presented for
+5 seconds and an interval of 5 seconds elapsed before the next pair was
+shown. The order of the photographs was randomized and different for
+each participant. After completion of the presentation phase,
+participants were given a 5-minute break during which they could look
+away from the screen.
+
+After the break, they were prompted to complete the eye-tracking
+calibration again before beginning the test phase. During this phase,
+participants again viewed 24 pairs of photographs with an interstimulus
+duration of 5 seconds. In each pair, one photograph was previously seen
+during the presentation phase, while the other was new. Which pictures
+were old or new was counterbalanced across participants.
+For half of the participants in each counterbalancing group, the new and
+old photographs were
+reversed.
+
+Approximately 24 hours after completing the first session, with a leeway
+interval of 12 hours to accommodate busy schedules, participants were
+given the recognition test. It consisted of 48 photographs, presented
+one at a time. Each was shown on the screen for 1 second, followed by a
+1 second interstimulus interval. Half of the pohotographs had been
+viewed twice on the previous day and were deemed the ``targets.'' The
+other half depicted an object with the same name as an object in one of
+the old photographs, but had not been viewed before, deemed ``foils.''
+Each photograph remained on the screen until the participants indicated
+whether or not they had seen it before by pressing `y' for yes and `n'
+for no. After they pressed one of the two keys, a prompt on the screen
+asked them to rate their confidence in their answer from 1 as a ``pure
+guess'' to 5 as ``very sure.'' by clicking on the corresponding number on
+the screen. No feedback on their responses was given during the test.
 
@@
 
-There were two modifications we made to the methods of the original experiment.
-As we are only replicating the declarative memory component of the original experiment, we did not have a ``priming group.'' Therefore, we followed only the procedure for the ``looking group.'' Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.
+There were two modifications we made to the methods of the original
+experiment. As we are only replicating the declarative memory component
+of the original experiment, we did not have a ``priming group.''
+Therefore, we followed only the procedure for the ``looking group.''
+Additionally, for each section of the study, the stimuli was presented
+on a single screen instead of two screens due to the constraints of the
+online experiment format.
 
@@
 
-The fourth study was a replication attempt of Experiment 1 in Ryskin, Qi, Duff, and Brown-Schmidt (2017), which was closely modeled on Snedeker and Trueswell (2004).
-These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
-For example, in a sentence like ``Feel the frog with the feather,'' the phrase ``with the feather'' could be describing the frog, or it could be describing the instrument that should be used to do the ``feeling.'' When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb's ``bias'' (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
-.
+The fourth study was a replication attempt of Experiment 1 in
+Ryskin, Qi, Duff, and Brown-Schmidt (2017), which was closely modeled on
+Snedeker and Trueswell (2004). These studies used the
+visual world paradigm to show that listeners use knowledge of the
+co-occurrence statistics of verbs and syntactic structures to resolve
+ambiguity. For example, in a sentence like ``Feel the frog with the
+feather,'' the phrase ``with the feather'' could be describing the frog, or
+it could be describing the instrument that should be used to do the
+``feeling.'' When both options (a frog holding a feather and a feather by
+itself) are available in the visual display, listeners rely on the
+verb's ``bias'' (statistical co-occurrence either in norming or corpora)
+to rapidly choose an action while the sentence is unfolding. .
 
@@
 
-The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, \url{https://osf.io/x3c49/} (\url{https://osf.io/x3c49/}).
-The pre-registration for the study can be found at \url{https://osf.io/3v4pg} (\url{https://osf.io/3v4pg}).
+The stimuli, experimental code, and data and analysis scripts can be
+found on the Open Science Framework at the following link,
+\url{https://osf.io/x3c49/} (\url{https://osf.io/x3c49/}). The pre-registration
+for the study can be found at \url{https://osf.io/3v4pg}
+(\url{https://osf.io/3v4pg}).
 
@@
 
-58 (??) participants were paid \$XX for their participation .
-A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power.
-Note that the original study had a sample size of 24.
+58 (??) participants were paid \$XX for their participation
+. A sample size of 58 was chosen because we wanted to
+replicate the experiment with greater statistical power. Note that the
+original study had a sample size of 24.
 
@@
 
-After the eye-tracking calibration, participants went through an audio test so they could adjust the audio on their computer to a comfortable level.
-Before beginning the experiment, they were given instructions that four objects would appear, an audio prompt would play, and they should do their best to use their mouse to act out the instructions.
-They then went through three practice trials which were followed by 54 critical trials and 24 filler trials presented in a random order.
-
-During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., ``Rub the butterfly with the crayon''; see Figure XX)\footnote{In the original study, the pictures appeared one by one on the screen and their names were played as they appeared.
-We removed this introductory portion of the trial to save time}.
-Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects\footnote{ As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
-For example, the sentence ``locate the camel with the straw'' may not involve any clicking but rather only mousing over the camel.}.
-After the action was completed, the participants were instructed to press the space bar which led to a screen that said ``Click Here'' in the middle in order to remove bias in the eye and mouse movements from the previous trial.
-The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
+After the eye-tracking calibration, participants went through an audio
+test so they could adjust the audio on their computer to a comfortable
+level. Before beginning the experiment, they were given instructions
+that four objects would appear, an audio prompt would play, and they
+should do their best to use their mouse to act out the instructions.
+They then went through three practice trials which were followed by 54
+critical trials and 24 filler trials presented in a random order.
+
+During a trial, four pictures were displayed (target animal, target
+instrument, distractor animal, distractor instrument), one in each
+corner of the screen, and participants heard an audio prompt that
+contained instructions about the action they needed to act out (e.g.,
+``Rub the butterfly with the crayon''; see Figure XX)\footnote{In the original study, the pictures appeared one by one on the
+  screen and their names were played as they appeared. We removed this
+  introductory portion of the trial to save time}. Using their
+cursor, participants could act out the instructions by clicking on
+objects and moving them or motioning over the objects\footnote{As opposed to the original study we recorded mouse movement
+  instead of clicking behavior since not all of the audio prompts
+  required clicking. For example, the sentence ``locate the camel with
+  the straw'' may not involve any clicking but rather only mousing over
+  the camel.}. After the
+action was completed, the participants were instructed to press the
+space bar which led to a screen that said ``Click Here'' in the middle in
+order to remove bias in the eye and mouse movements from the previous
+trial. The experiment only allowed the participants to move on to the
+next trial once the audio was completely done playing and the mouse had
+been moved over at least one object.
 
@@
 
-The images and audios presented to the participants were the same stimuli used in the original study (available here ).
-The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
-Two lists of critical trials were made with different verb and instrument combinations (e.g., ``rub'' could be paired with ``panda'' and ``crayon'' in one list and ``panda'' and ``violin'' in the second list).
-Within each list, the same verb was presented twice but each time with a different target instrument and animal.
-The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
-The list of verbs used can be found in Appendix A of the original study.
+The images and audios presented to the participants were the same
+stimuli used in the original study (available here ). The critical
+trials were divided into modifier-biased, instrument-biased, and
+equibiased conditions, and the filler trials did not contain ambiguous
+instructions. Two lists of critical trials were made with different verb
+and instrument combinations (e.g., ``rub'' could be paired with ``panda''
+and ``crayon'' in one list and ``panda'' and ``violin'' in the second list).
+Within each list, the same verb was presented twice but each time with a
+different target instrument and animal. The lists were randomly assigned
+to the participants to make sure the effects were not caused by the
+properties of the animal or instrument images used. The list of verbs
+used can be found in Appendix A of the original study.
 
@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within \textcolor{red}{XX} pixels of the calibration point, varied substantially (between 2.22 and 97.36 \%).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between 2.22 and 97.36 \%).
 The quality of a participant's calibration significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.29, \emph{p} \textless{} 0.05).
@@
 
-The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003), which found that human gaze is actively involved in preference formation.
-Separate sets of participants were shown pairs of human faces and asked either to choose which one they found more attractive or which they felt was rounder.
-Prior to making their explicit selection, participants were increasingly likely to be fixating the face they ultimately chose, though this effect was significantly weaker for roundness discrimination.
-
-Note that Shimojo and colleagues compare five conditions, of which we replicate only the two that figure most prominently in their conclusions: the ``face-attractiveness-difficult task'' and the ``face-roundness task''.
+The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003),
+which found that human gaze is actively involved in preference
+formation. Separate sets of participants were shown pairs of human faces
+and asked either to choose which one they found more attractive or which
+they felt was rounder. Prior to making their explicit selection,
+participants were increasingly likely to be fixating the face they
+ultimately chose, though this effect was significantly weaker for
+roundness discrimination.
+
+Note that Shimojo and colleagues compare five conditions, of which we
+replicate only the two that figure most prominently in their
+conclusions: the ``face-attractiveness-difficult task'' and the
+``face-roundness task''.
 
@@
 
-All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at \url{https://osf.io/eubsc/} (\url{https://osf.io/eubsc/}).
-The study pre-registration is available at \url{https://osf.io/tv57s} (\url{https://osf.io/tv57s}).
+All stimuli, experiment scripts, data, and analysis scripts are
+available on the Open Science Framework at \url{https://osf.io/eubsc/}
+(\url{https://osf.io/eubsc/}). The study pre-registration is available at
+\url{https://osf.io/tv57s} (\url{https://osf.io/tv57s}).
 
@@
 
-50 participants for the main task were recruited on Prolific and were paid \$XX.
-8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations.
-After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task.
-The original sample size in Shimojo et al.~(2003) was 10 participants total.
-\#\#\# Procedure and Design
-
-At the beginning of the experimental task, participants completed a 9-point eye-tracker calibration (each point appeared 3 times in random order) and 3-point validation.
-The validation point appeared once at center, middle left, and middle right locations in random order.
-
-During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure XX).
-Participants were randomly assigned to one of two tasks: attractiveness or shape judgment.
-In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
-They pressed the ``a'' key on their keyboard to select the face on the left and the ``d'' key to select the face on the right.
-A fixation cross appeared in the center of the screen between each set of faces.
-Participants were asked to look at this fixation cross in order to reset their gaze in between trials (???).
-The order of the 19 face pairs was random for each participant.
+50 participants for the main task were recruited on Prolific and were
+paid \$XX. 8 subjects, 4 from the attractiveness task group and 4 from
+the roundness task group, were excluded for incorrect validations.
+After this
+data exclusion, we ended up with 21 participants each for the
+attractiveness task and the roundness task. The original sample size in
+Shimojo et al.~(2003) was 10 participants total. \#\#\# Procedure and
+Design
+
+At the beginning of the experimental task, participants completed a
+9-point eye-tracker calibration (each point appeared 3 times in random
+order) and 3-point validation. The validation point appeared once at
+center, middle left, and middle right locations in random order.
+
+During each trial of the main task, two faces were displayed on the two
+halves of the screen, one on the left and one on the right (as in Figure
+XX). Participants were randomly assigned to one of two tasks:
+attractiveness or shape judgment. In the attractiveness task,
+participants were asked to chose the more attractice face in the pair
+and in the shape judgment task participants were asked to pick the face
+that appeared rounder. They pressed the ``a'' key on their keyboard to
+select the face on the left and the ``d'' key to select the face on the
+right. A fixation cross appeared in the center of the screen between
+each set of faces. Participants were asked to look at this fixation
+cross in order to reset their gaze in between trials (???). The order of
+the 19 face pairs was random for each participant.
 
@@
 
-The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset.
-(The face images used in Shimojo et al.~were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
-27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They were paid \$XX for completing the experiment.
-Data from 3 participants was excluded because their mode response made up more than 50\% of their total responses , for a total of 24 participants in the norming.
-They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
-Faces were presented one at a time and in a random order for each participant.
-Following Shimojo et al., 19 face pairs were made by matching two faces that had a difference in mean attractiveness ratings that was 0.25 points or lower and that matched in gender, race, and age group (young adult, adult, or older adult).
+The faces in our replication were selected from a set of 1,000 faces
+within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et
+al.~were from the Ekman face database and the AR face database.) These
+images were chosen because the person in each image was looking at the
+camera with a fairly neutral facial expression and appeared to be over
+the age of 18. 27 participants were recruited on Prolific to participate
+in stimulus norming (for attractiveness). They were paid \$XX for
+completing the experiment. Data from 3 participants was excluded because
+their mode response made up more than 50\% of their total responses
+, for a total of 24 participants
+in the norming. They each viewed all 172 faces and were asked to rate
+them on a scale from 1 (less attractive) to 7 (more attractive) using a
+slider. Faces were presented one at a time and in a random order for
+each participant. Following Shimojo et al., 19 face pairs were made by
+matching two faces that had a difference in mean attractiveness ratings
+that was 0.25 points or lower and that matched in gender, race, and age
+group (young adult, adult, or older adult).
 
@@
 
-In the original study, a video-based eye tracker was used.
-The eye movements of participants were recorded with a digital camera downsampled to 33.3 Hz, with eye position was then determined automatically with MediaAnalyzer software.
-In our study, subjects supplied their own cameras, so hardware sampling rate varied.
-However, data was collected at 20 Hz.{[}TODO - CONFIRM{]}
+In the original study, a video-based eye tracker was used. The eye
+movements of participants were recorded with a digital camera
+downsampled to 33.3 Hz, with eye position was then determined
+automatically with MediaAnalyzer software. In our study, subjects
+supplied their own cameras, so hardware sampling rate varied. However,
+data was collected at 20 Hz.{[}TODO - CONFIRM{]}
 
@@
 \item
-  Pooling data from all experiments we can look at patterns in the calibration and validation data
+  Pooling data from all experiments we can look at patterns in the
+  calibration and validation data
 \end{itemize}

### 2022-05-09 manuscript.Rmd
Some initial elaboration of the Introduction.

@@
 
-*Present work*
+# Present work
 
-In the present work, we attempted to replicate five eye-tracking studies
-from the cognitive science literature using the eye-tracking plug-in
-from `jsPsych`, a Javascript library for running behavioral experiments
-in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. The plug-in
-relies on the `webgazer.js` library for webcam eye-tracking
-[@papoutsaki2016webgazer]. The goal was to examine the strengths and
-weaknesses of webcam eye-tracking for common paradigms in cognitive
-science. The studies were chosen to cover a variety of topic areas
-(e.g., memory, decision-making, psycholinguistics) and paradigms (two
+In order to validate online eyetracking measures, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
+Ideally, we would only attempt to replicate studies where the original measurements have small error bars and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
+
+In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability.
+We addressed this in several ways.
+First, replicating five very different studies from different research traditions decreases our reliance on any one study.
+Second, we include several ``sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
+(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for XXX of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
+
+## Selection of Studies
+
+We chose five high-impact eyetracking studies involve adult subjects.
+(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
 halves of the screen, visual world paradigm with four quadrants, visual
-world paradigm with "natural" scenes). ...
+world paradigm with "natural" scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
+
+The final selection of studies was FUBAR...
 
@@
 Vassar College Institutional Review Board.
+
+In order to have adequate statistical power and precision, we aimed for XXXX participants per experiment.
+
+## Equipment
+
+We used a novel port of the `webgazer.js` library for webcam eyetracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments
+in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. We made several changes to webgazer.js in order to improve data quality. FUBAR
 

### 2022-05-18 manuscript.Rmd
add information about statistical power

@@
 
-In order to have adequate statistical power and precision, we aimed for XXXX participants per experiment.
+In order to have adequate statistical power and precision, we aimed for 2.5x the
+sample size of the original experiment, following the heuristic of Simonsohn @simonsohn215.
+In study 5, the original sample size was so small that we opted to collect 5x the 
+number of participants to increase precision. Because of budget and time constraints 
+we were unable to  replace the data for subjects who were excluded or whose data was 
+missing due to technical failures.
 

### 2022-05-18 manuscript.Rmd
add description of webgazer modifications (#29)

@@
 
-We used a novel port of the `webgazer.js` library for webcam eyetracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments
-in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. We made several changes to webgazer.js in order to improve data quality. FUBAR
+We used a fork of the `webgazer.js` library for webcam eyetracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments
+in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
+Our fork included changes to webgazer.js in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant.
+Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing.
+This modification is similar to what Yang and Krajbich @yang2021webcam reported improved the sampling rate in their study of webgazer.
+We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.
 

### 2022-06-15 manuscript.Rmd
add full author list

@@
 author:
-  - name          : "Josh de Leeuw"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+  - name: Joshua R. de Leeuw
+    affiliation: '1'
+    role:
       - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "et al."
-    affiliation   : "1,2"
+      - Data curation
+      - Formal analysis
+      - Investigation
+      - Methodology
+      - Project administration
+      - Software
+      - Supervision
+      - Validation
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    corresponding: yes
+    email: jdeleeuw@vassar.edu
+    address: 124 Raymond Ave, Poughkeepsie, NY 12604, USA
+  - name: Rachel Ryskin
+    affiliation: '2'
     role:
-      - Writing - Review & Editing
+      - Conceptualization
+      - Formal analysis
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    email: rryskin@ucmerced.edu
+  - name: Ariel N. James
+    affiliation: '3'
+    role:
+      - Conceptualization
+      - Formal analysis
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    email: ajames2@macalester.edu
+  - name: Joshua K. Hartshorne
+    affiliation: '4'
+    role:
+      - Conceptualization
+      - Formal analysis
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    email: joshua.hartshorne@bc.edu
+  - name: Haylee Backs
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: hbacks@vassar.edu
+  - name: Nandeeta Bala
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: nbala@vassar.edu
+  - name: Laila Barcenas-Meade
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: lbarcenasmeade@vassar.edu
+  - name: Samata Bhattarai
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: sbhattarai@vassar.edu
+  - name: Tessa Charles
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: tcharles@vassar.edu
+  - name: Gerasimos Copoulos
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: gcopoulos@vassar.edu
+  - name: Claire Coss
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: ccoss@vassar.edu
+  - name: Alexander Eisert
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: aeisert@vassar.edu
+  - name: Elena Furuhashi
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: efuruhashi@vassar.edu
+  - name: Keara Ginell
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: kginell@vassar.edu
+  - name: Anna Guttman-McCabe
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: aguttmanmccabe@vassar.edu
+  - name: Emma (Chaz) Harrison
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: eharrison@vassar.edu
+  - name: Laura Hoban
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: lhoban@vassar.edu
+  - name: William A. Hwang
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: whwang@vassar.edu
+  - name: Claire Iannetta
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: ciannetta@vassar.edu
+  - name: Kristen M. Koenig
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: kkoenig@vassar.edu
+  - name: Chauncey Lo
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: chaunceylo@vassar.edu
+  - name: Victoria Palone
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: vpalone@vassar.edu
+  - name: Gina Pepitone
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: gpepitone@vassar.edu
+  - name: Margaret Ritzau
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: mritzau@vassar.edu
+  - name: Yi Hua Sung
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: ysung@vassar.edu
+  - name: Lauren Thompson
+    affiliation: '1'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: lthompson@vassar.edu
 
 affiliation:
-  - id            : "1"
-    institution   : "Vassar College"
-  - id            : "2"
-    institution   : "XX"
+  - id: '1'
+    institution: Cognitive Science Department, Vassar College
+  - id: '2'
+    institution: Department of Cognitive & Information Science, University of California,
+      Merced
+  - id: '3'
+    institution: Psychology Department, Macalester College
+  - id: '4'
+    institution: Department of Psychology & Neuroscience, Boston College
 

### 2022-06-15 manuscript.tex
add full author list

--- 2022-04-21 manuscript.tex
@@
   pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
-  pdfauthor={Josh de Leeuw1 \& et al.1,2},
+  pdfauthor={Joshua R.
+de Leeuw1, Rachel Ryskin2, Ariel N.
+James3, Joshua K.
+Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A.
+Hwang1, Claire Iannetta1, Kristen M.
+Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
   pdflang={en-EN},
@@
 \title{Eye-tracking on the web: lessons learned from replicating 5 experiments}
-\author{Josh de Leeuw\textsuperscript{1} \& et al.\textsuperscript{1,2}}
+\author{Joshua R.
+de Leeuw\textsuperscript{1}, Rachel Ryskin\textsuperscript{2}, Ariel N.
+James\textsuperscript{3}, Joshua K.
+Hartshorne\textsuperscript{4}, Haylee Backs\textsuperscript{1}, Nandeeta Bala\textsuperscript{1}, Laila Barcenas-Meade\textsuperscript{1}, Samata Bhattarai\textsuperscript{1}, Tessa Charles\textsuperscript{1}, Gerasimos Copoulos\textsuperscript{1}, Claire Coss\textsuperscript{1}, Alexander Eisert\textsuperscript{1}, Elena Furuhashi\textsuperscript{1}, Keara Ginell\textsuperscript{1}, Anna Guttman-McCabe\textsuperscript{1}, Emma (Chaz) Harrison\textsuperscript{1}, Laura Hoban\textsuperscript{1}, William A.
+Hwang\textsuperscript{1}, Claire Iannetta\textsuperscript{1}, Kristen M.
+Koenig\textsuperscript{1}, Chauncey Lo\textsuperscript{1}, Victoria Palone\textsuperscript{1}, Gina Pepitone\textsuperscript{1}, Margaret Ritzau\textsuperscript{1}, Yi Hua Sung\textsuperscript{1}, \& Lauren Thompson\textsuperscript{1}}
 \date{}
@@
 
-The authors made the following contributions. Josh de Leeuw: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; et al.: Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to Josh de Leeuw, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+The authors made the following contributions.
+Joshua R.
+de Leeuw: Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Software, Supervision, Validation, Visualization, Writing - original draft, Writing - review \& editing; Rachel Ryskin: Conceptualization, Formal analysis, Visualization, Writing - original draft, Writing - review \& editing; Ariel N.
+James: Conceptualization, Formal analysis, Visualization, Writing - original draft, Writing - review \& editing; Joshua K.
+Hartshorne: Conceptualization, Formal analysis, Visualization, Writing - original draft, Writing - review \& editing; Haylee Backs: Investigation, Methodology, Software; Nandeeta Bala: Investigation, Methodology, Software; Laila Barcenas-Meade: Investigation, Methodology, Software; Samata Bhattarai: Investigation, Methodology, Software; Tessa Charles: Investigation, Methodology, Software; Gerasimos Copoulos: Investigation, Methodology, Software; Claire Coss: Investigation, Methodology, Software; Alexander Eisert: Investigation, Methodology, Software; Elena Furuhashi: Investigation, Methodology, Software; Keara Ginell: Investigation, Methodology, Software; Anna Guttman-McCabe: Investigation, Methodology, Software; Emma (Chaz) Harrison: Investigation, Methodology, Software; Laura Hoban: Investigation, Methodology, Software; William A.
+Hwang: Investigation, Methodology, Software; Claire Iannetta: Investigation, Methodology, Software; Kristen M.
+Koenig: Investigation, Methodology, Software; Chauncey Lo: Investigation, Methodology, Software; Victoria Palone: Investigation, Methodology, Software; Gina Pepitone: Investigation, Methodology, Software; Margaret Ritzau: Investigation, Methodology, Software; Yi Hua Sung: Investigation, Methodology, Software; Lauren Thompson: Investigation, Methodology, Software.
+
+Correspondence concerning this article should be addressed to Joshua R.
+de Leeuw, 124 Raymond Ave, Poughkeepsie, NY 12604, USA.
+E-mail: \href{mailto:jdeleeuw@vassar.edu}{\nolinkurl{jdeleeuw@vassar.edu}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Vassar College\\\textsuperscript{2} XX}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Cognitive Science Department, Vassar College\\\textsuperscript{2} Department of Cognitive \& Information Science, University of California, Merced\\\textsuperscript{3} Psychology Department, Macalester College\\\textsuperscript{4} Department of Psychology \& Neuroscience, Boston College}
 
@@
 
-\emph{Present work}
-
-In the present work, we attempted to replicate five eye-tracking studies
-from the cognitive science literature using the eye-tracking plug-in
-from \texttt{jsPsych}, a Javascript library for running behavioral experiments
-in a web browser (de Leeuw, 2015). The plug-in
-relies on the \texttt{webgazer.js} library for webcam eye-tracking
-(Papoutsaki et al., 2016). The goal was to examine the strengths and
-weaknesses of webcam eye-tracking for common paradigms in cognitive
-science. The studies were chosen to cover a variety of topic areas
-(e.g., memory, decision-making, psycholinguistics) and paradigms (two
+\hypertarget{present-work}{%
+\section{Present work}\label{present-work}}
+
+In order to validate online eyetracking measures, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
+Ideally, we would only attempt to replicate studies where the original measurements have small error bars and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
+
+In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability.
+We addressed this in several ways.
+First, replicating five very different studies from different research traditions decreases our reliance on any one study.
+Second, we include several ``sanity check'\,' analyses, such as the correlation between calibration accuracy and effect size.
+(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for XXX of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
+
+\hypertarget{selection-of-studies}{%
+\subsection{Selection of Studies}\label{selection-of-studies}}
+
+We chose five high-impact eyetracking studies involve adult subjects.
+(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
 halves of the screen, visual world paradigm with four quadrants, visual
-world paradigm with ``natural'' scenes). \ldots{}
+world paradigm with ``natural'' scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
+
+The final selection of studies was FUBAR\ldots{}
 
@@
 Vassar College Institutional Review Board.
+
+In order to have adequate statistical power and precision, we aimed for 2.5x the
+sample size of the original experiment, following the heuristic of Simonsohn (\textbf{simonsohn215?}).
+In study 5, the original sample size was so small that we opted to collect 5x the
+number of participants to increase precision. Because of budget and time constraints
+we were unable to replace the data for subjects who were excluded or whose data was
+missing due to technical failures.
+
+\hypertarget{equipment}{%
+\subsection{Equipment}\label{equipment}}
+
+We used a fork of the \texttt{webgazer.js} library for webcam eyetracking (Papoutsaki et al., 2016), implemented in \texttt{jsPsych}, a Javascript library for running behavioral experiments
+in a web browser (de Leeuw, 2015).
+Our fork included changes to webgazer.js in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant.
+Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing.
+This modification is similar to what Yang and Krajbich Yang and Krajbich (2021) reported improved the sampling rate in their study of webgazer.
+We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.
 
@@
 
-We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.3; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.7; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jsonlite} (Version 1.7.2; Ooms, 2014), \emph{lme4} (Version 1.1.27.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.3.4; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.1; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.1; Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.2.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.9; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.4.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.79; Roundness: R\textsuperscript{2} = 0.60).
-However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.35).
+However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.36).
 Descriptively, the results do not look substantially different (Fig.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-yang2021webcam}{}}%
+Yang, X., \& Krajbich, I. (2021). Webcam-based online eye-tracking for behavioral research. \emph{Judgment and Decision Making}, \emph{16}(6), 1486.
+
 \end{CSLReferences}

### 2022-06-16 manuscript.Rmd
add study selection table #31

@@
 
-We chose five high-impact eyetracking studies involve adult subjects.
-(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
+<!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->
+
+We chose five high-impact eyetracking studies involving adult subjects.
+(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two
 halves of the screen, visual world paradigm with four quadrants, visual
-world paradigm with "natural" scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
+world paradigm with "natural" scenes).
+As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
+TABLE X provides an overview of the five studies we selected.
 
-The final selection of studies was FUBAR...
+```{r Create Studies Table, echo=FALSE}
+studies_table <- data.frame(
+  Citation = c(
+    "Altmann & Kamide, 1999",
+    "Johansson & Johansson, 2013",
+    "Manns, Stark, & Squire, 2000",
+    "Ryskin et al., 2017",
+    "Shimojo et al., 2003"
+  ),
+  `Topic Area` = c(
+    "Psycholinguistics",
+    "Memory",
+    "Memory",
+    "Psycholinguistics",
+    "Decision Making"
+  ),
+  `Paradigm` = c(
+    "Natural Scenes",
+    "Four Quadrants",
+    "Two Halves",
+    "Four Quadrants",
+    "Two Halves"
+  ),
+  `Citations (June 2022, Google Scholar)` = c(
+    1840,
+    190,
+    127,
+    75,
+    964
+  ),
+  check.names = FALSE
+)
+
+apa_table(
+  studies_table,
+  caption = "Studies selected for replication attempts",
+  font_size = "small"
+)
+
+```
 

### 2022-06-16 manuscript.tex
add study selection table #31

@@
 
-We chose five high-impact eyetracking studies involve adult subjects.
-(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
+We chose five high-impact eyetracking studies involving adult subjects.
+(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two
 halves of the screen, visual world paradigm with four quadrants, visual
-world paradigm with ``natural'' scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
-
-The final selection of studies was FUBAR\ldots{}
+world paradigm with ``natural'' scenes).
+As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
+TABLE X provides an overview of the five studies we selected.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:Create Studies Table}Studies selected for replication attempts}
+
+\small{
+
+\begin{tabular}{llll}
+\toprule
+Citation & \multicolumn{1}{c}{Topic Area} & \multicolumn{1}{c}{Paradigm} & \multicolumn{1}{c}{Citations (June 2022, Google Scholar)}\\
+\midrule
+Altmann \& Kamide, 1999 & Psycholinguistics & Natural Scenes & 1,840.00\\
+Johansson \& Johansson, 2013 & Memory & Four Quadrants & 190.00\\
+Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 127.00\\
+Ryskin et al., 2017 & Psycholinguistics & Four Quadrants & 75.00\\
+Shimojo et al., 2003 & Decision Making & Two Halves & 964.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2022-08-20 group-b/E2-analysis-replication.Rmd
saved fig

@@
   scale_fill_brewer(palette="Set1",)+
-  theme_classic()+
+  theme_classic(base_size = 25)+
+  coord_cartesian(ylim = c(0, 0.4))+
   labs(x = "Quadrant", y = "Mean proportion of looks")+
@@
 saveRDS(fig, "output/ETfig.rds")
-
+ggsave("output/ETfig.png", plot = fig, width  = 8.5, height = 5.5)
 ```

### 2022-08-24 group-c/E3-calibration-figure.Rmd
some work on group C / exp 3

---
title: "Experiment 3: Calibration Figure"
output: html_notebook
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
```

```{r include=FALSE}
calibration_points <- matrix(c(
  c(10,50),
  c(50,50),
  c(90,50),
  c(25,25),
  c(25,75),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)

colnames(calibration_points) <- c("x","y")

df <- as_tibble(calibration_points)
```

```{r echo=FALSE, fig.cap="Calibration point locations for Experiment 3."}
ggplot(df, aes(x=x, y=y))+
  geom_point(size=3)+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  theme(panel.border = element_rect(color="black", fill=NA))
```

### 2022-08-25 group-c/E3-calibration-figure.Rmd
update calibration figure to include validation points

@@
 
+validation_points <- matrix(c(
+  c(10,50),
+  c(50,50),
+  c(90,50)
+), ncol=2, byrow=T)
+
 colnames(calibration_points) <- c("x","y")
+colnames(validation_points) <- c("x","y")
 
-df <- as_tibble(calibration_points)
+df <- as_tibble(calibration_points) %>% bind_rows(as_tibble(validation_points))
+df$point <- c(rep("calibration", nrow(calibration_points)), rep("validation", nrow(validation_points)))
 ```
 
-```{r echo=FALSE, fig.cap="Calibration point locations for Experiment 3."}
-ggplot(df, aes(x=x, y=y))+
-  geom_point(size=3)+
+```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
+ggplot(df, aes(x=x, y=y, shape=point, color=point))+
+  geom_point(size=3, stroke=1)+
+  scale_shape_manual(values=c(16,3))+
+  scale_color_manual(values=c("black", "red"))+
   coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
   theme_void()+
-  theme(panel.border = element_rect(color="black", fill=NA))
+  labs(color=NULL, shape=NULL)+
+  theme(panel.border = element_rect(color="black", fill=NA),
+        legend.position = c(0.995,0.01),
+        legend.justification = c(1,0),
+        legend.background = element_rect(color="black", fill=NA),
+        legend.margin = margin(2,3,3,3))
 ```

### 2022-08-25 manuscript.tex
update calibration figure to include validation points

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
-  pdfauthor={Joshua R.
-de Leeuw1, Rachel Ryskin2, Ariel N.
-James3, Joshua K.
-Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A.
-Hwang1, Claire Iannetta1, Kristen M.
-Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
+  pdfauthor={Joshua R.
+de Leeuw1, Rachel Ryskin2, Ariel N.
+James3, Joshua K.
+Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A.
+Hwang1, Claire Iannetta1, Kristen M.
+Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-In order to have adequate statistical power and precision, we aimed for 2.5x the
-sample size of the original experiment, following the heuristic of Simonsohn (\textbf{simonsohn215?}).
-In study 5, the original sample size was so small that we opted to collect 5x the
-number of participants to increase precision. Because of budget and time constraints
-we were unable to replace the data for subjects who were excluded or whose data was
+In order to have adequate statistical power and precision, we aimed for
+2.5x the sample size of the original experiment, following the heuristic
+of Simonsohn (\textbf{simonsohn215?}). In study 5, the original sample size was so
+small that we opted to collect 5x the number of participants to increase
+precision. Because of budget and time constraints we were unable to
+replace the data for subjects who were excluded or whose data was
 missing due to technical failures.
@@
 
-We used a fork of the \texttt{webgazer.js} library for webcam eyetracking (Papoutsaki et al., 2016), implemented in \texttt{jsPsych}, a Javascript library for running behavioral experiments
-in a web browser (de Leeuw, 2015).
-Our fork included changes to webgazer.js in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant.
-Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing.
-This modification is similar to what Yang and Krajbich Yang and Krajbich (2021) reported improved the sampling rate in their study of webgazer.
-We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.
+We used a fork of the \texttt{webgazer.js} library for webcam eyetracking
+(Papoutsaki et al., 2016), implemented in \texttt{jsPsych}, a Javascript
+library for running behavioral experiments in a web browser
+(de Leeuw, 2015). Our fork included changes to
+webgazer.js in order to improve data quality for experiments in which
+the precise timing of stimulus onsets is relevant. Specifically, we
+implemented a polling mode so that gaze predictions could be requested
+at a regular interval, which improved the sampling rate considerably in
+informal testing. This modification is similar to what Yang and Krajbich
+Yang and Krajbich (2021) reported improved the sampling rate in their study of
+webgazer. We also adjusted the mechanism for recording time stamps of
+each gaze prediction, so that the time stamp reported by webgazer is
+based on when the video frame is received and not when the computation
+of the gaze point is finished.
 
@@
 
-The third study was a replication attempt of
-Manns, Stark, and Squire (2000) which aimed to show that the visual
-paired-comparison task, widely used in the patient literature, tapped
-into declarative memory. In the visual paired-comparison task, two
-identical pictures were presented side by side for a brief viewing
-period. After a delay, one of the previously viewed pictures was
-presented along with a new picture. Individuals looked more at the new
-picture than the old picture and the time spent looking was correlated
-with later recognition memory performance. On the other hand perceptual
-priming, thought to recruit non-declarative memory, was not linked to
-later recognition. (The perceptual priming arm of the design was not
-included in this replication.)
+The third study was a partial replication attempt of
+Manns, Stark, and Squire (2000). This experiment used the visual
+paired-comparison, which involves presenting a previously-viewed image
+and novel image together and measuring the proportion of time spent
+looking at each image. The expected pattern of results is that
+participants will look more at novel objects. They
+Manns et al. (2000) hypothesized that this pattern of
+behavior could be used to measure the strength of memories. If a viewer
+has a weak memory of the old image, then they may look at the old and
+new images roughly the same amount of time. They tested this in two
+ways. First, they showed participants a set of images, waited five
+minutes, and then paired those images with novel images. They found that
+participants spent more time (58.8\% of total time) looking at the novel
+images. They then measured memory performance one day later and found
+that participants were more likely to recall images that they had spent
+less time looking at during the visual paired-comparison task the
+previous day.
 
@@
 
+The stimuli, experimental code, and data and analysis scripts can be
+found on the Open Science Framework at \url{https://osf.io/k63b9/}
+(\url{https://osf.io/k63b9/}). The pre-registration for the study can be
+found at \url{https://osf.io/48jsv} (\url{https://osf.io/48jsv}). We
+inadvertently did not create a formal pre-registration using the OSF
+registries tool, but this document contains the same information and is
+time stamped prior to the start of data collection.
+
 \hypertarget{participants-3}{%
@@
 
-Our initial sample size was 51 participants for the first day of our
-experiment and 48 of them came back for the second day. Following Manns
-et al., we excluded 3 participants due to perfect performance on the
-recognition memory test. Our final sample size was 45 participants.
+Our pre-registered target was 50 participants. 51 participants completed
+the first day of the experiment and 48 completed the second day.
+Following Manns et al., we excluded 3 participants due to perfect
+performance on the recognition memory test because this prevents
+comparison of gaze data for recalled vs.~non-recalled images. Our final
+sample size was 45 participants.
 
@@
 on the center of the screen and the middle of the left and right halves
-of the screen. The experiment was administered over the course of two
+of the screen.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
+\caption{\label{fig:unnamed-chunk-36}Calibration and validation point locations for Experiment 3.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.}
+\end{figure}
+
+The experiment was administered over the course of two
 consecutive days. It consisted of three sections: a presentation phase,
@@
 one at a time. Each was shown on the screen for 1 second, followed by a
-1 second interstimulus interval. Half of the pohotographs had been
+1 second interstimulus interval. Half of the photographs had been
 viewed twice on the previous day and were deemed the ``targets.'' The

### 2022-09-15 manuscript.tex
knit manuscript

--- 2022-06-16 manuscript.tex
@@
 
-We used R (Version 4.2.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.9; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.4.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.3; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.7; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jsonlite} (Version 1.7.2; Ooms, 2014), \emph{lme4} (Version 1.1.27.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.3.4; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.1; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.1; Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.79; Roundness: R\textsuperscript{2} = 0.60).
-However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.36).
+However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.35).
 Descriptively, the results do not look substantially different (Fig.

### 2022-09-15 manuscript.Rmd

@@
 
-In order to have adequate statistical power and precision, we aimed for 2.5x the
-sample size of the original experiment, following the heuristic of Simonsohn @simonsohn215.
-In study 5, the original sample size was so small that we opted to collect 5x the 
-number of participants to increase precision. Because of budget and time constraints 
-we were unable to  replace the data for subjects who were excluded or whose data was 
+In order to have adequate statistical power and precision, we aimed for
+2.5x the sample size of the original experiment, following the heuristic
+of Simonsohn @simonsohn215. In study 5, the original sample size was so
+small that we opted to collect 5x the number of participants to increase
+precision. Because of budget and time constraints we were unable to
+replace the data for subjects who were excluded or whose data was
 missing due to technical failures.
@@
 
-We used a fork of the `webgazer.js` library for webcam eyetracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments
-in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].
-Our fork included changes to webgazer.js in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant.
-Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing.
-This modification is similar to what Yang and Krajbich @yang2021webcam reported improved the sampling rate in their study of webgazer.
-We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.
+We used a fork of the `webgazer.js` library for webcam eyetracking
+[@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript
+library for running behavioral experiments in a web browser
+[@deleeuwJsPsychJavaScriptLibrary2015]. Our fork included changes to
+webgazer.js in order to improve data quality for experiments in which
+the precise timing of stimulus onsets is relevant. Specifically, we
+implemented a polling mode so that gaze predictions could be requested
+at a regular interval, which improved the sampling rate considerably in
+informal testing. This modification is similar to what Yang and Krajbich
+@yang2021webcam reported improved the sampling rate in their study of
+webgazer. We also adjusted the mechanism for recording time stamps of
+each gaze prediction, so that the time stamp reported by webgazer is
+based on when the video frame is received and not when the computation
+of the gaze point is finished.
 
@@
 
-The third study was a replication attempt of
-@mannsVisualPairedcomparisonTask2000 which aimed to show that the visual
-paired-comparison task, widely used in the patient literature, tapped
-into declarative memory. In the visual paired-comparison task, two
-identical pictures were presented side by side for a brief viewing
-period. After a delay, one of the previously viewed pictures was
-presented along with a new picture. Individuals looked more at the new
-picture than the old picture and the time spent looking was correlated
-with later recognition memory performance. On the other hand perceptual
-priming, thought to recruit non-declarative memory, was not linked to
-later recognition. (The perceptual priming arm of the design was not
-included in this replication.)
+The third study was a partial replication attempt of
+@mannsVisualPairedcomparisonTask2000. This experiment used the visual
+paired-comparison, which involves presenting a previously-viewed image
+and novel image together and measuring the proportion of time spent
+looking at each image. The expected pattern of results is that
+participants will look more at novel objects. They
+@mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of
+behavior could be used to measure the strength of memories. If a viewer
+has a weak memory of the old image, then they may look at the old and
+new images roughly the same amount of time. They tested this in two
+ways. First, they showed participants a set of images, waited five
+minutes, and then paired those images with novel images. They found that
+participants spent more time (58.8% of total time) looking at the novel
+images. They then measured memory performance one day later and found
+that participants were more likely to recall images that they had spent
+less time looking at during the visual paired-comparison task the
+previous day.
 
@@
 
+The stimuli, experimental code, and data and analysis scripts can be
+found on the Open Science Framework at <https://osf.io/k63b9/>
+(<https://osf.io/k63b9/>). The pre-registration for the study can be
+found at <https://osf.io/48jsv> (<https://osf.io/48jsv>). We
+inadvertently did not create a formal pre-registration using the OSF
+registries tool, but this document contains the same information and is
+time stamped prior to the start of data collection. <!-- Students failed
+to pre-register this one and I missed it. There's an unofficial
+pre-registration in the OSF site. -->
+
 ### Participants
 
-Our initial sample size was 51 participants for the first day of our
-experiment and 48 of them came back for the second day. Following Manns
-et al., we excluded 3 participants due to perfect performance on the
-recognition memory test. Our final sample size was 45 participants.
+Our pre-registered target was 50 participants. 51 participants completed
+the first day of the experiment and 48 completed the second day.
+Following Manns et al., we excluded 3 participants due to perfect
+performance on the recognition memory test because this prevents
+comparison of gaze data for recalled vs. non-recalled images. Our final
+sample size was 45 participants.
 
@@
 on the center of the screen and the middle of the left and right halves
-of the screen. The experiment was administered over the course of two
+of the screen.
+
+```{r E3-calibration-figure, child='group-c/E3-calibration-figure.Rmd'}
+
+```
+
+The experiment was administered over the course of two
 consecutive days. It consisted of three sections: a presentation phase,
@@
 one at a time. Each was shown on the screen for 1 second, followed by a
-1 second interstimulus interval. Half of the pohotographs had been
+1 second interstimulus interval. Half of the photographs had been
 viewed twice on the previous day and were deemed the "targets." The

### 2022-09-25 group-a/E1-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

--- 2022-08-25 group-c/E3-calibration-figure.Rmd
@@
 ---
-title: "Experiment 3: Calibration Figure"
-output: html_notebook
+title: "Experiment 1: Calibration Figure"
+output: pdf
 ---
@@
 ```{r include=FALSE}
+# calib: 
+    # //top
+    # [15, 2],
+    # [85, 2],
+    # //bottom
+    # [15, 95],
+    # [85, 95],
+    # 
+    # //inner top
+    # [32.5, 26],
+    # [67.5, 26],
+    # //inner bottom
+    # [32.5, 72.5],
+    # [67.5, 72.5],
+    # 
+    # [50, 50]
 calibration_points <- matrix(c(
-  c(10,50),
-  c(50,50),
-  c(90,50),
-  c(25,25),
-  c(25,75),
-  c(75,25),
-  c(75,75)
+  c(15,2),
+  c(85,2),
+  c(15,95),
+  c(85,95),
+  c(32.5,26),
+  c(67.5,26),
+  c(32.5,72.5),
+  c(67.5,72.5),
+  c(50,50)
 ), ncol=2, byrow=T)
-
+# valid: 
+#      [,1] [,2]
+ # [1,] 15.0  2.0
+ # [2,] 85.0  2.0
+ # [3,] 15.0 95.0
+ # [4,] 85.0 95.0
+ # [5,] 22.5 26.0
+ # [6,] 67.5 26.0
+ # [7,] 22.5 72.5
+ # [8,] 67.5 72.5
+ # [9,] 50.0 50.0
 validation_points <- matrix(c(
-  c(10,50),
-  c(50,50),
-  c(90,50)
+  c(15,2),
+  c(85,2),
+  c(15,95),
+  c(85,95),
+  c(22.5, 26),
+  c(67.5, 26),
+  c(22.5, 72.5),
+  c(67.5, 72.5),
+  c(50,50)
 ), ncol=2, byrow=T)
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3.
+```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1.
 Black points were used for calibration.

### 2022-09-25 group-b/E2-analysis-replication.Rmd
added calibration figs, example trials figs, other edits

@@
 
-The proportion of looks across quadrants in the free-viewing condition was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
+The proportions of looks across quadrants in the free-viewing condition were analyzed using a linear mixed-effects model with quadrant as the predictor (critical as the reference level).
 The model included random intercepts and slopes for participants^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`.
 Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent.
-This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.] Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )
+This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.].
+Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )
 
@@
 ```
-*Q: Can we recover item IDs to do crossed random effects?*

### 2022-09-25 group-b/E2-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

---
title: "Experiment 2: Calibration Figure"
output: html_notebook
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
```

```{r include=FALSE}
# calib: [25,25],[25,75],[50,50],[75,25],[75,75]
calibration_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)
# valid: c(25, 25, 50, 75, 75, 25, 75, 50, 25, 75)
#      [,1] [,2]
# [1,]   25   25
# [2,]   25   75
# [3,]   50   50
# [4,]   75   25
# [5,]   75   75
validation_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)

colnames(calibration_points) <- c("x","y")
colnames(validation_points) <- c("x","y")

df <- as_tibble(calibration_points) %>% bind_rows(as_tibble(validation_points))
df$point <- c(rep("calibration", nrow(calibration_points)), rep("validation", nrow(validation_points)))
```

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2022-09-25 group-c/E3-analysis-replication.Rmd
added calibration figs, example trials figs, other edits

@@
 
-```{r Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+```{r plot-cumulative-looking-score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
 ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
@@
 
-```{r Plot Looking Score Correlations, echo=FALSE}
+```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE}
 ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+

### 2022-09-25 group-d/E4-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

--- 2022-09-25 group-b/E2-calibration-figure.Rmd
@@
 ---
-title: "Experiment 2: Calibration Figure"
-output: html_notebook
+title: "Experiment 4: Calibration Figure"
+output: pdf
 ---
@@
 ), ncol=2, byrow=T)
-# valid: c(25, 25, 50, 75, 75, 25, 75, 50, 25, 75)
+# valid: 
 #     [,1] [,2]
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2.
+```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 4.
 Black points were used for calibration.

### 2022-09-25 group-e/E5-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

--- 2022-08-25 group-c/E3-calibration-figure.Rmd
@@
 ---
-title: "Experiment 3: Calibration Figure"
-output: html_notebook
+title: "Experiment 5: Calibration Figure"
+output: pdf
 ---
@@
 ```{r include=FALSE}
+# calib: [25,25],[25,75],[50,50],[75,25],[75,75],[25,50],[75,50],[15,50],[85,50]
 calibration_points <- matrix(c(
-  c(10,50),
-  c(50,50),
-  c(90,50),
   c(25,25),
   c(25,75),
+  c(50,50),
   c(75,25),
-  c(75,75)
+  c(75,75),
+  c(25,50),
+  c(75,50),
+  c(15,50),
+  c(85,50)
 ), ncol=2, byrow=T)
-
+# valid: 
+#      [,1] [,2]
+# [1,]   25   50
+# [2,]   75   50
+# [3,]   50   50
 validation_points <- matrix(c(
-  c(10,50),
-  c(50,50),
-  c(90,50)
+  c(25,50),
+  c(75,50),
+  c(50,50)
 ), ncol=2, byrow=T)
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3.
+```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 5.
 Black points were used for calibration.

### 2022-09-25 manuscript.Rmd
added calibration figs, example trials figs, other edits

@@
 ---
-title             : "Eye-tracking on the web: lessons learned from replicating 5 experiments"
-shorttitle        : "Just picked a random title: feel free to change"
+title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of 5 “classic” cognitive science experiments"
+shorttitle        : "Webcam eye-tracking paradigms"
 
@@
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
 abstract: |
@@
 
-keywords          : "keywords"
+keywords          : "eye-tracking, online, webcam, jsPsych, cognitive science"
 wordcount         : "X"
@@
 <!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->
+<!-- RR: switched ryskin to Snedeker & trueswell 2004 bcs my 75 looked sad -->
 
@@
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
-TABLE X provides an overview of the five studies we selected.
-
-```{r Create Studies Table, echo=FALSE}
+Table\ \ref(tab:studies-table) provides an overview of the five studies we selected.
+
+```{r studies-table, echo=FALSE}
 studies_table <- data.frame(
@@
     "Manns, Stark, & Squire, 2000",
-    "Ryskin et al., 2017",
+    "Snedeker & Trueswell, 2004",
     "Shimojo et al., 2003"
@@
     127,
-    75,
+    448,
     964
@@
 2.5x the sample size of the original experiment, following the heuristic
-of Simonsohn @simonsohn215. In study 5, the original sample size was so
+of Simonsohn [@simonsohn2015]. In study 5, the original sample size was so
 small that we opted to collect 5x the number of participants to increase
@@
 informal testing. This modification is similar to what Yang and Krajbich
-@yang2021webcam reported improved the sampling rate in their study of
+[-@yang2021webcam] reported improved the sampling rate in their study of
 webgazer. We also adjusted the mechanism for recording time stamps of
@@
 referents in sentence processing. For example, when looking at the
-display in Figure XX and listening to a sentence like "The boy will eat
-the...," participants are more likely to look at the cake than when they
-hear "The boy will move the...," in which case they tend to look at the
+display in Figure\ \@ref(fig:E1-example-trial) and listening to a sentence like
+"The boy will eat the...," participants are more likely to look at the cake than 
+when they hear "The boy will move the...," in which case they tend to look at the
 train, presumably because cakes are edible and trains are not. Semantic
@@
 
-All stimuli, experiment scrips, data, analysis scripts, and
+All stimuli, experiment scripts, data, analysis scripts, and a
 pre-registration are available on the Open Science Framework at
@@
 
-60 participants were paid \$XX for their participation. Our sample size
+60 participants were paid \$2.60 for their participation. Our sample size
 of participants was determined by the total run time of our experiment,
@@
 
-The task began with an <number of points>-point eye-tracker calibration
-and validation. During the experiment, the participants were
+The task began with a 9-point eye-tracker calibration
+and validation (Figure\ \@ref(fig:E1-calibration-figure)). 
+During the experiment, the participants were
 simultaneously presented with a visual image and a corresponding audio
@@
 was feasible given the visual image. There were two practice trials to
-ensure that participants had a sound understanding of the instructions
+ensure that participants understood the instructions
 before they undertook the main portion of the experiment. Participants'
@@
 were recorded for each trial.
+
+```{r E1-calibration-figure, child='group-a/E1-calibration-figure.Rmd'}
+
+```
 
@@
 The visual stimuli were created through Canva and depicted an agent
-accompanied by four to five objects in the scene (see Figure XX). On
+accompanied by four to five objects in the scene (see Figure\ \@ref(fig:E1-example-trial)). On
 critical trials, participants heard one of two sentences associated with
@@
 
+```{r E1-example-trial, fig.cap='Example trial from Experiment 1.
+Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.'}
+knitr::include_graphics("group-a/E1-example-trial.jpeg")
+```
+
 Each participant was presented with sixteen critical trials (eight in
@@
 subject-by-subject basis.<!-- right?-->
-
-*TO DO:* add figure
 
@@
 
+All stimuli, experiment scripts, data, analysis scripts, and a
+pre-registration are available on the Open Science Framework at
+<https://osf.io/xezfu/>.
+
 ### Participants
 
-60 participants were paid \$XX for their participation <!--right?-->.
+60 participants were paid for their participation.
 The sample size was motivated in part by budget constraints, but was
-nonetheless 2.5x larger than the original sample size of 24, as
-suggested by Simonsohn (2015). Data from 1 participant were not properly
+nonetheless 2.5x larger than the original sample size of 24). 
+Data from 1 participant were not properly
 recorded due to unknown technical issues, so data from 59 participants
@@
 ### Procedure
+
+The task began with a 9-point eye-tracker calibration
+and validation (Figure\ \@ref(fig:E2-calibration-figure)).
+
+```{r E2-calibration-figure, child='group-b/E2-calibration-figure.Rmd'}
+
+```
 
@@
 grid indicating the four quadrants of the screen. Each quadrant
-contained six images of items belonging to the same category (see Figure
-XX). The four categories were humanoids, household objects, animals, and
-methods of transportation. Participants were asked to remember the
-contents of the four quadrants. Different images were used in each
-block.
-
+contained six images of items belonging to the same category (see Figure\ \@ref(fig:E2-example-trial)). 
+The four categories were humanoids, household objects, animals, and
+methods of transportation. 
 Each of the four quadrants was presented one at a time. First, a list of
-the items in the quadrant were shown, then the items in the actual
-quadrant were shown (??). For each item, an audio file would play
-("???") asking the participant to use their arrow keys to identify which
-direction each item was facing (every item was facing either left or
-right (right??)). After the participant identified the direction of each
+the items in the quadrant was shown, then the pictures of items were displayed in the quadrant. 
+For each item, participants used their arrow keys to indicate whether the object was facing left or right. After the participant identified the direction of each
 item, they would have an additional 30 seconds to encode the name and
-orientation of each item in the quadrant. Then, after all four quadrants
-were presented in this way, the participant was shown the full grid of
+orientation of each item in the quadrant. Finally, after all four quadrants
+were presented, participants were shown the full grid of
 24 items and had 60 seconds to further encode the name and orientation
 of each item.
+
+```{r E2-example-trial, fig.cap='Example trial from Experiment 2.'}
+knitr::include_graphics("group-b/E2-example-figure.jpeg")
+```
 
@@
 obscured from the screen. Participants were randomly assigned to see the
-fixed-viewing or free-viewing block first.
+fixed-viewing or free-viewing block first. Different images were used in each block.
 
@@
 
-### Data analysis
-
 ## Results
@@
 ## Discussion
+
+As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located
+during encoding, suggesting that visuospatial information is integrated into the memory
+for objects.
+However, we did not observe a memory benefit, in terms of speed or accuracy, of spatial reinstatement via gaze position during retrieval of the picture.
+We can speculate that this may be due to the fact that participants struggled to maintain their gaze fixed in the center in the fixed-viewing condition, such that the difference between the fixed- and free-viewing conditions was minimal.
+Crucially for the current purposes, the webcam-based eye-tracking measurements were successful in replicating the key eye-tracking results.
 
@@
 The stimuli, experimental code, and data and analysis scripts can be
-found on the Open Science Framework at <https://osf.io/k63b9/>
-(<https://osf.io/k63b9/>). The pre-registration for the study can be
-found at <https://osf.io/48jsv> (<https://osf.io/48jsv>). We
+found on the Open Science Framework at <https://osf.io/k63b9/>.
+The pre-registration for the study can be
+found at <https://osf.io/48jsv> . We
 inadvertently did not create a formal pre-registration using the OSF
@@
 on the center of the screen and the middle of the left and right halves
-of the screen.
+of the screen (Figure\ \@ref(fig:E3-calibration-figure)).
 
@@
 
-The experimental design is visually depicted in Figure XX
+The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic)
+
+```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3'}
+knitr::include_graphics("group-c/E3-example-figure.jpeg")
+```
 
@@
 online experiment format.
-
-### Data analysis
 
@@
 found on the Open Science Framework at the following link,
-<https://osf.io/x3c49/> (<https://osf.io/x3c49/>). The pre-registration
-for the study can be found at <https://osf.io/3v4pg>
-(<https://osf.io/3v4pg>).
+<https://osf.io/x3c49/>. The pre-registration
+for the study can be found at <https://osf.io/3v4pg>.
 
@@
 
-58 (??) participants were paid \$XX for their participation
-<!--right?-->. A sample size of 58 was chosen because we wanted to
-replicate the experiment with greater statistical power. Note that the
-original study had a sample size of 24.
+57 participants were paid \$2.50 for their participation.
+A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power.
+Note that the original study had a sample size of 24.
 
@@
 
--   *TO DO:* add details of calibration point locations
-
-After the eye-tracking calibration, participants went through an audio
+After the eye-tracking calibration and validation (Figure\ \@ref(fig:E4-calibration-figure)), participants went through an audio
 test so they could adjust the audio on their computer to a comfortable
@@
 
+```{r E4-calibration-figure, child='group-d/E4-calibration-figure.Rmd'}
+
+```
+
 During a trial, four pictures were displayed (target animal, target
@@
 contained instructions about the action they needed to act out (e.g.,
-"Rub the butterfly with the crayon"; see Figure XX)[^1]. Using their
+"Rub the butterfly with the crayon"; see Figure\ \@ref(fig:E4-example-trial))[^1]. Using their
 cursor, participants could act out the instructions by clicking on
@@
 
-`r colorize("TO DO: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.", color = "red")`
+```{r E4-example-trial, fig.cap='An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.'}
+knitr::include_graphics("group-d/E4-example-figure.jpeg")
+```
 
@@
 50 participants for the main task were recruited on Prolific and were
-paid \$XX. 8 subjects, 4 from the attractiveness task group and 4 from
+paid \$10/hour. 8 subjects, 4 from the attractiveness task group and 4 from
 the roundness task group, were excluded for incorrect validations.
@@
 attractiveness task and the roundness task. The original sample size in
-Shimojo et al. (2003) was 10 participants total. \### Procedure and
-Design
+Shimojo et al. (2003) was 10 participants total.
+
+### Procedure and Design
 
@@
 order) and 3-point validation. The validation point appeared once at
-center, middle left, and middle right locations in random order.
+center, middle left, and middle right locations in random order (see Figure\ \@ref(fig:E5-calibration-figure)).
 <!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total?
@@
 -->
+```{r E5-calibration-figure, child='group-e/E5-calibration-figure.Rmd'}
+
+```
 
 During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in Figure
-XX). Participants were randomly assigned to one of two tasks:
+halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). Participants were randomly assigned to one of two tasks:
 attractiveness or shape judgment. In the attractiveness task,
@@
 the 19 face pairs was random for each participant.
+
+```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5. (Text did not appear on each screen.)'}
+knitr::include_graphics("group-e/E5-example-figure.jpeg")
+```
 
@@
 ```
-# Combined Analyses
+# Combined Analyses?
 
@@
 # General Discussion
+
+ - E1:
+
+ - E2: 
+    - replication of key result with 4 quadrants
+    - calib quality doesn't seem to matter 
+    - if attempting to control where people are looking, think about modifying task...
+
+ - E3:
+
+ - E4:
+
+ - E5:
 

### 2022-09-25 manuscript.tex
added calibration figs, example trials figs, other edits

--- 2022-08-25 manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{eye-tracking, online, webcam, jsPsych, cognitive science\newline\indent Word count: X}
 \usepackage{lineno}
@@
 \hypersetup{
-  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
+  pdftitle={What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments},
   pdfauthor={Joshua R.
@@
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={eye-tracking, online, webcam, jsPsych, cognitive science},
   hidelinks,
@@
 
-\title{Eye-tracking on the web: lessons learned from replicating 5 experiments}
+\title{What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments}
 \author{Joshua R.
@@
 
-\shorttitle{Just picked a random title: feel free to change}
+\shorttitle{Webcam eye-tracking paradigms}
 
 \authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
 
@@
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
-TABLE X provides an overview of the five studies we selected.
+Table~\ref(tab:studies-table) provides an overview of the five studies we selected.
 
@@
 
-\caption{\label{tab:Create Studies Table}Studies selected for replication attempts}
+\caption{\label{tab:studies-table}Studies selected for replication attempts}
 
@@
 Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 127.00\\
-Ryskin et al., 2017 & Psycholinguistics & Four Quadrants & 75.00\\
+Snedeker \& Trueswell, 2004 & Psycholinguistics & Four Quadrants & 448.00\\
 Shimojo et al., 2003 & Decision Making & Two Halves & 964.00\\
@@
 2.5x the sample size of the original experiment, following the heuristic
-of Simonsohn (\textbf{simonsohn215?}). In study 5, the original sample size was so
+of Simonsohn (Simonsohn, 2015). In study 5, the original sample size was so
 small that we opted to collect 5x the number of participants to increase
@@
 informal testing. This modification is similar to what Yang and Krajbich
-Yang and Krajbich (2021) reported improved the sampling rate in their study of
+(2021) reported improved the sampling rate in their study of
 webgazer. We also adjusted the mechanism for recording time stamps of
@@
 
-We used R (Version 4.2.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.9; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.4.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tidyr} (Version 1.2.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 referents in sentence processing. For example, when looking at the
-display in Figure XX and listening to a sentence like ``The boy will eat
-the\ldots,'' participants are more likely to look at the cake than when they
-hear ``The boy will move the\ldots,'' in which case they tend to look at the
+display in Figure~\ref{fig:E1-example-trial} and listening to a sentence like
+``The boy will eat the\ldots,'' participants are more likely to look at the cake than
+when they hear ``The boy will move the\ldots,'' in which case they tend to look at the
 train, presumably because cakes are edible and trains are not. Semantic
@@
 
-The task began with an -point eye-tracker calibration
-and validation. During the experiment, the participants were
+The task began with a 9-point eye-tracker calibration
+and validation (Figure~\ref{fig:E1-calibration-figure}).
+During the experiment, the participants were
 simultaneously presented with a visual image and a corresponding audio
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}Calibration and validation point locations for Experiment 1.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.}
+\end{figure}
+
 \hypertarget{materials-design}{%
@@
 The visual stimuli were created through Canva and depicted an agent
-accompanied by four to five objects in the scene (see Figure XX). On
+accompanied by four to five objects in the scene (see Figure~\ref{fig:E1-example-trial}). On
 critical trials, participants heard one of two sentences associated with
@@
 
+\begin{figure}
+\includegraphics[width=6.67in]{group-a/E1-example-trial} \caption{Example trial from Experiment 1.
+Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.}\label{fig:E1-example-trial}
+\end{figure}
+
 Each participant was presented with sixteen critical trials (eight in
@@
 subject-by-subject basis.
-
-\emph{TO DO:} add figure
 
@@
 
+All stimuli, experiment scripts, data, analysis scripts, and a
+pre-registration are available on the Open Science Framework at
+\url{https://osf.io/xezfu/}.
+
 \hypertarget{participants-2}{%
@@
 
-60 participants were paid \$XX for their participation .
+60 participants were paid for their participation.
 The sample size was motivated in part by budget constraints, but was
-nonetheless 2.5x larger than the original sample size of 24, as
-suggested by Simonsohn (2015). Data from 1 participant were not properly
+nonetheless 2.5x larger than the original sample size of 24).
+Data from 1 participant were not properly
 recorded due to unknown technical issues, so data from 59 participants
@@
 \subsubsection{Procedure}\label{procedure-1}}
+
+The task began with a 9-point eye-tracker calibration
+and validation (Figure~\ref{fig:E2-calibration-figure}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{\label{fig:unnamed-chunk-6}Calibration and validation point locations for Experiment 2.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)}
+\end{figure}
 
@@
 grid indicating the four quadrants of the screen. Each quadrant
-contained six images of items belonging to the same category (see Figure
-XX). The four categories were humanoids, household objects, animals, and
-methods of transportation. Participants were asked to remember the
-contents of the four quadrants. Different images were used in each
-block.
-
+contained six images of items belonging to the same category (see Figure~\ref{fig:E2-example-trial}).
+The four categories were humanoids, household objects, animals, and
+methods of transportation.
 Each of the four quadrants was presented one at a time. First, a list of
-the items in the quadrant were shown, then the items in the actual
-quadrant were shown (??). For each item, an audio file would play
-(``???'') asking the participant to use their arrow keys to identify which
-direction each item was facing (every item was facing either left or
-right (right??)). After the participant identified the direction of each
+the items in the quadrant was shown, then the pictures of items were displayed in the quadrant.
+For each item, participants used their arrow keys to indicate whether the object was facing left or right. After the participant identified the direction of each
 item, they would have an additional 30 seconds to encode the name and
-orientation of each item in the quadrant. Then, after all four quadrants
-were presented in this way, the participant was shown the full grid of
+orientation of each item in the quadrant. Finally, after all four quadrants
+were presented, participants were shown the full grid of
 24 items and had 60 seconds to further encode the name and orientation
 of each item.
+
+\begin{figure}
+\includegraphics[width=5.47in]{group-b/E2-example-figure} \caption{Example trial from Experiment 2.}\label{fig:E2-example-trial}
+\end{figure}
 
@@
 
-\hypertarget{data-analysis}{%
-\subsubsection{Data analysis}\label{data-analysis}}
-
 \hypertarget{results-1}{%
@@
 
-The proportion of looks across quadrants in the free-viewing condition was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level).
+The proportions of looks across quadrants in the free-viewing condition were analyzed using a linear mixed-effects model with quadrant as the predictor (critical as the reference level).
 The model included random intercepts and slopes for participants\footnote{ \texttt{lme4} syntax: \texttt{lmer(proportion\ \textasciitilde{}\ quadrant\ +\ (1+quadrant\textbar{}subject\_id))}.
 Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent.
-This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.} Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
+This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.}.
+Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
 
@@
 
-\emph{Q: Can we recover item IDs to do crossed random effects?}
-
 \hypertarget{calibration-1}{%
@@
 \subsection{Discussion}\label{discussion-1}}
+
+As in Johansson and Johansson (2014) and Spivey and Geng (2001), during memory retrieval, learners spontaneously look to blank screen locations where pictures were located
+during encoding, suggesting that visuospatial information is integrated into the memory
+for objects.
+However, we did not observe a memory benefit, in terms of speed or accuracy, of spatial reinstatement via gaze position during retrieval of the picture.
+We can speculate that this may be due to the fact that participants struggled to maintain their gaze fixed in the center in the fixed-viewing condition, such that the difference between the fixed- and free-viewing conditions was minimal.
+Crucially for the current purposes, the webcam-based eye-tracking measurements were successful in replicating the key eye-tracking results.
 
@@
 The stimuli, experimental code, and data and analysis scripts can be
-found on the Open Science Framework at \url{https://osf.io/k63b9/}
-(\url{https://osf.io/k63b9/}). The pre-registration for the study can be
-found at \url{https://osf.io/48jsv} (\url{https://osf.io/48jsv}). We
+found on the Open Science Framework at \url{https://osf.io/k63b9/}.
+The pre-registration for the study can be
+found at \url{https://osf.io/48jsv} . We
 inadvertently did not create a formal pre-registration using the OSF
@@
 on the center of the screen and the middle of the left and right halves
-of the screen.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
-\caption{\label{fig:unnamed-chunk-36}Calibration and validation point locations for Experiment 3.
+of the screen (Figure~\ref{fig:E3-calibration-figure}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-42-1.pdf}
+\caption{\label{fig:unnamed-chunk-42}Calibration and validation point locations for Experiment 3.
 Black points were used for calibration.
@@
 
-The experimental design is visually depicted in Figure XX
+The experimental design is visually depicted in Figure~\ref{fig:E3-design-schematic}
+
+\begin{figure}
+\includegraphics[width=3.41in]{group-c/E3-example-figure} \caption{Schematic of the design of Experiment 3}\label{fig:E3-design-schematic}
+\end{figure}
 
@@
 
-\hypertarget{data-analysis-1}{%
-\subsubsection{Data analysis}\label{data-analysis-1}}
-
 \hypertarget{results-2}{%
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/Plot of cumulative looking score-1.pdf}
-\caption{(\#fig:Plot of cumulative looking score)Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
+\includegraphics{manuscript_files/figure-latex/plot-cumulative-looking-score-1.pdf}
+\caption{\label{fig:plot-cumulative-looking-score}Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
 \end{figure}
@@
 Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(38) = 0.46, p = 0.65 (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(46) = 0.49, p = 0.63.
-
-\begin{verbatim}
-## Warning: Removed 75 rows containing missing values (geom_point).
-\end{verbatim}
 
@@
 found on the Open Science Framework at the following link,
-\url{https://osf.io/x3c49/} (\url{https://osf.io/x3c49/}). The pre-registration
-for the study can be found at \url{https://osf.io/3v4pg}
-(\url{https://osf.io/3v4pg}).
+\url{https://osf.io/x3c49/}. The pre-registration
+for the study can be found at \url{https://osf.io/3v4pg}.
 
@@
 
-58 (??) participants were paid \$XX for their participation
-. A sample size of 58 was chosen because we wanted to
-replicate the experiment with greater statistical power. Note that the
-original study had a sample size of 24.
+57 participants were paid \$2.50 for their participation.
+A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power.
+Note that the original study had a sample size of 24.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  \emph{TO DO:} add details of calibration point locations
-\end{itemize}
-
-After the eye-tracking calibration, participants went through an audio
+After the eye-tracking calibration and validation (Figure~\ref{fig:E4-calibration-figure}), participants went through an audio
 test so they could adjust the audio on their computer to a comfortable
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-45-1.pdf}
+\caption{\label{fig:unnamed-chunk-45}Calibration and validation point locations for Experiment 4.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)}
+\end{figure}
+
 During a trial, four pictures were displayed (target animal, target
@@
 contained instructions about the action they needed to act out (e.g.,
-``Rub the butterfly with the crayon''; see Figure XX)\footnote{In the original study, the pictures appeared one by one on the
+``Rub the butterfly with the crayon''; see Figure~\ref{fig:E4-example-trial})\footnote{In the original study, the pictures appeared one by one on the
   screen and their names were played as they appeared. We removed this
@@
 
-\textcolor{red}{TO DO: ADD FIGURES Figure 1: An example of a critical trial for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}
+\begin{figure}
+\includegraphics[width=4.5in]{group-d/E4-example-figure} \caption{An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}\label{fig:E4-example-trial}
+\end{figure}
 
@@
 attractiveness task and the roundness task. The original sample size in
-Shimojo et al.~(2003) was 10 participants total. \#\#\# Procedure and
-Design
+Shimojo et al.~(2003) was 10 participants total.
+
+\hypertarget{procedure-and-design}{%
+\subsubsection{Procedure and Design}\label{procedure-and-design}}
 
@@
 order) and 3-point validation. The validation point appeared once at
-center, middle left, and middle right locations in random order.
+center, middle left, and middle right locations in random order (see Figure~\ref{fig:E5-calibration-figure}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-89-1.pdf}
+\caption{\label{fig:unnamed-chunk-89}Calibration and validation point locations for Experiment 5.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.}
+\end{figure}
 
 During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in Figure
-XX). Participants were randomly assigned to one of two tasks:
+halves of the screen, one on the left and one on the right (as in Figure~\ref{fig:E5-example-trial}). Participants were randomly assigned to one of two tasks:
 attractiveness or shape judgment. In the attractiveness task,
@@
 the 19 face pairs was random for each participant.
+
+\begin{figure}
+\includegraphics[width=3.41in]{group-e/E5-example-figure} \caption{An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}\label{fig:E5-example-trial}
+\end{figure}
 
@@
 
-\hypertarget{data-analysis-2}{%
-\subsubsection{Data analysis}\label{data-analysis-2}}
+\hypertarget{data-analysis}{%
+\subsubsection{Data analysis}\label{data-analysis}}
 
@@
 \hypertarget{combined-analyses}{%
-\section{Combined Analyses}\label{combined-analyses}}
+\section{Combined Analyses?}\label{combined-analyses}}
 
@@
 \section{General Discussion}\label{general-discussion}}
+
+\begin{itemize}
+\item
+  E1:
+\item
+  E2:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    replication of key result with 4 quadrants
+  \item
+    calib quality doesn't seem to matter
+  \item
+    if attempting to control where people are looking, think about modifying task\ldots{}
+  \end{itemize}
+\item
+  E3:
+\item
+  E4:
+\item
+  E5:
+\end{itemize}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
+Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. \emph{Psychological Science}, \emph{26}(5), 559--569. \url{https://doi.org/10.1177/0956797614567341}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-afex}{}}%

### 2022-10-28 group-d/E4-analysis-replication-in-lab.Rmd
added prelim merced data

--- 2022-04-21 group-d/E4-analysis-replication.Rmd
@@
 ---
-title: "E4-analysis-replication"
+title: "E4-analysis-replication-in-lab"
 author: "Rachel Ryskin"
-date: "7/7/2021"
+date: ""
 output: pdf_document
@@
 
-```{r E4-load-data}
-data.files <- list.files('data/run-2', full.names = TRUE)
-data.tables <- lapply(data.files, function(file){
-  data.table <- fromJSON(file)
-  return(data.table)
-})
+```{r E4-in-lab-load-data}
+# data.files <- list.files('data/run-2', full.names = TRUE)
+# data.tables <- lapply(data.files, function(file){
+#   data.table <- fromJSON(file)
+#   return(data.table)
+# })
+data.tables = readRDS("data/in-lab-merced/verb_bias_ET_data_10_13_2022.rds")
 all.data <- bind_rows(data.tables)
@@
   dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
-  dplyr::select(subject, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
+  dplyr::select(user_id, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
 
@@
   tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
-  unnest(webgazer_data)
+  unnest_wider(webgazer_data) %>% 
+  unnest_longer(col = c(x, y, t))
+```
+
+```{r}
 
@@
 first.move <- mousetracking.data %>%
-  select(subject, trialID, object, type, compatibility, target_instrument, target_animal, images) %>%
-  group_by(subject, trialID) %>%
+  select(user_id, trialID, object, type, compatibility, target_instrument, target_animal, images) %>%
+  group_by(user_id, trialID) %>%
   filter(type=="enter") %>%
@@
 first.move.subject.summary <- first.move %>%
-  group_by(subject, compatibility) %>%
+  group_by(user_id, compatibility) %>%
   summarize(prop.animal = mean(first.move.type == 'animal'),
@@
 ```{r, eval=FALSE}
-write_csv(first.move, "output/E4_mouse_data.csv")
+#write_csv(first.move, "output/E4_mouse_data.csv")
 ```
@@
 # Merge in audio timing information
-eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
-  mutate(sound = str_split(audio, pattern="/", simplify = T)[,4])
+eyetracking.data.with.roi2 <- eyetracking.data.with.roi %>%
+  mutate(sound1 = str_split(audio, pattern="/", simplify = T)[,4]) %>% 
+  mutate(sound2 = str_split(sound1, pattern=fixed("."), simplify = T)[1]) %>% 
+  mutate(sound = paste0(sound2, ".mp3"))
 
-eyetracking.data.with.roi <- eyetracking.data.with.roi %>%
+eyetracking.data.with.roi3 <- eyetracking.data.with.roi2 %>%
   left_join(audio.info, by="sound")
@@
 # Add time window information
-eyetracking.data.with.time.windows <- eyetracking.data.with.roi %>%
+eyetracking.data.with.time.windows <- eyetracking.data.with.roi3 %>%
   mutate(time.window = case_when(
@@
   filter(between(t.window , -200, 4000)) %>%
-  group_by(subject, compatibility, t.window) %>%
+  group_by(user_id, compatibility, t.window) %>%
   summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%

### 2023-03-24 group-a/E1-analysis-replication.Rmd
added my Rmd files for Exp 1
the replication analysis needs to run first,  then the second one runs the calibration analyses

---
title: "Group A"
output: pdf_document
---
### Replication
<!-- # Setup -->
```{r setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source("~/round.comm.R")

knitr::opts_chunk$set(echo = FALSE)
```

<!-- # Import Data -->

<!-- Read JSON files and bind together into a tibble. -->

```{r import-data}
data.files <- list.files('data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

<!-- Mutate value types as needed -->

```{r value-types}
all.data <- all.data %>%
  mutate(subject_id = factor(subject_id))
```

<!-- Get a list of subject IDs. -->

```{r Get subj IDs}
subjects <- unique(all.data$subject_id)
```

<!-- # Extract Relevant Data -->

<!-- Get data from critical trials, select relevant columns, unnest/unpack webgazer data to get a tidy tibble, -->
<!-- and add gaze measurements as a percentage. -->

```{r Get data}
task.data <- all.data %>%
  filter(verb_type %in% c("restricting", "non-restricting")) %>%
  select(subject_id, stimulus, response, verb_type, webgazer_data, webgazer_targets) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(`#scenes`) %>%
  select(-x,-y) %>%
  unnest(webgazer_data) %>%
  mutate(gaze.x.percent = (x - left) / width * 100) %>%
  mutate(gaze.y.percent = (y - top) / height * 100)
```

<!-- # Add Stimulus Info -->

<!-- Merge in info on visual ROIs and audio onsets. -->

```{r Merge stim info, message=FALSE, warning=FALSE}
ref.image.height <- 1500 # height of images that were measured for ROIs
ref.image.width <- 1875 # width of images that were measured for ROIs
padding <- 20 # padding in pixels around the ROIs.

image.data <- read_csv('info/image_measurements.csv') %>%
  mutate(roi_top = (top_object_distance - padding) / ref.image.height * 100,
         roi_bottom = (bottom_object_distance + padding) / ref.image.height * 100,
         roi_left = (left_object_distance - padding) / ref.image.width * 100,
         roi_right = (right_object_distance + padding) / ref.image.width * 100) %>%
  mutate(object_class = if_else(object_type %in% c('subject', 'target.object'), object_type, 'distractor')) %>%
  select(image_name, object_type, object_class, roi_top, roi_bottom, roi_left, roi_right)

audio.data <- read_csv('info/audio_timestamps.csv') %>% filter(!is.na(stimulus))

critical.trials <- task.data %>%
  left_join(audio.data) %>%
  left_join(image.data)

#check for weirdness
discrep <- audio.data$delay_bw_onset_of_verb_and_onset_of_target_noun - 
  (audio.data$duration_of_verb + 
     audio.data$duration_of_intervening_determiner + 
     audio.data$intonation_break_bw_verb_and_determiner)
sum(discrep) #this should be zero, but it's 0.59! Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
```

<!--Figure out word durations by condition (AK Table 2)-->
```{r Word durations}
#First, grab the columns that match stimulus to condition name
stim.cond <- distinct(data.frame(critical.trials$stimulus, critical.trials$verb_type))
colnames(stim.cond) <- c("stimulus", "verb_type")

#Then merge with audio data
word.dur.data <- left_join(audio.data, stim.cond)

#Then summarize by condition
#word.dur.avg <- round.comm(colMeans(word.dur.data[,2:10])*1000)
word.dur.avg <- word.dur.data %>%
  group_by(verb_type) %>%
  summarise(Verb = round.comm(mean(duration_of_verb)*1000),
            Post_verbal_break = round.comm(mean(intonation_break_bw_verb_and_determiner)*1000),
            Determiner = round.comm(mean(duration_of_intervening_determiner)*1000),
            Total = Verb + Post_verbal_break + Determiner)

```

```{r Duration table, echo=FALSE}
#Set up a df of our data
our_table2 <- data.frame(
  Duration = c(
    "Verb",
    "Post-verbal break",
    "Determiner",
    "Verb + break + determiner"),
  Eat = c(
    word.dur.avg$Verb[2],
    word.dur.avg$Post_verbal_break[2],
    word.dur.avg$Determiner[2],
    word.dur.avg$Total[2]),
  Move = c(
    word.dur.avg$Verb[1],
    word.dur.avg$Post_verbal_break[1],
    word.dur.avg$Determiner[1],
    word.dur.avg$Total[1]),
  Difference = c(
    word.dur.avg$Verb[1] - word.dur.avg$Verb[2],
    word.dur.avg$Post_verbal_break[1] - word.dur.avg$Post_verbal_break[2],
    word.dur.avg$Determiner[1] - word.dur.avg$Determiner[2],
    word.dur.avg$Total[1] - word.dur.avg$Total[2])
  )

#Set up a df of our data
AK_table2 <- data.frame(
  AK_Eat = c(
    383,
    192,
    122,
    697),
  AK_Move = c(
    423,
    180,
    107,
    710),
  AK_Difference = c(
    40,
    -12,
    -15,
    13)
)

table2 <- cbind(our_table2,AK_table2)

knitr::kable(table2)

# apa_table(
#   table2,
#   caption = "Word durations for the restrictive ('eat') and non-restrictive ('move') sentences, in ms.",
#   font_size = "small"
# )    
#can I add a third dimension i.e. have two headings to group our data vs. AK data?
```

<!-- # Compute Gaze in ROI -->

<!-- Define a function for determining if `x,y` value falls in box. -->

```{r Gaze in ROI}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

<!-- Add a column with boolean value for whether gaze was in the ROI. -->

```{r Yes/No in ROI}
critical.trials <- critical.trials %>%
  mutate(is.fixating = in.box(gaze.x.percent, gaze.y.percent, roi_left, roi_right, roi_top, roi_bottom, 0))
```

<!-- # Subject Exclusion Criteria -->

<!-- We'll try this two ways. First if we adopt minimal exclusion criteria, removing subjects whose eye tracking data is essentially unusable. Second if we adopt aggressive exclusion criteria, removing subjects with obviously worse eye tracking data. -->

<!--###MINIMAL EXCLUSION-->
<!-- Set which mode here: -->
```{r Exclusion mode}
# 'AGGRESSIVE' or 'MINIMAL'
exclusion.mode <- 'MINIMAL' 
```

<!-- ## Proportion of measured data in an ROI. -->

<!-- Check the proportion of samples that were in at least one ROI for subjects. 
Which is to say: at each event time "t" per trial per subject, check whether they were looking at ANY of the objects (vs background/off-screen). What proportion of fixation events (total number varies by trial/subj) were in ANY ROI? -->

```{r prop-in-ROI}
prop.in.roi.by.subject <- critical.trials %>%
  group_by(subject_id, t, image_name) %>%
  summarize(fixation.in.roi = any(is.fixating)) %>%
  group_by(subject_id) %>%
  summarize(prop.of.samples.in.roi = mean(fixation.in.roi))
```
<!-- Visualize proportion of samples in ROI by subject. -->

```{r roi histogram}
hist(prop.in.roi.by.subject$prop.of.samples.in.roi, breaks=20)
```

<!-- Exclude subjects below a threshold -->

```{r exclude by prop in roi}
prop.samples.threshold.min <- 0

bad.subjects.prop.samples.min <- prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi <= prop.samples.threshold.min) %>%
  pull(subject_id)
```

<!-- ## Validation accuracy -->

```{r get validation data}
validation.accuracy.data <- all.data %>%
  filter(trial_type == 'webgazer-validate')
```

<!-- What % of subjects needed to recalibrate because of poor initial calibration? -->

```{r summarize something}
validation.accuracy.data %>% 
  group_by(subject_id) %>%
  count() %>%
  group_by(n) %>%
  count()
```

<!-- Get final average distance for each subject -->

```{r save validation percent in roi during validation}
validation.percent <- validation.accuracy.data %>%
  group_by(subject_id) %>%
  slice_tail() %>%
  select(subject_id, percent_in_roi) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  mutate(subject_id = fct_reorder(subject_id, M))

save(validation.percent, file = "validation.percent.RData")
```

```{r plot subjects by validation}
ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggresive is later) -->

```{r filter by validation}
validation.threshold.min <- 10

bad.subjects.validation.min <- validation.percent %>%
  filter(M <= validation.threshold.min) %>%
  pull(subject_id) %>%
  as.character()
```

<!-- ## Final exclusion data -->

```{r summarize exclusions}
bad.subjects.min <- unique(c(bad.subjects.prop.samples.min, bad.subjects.validation.min))

critical.trials.filtered.min <- critical.trials %>%
  filter(!subject_id %in% bad.subjects.min)

n.bad.subjects.min <- length(bad.subjects.min)
#There's a mysterious participant "55" who appears in bad.subjects but NOT in bad.subjects.prop.samples or in bad.subjects.validation...or anywhere? So there's really only 5 real bad subjects (leaving 57-5 = 52 participants in the filtered data)
```
<!-- This is where I should say how many people were excluded, right? -->
__Regions of Interest__. Regions of interest (ROIs) were defined by creating boxes around each object in the scene. The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding. Each scene contained an agent region, a target region, and three or four distractor regions.

__Minimal Exclusion__. The first set of analyses used minimal exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs. This resulted in the elimination of `r length(bad.subjects.prop.samples.min)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in an additional `r n.bad.subjects.min - length(bad.subjects.prop.samples.min)` excluded participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.min$subject_id))` participants.

<!-- # Calculating cumulative fixation probability -->

<!-- We start by calculating cumulative fixation probability on the objects after the verb onset. (Any fixations prior to the verb onset are not relevant to the core research questions.) -->

*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code); whether there's a 200-ms scootch.

<!-- First, add a column for time relative to verb onset, bin this to 50ms chunks, and filter the data to the 2,000 ms window after verb onset. -->

```{r set up 50 ms bins}
cumulative.fixation.data.min <- critical.trials.filtered.min %>%
  mutate(t.relative.to.verb.onset = t - (verb_onset*1000)) %>%
  filter(t.relative.to.verb.onset >= 0 & t.relative.to.verb.onset <2000) %>%
  mutate(t.w = floor(t.relative.to.verb.onset/50)*50)
```

<!-- Now check every time window within a trial to account for sparse samples. This calculating is time consuming, so we cache the result in a CSV file, and load from the CSV if it already exists. -->

```{r slowly build cumu fix data}
cumulative.fixation.calculation <- function(df){
  time <- seq(0,1950,50)
  fixations <- logical(length(time))
  hit.flag <- FALSE
  for(i in 1:length(fixations)){
    if(hit.flag){
      fixations[i] <- TRUE
    } else {
      val <- df %>% filter(t.w <= time[i]) %>% pull(is.fixating) %>% any()
      if(val == TRUE) {
        hit.flag <- TRUE
      }
      fixations[i] <- val
    }
  }
  out <- tibble(t.window = time, has.fixated = fixations)
  return(out)
}

setwd("/Users/ajames2/Documents/GitHub/219-2021-eyetracking-analysis/group-a")

if(file.exists("data/generated/cumulative_fixation_data_min.csv")){
  cumulative.fixation.windows.data.min <- read_csv("data/generated/cumulative_fixation_data_min.csv")
} else {

  cumulative.fixation.windows.data.min <- cumulative.fixation.data.min %>%
    group_by(subject_id, verb_type, image_name, object_type, object_class) %>%
    summarize(cumulative.fixation.calculation(cur_data()))

  write_csv(cumulative.fixation.windows.data.min, file="data/generated/cumulative_fixation_data_min.csv")
}
```

<!-- Then group by object class to calculate fixation probability for each kind of object, normalizing by the number of objects of that type. -->

```{r group cumu fix by object}
cumulative.fixation.windows.grouped.data.min <- cumulative.fixation.windows.data.min %>%
  filter(!subject_id %in% bad.subjects.min) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

<!-- Then collapse over trials to get a cumulative probability for the whole window for each subject -->

```{r collapse sumu fix over trials}
cumulative.fixation.windows.grouped.average.data.min <- cumulative.fixation.windows.grouped.data.min %>%
  group_by(subject_id, verb_type, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(cumulative.fixation.p))
```

<!-- Collapse across subjects to generate the equivalent of the figure from Altmann & Kamide. -->

```{r create summary data for spag plot}
cumulative.fixation.data.summary.min <- cumulative.fixation.windows.grouped.average.data.min %>%
  filter(object_class %in% c('target.object', 'distractor')) %>%
  group_by(t.window, verb_type, object_class) %>%
  summarize(cumulative.fixation.m = mean(cumulative.fixation.p))
```

__Cumulative Fixation Probabilities__. For each sentence target time window began at the onset of the verb and ended 2000 milliseconds later. This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin. Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure X. *I dunno how to make the figure show up when I knit the doc :-/

```{r make spag plot} 
#|E1-spaghetti-fig, 
#|fig.cap = "Cumulative probability of fixating distractor 
#|,and target objects across conditions."
E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")

E1_spag_fig
#we should insert a vertical line for the average noun onset
```

<!-- __Question 1: Are there more pre-noun first looks to the target object than to the distractors?__

First, grab the noun onset times to merge into our cumulative fixation data.-->

```{r set up noun onset times}
noun.onset.times.min <- critical.trials.filtered.min %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, delay_bw_onset_of_verb_and_onset_of_target_noun) %>%
  mutate(relative.noun.onset = delay_bw_onset_of_verb_and_onset_of_target_noun * 1000) %>%
  select(-delay_bw_onset_of_verb_and_onset_of_target_noun)

trial.level.cumulative.fixation.data.min <- cumulative.fixation.windows.grouped.data.min %>%
  left_join(noun.onset.times.min, by=c("image_name", "verb_type"))
```

<!--Then, grab the last time window before the noun onset for each trial. This is the critical data for this test.-->

```{r find prenoun window data}
pre.noun.first.looks.data.min <- trial.level.cumulative.fixation.data.min %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.noun.onset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r save prenoun window data}
pre.noun.first.looks.data.min$verb_type <- as.factor(pre.noun.first.looks.data.min$verb_type)
pre.noun.first.looks.data.min$object_class <- as.factor(pre.noun.first.looks.data.min$object_class)

save(pre.noun.first.looks.data.min, file = "pre.noun.first.looks.data.min.RData")
```
<!--Fit the model, with no covariance between random effects because the model cannot converge with full covariance matrix.-->

```{r run model 1}
E1_model1.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data.min)
summary(E1_model1.min)

E1_model1_tab.min = broom.mixed::tidy(E1_model1.min) 
E1_model1_obj.min = E1_model1_tab.min %>% filter(term == "object_classtarget.object")
E1_model1_verb.min = E1_model1_tab.min %>% filter(term == "verb_typerestricting")
E1_model1_obj_verb.min = E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
__Pre-noun fixations.__ In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting. The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun. We ran a regression model predicting the cumulative fixation proportion in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix). There were no significant effects, although the critical interaction was in the right direction [bar graph?] (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`). [should i use a table? should i change to effects coding like other Exps? i think 0/1 is intuitive in this case]

<!--Verb offset times-->

```{r find verb offset data}
verb.offset.times.min <- critical.trials.filtered.min %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, duration_of_verb) %>%
  mutate(relative.verb.offset = duration_of_verb * 1000) %>%
  select(-duration_of_verb)

trial.level.cumulative.fixation.data.verb.offset.min <- cumulative.fixation.windows.grouped.data.min %>%
  left_join(verb.offset.times.min, by=c("image_name", "verb_type"))
```

```{r save verb offset data}
pre.verb.offset.first.looks.data.min <- trial.level.cumulative.fixation.data.verb.offset.min %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.verb.offset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))

save(pre.verb.offset.first.looks.data.min, file = "pre.verb.offset.first.looks.data.min.RData")
```

```{r run model 2}
#model <- lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.min)
#summary(model)

E1_model2.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.min)
summary(E1_model2.min)

E1_model2_tab.min = broom.mixed::tidy(E1_model2.min) 
E1_model2_obj.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object")
E1_model2_verb.min = E1_model2_tab.min %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
__Pre-verb-offset fixations.__ Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

<!--Relative to noun onset, when is the first (post-verb) fixation on the target?-->

```{r}
first.fixation.after.verb.onset.min <- critical.trials.filtered.min %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>%
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>%
  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
  mutate(von_relative.t = t - (verb_onset*1000)) %>%
  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
```

```{r Table1, echo=FALSE}
#summarize data for table
first.fix.avg.min <- first.fixation.after.verb.onset.min %>%
  group_by(verb_type) %>%
  summarise(Verb.on = round.comm(mean(von_relative.t)),
            Verb.off = round.comm(mean(voff_relative.t)),
            Det.on = round.comm(mean(det_relative.t)),
            Noun.on = round.comm(mean(noun_relative.t)))

#put data into a data frame
our_table1_min <- data.frame(
  Time = c("Verb onset", "Verb offset", "Determiner onset", "Noun onset"),
  Eat = c(first.fix.avg.min$Verb.on[2],
           first.fix.avg.min$Verb.off[2],
           first.fix.avg.min$Det.on[2],
           first.fix.avg.min$Noun.on[2]),
  Move = c(first.fix.avg.min$Verb.on[1],
           first.fix.avg.min$Verb.off[1],
           first.fix.avg.min$Det.on[1],
           first.fix.avg.min$Noun.on[1]),
  Difference = c(first.fix.avg.min$Verb.on[1]-first.fix.avg.min$Verb.on[2],
                  first.fix.avg.min$Verb.off[1]-first.fix.avg.min$Verb.off[2],
                  first.fix.avg.min$Det.on[1]-first.fix.avg.min$Det.on[2],
                  first.fix.avg.min$Noun.on[1]-first.fix.avg.min$Noun.on[2])
)

AK_table1 <- data.frame(
  Time = c("Verb onset", "Verb offset", "Determiner onset", "Noun onset"),
  Eat = c(611, 228, 37, -85),
  Move = c(838, 415, 234, 127),
  Difference = c(227, 187, 197, 212))

table1_min <- merge(our_table1_min, AK_table1, by = "Time")

# apa_table(
#   table1_min,
#   caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
#   font_size = "small",
#    col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
# )

#can I add a third dimension i.e. have two headings to group our data vs. AK data?

knitr::kable(table1_min)
```

```{r}
first.fixation.after.verb.onset.analysis.data.min <- first.fixation.after.verb.onset.min %>%
  ungroup() %>%
  select(subject_id, image_name, verb_type, duration_of_verb, noun_relative.t) %>%
  mutate(dur_verb_ms_c = scale(duration_of_verb, scale = FALSE)*1000) #mean-center verb duration

save(first.fixation.after.verb.onset.analysis.data.min, file = "first.fixation.after.verb.onset.analysis.data.min.RData")
```

```{r}
E1_model3.min <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data.min)

summary(E1_model3.min)

E1_model3_tab.min = broom.mixed::tidy(E1_model3.min) 
E1_model3_verb.min = E1_model3_tab.min %>% filter(term == "verb_typerestricting")

```
__First target fixations after verb.__ Finally, we address whether participants look to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. [On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs. AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).

```{r}
first.fixation.after.verb.onset.subject.summary.min <- first.fixation.after.verb.onset.min %>%
  group_by(subject_id, verb_type) %>%
  summarize(m.t = mean(noun_relative.t), ct = n())

first.fixation.after.verb.onset.summary.min <- first.fixation.after.verb.onset.subject.summary.min %>%
  group_by(verb_type) %>%
  summarize(m=mean(m.t), sd=sd(m.t), se=sd/sqrt(n()))

save(first.fixation.after.verb.onset.summary.min, file = "first.fixation.after.verb.onset.subject.summary.min.RData")
```

```{r}
ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
  geom_col()+
  geom_errorbar(width=0.2)
```

<!--###AGGRESSIVE EXCLUSION-->
<!-- Set which mode here: -->
```{r}
# 'AGGRESSIVE' or 'MINIMAL'
exclusion.mode <- 'AGGRESSIVE' 
```

<!-- ## Proportion of measured data in an ROI. -->

<!-- Check the proportion of samples that were in at least one ROI for subjects. 
Which is to say: at each event time "t" per trial per subject, check whether they were looking at ANY of the objects (vs background/off-screen). What proportion of fixation events (total number varies by trial/subj) were in ANY ROI? -->

<!-- Exclude subjects below a threshold -->

```{r}
prop.samples.threshold.aggro <- 0.2

bad.subjects.prop.samples.aggro <- prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi <= prop.samples.threshold.aggro) %>%
  pull(subject_id)
```

<!-- Set criteria for minimal and aggressive exclusions -->

```{r}
validation.threshold.aggro <- 50

bad.subjects.validation.aggro <- validation.percent %>%
  filter(M <= validation.threshold.aggro) %>%
  pull(subject_id) %>%
  as.character()
```

<!-- ## Final exclusion data -->

```{r}
bad.subjects.aggro <- unique(c(bad.subjects.prop.samples.aggro, bad.subjects.validation.aggro))

critical.trials.filtered.aggro <- critical.trials %>%
  filter(!subject_id %in% bad.subjects.aggro)

n.bad.subjects.aggro <- length(bad.subjects.aggro)
```
__Aggressive Exclusion__. The second set of analyses used more aggressive exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.aggro*100` percent of fixations in any ROIs. This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.aggro` percent, which eliminated an additional `r n.bad.subjects.aggro - length(bad.subjects.prop.samples.aggro)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.

<!-- # Calculating cumulative fixation probability -->

<!-- We start by calculating cumulative fixation probability on the objects after the verb onset. (Any fixations prior to the verb onset are not relevant to the core research questions.) -->

<!-- First, add a column for time relative to verb onset, bin this to 50ms chunks, and filter the data to the 2,000 ms window after verb onset. -->

```{r}
cumulative.fixation.data.aggro <- critical.trials.filtered.aggro %>%
  mutate(t.relative.to.verb.onset = t - (verb_onset*1000)) %>%
  filter(t.relative.to.verb.onset >= 0 & t.relative.to.verb.onset <2000) %>%
  mutate(t.w = floor(t.relative.to.verb.onset/50)*50)
```

<!-- Now check every time window within a trial to account for sparse samples. This calculating is time consuming, so we cache the result in a CSV file, and load from the CSV if it already exists. -->

```{r}
# cumulative.fixation.calculation <- function(df){
#   time <- seq(0,1950,50)
#   fixations <- logical(length(time))
#   hit.flag <- FALSE
#   for(i in 1:length(fixations)){
#     if(hit.flag){
#       fixations[i] <- TRUE
#     } else {
#       val <- df %>% filter(t.w <= time[i]) %>% pull(is.fixating) %>% any()
#       if(val == TRUE) {
#         hit.flag <- TRUE
#       }
#       fixations[i] <- val
#     }
#   }
#   out <- tibble(t.window = time, has.fixated = fixations)
#   return(out)
# }
# 
# setwd("/Users/ajames2/Documents/GitHub/219-2021-eyetracking-analysis/group-a")

if(file.exists("data/generated/cumulative_fixation_data_aggro.csv")){
  cumulative.fixation.windows.data.aggro <- read_csv("data/generated/cumulative_fixation_data_aggro.csv")
} else {

  cumulative.fixation.windows.data.aggro <- cumulative.fixation.data.aggro %>%
    group_by(subject_id, verb_type, image_name, object_type, object_class) %>%
    summarize(cumulative.fixation.calculation(cur_data()))

  write_csv(cumulative.fixation.windows.data.aggro, file ="data/generated/cumulative_fixation_data_aggro.csv")
}
```

<!-- Then group by object class to calculate fixation probability for each kind of object, normalizing by the number of objects of that type. -->

```{r}
cumulative.fixation.windows.grouped.data.aggro <- cumulative.fixation.windows.data.aggro %>%
  filter(!subject_id %in% bad.subjects.aggro) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

<!-- Then collapse over trials to get a cumulative probability for the whole window for each subject -->

```{r}
cumulative.fixation.windows.grouped.average.data.aggro <- cumulative.fixation.windows.grouped.data.aggro %>%
  group_by(subject_id, verb_type, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(cumulative.fixation.p))
```

<!-- Collapse across subjects to generate the equivalent of the figure from Altmann & Kamide. -->

```{r}
cumulative.fixation.data.summary.aggro <- cumulative.fixation.windows.grouped.average.data.aggro %>%
  filter(object_class %in% c('target.object', 'distractor')) %>%
  group_by(t.window, verb_type, object_class) %>%
  summarize(cumulative.fixation.m = mean(cumulative.fixation.p))
```

```{r} 
#|E1-spaghetti-fig, 
#|fig.cap = "Cumulative probability of fixating distractor 
#|,and target objects across conditions."
E1_spag_fig <- ggplot(cumulative.fixation.data.summary.aggro, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")

E1_spag_fig
#we should insert a vertical line for the average noun onset
```

<!-- __Question 1: Are there more pre-noun first looks to the target object than to the distractors?__

First, grab the noun onset times to merge into our cumulative fixation data.-->

```{r}
noun.onset.times.aggro <- critical.trials.filtered.aggro %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, delay_bw_onset_of_verb_and_onset_of_target_noun) %>%
  mutate(relative.noun.onset = delay_bw_onset_of_verb_and_onset_of_target_noun * 1000) %>%
  select(-delay_bw_onset_of_verb_and_onset_of_target_noun)

trial.level.cumulative.fixation.data.aggro <- cumulative.fixation.windows.grouped.data.aggro %>%
  left_join(noun.onset.times.aggro, by=c("image_name", "verb_type"))
```

<!--Then, grab the last time window before the noun onset for each trial. This is the critical data for this test.-->

```{r}
pre.noun.first.looks.data.aggro <- trial.level.cumulative.fixation.data.aggro %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.noun.onset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r}
pre.noun.first.looks.data.aggro$verb_type <- as.factor(pre.noun.first.looks.data.aggro$verb_type)
pre.noun.first.looks.data.aggro$object_class <- as.factor(pre.noun.first.looks.data.aggro$object_class)
```
<!--Fit the model, with no covariance between random effects because the model cannot converge with full covariance matrix.-->

```{r}
E1_model1.aggro <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data.aggro)
summary(E1_model1.aggro)

E1_model1_tab.aggro = broom.mixed::tidy(E1_model1.aggro) 
E1_model1_obj.aggro = E1_model1_tab.aggro %>% filter(term == "object_classtarget.object")
E1_model1_verb.aggro = E1_model1_tab.aggro %>% filter(term == "verb_typerestricting")
E1_model1_obj_verb.aggro = E1_model1_tab.aggro %>% filter(term == "object_classtarget.object:verb_typerestricting")
```

<!--Verb offset times-->

```{r}
verb.offset.times.aggro <- critical.trials.filtered.aggro %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, duration_of_verb) %>%
  mutate(relative.verb.offset = duration_of_verb * 1000) %>%
  select(-duration_of_verb)

trial.level.cumulative.fixation.data.verb.offset.aggro <- cumulative.fixation.windows.grouped.data.aggro %>%
  left_join(verb.offset.times.aggro, by=c("image_name", "verb_type"))
```

```{r}
pre.verb.offset.first.looks.data.aggro <- trial.level.cumulative.fixation.data.verb.offset.aggro %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.verb.offset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r}
#model <- lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.aggro)
#summary(model)

E1_model2.aggro <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.aggro)
summary(E1_model2.aggro)

E1_model2_tab.aggro = broom.mixed::tidy(E1_model2.aggro) 
E1_model2_obj.aggro = E1_model2_tab.aggro %>% filter(term == "object_classtarget.object")
E1_model2_verb.aggro = E1_model2_tab.aggro %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.aggro = E1_model2_tab.aggro %>% filter(term == "object_classtarget.object:verb_typerestricting")
```

<!--Relative to noun onset, when is the first (post-verb) fixation on the target?-->

```{r}
first.fixation.after.verb.onset.aggro <- critical.trials.filtered.aggro %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>%
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>%
  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
  mutate(von_relative.t = t - (verb_onset*1000)) %>%
  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
```

```{r, echo=FALSE}
# #summarize data for table
# first.fix.avg.aggro <- first.fixation.after.verb.onset.aggro %>%
#   group_by(verb_type) %>%
#   summarise(Verb.on = round.comm(mean(von_relative.t)),
#             Verb.off = round.comm(mean(voff_relative.t)),
#             Det.on = round.comm(mean(det_relative.t)),
#             Noun.on = round.comm(mean(noun_relative.t)))
# 
# #put data into a data frame
# our_table1_aggro <- data.frame(
#   Time = c("Verb onset", "Verb offset", "Determiner onset", "Noun onset"),
#   Eat = c(first.fix.avg.aggro$Verb.on[2],
#            first.fix.avg.aggro$Verb.off[2],
#            first.fix.avg.aggro$Det.on[2],
#            first.fix.avg.aggro$Noun.on[2]),
#   Move = c(first.fix.avg.aggro$Verb.on[1],
#            first.fix.avg.aggro$Verb.off[1],
#            first.fix.avg.aggro$Det.on[1],
#            first.fix.avg.aggro$Noun.on[1]),
#   Difference = c(first.fix.avg.aggro$Verb.on[1]-first.fix.avg.aggro$Verb.on[2],
#                   first.fix.avg.aggro$Verb.off[1]-first.fix.avg.aggro$Verb.off[2],
#                   first.fix.avg.aggro$Det.on[1]-first.fix.avg.aggro$Det.on[2],
#                   first.fix.avg.aggro$Noun.on[1]-first.fix.avg.aggro$Noun.on[2])
# )
# 
# AK_table1 <- data.frame(
#   Time = c("Verb onset", "Verb offset", "Determiner onset", "Noun onset"),
#   Eat = c(611, 228, 37, -85),
#   Move = c(838, 415, 234, 127),
#   Difference = c(227, 187, 197, 212))
# 
# table1_aggro <- merge(our_table1_aggro, AK_table1, by = "Time")
#   
# apa_table(
#   table1_aggro,
#   caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
#   font_size = "small",
#    col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
# )    
# #can I add a third dimension i.e. have two headings to group our data vs. AK data?
```

```{r}
first.fixation.after.verb.onset.analysis.data.aggro <- first.fixation.after.verb.onset.aggro %>%
  ungroup() %>%
  select(subject_id, image_name, verb_type, duration_of_verb, noun_relative.t) %>%
  mutate(dur_verb_ms_c = scale(duration_of_verb, scale = FALSE)*1000) #mean-center verb duration
```

```{r}
E1_model3.aggro <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data.aggro)

summary(E1_model3.aggro)

E1_model3_tab.aggro = broom.mixed::tidy(E1_model3.aggro) 
E1_model3_verb.aggro = E1_model3_tab.aggro %>% filter(term == "verb_typerestricting")

```
We tested the same three models under these more aggressive exclusion criteria. The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`). However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).

```{r}
first.fixation.after.verb.onset.subject.summary.aggro <- first.fixation.after.verb.onset.aggro %>%
  group_by(subject_id, verb_type) %>%
  summarize(m.t = mean(noun_relative.t), ct = n())

first.fixation.after.verb.onset.summary.aggro <- first.fixation.after.verb.onset.subject.summary.aggro %>%
  group_by(verb_type) %>%
  summarize(m=mean(m.t), sd=sd(m.t), se=sd/sqrt(n()))
```

```{r}
ggplot(first.fixation.after.verb.onset.summary.aggro, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
  geom_col()+
  geom_errorbar(width=0.2)
```

```{r Lab comparison}

```

### 2023-07-06 group-d/E4-analysis-replication-in-lab.Rmd
added more merced data and did first pass analysis

@@
 library(jsonlite)
-library(dplyr)
+library(purrr)
+#library(dplyr)
 library(readr)
@@
 ```{r E4-in-lab-load-data}
-# data.files <- list.files('data/run-2', full.names = TRUE)
+user.data.files <- list.files('data/in-lab-merced', pattern = "pushkin_users_*",full.names = TRUE)
+
+all.user.data <- map_dfr(user.data.files, readRDS)
+
+data.files <- list.files('data/in-lab-merced', pattern = "lex_*",full.names = TRUE)
 # data.tables <- lapply(data.files, function(file){
@@
 # })
-data.tables = readRDS("data/in-lab-merced/verb_bias_ET_data_10_13_2022.rds")
-all.data <- bind_rows(data.tables)
+
+#data.tables = readRDS("data/in-lab-merced/lex_stimulusResponses_2023-05-01.rds")
+all.data <- map_dfr(data.files, readRDS) %>% 
+  bind_rows(readRDS("data/in-lab-merced/verb_bias_ET_data_10_13_2022.rds")) %>% 
+  arrange(user_id, trial_index, time_elapsed) %>% 
+  group_by(user_id, trial_index) %>% 
+  mutate(subjnum = 1:n(),
+         unique_id = str_c(subjnum,"__", user_id)) %>% 
+  ungroup() %>% 
+  arrange(unique_id, trial_index)
+
 ```
+
+*TO DO:* cross ref with angela's list of participant times/dates
 
@@
   dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
-  dplyr::select(user_id, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
+  dplyr::select(unique_id, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
 
@@
 first.move <- mousetracking.data %>%
-  select(user_id, trialID, object, type, compatibility, target_instrument, target_animal, images) %>%
-  group_by(user_id, trialID) %>%
+  select(unique_id, trialID, object, type, compatibility, target_instrument, target_animal, images, audio) %>%
+  group_by(unique_id, trialID) %>%
   filter(type=="enter") %>%
@@
 first.move.subject.summary <- first.move %>%
-  group_by(user_id, compatibility) %>%
+  group_by(unique_id, compatibility) %>%
   summarize(prop.animal = mean(first.move.type == 'animal'),
             prop.instrument = mean(first.move.type == 'instrument'),
-            prop.other = mean(first.move.type == 'other')) %>%
+            prop.other = mean(first.move.type == 'other'),
+            n_trials= n()) %>%
+  filter(n_trials > 9) %>% ## CAHNGE WHEN THERE'S A BETTER WAY TO CROSSREF
   pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
@@
 
-```{r E4-mouse-moves-analysis}
+```{r E4-mouse-moves-analysis-lab}
 contrasts(first.move$compatibility) <- cbind(c(1/3, -2/3, 1/3), c(-1/2, 0, 1/2))
 
-E4_mouse_moves_model <- glmer(is.mouse.instrument ~ compatibility + (1 + compatibility | subject) + (1 | trialID), data=first.move, family="binomial",
+E4_mouse_moves_model <- glmer(is.mouse.instrument ~ compatibility + (1 + compatibility | unique_id) + (1 | trialID), 
+                              data=first.move, family="binomial",
                               glmerControl(optimizer = "bobyqa"))
@@
 
+```{r E4-summarizing-gaze-data-for-plotting, eval = FALSE, warning = FALSE}
+#Summarize data for plotting
+eyetracking.data.with.time.windows %>%
+  filter(between(t.window , -200, 4000)) %>%
+  filter(unique_id %in% unique(first.move.subject.summary$unique_id)) %>% #CHANGE WHEN CROSSREF
+  group_by(unique_id, compatibility, t.window) %>%
+  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
+  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
+  ggplot()+
+  stat_summary(aes(x = t.window, y=prop_fixations,  color = object_type), fun="mean")+
+  facet_wrap(~unique_id)
+  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
+ # group_by(compatibility, t.window, object_type) %>%
+ # summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
+```
+
 ```{r E4-summarizing-gaze-data-for-plotting}
@@
   filter(between(t.window , -200, 4000)) %>%
-  group_by(user_id, compatibility, t.window) %>%
+  filter(unique_id %in% unique(first.move.subject.summary$unique_id)) %>% #CHANGE WHEN CROSSREF
+  group_by(unique_id, compatibility, t.window) %>%
   summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
@@
 ```{r, eval=FALSE}
-saveRDS(fig2, "output/ETfig.rds")
-ggsave("output/ETfig.png", plot = fig2, height = 4, width = 6)
+saveRDS(fig2, "output/ETfig-in-lab.rds")
+ggsave("output/ETfig-in-lab.png", plot = fig2, height = 4, width = 6)
 ```
@@
 eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
-  group_by(subject, trialID, sound, compatibility, time.window) %>%
+  group_by(unique_id, trialID, sound, compatibility, time.window) %>%
   summarize(prop.fixations.animal = sum(in.roi.animal) / n(),
@@
 
-model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.1,
+model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | unique_id) + (1 | trialID), data=data.time.window.1,
                             control = lmerControl(optimizer = "bobyqa",
@@
 
-model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)
+model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | unique_id) + (1 | trialID), data=data.time.window.2)
 ```
@@
 
-model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 | subject) + (1 | trialID), data=data.time.window.3)
+model.time.window.3 <- lmer(prop.fixations.animal ~ compatibility + (1 | unique_id) + (1 | trialID), data=data.time.window.3)
 ```

### 2023-07-06 group-a/E1-analysis-calibration.Rmd
edited manuscript.Rmd to refer to E1 Rmds; fixed stuff

```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
# library(dplyr)
# library(tidyr)
# library(jsonlite)
# library(ggplot2)
# library(readr)
# library(afex)
# library(forcats)
# library(papaja)
# source("~/round.comm.R")

knitr::opts_chunk$set(include = FALSE, echo = FALSE)
#knitr::opts_knit$set(root.dir =)

#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

```{r Load data}
# load("pre.noun.first.looks.data.min.RData") 
# load("pre.verb.offset.first.looks.data.min.RData")
# load("first.fixation.after.verb.onset.analysis.data.min.RData")
# load("validation.percent.RData")
# load("first.fixation.after.verb.onset.subject.summary.min.RData")

pre.noun.first.looks.data <- pre.noun.first.looks.data.min
pre.verb.offset.first.looks.data <- pre.verb.offset.first.looks.data.min
first.fixation.after.verb.onset.analysis.data <- first.fixation.after.verb.onset.analysis.data.min
first.fixation.after.verb.onset.subject.summary <- first.fixation.after.verb.onset.subject.summary.min  
```

```{r Model 1 subject summary}
pre.noun.subj.summary <- pre.noun.first.looks.data %>%
  group_by(subject_id, verb_type, object_class) %>%
  summarize(fix.p = mean(cumulative.fixation.p))

pre.noun.by.verb <- pre.noun.subj.summary %>%
  pivot_wider(names_from = object_class, values_from = fix.p) %>%
  mutate(tar.adv = target.object - distractor)

pre.noun.effects <- pre.noun.by.verb %>%
  select(subject_id, verb_type, tar.adv) %>%
  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(effect = restricting - non_restricting)
```

```{r Model 1 effect size by calibration}
#merge with validation percent

cali.analy.1 <- merge(pre.noun.effects, validation.percent, by = "subject_id")

#correlate
m1_diffdiff_cor <- cor.test(cali.analy.1$effect, cali.analy.1$M, use = "pairwise.complete.obs") #difference of differences
#0.03107354
m1_diffdiff_cor_r <- m1_diffdiff_cor$estimate
m1_diffdiff_cor_p <- m1_diffdiff_cor$p.value

m1_diff_cor <- cor.test(cali.analy.1$restricting, cali.analy.1$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
#0.2096605
m1_diff_cor_r <- m1_diff_cor$estimate
m1_diff_cor_p <- m1_diff_cor$p.value
```

```{r Model 2 subject summary}
pre.verb.subj.summary <- pre.verb.offset.first.looks.data %>%
  group_by(subject_id, verb_type, object_class) %>%
  summarize(fix.p = mean(cumulative.fixation.p))

pre.verb.by.verb <- pre.verb.subj.summary %>%
  pivot_wider(names_from = object_class, values_from = fix.p) %>%
  mutate(tar.adv = target.object - distractor)

pre.verb.effects <- pre.verb.by.verb %>%
  select(subject_id, verb_type, tar.adv) %>%
  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(effect = restricting - non_restricting)
```

```{r Model 2 effect size by calibration}
#merge with validation percent
cali.analy.2 <- merge(pre.verb.effects, validation.percent, by = "subject_id")

#correlate
m2_diffdiff_cor <- cor.test(cali.analy.2$effect, cali.analy.2$M, use = "pairwise.complete.obs") #difference of differences
#-0.04809241
m2_diffdiff_cor_r <- m2_diffdiff_cor$estimate
m2_diffdiff_cor_p <- m2_diffdiff_cor$p.value

m2_diff_cor <- cor.test(cali.analy.2$restricting, cali.analy.2$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
#-0.03601876
m2_diff_cor_r <- m2_diff_cor$estimate
m2_diff_cor_p <- m2_diff_cor$p.value

```

```{r Model 3 effect size by calibration}
#summary(validation.percent)
#make looking scores for Ps
looking.scores <- first.fixation.after.verb.onset.subject.summary[,1:3] %>% 
  spread(verb_type, m.t) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(diff = non_restricting - restricting)

#merge with validation percent
cali.analy.3 <- merge(looking.scores, validation.percent, by = "subject_id")

#correlate
m3_diff_cor <- cor.test(cali.analy.3$diff, cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
m3_diff_cor_r <- m3_diff_cor$estimate
m3_diff_cor_p <- m3_diff_cor$p.value
```

Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality varied widely, ranging from `r min(validation.percent$M) %>% round(digits = 2)`% to `r max(validation.percent$M) %>% round(digits = 2)`%.

We tested whether a participant's calibration quality was correlated with their effect size. The quality of a participant's calibration was not significantly correlated with the participant's effect size. There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions). Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`. However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e. rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).

### 2023-07-06 group-a/E1-analysis-replication.Rmd
edited manuscript.Rmd to refer to E1 Rmds; fixed stuff

@@
 ---
-### Replication
 <!-- # Setup -->
-```{r setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
+```{r E1-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
 library(dplyr)
@@
      audio.data$intonation_break_bw_verb_and_determiner)
-sum(discrep) #this should be zero, but it's 0.59! Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
+#sum(discrep) 
+#this should be zero, but it's 0.59! TO-DO: Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
 ```
@@
 
-```{r Duration table, echo=FALSE}
+```{r E1_word_dur_table, echo=FALSE, eval=FALSE}
 #Set up a df of our data
 our_table2 <- data.frame(
-  Duration = c(
-    "Verb",
-    "Post-verbal break",
-    "Determiner",
-    "Verb + break + determiner"),
   Eat = c(
@@
   )
-
 #Set up a df of our data
@@
 
-table2 <- cbind(our_table2,AK_table2)
+#E1_word_dur_table <- cbind(our_table2,AK_table2)
+E1_word_dur_table <- structure(list(
+  Segment = c(
+    "Verb",
+    "Post-verbal break",
+    "Determiner",
+    "Verb + break + determiner"),
+  our_table2, AK_table2),
+  class = "data.frame",
+  row.names = c(NA, 4L))
 
-knitr::kable(table2)
+#knitr::kable(table2)
 
  # apa_table(
-#   table2,
+ #  E1_word_dur_table,
  #   caption = "Word durations for the restrictive ('eat') and non-restrictive ('move') sentences, in ms.",
@@
  # )    
-#can I add a third dimension i.e. have two headings to group our data vs. AK data?
+#TO-DO: can I add a third dimension i.e. have two headings to group our data vs. AK data?
 ```
@@
 
-```{r roi histogram}
+```{r roi histogram, eval=F}
+#printed?
 hist(prop.in.roi.by.subject$prop.of.samples.in.roi, breaks=20)
@@
 
-```{r summarize something}
+```{r summarize calibration data, eval=F}
+#printed?
 validation.accuracy.data %>% 
@@
 
-```{r plot subjects by validation}
+```{r plot subjects by validation, eval=F}
+#printed?
 ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
@@
 ```
-<!-- Set criteria for minimal exclusions (aggresive is later) -->
+<!-- Set criteria for minimal exclusions (aggressive is later) -->
 
@@
 
-*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code); whether there's a 200-ms scootch.
+*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.
 
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure X.
-*I dunno how to make the figure show up when I knit the doc :-/
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:E1-spaghetti-fig).
 
-```{r make spag plot} 
-#|E1-spaghetti-fig, 
-#|fig.cap = "Cumulative probability of fixating distractor 
-#|,and target objects across conditions."
+```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions. The vertical line marks the mean noun onset across trials and conditions."} 
 E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
@@
   scale_x_continuous(expand=c(0.01,0.01))+
-  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")
+  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
+  geom_vline(xintercept = mean(word.dur.avg$Total))
 
 E1_spag_fig
-#we should insert a vertical line for the average noun onset
 ```
@@
 E1_model1.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data.min)
-summary(E1_model1.min)
+#summary(E1_model1.min)
 
@@
 E1_model2.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.min)
-summary(E1_model2.min)
+#summary(E1_model2.min)
 
@@
 
-```{r Table1, echo=FALSE}
+```{r E1-latency-table-min, echo=FALSE, eval=FALSE}
 #summarize data for table
@@
 
-table1_min <- merge(our_table1_min, AK_table1, by = "Time")
+E1_latency_table_min <- merge(our_table1_min, AK_table1, by = "Time")
 
-# apa_table(
-#   table1_min,
-#   caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
-#   font_size = "small",
-#    col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
-# )
+apa_table(
+  E1_latency_table_min,
+  caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
+  font_size = "small",
+   col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
+)
 
@@
 
-knitr::kable(table1_min)
+#knitr::kable(table1_min)
 ```
@@
 
-```{r}
+```{r run model 3}
 E1_model3.min <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data.min)
 
-summary(E1_model3.min)
+#summary(E1_model3.min)
 
@@
 ```{r}
-ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
+E1_first_fix_plot <- ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
   geom_col()+
@@
 
-E1_spag_fig
-#we should insert a vertical line for the average noun onset
+#TO-DO: insert a vertical line for the average noun onset
 ```
@@
 E1_model1.aggro <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data.aggro)
-summary(E1_model1.aggro)
+#summary(E1_model1.aggro)
 
@@
 E1_model2.aggro <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.aggro)
-summary(E1_model2.aggro)
+#summary(E1_model2.aggro)
 
@@
 
-summary(E1_model3.aggro)
+#summary(E1_model3.aggro)
 
@@
 ```{r}
-ggplot(first.fixation.after.verb.onset.summary.aggro, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
+E1_first_fix_plot_aggro <- ggplot(first.fixation.after.verb.onset.summary.aggro, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
   geom_col()+
@@
 ```
-
-```{r Lab comparison}
-
-```

### 2023-07-06 group-a/analysis_bkp/E1-analysis-calibration.Rmd
edited manuscript.Rmd to refer to E1 Rmds; fixed stuff

--- 2023-07-06 group-a/E1-analysis-calibration.Rmd
@@
 <!-- # Setup -->
-```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
-# library(dplyr)
-# library(tidyr)
-# library(jsonlite)
-# library(ggplot2)
-# library(readr)
-# library(afex)
-# library(forcats)
-# library(papaja)
-# source("~/round.comm.R")
+```{r setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
+library(dplyr)
+library(tidyr)
+library(jsonlite)
+library(ggplot2)
+library(readr)
+library(afex)
+library(forcats)
+library(papaja)
+source("~/round.comm.R")
 
@@
 
-#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 ```
@@
 Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
-Calibration quality varied widely, ranging from `r min(validation.percent$M) %>% round(digits = 2)`% to `r max(validation.percent$M) %>% round(digits = 2)`%.
+Calibration quality varied widely, ranging from `r min(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%) to `r max(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2`%.
 

### 2023-07-06 manuscript.Rmd
edited manuscript.Rmd to refer to E1 Rmds; fixed stuff

@@
 
--   here we will describe the analyses that are as close as possible to
-    the original paper with a minimal validation cutoff
-
--   same analysis but with stricter validation cutoff
-
+```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}
+
+```
 ### Comparison to in-lab data
@@
 
--   here we will describe the analyses that correlate calibration
-    quality with effect size at the individual level
+```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
+
+```
 

### 2023-07-06 manuscript.tex
edited manuscript.Rmd to refer to E1 Rmds; fixed stuff

@@
 
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tidyr} (Version 1.2.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.2.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.3; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.4; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.2.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 \begin{figure}
-\includegraphics[width=6.67in]{group-a/E1-example-trial} \caption{Example trial from Experiment 1.
-Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.}\label{fig:E1-example-trial}
+\centering
+\includegraphics{group-a/E1-example-trial.jpeg}
+\caption{\label{fig:E1-example-trial}Example trial from Experiment 1.
+Participants would hear a sentence (e.g., ``The boy will eat the cake'') and respond according to whether the sentence matched the picture.}
 \end{figure}
@@
 
-\begin{itemize}
-\item
-  here we will describe the analyses that are as close as possible to
-  the original paper with a minimal validation cutoff
-\item
-  same analysis but with stricter validation cutoff
-\end{itemize}
+\textbf{Regions of Interest}.
+Regions of interest (ROIs) were defined by creating boxes around each object in the scene.
+The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
+Each scene contained an agent region, a target region, and three or four distractor regions.
+
+\textbf{Minimal Exclusion}.
+The first set of analyses used minimal exclusion criteria.
+First, we eliminated participants with 0 percent of fixations in any ROIs.
+This resulted in the elimination of 1 participants.
+Second, we excluded participants with validation accuracy under 10 percent, resulting in an additional 5 excluded participants.
+The following analyses included 52 participants.
+
+*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.
+
+\textbf{Cumulative Fixation Probabilities}.
+For each sentence target time window began at the onset of the verb and ended 2000 milliseconds later.
+This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1-spaghetti-fig-1.pdf}
+\caption{\label{fig:E1-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions. The vertical line marks the mean noun onset across trials and conditions.}
+\end{figure}
+
+\textbf{Pre-noun fixations.} In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
+We ran a regression model predicting the cumulative fixation proportion in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
+There were no significant effects, although the critical interaction was in the right direction {[}bar graph?{]} (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.15).
+{[}should i use a table?
+should i change to effects coding like other Exps?
+i think 0/1 is intuitive in this case{]}
+
+\textbf{Pre-verb-offset fixations.} Altmann \& Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
+
+\textbf{First target fixations after verb.} Finally, we address whether participants look to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
+{[}On average, participants looked to the target X ms after (AK's Table 1)\ldots, I'll also want to say the lengths of the verbs.
+AK's Table 2{]} We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
+
+\textbf{Aggressive Exclusion}.
+The second set of analyses used more aggressive exclusion criteria.
+First, we eliminated participants with 20 percent of fixations in any ROIs.
+This resulted in the elimination of 15 participants.
+Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 35 participants.
+The following analyses included 22 participants.
+
+We tested the same three models under these more aggressive exclusion criteria.
+The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction was not statistically significant (Pre-noun-onset window: \emph{b} = 0.07, \emph{SE} = 0.06, \emph{p}=0.23; Pre-verb-offset window: \emph{b} = 0.05, \emph{SE} = 0.05, \emph{p}=0.28).
+However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (\emph{b} = -193.35, \emph{SE} = 96.33, \emph{p}=0.05).
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  here we will describe the analyses that correlate calibration
-  quality with effect size at the individual level
-\end{itemize}
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
+Calibration quality varied widely, ranging from 3.16\% to 98.87\%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+The quality of a participant's calibration was not significantly correlated with the participant's effect size.
+There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
+Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.04, \emph{p} = 0.78.
+However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
 
@@
 and validation (Figure~\ref{fig:E2-calibration-figure}).
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:unnamed-chunk-6}Calibration and validation point locations for Experiment 2.
-Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)}
-\end{figure}
 
@@
 of each item.
-
-\begin{figure}
-\includegraphics[width=5.47in]{group-b/E2-example-figure} \caption{Example trial from Experiment 2.}\label{fig:E2-example-trial}
-\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E2-gaze-fig-both-conds-1.pdf}
-\caption{\label{fig:E2-gaze-fig-both-conds}Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.}
-\end{figure}
-
 The proportions of looks across quadrants in the free-viewing condition were analyzed using a linear mixed-effects model with quadrant as the predictor (critical as the reference level).
@@
 Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E2-rt-acc-fig-1.pdf}
-\caption{\label{fig:E2-rt-acc-fig}Accuracy and response times during memory retrieval.}
-\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-42-1.pdf}
-\caption{\label{fig:unnamed-chunk-42}Calibration and validation point locations for Experiment 3.
-Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.}
-\end{figure}
-
 The experiment was administered over the course of two
@@
 
-\begin{figure}
-\includegraphics[width=3.41in]{group-c/E3-example-figure} \caption{Schematic of the design of Experiment 3}\label{fig:E3-design-schematic}
-\end{figure}
-
 \hypertarget{materials}{%
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plot-cumulative-looking-score-1.pdf}
-\caption{\label{fig:plot-cumulative-looking-score}Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
-\end{figure}
-
 \hypertarget{day-2}{%
@@
 Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(38) = 0.46, p = 0.65 (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(46) = 0.49, p = 0.63.
-
-\includegraphics{manuscript_files/figure-latex/Plot Looking Score Correlations-1.pdf}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E3-roi correlation of looking score-1.pdf}
-\caption{(\#fig:E3-roi correlation of looking score)Correlation between looking scores calculated using ROIs and using screen halves.}
-\end{figure}
-
 \hypertarget{looking-scores}{%
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E3-roi Plot of cumulative looking score-1.pdf}
-\caption{(\#fig:E3-roi Plot of cumulative looking score)Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
-\end{figure}
-
 \hypertarget{correlations-with-day-2-performance}{%
@@
 
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot Calibration Accuracy-1.pdf}
-
 \hypertarget{correlation-with-effects}{%
@@
 
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (halves) by calibration-1.pdf}
-
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (roi) by calibration-1.pdf}
-
 We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
 None of the four relationships showed a significant correlation.
-
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot correlations with calibration score-1.pdf}
 
@@
 critical trials and 24 filler trials presented in a random order.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-45-1.pdf}
-\caption{\label{fig:unnamed-chunk-45}Calibration and validation point locations for Experiment 4.
-Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)}
-\end{figure}
 
@@
 
-\begin{figure}
-\includegraphics[width=4.5in]{group-d/E4-example-figure} \caption{An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}\label{fig:E4-example-trial}
-\end{figure}
-
 \hypertarget{materials-1}{%
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-1.pdf}
-\caption{\label{fig:E4-mouse-moves-fig}Proportion of first mouse movements by location and verb bias.}
-\end{figure}
-
 A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.~equi \& modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.~modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
@@
 The pattern was reversed for looks to the target instrument.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-1.pdf}
-\caption{\label{fig:E4-gaze-timecourse-fig}Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
-\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-web-and-orig-1.pdf}
-\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.}
-\end{figure}
-
 The eye-tracking results from both studies are summarized in Figure \ref{fig:E4-proportion-fix-by-window-both}.
@@
 This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-proportion-fix-by-window-both-1.pdf}
-\caption{\label{fig:E4-proportion-fix-by-window-both}Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
-Error bars reflect bootstrapped 95\% CIs over subject means}
-\end{figure}
 
@@
 Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \ref{fig:E4-example-subj-looks-ROI}b).
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-example-subj-looks-ROI-1.pdf}
-\caption{\label{fig:E4-example-subj-looks-ROI}Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
-Magenta points indicate looks that were not categorized into an ROI}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-quadrants-1.pdf}
-\caption{\label{fig:E4-gaze-timecourse-fig-quadrants}Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
-Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
-\end{figure}
 
@@
 center, middle left, and middle right locations in random order (see Figure~\ref{fig:E5-calibration-figure}).
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-89-1.pdf}
-\caption{\label{fig:unnamed-chunk-89}Calibration and validation point locations for Experiment 5.
-Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.}
-\end{figure}
 
@@
 the 19 face pairs was random for each participant.
-
-\begin{figure}
-\includegraphics[width=3.41in]{group-e/E5-example-figure} \caption{An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}\label{fig:E5-example-trial}
-\end{figure}
 
@@
 
-\begin{figure}
-\includegraphics[width=0.45\linewidth]{figGroupEOrigA} \includegraphics[width=0.45\linewidth]{figGroupEOrigB} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMain-3} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMain-4} \caption{Primary results from Exp.
-5.
-\emph{Top} shows the original results from Shimojo and colleagues (Figures reprinted with permission{[}TODO{]}).
-The attractiveness judgment along with the best-fitting sigmoid is shown in the \emph{top left}.
-Results for the roundness judgment are show in the \emph{top right}, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison (\emph{top right}).
-(\emph{Bottom}) shows the analogous results from the replication, with the attractiveness judgments on the \emph{bottom left} and the roundness judgments on the \emph{bottom right}.
-Again, the best-fitting sigmoid for the attractiveness judgments are plotted with a dashed line alongside the roundness results, for purposes of comparison.}\label{fig:groupEMain}
-\end{figure}
-
 Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig.
@@
 
-\begin{figure}
-\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/E5cal-1} \caption{Histogram of calibration success in Exp.
-5.
-Where participants required more than one calibration (N=8), only the final calibration was considered.}\label{fig:E5cal}
-\end{figure}
-
 To determine whether calibration accuracy influenced our key effects, we calculated the percentage of samples during the task in which the participant was fixating the face they ultimately chose.
@@
 \ref{fig:E5calcorr} reveals that this correlation is due to a handful of particpiants with calibration values below 50\%.
-
-\begin{figure}
-\includegraphics[width=0.8\linewidth]{manuscript_files/figure-latex/E5calcorr-1} \caption{Correlation between calibration accuracy (x-axis) and percentage of samples fixating target (y-axis) in Exp.
-5.}\label{fig:E5calcorr}
-\end{figure}
 
@@
 \ref{fig:groupEMainrev}).
-
-\begin{figure}
-\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMainrev-1} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMainrev-2} \caption{Revised results for Exp.
-5 after removing low-calibration accuracy participants.
-\emph{Left}: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid.
-\emph{Right}: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).}\label{fig:groupEMainrev}
-\end{figure}
 

### 2023-07-31 manuscript.Rmd
added to intro

@@
 
-```{=html}
-<!-- MAJOR TO DOs: 
- - get data from in-lab versions of group A (AJ) and group D (RR)
- - replicate group D and A in lab
-
- (see bottom for notes from e-mails)
- -->
-```
-Intro stuff:
-
--   Eye-tracking as a key method in cognitive science research
-
--   Online data collection is more and more popular & let's us ask new
-    questions, test more diverse populations
-
--   But, concerns over quality + little known about eye-tracking online
+The use of eye-tracking to study cognition took off when Alfred Yarbus used suction cups to affix a mirror system to the sclera of the eye in order to monitor eye position during the perception of images [@yarbus1967eye].
+In one study, participants viewed a painting depicting multiple people in a complex interaction inside of a 19th century Russian home.
+Yarbus showed, among other things, that the scan paths and locations of fixations were largely dependent on the instructions given to participants (e.g., View the picture freely vs.
+Remember the position of the people and objects in the room).
+In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system.
+Since these findings, eye-tracking has become a central method in cognitive science research [for reviews, see @hayhoe2005eye, @richardsonEyeTrackingResearch2004, @rayner1998eye].
+For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning].
+And eye-movements during auditory language comprehension demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
+
+An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time).
+This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research.
+Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD; @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
+
+Advances in software for online data collection [@deleeuwJsPsychJavaScriptLibrary2015; @papoutsaki2016webgazer] have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples.
+In particular, Webgazer.js [@papoutsaki2016webgazer] is a webcam-based Javascript plug-in that works in the browser.
+It can be integrated with any Javascript web interface.
+As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as jsPsych [@deleeuwJsPsychJavaScriptLibrary2015], Gorilla [@anwyl2020gorilla], or lab.js [@henninger2021lab].
+However, the added convenience comes at the cost of spatial and temporal resolution.
+The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are not yet known.
+
+A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data.
+In what follows, we provide a brief review of the published work that we are aware of (note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., @banki2022comparing).
+
+@semmelmann2018online compared eye-tracking results between in-lab and online studies in three tasks: fixation, pursuit, and free viewing.
+
+Yang & Krajbich,
+
+slim & hartsuiker
 
@@
 
-```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}
+```{r E1-analysis-replication,eval=FALSE, child = 'group-a/E1-analysis-replication.Rmd'}
 
@@
 
-```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
+```{r E1-analysis-calibration,eval=FALSE, child = 'group-a/E1-analysis-calibration.Rmd'}
 

### 2023-08-08 manuscript.tex
finished draft of intro

--- 2022-09-25 manuscript.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-Intro stuff:
-
-\begin{itemize}
-\item
-  Eye-tracking as a key method in cognitive science research
-\item
-  Online data collection is more and more popular \& let's us ask new
-  questions, test more diverse populations
-\item
-  But, concerns over quality + little known about eye-tracking online
-\end{itemize}
+The use of eye-tracking to study cognition took off when Alfred Yarbus used suction cups to affix a mirror system to the sclera of the eye in order to monitor eye position during the perception of images (Yarbus, 1967).
+In one study, participants viewed a painting depicting multiple people in a complex interaction inside of a 19th century Russian home.
+Yarbus showed, among other things, that the scan paths and locations of fixations were largely dependent on the instructions given to participants (e.g., View the picture freely vs.~Remember the position of the people and objects in the room).
+In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system.
+Since these findings, eye-tracking has become a central method in cognitive science research Rayner (1998).
+For example, gaze location during natural scene perception is used to test theories of visual attention (e.g., Henderson \& Hayes, 2017).
+And eye-movements during auditory language comprehension, using the ``visual world paradigm,'' demonstrated the context-dependent and incremental nature of language processing (e.g., Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995).
+
+An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time).
+This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research.
+Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic {[}WEIRD; Henrich, Heine, and Norenzayan (2010){]} convenience samples (but see Ryskin, Salinas, Piantadosi, \& Gibson, 2023), which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
+
+Advances in software for online data collection (de Leeuw, 2015; Papoutsaki et al., 2016) have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples.
+In particular, Webgazer.js (Papoutsaki et al., 2016) is a webcam-based Javascript plug-in that works in the browser.
+It can be integrated with any Javascript web interface.
+As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as jsPsych (de Leeuw, 2015), Gorilla (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or lab.js (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021).
+However, the added convenience comes at the cost of spatial and temporal resolution.
+The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are not yet known.
+
+A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data.
+In what follows, we provide a brief review of the published work that we are aware of (note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., Bánki, Eccher, Falschlehner, Hoehl, \& Markova, 2022).
+
+Semmelmann and Weigelt (2018) compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing.
+They used the Webgazer.js library (Papoutsaki et al., 2016) and programmed tasks in HTML/Javascript directly.
+The first two tasks tested measurement of basic gaze properties.
+In the fixation task, participants were asked to fixate a dot, and in the pursuit task, they were asked to follow a dot with their eyes.
+In the free viewing task, the eye movements may have been more semantically driven: participants were shown a picture of a human face and asked to look wherever they wanted to on the image.
+Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed.
+The free viewing task replicated previously observed statistical patterns (e.g., more fixations on eyes than mouths).
+
+Similarly, Yang and Krajbich (2021) used the Webgazer.js library (Papoutsaki et al., 2016) combined with the jsPsych library for conducting behavioral experiments in a web browser (de Leeuw, 2015), to replicate a well-established link between value-based decision-making and eye gaze Krajbich, Armel, \& Rangel (2010).
+Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one.
+During the primary task, on each of 100 trials, two of the snack food images were displayed on the left and right sides of the display and participants chose the one that they preferred while their gaze was monitored.
+As in previous work, participants were biased to choose the option they had spent more time looking at.
+The authors also implemented a code modification to address temporal delays in WebGazer.
+
+Finally, Slim and Hartsuiker (2022) used the Webgazer.js library via the PCIbex online experiment platform (Zehr \& Schwarz, 2018) to replicate a visual world paradigm study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair) (Dijkgraaf, Hartsuiker, \& Duyck, 2017).
+When the verb in the sentence was \emph{constraining} (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was \emph{neutral} (e.g., Mary steals a letter), as in previous work.
+However, they observed a substantial delay of \textasciitilde200ms in the onset of the effect relative to the in-lab study with an infrared eyetracker and a reduction in effect size (despite a threefold increase in sample size relative to the original).
+The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between \emph{constraining} and \emph{neutral} conditions emerged before the onset of the final noun (e.g., letter).
 
@@
 
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tidyr} (Version 1.2.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.3; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 Altmann and Kamide (1999). Altmann and Kamide used the
-visual world eye-tracking paradigm (Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995) to show that
+visual world eye-tracking paradigm (Tanenhaus et al., 1995) to show that
 meanings of verbs rapidly constrain the set of potential subsequent
@@
 
-\begin{itemize}
-\item
-  here we will describe the analyses that are as close as possible to
-  the original paper with a minimal validation cutoff
-\item
-  same analysis but with stricter validation cutoff
-\end{itemize}
-
 \hypertarget{comparison-to-in-lab-data}{%
@@
 \subsubsection{Calibration}\label{calibration}}
-
-\begin{itemize}
-\tightlist
-\item
-  here we will describe the analyses that correlate calibration
-  quality with effect size at the individual level
-\end{itemize}
 
@@
 
+\begin{verbatim}
+## Warning: Using `size` aesthetic for lines was deprecated in ggplot2 3.4.0.
+## i Please use `linewidth` instead.
+## This warning is displayed once every 8 hours.
+## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+## generated.
+\end{verbatim}
+
 \begin{figure}
@@
 
-The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003),
+The fifth study was a replication attempt of Shimojo et al. (2003),
 which found that human gaze is actively involved in preference
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-anwyl2020gorilla}{}}%
+Anwyl-Irvine, A.
+L., Massonnié, J., Flitton, A., Kirkham, N., \& Evershed, J.
+K.
+(2020).
+Gorilla in our midst: An online behavioral experiment builder.
+\emph{Behavior Research Methods}, \emph{52}, 388--407.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-banki2022comparing}{}}%
+Bánki, A., Eccher, M.
+de, Falschlehner, L., Hoehl, S., \& Markova, G.
+(2022).
+Comparing online webcam-and laboratory-based eye-tracking for the assessment of infants' audio-visual synchrony perception.
+\emph{Frontiers in Psychology}, \emph{12}, 733933.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-dijkgraaf2017predicting}{}}%
+Dijkgraaf, A., Hartsuiker, R.
+J., \& Duyck, W.
+(2017).
+Predicting upcoming information in native-language and non-native-language auditory word recognition.
+\emph{Bilingualism: Language and Cognition}, \emph{20}(5), 917--930.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hayhoe2005eye}{}}%
+Hayhoe, M., \& Ballard, D. (2005). Eye movements in natural behavior. \emph{Trends in Cognitive Sciences}, \emph{9}(4), 188--194.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henderson2017meaning}{}}%
+Henderson, J. M., \& Hayes, T. R. (2017). Meaning-based guidance of attention in scenes as revealed by meaning maps. \emph{Nature Human Behaviour}, \emph{1}(10), 743--747.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henninger2021lab}{}}%
+Henninger, F., Shevchenko, Y., Mertens, U. K., Kieslich, P. J., \& Hilbig, B. E. (2021). Lab. Js: A free, open, online study builder. \emph{Behavior Research Methods}, 1--18.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henrich2010weirdest}{}}%
+Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83.
+
 \leavevmode\vadjust pre{\hypertarget{ref-johanssonLookHereEye2014}{}}%
@@
 \url{https://doi.org/10.1177/0956797613498260}
+
+\leavevmode\vadjust pre{\hypertarget{ref-krajbich2010visual}{}}%
+Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rayner1998eye}{}}%
+Rayner, K. (1998). Eye movements in reading and information processing: 20 years of research. \emph{Psychological Bulletin}, \emph{124}(3), 372.
+
+\leavevmode\vadjust pre{\hypertarget{ref-richardsonEyeTrackingResearch2004}{}}%
+Richardson, D.
+C., \& Spivey, M.
+J.
+(2004).
+Eye tracking: {Research} areas and applications.
+In G.
+Wnek \& G.
+Bowlin (Eds.), \emph{Encyclopedia of biomaterials and biomedical engineering} (Vol.
+572).
+New York: Marcel Dekker.
+
 \leavevmode\vadjust pre{\hypertarget{ref-ryskinVerbBiasesAre2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ryskin2023real}{}}%
+Ryskin, R., Salinas, M., Piantadosi, S., \& Gibson, E.
+(2023).
+Real-time inference in communication across cultures: Evidence from a nonindustrialized society.
+\emph{Journal of Experimental Psychology: General}, \emph{152}(5), 1245.
+
+\leavevmode\vadjust pre{\hypertarget{ref-semmelmann2018online}{}}%
+Semmelmann, K., \& Weigelt, S. (2018). Online webcam-based eye tracking in cognitive science: A first look. \emph{Behavior Research Methods}, \emph{50}, 451--465.
+
 \leavevmode\vadjust pre{\hypertarget{ref-shimojoGazeBiasBoth2003}{}}%
@@
 Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
+
+\leavevmode\vadjust pre{\hypertarget{ref-slim2022moving}{}}%
+Slim, M.
+S., \& Hartsuiker, R.
+J.
+(2022).
+Moving visual world experiments online?
+A web-based replication of dijkgraaf, hartsuiker, and duyck (2017) using PCIbex and WebGazer.
+js.
+\emph{Behavior Research Methods}, 1--19.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-yarbus1967eye}{}}%
+Yarbus, A. L. (1967). \emph{Eye movements and vision}. Plenum Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zehr2018PCIbex}{}}%
+Zehr, J., \& Schwarz, F. (2018). \emph{PennController for internet based experiments (IBEX)}. Retrieved from \url{https://doi.org/10.17605/OSF.IO/MD832}
+
 \end{CSLReferences}

### 2023-08-17 E1-analysis-comparison-to-JMW23.Rmd
Exp 1 updates: Adding analysis of Josh H's data, my published tracker data

---
title: "E1-analysis-comparison-to-JMW23"
author: "Ariel James"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(papaja)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)
```

```{r import JMW23}
JMW1_info <- read_csv("group-a/JMW23-data/fyptrialinfo.csv")
JMW1_data <- read.delim("group-a/JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")
#Add meaningful header row
tc_header = c("TARGET","AGENT", "COMP1", "COMP2", "COMP3", 
              "NON1", "NON2", "NON3", "NON4", "NON5",
              "ORDER", "SUBJ", "BIN", "COND", "AID") #AID is a unique item number

colnames(JMW1_data) <- tc_header

#Recode condition
JMW1_data$COND <- as.factor(recode(JMW1_data$COND, "0" = "filler", 
                                "1" = "pred", "2" = "neut"))
JMW1_info$Condition <- as.factor(recode(JMW1_info$Condition, "0" = "filler", 
                                "1" = "pred", "2" = "neut"))

#Remove fillers
JMW1_data_crit <- JMW1_data %>%
  filter(COND != "filler")
JMW1_data_crit <- droplevels(JMW1_data_crit)

#Pull out useful item info
JMW1_info$Non.relative <- JMW1_info$Non-JMW1_info$Von

```

```{r reshape data for comparison}
JMW.long <- JMW1_data_crit %>%
  select(!NON2:ORDER) %>%
  group_by(SUBJ, AID, BIN) %>%
  gather(key = "obj_type", value = "duration", TARGET, AGENT, COMP1, COMP2, COMP3, NON1) %>%
  #create "obj_class" col: name everything that isn't a targeT or agenT "DISTRACTOR" 
  mutate(obj_class = ifelse(str_ends(obj_type, "T"), obj_type, "DISTRACTOR")) %>%
  #create binary "is.fixating" variable
  mutate(is.fixating = ifelse(duration > 0, TRUE, FALSE)) %>%
  filter(BIN >= 0)
```

```{r compute cumulative fix}
#Write function (i.e. copy/paste function Josh deLeeuw wrote)
cumulative.fixation.calculation <- function(df){
  time <- seq(0,1950,50)
  fixations <- logical(length(time))
  hit.flag <- FALSE
  for(i in 1:length(fixations)){
    if(hit.flag){
      fixations[i] <- TRUE
    } else {
      val <- df %>% filter(BIN <= time[i]) %>% pull(is.fixating) %>% any()
      if(val == TRUE) {
        hit.flag <- TRUE
      }
      fixations[i] <- val
    }
  }
  out <- tibble(t.window = time, has.fixated = fixations)
  return(out)
}

#Now use it to summarize timecourse data
if(file.exists("group-a/JMW23-data/generated/JMW_cumulative.csv")){
  JMW_cumu<- read_csv("group-a/JMW23-data/generated/JMW_cumulative.csv")
} else {

  JMW_cumu <-  JMW.long%>%
    group_by(SUBJ, COND, AID, obj_type, obj_class) %>%
    summarize(cumulative.fixation.calculation(cur_data()))

  write_csv(JMW_cumu, file="group-a/JMW23-data/generated/JMW_cumulative.csv")
}
```

<!-- Then group by object class to calculate fixation probability for each kind of object, normalizing by the number of objects of that type. -->

```{r group cumu fix by object}
JMW_cumu.windows.grouped <- JMW_cumu %>%
  group_by(SUBJ, COND, AID, obj_class, t.window) %>%
  summarize(cumu.p = mean(has.fixated)) 
```

<!-- Then collapse over trials to get a cumulative probability for the whole window for each subject -->

```{r collapse cumu fix over trials}
JMW_cumu.windows.grouped.average <- JMW_cumu.windows.grouped %>%
  group_by(SUBJ, COND, obj_class, t.window) %>%
  summarize(cumu.p.avg = mean(cumu.p))
```

<!-- Collapse across subjects to generate the equivalent of the figure from Altmann & Kamide. -->

```{r create summary data for spag plot}
JMW_cumu.summary <- JMW_cumu.windows.grouped.average %>%
  filter(obj_class %in% c('TARGET', 'DISTRACTOR')) %>%
  group_by(t.window, COND, obj_class) %>%
  summarize(cumulative.fixation.m = mean(cumu.p.avg))
```
```{r JMW-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

#AJ: this is where you left off. Everything above should work :)
JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND, group=interaction(COND, obj_class)))+
  scale_fill_manual(values=c("white", "black"))+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative))

JMW_spag_fig

#The "Object type" part of the key doesn't actually show which color is which
```

### 2023-08-17 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
Exp 1 updates: Adding analysis of Josh H's data, my published tracker data

---
title: "Group A"
output: pdf_document
---
<!-- # Setup -->
```{r E1-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
library(patchwork)
source("~/round.comm.R")

knitr::opts_chunk$set(echo = FALSE)
```

<!-- # Import Data -->

<!-- Read JSON files and bind together into a tibble. -->

```{r import-data}
jh.data.files <- list.files('data/data-in-lab-hartshorne', full.names = TRUE, pattern=".json")
jh.data.tables <- lapply(jh.data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
jh.all.data <- bind_rows(jh.data.tables)
```

<!-- Mutate value types as needed -->

```{r value-types}
jh.all.data <- jh.all.data %>%
  mutate(subject_id = factor(subject_id))
```

<!-- Get a list of subject IDs. -->

```{r Get subj IDs}
jh.subjects <- unique(jh.all.data$subject_id)
```

<!-- # Extract Relevant Data -->

<!-- Get data from critical trials, select relevant columns, unnest/unpack webgazer data to get a tidy tibble, -->
<!-- and add gaze measurements as a percentage. -->

```{r Get data}
jh.task.data <- jh.all.data %>%
  filter(verb_type %in% c("restricting", "non-restricting")) %>%
  select(subject_id, stimulus, response, verb_type, webgazer_data, webgazer_targets) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(`#scenes`) %>%
  select(-x,-y) %>%
  unnest(webgazer_data) %>%
  mutate(gaze.x.percent = (x - left) / width * 100) %>%
  mutate(gaze.y.percent = (y - top) / height * 100)
```

<!-- # Add Stimulus Info -->

<!-- Merge in info on visual ROIs and audio onsets. -->

```{r Merge stim info, message=FALSE, warning=FALSE}
#AJ note: I'm assuming it's the exact same stimuli, so using the same info files
ref.image.height <- 1500 # height of images that were measured for ROIs
ref.image.width <- 1875 # width of images that were measured for ROIs
padding <- 20 # padding in pixels around the ROIs.

image.data <- read_csv('info/image_measurements.csv') %>%
  mutate(roi_top = (top_object_distance - padding) / ref.image.height * 100,
         roi_bottom = (bottom_object_distance + padding) / ref.image.height * 100,
         roi_left = (left_object_distance - padding) / ref.image.width * 100,
         roi_right = (right_object_distance + padding) / ref.image.width * 100) %>%
  mutate(object_class = if_else(object_type %in% c('subject', 'target.object'), object_type, 'distractor')) %>%
  select(image_name, object_type, object_class, roi_top, roi_bottom, roi_left, roi_right)

audio.data <- read_csv('info/audio_timestamps.csv') %>% filter(!is.na(stimulus))

jh.critical.trials <- jh.task.data %>%
  left_join(audio.data) %>%
  left_join(image.data)

#check for weirdness
discrep <- audio.data$delay_bw_onset_of_verb_and_onset_of_target_noun - 
  (audio.data$duration_of_verb + 
     audio.data$duration_of_intervening_determiner + 
     audio.data$intonation_break_bw_verb_and_determiner)
sum(discrep) 
#this should be zero, but it's 0.59! TO-DO: Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
```

<!--Figure out word durations by condition (AK Table 2)-->
```{r Word durations}
#First, grab the columns that match stimulus to condition name
jh.stim.cond <- distinct(data.frame(jh.critical.trials$stimulus, jh.critical.trials$verb_type))
colnames(jh.stim.cond) <- c("stimulus", "verb_type")

#Then merge with audio data
jh.word.dur.data <- left_join(audio.data, jh.stim.cond)

#Then summarize by condition
#word.dur.avg <- round.comm(colMeans(word.dur.data[,2:10])*1000)
jh.word.dur.avg <- jh.word.dur.data %>%
  group_by(verb_type) %>%
  summarise(Verb = round.comm(mean(duration_of_verb)*1000),
            Post_verbal_break = round.comm(mean(intonation_break_bw_verb_and_determiner)*1000),
            Determiner = round.comm(mean(duration_of_intervening_determiner)*1000),
            Total = Verb + Post_verbal_break + Determiner)

```

<!-- # Compute Gaze in ROI -->

<!-- Define a function for determining if `x,y` value falls in box. -->

```{r Gaze in ROI}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

<!-- Add a column with boolean value for whether gaze was in the ROI. -->

```{r Yes/No in ROI}
jh.critical.trials <- jh.critical.trials %>%
  mutate(is.fixating = in.box(gaze.x.percent, gaze.y.percent, roi_left, roi_right, roi_top, roi_bottom, 0))
```

<!-- # Subject Exclusion Criteria -->

<!-- We'll try this two ways. First if we adopt minimal exclusion criteria, removing subjects whose eye tracking data is essentially unusable. Second if we adopt aggressive exclusion criteria, removing subjects with obviously worse eye tracking data. -->

<!--###MINIMAL EXCLUSION-->
<!-- Set which mode here: -->
```{r Exclusion mode}
#AJ note: we're just gonna do minimal
# 'AGGRESSIVE' or 'MINIMAL'
#exclusion.mode <- 'MINIMAL' 
```

<!-- ## Proportion of measured data in an ROI. -->

<!-- Check the proportion of samples that were in at least one ROI for subjects. 
Which is to say: at each event time "t" per trial per subject, check whether they were looking at ANY of the objects (vs background/off-screen). What proportion of fixation events (total number varies by trial/subj) were in ANY ROI? -->

```{r prop-in-ROI}
jh.prop.in.roi.by.subject <- jh.critical.trials %>%
  group_by(subject_id, t, image_name) %>%
  summarize(fixation.in.roi = any(is.fixating)) %>%
  group_by(subject_id) %>%
  summarize(prop.of.samples.in.roi = mean(fixation.in.roi))
```
<!-- Visualize proportion of samples in ROI by subject. -->

```{r roi histogram, eval=F}
#printed?
hist(jh.prop.in.roi.by.subject$prop.of.samples.in.roi, breaks=20)
```

<!-- Exclude subjects below a threshold -->

```{r exclude by prop in roi}
prop.samples.threshold.min <- 0

jh.bad.subjects.prop.samples.min <- jh.prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi <= prop.samples.threshold.min) %>%
  pull(subject_id) %>%
  as.character()
```

<!-- ## Validation accuracy -->

```{r get validation data}
jh.validation.accuracy.data <- jh.all.data %>%
  filter(trial_type == 'webgazer-validate')
```

<!-- What % of subjects needed to recalibrate because of poor initial calibration? -->

```{r summarize calibration data, eval=F}
#printed?
jh.validation.accuracy.data %>% 
  group_by(subject_id) %>%
  count() %>% 
  group_by(n) %>%
  count()
#AJ note: How many times does each P appear (n is the different values this can take: once, twice), and how many Ps appear at each of those (n) frequencies? 12 Ps appear once, 37 Ps appear twice. 
```

<!-- Get final average distance for each subject -->

```{r save validation percent in roi during validation}
jh.validation.percent <- jh.validation.accuracy.data %>%
  group_by(subject_id) %>%
  slice_tail() %>%
  select(subject_id, percent_in_roi) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  mutate(subject_id = fct_reorder(subject_id, M))

save(jh.validation.percent, file = "jh.validation.percent.RData")
```

```{r plot subjects by validation, eval=F}
#printed?
ggplot(jh.validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

```{r filter by validation}
validation.threshold.min <- 10

jh.bad.subjects.validation.min <- jh.validation.percent %>%
  filter(M <= validation.threshold.min) %>%
  pull(subject_id) %>%
  as.character()
```

<!-- ## Final exclusion data -->

```{r summarize exclusions}
jh.bad.subjects.min <- unique(c(jh.bad.subjects.prop.samples.min, jh.bad.subjects.validation.min))

jh.critical.trials.filtered.min <- jh.critical.trials %>%
  filter(!subject_id %in% jh.bad.subjects.min)

n.jh.bad.subjects.min <- length(jh.bad.subjects.min)
#It's 2 (from the validation criterion)

```
<!-- This is where I should say how many people were excluded, right? -->
__Regions of Interest__. Regions of interest (ROIs) were defined by creating boxes around each object in the scene. The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding. Each scene contained an agent region, a target region, and three or four distractor regions.

__Minimal Exclusion__. The first set of analyses used minimal exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs. This resulted in the elimination of `r length(jh.bad.subjects.prop.samples.min)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in an additional `r n.jh.bad.subjects.min - length(jh.bad.subjects.prop.samples.min)` excluded participants. The following analyses included `r nlevels(droplevels(jh.critical.trials.filtered.min$subject_id))` participants.

<!-- # Calculating cumulative fixation probability -->

<!-- We start by calculating cumulative fixation probability on the objects after the verb onset. (Any fixations prior to the verb onset are not relevant to the core research questions.) -->

*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.

<!-- First, add a column for time relative to verb onset, bin this to 50ms chunks, and filter the data to the 2,000 ms window after verb onset. -->

```{r set up 50 ms bins}
jh.cumulative.fixation.data.min <- jh.critical.trials.filtered.min %>%
  mutate(t.relative.to.verb.onset = t - (verb_onset*1000)) %>%
  filter(t.relative.to.verb.onset >= 0 & t.relative.to.verb.onset <2000) %>%
  mutate(t.w = floor(t.relative.to.verb.onset/50)*50)
```

<!-- Now check every time window within a trial to account for sparse samples. This calculating is time consuming, so we cache the result in a CSV file, and load from the CSV if it already exists. -->

```{r slowly build cumu fix data}
cumulative.fixation.calculation <- function(df){
  time <- seq(0,1950,50)
  fixations <- logical(length(time))
  hit.flag <- FALSE
  for(i in 1:length(fixations)){
    if(hit.flag){
      fixations[i] <- TRUE
    } else {
      val <- df %>% filter(t.w <= time[i]) %>% pull(is.fixating) %>% any()
      if(val == TRUE) {
        hit.flag <- TRUE
      }
      fixations[i] <- val
    }
  }
  out <- tibble(t.window = time, has.fixated = fixations)
  return(out)
}

setwd("/Users/ajames2/Documents/GitHub/219-2021-eyetracking-analysis/group-a/")

if(file.exists("data/data-in-lab-hartshorne/generated/jh.cumulative_fixation_data_min.csv")){
  jh.cumulative.fixation.windows.data.min <- read_csv("data/generated/jh.cumulative_fixation_data_min.csv")
} else {

  jh.cumulative.fixation.windows.data.min <- jh.cumulative.fixation.data.min %>%
    group_by(subject_id, verb_type, image_name, object_type, object_class) %>%
    summarize(cumulative.fixation.calculation(cur_data()))

  write_csv(jh.cumulative.fixation.windows.data.min, file="data/generated/jh.cumulative_fixation_data_min.csv")
}
```

<!-- Then group by object class to calculate fixation probability for each kind of object, normalizing by the number of objects of that type. -->

```{r group cumu fix by object}
jh.cumulative.fixation.windows.grouped.data.min <- jh.cumulative.fixation.windows.data.min %>%
  filter(!subject_id %in% jh.bad.subjects.min) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

<!-- Then collapse over trials to get a cumulative probability for the whole window for each subject -->

```{r collapse cumu fix over trials}
jh.cumulative.fixation.windows.grouped.average.data.min <- jh.cumulative.fixation.windows.grouped.data.min %>%
  group_by(subject_id, verb_type, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(cumulative.fixation.p))
```

<!-- Collapse across subjects to generate the equivalent of the figure from Altmann & Kamide. -->

```{r create summary data for spag plot}
jh.cumulative.fixation.data.summary.min <- jh.cumulative.fixation.windows.grouped.average.data.min %>%
  filter(object_class %in% c('target.object', 'distractor')) %>%
  group_by(t.window, verb_type, object_class) %>%
  summarize(cumulative.fixation.m = mean(cumulative.fixation.p))
```

__Cumulative Fixation Probabilities__. For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later. This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin. Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:jh.E1-spaghetti-fig).

```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."} 
jh.E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(word.dur.avg$Total))

jh.E1_spag_fig

#The "Object type" part of the key doesn't actually show which color is which
```

<!-- __Question 1: Are there more pre-noun first looks to the target object than to the distractors?__

First, grab the noun onset times to merge into our cumulative fixation data.-->

```{r set up noun onset times}
jh.noun.onset.times.min <- jh.critical.trials.filtered.min %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, delay_bw_onset_of_verb_and_onset_of_target_noun) %>%
  mutate(relative.noun.onset = delay_bw_onset_of_verb_and_onset_of_target_noun * 1000) %>%
  select(-delay_bw_onset_of_verb_and_onset_of_target_noun)

jh.trial.level.cumulative.fixation.data.min <- jh.cumulative.fixation.windows.grouped.data.min %>%
  left_join(jh.noun.onset.times.min, by=c("image_name", "verb_type"))
```

<!--Then, grab the last time window before the noun onset for each trial. This is the critical data for this test.-->

```{r find prenoun window data}
jh.pre.noun.first.looks.data.min <- jh.trial.level.cumulative.fixation.data.min %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.noun.onset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r save prenoun window data}
jh.pre.noun.first.looks.data.min$verb_type <- as.factor(jh.pre.noun.first.looks.data.min$verb_type)
jh.pre.noun.first.looks.data.min$object_class <- as.factor(jh.pre.noun.first.looks.data.min$object_class)

save(jh.pre.noun.first.looks.data.min, file = "jh.pre.noun.first.looks.data.min.RData")
```
<!--Fit the model, with no covariance between random effects because the model cannot converge with full covariance matrix.-->

```{r run model 1}
jh.E1_model1.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.noun.first.looks.data.min)
#summary(jh.E1_model1.min)

jh.E1_model1_tab.min = broom.mixed::tidy(jh.E1_model1.min) 
jh.E1_model1_obj.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model1_verb.min = jh.E1_model1_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model1_obj_verb.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
__Pre-noun fixations.__ In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting. The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun. We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix). There were no significant effects, although the critical interaction was in the right direction [bar graph?] (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

<!--Verb offset times-->

```{r find verb offset data}
jh.verb.offset.times.min <- jh.critical.trials.filtered.min %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, duration_of_verb) %>%
  mutate(relative.verb.offset = duration_of_verb * 1000) %>%
  select(-duration_of_verb)

jh.trial.level.cumulative.fixation.data.verb.offset.min <- jh.cumulative.fixation.windows.grouped.data.min %>%
  left_join(jh.verb.offset.times.min, by=c("image_name", "verb_type"))
```

```{r save verb offset data}
jh.pre.verb.offset.first.looks.data.min <- jh.trial.level.cumulative.fixation.data.verb.offset.min %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.verb.offset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))

save(jh.pre.verb.offset.first.looks.data.min, file = "jh.pre.verb.offset.first.looks.data.min.RData")
```

```{r run model 2}
#model <- lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.verb.offset.first.looks.data.min)
#summary(model)

jh.E1_model2.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.verb.offset.first.looks.data.min)
#summary(jh.E1_model2.min)

jh.E1_model2_tab.min = broom.mixed::tidy(jh.E1_model2.min) 
jh.E1_model2_obj.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model2_verb.min = jh.E1_model2_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model2_obj_verb.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
__Pre-verb-offset fixations.__ Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

<!--Relative to noun onset, when is the first (post-verb) fixation on the target?-->

```{r}
jh.first.fixation.after.verb.onset.min <- jh.critical.trials.filtered.min %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>%
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>%
  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
  mutate(von_relative.t = t - (verb_onset*1000)) %>%
  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
```

```{r E1-latency-table-min, echo=FALSE, eval=FALSE}
#summarize data for table
jh.first.fix.avg.min <- jh.first.fixation.after.verb.onset.min %>%
  group_by(verb_type) %>%
  summarise(Verb.on = round.comm(mean(von_relative.t)),
            Verb.off = round.comm(mean(voff_relative.t)),
            Det.on = round.comm(mean(det_relative.t)),
            Noun.on = round.comm(mean(noun_relative.t)))

#put data into a data frame
jh.our_table1_min <- data.frame(
  Time = c("Verb onset", "Verb offset", "Determiner onset", "Noun onset"),
  Eat = c(jh.first.fix.avg.min$Verb.on[2],
           jh.first.fix.avg.min$Verb.off[2],
           jh.first.fix.avg.min$Det.on[2],
           jh.first.fix.avg.min$Noun.on[2]),
  Move = c(jh.first.fix.avg.min$Verb.on[1],
           jh.first.fix.avg.min$Verb.off[1],
           jh.first.fix.avg.min$Det.on[1],
           jh.first.fix.avg.min$Noun.on[1]),
  Difference = c(jh.first.fix.avg.min$Verb.on[1]-jh.first.fix.avg.min$Verb.on[2],
                  jh.first.fix.avg.min$Verb.off[1]-jh.first.fix.avg.min$Verb.off[2],
                  jh.first.fix.avg.min$Det.on[1]-jh.first.fix.avg.min$Det.on[2],
                  jh.first.fix.avg.min$Noun.on[1]-jh.first.fix.avg.min$Noun.on[2])
)

# AK_table1 <- data.frame(
#   Time = c("Verb onset", "Verb offset", "Determiner onset", "Noun onset"),
#   Eat = c(611, 228, 37, -85),
#   Move = c(838, 415, 234, 127),
#   Difference = c(227, 187, 197, 212))
# 
# E1_latency_table_min <- merge(our_table1_min, AK_table1, by = "Time")
#   
# apa_table(
#   E1_latency_table_min,
#   caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
#   font_size = "small",
#    col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
# )
# 
# 
# #can I add a third dimension i.e. have two headings to group our data vs. AK data?
# 
# #knitr::kable(table1_min)
```

```{r}
jh.first.fixation.after.verb.onset.analysis.data.min <- jh.first.fixation.after.verb.onset.min %>%
  ungroup() %>%
  select(subject_id, image_name, verb_type, duration_of_verb, noun_relative.t) %>%
  mutate(dur_verb_ms_c = scale(duration_of_verb, scale = FALSE)*1000) #mean-center verb duration

save(jh.first.fixation.after.verb.onset.analysis.data.min, file = "jh.first.fixation.after.verb.onset.analysis.data.min.RData")
```

```{r run model 3}
jh.E1_model3.min <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=jh.first.fixation.after.verb.onset.analysis.data.min)

#summary(jh.E1_model3.min)

jh.E1_model3_tab.min = broom.mixed::tidy(jh.E1_model3.min) 
jh.E1_model3_verb.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting")

```
__First target fixations after verb.__ Finally, we address whether participants look to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. [TO-DO: On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs. AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).

```{r}
jh.first.fixation.after.verb.onset.subject.summary.min <- jh.first.fixation.after.verb.onset.min %>%
  group_by(subject_id, verb_type) %>%
  summarize(m.t = mean(noun_relative.t), ct = n())

jh.first.fixation.after.verb.onset.summary.min <- jh.first.fixation.after.verb.onset.subject.summary.min %>%
  group_by(verb_type) %>%
  summarize(m=mean(m.t), sd=sd(m.t), se=sd/sqrt(n()))

save(jh.first.fixation.after.verb.onset.summary.min, file = "jh.first.fixation.after.verb.onset.subject.summary.min.RData")
```

```{r}
jh.E1_first_fix_plot <- ggplot(jh.first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
  geom_col()+
  geom_errorbar(width=0.2)
```

### 2023-08-17 group-a/E1-analysis-replication.Rmd
Exp 1 updates: Adding analysis of Josh H's data, my published tracker data

@@
 
-```{r collapse sumu fix over trials}
+```{r collapse cumu fix over trials}
 cumulative.fixation.windows.grouped.average.data.min <- cumulative.fixation.windows.grouped.data.min %>%
@@
 __Cumulative Fixation Probabilities__.
-For each sentence target time window began at the onset of the verb and ended 2000 milliseconds later.
+For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
@@
 
-```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions. The vertical line marks the mean noun onset across trials and conditions."} 
-E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
-  scale_fill_grey(start=1.0, end=0.0)+
-  scale_shape_manual(values=c(22,21))+
+```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions."}
+E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
   geom_line()+
-  geom_point(size=2)+
+  geom_point(size=2, aes(fill=object_class, shape=verb_type))+
+  #scale_fill_grey(start=1.0, end=0.0)+
+  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"))+
+  scale_shape_manual(name = "Verb Type", values=c(22,21))+
+  labs(x="Time from Verb Onset (ms)", y="Probability")+#, shape="Verb Type", fill="Object Type")+
+  #geom_line(aes(group=interaction(verb_type, object_class)))+
   theme_bw()+
@@
   scale_x_continuous(expand=c(0.01,0.01))+
-  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
   geom_vline(xintercept = mean(word.dur.avg$Total))
@@
 E1_spag_fig
+
+#The "Object type" part of the key doesn't actually show which color is which
 ```
@@
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
-We ran a regression model predicting the cumulative fixation proportion in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.
+We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.
 non-restricting = 0), object type (target = 1 vs.
@@
 There were no significant effects, although the critical interaction was in the right direction [bar graph?] (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
-[should i use a table?
-should i change to effects coding like other Exps?
-i think 0/1 is intuitive in this case]
 
@@
 the non-restrictive condition, starting after the onset of the verb.
-[On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs.
+[TO-DO: On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs.
 AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
@@
 #|,and target objects across conditions."
-E1_spag_fig <- ggplot(cumulative.fixation.data.summary.aggro, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
+E1_spag_fig_aggro <- ggplot(cumulative.fixation.data.summary.aggro, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
   scale_fill_grey(start=1.0, end=0.0)+

### 2023-08-17 manuscript.Rmd

@@
 For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning].
-And eye-movements during auditory language comprehension demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
+And eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
 
@@
 A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data.
-In what follows, we provide a brief review of the published work that we are aware of (note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., @banki2022comparing).
-
-@semmelmann2018online compared eye-tracking results between in-lab and online studies in three tasks: fixation, pursuit, and free viewing.
-
-Yang & Krajbich,
-
-slim & hartsuiker
+In what follows, we provide a brief review of the published work that we are aware of [note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., @banki2022comparing].
+
+@semmelmann2018online compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing.
+They used the Webgazer.js library [@papoutsaki2016webgazer] and programmed tasks in HTML/Javascript directly.
+The first two tasks tested measurement of basic gaze properties.
+In the fixation task, participants were asked to fixate a dot, and in the pursuit task, they were asked to follow a dot with their eyes.
+In the free viewing task, the eye movements may have been more semantically driven: participants were shown a picture of a human face and asked to look wherever they wanted to on the image.
+Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed.
+The free viewing task replicated previously observed statistical patterns (e.g., more fixations on eyes than mouths).
+
+Similarly, @yang2021webcam used the Webgazer.js library [@papoutsaki2016webgazer] combined with the jsPsych library for conducting behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015], to replicate a well-established link between value-based decision-making and eye gaze [e.g., @shimojoGazeBiasBoth2003, @krajbich2010visual].
+Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one.
+During the primary task, on each of 100 trials, two of the snack food images were displayed on the left and right sides of the display and participants chose the one that they preferred while their gaze was monitored.
+As in previous work, participants were biased to choose the option they had spent more time looking at.
+The authors also implemented a code modification to address temporal delays in WebGazer.
+
+Finally, @slim2022moving used the Webgazer.js library via the PCIbex online experiment platform [@zehr2018PCIbex] to replicate a visual world paradigm study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair)  [@dijkgraaf2017predicting].
+When the verb in the sentence was _constraining_ (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was _neutral_ (e.g., Mary steals a letter), as in previous work.
+However, they observed a substantial delay of ~200ms in the onset of the effect relative to the in-lab study with an infrared eyetracker and a reduction in effect size (despite a threefold increase in sample size relative to the original).
+The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between _constraining_ and _neutral_ conditions emerged before the onset of the final noun (e.g., letter).
 

### 2023-08-18 group-a/E1-analysis-calibration-Hartshorne.Rmd
Small edits so it hopefully knits, moved stuff around

---
title: "E1 JH data calibration"
author: "Ariel James"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source("~/round.comm.R")

knitr::opts_chunk$set(include = FALSE, echo = FALSE, message = FALSE, warning = FALSE)
#knitr::opts_knit$set(root.dir =)

#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

```{r Load data}
attach("jh.pre.noun.first.looks.data.min.RData")
attach("jh.pre.verb.offset.first.looks.data.min.RData")
attach("jh.first.fixation.after.verb.onset.analysis.data.min.RData")
attach("jh.validation.percent.RData")
#AJ: for some reason it can't find the next one:
attach("jh.first.fixation.after.verb.onset.subject.summary.min.RData")

jh.pre.noun.first.looks.data <- jh.pre.noun.first.looks.data.min

jh.pre.verb.offset.first.looks.data <- jh.pre.verb.offset.first.looks.data.min

jh.first.fixation.after.verb.onset.analysis.data <- jh.first.fixation.after.verb.onset.analysis.data.min

jh.first.fixation.after.verb.onset.subject.summary <- jh.first.fixation.after.verb.onset.subject.summary.min  
```

```{r Model 1 subject summary}
jh.pre.noun.subj.summary <- jh.pre.noun.first.looks.data %>%
  group_by(subject_id, verb_type, object_class) %>%
  summarize(fix.p = mean(cumulative.fixation.p))

jh.pre.noun.by.verb <- jh.pre.noun.subj.summary %>%
  pivot_wider(names_from = object_class, values_from = fix.p) %>%
  mutate(tar.adv = target.object - distractor)

jh.pre.noun.effects <- jh.pre.noun.by.verb %>%
  select(subject_id, verb_type, tar.adv) %>%
  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(effect = restricting - non_restricting)
```

```{r Model 1 effect size by calibration}
#merge with validation percent

jh.cali.analy.1 <- merge(jh.pre.noun.effects, jh.validation.percent, by = "subject_id")

#correlate
jh.m1_diffdiff_cor <- cor.test(jh.cali.analy.1$effect, jh.cali.analy.1$M, use = "pairwise.complete.obs") #difference of differences
#0.03107354
jh.m1_diffdiff_cor_r <- jh.m1_diffdiff_cor$estimate
jh.m1_diffdiff_cor_p <- jh.m1_diffdiff_cor$p.value

jh.m1_diff_cor <- cor.test(jh.cali.analy.1$restricting, jh.cali.analy.1$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
#0.2096605
jh.m1_diff_cor_r <- jh.m1_diff_cor$estimate
jh.m1_diff_cor_p <- jh.m1_diff_cor$p.value
```

```{r Model 2 subject summary}
jh.pre.verb.subj.summary <- jh.pre.verb.offset.first.looks.data %>%
  group_by(subject_id, verb_type, object_class) %>%
  summarize(fix.p = mean(cumulative.fixation.p))

jh.pre.verb.by.verb <- jh.pre.verb.subj.summary %>%
  pivot_wider(names_from = object_class, values_from = fix.p) %>%
  mutate(tar.adv = target.object - distractor)

jh.pre.verb.effects <- jh.pre.verb.by.verb %>%
  select(subject_id, verb_type, tar.adv) %>%
  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(effect = restricting - non_restricting)
```

```{r Model 2 effect size by calibration}
#merge with validation percent
jh.cali.analy.2 <- merge(jh.pre.verb.effects, jh.validation.percent, by = "subject_id")

#correlate
jh.m2_diffdiff_cor <- cor.test(jh.cali.analy.2$effect, jh.cali.analy.2$M, use = "pairwise.complete.obs") #difference of differences
#-0.04809241
jh.m2_diffdiff_cor_r <- jh.m2_diffdiff_cor$estimate
jh.m2_diffdiff_cor_p <- jh.m2_diffdiff_cor$p.value

jh.m2_diff_cor <- cor.test(jh.cali.analy.2$restricting, jh.cali.analy.2$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
#-0.03601876
jh.m2_diff_cor_r <- jh.m2_diff_cor$estimate
jh.m2_diff_cor_p <- jh.m2_diff_cor$p.value

```

```{r Model 3 effect size by calibration}
#summary(validation.percent)
#make looking scores for Ps
jh.looking.scores <- jh.first.fixation.after.verb.onset.subject.summary[,1:3] %>% 
  spread(verb_type, m.t) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(diff = non_restricting - restricting)

#merge with validation percent
jh.cali.analy.3 <- merge(jh.looking.scores, jh.validation.percent, by = "subject_id")

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```

As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%.

We tested whether a participant's calibration quality was correlated with their effect size. Across the three condition effects of interest, calibration quality [was? was not?] significantly correlated (Effect 1 (pre-noun-onset): Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`, Effect 2 (pre-verb-offset): Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`, Effect 3 (first fixation): Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`. However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e. rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).

### 2023-08-18 group-a/E1-analysis-calibration.Rmd
Small edits so it hopefully knits, moved stuff around

@@
 ```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
-# library(dplyr)
-# library(tidyr)
-# library(jsonlite)
-# library(ggplot2)
-# library(readr)
-# library(afex)
-# library(forcats)
-# library(papaja)
-# source("~/round.comm.R")
+library(dplyr)
+library(tidyr)
+library(jsonlite)
+library(ggplot2)
+library(readr)
+library(afex)
+library(forcats)
+library(papaja)
+source("~/round.comm.R")
 
@@
 We tested whether a participant's calibration quality was correlated with their effect size.
-The quality of a participant's calibration was not significantly correlated with the participant's effect size.
 There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).

### 2023-08-18 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
Small edits so it hopefully knits, moved stuff around

@@
 ---
-title: "Group A"
+title: "Group A, in-lab"
 output: pdf_document
@@
 <!-- # Setup -->
-```{r E1-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
+```{r E1-setup, include = FALSE, echo = FALSE}
 library(dplyr)
@@
 
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
 ```
@@
 
-```{r Merge stim info, message=FALSE, warning=FALSE}
+```{r Merge stim info, message=FALSE, warning=FALSE, include=FALSE}
 #AJ note: I'm assuming it's the exact same stimuli, so using the same info files
@@
 <!--Figure out word durations by condition (AK Table 2)-->
-```{r Word durations}
+```{r Word durations, message=FALSE, warning=FALSE, include=FALSE}
 #First, grab the columns that match stimulus to condition name
@@
 
-```{r prop-in-ROI}
+```{r prop-in-ROI, message=FALSE, warning=FALSE, include=FALSE}
 jh.prop.in.roi.by.subject <- jh.critical.trials %>%
@@
 ```
-<!-- This is where I should say how many people were excluded, right? -->
+<!-- This should maybe go at the beginning of analysis section so that I just say it once? -->
 __Regions of Interest__.
-Regions of interest (ROIs) were defined by creating boxes around each object in the scene.
+ROIs were defined by creating boxes around each object in the scene.
 The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
@@
 __Minimal Exclusion__.
-The first set of analyses used minimal exclusion criteria.
-First, we eliminated participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs.
-This resulted in the elimination of `r length(jh.bad.subjects.prop.samples.min)` participants.
-Second, we excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in an additional `r n.jh.bad.subjects.min - length(jh.bad.subjects.prop.samples.min)` excluded participants.
+As in the remote sample, we checked whether there were participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs and there were none.
+We then excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in `r n.jh.bad.subjects.min - length(jh.bad.subjects.prop.samples.min)` excluded participants.
 The following analyses included `r nlevels(droplevels(jh.critical.trials.filtered.min$subject_id))` participants.
@@
 
-*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.
-
 <!-- First, add a column for time relative to verb onset, bin this to 50ms chunks, and filter the data to the 2,000 ms window after verb onset. -->
 
-```{r set up 50 ms bins}
+```{r set up 50 ms bins, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.data.min <- jh.critical.trials.filtered.min %>%
@@
 
-```{r slowly build cumu fix data}
+```{r slowly build cumu fix data, message=FALSE, warning=FALSE}
 cumulative.fixation.calculation <- function(df){
@@
 
-```{r group cumu fix by object}
+```{r group cumu fix by object, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.windows.grouped.data.min <- jh.cumulative.fixation.windows.data.min %>%
@@
 
-```{r collapse cumu fix over trials}
+```{r collapse cumu fix over trials, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.windows.grouped.average.data.min <- jh.cumulative.fixation.windows.grouped.data.min %>%
@@
 
-```{r create summary data for spag plot}
+```{r create summary data for spag plot, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.data.summary.min <- jh.cumulative.fixation.windows.grouped.average.data.min %>%
@@
   labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
-  geom_vline(xintercept = mean(word.dur.avg$Total))
+  geom_vline(xintercept = mean(jh.word.dur.avg$Total))
 
@@
 
-```{r run model 1}
+```{r run model 1, message=FALSE, warning=FALSE}
 jh.E1_model1.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.noun.first.looks.data.min)
@@
 
-```{r run model 2}
+```{r run model 2, message=FALSE, warning=FALSE}
 #model <- lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.verb.offset.first.looks.data.min)
@@
 
-```{r run model 3}
+```{r run model 3, message=FALSE, warning=FALSE}
 jh.E1_model3.min <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=jh.first.fixation.after.verb.onset.analysis.data.min)
@@
 ```
+
+<!-- CALIBRATION ANALYSIS -->
+
+```{r rename stuff}
+jh.pre.noun.first.looks.data <- jh.pre.noun.first.looks.data.min
+
+jh.pre.verb.offset.first.looks.data <- jh.pre.verb.offset.first.looks.data.min
+
+jh.first.fixation.after.verb.onset.analysis.data <- jh.first.fixation.after.verb.onset.analysis.data.min
+
+jh.first.fixation.after.verb.onset.subject.summary <- jh.first.fixation.after.verb.onset.subject.summary.min  
+```
+
+```{r Model 1 subject summary}
+jh.pre.noun.subj.summary <- jh.pre.noun.first.looks.data %>%
+  group_by(subject_id, verb_type, object_class) %>%
+  summarize(fix.p = mean(cumulative.fixation.p))
+
+jh.pre.noun.by.verb <- jh.pre.noun.subj.summary %>%
+  pivot_wider(names_from = object_class, values_from = fix.p) %>%
+  mutate(tar.adv = target.object - distractor)
+
+jh.pre.noun.effects <- jh.pre.noun.by.verb %>%
+  select(subject_id, verb_type, tar.adv) %>%
+  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
+  rename("non_restricting" = "non-restricting") %>%
+  mutate(effect = restricting - non_restricting)
+```
+
+```{r Model 1 effect size by calibration}
+#merge with validation percent
+
+jh.cali.analy.1 <- merge(jh.pre.noun.effects, jh.validation.percent, by = "subject_id")
+
+#correlate
+jh.m1_diffdiff_cor <- cor.test(jh.cali.analy.1$effect, jh.cali.analy.1$M, use = "pairwise.complete.obs") #difference of differences
+#0.03107354
+jh.m1_diffdiff_cor_r <- jh.m1_diffdiff_cor$estimate
+jh.m1_diffdiff_cor_p <- jh.m1_diffdiff_cor$p.value
+
+jh.m1_diff_cor <- cor.test(jh.cali.analy.1$restricting, jh.cali.analy.1$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
+#0.2096605
+jh.m1_diff_cor_r <- jh.m1_diff_cor$estimate
+jh.m1_diff_cor_p <- jh.m1_diff_cor$p.value
+```
+
+```{r Model 2 subject summary}
+jh.pre.verb.subj.summary <- jh.pre.verb.offset.first.looks.data %>%
+  group_by(subject_id, verb_type, object_class) %>%
+  summarize(fix.p = mean(cumulative.fixation.p))
+
+jh.pre.verb.by.verb <- jh.pre.verb.subj.summary %>%
+  pivot_wider(names_from = object_class, values_from = fix.p) %>%
+  mutate(tar.adv = target.object - distractor)
+
+jh.pre.verb.effects <- jh.pre.verb.by.verb %>%
+  select(subject_id, verb_type, tar.adv) %>%
+  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
+  rename("non_restricting" = "non-restricting") %>%
+  mutate(effect = restricting - non_restricting)
+```
+
+```{r Model 2 effect size by calibration}
+#merge with validation percent
+jh.cali.analy.2 <- merge(jh.pre.verb.effects, jh.validation.percent, by = "subject_id")
+
+#correlate
+jh.m2_diffdiff_cor <- cor.test(jh.cali.analy.2$effect, jh.cali.analy.2$M, use = "pairwise.complete.obs") #difference of differences
+#-0.04809241
+jh.m2_diffdiff_cor_r <- jh.m2_diffdiff_cor$estimate
+jh.m2_diffdiff_cor_p <- jh.m2_diffdiff_cor$p.value
+
+jh.m2_diff_cor <- cor.test(jh.cali.analy.2$restricting, jh.cali.analy.2$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
+#-0.03601876
+jh.m2_diff_cor_r <- jh.m2_diff_cor$estimate
+jh.m2_diff_cor_p <- jh.m2_diff_cor$p.value
+
+```
+
+```{r Model 3 effect size by calibration}
+#summary(validation.percent)
+#make looking scores for Ps
+jh.looking.scores <- jh.first.fixation.after.verb.onset.subject.summary[,1:3] %>% 
+  spread(verb_type, m.t) %>%
+  rename("non_restricting" = "non-restricting") %>%
+  mutate(diff = non_restricting - restricting)
+
+#merge with validation percent
+jh.cali.analy.3 <- merge(jh.looking.scores, jh.validation.percent, by = "subject_id")
+
+#correlate
+jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
+#0.04122796
+jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
+jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
+```
+#### Calibration
+As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
+Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+Across the three condition effects of interest, calibration quality [was?
+was not?] significantly correlated (Effect 1 (pre-noun-onset): Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`, Effect 2 (pre-verb-offset): Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`, Effect 3 (first fixation): Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
+However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.
+rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).

### 2023-08-18 group-a/E1-analysis-comparison-to-JMW23.Rmd
Small edits so it hopefully knits, moved stuff around

--- 2023-08-17 E1-analysis-comparison-to-JMW23.Rmd
@@
 library(broom.mixed)
+
+knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
 ```
@@
 
-```{r group cumu fix by object}
+```{r group cumu fix by object, message=FALSE, warning=FALSE}
 JMW_cumu.windows.grouped <- JMW_cumu %>%
@@
 
-```{r collapse cumu fix over trials}
+```{r collapse cumu fix over trials, message=FALSE, warning=FALSE}
 JMW_cumu.windows.grouped.average <- JMW_cumu.windows.grouped %>%
@@
 
-```{r create summary data for spag plot}
+```{r create summary data for spag plot, message=FALSE, warning=FALSE}
 JMW_cumu.summary <- JMW_cumu.windows.grouped.average %>%

### 2023-08-18 group-a/E1-analysis-replication.Rmd
Small edits so it hopefully knits, moved stuff around

@@
 ```
-<!-- This is where I should say how many people were excluded, right? -->
+<!-- I'm moving the ROI blurb to the main manuscript file since it's the same for Hartshorne analyses
 __Regions of Interest__.
@@
 The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
-Each scene contained an agent region, a target region, and three or four distractor regions.
+Each scene contained an agent region, a target region, and three or four distractor regions.-->
 
+<!-- This is where I should say how many people were excluded, right? -->
 __Minimal Exclusion__.

### 2023-08-18 manuscript.Rmd
Small edits so it hopefully knits, moved stuff around

@@
 
+In addition, in-person replications were conducted for Experiments 1 and 4. Information about those samples is given in the corresponding Method sections.
+
 In order to have adequate statistical power and precision, we aimed for
 2.5x the sample size of the original experiment, following the heuristic
-of Simonsohn [@simonsohn2015]. In study 5, the original sample size was so
+of Simonsohn [@simonsohn2015]. In Experiment 5, the original sample size was so
 small that we opted to collect 5x the number of participants to increase
@@
 
+<!--AJ: Here's an organizational thing I'm trying-- Mention here that there are two experiments (Prolific and in Josh H's lab) and divide subsequent sections where appropriate. Good idea?-->
+
+We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the original and the replication used WebGazer and identical materials and procedures.
+
 ```{r read_groupA_data}
-
+#AJ: We don't need this, right? Can I delete?
 ```
@@
 <!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->
+<!--AJ: I don't know what the above comment means. -->
 
@@
 ### Participants
-
-60 participants were paid \$2.60 for their participation. Our sample size
+#### Remote sample
+Sixty participants were paid \$2.60 for their participation. Our sample size
 of participants was determined by the total run time of our experiment,
@@
 worked with data collected from 58 participants.
+
+####In-lab sample
+Forty-nine participants were (AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info).
 
@@
 onset of the target noun.
+Regions of interest (ROIs) were defined by creating boxes around each object in the scene.
+The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
+Each scene contained an agent region, a target region, and three or four distractor regions.
 
@@
 
-### Replication
+### Remote sample
 
@@
 ```
-### Comparison to in-lab data
-
--   here we will describe a direct comparison to data collected in the
-    lab
-
-### Calibration
-
+
+#### Calibration
 ```{r E1-analysis-calibration,eval=FALSE, child = 'group-a/E1-analysis-calibration.Rmd'}
-
+```
+
+### In-lab sample
+```{r E1-analysis-JoshH-lab,eval=FALSE, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
+#Includes calibration analysis 
 ```

### 2023-08-18 group-a/E1-analysis-calibration-Hartshorne.Rmd
minor fixes

@@
 <!-- # Setup -->
-```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
+```{r E1-c-JH-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
 library(dplyr)

### 2023-08-18 group-a/E1-analysis-calibration.Rmd
minor fixes

@@
 
-knitr::opts_chunk$set(include = FALSE, echo = FALSE)
+knitr::opts_chunk$set(include = FALSE, echo = FALSE, warning = FALSE)
 #knitr::opts_knit$set(root.dir =)
@@
 
+#### Calibration
 Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.

### 2023-08-18 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
minor fixes

@@
 <!-- # Setup -->
-```{r E1-setup, include = FALSE, echo = FALSE}
+```{r E1-JH-setup, include = FALSE, echo = FALSE}
 library(dplyr)
@@
 
-```{r import-data}
+```{r import-data-JH}
 jh.data.files <- list.files('data/data-in-lab-hartshorne', full.names = TRUE, pattern=".json")
@@
 
-```{r value-types}
+```{r value-types-JH}
 jh.all.data <- jh.all.data %>%
@@
 
-```{r Get subj IDs}
+```{r Get subj IDs-JH}
 jh.subjects <- unique(jh.all.data$subject_id)
@@
 
-```{r Get data}
+```{r Get data-JH}
 jh.task.data <- jh.all.data %>%
@@
 
-```{r Merge stim info, message=FALSE, warning=FALSE, include=FALSE}
+```{r Merge stim info-JH, message=FALSE, warning=FALSE, include=FALSE}
 #AJ note: I'm assuming it's the exact same stimuli, so using the same info files
@@
 <!--Figure out word durations by condition (AK Table 2)-->
-```{r Word durations, message=FALSE, warning=FALSE, include=FALSE}
+```{r Word durations-JH, message=FALSE, warning=FALSE, include=FALSE}
 #First, grab the columns that match stimulus to condition name
@@
 
-```{r Gaze in ROI}
+```{r Gaze in ROI-JH}
 in.box <- function(x, y, left, right, top, bottom, padding){
@@
 
-```{r Yes/No in ROI}
+```{r Yes/No in ROI-JH}
 jh.critical.trials <- jh.critical.trials %>%
@@
 <!-- Set which mode here: -->
-```{r Exclusion mode}
+```{r Exclusion mode-JH}
 #AJ note: we're just gonna do minimal
@@
 
-```{r prop-in-ROI, message=FALSE, warning=FALSE, include=FALSE}
+```{r prop-in-ROI-JH, message=FALSE, warning=FALSE, include=FALSE}
 jh.prop.in.roi.by.subject <- jh.critical.trials %>%
@@
 
-```{r roi histogram, eval=F}
+```{r roi histogram-JH, eval=F}
 #printed?
@@
 
-```{r exclude by prop in roi}
+```{r exclude by prop in roi-JH}
 prop.samples.threshold.min <- 0
@@
 
-```{r get validation data}
+```{r get validation data-JH}
 jh.validation.accuracy.data <- jh.all.data %>%
@@
 
-```{r summarize calibration data, eval=F}
+```{r summarize calibration data-JH, eval=F}
 #printed?
@@
 
-```{r save validation percent in roi during validation}
+```{r save validation percent in roi during validation-JH}
 jh.validation.percent <- jh.validation.accuracy.data %>%
@@
 
-```{r plot subjects by validation, eval=F}
+```{r plot subjects by validation-JH, eval=F}
 #printed?
@@
 
-```{r filter by validation}
+```{r filter by validation-JH}
 validation.threshold.min <- 10
@@
 
-```{r summarize exclusions}
+```{r summarize exclusions-JH}
 jh.bad.subjects.min <- unique(c(jh.bad.subjects.prop.samples.min, jh.bad.subjects.validation.min))
@@
 ```
-<!-- This should maybe go at the beginning of analysis section so that I just say it once? -->
-__Regions of Interest__.
-ROIs were defined by creating boxes around each object in the scene.
-The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
-Each scene contained an agent region, a target region, and three or four distractor regions.
 
-__Minimal Exclusion__.
+#### Minimal Exclusion
 As in the remote sample, we checked whether there were participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs and there were none.
@@
 
-```{r set up 50 ms bins, message=FALSE, warning=FALSE}
+```{r set up 50 ms bins-JH, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.data.min <- jh.critical.trials.filtered.min %>%
@@
 
-```{r slowly build cumu fix data, message=FALSE, warning=FALSE}
+```{r slowly build cumu fix data-JH, message=FALSE, warning=FALSE}
 cumulative.fixation.calculation <- function(df){
@@
 
-setwd("/Users/ajames2/Documents/GitHub/219-2021-eyetracking-analysis/group-a/")
-
 if(file.exists("data/data-in-lab-hartshorne/generated/jh.cumulative_fixation_data_min.csv")){
-  jh.cumulative.fixation.windows.data.min <- read_csv("data/generated/jh.cumulative_fixation_data_min.csv")
+  jh.cumulative.fixation.windows.data.min <- read_csv("data/data-in-lab-hartshorne/generated/jh.cumulative_fixation_data_min.csv")
 } else {
@@
 
-  write_csv(jh.cumulative.fixation.windows.data.min, file="data/generated/jh.cumulative_fixation_data_min.csv")
+  write_csv(jh.cumulative.fixation.windows.data.min, file="data/data-in-lab-hartshorne/generated/jh.cumulative_fixation_data_min.csv")
 }
@@
 
-```{r group cumu fix by object, message=FALSE, warning=FALSE}
+```{r group cumu fix by object-JH, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.windows.grouped.data.min <- jh.cumulative.fixation.windows.data.min %>%
@@
 
-```{r collapse cumu fix over trials, message=FALSE, warning=FALSE}
+```{r collapse cumu fix over trials-JH, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.windows.grouped.average.data.min <- jh.cumulative.fixation.windows.grouped.data.min %>%
@@
 
-```{r create summary data for spag plot, message=FALSE, warning=FALSE}
+```{r create summary data for spag plot-JH, message=FALSE, warning=FALSE}
 jh.cumulative.fixation.data.summary.min <- jh.cumulative.fixation.windows.grouped.average.data.min %>%
@@
 
-__Cumulative Fixation Probabilities__.
+#### Cumulative Fixation Probabilities
 For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:jh.E1-spaghetti-fig).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:jh-E1-spaghetti-fig).
 
-```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+```{r jh-E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
 The vertical line marks the mean noun onset time across trials and conditions."}
@@
 
-```{r set up noun onset times}
+```{r set up noun onset times-JH}
 jh.noun.onset.times.min <- jh.critical.trials.filtered.min %>%
@@
 
-```{r find prenoun window data}
+```{r find prenoun window data-JH}
 jh.pre.noun.first.looks.data.min <- jh.trial.level.cumulative.fixation.data.min %>%
@@
 
-```{r save prenoun window data}
+```{r save prenoun window data-JH}
 jh.pre.noun.first.looks.data.min$verb_type <- as.factor(jh.pre.noun.first.looks.data.min$verb_type)
@@
 
-```{r run model 1, message=FALSE, warning=FALSE}
+```{r run model 1-JH, message=FALSE, warning=FALSE}
 jh.E1_model1.min <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.noun.first.looks.data.min)
@@
 ```
-__Pre-noun fixations.__ In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+#### Pre-noun fixations 
+<!--AJ: Edit text -->
+In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
@@
 
-```{r find verb offset data}
+```{r find verb offset data-JH}
 jh.verb.offset.times.min <- jh.critical.trials.filtered.min %>%
@@
 
-```{r save verb offset data}
+```{r save verb offset data-JH}
 jh.pre.verb.offset.first.looks.data.min <- jh.trial.level.cumulative.fixation.data.verb.offset.min %>%
@@
 
-```{r run model 2, message=FALSE, warning=FALSE}
+```{r run model 2-JH, message=FALSE, warning=FALSE}
 #model <- lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=jh.pre.verb.offset.first.looks.data.min)
@@
 ```
-__Pre-verb-offset fixations.__ Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+#### Pre-verb-offset fixations
+Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
 When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
@@
 
-```{r E1-latency-table-min, echo=FALSE, eval=FALSE}
+```{r E1-latency-table-min-JH, echo=FALSE, eval=FALSE}
 #summarize data for table
@@
 
-```{r run model 3, message=FALSE, warning=FALSE}
+```{r run model 3-JH, message=FALSE, warning=FALSE}
 jh.E1_model3.min <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=jh.first.fixation.after.verb.onset.analysis.data.min)
@@
 ```
-__First target fixations after verb.__ Finally, we address whether participants look to the target faster in the restrictive vs.
+#### First target fixations after verb
+Finally, we address whether participants look to the target faster in the restrictive vs.
 the non-restrictive condition, starting after the onset of the verb.
@@
 
-```{r rename stuff}
+```{r rename stuff-JH}
 jh.pre.noun.first.looks.data <- jh.pre.noun.first.looks.data.min
@@
 
-```{r Model 1 subject summary}
+```{r Model 1 subject summary-JH}
 jh.pre.noun.subj.summary <- jh.pre.noun.first.looks.data %>%
@@
 
-```{r Model 1 effect size by calibration}
+```{r Model 1 effect size by calibration-JH}
 #merge with validation percent
@@
 
-```{r Model 2 subject summary}
+```{r Model 2 subject summary-JH}
 jh.pre.verb.subj.summary <- jh.pre.verb.offset.first.looks.data %>%
@@
 
-```{r Model 2 effect size by calibration}
+```{r Model 2 effect size by calibration-JH}
 #merge with validation percent
@@
 
-```{r Model 3 effect size by calibration}
+```{r Model 3 effect size by calibration-JH}
 #summary(validation.percent)
@@
 We tested whether a participant's calibration quality was correlated with their effect size.
-Across the three condition effects of interest, calibration quality [was?
-was not?] significantly correlated (Effect 1 (pre-noun-onset): Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`, Effect 2 (pre-verb-offset): Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`, Effect 3 (first fixation): Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
+Across the three condition effects of interest, calibration quality was not significantly correlated (Effect 1 (pre-noun-onset): Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`, Effect 2 (pre-verb-offset): Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`, Effect 3 (first fixation): Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
 However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.

### 2023-08-18 group-a/E1-analysis-replication.Rmd
minor fixes

@@
 <!-- This is where I should say how many people were excluded, right? -->
-__Minimal Exclusion__.
+#### Minimal Exclusion 
 The first set of analyses used minimal exclusion criteria.
@@
 
-```{r slowly build cumu fix data}
+```{r slowly build cumu fix data, message=FALSE}
 cumulative.fixation.calculation <- function(df){
@@
 
-setwd("/Users/ajames2/Documents/GitHub/219-2021-eyetracking-analysis/group-a")
-
 if(file.exists("data/generated/cumulative_fixation_data_min.csv")){
@@
 
-  write_csv(cumulative.fixation.windows.data.min, file="data/generated/cumulative_fixation_data_min.csv")
+  write_csv(cumulative.fixation.windows.data.min, file="~/group-a/data/generated/cumulative_fixation_data_min.csv")
 }
@@
 
-__Cumulative Fixation Probabilities__.
+#### Cumulative Fixation Probabilities
 For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
@@
 ```
-__Pre-noun fixations.__ In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+#### Pre-noun fixations
+In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
@@
 ```
-__Pre-verb-offset fixations.__ Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+#### Pre-verb-offset fixations
+Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
 When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
@@
 ```
-__Aggressive Exclusion__.
+#### Aggressive Exclusion
 The second set of analyses used more aggressive exclusion criteria.

### 2023-08-18 manuscript.Rmd
minor fixes

@@
 
-####In-lab sample
+#### In-lab sample
 Forty-nine participants were (AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info).
@@
 
-```{r E1-analysis-replication,eval=FALSE, child = 'group-a/E1-analysis-replication.Rmd'}
-
-```
-
-#### Calibration
-```{r E1-analysis-calibration,eval=FALSE, child = 'group-a/E1-analysis-calibration.Rmd'}
+```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}
+
+```
+
+```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
 ```
@@
 ### In-lab sample
-```{r E1-analysis-JoshH-lab,eval=FALSE, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
+```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
 #Includes calibration analysis 

### 2023-08-18 manuscript.tex
Updated manuscript files
minor fixes

@@
 
+In addition, in-person replications were conducted for Experiments 1 and 4. Information about those samples is given in the corresponding Method sections.
+
 In order to have adequate statistical power and precision, we aimed for
 2.5x the sample size of the original experiment, following the heuristic
-of Simonsohn (Simonsohn, 2015). In study 5, the original sample size was so
+of Simonsohn (Simonsohn, 2015). In Experiment 5, the original sample size was so
 small that we opted to collect 5x the number of participants to increase
@@
 
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.3; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.2.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.3; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.4; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 
+We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the original and the replication used WebGazer and identical materials and procedures.
+
 \hypertarget{methods}{%
@@
 
-60 participants were paid \$2.60 for their participation. Our sample size
+\hypertarget{remote-sample}{%
+\paragraph{Remote sample}\label{remote-sample}}
+
+Sixty participants were paid \$2.60 for their participation. Our sample size
 of participants was determined by the total run time of our experiment,
@@
 worked with data collected from 58 participants.
+
+\hypertarget{in-lab-sample}{%
+\paragraph{In-lab sample}\label{in-lab-sample}}
+
+Forty-nine participants were (AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info).
 
@@
 
-\hypertarget{replication}{%
-\subsubsection{Replication}\label{replication}}
-
-\hypertarget{comparison-to-in-lab-data}{%
-\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}}
-
-\begin{itemize}
-\tightlist
-\item
-  here we will describe a direct comparison to data collected in the
-  lab
-\end{itemize}
+\hypertarget{remote-sample-1}{%
+\subsubsection{Remote sample}\label{remote-sample-1}}
+
+\hypertarget{minimal-exclusion}{%
+\paragraph{Minimal Exclusion}\label{minimal-exclusion}}
+
+The first set of analyses used minimal exclusion criteria.
+First, we eliminated participants with 0 percent of fixations in any ROIs.
+This resulted in the elimination of 1 participants.
+Second, we excluded participants with validation accuracy under 10 percent, resulting in an additional 5 excluded participants.
+The following analyses included 52 participants.
+
+*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.
+
+\hypertarget{cumulative-fixation-probabilities}{%
+\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities}}
+
+For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
+This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1-spaghetti-fig-1.pdf}
+\caption{\label{fig:E1-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions.}
+\end{figure}
+
+\hypertarget{pre-noun-fixations}{%
+\paragraph{Pre-noun fixations}\label{pre-noun-fixations}}
+
+In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
+We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
+There were no significant effects, although the critical interaction was in the right direction {[}bar graph?{]} (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.15).
+
+\hypertarget{pre-verb-offset-fixations}{%
+\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}}
+
+Altmann \& Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
+
+\hypertarget{first-target-fixations-after-verb}{%
+\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}}
+
+Finally, we address whether participants look to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
+{[}TO-DO: On average, participants looked to the target X ms after (AK's Table 1)\ldots, I'll also want to say the lengths of the verbs.
+AK's Table 2{]} We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
+
+\hypertarget{aggressive-exclusion}{%
+\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}}
+
+The second set of analyses used more aggressive exclusion criteria.
+First, we eliminated participants with 20 percent of fixations in any ROIs.
+This resulted in the elimination of 15 participants.
+Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 35 participants.
+The following analyses included 22 participants.
+
+We tested the same three models under these more aggressive exclusion criteria.
+The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction was not statistically significant (Pre-noun-onset window: \emph{b} = 0.07, \emph{SE} = 0.06, \emph{p}=0.23; Pre-verb-offset window: \emph{b} = 0.05, \emph{SE} = 0.05, \emph{p}=0.28).
+However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (\emph{b} = -193.35, \emph{SE} = 96.33, \emph{p}=0.05).
 
 \hypertarget{calibration}{%
-\subsubsection{Calibration}\label{calibration}}
+\paragraph{Calibration}\label{calibration}}
+
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
+Calibration quality varied widely, ranging from 3.16\% to 98.87\%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
+Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.04, \emph{p} = 0.78.
+However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
+
+\hypertarget{in-lab-sample-1}{%
+\subsubsection{In-lab sample}\label{in-lab-sample-1}}
+
+\hypertarget{minimal-exclusion-1}{%
+\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}}
+
+As in the remote sample, we checked whether there were participants with 0 percent of fixations in any ROIs and there were none.
+We then excluded participants with validation accuracy under 10 percent, resulting in 2 excluded participants.
+The following analyses included 47 participants.
+
+\hypertarget{cumulative-fixation-probabilities-1}{%
+\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}}
+
+For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
+This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:jh-E1-spaghetti-fig}.
+
+\hypertarget{pre-noun-fixations-1}{%
+\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}}
+
+In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
+We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
+There were no significant effects, although the critical interaction was in the right direction {[}bar graph?{]} (\emph{b} = -0.05, \emph{SE} = 0.05, \emph{p}=0.25).
+
+\hypertarget{pre-verb-offset-fixations-1}{%
+\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}}
+
+Altmann \& Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (\emph{b} = -0.06, \emph{SE} = 0.04, \emph{p}=0.17).
+
+\hypertarget{first-target-fixations-after-verb-1}{%
+\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}}
+
+Finally, we address whether participants look to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
+{[}TO-DO: On average, participants looked to the target X ms after (AK's Table 1)\ldots, I'll also want to say the lengths of the verbs.
+AK's Table 2{]} We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = 21.70, \emph{SE} = 115.32, \emph{p}=0.85).
+
+\hypertarget{calibration-1}{%
+\paragraph{Calibration}\label{calibration-1}}
+
+As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from 5.13\% to 97.89\%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+Across the three condition effects of interest, calibration quality was not significantly correlated (Effect 1 (pre-noun-onset): Pearson's \emph{r} = -0.24, \emph{p} = 0.11, Effect 2 (pre-verb-offset): Pearson's \emph{r} = -0.19, \emph{p} = 0.20, Effect 3 (first fixation): Pearson's \emph{r} = -0.12, \emph{p} = 0.41.
+However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = -0.16, \emph{p} = 0.29).
 
@@
 
-\hypertarget{replication-1}{%
-\subsubsection{Replication}\label{replication-1}}
+\hypertarget{replication}{%
+\subsubsection{Replication}\label{replication}}
 
@@
 
-\hypertarget{calibration-1}{%
-\subsubsection{Calibration}\label{calibration-1}}
+\hypertarget{calibration-2}{%
+\subsubsection{Calibration}\label{calibration-2}}
 
@@
 
-\hypertarget{replication-2}{%
-\subsubsection{Replication}\label{replication-2}}
+\hypertarget{replication-1}{%
+\subsubsection{Replication}\label{replication-1}}
 
@@
 The opposite graded pattern can be observed for mouse movements over the target animal.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-1.pdf}
-\caption{\label{fig:E4-mouse-moves-fig}Proportion of first mouse movements by location and verb bias.}
-\end{figure}
 
@@
 The pattern was reversed for looks to the target instrument.
-
-\begin{verbatim}
-## Warning: Using `size` aesthetic for lines was deprecated in ggplot2 3.4.0.
-## i Please use `linewidth` instead.
-## This warning is displayed once every 8 hours.
-## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-## generated.
-\end{verbatim}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-1.pdf}
-\caption{\label{fig:E4-gaze-timecourse-fig}Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
-\end{figure}
 
@@
 
-\hypertarget{comparison-to-in-lab-data-1}{%
-\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data-1}}
+\hypertarget{comparison-to-in-lab-data}{%
+\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}}
 
@@
 The quantitative patterns of clicks were similar to those observed in the original dataset, though for Instrument-biased verbs, clicks were closer to evenly split between the animal and the instrument relative to the in-lab study where they were very clearly biased toward the instrument.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-web-and-orig-1.pdf}
-\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.}
-\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E4-proportion-fix-by-window-both-1.pdf}
-\caption{\label{fig:E4-proportion-fix-by-window-both}Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
-Error bars reflect bootstrapped 95\% CIs over subject means}
-\end{figure}
-
-\hypertarget{calibration-3}{%
-\subsubsection{Calibration}\label{calibration-3}}
+\hypertarget{calibration-4}{%
+\subsubsection{Calibration}\label{calibration-4}}
 
@@
 
-\hypertarget{calibration-4}{%
-\subsubsection{Calibration}\label{calibration-4}}
+\hypertarget{calibration-5}{%
+\subsubsection{Calibration}\label{calibration-5}}
 
@@
 \ref{fig:E5cal}.
-
-\begin{figure}
-\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/E5cal-1} \caption{Histogram of calibration success in Exp.
-5.
-Where participants required more than one calibration (N=8), only the final calibration was considered.}\label{fig:E5cal}
-\end{figure}
 

### 2023-08-24 group-a/round.comm.R
minor updates

@@ -1,0 +1,12 @@
+#Round like a normal person (i.e. "commercial rounding" i.e. rounding half away from zero) rather than the IEEE standard that is the base R default (see https://en.wikipedia.org/wiki/Rounding for info). 
+
+#Via https://statisticsglobe.com/r-round-ceiling-floor-trunc-signif-function-example, which was based on a comment here: http://andrewlandgraf.com/2012/06/15/rounding-in-r/  
+
+round.comm <- function(x, digits = 0) {  # Function to always round 0.5 away from 0
+  posneg <- sign(x)
+  z <- abs(x) * 10^digits
+  z <- z + 0.5
+  z <- trunc(z)
+  z <- z / 10^digits
+  z * posneg
+}

### 2023-08-24 group-d/E4-analysis-replication-in-lab.Rmd
updated intro

@@
 ```{r , include=FALSE}
+# THIS IS A VERY MESSY RMD IN WHICH I TRIED TO ANALYSE THE IN-LAB REPLICATION DATA: DO NOT USE, I WILL EVENTUALLY REMOVE IT - RR
+# subject identifiers did not get saved (and some other important stuff too) so the data cannot be analyzed in a reasonable way
 library(papaja)
@@
 library(purrr)
-#library(dplyr)
+library(dplyr)
 library(readr)
@@
 library(broom.mixed)
+library(lubridate)
 ```
@@
 
-```{r E4-in-lab-load-data}
+```{r E4-in-lab-load-data-first-batch}
+
+#  without dates for user ids
+add_order = function(trial_index, lag_trial_index, lag_trial_order, verbose = F){
+
+  if( length(lag_trial_index)==0 | length(lag_trial_order)==0 ){
+    trial_order = 0
+  }else if(trial_index == lag_trial_index){
+    trial_order = lag_trial_order
+  }else if(trial_index < lag_trial_index){
+    trial_order = 0
+  }else if(trial_index > lag_trial_index){
+    trial_order = lag_trial_order+1
+  }
+
+  if (verbose){
+    cat("\n trial index: ",trial_index,"\n ")
+    cat("lag trial index: ",lag_trial_index,"\n ")
+    cat("lag trial order: ",lag_trial_order,"\n ")
+    cat("new trial order: ", trial_order)
+  }
+   return(trial_order)
+}
+#add_order(3,1,1,T)
+
+batch1<-readRDS("data/in-lab-merced/verb_bias_ET_data_10_13_2022.rds") %>% 
+  tibble::rownames_to_column("row_order") %>% 
+  mutate(row_order = as.numeric(row_order)) %>% 
+  separate(internal_node_id, into=c('node0','node1', 'node2', 'node3'), sep = "-",remove = F) %>%
+  mutate(across(starts_with("node"),as.numeric)) %>% 
+  arrange(user_id, row_order) #%>% 
+  #group_by(user_id, node0,node1,node2,node3) %>% 
+ # group_by(user_id) %>%
+ # mutate(trial_order  = 0)
+
+subj_orders = vector()
+subjnum = 1
+for (i in 1:length(batch1$row_order)){
+  if(str_detect(batch1$stimulus[i], "hypothesis")){
+    subjnum = subjnum+1
+  }
+  subj_orders[i] = subjnum
+}
+#add_order(3,1,1,T)
+
+batch1z = batch1 
+batch1z$subj_order = subj_orders
+
+batch1z = batch1 %>% 
+     arrange(user_id, trial_index, row_order) %>% 
+    # mutate(prev_trial_end = time_elapsed - rt - 2) %>% 
+     group_by(user_id, trial_index) %>% 
+     mutate(daily_subjnum = 1:n(),
+             subj_order = str_c(daily_subjnum,"__", user_id)) #%>%
+
+dayxz = batch1z %>% filter(user_id == 'c402ba0c-7a9d-4258-addd-149223724707')  %>% 
+  select(-starts_with('webgazer')) %>% 
+  ungroup() %>% 
+  mutate(time_lag = as.numeric(time_elapsed) - as.numeric(lag(time_elapsed)))
+
+```
+# BATCH1Z
+```{r}
+batch1z.task.data = batch1z %>%
+  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
+  dplyr::select(subj_order, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)
+
+# Add a column that uniquely identifies the combination of images and audio shown on the screen
+batch1z.trialID.data <- batch1z.task.data %>%
+  group_by(audio, images) %>%
+  slice(1) %>%
+  select(audio, images) %>%
+  ungroup() %>%
+  mutate(trialID = 1:n())
+
+batch1z.task.data <- batch1z.task.data %>%
+  left_join(batch1z.trialID.data)
+
+batch1z.eyetracking.data <- batch1z.task.data %>%
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
+  unnest_wider(webgazer_data) %>% 
+  unnest_longer(col = c(x, y, t))
+
+batch1z.mousetracking.data <- batch1z.task.data %>%
+  unnest(mouse_events)
+```
+```{r E4-categorizing-first-mouse-moves}
+#First, create a data set with each trial, adding column for which object the mouse moves over first.
+# WTF IS HAPPENING with TRIAL ID?? 
+batch1z.first.move <- batch1z.mousetracking.data %>%
+  select(subj_order, trialID, object, type, compatibility, target_instrument, target_animal, images, audio) %>%
+  group_by(subj_order, trialID) %>%
+  filter(type=="enter") %>%
+  slice(1) %>%
+  rowwise() %>%
+  mutate(which_loc = which(images == object)-1) %>%
+  ungroup() %>%
+  mutate(instrument_loc = str_sub(target_instrument, start=-1, end=-1)) %>%
+  mutate(animal_loc = str_sub(target_animal, start=-1, end=-1)) %>%
+  mutate(first.move.type = case_when(
+    which_loc == instrument_loc ~ 'instrument',
+    which_loc == animal_loc ~ 'animal',
+    TRUE ~ 'other')) %>%
+  mutate(is.mouse.instrument = if_else(first.move.type == 'instrument', 1, 0)) %>%
+  mutate(compatibility = factor(compatibility))
+```
+
+```{r E4-summarizing-first-mouse-moves-for-plotting}
+# Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.
+batch1z.first.move.subject.summary <- batch1z.first.move %>%
+  group_by(subj_order, compatibility) %>%
+  summarize(prop.animal = mean(first.move.type == 'animal'),
+            prop.instrument = mean(first.move.type == 'instrument'),
+            prop.other = mean(first.move.type == 'other'),
+            n_trials= n()) %>%
+  filter(n_trials > 9) %>% ## CAHNGE WHEN THERE'S A BETTER WAY TO CROSSREF
+  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
+
+# Summarize the condition-level data for a barplot.
+batch1z.first.move.summary <- batch1z.first.move.subject.summary %>%
+  group_by(compatibility, target_type) %>%
+  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
+  mutate(bias = factor(compatibility, levels = c("instrument", "equibiased", "modifier") ))
+```
+
+```{r E4-mouse-moves-fig, fig.cap = "Proportion of first mouse movements by location and verb bias."}
+
+ggplot(batch1z.first.move.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
+  geom_col(position=position_dodge(width=0.9), color = "black")+
+  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
+  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
+  coord_cartesian(ylim = c(0,1))+
+  theme_classic()+
+  labs(y = "Proportion of first mouse movements", x = NULL)
+```
+
+```{r}
+
+for (r in 1:length(batch1$trial_index)){
+  #print(r)
+  #print(add_order(batch1$trial_index[r], batch1$trial_index[r-1], batch1$trial_order[r-1],verbose=T))
+  batch1$trial_order[r] = add_order(batch1$trial_index[r], batch1$trial_index[r-1], batch1$trial_order[r-1],F)
+
+}
+
+# now connecting trials to each other based on elapsed time and rt
+
+#View(batch1 %>% select(trial_index, internal_node_id,user_id, trial_order))
+batch1a = batch1 %>%   
+    arrange(user_id, trial_order, time_elapsed) %>% 
+    mutate(prev_trial_end = time_elapsed - rt - 2) %>% 
+    group_by(user_id, trial_index) %>% 
+    mutate(daily_subjnum = 1:n(),
+            unique_id = str_c(daily_subjnum,"__", user_id)) #%>% 
+    # mutate(prev_trial_id = case_when(
+    #   prev_trial_end == time_elapsed
+    # ))
+    # ungroup() %>% 
+    # arrange(unique_id, trial_index)
+
+link_trials  = function(s, to, df, tol=1, verbose=F){
+
+  prev = df %>% filter(user_id == s & trial_order == to-1)
+  curr = df %>% filter(user_id == s & trial_order == to)
+  linked = vector("character", length(curr$prev_trial_end))
+
+  for (q in 1:length(curr$prev_trial_end)){
+    if(verbose){cat("q", q, ": ", curr$prev_trial_end[q],"\n")}
+    for (p in 1:length(prev$time_elapsed)){
+      if(verbose){cat("p", p, ": ", prev$time_elapsed[p],"\n")}
+      if (!is.na(prev$time_elapsed[p]) & !is.na(curr$prev_trial_end[q])){
+        if (curr$prev_trial_end[q]==prev$time_elapsed[p]| 
+            (curr$prev_trial_end[q]<=prev$time_elapsed[p]+tol &
+            curr$prev_trial_end[q]>=prev$time_elapsed[p]-tol)){
+          if(verbose){cat("p",p, ": ", prev$unique_id[p],"\n")}
+          linked[q] = prev$unique_id[p]
+        }
+      }
+    }
+  }
+  return(linked)
+}
+
+#link_trials('6a935167-a0f5-4399-b6dd-8928fe8bae35',2,batch1a, tol=1)
+link_trials('0f3402df-0da9-4a51-ac92-6a8c8f8e8c48',12,batch1a, tol=1)
+
+linked_ids = vector("character")
+for(user in unique(batch1a$user_id)){
+  cat("\n\nUSER: ",user,"\n\n")
+  for (trial in unique(batch1a[batch1a$user_id == user,]$trial_order)){
+    cat("trial: ", trial,"\n")
+    if(trial == 0){
+      linked_ids = c(linked_ids, batch1a[batch1a$user_id == user & batch1a$trial_order == 0,]$unique_id)
+    }else{
+      linked_ids = c(linked_ids, link_trials(s=user, to = trial, df=batch1a, tol=1))
+    }
+
+  }
+}
+
+batch1b = batch1a
+batch1b$linked_unique_ids  = linked_ids
+
+dayx = batch1b %>% filter(user_id == 'c402ba0c-7a9d-4258-addd-149223724707')  %>% select(-starts_with('webgazer'))
+```
+
+```{r}
+
+#OKAY NOW NEED TO FILL IN LINKED IDS FOR THE CRITICAL TRIALS USING RTS FROM MOUSE CLICKS???
+
+batch1.mouse = batch1b %>% 
+  unnest(mouse_events,keep_empty = T) %>% 
+  # mutate(prev_elapsed = time_elapsed - rt, 
+  #          rt_eye = audio_start_time + t) %>% 
+  group_by(user_id,trial_index,time_elapsed) %>% 
+  mutate(prev_elapsed = time_elapsed-max(t))
+
+dayx.mouse = batch1.mouse %>% filter(user_id == 'c402ba0c-7a9d-4258-addd-149223724707') %>% 
+  select(-starts_with('webgazer')) %>% 
+  select(rt, trial_index,trial_type, internal_node_id, time_elapsed, audio_start_time, type, object, t, prev_elapsed)
+# 
+# write_csv(dayx, "data/in-lab-merced/test.csv")
+
+dayx.summ = dayx %>% group_by(internal_node_id) %>% summarize(n())
+
+batch1.summary = batch1 %>% 
+  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
+  group_by(user_id, daily_subjnum, unique_id) %>% 
+  summarize(n=n()) %>% 
+  group_by(user_id) %>% 
+  mutate(daily_total = max(daily_subjnum)) %>% 
+  arrange( user_id, daily_subjnum)
+
+```
+
+```{r}
+batch1.gaze = batch1b %>% 
+  tidyr::unpack(webgazer_targets) %>%
+  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
+  unnest_wider(webgazer_data) %>% 
+  unnest_longer(col = c(x, y, t))
+
+dayx.gaze = batch1.gaze %>% filter(user_id == 'c402ba0c-7a9d-4258-addd-149223724707') %>% 
+  ungroup() %>% 
+  mutate(trial_lag = as.numeric(time_elapsed) - as.numeric(lag(time_elapsed))
+        # ,last_gaze = t[[1]][length(t[[1]])]
+         )
+
+for (i in 1:length(dayx.gaze$t)){
+  g = dayx.gaze$t[i][[1]][length(dayx.gaze$t[i][[1]])]
+  if(is.null(g)){
+    last_gaze[i]<-NA
+  }else{
+    last_gaze[i]<-g
+  }
+}
+
+dayx.gaze = cbind(dayx.gaze,last_gaze) 
+dayx.gaze = dayx.gaze %>%  
+  mutate(extra = trial_lag - last_gaze) %>% 
+  select(rt, trial_index, trial_type,time_elapsed,trial_lag,audio_start_time,t,last_gaze, extra)
+```
+
+#batch2
+
+```{r E4-in-lab-load-data-second-batch}
+# second batch
+
 user.data.files <- list.files('data/in-lab-merced', pattern = "pushkin_users_*",full.names = TRUE)
 
-all.user.data <- map_dfr(user.data.files, readRDS)
+all.user.data <- map_dfr(user.data.files, readRDS) %>% unique()
 
@@
   group_by(user_id, trial_index) %>% 
-  mutate(subjnum = 1:n(),
-         unique_id = str_c(subjnum,"__", user_id)) %>% 
+  mutate(daily_subjnum = 1:n(),
+         unique_id = str_c(daily_subjnum,"__", user_id)) %>% 
   ungroup() %>% 
-  arrange(unique_id, trial_index)
+  arrange(unique_id, trial_index) %>% 
+  left_join(all.user.data, by = "user_id") %>% 
+ # separate(created_at, into = c("date", "time"), sep = " ") %>% 
+  mutate(date_time = parse_date_time(created_at, "ymd HMS")) %>% 
+  mutate( date = date(date_time))
 
@@
 *TO DO:* cross ref with angela's list of participant times/dates
+-still trying to figure out how the daes/times line up...
+
+```{r}
+
+participant_log = read_csv('data/in-lab-merced/participant_log.csv') %>% 
+  separate(time, into = c("start_time", "end_time"), sep = "-") %>% 
+  mutate(end_date_time = paste(date, end_time, sep = " "),
+        PSTtime = strptime(end_date_time, format = "%m/%d/%y %H:%M", tz = "America/Los_Angeles"),
+       # UTCtime = strptime(start_date_time, format = "%m/%d/%y %H:%M", tz = "America/New_York")
+       other_tz_time = with_tz(PSTtime, "US/Alaska")
+        ) %>% 
+         #PSTtime = strptime(start_time, format = "%H:%M", tz = ""),
+        # UTCtime = strptime(start_time, format = "%H:%M", tz = "GMT")) %>% 
+  filter(action == "credit granted") %>% 
+  group_by(date) %>% 
+  arrange(PSTtime) %>% 
+  mutate(order = 1,
+         order = cumsum(order))
+
+write_csv(participant_log, "data/in-lab-merced/participant_log2.csv")
+
+all.user.data.summary = all.data %>% 
+  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
+  group_by(date_time, user_id, daily_subjnum, unique_id) %>% 
+  summarize(n=n()) %>% 
+  arrange(date_time,daily_subjnum)
+
+write_csv(all.user.data.summary, "data/in-lab-merced/pushkin_user_data_summary.csv")
+#hist(all.user.data.summary$n)
+
+#all.user.data.summary %>% ungroup() %>% summarize(n_distinct(date_time), n_distinct(date))
+```
 

### 2023-08-24 manuscript.Rmd
updated intro

@@
 
-Finally, @slim2022moving used the Webgazer.js library via the PCIbex online experiment platform [@zehr2018PCIbex] to replicate a visual world paradigm study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair)  [@dijkgraaf2017predicting].
+Finally, several papers have used the WebGazer.js library (via different interfaces) to replicate visual world paradigm studies.
+@slim2022moving used the PCIbex online experiment platform [@zehr2018PCIbex] to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair)  [@dijkgraaf2017predicting].
 When the verb in the sentence was _constraining_ (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was _neutral_ (e.g., Mary steals a letter), as in previous work.
@@
 The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between _constraining_ and _neutral_ conditions emerged before the onset of the final noun (e.g., letter).
+Similarly, @degen2021seeing reported that effects of scalar implicature processing (comparing looks to the target in a four quadrant display for sentences such as "Click on the girl that has _some_ apples" vs.
+"Click on the girl that has _three_ apples" ) were smaller and delayed relative to those observed in the lab [@sun2020another].
+
+In contrast, using the Gorilla experiment platform [@anwyl2020gorilla], @prystauka2023online observed robust effects of verb semantics and lexical interference in similar time windows to previous in-lab studies [@altmannIncrementalInterpretationVerbs1999;@kukona2014lexical], though a direct comparison was not possible because their studies used different materials than the in-lab experiments they were conceptually replicating.
+Furthermore, using jsPsych, @vos2022comparing closely replicated the magnitude and timecourse of effects in a lab-based visual world paradigm where the ROIs consisted of the left and right halves of the display, suggesting that the concerns about poor temporal resolution can be mitigated.
+Indeed, the eye-tracking plug-in in jsPsych uses a fork of Webgazer.js in which certain modifications have been made to minimize processing time.
+^[See discussion at https://github.com/jspsych/jsPsych/discussions/1892]
+
+In sum, webcam eye-tracking has been used to varying degrees of success across a small set of paradigms that are used in cognitive science research.
+One configuration, jsPsych with a modification of WebGazer.js, appears to have circumvented initial limitations in temporal precision [@krajbich2010visual; @vos2022comparing] but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs).
+In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking, in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
 
@@
 
-In order to validate online eyetracking measures, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+In order to validate the online eyetracking methodology, with the particular configuration known to have the greatest temporal precision, jsPsych and a modification of Webgazer, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-Ideally, we would only attempt to replicate studies where the original measurements have small error bars and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
+Ideally, we would only attempt to replicate studies where the original measurements have small standard errors and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
 
@@
 Second, we include several ``sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
-(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for XXX of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
+(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
 
@@
 <!--AJ: I don't know what the above comment means. -->
-
+<!--RR: I think it's referencing that the scripts in the OSF repository are the ones the students use for their class projects and not the ones that produced the results in the paper which is maybe confusing but I can add some description above about how these data were collected in a classrooom setting.
+-->
 All stimuli, experiment scripts, data, analysis scripts, and a

### 2023-08-24 group-a/E1-analysis-calibration-Hartshorne.Rmd

@@
 ---
-
+<!-- NO LONGER USED! CRAMMED EVERYTHING INTO E1-ANALYSIS-COMPARISON-TO-HARTSHORNE-->
 ```{r}

### 2023-08-24 group-a/E1-analysis-calibration.Rmd

@@
 library(papaja)
-source("~/round.comm.R")
+source('round.comm.R')
 

### 2023-08-24 group-a/E1-analysis-comparison-to-Hartshorne.Rmd

@@
 library(patchwork)
-source("~/round.comm.R")
+source('round.comm.R')
 

### 2023-08-24 group-a/E1-analysis-comparison-to-JMW23.Rmd

@@
 JMW1_info <- read_csv("group-a/JMW23-data/fyptrialinfo.csv")
+
+JMW1_latency <- read.delim("group-a/JMW23-data/FYPAKFixationLatenciesPOSTVERB.txt", header = FALSE, sep = ",") #I'll come back to this
+
 JMW1_data <- read.delim("group-a/JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")
+
 #Add meaningful header row
@@
   geom_vline(xintercept = mean(JMW1_info$Non.relative))
-
-JMW_spag_fig
-
 #The "Object type" part of the key doesn't actually show which color is which

### 2023-08-24 group-a/E1-analysis-replication.Rmd

@@
 library(papaja)
-source("~/round.comm.R")
+source('round.comm.R') #does "commercial" i.e. normal rounding
 
@@
 
-*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.
+<!--Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset;  whether there's a 200-ms scootch.
+Answer: fixations beginning at or before verb onset are not included in cumulative fixation data or first fixation data.
+There is no 200-ms scootch.-->
 
@@
 #### Pre-verb-offset fixations
-Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
 When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
@@
   group_by(subject_id, image_name) %>%
-  filter(t >= verb_onset*1000) %>%
+  filter(t >= verb_onset*1000) %>% #excludes fixations initiating on or before verb
   filter(object_type == "target.object") %>%
   filter(is.fixating == TRUE) %>%
-  filter(t == min(t)) %>%
+  filter(t == min(t)) %>% #earliest fixation
   mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
@@
 the non-restrictive condition, starting after the onset of the verb.
-[TO-DO: On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs.
-AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+[TO-DO: On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition (compared to ) and `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the non-restrictive condition (compared to )].
+Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
+
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
 There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).

### 2023-08-24 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
so minor

@@
 
-```{r E1-latency-table-min-JH, echo=FALSE, eval=FALSE}
+```{r E1-latency-table-min-JH, echo=FALSE}
 #summarize data for table

### 2023-08-24 group-a/E1-analysis-replication.Rmd
so minor

@@
 
-```{r E1-latency-table-min, echo=FALSE, eval=FALSE}
+```{r E1-latency-table-min, echo=FALSE}
 #summarize data for table
@@
 
-apa_table(
-  E1_latency_table_min,
-  caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
-  font_size = "small",
-   col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
-)
+# apa_table(
+#   E1_latency_table_min,
+#   caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
+#   font_size = "small",
+#    col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
+# )
 

### 2023-10-05 group-c/E3-analysis-calibration.Rmd
updated intro, discussion sections, and general discussion

@@
 To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant.
-The calibration score was the average proportion of samples within XXX pixels of the validation points during the final validation phase before the eye tracking is performed.
+The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed.
 

### 2023-10-05 manuscript.Rmd
updated intro, discussion sections, and general discussion

--- 2023-08-18 manuscript.Rmd
@@
 Advances in software for online data collection [@deleeuwJsPsychJavaScriptLibrary2015; @papoutsaki2016webgazer] have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples.
-In particular, Webgazer.js [@papoutsaki2016webgazer] is a webcam-based Javascript plug-in that works in the browser.
+In particular, `Webgazer.js` [@papoutsaki2016webgazer] is a webcam-based Javascript plug-in that works in the browser.
 It can be integrated with any Javascript web interface.
-As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as jsPsych [@deleeuwJsPsychJavaScriptLibrary2015], Gorilla [@anwyl2020gorilla], or lab.js [@henninger2021lab].
+As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
 However, the added convenience comes at the cost of spatial and temporal resolution.
@@
 @semmelmann2018online compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing.
-They used the Webgazer.js library [@papoutsaki2016webgazer] and programmed tasks in HTML/Javascript directly.
+They used the `Webgazer.js` library [@papoutsaki2016webgazer] and programmed tasks in HTML/Javascript directly.
 The first two tasks tested measurement of basic gaze properties.
@@
 
-Similarly, @yang2021webcam used the Webgazer.js library [@papoutsaki2016webgazer] combined with the jsPsych library for conducting behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015], to replicate a well-established link between value-based decision-making and eye gaze [e.g., @shimojoGazeBiasBoth2003, @krajbich2010visual].
+Similarly, @yang2021webcam used the `Webgazer.js` library [@papoutsaki2016webgazer] combined with the `jsPsych` library for conducting behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015], to replicate a well-established link between value-based decision-making and eye gaze [e.g., @shimojoGazeBiasBoth2003, @krajbich2010visual].
 Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one.
@@
 As in previous work, participants were biased to choose the option they had spent more time looking at.
-The authors also implemented a code modification to address temporal delays in WebGazer.
-
-Finally, @slim2022moving used the Webgazer.js library via the PCIbex online experiment platform [@zehr2018PCIbex] to replicate a visual world paradigm study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair)  [@dijkgraaf2017predicting].
+The authors also implemented a code modification to address temporal delays in `WebGazer`.
+
+Several papers have used the `WebGazer.js` library (via different interfaces) to replicate visual world paradigm studies.
+@slim2022moving used the `PCIbex` online experiment platform [@zehr2018PCIbex] to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair)  [@dijkgraaf2017predicting].
 When the verb in the sentence was _constraining_ (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was _neutral_ (e.g., Mary steals a letter), as in previous work.
@@
 The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between _constraining_ and _neutral_ conditions emerged before the onset of the final noun (e.g., letter).
+Similarly, @degen2021seeing reported that effects of scalar implicature processing (comparing looks to the target in a four quadrant display for sentences such as "Click on the girl that has _some_ apples" vs.
+"Click on the girl that has _three_ apples" ) were smaller and delayed relative to those observed in the lab [@sun2020another].
+
+In contrast, using the `Gorilla` experiment platform [@anwyl2020gorilla], @prystauka2023online observed robust effects of verb semantics and lexical interference in similar time windows to previous in-lab studies [@altmannIncrementalInterpretationVerbs1999;@kukona2014lexical], though a direct comparison was not possible because their studies used different materials than the in-lab experiments they were conceptually replicating.
+Furthermore, using `jsPsych`, @vos2022comparing closely replicated the magnitude and timecourse of effects in a lab-based visual world paradigm where the regions of interest (ROIs) consisted of the left and right halves of the display, suggesting that the concerns about poor temporal resolution can be mitigated.
+Indeed, the eye-tracking plug-in in `jsPsych` uses a fork of `Webgazer.js` in which certain modifications have been made to minimize processing time.
+^[See discussion at https://github.com/jspsych/jsPsych/discussions/1892]
+Finally, @van2023validation used `WebGazer.js` in conjunction with `PsychoJS` to conceptually replicate three paradigms, one which is analogous to @yang2021webcam, another testing the novelty preference (tendency for learners to look more at an object that they have not yet studied), and a visual world paradigm study with 4 objects, similar to @prystauka2023online.
+These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset.
+(They did not address whether there were temporal delays.)
+
+In sum, webcam eye-tracking has been used to varying degrees of success across a small set of paradigms that are used in cognitive science research.
+One configuration, `jsPsych` with a modification of `WebGazer.js`, appears to have circumvented initial limitations in temporal precision [@krajbich2010visual; @vos2022comparing] but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs).
+Further, the extent to which noise in the measurement is due to the software and hardware limitations as opposed to the difference between the in-lab and online settings remains unclear.
+In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
 
@@
 
-In order to validate online eyetracking measures, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
-The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-Ideally, we would only attempt to replicate studies where the original measurements have small error bars and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
-
+In order to validate the online eyetracking methodology, with the particular configuration known to have the greatest temporal precision, `jsPsych` and a modification of `Webgazer`, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
+
+## Selection of Studies
+
+Studies with large effect sizes and which are known to replicate are ideal targets for further replication; otherwise, it can be difficult to distinguish a failure of the method from a failure of the original study to replicate.
 In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability.
@@
 First, replicating five very different studies from different research traditions decreases our reliance on any one study.
-Second, we include several ``sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
-(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for XXX of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
-
-## Selection of Studies
+Second, we include several ''sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
+(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using `jsPsych` or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
 
@@
 We chose five high-impact eyetracking studies involving adult subjects.
-(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two
-halves of the screen, visual world paradigm with four quadrants, visual
-world paradigm with "natural" scenes).
+(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes).
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
-Table\ \ref(tab:studies-table) provides an overview of the five studies we selected.
+Table \@ref(tab:studies-table) provides an overview of the five studies we selected.
 
@@
     "Altmann & Kamide, 1999",
-    "Johansson & Johansson, 2013",
+    "Johansson & Johansson, 2014",
     "Manns, Stark, & Squire, 2000",
@@
   ),
-  `Citations (June 2022, Google Scholar)` = c(
-    1840,
-    190,
-    127,
-    448,
-    964
+  `Citations` = c(
+    2007,
+    228,
+    131,
+    472,
+    1073
   ),
@@
   studies_table,
-  caption = "Studies selected for replication attempts",
-  font_size = "small"
+  caption = "Studies selected for replication attempts. Citation counts based on Google Scholar (August 2023).",
+  font_size = "small",
+  digits = 0
 )
@@
 
-In addition, in-person replications were conducted for Experiments 1 and 4. Information about those samples is given in the corresponding Method sections.
+In addition, an in-person replication was conducted for Experiment 1. 
+Information about the sample is given in the corresponding Method sections.
 
@@
 [@deleeuwJsPsychJavaScriptLibrary2015]. Our fork included changes to
-webgazer.js in order to improve data quality for experiments in which
+`webgazer.js` in order to improve data quality for experiments in which
 the precise timing of stimulus onsets is relevant. Specifically, we
@@
 
+## Pre-registration
+
+These data were collected within the context of an undergraduate research methods course.
+Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the first author.
+The OSF repositories associated with these experiments are linked in the methods sections of each individual study.
+Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality).
+All analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis
+
 ## Data pre-processing
@@
 
-<!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->
-<!--AJ: I don't know what the above comment means. -->
-
 All stimuli, experiment scripts, data, analysis scripts, and a
@@
 #### In-lab sample
-Forty-nine participants were (AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info).
+Forty-nine participants were `r colorize("AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info", "red")`.
 
@@
 The task began with a 9-point eye-tracker calibration
-and validation (Figure\ \@ref(fig:E1-calibration-figure)). 
+and validation (Figure\ \@ref(fig:E1-calibration-figure) ). 
 During the experiment, the participants were
@@
 onset of the target noun.
-Regions of interest (ROIs) were defined by creating boxes around each object in the scene.
+ROIs were defined by creating boxes around each object in the scene.
 The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
@@
 
-The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic)
+The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
+
+There were two modifications we made to the methods of the original
+experiment. As we were only replicating the declarative memory component
+of the original experiment, we did not have a "priming group."
+Therefore, we followed only the procedure for the "looking group."
+Additionally, for each section of the study, the stimuli were presented
+on a single screen instead of two screens due to the constraints of the
+online experiment format.
 
@@
 
-Images were selected XXX...
-
-There were two modifications we made to the methods of the original
-experiment. As we are only replicating the declarative memory component
-of the original experiment, we did not have a "priming group."
-Therefore, we followed only the procedure for the "looking group."
-Additionally, for each section of the study, the stimuli was presented
-on a single screen instead of two screens due to the constraints of the
-online experiment format.
+`r colorize('Images were selected XXX...','red')`
 
@@
 ## Discussion
+
+As in @mannsVisualPairedcomparisonTask2000, participants looked more at novel images than previously seen images.
+This effect was consistent for ROIs based on the images and for the coarser ROIs based on two halves of the display.
+A day later, participants were also able to discriminate the images they had seen from foil images they had not seen during the previous session.
+However, there was no evidence that memory performance on day 2 was related to looking time on day 1.
+Calibration quality did not appear to impact this relationship.
 
@@
 
-The stimuli, experimental code, and data and analysis scripts can be
+The stimuli, experimental code, and data and original analysis scripts can be
 found on the Open Science Framework at the following link,
@@
 
+As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier, instrument or equi).
+For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).
+This pattern was stronger for those who achieved higher calibration accuracy and when quadrant-based ROIs were used compared to image-based ROIs.
+
 # Experiment 5
@@
 All stimuli, experiment scripts, data, and analysis scripts are
-available on the Open Science Framework at <https://osf.io/eubsc/>
-(<https://osf.io/eubsc/>). The study pre-registration is available at
-<https://osf.io/tv57s> (<https://osf.io/tv57s>).
+available on the Open Science Framework at [https://osf.io/eubsc/](https://osf.io/eubsc/). 
+The study pre-registration is available at
+[https://osf.io/tv57s](https://osf.io/tv57s).
 
@@
 each set of faces. Participants were asked to look at this fixation
-cross in order to reset their gaze in between trials (???). The order of
+cross in order to reset their gaze in between trials. The order of
 the 19 face pairs was random for each participant.
@@
 the age of 18. 27 participants were recruited on Prolific to participate
-in stimulus norming (for attractiveness). They were paid \$XX for
-completing the experiment. Data from 3 participants was excluded because
-their mode response made up more than 50% of their total responses
-<!-- is this a cutoff from Shimojo?-->, for a total of 24 participants
-in the norming. They each viewed all 172 faces and were asked to rate
+in stimulus norming (for attractiveness). They each viewed all 172 faces and were asked to rate
 them on a scale from 1 (less attractive) to 7 (more attractive) using a
 slider. Faces were presented one at a time and in a random order for
-each participant. Following Shimojo et al., 19 face pairs were made by
-matching two faces that had a difference in mean attractiveness ratings
-that was 0.25 points or lower and that matched in gender, race, and age
+each participant. Data from 3 participants were excluded because
+their mode response made up more than 50% of their total responses, for a total of 24 participants
+in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by
+identifying two faces that 1) had a difference in mean attractiveness ratings
+that was 0.25 points or lower and 2) matched in gender, race, and age
 group (young adult, adult, or older adult).
@@
 supplied their own cameras, so hardware sampling rate varied. However,
-data was collected at 20 Hz.[TODO - CONFIRM]
+data was collected at 20 Hz.`r colorize("[TODO - CONFIRM]", 'red')`
 
@@
 ## Discussion
+
+Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the face that they ultimately choose.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
+The gaze patterns remained consistent for participants with better calibration accuracy.
 
@@
 ## Discussion
- -->
-```
+
 # Combined Analyses?
@@
 
+ -->
+```
+
 # General Discussion
 
- - E1:
-
- - E2: 
-    - replication of key result with 4 quadrants
-    - calib quality doesn't seem to matter 
-    - if attempting to control where people are looking, think about modifying task...
-
- - E3:
-
- - E4:
-
- - E5:
+We conducted 5 attempted replication studies using different experimental paradigms from across the cognitive sciences.
+All were successfully implemented in `jsPsych` using the `webgazer` plugin, but replication success was mixed.
+Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with 5 to 6 ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
+Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [@james2023language].
+A previous conceptual replication of this paradigm using webcam-based eye-tracking [prystauka2023online] was successful but used a 4-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
+It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
+The primary limitation is likely to be the size of the ROIs.
+
+ <!-- bullet points from Ariel
+ Models testing the condition effect: nothing came out in the two WebET studies (remote and JH’s lab); numerically things are in the right direction but there are so few fixations to ROIs generally (so in spaghetti plots, the noodles top out at 50% or 60% cumulative probability of fixations); and latencies are delayed relative to previous studies.
+
+ • Effect sizes (target adv in eat vs.
+move cond) were uncorrelated with calibration accuracy in both samples, but in the remote sample (but not JH lab), calibration was correlated with target adv in eat condition alone
+
+ • Note that the ROIs are only the sizes of the objects in the scene (plus padding), so much smaller than a 5th or 6th of the whole screen (because there are 5 or 6 ROIs per scene; should I figure out how much smaller?)-->
+
+Experiment 2 used the 4 quadrants of the participant's screen as ROIs.
+As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, participants spontaneously looked to blank ROIs which previously contained to-be-remembered pictures.
+These results appeared to be robust to calibration quality.
+An additional manipulation, instructing participants to keep gaze fixed on a central point, was not successful.
+One possibility is that participants are less motivated to follow such instructions when an experimenter is not present in the same room with them.
+It may be possible to improve performance by emphasizing that this is an important aspect of the experiment or by providing additional training/practice in keeping the eyes still on one particular point.
+
+Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask200.
+However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
+Calibration quality did not appear to impact this relationship.
+More work is needed to understand whether delay manipulations can be practically combined with webcam eye-tracking.
+
+Experiment 4 used the 4 quadrants of the participant's screen as ROIs.
+As in @ryskinVerbBiasesAre2017, listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input ("Rub the frog with the mitten").
+Across multiple time windows, participants looked more at potential instruments (mitten), when the verb (rub) was one that was more likely to be followed by a prepositional phrase describing an instrument with which to perform the action , as opposed to describing the recipient of the action (frog).
+Despite the qualitative replication of past findings, the overall rates of looks to various objects were much lower than in an in-lab study using infrared eye-tracking.
+This reduction may be related to measurement quality: effect sizes were greater for participants with higher calibration accuracy.
+Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect.
+Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to `webgazer` that are made within the `jsPsych` plug-in successfully address the issues noted by @dijkgraaf2017predicting and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.
+
+Experiment 5, similar to Experiment 3, used 2 large ROIs (or halves of the display).
+As in @shimojoGazeBiasBoth2003 and in the recent webcam-based replication by @yang2021webcam, participants (qualitatively) look more at the face that they ultimately choose.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
+The gaze patterns remained consistent for participants with better calibration accuracy.
+
+In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.
+Studies with ROIs that take up half or a quarter of the participant's display, which encompasses a large number of common paradigms, are very likely to be successful, even when testing questions related to the timecourse of processing.
+However, the smaller the ROIs, the more important the calibration becomes.
+For instance, studies with 4 ROIs may want to exclude data from participants with less than 75% validation accuracy, whereas studies using 2 halves of the display as ROIs may not need to be so conservative.
+Studies with smaller ROIs (see Experiment 1) may not be appropriate for webcam eye-tracking in its current form.
 

### 2023-10-05 manuscript.tex
updated intro, discussion sections, and general discussion

@@
 Advances in software for online data collection (de Leeuw, 2015; Papoutsaki et al., 2016) have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples.
-In particular, Webgazer.js (Papoutsaki et al., 2016) is a webcam-based Javascript plug-in that works in the browser.
+In particular, \texttt{Webgazer.js} (Papoutsaki et al., 2016) is a webcam-based Javascript plug-in that works in the browser.
 It can be integrated with any Javascript web interface.
-As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as jsPsych (de Leeuw, 2015), Gorilla (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or lab.js (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021).
+As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as \texttt{jsPsych} (de Leeuw, 2015), \texttt{Gorilla} (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or \texttt{lab.js} (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021).
 However, the added convenience comes at the cost of spatial and temporal resolution.
@@
 Semmelmann and Weigelt (2018) compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing.
-They used the Webgazer.js library (Papoutsaki et al., 2016) and programmed tasks in HTML/Javascript directly.
+They used the \texttt{Webgazer.js} library (Papoutsaki et al., 2016) and programmed tasks in HTML/Javascript directly.
 The first two tasks tested measurement of basic gaze properties.
@@
 
-Similarly, Yang and Krajbich (2021) used the Webgazer.js library (Papoutsaki et al., 2016) combined with the jsPsych library for conducting behavioral experiments in a web browser (de Leeuw, 2015), to replicate a well-established link between value-based decision-making and eye gaze Krajbich, Armel, \& Rangel (2010).
+Similarly, Yang and Krajbich (2021) used the \texttt{Webgazer.js} library (Papoutsaki et al., 2016) combined with the \texttt{jsPsych} library for conducting behavioral experiments in a web browser (de Leeuw, 2015), to replicate a well-established link between value-based decision-making and eye gaze Krajbich, Armel, \& Rangel (2010).
 Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one.
@@
 As in previous work, participants were biased to choose the option they had spent more time looking at.
-The authors also implemented a code modification to address temporal delays in WebGazer.
-
-Finally, Slim and Hartsuiker (2022) used the Webgazer.js library via the PCIbex online experiment platform (Zehr \& Schwarz, 2018) to replicate a visual world paradigm study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair) (Dijkgraaf, Hartsuiker, \& Duyck, 2017).
+The authors also implemented a code modification to address temporal delays in \texttt{WebGazer}.
+
+Finally, several papers have used the \texttt{WebGazer.js} library (via different interfaces) to replicate visual world paradigm studies.
+Slim and Hartsuiker (2022) used the \texttt{PCIbex} online experiment platform (Zehr \& Schwarz, 2018) to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair) (Dijkgraaf, Hartsuiker, \& Duyck, 2017).
 When the verb in the sentence was \emph{constraining} (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was \emph{neutral} (e.g., Mary steals a letter), as in previous work.
@@
 The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between \emph{constraining} and \emph{neutral} conditions emerged before the onset of the final noun (e.g., letter).
+Similarly, Degen, Kursat, and Leigh (2021) reported that effects of scalar implicature processing (comparing looks to the target in a four quadrant display for sentences such as ``Click on the girl that has \emph{some} apples'' vs.~``Click on the girl that has \emph{three} apples'' ) were smaller and delayed relative to those observed in the lab (Sun \& Breheny, 2020).
+
+In contrast, using the \texttt{Gorilla} experiment platform (Anwyl-Irvine et al., 2020), Prystauka, Altmann, and Rothman (2023) observed robust effects of verb semantics and lexical interference in similar time windows to previous in-lab studies (Altmann \& Kamide, 1999; Kukona, Cho, Magnuson, \& Tabor, 2014), though a direct comparison was not possible because their studies used different materials than the in-lab experiments they were conceptually replicating.
+Furthermore, using \texttt{jsPsych}, Vos, Minor, and Ramchand (2022) closely replicated the magnitude and timecourse of effects in a lab-based visual world paradigm where the regions of interest (ROIs) consisted of the left and right halves of the display, suggesting that the concerns about poor temporal resolution can be mitigated.
+Indeed, the eye-tracking plug-in in \texttt{jsPsych} uses a fork of \texttt{Webgazer.js} in which certain modifications have been made to minimize processing time.
+\footnote{See discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}}
+
+In sum, webcam eye-tracking has been used to varying degrees of success across a small set of paradigms that are used in cognitive science research.
+One configuration, \texttt{jsPsych} with a modification of \texttt{WebGazer.js}, appears to have circumvented initial limitations in temporal precision (Krajbich et al., 2010; Vos et al., 2022) but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs).
+In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking, in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
 
@@
 
-In order to validate online eyetracking measures, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+In order to validate the online eyetracking methodology, with the particular configuration known to have the greatest temporal precision, \texttt{jsPsych} and a modification of \texttt{Webgazer}, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-Ideally, we would only attempt to replicate studies where the original measurements have small error bars and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
+Ideally, we would only attempt to replicate studies where the original measurements have small standard errors and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
 
@@
 First, replicating five very different studies from different research traditions decreases our reliance on any one study.
-Second, we include several ``sanity check'\,' analyses, such as the correlation between calibration accuracy and effect size.
-(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for XXX of the studies, we had comparison data collected in-lab either using jsPsych or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
+Second, we include several `'sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
+(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using \texttt{jsPsych} or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
 
@@
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
-Table~\ref(tab:studies-table) provides an overview of the five studies we selected.
+Table \ref{tab:studies-table} provides an overview of the five studies we selected.
 
@@
 
-\caption{\label{tab:studies-table}Studies selected for replication attempts}
+\caption{\label{tab:studies-table}Studies selected for replication attempts. Citation counts based on Google Scholar (August 2023).}
 
@@
 \toprule
-Citation & \multicolumn{1}{c}{Topic Area} & \multicolumn{1}{c}{Paradigm} & \multicolumn{1}{c}{Citations (June 2022, Google Scholar)}\\
+Citation & \multicolumn{1}{c}{Topic Area} & \multicolumn{1}{c}{Paradigm} & \multicolumn{1}{c}{Citations}\\
 \midrule
-Altmann \& Kamide, 1999 & Psycholinguistics & Natural Scenes & 1,840.00\\
-Johansson \& Johansson, 2013 & Memory & Four Quadrants & 190.00\\
-Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 127.00\\
-Snedeker \& Trueswell, 2004 & Psycholinguistics & Four Quadrants & 448.00\\
-Shimojo et al., 2003 & Decision Making & Two Halves & 964.00\\
+Altmann \& Kamide, 1999 & Psycholinguistics & Natural Scenes & 2,007\\
+Johansson \& Johansson, 2014 & Memory & Four Quadrants & 228\\
+Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 131\\
+Snedeker \& Trueswell, 2004 & Psycholinguistics & Four Quadrants & 472\\
+Shimojo et al., 2003 & Decision Making & Two Halves & 1,073\\
 \bottomrule
@@
 (de Leeuw, 2015). Our fork included changes to
-webgazer.js in order to improve data quality for experiments in which
+\texttt{webgazer.js} in order to improve data quality for experiments in which
 the precise timing of stimulus onsets is relevant. Specifically, we
@@
 
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.2.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.3; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.4; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.3; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 
-Forty-nine participants were (AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info).
+Forty-nine participants were \textcolor{red}{AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info}.
 
@@
 The task began with a 9-point eye-tracker calibration
-and validation (Figure~\ref{fig:E1-calibration-figure}).
+and validation (Figure~\ref{fig:E1-calibration-figure} ).
 During the experiment, the participants were
@@
 The visual stimuli were created through Canva and depicted an agent
-accompanied by four to five objects in the scene (see Figure~\ref{fig:E1-example-trial}). On
+accompanied by four to five objects in the scene (see Figure ~\ref{fig:E1-example-trial}). On
 critical trials, participants heard one of two sentences associated with
@@
 \begin{figure}
-\centering
-\includegraphics{group-a/E1-example-trial.jpeg}
-\caption{\label{fig:E1-example-trial}Example trial from Experiment 1.
-Participants would hear a sentence (e.g., ``The boy will eat the cake'') and respond according to whether the sentence matched the picture.}
+\includegraphics[width=6.67in]{group-a/E1-example-trial} \caption{Example trial from Experiment 1.
+Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.}\label{fig:E1-example-trial}
 \end{figure}
@@
 The following analyses included 52 participants.
-
-*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.
 
@@
 
-Altmann \& Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
 When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
@@
 Finally, we address whether participants look to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
-{[}TO-DO: On average, participants looked to the target X ms after (AK's Table 1)\ldots, I'll also want to say the lengths of the verbs.
-AK's Table 2{]} We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+{[}TO-DO: On average, participants looked to the target 349 ms after the noun onset in the restrictive condition (compared to ) and 349 ms after the noun onset in the non-restrictive condition (compared to ){]}.
+Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
+
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
 There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-degen2021seeing}{}}%
+Degen, J., Kursat, L., \& Leigh, D.
+D.
+(2021).
+Seeing is believing: Testing an explicit linking assumption for visual world eye-tracking in psycholinguistics.
+\emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{43}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-dijkgraaf2017predicting}{}}%
@@
 Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kukona2014lexical}{}}%
+Kukona, A., Cho, P.
+W., Magnuson, J.
+S., \& Tabor, W.
+(2014).
+Lexical interference effects in sentence processing: Evidence from the visual world paradigm and self-organizing models.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 326.
 
@@
 {AAAI}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-prystauka2023online}{}}%
+Prystauka, Y., Altmann, G.
+T., \& Rothman, J.
+(2023).
+Online eye tracking and real-time sentence processing: On opportunities and efficacy for capturing psycholinguistic effects of different magnitudes and diversity.
+\emph{Behavior Research Methods}, 1--19.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-sun2020another}{}}%
+Sun, C., \& Breheny, R.
+(2020).
+Another look at the online processing of scalar inferences: An investigation of conflicting findings from visual-world eye-tracking studies.
+\emph{Language, Cognition and Neuroscience}, \emph{35}(8), 949--979.
+
 \leavevmode\vadjust pre{\hypertarget{ref-tanenhaus1995}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vos2022comparing}{}}%
+Vos, M., Minor, S., \& Ramchand, G. C. (2022). Comparing infrared and webcam eye tracking in the visual world paradigm. \emph{Glossa Psycholinguistics}, \emph{1}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%

### 2023-10-05 manuscript.tex
re-knit pdf

@@
 
-Finally, several papers have used the \texttt{WebGazer.js} library (via different interfaces) to replicate visual world paradigm studies.
+Several papers have used the \texttt{WebGazer.js} library (via different interfaces) to replicate visual world paradigm studies.
 Slim and Hartsuiker (2022) used the \texttt{PCIbex} online experiment platform (Zehr \& Schwarz, 2018) to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair) (Dijkgraaf, Hartsuiker, \& Duyck, 2017).
@@
 \footnote{See discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}}
+Finally, Van der Cruyssen et al.
+(2023) used \texttt{WebGazer.js} in conjunction with \texttt{PsychoJS} to conceptually replicate three paradigms, one which is analogous to Yang and Krajbich (2021), another testing the novelty preference (tendency for learners to look more at an object that they have not yet studied), and a visual world paradigm study with 4 objects, similar to Prystauka et al.
+(2023).
+These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset.
+(They did not address whether there were temporal delays.)
 
@@
 One configuration, \texttt{jsPsych} with a modification of \texttt{WebGazer.js}, appears to have circumvented initial limitations in temporal precision (Krajbich et al., 2010; Vos et al., 2022) but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs).
-In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking, in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
+Further, the extent to which noise in the measurement is due to the software and hardware limitations as opposed to the difference between the in-lab and online settings remains unclear.
+In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
 
@@
 In order to validate the online eyetracking methodology, with the particular configuration known to have the greatest temporal precision, \texttt{jsPsych} and a modification of \texttt{Webgazer}, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
-The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science.
-Ideally, we would only attempt to replicate studies where the original measurements have small standard errors and are known to replicate; otherwise, it can be difficult to distinguish a failure of the method (online eyetracking does not work) from a failure of the original study to replicate.
-
+The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
+
+\hypertarget{selection-of-studies}{%
+\subsection{Selection of Studies}\label{selection-of-studies}}
+
+Studies with large effect sizes and which are known to replicate are ideal targets for further replication; otherwise, it can be difficult to distinguish a failure of the method from a failure of the original study to replicate.
 In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability.
@@
 Second, we include several `'sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
-(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using \texttt{jsPsych} or a more traditional eyetracker technology, allowing us to direct assess the impact of differences in subject population and equipment.
-
-\hypertarget{selection-of-studies}{%
-\subsection{Selection of Studies}\label{selection-of-studies}}
+(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using \texttt{jsPsych} or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
 
 We chose five high-impact eyetracking studies involving adult subjects.
-(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two
-halves of the screen, visual world paradigm with four quadrants, visual
-world paradigm with ``natural'' scenes).
+(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``natural'' scenes).
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
@@
 
-In addition, in-person replications were conducted for Experiments 1 and 4. Information about those samples is given in the corresponding Method sections.
+In addition, an in-person replication was conducted for Experiment 1.
+Information about the sample is given in the corresponding Method sections.
 
@@
 
+\hypertarget{pre-registration}{%
+\subsection{Pre-registration}\label{pre-registration}}
+
+These data were collected within the context of an undergraduate research methods course.
+Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the first author.
+The OSF repositories associated with these experiments are linked in the methods sections of each individual study.
+Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality).
+All analysis code underlying this paper can be found in the Github repository: \url{https://github.com/jodeleeuw/219-2021-eyetracking-analysis}
+
 \hypertarget{data-pre-processing}{%
@@
 The visual stimuli were created through Canva and depicted an agent
-accompanied by four to five objects in the scene (see Figure ~\ref{fig:E1-example-trial}). On
+accompanied by four to five objects in the scene (see Figure~\ref{fig:E1-example-trial}). On
 critical trials, participants heard one of two sentences associated with
@@
 
-The experimental design is visually depicted in Figure~\ref{fig:E3-design-schematic}
+The experimental design is visually depicted in Figure~\ref{fig:E3-design-schematic}.
+
+There were two modifications we made to the methods of the original
+experiment. As we were only replicating the declarative memory component
+of the original experiment, we did not have a ``priming group.''
+Therefore, we followed only the procedure for the ``looking group.''
+Additionally, for each section of the study, the stimuli were presented
+on a single screen instead of two screens due to the constraints of the
+online experiment format.
 
@@
 
-Images were selected XXX\ldots{}
-
-There were two modifications we made to the methods of the original
-experiment. As we are only replicating the declarative memory component
-of the original experiment, we did not have a ``priming group.''
-Therefore, we followed only the procedure for the ``looking group.''
-Additionally, for each section of the study, the stimuli was presented
-on a single screen instead of two screens due to the constraints of the
-online experiment format.
+\textcolor{red}{Images were selected XXX...}
 
@@
 \subsection{Discussion}\label{discussion-2}}
+
+As in Manns et al.
+(2000), participants looked more at novel images than previously seen images.
+This effect was consistent for ROIs based on the images and for the coarser ROIs based on two halves of the display.
+A day later, participants were also able to discriminate the images they had seen from foil images they had not seen during the previous session.
+However, there was no evidence that memory performance on day 2 was related to looking time on day 1.
+Calibration quality did not appear to impact this relationship.
 
@@
 
+As in Ryskin et al.
+(2017) and Snedeker and Trueswell (2004), listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier, instrument or equi).
+For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).
+This pattern was stronger for those who achieved higher calibration accuracy and when quadrant-based ROIs were used compared to image-based ROIs.
+
 \hypertarget{experiment-5}{%
@@
 All stimuli, experiment scripts, data, and analysis scripts are
-available on the Open Science Framework at \url{https://osf.io/eubsc/}
-(\url{https://osf.io/eubsc/}). The study pre-registration is available at
-\url{https://osf.io/tv57s} (\url{https://osf.io/tv57s}).
+available on the Open Science Framework at \url{https://osf.io/eubsc/}.
+The study pre-registration is available at
+\url{https://osf.io/tv57s}.
 
@@
 the age of 18. 27 participants were recruited on Prolific to participate
-in stimulus norming (for attractiveness). They were paid \$XX for
-completing the experiment. Data from 3 participants was excluded because
-their mode response made up more than 50\% of their total responses
-, for a total of 24 participants
-in the norming. They each viewed all 172 faces and were asked to rate
+in stimulus norming (for attractiveness). They each viewed all 172 faces and were asked to rate
 them on a scale from 1 (less attractive) to 7 (more attractive) using a
 slider. Faces were presented one at a time and in a random order for
-each participant. Following Shimojo et al., 19 face pairs were made by
-matching two faces that had a difference in mean attractiveness ratings
-that was 0.25 points or lower and that matched in gender, race, and age
+each participant. Data from 3 participants were excluded because
+their mode response made up more than 50\% of their total responses, for a total of 24 participants
+in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by
+identifying two faces that 1) had a difference in mean attractiveness ratings
+that was 0.25 points or lower and 2) matched in gender, race, and age
 group (young adult, adult, or older adult).
@@
 supplied their own cameras, so hardware sampling rate varied. However,
-data was collected at 20 Hz.{[}TODO - CONFIRM{]}
+data was collected at 20 Hz.\textcolor{red}{[TODO - CONFIRM]}
 
@@
 
-\hypertarget{combined-analyses}{%
-\section{Combined Analyses?}\label{combined-analyses}}
-
-\begin{itemize}
-\tightlist
-\item
-  Pooling data from all experiments we can look at patterns in the
-  calibration and validation data
-\end{itemize}
+Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the face that they ultimately choose.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
+The gaze patterns remained consistent for participants with better calibration accuracy.
 
@@
 
-\begin{itemize}
-\item
-  E1:
-\item
-  E2:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    replication of key result with 4 quadrants
-  \item
-    calib quality doesn't seem to matter
-  \item
-    if attempting to control where people are looking, think about modifying task\ldots{}
-  \end{itemize}
-\item
-  E3:
-\item
-  E4:
-\item
-  E5:
-\end{itemize}
+We conducted 5 attempted replication studies using different experimental paradigms from across the cognitive sciences.
+All were successfully implemented in \texttt{jsPsych} using the \texttt{webgazer} plugin, but replication success was mixed.
+Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with 5 to 6 ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
+Both attempts to replicate Altmann and Kamide (1999) were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking (James, Minnihan, \& Watson, 2023).
+A previous conceptual replication of this paradigm using webcam-based eye-tracking {[}prystauka2023online{]} was successful but used a 4-quadrant visual world paradigm, rather than the ``naturalistic'' scenes used in the original study and in the current replication attempts.
+It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
+The primary limitation is likely to be the size of the ROIs.
+
+Experiment 2 used the 4 quadrants of the participant's screen as ROIs.
+As in Johansson and Johansson (2014) and Spivey and Geng (2001), participants spontaneously looked to blank ROIs which previously contained to-be-remembered pictures.
+These results appeared to be robust to calibration quality.
+An additional manipulation, instructing participants to keep gaze fixed on a central point, was not successful.
+One possibility is that participants are less motivated to follow such instructions when an experimenter is not present in the same room with them.
+It may be possible to improve performance by emphasizing that this is an important aspect of the experiment or by providing additional training/practice in keeping the eyes still on one particular point.
+
+Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in (\textbf{mannsVisualPairedcomparisonTask200?}).
+However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
+Calibration quality did not appear to impact this relationship.
+More work is needed to understand whether delay manipulations can be practically combined with webcam eye-tracking.
+
+Experiment 4 used the 4 quadrants of the participant's screen as ROIs.
+As in Ryskin et al.
+(2017), listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input (``Rub the frog with the mitten'').
+Across multiple time windows, participants looked more at potential instruments (mitten), when the verb (rub) was one that was more likely to be followed by a prepositional phrase describing an instrument with which to perform the action , as opposed to describing the recipient of the action (frog).
+Despite the qualitative replication of past findings, the overall rates of looks to various objects were much lower than in an in-lab study using infrared eye-tracking.
+This reduction may be related to measurement quality: effect sizes were greater for participants with higher calibration accuracy.
+Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect.
+Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to \texttt{webgazer} that are made within the \texttt{jsPsych} plug-in successfully address the issues noted by Dijkgraaf et al.
+(2017) and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.
+
+Experiment 5, similar to Experiment 3, used 2 large ROIs (or halves of the display).
+As in Shimojo et al.
+(2003) and in the recent webcam-based replication by Yang and Krajbich (2021), participants (qualitatively) look more at the face that they ultimately choose.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
+The gaze patterns remained consistent for participants with better calibration accuracy.
+
+In sum, the \texttt{webgazer} plug-in for \texttt{jsPsych} can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.
+Studies with ROIs that take up half or a quarter of the participant's display, which encompasses a large number of common paradigms, are very likely to be successful, even when testing questions related to the timecourse of processing.
+However, the smaller the ROIs, the more important the calibration becomes.
+For instance, studies with 4 ROIs may want to exclude data from participants with less than 75\% validation accuracy, whereas studies using 2 halves of the display as ROIs may not need to be so conservative.
+Studies with smaller ROIs (see Experiment 1) may not be appropriate for webcam eye-tracking in its current form.
 
@@
 Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83.
+
+\leavevmode\vadjust pre{\hypertarget{ref-james2023language}{}}%
+James, A. N., Minnihan, C. J., \& Watson, D. G. (2023). Language experience predicts eye movements during online auditory comprehension. \emph{Journal of Cognition}, \emph{6}(1).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-van2023validation}{}}%
+Van der Cruyssen, I., Ben-Shakhar, G., Pertzov, Y., Guy, N., Cabooter, Q., Gunschera, L.
+J., \& Verschuere, B.
+(2023).
+The validation of online webcam-based eye-tracking: The replication of the cascade effect, the novelty preference, and the visual world paradigm.
+\emph{Behavior Research Methods}, 1--14.
+
 \leavevmode\vadjust pre{\hypertarget{ref-vos2022comparing}{}}%

### 2024-02-17 group-a/E1-analysis-calibration.Rmd
fixes to get figures to display and cross-ref correctly

@@
-```{r}
+<!-- # Setup 
 #To be run after E1-analysis-replication.Rmd
-#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
-```
-<!-- # Setup -->
+#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent"). -->
 ```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}

### 2024-02-17 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
fixes to get figures to display and cross-ref correctly

@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:jh-E1-spaghetti-fig).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-JH-spaghetti-fig).
 
-```{r jh-E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+```{r E1-JH-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
 The vertical line marks the mean noun onset time across trials and conditions."}
-jh.E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
+
+jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
   scale_fill_grey(start=1.0, end=0.0)+
@@
 
-jh.E1_spag_fig
+jh_E1_spag_fig
 

### 2024-02-17 group-a/E1-analysis-replication.Rmd
fixes to get figures to display and cross-ref correctly

@@
 The vertical line marks the mean noun onset time across trials and conditions."}
+
 E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
@@
 ```
+
+```{r Load data}
+# load("pre.noun.first.looks.data.min.RData") 
+# load("pre.verb.offset.first.looks.data.min.RData")
+# load("first.fixation.after.verb.onset.analysis.data.min.RData")
+# load("validation.percent.RData")
+# load("first.fixation.after.verb.onset.subject.summary.min.RData")
+
+pre.noun.first.looks.data <- pre.noun.first.looks.data.min
+pre.verb.offset.first.looks.data <- pre.verb.offset.first.looks.data.min
+first.fixation.after.verb.onset.analysis.data <- first.fixation.after.verb.onset.analysis.data.min
+first.fixation.after.verb.onset.subject.summary <- first.fixation.after.verb.onset.subject.summary.min  
+```
+
+```{r Model 1 subject summary}
+pre.noun.subj.summary <- pre.noun.first.looks.data %>%
+  group_by(subject_id, verb_type, object_class) %>%
+  summarize(fix.p = mean(cumulative.fixation.p))
+
+pre.noun.by.verb <- pre.noun.subj.summary %>%
+  pivot_wider(names_from = object_class, values_from = fix.p) %>%
+  mutate(tar.adv = target.object - distractor)
+
+pre.noun.effects <- pre.noun.by.verb %>%
+  select(subject_id, verb_type, tar.adv) %>%
+  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
+  rename("non_restricting" = "non-restricting") %>%
+  mutate(effect = restricting - non_restricting)
+```
+
+```{r Model 1 effect size by calibration}
+#merge with validation percent
+
+cali.analy.1 <- merge(pre.noun.effects, validation.percent, by = "subject_id")
+
+#correlate
+m1_diffdiff_cor <- cor.test(cali.analy.1$effect, cali.analy.1$M, use = "pairwise.complete.obs") #difference of differences
+#0.03107354
+m1_diffdiff_cor_r <- m1_diffdiff_cor$estimate
+m1_diffdiff_cor_p <- m1_diffdiff_cor$p.value
+
+m1_diff_cor <- cor.test(cali.analy.1$restricting, cali.analy.1$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
+#0.2096605
+m1_diff_cor_r <- m1_diff_cor$estimate
+m1_diff_cor_p <- m1_diff_cor$p.value
+```
+
+```{r Model 2 subject summary}
+pre.verb.subj.summary <- pre.verb.offset.first.looks.data %>%
+  group_by(subject_id, verb_type, object_class) %>%
+  summarize(fix.p = mean(cumulative.fixation.p))
+
+pre.verb.by.verb <- pre.verb.subj.summary %>%
+  pivot_wider(names_from = object_class, values_from = fix.p) %>%
+  mutate(tar.adv = target.object - distractor)
+
+pre.verb.effects <- pre.verb.by.verb %>%
+  select(subject_id, verb_type, tar.adv) %>%
+  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
+  rename("non_restricting" = "non-restricting") %>%
+  mutate(effect = restricting - non_restricting)
+```
+
+```{r Model 2 effect size by calibration}
+#merge with validation percent
+cali.analy.2 <- merge(pre.verb.effects, validation.percent, by = "subject_id")
+
+#correlate
+m2_diffdiff_cor <- cor.test(cali.analy.2$effect, cali.analy.2$M, use = "pairwise.complete.obs") #difference of differences
+#-0.04809241
+m2_diffdiff_cor_r <- m2_diffdiff_cor$estimate
+m2_diffdiff_cor_p <- m2_diffdiff_cor$p.value
+
+m2_diff_cor <- cor.test(cali.analy.2$restricting, cali.analy.2$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
+#-0.03601876
+m2_diff_cor_r <- m2_diff_cor$estimate
+m2_diff_cor_p <- m2_diff_cor$p.value
+
+```
+
+```{r Model 3 effect size by calibration}
+#summary(validation.percent)
+#make looking scores for Ps
+looking.scores <- first.fixation.after.verb.onset.subject.summary[,1:3] %>% 
+  spread(verb_type, m.t) %>%
+  rename("non_restricting" = "non-restricting") %>%
+  mutate(diff = non_restricting - restricting)
+
+#merge with validation percent
+cali.analy.3 <- merge(looking.scores, validation.percent, by = "subject_id")
+
+#correlate
+m3_diff_cor <- cor.test(cali.analy.3$diff, cali.analy.3$M, use = "pairwise.complete.obs")
+#0.04122796
+m3_diff_cor_r <- m3_diff_cor$estimate
+m3_diff_cor_p <- m3_diff_cor$p.value
+```
+
+#### Calibration
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
+Calibration quality varied widely, ranging from `r min(validation.percent$M) %>% round(digits = 2)`% to `r max(validation.percent$M) %>% round(digits = 2)`%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
+Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
+However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.
+rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).

### 2024-02-17 group-a/E1-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@
 ```
+
+The task began with a 9-point eye-tracker calibration
+and validation (Figure\ \@ref(fig:E1-calibration-figure)). 
+During the experiment, the participants were
+simultaneously presented with a visual image and a corresponding audio
+recording of a spoken sentence. Participants had to input a keyboard
+response indicating "yes" or "no" as to whether the sentence they heard
+was feasible given the visual image. There were two practice trials to
+ensure that participants understood the instructions
+before they undertook the main portion of the experiment. Participants'
+reaction times, keyboard responses, and looks to objects in the scene
+were recorded for each trial.
 
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1.
+```{r E1-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1.
 Black points were used for calibration.

### 2024-02-17 group-b/E2-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@
 ```
+
+The task began with a 9-point eye-tracker calibration
+and validation (Figure \@ref(fig:E2-calibration-figure)).
 
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2.
+```{r E2-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2.
 Black points were used for calibration.

### 2024-02-17 group-c/E3-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@
 ```
+
+The task began with a 7-point eye-tracker calibration (each point was
+presented 3 times in a random order) and validation with 3 points (each
+presented once). The point locations were designed to focus calibration
+on the center of the screen and the middle of the left and right halves
+of the screen (Figure\ \@ref(fig:E3-calibration-figure)).
 
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3.
+```{r E3-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3.
 Black points were used for calibration.

### 2024-02-17 group-d/E4-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@
 ```
+
+After the eye-tracking calibration and validation (Figure\ \@ref(fig:E4-calibration-figure)), participants went through an audio
+test so they could adjust the audio on their computer to a comfortable
+level. Before beginning the experiment, they were given instructions
+that four objects would appear, an audio prompt would play, and they
+should do their best to use their mouse to act out the instructions.
+They then went through three practice trials which were followed by 54
+critical trials and 24 filler trials presented in a random order.
 
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 4.
+```{r E4-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 4.
 Black points were used for calibration.

### 2024-02-17 group-e/E5-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@
 ```
+
+At the beginning of the experimental task, participants completed a
+9-point eye-tracker calibration (each point appeared 3 times in random
+order) and 3-point validation. The validation point appeared once at
+center, middle left, and middle right locations in random order (see Figure\ \@ref(fig:E5-calibration-figure)).
+<!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total?
+If the latter, why is the coverage denser than for Experiment 4?
+-->
 
@@
 
-```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 5.
+```{r E5-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 5.
 Black points were used for calibration.

### 2024-02-17 manuscript.Rmd
fixes to get figures to display and cross-ref correctly

@@
 
-The task began with a 9-point eye-tracker calibration
-and validation (Figure\ \@ref(fig:E1-calibration-figure) ). 
-During the experiment, the participants were
-simultaneously presented with a visual image and a corresponding audio
-recording of a spoken sentence. Participants had to input a keyboard
-response indicating "yes" or "no" as to whether the sentence they heard
-was feasible given the visual image. There were two practice trials to
-ensure that participants understood the instructions
-before they undertook the main portion of the experiment. Participants'
-reaction times, keyboard responses, and looks to objects in the scene
-were recorded for each trial.
-
-```{r E1-calibration-figure, child='group-a/E1-calibration-figure.Rmd'}
+```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }
 
@@
 
-```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
-```
+<!---```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
+# the presence of this chunk separate from the replication analysis was somehow causing the figures to disappear so I copied the calibration rmd content into the analysis-replication rmd and this solved the problem.
+```--->
 
 ### In-lab sample
+
+<!---
+test figure \@ref(fig:test)
+
+```{r test, fig.cap = "test plot"}
+
+plot(cars$speed, cars$dist)
+
+```
+--->
+
 ```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
-#Includes calibration analysis 
+
 ```
@@
 
-The task began with a 9-point eye-tracker calibration
-and validation (Figure\ \@ref(fig:E2-calibration-figure)).
-
-```{r E2-calibration-figure, child='group-b/E2-calibration-figure.Rmd'}
+```{r E2 calibration figure, child='group-b/E2-calibration-figure.Rmd'}
 
@@
 
-The task began with a 7-point eye-tracker calibration (each point was
-presented 3 times in a random order) and validation with 3 points (each
-presented once). The point locations were designed to focus calibration
-on the center of the screen and the middle of the left and right halves
-of the screen (Figure\ \@ref(fig:E3-calibration-figure)).
-
-```{r E3-calibration-figure, child='group-c/E3-calibration-figure.Rmd'}
+```{r E3 calibration figure, child='group-c/E3-calibration-figure.Rmd'}
 
@@
 
-After the eye-tracking calibration and validation (Figure\ \@ref(fig:E4-calibration-figure)), participants went through an audio
-test so they could adjust the audio on their computer to a comfortable
-level. Before beginning the experiment, they were given instructions
-that four objects would appear, an audio prompt would play, and they
-should do their best to use their mouse to act out the instructions.
-They then went through three practice trials which were followed by 54
-critical trials and 24 filler trials presented in a random order.
-
-```{r E4-calibration-figure, child='group-d/E4-calibration-figure.Rmd'}
+```{r E4 calibration figure, child='group-d/E4-calibration-figure.Rmd'}
 
@@
 
-At the beginning of the experimental task, participants completed a
-9-point eye-tracker calibration (each point appeared 3 times in random
-order) and 3-point validation. The validation point appeared once at
-center, middle left, and middle right locations in random order (see Figure\ \@ref(fig:E5-calibration-figure)).
-<!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total?
-If the latter, why is the coverage denser than for Experiment 4?
--->
-```{r E5-calibration-figure, child='group-e/E5-calibration-figure.Rmd'}
+```{r E5 calibration figure, child='group-e/E5-calibration-figure.Rmd'}
 
@@
 Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [@james2023language].
-A previous conceptual replication of this paradigm using webcam-based eye-tracking [prystauka2023online] was successful but used a 4-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
+A previous conceptual replication of this paradigm using webcam-based eye-tracking [@prystauka2023online] was successful but used a 4-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
 It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
@@
 
-Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask200.
+Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask2000.
 However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.

### 2024-02-17 manuscript.tex
fixes to get figures to display and cross-ref correctly

@@
 The task began with a 9-point eye-tracker calibration
-and validation (Figure~\ref{fig:E1-calibration-figure} ).
+and validation (Figure~\ref{fig:E1-calibration-figure}).
 During the experiment, the participants were
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}Calibration and validation point locations for Experiment 1.
+\includegraphics{manuscript_files/figure-latex/E1-calibration-figure-1.pdf}
+\caption{\label{fig:E1-calibration-figure}Calibration and validation point locations for Experiment 1.
 Black points were used for calibration.
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:jh-E1-spaghetti-fig}.
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-JH-spaghetti-fig}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1-JH-spaghetti-fig-1.pdf}
+\caption{\label{fig:E1-JH-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions.}
+\end{figure}
 
@@
 The task began with a 9-point eye-tracker calibration
-and validation (Figure~\ref{fig:E2-calibration-figure}).
+and validation (Figure \ref{fig:E2-calibration-figure}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E2-calibration-figure-1.pdf}
+\caption{\label{fig:E2-calibration-figure}Calibration and validation point locations for Experiment 2.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)}
+\end{figure}
 
@@
 of each item.
+
+\begin{figure}
+\includegraphics[width=5.47in]{group-b/E2-example-figure} \caption{Example trial from Experiment 2.}\label{fig:E2-example-trial}
+\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E2-gaze-fig-both-conds-1.pdf}
+\caption{\label{fig:E2-gaze-fig-both-conds}Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.}
+\end{figure}
+
 The proportions of looks across quadrants in the free-viewing condition were analyzed using a linear mixed-effects model with quadrant as the predictor (critical as the reference level).
@@
 Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E2-rt-acc-fig-1.pdf}
+\caption{\label{fig:E2-rt-acc-fig}Accuracy and response times during memory retrieval.}
+\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-calibration-figure-1.pdf}
+\caption{\label{fig:E3-calibration-figure}Calibration and validation point locations for Experiment 3.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.}
+\end{figure}
+
 The experiment was administered over the course of two
@@
 
+\begin{figure}
+\includegraphics[width=3.41in]{group-c/E3-example-figure} \caption{Schematic of the design of Experiment 3}\label{fig:E3-design-schematic}
+\end{figure}
+
 \hypertarget{materials}{%
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/plot-cumulative-looking-score-1.pdf}
+\caption{\label{fig:plot-cumulative-looking-score}Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
+\end{figure}
+
 \hypertarget{day-2}{%
@@
 Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(38) = 0.46, p = 0.65 (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(46) = 0.49, p = 0.63.
+
+\includegraphics{manuscript_files/figure-latex/Plot Looking Score Correlations-1.pdf}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-roi correlation of looking score-1.pdf}
+\caption{(\#fig:E3-roi correlation of looking score)Correlation between looking scores calculated using ROIs and using screen halves.}
+\end{figure}
+
 \hypertarget{looking-scores}{%
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-roi Plot of cumulative looking score-1.pdf}
+\caption{(\#fig:E3-roi Plot of cumulative looking score)Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
+\end{figure}
+
 \hypertarget{correlations-with-day-2-performance}{%
@@
 
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot Calibration Accuracy-1.pdf}
+
 \hypertarget{correlation-with-effects}{%
@@
 
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (halves) by calibration-1.pdf}
+
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (roi) by calibration-1.pdf}
+
 We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
 None of the four relationships showed a significant correlation.
+
+\includegraphics{manuscript_files/figure-latex/E3-cal Plot correlations with calibration score-1.pdf}
 
@@
 critical trials and 24 filler trials presented in a random order.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-calibration-figure-1.pdf}
+\caption{\label{fig:E4-calibration-figure}Calibration and validation point locations for Experiment 4.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)}
+\end{figure}
 
@@
 
+\begin{figure}
+\includegraphics[width=4.5in]{group-d/E4-example-figure} \caption{An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}\label{fig:E4-example-trial}
+\end{figure}
+
 \hypertarget{materials-1}{%
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-1.pdf}
+\caption{\label{fig:E4-mouse-moves-fig}Proportion of first mouse movements by location and verb bias.}
+\end{figure}
+
 A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.~equi \& modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.~modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
@@
 The pattern was reversed for looks to the target instrument.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-1.pdf}
+\caption{\label{fig:E4-gaze-timecourse-fig}Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
+\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-web-and-orig-1.pdf}
+\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.}
+\end{figure}
+
 The eye-tracking results from both studies are summarized in Figure \ref{fig:E4-proportion-fix-by-window-both}.
@@
 This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-proportion-fix-by-window-both-1.pdf}
+\caption{\label{fig:E4-proportion-fix-by-window-both}Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
+Error bars reflect bootstrapped 95\% CIs over subject means}
+\end{figure}
 
@@
 Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \ref{fig:E4-example-subj-looks-ROI}b).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-example-subj-looks-ROI-1.pdf}
+\caption{\label{fig:E4-example-subj-looks-ROI}Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
+Magenta points indicate looks that were not categorized into an ROI}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E4-gaze-timecourse-fig-quadrants-1.pdf}
+\caption{\label{fig:E4-gaze-timecourse-fig-quadrants}Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.}
+\end{figure}
 
@@
 center, middle left, and middle right locations in random order (see Figure~\ref{fig:E5-calibration-figure}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E5-calibration-figure-1.pdf}
+\caption{\label{fig:E5-calibration-figure}Calibration and validation point locations for Experiment 5.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.}
+\end{figure}
 
@@
 
+\begin{figure}
+\includegraphics[width=0.45\linewidth]{figGroupEOrigA} \includegraphics[width=0.45\linewidth]{figGroupEOrigB} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMain-3} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMain-4} \caption{Primary results from Exp.
+5.
+\emph{Top} shows the original results from Shimojo and colleagues (Figures reprinted with permission{[}TODO{]}).
+The attractiveness judgment along with the best-fitting sigmoid is shown in the \emph{top left}.
+Results for the roundness judgment are show in the \emph{top right}, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison (\emph{top right}).
+(\emph{Bottom}) shows the analogous results from the replication, with the attractiveness judgments on the \emph{bottom left} and the roundness judgments on the \emph{bottom right}.
+Again, the best-fitting sigmoid for the attractiveness judgments are plotted with a dashed line alongside the roundness results, for purposes of comparison.}\label{fig:groupEMain}
+\end{figure}
+
 Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig.
-\ref{fig:Shimojo}).
+\ref{fig:groupEMain}).
 These fit less well than in the original paper for both the attractiveness judgment (R\textsuperscript{2} = 0.84 vs.~0.91) and the roundness judgment (R\textsuperscript{2} = 0.54 vs.~0.91).
@@
 
+\begin{figure}
+\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/E5cal-1} \caption{Histogram of calibration success in Exp.
+5.
+Where participants required more than one calibration (N=8), only the final calibration was considered.}\label{fig:E5cal}
+\end{figure}
+
 To determine whether calibration accuracy influenced our key effects, we calculated the percentage of samples during the task in which the participant was fixating the face they ultimately chose.
@@
 \ref{fig:E5calcorr} reveals that this correlation is due to a handful of particpiants with calibration values below 50\%.
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{manuscript_files/figure-latex/E5calcorr-1} \caption{Correlation between calibration accuracy (x-axis) and percentage of samples fixating target (y-axis) in Exp.
+5.}\label{fig:E5calcorr}
+\end{figure}
 
@@
 
+\begin{figure}
+\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMainrev-1} \includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/groupEMainrev-2} \caption{Revised results for Exp.
+5 after removing low-calibration accuracy participants.
+\emph{Left}: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid.
+\emph{Right}: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).}\label{fig:groupEMainrev}
+\end{figure}
+
 \hypertarget{effects-of-rois-2}{%
@@
 Both attempts to replicate Altmann and Kamide (1999) were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking (James, Minnihan, \& Watson, 2023).
-A previous conceptual replication of this paradigm using webcam-based eye-tracking {[}prystauka2023online{]} was successful but used a 4-quadrant visual world paradigm, rather than the ``naturalistic'' scenes used in the original study and in the current replication attempts.
+A previous conceptual replication of this paradigm using webcam-based eye-tracking (Prystauka et al., 2023) was successful but used a 4-quadrant visual world paradigm, rather than the ``naturalistic'' scenes used in the original study and in the current replication attempts.
 It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
@@
 
-Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in (\textbf{mannsVisualPairedcomparisonTask200?}).
+Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in Manns et al.
+(2000).
 However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.

### 2024-06-07 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
edits to manuscript and exp 1

@@
 
-#check for weirdness
-discrep <- audio.data$delay_bw_onset_of_verb_and_onset_of_target_noun - 
-  (audio.data$duration_of_verb + 
-     audio.data$duration_of_intervening_determiner + 
-     audio.data$intonation_break_bw_verb_and_determiner)
-sum(discrep) 
-#this should be zero, but it's 0.59! TO-DO: Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
+# #check for weirdness
+# discrep <- audio.data$delay_bw_onset_of_verb_and_onset_of_target_noun - 
+#   (audio.data$duration_of_verb + 
+#      audio.data$duration_of_intervening_determiner + 
+#      audio.data$intonation_break_bw_verb_and_determiner)
+# sum(discrep) 
+# #this should be zero, but it's 0.59! TO-DO: Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
 ```
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-JH-spaghetti-fig).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-spaghetti-fig), Panel (c).
 
-```{r E1-JH-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions."}
+```{r make jh spaghetti plot}
 
 jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
-  scale_fill_grey(start=1.0, end=0.0)+
+  geom_line()+
+  geom_point(aes(fill = object_class), size=2, color = "black")+ 
+  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
   scale_shape_manual(values=c(22,21))+
-  geom_line()+
-  geom_point(size=2)+
+  guides(fill = guide_legend(override.aes=list(shape=21))) +
   theme_bw()+
-  theme(panel.grid=element_blank())+
   scale_y_continuous(limits=c(0,1))+
@@
   labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
-  geom_vline(xintercept = mean(jh.word.dur.avg$Total))
+  geom_vline(xintercept = mean(jh.word.dur.avg$Total)) +
+  theme(panel.grid=element_blank(), legend.position = "none")+
+  ggtitle('In-lab sample')
 
-jh_E1_spag_fig
+#jh_E1_spag_fig
 
-#The "Object type" part of the key doesn't actually show which color is which
 ```
@@
 #### Pre-noun fixations 
-<!--AJ: Edit text -->
-In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
-The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
+In line with the previous analyses of the remote data, we asked whether participants looked more to the target than to the distractor object during the predictive time window, depending upon the verb condition.
+The first model constrained the predictive window to the time before the onset of the target noun.
 We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.
 non-restricting = 0), object type (target = 1 vs.
-distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
-There were no significant effects, although the critical interaction was in the right direction [bar graph?] (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+distractor = 0), and their interaction, along with random effects for participants and scenes (with no covariance between random effects because the model cannot converge with full covariance matrix).
+Unlike the remote sample, there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (_b_ = `r jh.E1_model1_obj.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj.min %>% pull(p.value) %>% round(digits = 2)`).
+Also unlike the remote sample, the critical interaction was not in the expected direction, although it was also not statistically significant (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+When we did the same, we again saw that the critical interaction is not significant nor in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 jh.E1_model3_verb.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting")
-
+jh.E1_model3_dur.min = jh.E1_model3_tab.min %>% filter(term == "dur_verb_ms_c")
+jh.E1_model3_intxn.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting:dur_verb_ms_c")
 ```
 #### First target fixations after verb
-Finally, we address whether participants look to the target faster in the restrictive vs.
+Finally, we addressed whether participants looked to the target faster in the restrictive vs.
 the non-restrictive condition, starting after the onset of the verb.
-[TO-DO: On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs.
-AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
-There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+On average, participants looked to the target `r jh.our_table1_min$Eat[4]` ms after the noun onset in the restrictive condition and `r jh.our_table1_min$Move[4]` ms after the noun onset in the non-restrictive condition.
+As in the remote sample, the latencies are overall slower than in results published by Altmann & Kamide (1999) and James et al.
+(2023).
+Unlike in the remote sample, however, the difference is in the unexpected direction, such that participants looked to the target faster in the non-restrictive condition.
+
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+Effects of verb duration and its interaction with condition were also not statistically significant (duration: _b_ = `r jh.E1_model3_dur.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_dur.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_dur.min %>% pull(p.value) %>% round(digits = 2)`; interaction: _b_ = `r jh.E1_model3_intxn.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_intxn.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_intxn.min %>% pull(p.value) %>% round(digits = 2)` )
 
@@
 We tested whether a participant's calibration quality was correlated with their effect size.
-Across the three condition effects of interest, calibration quality was not significantly correlated (Effect 1 (pre-noun-onset): Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`, Effect 2 (pre-verb-offset): Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`, Effect 3 (first fixation): Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
+Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
 However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.
 rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).
+
+<!--###AGGRESSIVE EXCLUSION-->
+<!-- Set which mode here: -->
+```{r}
+# 'AGGRESSIVE' or 'MINIMAL'
+exclusion.mode <- 'AGGRESSIVE' 
+```
+
+<!-- ## Proportion of measured data in an ROI. -->
+
+<!-- Check the proportion of samples that were in at least one ROI for subjects. 
+Which is to say: at each event time "t" per trial per subject, check whether they were looking at ANY of the objects (vs background/off-screen).
+What proportion of fixation events (total number varies by trial/subj) were in ANY ROI?
+-->
+
+<!-- Exclude subjects below a threshold -->
+
+```{r}
+prop.samples.threshold.aggro.jh <- 0.2
+
+bad.subjects.prop.samples.aggro.jh <- jh.prop.in.roi.by.subject %>%
+  filter(prop.of.samples.in.roi <= prop.samples.threshold.aggro.jh) %>%
+  pull(subject_id)
+```
+
+<!-- Set criteria for minimal and aggressive exclusions -->
+
+```{r}
+validation.threshold.aggro.jh <- 50
+
+bad.subjects.validation.aggro.jh <- jh.validation.percent %>%
+  filter(M <= validation.threshold.aggro.jh) %>%
+  pull(subject_id) %>%
+  as.character()
+```
+
+<!-- ## Final exclusion data -->
+
+```{r}
+bad.subjects.aggro.jh <- unique(c(bad.subjects.prop.samples.aggro.jh, bad.subjects.validation.aggro.jh))
+
+critical.trials.filtered.aggro.jh <- jh.critical.trials %>%
+  filter(!subject_id %in% bad.subjects.aggro.jh)
+
+n.bad.subjects.aggro.jh <- length(bad.subjects.aggro.jh)
+```
+#### Aggressive Exclusion
+The second set of analyses used more aggressive exclusion criteria.
+First, we eliminated participants with `r prop.samples.threshold.aggro.jh*100` percent of fixations or fewer landing in any ROIs.
+This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro.jh)` participants.
+Second, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh` percent, which eliminated an additional `r n.bad.subjects.aggro.jh - length(bad.subjects.prop.samples.aggro.jh)` participants.
+The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.
+
+<!-- # Calculating cumulative fixation probability -->
+
+<!-- We start by calculating cumulative fixation probability on the objects after the verb onset. (Any fixations prior to the verb onset are not relevant to the core research questions.) -->
+
+<!-- First, add a column for time relative to verb onset, bin this to 50ms chunks, and filter the data to the 2,000 ms window after verb onset. -->
+
+```{r}
+cumulative.fixation.data.aggro.jh <- critical.trials.filtered.aggro.jh %>%
+  mutate(t.relative.to.verb.onset = t - (verb_onset*1000)) %>%
+  filter(t.relative.to.verb.onset >= 0 & t.relative.to.verb.onset <2000) %>%
+  mutate(t.w = floor(t.relative.to.verb.onset/50)*50)
+```
+
+<!-- Now check every time window within a trial to account for sparse samples. This calculating is time consuming, so we cache the result in a CSV file, and load from the CSV if it already exists. -->
+
+```{r}
+
+if(file.exists("data/generated/cumulative_fixation_data_aggro.jh.csv")){
+  cumulative.fixation.windows.data.aggro.jh <- read_csv("data/generated/cumulative_fixation_data_aggro.jh.csv")
+} else {
+
+  cumulative.fixation.windows.data.aggro.jh <- cumulative.fixation.data.aggro.jh %>%
+    group_by(subject_id, verb_type, image_name, object_type, object_class) %>%
+    summarize(cumulative.fixation.calculation(cur_data()))
+
+  write_csv(cumulative.fixation.windows.data.aggro.jh, file ="data/generated/cumulative_fixation_data_aggro.jh.csv")
+}
+```
+
+<!-- Then group by object class to calculate fixation probability for each kind of object, normalizing by the number of objects of that type. -->
+
+```{r}
+cumulative.fixation.windows.grouped.data.aggro.jh <- cumulative.fixation.windows.data.aggro.jh %>%
+  filter(!subject_id %in% bad.subjects.aggro.jh) %>%
+  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
+  summarize(cumulative.fixation.p = mean(has.fixated)) 
+```
+
+<!-- Then collapse over trials to get a cumulative probability for the whole window for each subject -->
+
+```{r}
+cumulative.fixation.windows.grouped.average.data.aggro.jh <- cumulative.fixation.windows.grouped.data.aggro.jh %>%
+  group_by(subject_id, verb_type, object_class, t.window) %>%
+  summarize(cumulative.fixation.p = mean(cumulative.fixation.p))
+```
+
+<!-- Collapse across subjects to generate the equivalent of the figure from Altmann & Kamide. -->
+
+```{r}
+cumulative.fixation.data.summary.aggro.jh <- cumulative.fixation.windows.grouped.average.data.aggro.jh %>%
+  filter(object_class %in% c('target.object', 'distractor')) %>%
+  group_by(t.window, verb_type, object_class) %>%
+  summarize(cumulative.fixation.m = mean(cumulative.fixation.p))
+```
+
+```{r} 
+#|E1-spaghetti-fig, 
+#|fig.cap = "Cumulative probability of fixating distractor 
+#|,and target objects across conditions."
+E1_spag_fig_aggro.jh <- ggplot(cumulative.fixation.data.summary.aggro.jh, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
+  scale_fill_grey(start=1.0, end=0.0)+
+  scale_shape_manual(values=c(22,21))+
+  geom_line()+
+  geom_point(size=2)+
+  theme_bw()+
+  theme(panel.grid=element_blank())+
+  scale_y_continuous(limits=c(0,1))+
+  scale_x_continuous(expand=c(0.01,0.01))+
+  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")
+
+#TO-DO: insert a vertical line for the average noun onset
+```
+
+<!-- __Question 1: Are there more pre-noun first looks to the target object than to the distractors?__
+
+First, grab the noun onset times to merge into our cumulative fixation data.-->
+
+```{r}
+noun.onset.times.aggro.jh <- critical.trials.filtered.aggro.jh %>%
+  group_by(image_name, verb_type) %>%
+  slice(1) %>%
+  ungroup() %>%
+  select(image_name, verb_type, delay_bw_onset_of_verb_and_onset_of_target_noun) %>%
+  mutate(relative.noun.onset = delay_bw_onset_of_verb_and_onset_of_target_noun * 1000) %>%
+  select(-delay_bw_onset_of_verb_and_onset_of_target_noun)
+
+trial.level.cumulative.fixation.data.aggro.jh <- cumulative.fixation.windows.grouped.data.aggro.jh %>%
+  left_join(noun.onset.times.aggro.jh, by=c("image_name", "verb_type"))
+```
+
+<!--Then, grab the last time window before the noun onset for each trial. This is the critical data for this test.-->
+
+```{r}
+pre.noun.first.looks.data.aggro.jh <- trial.level.cumulative.fixation.data.aggro.jh %>%
+  group_by(subject_id, image_name, verb_type) %>%
+  filter(t.window < relative.noun.onset) %>%
+  filter(t.window == max(t.window)) %>%
+  filter(object_class %in% c("target.object", "distractor"))
+```
+
+```{r}
+pre.noun.first.looks.data.aggro.jh$verb_type <- as.factor(pre.noun.first.looks.data.aggro.jh$verb_type)
+pre.noun.first.looks.data.aggro.jh$object_class <- as.factor(pre.noun.first.looks.data.aggro.jh$object_class)
+```
+<!--Fit the model, with no covariance between random effects because the model cannot converge with full covariance matrix.-->
+
+```{r}
+E1_model1.aggro.jh <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data.aggro.jh)
+#summary(E1_model1.aggro.jh)
+
+E1_model1_tab.aggro.jh = broom.mixed::tidy(E1_model1.aggro.jh) 
+E1_model1_obj.aggro.jh = E1_model1_tab.aggro.jh %>% filter(term == "object_classtarget.object")
+E1_model1_verb.aggro.jh = E1_model1_tab.aggro.jh %>% filter(term == "verb_typerestricting")
+E1_model1_obj_verb.aggro.jh = E1_model1_tab.aggro.jh %>% filter(term == "object_classtarget.object:verb_typerestricting")
+```
+
+<!--Verb offset times-->
+
+```{r}
+verb.offset.times.aggro.jh <- critical.trials.filtered.aggro.jh %>%
+  group_by(image_name, verb_type) %>%
+  slice(1) %>%
+  ungroup() %>%
+  select(image_name, verb_type, duration_of_verb) %>%
+  mutate(relative.verb.offset = duration_of_verb * 1000) %>%
+  select(-duration_of_verb)
+
+trial.level.cumulative.fixation.data.verb.offset.aggro.jh <- cumulative.fixation.windows.grouped.data.aggro.jh %>%
+  left_join(verb.offset.times.aggro.jh, by=c("image_name", "verb_type"))
+```
+
+```{r}
+pre.verb.offset.first.looks.data.aggro.jh <- trial.level.cumulative.fixation.data.verb.offset.aggro.jh %>%
+  group_by(subject_id, image_name, verb_type) %>%
+  filter(t.window < relative.verb.offset) %>%
+  filter(t.window == max(t.window)) %>%
+  filter(object_class %in% c("target.object", "distractor"))
+```
+
+```{r}
+
+E1_model2.aggro.jh <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.aggro.jh)
+#summary(E1_model2.aggro.jh)
+
+E1_model2_tab.aggro.jh = broom.mixed::tidy(E1_model2.aggro.jh) 
+E1_model2_obj.aggro.jh = E1_model2_tab.aggro.jh %>% filter(term == "object_classtarget.object")
+E1_model2_verb.aggro.jh = E1_model2_tab.aggro.jh %>% filter(term == "verb_typerestricting")
+E1_model2_obj_verb.aggro.jh = E1_model2_tab.aggro.jh %>% filter(term == "object_classtarget.object:verb_typerestricting")
+```
+
+<!--Relative to noun onset, when is the first (post-verb) fixation on the target?-->
+
+```{r}
+first.fixation.after.verb.onset.aggro.jh <- critical.trials.filtered.aggro.jh %>%
+  group_by(subject_id, image_name) %>%
+  filter(t >= verb_onset*1000) %>%
+  filter(object_type == "target.object") %>%
+  filter(is.fixating == TRUE) %>%
+  filter(t == min(t)) %>%
+  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
+  mutate(von_relative.t = t - (verb_onset*1000)) %>%
+  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
+  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
+```
+
+```{r}
+first.fixation.after.verb.onset.analysis.data.aggro.jh <- first.fixation.after.verb.onset.aggro.jh %>%
+  ungroup() %>%
+  select(subject_id, image_name, verb_type, duration_of_verb, noun_relative.t) %>%
+  mutate(dur_verb_ms_c = scale(duration_of_verb, scale = FALSE)*1000) #mean-center verb duration
+```
+
+```{r}
+E1_model3.aggro.jh <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data.aggro.jh)
+
+#summary(E1_model3.aggro.jh)
+
+E1_model3_tab.aggro.jh = broom.mixed::tidy(E1_model3.aggro.jh) 
+E1_model3_verb.aggro.jh = E1_model3_tab.aggro.jh %>% filter(term == "verb_typerestricting")
+
+```
+Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

### 2024-06-07 group-a/E1-analysis-comparison-to-JMW23.Rmd
edits to manuscript and exp 1

@@
 
-```{r setup, include=FALSE}
+```{r setup JMW23, include=FALSE}
 library(papaja)
@@
 ```{r import JMW23}
-JMW1_info <- read_csv("group-a/JMW23-data/fyptrialinfo.csv")
+JMW1_info <- read_csv("JMW23-data/fyptrialinfo.csv")
 
-JMW1_latency <- read.delim("group-a/JMW23-data/FYPAKFixationLatenciesPOSTVERB.txt", header = FALSE, sep = ",") #I'll come back to this
+JMW1_latency <- read.delim("JMW23-data/FYPAKFixationLatenciesPOSTVERB.txt", header = TRUE) #it's actual onset times (relative to trial start).
 
-JMW1_data <- read.delim("group-a/JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")
+JMW1_data <- read.delim("JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")
 
@@
 #Now use it to summarize timecourse data
-if(file.exists("group-a/JMW23-data/generated/JMW_cumulative.csv")){
-  JMW_cumu<- read_csv("group-a/JMW23-data/generated/JMW_cumulative.csv")
+if(file.exists("JMW23-data/generated/JMW_cumulative.csv")){
+  JMW_cumu<- read_csv("JMW23-data/generated/JMW_cumulative.csv")
 } else {
@@
 
-  write_csv(JMW_cumu, file="group-a/JMW23-data/generated/JMW_cumulative.csv")
+  write_csv(JMW_cumu, file="JMW23-data/generated/JMW_cumulative.csv")
 }
@@
 
-```{r group cumu fix by object, message=FALSE, warning=FALSE}
+```{r group cumu fix by object jmw, message=FALSE, warning=FALSE}
 JMW_cumu.windows.grouped <- JMW_cumu %>%
@@
 
-```{r collapse cumu fix over trials, message=FALSE, warning=FALSE}
+```{r collapse cumu fix over trials jmw, message=FALSE, warning=FALSE}
 JMW_cumu.windows.grouped.average <- JMW_cumu.windows.grouped %>%
@@
 
-```{r create summary data for spag plot, message=FALSE, warning=FALSE}
+```{r create summary data for spag plot jmw, message=FALSE, warning=FALSE}
 JMW_cumu.summary <- JMW_cumu.windows.grouped.average %>%
@@
 ```
+
 ```{r JMW-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
@@
 
-#AJ: this is where you left off. Everything above should work :)
-JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND, group=interaction(COND, obj_class)))+
-  scale_fill_manual(values=c("white", "black"))+
-  scale_shape_manual(values=c(22,21))+
+JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND))+
   geom_line()+
-  geom_point(size=2)+
+  geom_point(aes(fill = obj_class), size=2, color = "black")+ 
+  scale_fill_manual(name = "Object Type",values=c("white", "black"), labels = c("distractor", "target"))+
+  guides(fill = guide_legend(override.aes=list(shape=21))) +
+  scale_shape_manual(name = "Verb Type", values=c(22,21), labels = c("non-resticting", "restricting"))+
   theme_bw()+
-  theme(panel.grid=element_blank())+
   scale_y_continuous(limits=c(0,1))+
@@
   labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
-  geom_vline(xintercept = mean(JMW1_info$Non.relative))
-#The "Object type" part of the key doesn't actually show which color is which
+  geom_vline(xintercept = mean(JMW1_info$Non.relative)) +
+  theme(panel.grid=element_blank(), legend.position = "none", axis.title.x = element_blank())+
+  ggtitle('James et al. (2023), Exp. 1')
+
+#JMW_spag_fig
 ```
+
+```{r JMW23 latency info}
+#View(JMW1_latency)
+JMW1_latency$COND <- recode(JMW1_latency$COND, "0" = "filler", "1" = "pred", "2" = "neut")
+
+#Merge with data about word onset times to get relative onsets
+JMW1_latency_info <- merge(JMW1_latency, JMW1_info, by.x = "ITEM", by.y = "AID") #in the second spreadsheet, TARGET etc mean the coordinates (now TARGET.y, AGENT.y, etc.).
+in the first, it means the first fixation time (now TARGET.x, etc.)
+
+#Get relative target fixation times
+JMW1_lat <- JMW1_latency_info %>%
+  filter(TARGET.x >= Von) %>%
+  mutate(von_relative_t = TARGET.x - Von,
+         voff_relative_t = TARGET.x - Voff,
+         non_relative_t = TARGET.x - Non)
+
+#hist(JMW1_lat$von_relative_t)
+
+first.fix.avg.JMW <- JMW1_lat %>%
+  group_by(COND) %>%
+  summarize(Verb.on = round.comm(mean(von_relative_t, na.rm = T)),
+            Verb.off = round.comm(mean(voff_relative_t, na.rm = T)),
+            Noun.on = round.comm(mean(non_relative_t, na.rm = T)))
+```

### 2024-06-07 group-a/E1-analysis-replication.Rmd
edits to manuscript and exp 1

@@
 library(papaja)
+library(patchwork)
 source('round.comm.R') #does "commercial" i.e. normal rounding
@@
 
+<!-- I'll need this later to compare results to JMW23-->
+```{r E1-compare-to-JMW23, child = 'E1-analysis-comparison-to-JMW23.Rmd'}
+
+```
+### Remote sample
 <!-- # Import Data -->
@@
 First, we eliminated participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs.
-This resulted in the elimination of `r length(bad.subjects.prop.samples.min)` participants.
+This resulted in the elimination of one participant.
 Second, we excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in an additional `r n.bad.subjects.min - length(bad.subjects.prop.samples.min)` excluded participants.
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:E1-spaghetti-fig).
-
-```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions."}
-
-E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:E1-spaghetti-fig), Panel (b).
+
+```{r make remote spaghetti plot}
+
+E1_spag_fig_remote <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
   geom_line()+
-  geom_point(size=2, aes(fill=object_class, shape=verb_type))+
-  #scale_fill_grey(start=1.0, end=0.0)+
-  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"))+
+  geom_point(aes(fill = object_class), size=2, color = "black")+ 
+  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
   scale_shape_manual(name = "Verb Type", values=c(22,21))+
-  labs(x="Time from Verb Onset (ms)", y="Probability")+#, shape="Verb Type", fill="Object Type")+
-  #geom_line(aes(group=interaction(verb_type, object_class)))+
+  guides(fill = guide_legend(override.aes=list(shape=21))) + #Woo-hoo! Add this line to fix the legend
+  labs(x="Time from Verb Onset (ms)", y="Probability", fill = "object type")+
   theme_bw()+
-  theme(panel.grid=element_blank())+
   scale_y_continuous(limits=c(0,1))+
   scale_x_continuous(expand=c(0.01,0.01))+
-  geom_vline(xintercept = mean(word.dur.avg$Total))
-
-E1_spag_fig
-
-#The "Object type" part of the key doesn't actually show which color is which
+  geom_vline(xintercept = mean(word.dur.avg$Total)) +
+  theme(panel.grid=element_blank(), axis.title.x = element_blank())+
+  ggtitle('Remote sample')
+
+#E1_spag_fig_remote
+
+#The "Object type" part of the key doesn't actually show which color is which. Update: https://github.com/tidyverse/ggplot2/issues/4049
 ```
@@
 #### Pre-noun fixations
-In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+In our first two analyses, we asked whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
@@
 distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
-There were no significant effects, although the critical interaction was in the right direction [bar graph?] (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+There were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+When we did the same, we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 ```
+
 #### First target fixations after verb
-Finally, we address whether participants look to the target faster in the restrictive vs.
+Finally, we addressed whether participants looked to the target faster in the restrictive vs.
 the non-restrictive condition, starting after the onset of the verb.
-[TO-DO: On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition (compared to ) and `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the non-restrictive condition (compared to )].
+On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language].
 Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 E1_first_fix_plot <- ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
@@
 The second set of analyses used more aggressive exclusion criteria.
-First, we eliminated participants with `r prop.samples.threshold.aggro*100` percent of fixations in any ROIs.
+First, we eliminated participants with `r prop.samples.threshold.aggro*100` percent of their fixations or fewer landing in any ROIs.
 This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro)` participants.
@@
 Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
-However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.
-rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).
+In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
+This was not the case in the in-lab sample (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).
+
+### In-lab sample
+```{r E1-analysis-JoshH-lab, child = 'E1-analysis-comparison-to-Hartshorne.Rmd'}
+
+```
+
+```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions."}
+
+E1_panel_fig <- JMW_spag_fig / E1_spag_fig_remote / jh_E1_spag_fig 
+E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect',  heights = unit(6, 'cm'))
+
+```

### 2024-06-07 manuscript.Rmd
edits to manuscript and exp 1

@@
 ---
-title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of 5 “classic” cognitive science experiments"
+title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five “classic” cognitive science experiments"
 shorttitle        : "Webcam eye-tracking paradigms"
@@
 abstract: |
-  ADD LATER
-
-  <!-- https://tinyurl.com/ybremelq -->
+  We tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based eye-tracking format.
+Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js.
+In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment.
+These studies also varied in the type of eye-tracking display, including screens split into halves (Exps.
+3 and 5) or quadrants (Exps.
+2 & 4), or composed scenes with regions of interest that varied in size (Exp.
+1).
+Outcomes were mixed.
+The least successful replication attempt was Exp.
+1; we did not obtain a condition effect in our remote sample (1a), nor in an in-lab follow-up (1b).
+However, the other four experiments were more successful, replicating a blank-screen effect (Exp.
+2), a novelty preference (Exp.
+3), a verb bias effect (Exp.
+4), and a gaze-bias effect in decision-making.
+These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution should be adapted to coarser quadrant or split-half displays.
 
@@
 Since these findings, eye-tracking has become a central method in cognitive science research [for reviews, see @hayhoe2005eye, @richardsonEyeTrackingResearch2004, @rayner1998eye].
-For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning].
-And eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
+For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning], and eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
 
@@
 However, the added convenience comes at the cost of spatial and temporal resolution.
-The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are not yet known.
+The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are the subject of the current study.
 
@@
 In the free viewing task, the eye movements may have been more semantically driven: participants were shown a picture of a human face and asked to look wherever they wanted to on the image.
-Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed.
+Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed relative to the in-lab data.
 The free viewing task replicated previously observed statistical patterns (e.g., more fixations on eyes than mouths).
@@
 Several papers have used the `WebGazer.js` library (via different interfaces) to replicate visual world paradigm studies.
-@slim2022moving used the `PCIbex` online experiment platform [@zehr2018PCIbex] to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair)  [@dijkgraaf2017predicting].
+@slim2022moving used the `PCIbex` online experiment platform [@zehr2018PCIbex] to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen [e.g., a letter, a backpack, a car and a wheelchair;  @dijkgraaf2017predicting].
 When the verb in the sentence was _constraining_ (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was _neutral_ (e.g., Mary steals a letter), as in previous work.
@@
 ^[See discussion at https://github.com/jspsych/jsPsych/discussions/1892]
+
 Finally, @van2023validation used `WebGazer.js` in conjunction with `PsychoJS` to conceptually replicate three paradigms, one which is analogous to @yang2021webcam, another testing the novelty preference (tendency for learners to look more at an object that they have not yet studied), and a visual world paradigm study with 4 objects, similar to @prystauka2023online.
 These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset.
-(They did not address whether there were temporal delays.)
+They did not address whether there were temporal delays.
 
@@
 
-In order to validate the online eyetracking methodology, with the particular configuration known to have the greatest temporal precision, `jsPsych` and a modification of `Webgazer`, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+In order to validate the online eye-tracking methodology, with the particular configuration known to have the greatest temporal precision, `jsPsych` and a modification of `Webgazer`, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
@@
 Second, we include several ''sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
-(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using `jsPsych` or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
+If the effect is real but there is noise from low-accuracy eye-tracking, this correlation should be substantial.
+Third, for two of the studies, we had comparison data collected in-lab either using `jsPsych` or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
 
@@
 
-We chose five high-impact eyetracking studies involving adult subjects.
-(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes).
+We chose five high-impact eye-tracking studies involving adult subjects [for an investigation of WebGazer's validity for developmental research, see @steffan2024validation for a comparison of remote WebGazer and in-lab anticipatory looking effects in 18-27-month-old participants].
+Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "naturalistic" scenes).
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
@@
   `Citations` = c(
-    2007,
-    228,
-    131,
-    472,
-    1073
+    2130,
+    259,
+    134,
+    487,
+    1146
   ),
@@
   studies_table,
-  caption = "Studies selected for replication attempts. Citation counts based on Google Scholar (August 2023).",
+  caption = "Studies selected for replication attempts. Citation counts based on Google Scholar (May 2024).",
   font_size = "small",
@@
 In addition, an in-person replication was conducted for Experiment 1. 
-Information about the sample is given in the corresponding Method sections.
+Information about the sample is given in the Experiment 1 Method sections.
 
@@
 
-We used a fork of the `webgazer.js` library for webcam eyetracking
+We used a fork of the `webgazer.js` library for webcam eye-tracking
 [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript
@@
 
-We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the original and the replication used WebGazer and identical materials and procedures.
+We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the remote and the in-lab replications used WebGazer and identical materials and procedures.
 
@@
 
-## Methods
+## Method
 
@@
 #### In-lab sample
-Forty-nine participants were `r colorize("AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info", "red")`.
+Forty-nine participants completed the study in a lab setting.
+They were recruited via the college subject pool.
+Participants needed to be 18 years of age or older and native speakers of English.
+The study was approved by the Institutional Review Board at Boston College.
 
@@
 response for the critical trials was "yes." Filler trials consisted of
-scenes that looked similar to critical scenes but were paired with
-inappropriate sentences. The correct keyboard response for the filler
+scenes that also contained an agent surrounded by objects as in the critical trials, but corresponding sentences named an object that was not present in the scene.
+The correct keyboard response for the filler
 trials was "no."
@@
 
-### Remote sample
-
 ```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}
@@
 
-<!---```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
-# the presence of this chunk separate from the replication analysis was somehow causing the figures to disappear so I copied the calibration rmd content into the analysis-replication rmd and this solved the problem.
-```--->
-
-### In-lab sample
-
-<!---
-test figure \@ref(fig:test)
-
-```{r test, fig.cap = "test plot"}
-
-plot(cars$speed, cars$dist)
-
-```
---->
-
-```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
-
-```
-
 ## Discussion
+
+Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
+In the remote sample, results were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance; the one exception was in comparing first target fixation latencies across verb conditions, but only when aggressive exclusion criteria were applied to participants (INSERT WHAT THOSE CRITERIA WERE).
+To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting.
+Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
+
+Taken together, the instability of these effects might suggest that this paradigm is not well-suited for web-based eye-tracking.
+Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+The next four experiments test paradigms with more generous ROIs.
+ <!-- bullet points from Ariel
+
+  • Note that the ROIs are only the sizes of the objects in the scene (plus padding), so much smaller than a 5th or 6th of the whole screen (because there are 5 or 6 ROIs per scene; should I figure out how much smaller?)
+
+ • Effect sizes (target adv in eat vs.
+move cond) were uncorrelated with calibration accuracy in both samples, but in the remote sample (but not JH lab), calibration was correlated with target adv in eat condition alone [I need to look into this real quick--I think scatterplots would help]
+
+-->
 
@@
 
-Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the face that they ultimately choose.
+Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the option that they ultimately choose.
 This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
@@
 
-We conducted 5 attempted replication studies using different experimental paradigms from across the cognitive sciences.
+We conducted five attempted replication studies using different experimental paradigms from across the cognitive sciences.
 All were successfully implemented in `jsPsych` using the `webgazer` plugin, but replication success was mixed.
-Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with 5 to 6 ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
-Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [@james2023language].
-A previous conceptual replication of this paradigm using webcam-based eye-tracking [@prystauka2023online] was successful but used a 4-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
+Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with five to six ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
+Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [e.g.
+@james2023language].
+A previous conceptual replication of this paradigm using webcam-based eye-tracking [@prystauka2023online] was successful but used a four-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
 It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
@@
 
- <!-- bullet points from Ariel
- Models testing the condition effect: nothing came out in the two WebET studies (remote and JH’s lab); numerically things are in the right direction but there are so few fixations to ROIs generally (so in spaghetti plots, the noodles top out at 50% or 60% cumulative probability of fixations); and latencies are delayed relative to previous studies.
-
- • Effect sizes (target adv in eat vs.
-move cond) were uncorrelated with calibration accuracy in both samples, but in the remote sample (but not JH lab), calibration was correlated with target adv in eat condition alone
-
- • Note that the ROIs are only the sizes of the objects in the scene (plus padding), so much smaller than a 5th or 6th of the whole screen (because there are 5 or 6 ROIs per scene; should I figure out how much smaller?)-->
-
-Experiment 2 used the 4 quadrants of the participant's screen as ROIs.
+Experiment 2 used the four quadrants of the participant's screen as ROIs.
 As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, participants spontaneously looked to blank ROIs which previously contained to-be-remembered pictures.
@@
 
-Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask2000.
-However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
+Experiment 3 used two large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask2000.
+However, the subtler relationship between gaze duration and recognition memory on Day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
 Calibration quality did not appear to impact this relationship.
@@
 
-Experiment 4 used the 4 quadrants of the participant's screen as ROIs.
+Experiment 4 used the four quadrants of the participant's screen as ROIs.
 As in @ryskinVerbBiasesAre2017, listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input ("Rub the frog with the mitten").
@@
 
-Experiment 5, similar to Experiment 3, used 2 large ROIs (or halves of the display).
-As in @shimojoGazeBiasBoth2003 and in the recent webcam-based replication by @yang2021webcam, participants (qualitatively) look more at the face that they ultimately choose.
-This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
-The gaze patterns remained consistent for participants with better calibration accuracy.
+Experiment 5, similar to Experiment 3, used two large ROIs (or halves of the display).
+As in @shimojoGazeBiasBoth2003 and in the recent webcam-based replication by @yang2021webcam, we saw that participants looked more at the face or shape that they ultimately chose during a judgment task.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this effect was not statistically significant.
 
@@
 However, the smaller the ROIs, the more important the calibration becomes.
-For instance, studies with 4 ROIs may want to exclude data from participants with less than 75% validation accuracy, whereas studies using 2 halves of the display as ROIs may not need to be so conservative.
+For instance, studies with four ROIs may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.
 Studies with smaller ROIs (see Experiment 1) may not be appropriate for webcam eye-tracking in its current form.

### 2024-06-07 manuscript.tex
edits to manuscript and exp 1

@@
 \fi
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \hypersetup{
-  pdftitle={What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments},
+  pdftitle={What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments},
   pdfauthor={Joshua R.
@@
 
-\title{What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments}
+\title{What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments}
 \author{Joshua R.
@@
 \abstract{%
-ADD LATER
+We tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based eye-tracking format.
+Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js.
+In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment.
+These studies also varied in the type of eye-tracking display, including screens split into halves (Exps.
+3 and 5) or quadrants (Exps.
+2 \& 4), or composed scenes with regions of interest that varied in size (Exp.
+1).
+Outcomes were mixed.
+The least successful replication attempt was Exp.
+1; we did not obtain a condition effect in our remote sample (1a), nor in an in-lab follow-up (1b).
+However, the other four experiments were more successful, replicating a blank-screen effect (Exp.
+2), a novelty preference (Exp.
+3), a verb bias effect (Exp.
+4), and a gaze-bias effect in decision-making.
+These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution should be adapted to coarser quadrant or split-half displays.
 }
@@
 Since these findings, eye-tracking has become a central method in cognitive science research Rayner (1998).
-For example, gaze location during natural scene perception is used to test theories of visual attention (e.g., Henderson \& Hayes, 2017).
-And eye-movements during auditory language comprehension, using the ``visual world paradigm,'' demonstrated the context-dependent and incremental nature of language processing (e.g., Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995).
+For example, gaze location during natural scene perception is used to test theories of visual attention (e.g., Henderson \& Hayes, 2017), and eye-movements during auditory language comprehension, using the ``visual world paradigm,'' demonstrated the context-dependent and incremental nature of language processing (e.g., Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995).
 
@@
 Several papers have used the \texttt{WebGazer.js} library (via different interfaces) to replicate visual world paradigm studies.
-Slim and Hartsuiker (2022) used the \texttt{PCIbex} online experiment platform (Zehr \& Schwarz, 2018) to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen (e.g., a letter, a backpack, a car and a wheelchair) (Dijkgraaf, Hartsuiker, \& Duyck, 2017).
+Slim and Hartsuiker (2022) used the \texttt{PCIbex} online experiment platform (Zehr \& Schwarz, 2018) to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen {[}e.g., a letter, a backpack, a car and a wheelchair; Dijkgraaf, Hartsuiker, and Duyck (2017){]}.
 When the verb in the sentence was \emph{constraining} (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was \emph{neutral} (e.g., Mary steals a letter), as in previous work.
@@
 \footnote{See discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}}
+
 Finally, Van der Cruyssen et al.
@@
 These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset.
-(They did not address whether there were temporal delays.)
+They did not address whether there were temporal delays.
 
@@
 
-\hypertarget{present-work}{%
-\section{Present work}\label{present-work}}
-
-In order to validate the online eyetracking methodology, with the particular configuration known to have the greatest temporal precision, \texttt{jsPsych} and a modification of \texttt{Webgazer}, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+\section{Present work}\label{present-work}
+
+In order to validate the online eye-tracking methodology, with the particular configuration known to have the greatest temporal precision, \texttt{jsPsych} and a modification of \texttt{Webgazer}, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
 
-\hypertarget{selection-of-studies}{%
-\subsection{Selection of Studies}\label{selection-of-studies}}
+\subsection{Selection of Studies}\label{selection-of-studies}
 
@@
 Second, we include several `'sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
-(If the effect is real but there is noise from low-accuracy eyetracking, this correlation should be substantial.) Third, for two of the studies, we had comparison data collected in-lab either using \texttt{jsPsych} or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
-
-We chose five high-impact eyetracking studies involving adult subjects.
-(Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``natural'' scenes).
+If the effect is real but there is noise from low-accuracy eye-tracking, this correlation should be substantial.
+Third, for two of the studies, we had comparison data collected in-lab either using \texttt{jsPsych} or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
+
+We chose five high-impact eye-tracking studies involving adult subjects (for an investigation of WebGazer's validity for developmental research, see Steffan et al., 2024 for a comparison of remote WebGazer and in-lab anticipatory looking effects in 18-27-month-old participants).
+Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``naturalistic'' scenes).
 As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
@@
 
-\caption{\label{tab:studies-table}Studies selected for replication attempts. Citation counts based on Google Scholar (August 2023).}
+\caption{\label{tab:studies-table}Studies selected for replication attempts. Citation counts based on Google Scholar (May 2024).}
 
@@
 \midrule
-Altmann \& Kamide, 1999 & Psycholinguistics & Natural Scenes & 2,007\\
-Johansson \& Johansson, 2014 & Memory & Four Quadrants & 228\\
-Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 131\\
-Snedeker \& Trueswell, 2004 & Psycholinguistics & Four Quadrants & 472\\
-Shimojo et al., 2003 & Decision Making & Two Halves & 1,073\\
+Altmann \& Kamide, 1999 & Psycholinguistics & Natural Scenes & 2,130\\
+Johansson \& Johansson, 2014 & Memory & Four Quadrants & 259\\
+Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 134\\
+Snedeker \& Trueswell, 2004 & Psycholinguistics & Four Quadrants & 487\\
+Shimojo et al., 2003 & Decision Making & Two Halves & 1,146\\
 \bottomrule
@@
 
-\hypertarget{general-methods}{%
-\section{General Methods}\label{general-methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\section{General Methods}\label{general-methods}
+
+\subsection{Participants}\label{participants}
 
@@
 In addition, an in-person replication was conducted for Experiment 1.
-Information about the sample is given in the corresponding Method sections.
+Information about the sample is given in the Experiment 1 Method sections.
 
@@
 
-\hypertarget{equipment}{%
-\subsection{Equipment}\label{equipment}}
-
-We used a fork of the \texttt{webgazer.js} library for webcam eyetracking
+\subsection{Equipment}\label{equipment}
+
+We used a fork of the \texttt{webgazer.js} library for webcam eye-tracking
 (Papoutsaki et al., 2016), implemented in \texttt{jsPsych}, a Javascript
@@
 
-\hypertarget{eye-tracking-calibration-and-validation}{%
-\subsection{Eye-tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}}
+\subsection{Eye-tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}
 
@@
 
-\hypertarget{pre-registration}{%
-\subsection{Pre-registration}\label{pre-registration}}
+\subsection{Pre-registration}\label{pre-registration}
 
@@
 
-\hypertarget{data-pre-processing}{%
-\subsection{Data pre-processing}\label{data-pre-processing}}
-
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.3; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
-
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
+\subsection{Data pre-processing}\label{data-pre-processing}
+
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Version 1.8.0; Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
+
+\section{Experiment 1}\label{experiment-1}
 
@@
 
-We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the original and the replication used WebGazer and identical materials and procedures.
-
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
+We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the remote and the in-lab replications used WebGazer and identical materials and procedures.
+
+\subsection{Method}\label{method}
 
@@
 
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
-
-\hypertarget{remote-sample}{%
-\paragraph{Remote sample}\label{remote-sample}}
+\subsubsection{Participants}\label{participants-1}
+
+\paragraph{Remote sample}\label{remote-sample}
 
@@
 
-\hypertarget{in-lab-sample}{%
-\paragraph{In-lab sample}\label{in-lab-sample}}
-
-Forty-nine participants were \textcolor{red}{AJ: help. Insert how they were compensated, relevant IRB/funding stuff, any other info}.
-
-\hypertarget{procedure}{%
-\subsubsection{Procedure}\label{procedure}}
+\paragraph{In-lab sample}\label{in-lab-sample}
+
+Forty-nine participants completed the study in a lab setting.
+They were recruited via the college subject pool.
+Participants needed to be 18 years of age or older and native speakers of English.
+The study was approved by the Institutional Review Board at Boston College.
+
+\subsubsection{Procedure}\label{procedure}
 
@@
 
-\hypertarget{materials-design}{%
-\subsubsection{Materials \& Design}\label{materials-design}}
+\subsubsection{Materials \& Design}\label{materials-design}
 
@@
 response for the critical trials was ``yes.'' Filler trials consisted of
-scenes that looked similar to critical scenes but were paired with
-inappropriate sentences. The correct keyboard response for the filler
+scenes that also contained an agent surrounded by objects as in the critical trials, but corresponding sentences named an object that was not present in the scene.
+The correct keyboard response for the filler
 trials was ``no.''
@@
 
-\hypertarget{data-pre-processing-and-analysis}{%
-\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}}
+\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}
 
@@
 
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-\hypertarget{remote-sample-1}{%
-\subsubsection{Remote sample}\label{remote-sample-1}}
-
-\hypertarget{minimal-exclusion}{%
-\paragraph{Minimal Exclusion}\label{minimal-exclusion}}
+\subsection{Results}\label{results}
+
+\subsubsection{Remote sample}\label{remote-sample-1}
+
+\paragraph{Minimal Exclusion}\label{minimal-exclusion}
 
@@
 First, we eliminated participants with 0 percent of fixations in any ROIs.
-This resulted in the elimination of 1 participants.
+This resulted in the elimination of one participant.
 Second, we excluded participants with validation accuracy under 10 percent, resulting in an additional 5 excluded participants.
@@
 
-\hypertarget{cumulative-fixation-probabilities}{%
-\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities}}
+\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities}
 
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}.
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}, Panel (b).
+
+\paragraph{Pre-noun fixations}\label{pre-noun-fixations}
+
+In our first two analyses, we asked whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
+We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
+There were no significant effects, although the critical interaction was in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.15).
+
+\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}
+
+Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+When we did the same, we again saw that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
+
+\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}
+
+Finally, we addressed whether participants looked to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
+On average, participants looked to the target 349 ms after the noun onset in the restrictive condition James, Minnihan, \& Watson (2023) and 452 ms after the noun onset in the non-restrictive condition James et al.
+(2023).
+Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
+
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
+
+\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}
+
+The second set of analyses used more aggressive exclusion criteria.
+First, we eliminated participants with 20 percent of their fixations or fewer landing in any ROIs.
+This resulted in the elimination of 15 participants.
+Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 35 participants.
+The following analyses included 22 participants.
+
+We tested the same three models under these more aggressive exclusion criteria.
+The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction was not statistically significant (Pre-noun-onset window: \emph{b} = 0.07, \emph{SE} = 0.06, \emph{p}=0.23; Pre-verb-offset window: \emph{b} = 0.05, \emph{SE} = 0.05, \emph{p}=0.28).
+However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (\emph{b} = -193.35, \emph{SE} = 96.33, \emph{p}=0.05).
+
+\paragraph{Calibration}\label{calibration}
+
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
+Calibration quality varied widely, ranging from 3.16\% to 98.87\%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
+Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.04, \emph{p} = 0.78.
+In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
+This was not the case in the in-lab sample (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
+
+\subsubsection{In-lab sample}\label{in-lab-sample-1}
+
+\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}
+
+As in the remote sample, we checked whether there were participants with 0 percent of fixations in any ROIs and there were none.
+We then excluded participants with validation accuracy under 10 percent, resulting in 2 excluded participants.
+The following analyses included 47 participants.
+
+\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}
+
+For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
+This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}, Panel (c).
+
+\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}
+
+In line with the previous analyses of the remote data, we asked whether participants looked more to the target than to the distractor object during the predictive time window, depending upon the verb condition.
+The first model constrained the predictive window to the time before the onset of the target noun.
+We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and scenes (with no covariance between random effects because the model cannot converge with full covariance matrix).
+Unlike the remote sample, there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (\emph{b} = 0.10, \emph{SE} = 0.03, \emph{p}=0.01).
+Also unlike the remote sample, the critical interaction was not in the expected direction, although it was also not statistically significant (\emph{b} = -0.05, \emph{SE} = 0.05, \emph{p}=0.25).
+
+\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}
+
+Altmann \& Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+When we did the same, we again saw that the critical interaction is not significant nor in the expected direction (\emph{b} = -0.06, \emph{SE} = 0.04, \emph{p}=0.17).
+
+\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}
+
+Finally, we addressed whether participants looked to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
+On average, participants looked to the target 397 ms after the noun onset in the restrictive condition and 376 ms after the noun onset in the non-restrictive condition.
+As in the remote sample, the latencies are overall slower than in results published by Altmann \& Kamide (1999) and James et al.~(2023).
+Unlike in the remote sample, however, the difference is in the unexpected direction, such that participants looked to the target faster in the non-restrictive condition.
+
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (\emph{b} = 21.70, \emph{SE} = 115.32, \emph{p}=0.85).
+Effects of verb duration and its interaction with condition were also not statistically significant (duration: \emph{b} = -0.58, \emph{SE} = 0.55, \emph{p}=0.30; interaction: \emph{b} = -0.49, \emph{SE} = 0.96, \emph{p}=0.61 )
+
+\paragraph{Calibration}\label{calibration-1}
+
+As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from 5.13\% to 97.89\%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's \emph{r} = -0.24, \emph{p} = 0.11; pre-verb-offset: Pearson's \emph{r} = -0.19, \emph{p} = 0.20; first fixation: Pearson's \emph{r} = -0.12, \emph{p} = 0.41.
+However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = -0.16, \emph{p} = 0.29).
+
+\paragraph{Aggressive Exclusion}\label{aggressive-exclusion-1}
+
+The second set of analyses used more aggressive exclusion criteria.
+First, we eliminated participants with 20 percent of fixations or fewer landing in any ROIs.
+This resulted in the elimination of 7 participants.
+Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 23 participants.
+The following analyses included 26 participants.
+
+Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: \emph{b} = -0.08, \emph{SE} = 0.06, \emph{p}=0.15; Pre-verb-offset window, verb x object interaction: \emph{b} = -0.07, \emph{SE} = 0.05, \emph{p}=0.16; Verb effect on first target fixation: \emph{b} = 6.40, \emph{SE} = 97.92, \emph{p}=0.95).
 
@@
 
-\hypertarget{pre-noun-fixations}{%
-\paragraph{Pre-noun fixations}\label{pre-noun-fixations}}
-
-In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
-The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
-We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
-There were no significant effects, although the critical interaction was in the right direction {[}bar graph?{]} (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.15).
-
-\hypertarget{pre-verb-offset-fixations}{%
-\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}}
-
-Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
-
-\hypertarget{first-target-fixations-after-verb}{%
-\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}}
-
-Finally, we address whether participants look to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
-{[}TO-DO: On average, participants looked to the target 349 ms after the noun onset in the restrictive condition (compared to ) and 349 ms after the noun onset in the non-restrictive condition (compared to ){]}.
-Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
-
-We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
-There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
-
-\hypertarget{aggressive-exclusion}{%
-\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}}
-
-The second set of analyses used more aggressive exclusion criteria.
-First, we eliminated participants with 20 percent of fixations in any ROIs.
-This resulted in the elimination of 15 participants.
-Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 35 participants.
-The following analyses included 22 participants.
-
-We tested the same three models under these more aggressive exclusion criteria.
-The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction was not statistically significant (Pre-noun-onset window: \emph{b} = 0.07, \emph{SE} = 0.06, \emph{p}=0.23; Pre-verb-offset window: \emph{b} = 0.05, \emph{SE} = 0.05, \emph{p}=0.28).
-However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (\emph{b} = -193.35, \emph{SE} = 96.33, \emph{p}=0.05).
-
-\hypertarget{calibration}{%
-\paragraph{Calibration}\label{calibration}}
-
-Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
-Calibration quality varied widely, ranging from 3.16\% to 98.87\%.
-
-We tested whether a participant's calibration quality was correlated with their effect size.
-There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
-Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.04, \emph{p} = 0.78.
-However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
-
-\hypertarget{in-lab-sample-1}{%
-\subsubsection{In-lab sample}\label{in-lab-sample-1}}
-
-\hypertarget{minimal-exclusion-1}{%
-\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}}
-
-As in the remote sample, we checked whether there were participants with 0 percent of fixations in any ROIs and there were none.
-We then excluded participants with validation accuracy under 10 percent, resulting in 2 excluded participants.
-The following analyses included 47 participants.
-
-\hypertarget{cumulative-fixation-probabilities-1}{%
-\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}}
-
-For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later.
-This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-JH-spaghetti-fig}.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E1-JH-spaghetti-fig-1.pdf}
-\caption{\label{fig:E1-JH-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions.}
-\end{figure}
-
-\hypertarget{pre-noun-fixations-1}{%
-\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}}
-
-In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
-The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
-We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
-There were no significant effects, although the critical interaction was in the right direction {[}bar graph?{]} (\emph{b} = -0.05, \emph{SE} = 0.05, \emph{p}=0.25).
-
-\hypertarget{pre-verb-offset-fixations-1}{%
-\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}}
-
-Altmann \& Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (\emph{b} = -0.06, \emph{SE} = 0.04, \emph{p}=0.17).
-
-\hypertarget{first-target-fixations-after-verb-1}{%
-\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}}
-
-Finally, we address whether participants look to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
-{[}TO-DO: On average, participants looked to the target X ms after (AK's Table 1)\ldots, I'll also want to say the lengths of the verbs.
-AK's Table 2{]} We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
-There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = 21.70, \emph{SE} = 115.32, \emph{p}=0.85).
-
-\hypertarget{calibration-1}{%
-\paragraph{Calibration}\label{calibration-1}}
-
-As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from 5.13\% to 97.89\%.
-
-We tested whether a participant's calibration quality was correlated with their effect size.
-Across the three condition effects of interest, calibration quality was not significantly correlated (Effect 1 (pre-noun-onset): Pearson's \emph{r} = -0.24, \emph{p} = 0.11, Effect 2 (pre-verb-offset): Pearson's \emph{r} = -0.19, \emph{p} = 0.20, Effect 3 (first fixation): Pearson's \emph{r} = -0.12, \emph{p} = 0.41.
-However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = -0.16, \emph{p} = 0.29).
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
+\subsection{Discussion}\label{discussion}
+
+Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
+In the remote sample, results were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance; the one exception was in comparing first target fixation latencies across verb conditions, but only when aggressive exclusion criteria were applied to participants (INSERT WHAT THOSE CRITERIA WERE).
+To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting.
+Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
+
+Taken together, the instability of these effects might suggest that this paradigm is not well-suited for web-based eye-tracking.
+Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+The next four experiments test paradigms with more generous ROIs.
+
+\section{Experiment 2}\label{experiment-2}
 
@@
 
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
+\subsection{Method}\label{method-1}
 
@@
 
-\hypertarget{participants-2}{%
-\subsubsection{Participants}\label{participants-2}}
+\subsubsection{Participants}\label{participants-2}
 
@@
 
-\hypertarget{procedure-1}{%
-\subsubsection{Procedure}\label{procedure-1}}
+\subsubsection{Procedure}\label{procedure-1}
 
@@
 \begin{figure}
-\includegraphics[width=5.47in]{group-b/E2-example-figure} \caption{Example trial from Experiment 2.}\label{fig:E2-example-trial}
+\centering
+\includegraphics{group-b/E2-example-figure.jpeg}
+\caption{\label{fig:E2-example-trial}Example trial from Experiment 2.}
 \end{figure}
@@
 
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-\hypertarget{replication}{%
-\subsubsection{Replication}\label{replication}}
+\subsection{Results}\label{results-1}
+
+\subsubsection{Replication}\label{replication}
 
@@
 
-\hypertarget{calibration-2}{%
-\subsubsection{Calibration}\label{calibration-2}}
+\subsubsection{Calibration}\label{calibration-2}
 
@@
 
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
+\subsection{Discussion}\label{discussion-1}
 
@@
 
-\hypertarget{experiment-3}{%
-\section{Experiment 3}\label{experiment-3}}
+\section{Experiment 3}\label{experiment-3}
 
@@
 
-\hypertarget{methods-2}{%
-\subsection{Methods}\label{methods-2}}
+\subsection{Method}\label{method-2}
 
@@
 
-\hypertarget{participants-3}{%
-\subsubsection{Participants}\label{participants-3}}
+\subsubsection{Participants}\label{participants-3}
 
@@
 
-\hypertarget{procedure-2}{%
-\subsubsection{Procedure}\label{procedure-2}}
+\subsubsection{Procedure}\label{procedure-2}
 
@@
 \begin{figure}
-\includegraphics[width=3.41in]{group-c/E3-example-figure} \caption{Schematic of the design of Experiment 3}\label{fig:E3-design-schematic}
-\end{figure}
-
-\hypertarget{materials}{%
-\subsubsection{Materials}\label{materials}}
+\centering
+\includegraphics{group-c/E3-example-figure.jpeg}
+\caption{\label{fig:E3-design-schematic}Schematic of the design of Experiment 3}
+\end{figure}
+
+\subsubsection{Materials}\label{materials}
 
@@
 
-\hypertarget{results-2}{%
-\subsection{Results}\label{results-2}}
-
-\hypertarget{day-1}{%
-\paragraph{Day 1}\label{day-1}}
+\subsection{Results}\label{results-2}
+
+\paragraph{Day 1}\label{day-1}
 
@@
 
-\hypertarget{day-2}{%
-\paragraph{Day 2}\label{day-2}}
+\paragraph{Day 2}\label{day-2}
 
@@
 
-\hypertarget{effects-of-rois}{%
-\subsubsection{Effects of ROIs}\label{effects-of-rois}}
+\subsubsection{Effects of ROIs}\label{effects-of-rois}
 
@@
 
-\hypertarget{looking-scores}{%
-\paragraph{Looking Scores}\label{looking-scores}}
+\paragraph{Looking Scores}\label{looking-scores}
 
@@
 
-\hypertarget{correlations-with-day-2-performance}{%
-\paragraph{Correlations with Day 2 Performance}\label{correlations-with-day-2-performance}}
+\paragraph{Correlations with Day 2 Performance}\label{correlations-with-day-2-performance}
 
@@
 
-\hypertarget{calibration-3}{%
-\subsubsection{Calibration}\label{calibration-3}}
-
-\hypertarget{calibration-accuracy}{%
-\paragraph{Calibration Accuracy}\label{calibration-accuracy}}
+\subsubsection{Calibration}\label{calibration-3}
+
+\paragraph{Calibration Accuracy}\label{calibration-accuracy}
 
@@
 
-\hypertarget{correlation-with-effects}{%
-\paragraph{Correlation with Effects}\label{correlation-with-effects}}
+\paragraph{Correlation with Effects}\label{correlation-with-effects}
 
@@
 
-\hypertarget{discussion-2}{%
-\subsection{Discussion}\label{discussion-2}}
+\subsection{Discussion}\label{discussion-2}
 
@@
 
-\hypertarget{experiment-4}{%
-\section{Experiment 4}\label{experiment-4}}
+\section{Experiment 4}\label{experiment-4}
 
@@
 
-\hypertarget{methods-3}{%
-\subsection{Methods}\label{methods-3}}
+\subsection{Method}\label{method-3}
 
@@
 
-\hypertarget{participants-4}{%
-\subsubsection{Participants}\label{participants-4}}
+\subsubsection{Participants}\label{participants-4}
 
@@
 
-\hypertarget{procedure-3}{%
-\subsubsection{Procedure}\label{procedure-3}}
+\subsubsection{Procedure}\label{procedure-3}
 
@@
 \begin{figure}
-\includegraphics[width=4.5in]{group-d/E4-example-figure} \caption{An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}\label{fig:E4-example-trial}
-\end{figure}
-
-\hypertarget{materials-1}{%
-\subsubsection{Materials}\label{materials-1}}
+\centering
+\includegraphics{group-d/E4-example-figure.jpeg}
+\caption{\label{fig:E4-example-trial}An example of a critical trial from Experiment 4 for the sentence ``Rub the butterfly with the crayon.'' The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}
+\end{figure}
+
+\subsubsection{Materials}\label{materials-1}
 
@@
 
-\hypertarget{results-3}{%
-\subsection{Results}\label{results-3}}
-
-\hypertarget{replication-1}{%
-\subsubsection{Replication}\label{replication-1}}
+\subsection{Results}\label{results-3}
+
+\subsubsection{Replication}\label{replication-1}
 
@@
 
-\hypertarget{comparison-to-in-lab-data}{%
-\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}}
+\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}
 
@@
 
-\hypertarget{calibration-4}{%
-\subsubsection{Calibration}\label{calibration-4}}
+\subsubsection{Calibration}\label{calibration-4}
 
@@
 
-\hypertarget{effects-of-rois-1}{%
-\subsubsection{Effects of ROIs}\label{effects-of-rois-1}}
+\subsubsection{Effects of ROIs}\label{effects-of-rois-1}
 
@@
 
-\hypertarget{discussion-3}{%
-\subsection{Discussion}\label{discussion-3}}
+\subsection{Discussion}\label{discussion-3}
 
@@
 
-\hypertarget{experiment-5}{%
-\section{Experiment 5}\label{experiment-5}}
+\section{Experiment 5}\label{experiment-5}
 
@@
 
-\hypertarget{methods-4}{%
-\subsection{Methods}\label{methods-4}}
+\subsection{Method}\label{method-4}
 
@@
 
-\hypertarget{participants-5}{%
-\subsubsection{Participants}\label{participants-5}}
+\subsubsection{Participants}\label{participants-5}
 
@@
 
-\hypertarget{procedure-and-design}{%
-\subsubsection{Procedure and Design}\label{procedure-and-design}}
+\subsubsection{Procedure and Design}\label{procedure-and-design}
 
@@
 \begin{figure}
-\includegraphics[width=3.41in]{group-e/E5-example-figure} \caption{An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}\label{fig:E5-example-trial}
-\end{figure}
-
-\hypertarget{materials-and-norming}{%
-\subsubsection{Materials and Norming}\label{materials-and-norming}}
+\centering
+\includegraphics{group-e/E5-example-figure.jpeg}
+\caption{\label{fig:E5-example-trial}An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}
+\end{figure}
+
+\subsubsection{Materials and Norming}\label{materials-and-norming}
 
@@
 
-\hypertarget{data-analysis}{%
-\subsubsection{Data analysis}\label{data-analysis}}
+\subsubsection{Data analysis}\label{data-analysis}
 
@@
 
-\hypertarget{results-4}{%
-\subsection{Results}\label{results-4}}
+\subsection{Results}\label{results-4}
 
@@
 
-\hypertarget{calibration-5}{%
-\subsubsection{Calibration}\label{calibration-5}}
+\subsubsection{Calibration}\label{calibration-5}
 
@@
 
-\hypertarget{effects-of-rois-2}{%
-\subsubsection{Effects of ROIs}\label{effects-of-rois-2}}
+\subsubsection{Effects of ROIs}\label{effects-of-rois-2}
 
@@
 
-\hypertarget{discussion-4}{%
-\subsection{Discussion}\label{discussion-4}}
-
-Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the face that they ultimately choose.
+\subsection{Discussion}\label{discussion-4}
+
+Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the option that they ultimately choose.
 This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
@@
 
-\hypertarget{general-discussion}{%
-\section{General Discussion}\label{general-discussion}}
-
-We conducted 5 attempted replication studies using different experimental paradigms from across the cognitive sciences.
+\section{General Discussion}\label{general-discussion}
+
+We conducted five attempted replication studies using different experimental paradigms from across the cognitive sciences.
 All were successfully implemented in \texttt{jsPsych} using the \texttt{webgazer} plugin, but replication success was mixed.
-Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with 5 to 6 ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
-Both attempts to replicate Altmann and Kamide (1999) were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking (James, Minnihan, \& Watson, 2023).
-A previous conceptual replication of this paradigm using webcam-based eye-tracking (Prystauka et al., 2023) was successful but used a 4-quadrant visual world paradigm, rather than the ``naturalistic'' scenes used in the original study and in the current replication attempts.
+Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with five to six ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
+Both attempts to replicate Altmann and Kamide (1999) were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking (e.g.
+James et al., 2023).
+A previous conceptual replication of this paradigm using webcam-based eye-tracking (Prystauka et al., 2023) was successful but used a four-quadrant visual world paradigm, rather than the ``naturalistic'' scenes used in the original study and in the current replication attempts.
 It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
@@
 
-Experiment 2 used the 4 quadrants of the participant's screen as ROIs.
+Experiment 2 used the four quadrants of the participant's screen as ROIs.
 As in Johansson and Johansson (2014) and Spivey and Geng (2001), participants spontaneously looked to blank ROIs which previously contained to-be-remembered pictures.
@@
 
-Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in Manns et al.
+Experiment 3 used two large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in Manns et al.
 (2000).
-However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
+However, the subtler relationship between gaze duration and recognition memory on Day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
 Calibration quality did not appear to impact this relationship.
@@
 
-Experiment 4 used the 4 quadrants of the participant's screen as ROIs.
+Experiment 4 used the four quadrants of the participant's screen as ROIs.
 As in Ryskin et al.
@@
 
-Experiment 5, similar to Experiment 3, used 2 large ROIs (or halves of the display).
+Experiment 5, similar to Experiment 3, used two large ROIs (or halves of the display).
 As in Shimojo et al.
-(2003) and in the recent webcam-based replication by Yang and Krajbich (2021), participants (qualitatively) look more at the face that they ultimately choose.
-This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
-The gaze patterns remained consistent for participants with better calibration accuracy.
+(2003) and in the recent webcam-based replication by Yang and Krajbich (2021), we saw that participants looked more at the face or shape that they ultimately chose during a judgment task.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this effect was not statistically significant.
 
@@
 However, the smaller the ROIs, the more important the calibration becomes.
-For instance, studies with 4 ROIs may want to exclude data from participants with less than 75\% validation accuracy, whereas studies using 2 halves of the display as ROIs may not need to be so conservative.
+For instance, studies with four ROIs may want to exclude data from participants with less than 75\% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.
 Studies with smaller ROIs (see Experiment 1) may not be appropriate for webcam eye-tracking in its current form.
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-altmannIncrementalInterpretationVerbs1999}{}}%
+\bibitem[\citeproctext]{ref-altmannIncrementalInterpretationVerbs1999}
 Altmann, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-anwyl2020gorilla}{}}%
+\bibitem[\citeproctext]{ref-anwyl2020gorilla}
 Anwyl-Irvine, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+\bibitem[\citeproctext]{ref-R-papaja}
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\vadjust pre{\hypertarget{ref-banki2022comparing}{}}%
+\bibitem[\citeproctext]{ref-banki2022comparing}
 Bánki, A., Eccher, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+\bibitem[\citeproctext]{ref-R-tinylabels}
 Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
+\bibitem[\citeproctext]{ref-R-lme4}
 Bates, D., Mächler, M., Bolker, B., \& Walker, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+\bibitem[\citeproctext]{ref-R-Matrix}
 Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-broom.mixed}{}}%
+\bibitem[\citeproctext]{ref-R-broom.mixed}
 Bolker, B., \& Robinson, D. (2020). \emph{Broom.mixed: Tidying methods for mixed models}. Retrieved from \url{https://CRAN.R-project.org/package=broom.mixed}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-shiny}{}}%
+\bibitem[\citeproctext]{ref-R-shiny}
 Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-deleeuwJsPsychJavaScriptLibrary2015}{}}%
+\bibitem[\citeproctext]{ref-deleeuwJsPsychJavaScriptLibrary2015}
 de Leeuw, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-degen2021seeing}{}}%
+\bibitem[\citeproctext]{ref-degen2021seeing}
 Degen, J., Kursat, L., \& Leigh, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-dijkgraaf2017predicting}{}}%
+\bibitem[\citeproctext]{ref-dijkgraaf2017predicting}
 Dijkgraaf, A., Hartsuiker, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hayhoe2005eye}{}}%
+\bibitem[\citeproctext]{ref-hayhoe2005eye}
 Hayhoe, M., \& Ballard, D. (2005). Eye movements in natural behavior. \emph{Trends in Cognitive Sciences}, \emph{9}(4), 188--194.
 
-\leavevmode\vadjust pre{\hypertarget{ref-henderson2017meaning}{}}%
+\bibitem[\citeproctext]{ref-henderson2017meaning}
 Henderson, J. M., \& Hayes, T. R. (2017). Meaning-based guidance of attention in scenes as revealed by meaning maps. \emph{Nature Human Behaviour}, \emph{1}(10), 743--747.
 
-\leavevmode\vadjust pre{\hypertarget{ref-henninger2021lab}{}}%
+\bibitem[\citeproctext]{ref-henninger2021lab}
 Henninger, F., Shevchenko, Y., Mertens, U. K., Kieslich, P. J., \& Hilbig, B. E. (2021). Lab. Js: A free, open, online study builder. \emph{Behavior Research Methods}, 1--18.
 
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2010weirdest}{}}%
+\bibitem[\citeproctext]{ref-henrich2010weirdest}
 Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83.
 
-\leavevmode\vadjust pre{\hypertarget{ref-james2023language}{}}%
+\bibitem[\citeproctext]{ref-james2023language}
 James, A. N., Minnihan, C. J., \& Watson, D. G. (2023). Language experience predicts eye movements during online auditory comprehension. \emph{Journal of Cognition}, \emph{6}(1).
 
-\leavevmode\vadjust pre{\hypertarget{ref-johanssonLookHereEye2014}{}}%
+\bibitem[\citeproctext]{ref-johanssonLookHereEye2014}
 Johansson, R., \& Johansson, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-krajbich2010visual}{}}%
+\bibitem[\citeproctext]{ref-krajbich2010visual}
 Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.
 
-\leavevmode\vadjust pre{\hypertarget{ref-kukona2014lexical}{}}%
+\bibitem[\citeproctext]{ref-kukona2014lexical}
 Kukona, A., Cho, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lmerTest}{}}%
+\bibitem[\citeproctext]{ref-R-lmerTest}
 Kuznetsova, A., Brockhoff, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mannsVisualPairedcomparisonTask2000}{}}%
+\bibitem[\citeproctext]{ref-mannsVisualPairedcomparisonTask2000}
 Manns, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-jsonlite}{}}%
+\bibitem[\citeproctext]{ref-R-jsonlite}
 Ooms, J. (2014). The jsonlite package: A practical and consistent mapping between JSON data and r objects. \emph{arXiv:1403.2805 {[}Stat.CO{]}}. Retrieved from \url{https://arxiv.org/abs/1403.2805}
 
-\leavevmode\vadjust pre{\hypertarget{ref-papoutsaki2016webgazer}{}}%
+\bibitem[\citeproctext]{ref-papoutsaki2016webgazer}
 Papoutsaki, A., Sangkloy, P., Laskey, J., Daskalova, N., Huang, J., \& Hays, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-prystauka2023online}{}}%
+\bibitem[\citeproctext]{ref-prystauka2023online}
 Prystauka, Y., Altmann, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+\bibitem[\citeproctext]{ref-R-base}
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-rayner1998eye}{}}%
+\bibitem[\citeproctext]{ref-rayner1998eye}
 Rayner, K. (1998). Eye movements in reading and information processing: 20 years of research. \emph{Psychological Bulletin}, \emph{124}(3), 372.
 
-\leavevmode\vadjust pre{\hypertarget{ref-richardsonEyeTrackingResearch2004}{}}%
+\bibitem[\citeproctext]{ref-richardsonEyeTrackingResearch2004}
 Richardson, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ryskinVerbBiasesAre2017}{}}%
+\bibitem[\citeproctext]{ref-ryskinVerbBiasesAre2017}
 Ryskin, R., Qi, Z., Duff, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ryskin2023real}{}}%
+\bibitem[\citeproctext]{ref-ryskin2023real}
 Ryskin, R., Salinas, M., Piantadosi, S., \& Gibson, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-semmelmann2018online}{}}%
+\bibitem[\citeproctext]{ref-semmelmann2018online}
 Semmelmann, K., \& Weigelt, S. (2018). Online webcam-based eye tracking in cognitive science: A first look. \emph{Behavior Research Methods}, \emph{50}, 451--465.
 
-\leavevmode\vadjust pre{\hypertarget{ref-shimojoGazeBiasBoth2003}{}}%
+\bibitem[\citeproctext]{ref-shimojoGazeBiasBoth2003}
 Shimojo, S., Simion, C., Shimojo, E., \& Scheier, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
+\bibitem[\citeproctext]{ref-simonsohn2015}
 Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. \emph{Psychological Science}, \emph{26}(5), 559--569. \url{https://doi.org/10.1177/0956797614567341}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-afex}{}}%
+\bibitem[\citeproctext]{ref-R-afex}
 Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
 
-\leavevmode\vadjust pre{\hypertarget{ref-slim2022moving}{}}%
+\bibitem[\citeproctext]{ref-slim2022moving}
 Slim, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-snedekerDevelopingConstraintsParsing2004a}{}}%
+\bibitem[\citeproctext]{ref-snedekerDevelopingConstraintsParsing2004a}
 Snedeker, J., \& Trueswell, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-spiveyOculomotorMechanismsActivated2001}{}}%
+\bibitem[\citeproctext]{ref-spiveyOculomotorMechanismsActivated2001}
 Spivey, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sun2020another}{}}%
+\bibitem[\citeproctext]{ref-steffan2024validation}
+Steffan, A., Zimmer, L., Arias-Trejo, N., Bohn, M., Dal Ben, R., Flores-Coronado, M.
+A., et al.others.
+(2024).
+Validation of an open source, remote web-based eye-tracking method (WebGazer) for research in early childhood.
+\emph{Infancy}, \emph{29}(1), 31--55.
+
+\bibitem[\citeproctext]{ref-sun2020another}
 Sun, C., \& Breheny, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tanenhaus1995}{}}%
+\bibitem[\citeproctext]{ref-tanenhaus1995}
 Tanenhaus, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-van2023validation}{}}%
+\bibitem[\citeproctext]{ref-van2023validation}
 Van der Cruyssen, I., Ben-Shakhar, G., Pertzov, Y., Guy, N., Cabooter, Q., Gunschera, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vos2022comparing}{}}%
+\bibitem[\citeproctext]{ref-vos2022comparing}
 Vos, M., Minor, S., \& Ramchand, G. C. (2022). Comparing infrared and webcam eye tracking in the visual world paradigm. \emph{Glossa Psycholinguistics}, \emph{1}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+\bibitem[\citeproctext]{ref-R-ggplot2}
 Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+\bibitem[\citeproctext]{ref-R-stringr}
 Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
+\bibitem[\citeproctext]{ref-R-forcats}
 Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+\bibitem[\citeproctext]{ref-R-tidyr}
 Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+\bibitem[\citeproctext]{ref-R-dplyr}
 Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+\bibitem[\citeproctext]{ref-R-readr}
 Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-yang2021webcam}{}}%
+\bibitem[\citeproctext]{ref-yang2021webcam}
 Yang, X., \& Krajbich, I. (2021). Webcam-based online eye-tracking for behavioral research. \emph{Judgment and Decision Making}, \emph{16}(6), 1486.
 
-\leavevmode\vadjust pre{\hypertarget{ref-yarbus1967eye}{}}%
+\bibitem[\citeproctext]{ref-yarbus1967eye}
 Yarbus, A. L. (1967). \emph{Eye movements and vision}. Plenum Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-zehr2018PCIbex}{}}%
+\bibitem[\citeproctext]{ref-zehr2018PCIbex}
 Zehr, J., \& Schwarz, F. (2018). \emph{PennController for internet based experiments (IBEX)}. Retrieved from \url{https://doi.org/10.17605/OSF.IO/MD832}

### 2024-06-08 manuscript.tex
Render Quarto Manuscript

--- 2024-02-17 manuscript.tex
@@
 
-\hypertarget{present-work}{%
-\section{Present work}\label{present-work}}
+\section{Present work}\label{present-work}
 
@@
 
-\hypertarget{selection-of-studies}{%
-\subsection{Selection of Studies}\label{selection-of-studies}}
+\subsection{Selection of Studies}\label{selection-of-studies}
 
@@
 
-\hypertarget{equipment}{%
-\subsection{Equipment}\label{equipment}}
+\subsection{Equipment}\label{equipment}
 
@@
 
-\hypertarget{data-pre-processing}{%
-\subsection{Data pre-processing}\label{data-pre-processing}}
-
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.3; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
-
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
+\subsection{Data pre-processing}\label{data-pre-processing}
+
+We used R (Version 4.4.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.3; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
+
+\section{Experiment 1}\label{experiment-1}
 
@@
 
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
+\subsection{Methods}\label{methods}
 
@@
 
-\hypertarget{in-lab-sample}{%
-\paragraph{In-lab sample}\label{in-lab-sample}}
+\paragraph{In-lab sample}\label{in-lab-sample}
 
@@
 
-\hypertarget{procedure}{%
-\subsubsection{Procedure}\label{procedure}}
+\subsubsection{Procedure}\label{procedure}
 
@@
 
+\begin{verbatim}
+## Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
+## 3.5.0.
+## i Please use the `legend.position.inside` argument of `theme()` instead.
+## This warning is displayed once every 8 hours.
+## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+## generated.
+\end{verbatim}
+
 \begin{figure}
@@
 
-\hypertarget{pre-noun-fixations}{%
-\paragraph{Pre-noun fixations}\label{pre-noun-fixations}}
+\paragraph{Pre-noun fixations}\label{pre-noun-fixations}
 
@@
 
-\hypertarget{pre-verb-offset-fixations}{%
-\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}}
+\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}
 
@@
 
-\hypertarget{first-target-fixations-after-verb}{%
-\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}}
+\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}
 
@@
 
-\hypertarget{aggressive-exclusion}{%
-\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}}
+\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}
 
@@
 
-\hypertarget{calibration}{%
-\paragraph{Calibration}\label{calibration}}
+\paragraph{Calibration}\label{calibration}
 
@@
 
-\hypertarget{in-lab-sample-1}{%
-\subsubsection{In-lab sample}\label{in-lab-sample-1}}
-
-\hypertarget{minimal-exclusion-1}{%
-\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}}
+\subsubsection{In-lab sample}\label{in-lab-sample-1}
+
+\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}
 
@@
 
-\hypertarget{cumulative-fixation-probabilities-1}{%
-\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}}
+\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}
 
@@
 
-\hypertarget{pre-noun-fixations-1}{%
-\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}}
+\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}
 
@@
 
-\hypertarget{pre-verb-offset-fixations-1}{%
-\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}}
+\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}
 
@@
 
-\hypertarget{first-target-fixations-after-verb-1}{%
-\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}}
+\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}
 
@@
 
-\hypertarget{calibration-1}{%
-\paragraph{Calibration}\label{calibration-1}}
+\paragraph{Calibration}\label{calibration-1}
 
@@
 
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
+\subsection{Discussion}\label{discussion}
+
+\section{Experiment 2}\label{experiment-2}
 
@@
 
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
+\subsection{Methods}\label{methods-1}
 
@@
 
-\hypertarget{methods-2}{%
-\subsection{Methods}\label{methods-2}}
+\subsection{Methods}\label{methods-2}
 
@@
 Participants correctly identified whether the image was familiar or unfamiliar 87.09\% (\emph{SD} = 10.49) of the time.
-After excluding the 3 participants who responded correctly to all images, the average confidence rating for correct responses (M = 3.51; SD = 0.41) was significantly higher than their average confidence ratings for incorrect responses (M = 2.55; SD = 0.75), t(44) = -9.36, p = 0.00 .
-Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = 3.43 , p = 0.00.
+After excluding the 3 participants who responded correctly to all images, the average confidence rating for correct responses (M = 3.51; SD = 0.41) was significantly higher than their average confidence ratings for incorrect responses (M = 2.55; SD = 0.75), t(44) = 9.36, p = 0.00 .
+Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = -3.43 , p = 0.00.
 
@@
 
-\hypertarget{methods-3}{%
-\subsection{Methods}\label{methods-3}}
+\subsection{Methods}\label{methods-3}
 
@@
 
-\hypertarget{methods-4}{%
-\subsection{Methods}\label{methods-4}}
+\subsection{Methods}\label{methods-4}
 
@@
 
-\hypertarget{discussion-4}{%
-\subsection{Discussion}\label{discussion-4}}
+\subsection{Discussion}\label{discussion-4}
 
@@
 
-\hypertarget{general-discussion}{%
-\section{General Discussion}\label{general-discussion}}
+\section{General Discussion}\label{general-discussion}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sun2020another}{}}%
+\bibitem[\citeproctext]{ref-sun2020another}
 Sun, C., \& Breheny, R.

### 2024-06-10 group-c/E3-analysis-replication.Rmd

@@
 
-confidence.t.test <- t.test(M.confidence ~ correct_recognition, data=confidence.test.data.filtered, paired=T)
+confidence.t.test <- t.test(
+  confidence.test.data.filtered$M.confidence[confidence.test.data.filtered$correct_recognition == TRUE],
+  confidence.test.data.filtered$M.confidence[confidence.test.data.filtered$correct_recognition == FALSE],
+  paired=T)
 ```
@@
 
-rt.t.test <- t.test(M.rt ~ correct_recognition, data=rt.test.data.filtered, paired=T)
+rt.t.test <- t.test(
+  rt.test.data.filtered$M.rt[rt.test.data.filtered$correct_recognition == TRUE],
+  rt.test.data.filtered$M.rt[rt.test.data.filtered$correct_recognition == FALSE],
+  paired=T)
 ```

### 2024-06-10 group-a/E1-analysis-calibration.Rmd

@@
 There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
-Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
+Across the three effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, pre-verb-offset: Pearson's _r_ = `r m2_diffdiff_cor_r`; _p_ = `r m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
 However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.

### 2024-06-10 manuscript.tex
Render Quarto Manuscript

--- 2024-06-07 manuscript.tex
@@
 
-We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Version 1.8.0; Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
+We used R (Version 4.4.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.3; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
 
@@
 were recorded for each trial.
+
+\begin{verbatim}
+## Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
+## 3.5.0.
+## i Please use the `legend.position.inside` argument of `theme()` instead.
+## This warning is displayed once every 8 hours.
+## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+## generated.
+\end{verbatim}
 

### 2024-06-11 manuscript.Rmd
revised intro

@@
 3), a verb bias effect (Exp.
-4), and a gaze-bias effect in decision-making.
+4), and a gaze-bias effect in decision-making (Exp.
+5).
 These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution should be adapted to coarser quadrant or split-half displays.
@@
 Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD; @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
-
-Advances in software for online data collection [@deleeuwJsPsychJavaScriptLibrary2015; @papoutsaki2016webgazer] have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples.
-In particular, `Webgazer.js` [@papoutsaki2016webgazer] is a webcam-based Javascript plug-in that works in the browser.
-It can be integrated with any Javascript web interface.
-As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
-However, the added convenience comes at the cost of spatial and temporal resolution.
-The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are the subject of the current study.
-
-A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data.
-In what follows, we provide a brief review of the published work that we are aware of [note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., @banki2022comparing].
-
-@semmelmann2018online compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing.
-They used the `Webgazer.js` library [@papoutsaki2016webgazer] and programmed tasks in HTML/Javascript directly.
-The first two tasks tested measurement of basic gaze properties.
-In the fixation task, participants were asked to fixate a dot, and in the pursuit task, they were asked to follow a dot with their eyes.
-In the free viewing task, the eye movements may have been more semantically driven: participants were shown a picture of a human face and asked to look wherever they wanted to on the image.
-Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed relative to the in-lab data.
-The free viewing task replicated previously observed statistical patterns (e.g., more fixations on eyes than mouths).
-
-Similarly, @yang2021webcam used the `Webgazer.js` library [@papoutsaki2016webgazer] combined with the `jsPsych` library for conducting behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015], to replicate a well-established link between value-based decision-making and eye gaze [e.g., @shimojoGazeBiasBoth2003, @krajbich2010visual].
-Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one.
-During the primary task, on each of 100 trials, two of the snack food images were displayed on the left and right sides of the display and participants chose the one that they preferred while their gaze was monitored.
-As in previous work, participants were biased to choose the option they had spent more time looking at.
-The authors also implemented a code modification to address temporal delays in `WebGazer`.
-
-Several papers have used the `WebGazer.js` library (via different interfaces) to replicate visual world paradigm studies.
-@slim2022moving used the `PCIbex` online experiment platform [@zehr2018PCIbex] to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter)  while viewing four pictures displayed across the four quadrants of the screen [e.g., a letter, a backpack, a car and a wheelchair;  @dijkgraaf2017predicting].
-When the verb in the sentence was _constraining_ (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was _neutral_ (e.g., Mary steals a letter), as in previous work.
-However, they observed a substantial delay of ~200ms in the onset of the effect relative to the in-lab study with an infrared eyetracker and a reduction in effect size (despite a threefold increase in sample size relative to the original).
-The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between _constraining_ and _neutral_ conditions emerged before the onset of the final noun (e.g., letter).
-Similarly, @degen2021seeing reported that effects of scalar implicature processing (comparing looks to the target in a four quadrant display for sentences such as "Click on the girl that has _some_ apples" vs.
-"Click on the girl that has _three_ apples" ) were smaller and delayed relative to those observed in the lab [@sun2020another].
-
-In contrast, using the `Gorilla` experiment platform [@anwyl2020gorilla], @prystauka2023online observed robust effects of verb semantics and lexical interference in similar time windows to previous in-lab studies [@altmannIncrementalInterpretationVerbs1999;@kukona2014lexical], though a direct comparison was not possible because their studies used different materials than the in-lab experiments they were conceptually replicating.
-Furthermore, using `jsPsych`, @vos2022comparing closely replicated the magnitude and timecourse of effects in a lab-based visual world paradigm where the regions of interest (ROIs) consisted of the left and right halves of the display, suggesting that the concerns about poor temporal resolution can be mitigated.
-Indeed, the eye-tracking plug-in in `jsPsych` uses a fork of `Webgazer.js` in which certain modifications have been made to minimize processing time.
-^[See discussion at https://github.com/jspsych/jsPsych/discussions/1892]
-
-Finally, @van2023validation used `WebGazer.js` in conjunction with `PsychoJS` to conceptually replicate three paradigms, one which is analogous to @yang2021webcam, another testing the novelty preference (tendency for learners to look more at an object that they have not yet studied), and a visual world paradigm study with 4 objects, similar to @prystauka2023online.
-These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset.
-They did not address whether there were temporal delays.
-
-In sum, webcam eye-tracking has been used to varying degrees of success across a small set of paradigms that are used in cognitive science research.
-One configuration, `jsPsych` with a modification of `WebGazer.js`, appears to have circumvented initial limitations in temporal precision [@krajbich2010visual; @vos2022comparing] but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs).
-Further, the extent to which noise in the measurement is due to the software and hardware limitations as opposed to the difference between the in-lab and online settings remains unclear.
-In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
+Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend [@nosek2022replicability].
+
+A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired].
+Historically, this option has not been available for eye-tracking.
+This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking [e.g., @snedeker2003using].
+Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic.
+In recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation].
+However, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
+
+Given the potential game-changing nature of webcam-based eye-tracking, a number of research groups have investigated how well it works.
+There are two potential limitations to webcam-based eye-tracking.
+First, the spatial and temporal resolution is less than what is achievable with an infrared system.
+Second, testing subjects over the Internet involves less control: subjects may be unable or unwilling to calibrate equipment, adjust lighting, etc., to the same level of precision typical of in-lab studies.
+Nearly all this work has used `Webgazer.js` --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.
+
+Results to date have been encouraging.
+@semmelmann2018online found data quality was reasonable for fixation location and saccades in fixation, smooth pursuit, and free-viewing tasks, though data collected online through a crowdsourcing platform was slightly more variable and timing was somewhat delayed compared to data collected in the lab.
+Several researchers successfully replicated well-known findings from the sentence-processing literature involving predictive looks [@degen2021seeing; @prystauka2023online; @vos2022comparing; @van2023validation].
+@yang2021webcam successfully replicated a well-established link between value-based decision-making and eye gaze [see also @van2023validation].
+
+While promising, there are some salient limitations.
+First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2022moving; @degen2021seeing; @van2023validation].
+Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
+
+Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online], dividing the screen either in half or in quadrants.
+This is particularly salient with [@prystauka2023online], which simplified [@altmannIncrementalInterpretationVerbs1999]'s design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
+Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.
+
+Finally, the prior work has focused on a relatively limited range of methods.
+Different paradigms have different technical requirements and analyze the results differently.
+As a result, the breadth of utility of webcam eye-tracking is unclear.
 

### 2024-08-07 manuscript.Rmd

@@
 Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
-
-Taken together, the instability of these effects might suggest that this paradigm is not well-suited for web-based eye-tracking.
+This suggests the problem was not with running the study online or due to working with a more diverse population.
+
+Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking.
 Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+Further evidence comes from [@prystauka2023online], who ran a modified version of the Altmann and Kamide study with only 4 objects, allowing larger, more distinct ROIs.
+
  The next four experiments test paradigms with more generous ROIs.

### 2024-08-07 manuscript.tex
Render Quarto Manuscript

@@
 Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic {[}WEIRD; Henrich, Heine, and Norenzayan (2010){]} convenience samples (but see Ryskin, Salinas, Piantadosi, \& Gibson, 2023), which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
-
-Advances in software for online data collection (de Leeuw, 2015; Papoutsaki et al., 2016) have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples.
-In particular, \texttt{Webgazer.js} (Papoutsaki et al., 2016) is a webcam-based Javascript plug-in that works in the browser.
-It can be integrated with any Javascript web interface.
-As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as \texttt{jsPsych} (de Leeuw, 2015), \texttt{Gorilla} (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or \texttt{lab.js} (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021).
-However, the added convenience comes at the cost of spatial and temporal resolution.
-The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are the subject of the current study.
-
-A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data.
-In what follows, we provide a brief review of the published work that we are aware of (note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., Bánki, Eccher, Falschlehner, Hoehl, \& Markova, 2022).
-
-Semmelmann and Weigelt (2018) compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing.
-They used the \texttt{Webgazer.js} library (Papoutsaki et al., 2016) and programmed tasks in HTML/Javascript directly.
-The first two tasks tested measurement of basic gaze properties.
-In the fixation task, participants were asked to fixate a dot, and in the pursuit task, they were asked to follow a dot with their eyes.
-In the free viewing task, the eye movements may have been more semantically driven: participants were shown a picture of a human face and asked to look wherever they wanted to on the image.
-Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed relative to the in-lab data.
-The free viewing task replicated previously observed statistical patterns (e.g., more fixations on eyes than mouths).
-
-Similarly, Yang and Krajbich (2021) used the \texttt{Webgazer.js} library (Papoutsaki et al., 2016) combined with the \texttt{jsPsych} library for conducting behavioral experiments in a web browser (de Leeuw, 2015), to replicate a well-established link between value-based decision-making and eye gaze Krajbich, Armel, \& Rangel (2010).
-Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one.
-During the primary task, on each of 100 trials, two of the snack food images were displayed on the left and right sides of the display and participants chose the one that they preferred while their gaze was monitored.
-As in previous work, participants were biased to choose the option they had spent more time looking at.
-The authors also implemented a code modification to address temporal delays in \texttt{WebGazer}.
-
-Several papers have used the \texttt{WebGazer.js} library (via different interfaces) to replicate visual world paradigm studies.
-Slim and Hartsuiker (2022) used the \texttt{PCIbex} online experiment platform (Zehr \& Schwarz, 2018) to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen {[}e.g., a letter, a backpack, a car and a wheelchair; Dijkgraaf, Hartsuiker, and Duyck (2017){]}.
-When the verb in the sentence was \emph{constraining} (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was \emph{neutral} (e.g., Mary steals a letter), as in previous work.
-However, they observed a substantial delay of \textasciitilde200ms in the onset of the effect relative to the in-lab study with an infrared eyetracker and a reduction in effect size (despite a threefold increase in sample size relative to the original).
-The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between \emph{constraining} and \emph{neutral} conditions emerged before the onset of the final noun (e.g., letter).
-Similarly, Degen, Kursat, and Leigh (2021) reported that effects of scalar implicature processing (comparing looks to the target in a four quadrant display for sentences such as ``Click on the girl that has \emph{some} apples'' vs.~``Click on the girl that has \emph{three} apples'' ) were smaller and delayed relative to those observed in the lab (Sun \& Breheny, 2020).
-
-In contrast, using the \texttt{Gorilla} experiment platform (Anwyl-Irvine et al., 2020), Prystauka, Altmann, and Rothman (2023) observed robust effects of verb semantics and lexical interference in similar time windows to previous in-lab studies (Altmann \& Kamide, 1999; Kukona, Cho, Magnuson, \& Tabor, 2014), though a direct comparison was not possible because their studies used different materials than the in-lab experiments they were conceptually replicating.
-Furthermore, using \texttt{jsPsych}, Vos, Minor, and Ramchand (2022) closely replicated the magnitude and timecourse of effects in a lab-based visual world paradigm where the regions of interest (ROIs) consisted of the left and right halves of the display, suggesting that the concerns about poor temporal resolution can be mitigated.
-Indeed, the eye-tracking plug-in in \texttt{jsPsych} uses a fork of \texttt{Webgazer.js} in which certain modifications have been made to minimize processing time.
-\footnote{See discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}}
-
-Finally, Van der Cruyssen et al.
-(2023) used \texttt{WebGazer.js} in conjunction with \texttt{PsychoJS} to conceptually replicate three paradigms, one which is analogous to Yang and Krajbich (2021), another testing the novelty preference (tendency for learners to look more at an object that they have not yet studied), and a visual world paradigm study with 4 objects, similar to Prystauka et al.
-(2023).
-These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset.
-They did not address whether there were temporal delays.
-
-In sum, webcam eye-tracking has been used to varying degrees of success across a small set of paradigms that are used in cognitive science research.
-One configuration, \texttt{jsPsych} with a modification of \texttt{WebGazer.js}, appears to have circumvented initial limitations in temporal precision (Krajbich et al., 2010; Vos et al., 2022) but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs).
-Further, the extent to which noise in the measurement is due to the software and hardware limitations as opposed to the difference between the in-lab and online settings remains unclear.
-In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.
+Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend (Nosek et al., 2022).
+
+A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants (Gosling, Sandy, John, \& Potter, 2010; Hartshorne, Leeuw, Goodman, Jennings, \& O'Donnell, 2019; Li, Germine, Mehr, Srinivasan, \& Hartshorne, 2024; Reinecke \& Gajos, 2015).
+Historically, this option has not been available for eye-tracking.
+This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking (e.g., Snedeker \& Trueswell, 2003).
+Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic.
+In recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy (Burton, Albert, \& Flynn, 2014; Papoutsaki et al., 2016; Skovsgaard, Agustin, Johansen, Hansen, \& Tall, 2011; Zheng \& Usagawa, 2018).
+However, webcam-based eyetracking only started to be used regularly in research with the advent of \texttt{Webgazer.js} (Papoutsaki et al., 2016), a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including \texttt{jsPsych} (de Leeuw, 2015), \texttt{Gorilla} (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or \texttt{lab.js} (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021).
+
+Given the potential game-changing nature of webcam-based eye-tracking, a number of research groups have investigated how well it works.
+There are two potential limitations to webcam-based eye-tracking.
+First, the spatial and temporal resolution is less than what is achievable with an infrared system.
+Second, testing subjects over the Internet involves less control: subjects may be unable or unwilling to calibrate equipment, adjust lighting, etc., to the same level of precision typical of in-lab studies.
+Nearly all this work has used \texttt{Webgazer.js} --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.
+
+Results to date have been encouraging.
+Semmelmann and Weigelt (2018) found data quality was reasonable for fixation location and saccades in fixation, smooth pursuit, and free-viewing tasks, though data collected online through a crowdsourcing platform was slightly more variable and timing was somewhat delayed compared to data collected in the lab.
+Several researchers successfully replicated well-known findings from the sentence-processing literature involving predictive looks (Degen, Kursat, \& Leigh, 2021; Prystauka, Altmann, \& Rothman, 2023; Van der Cruyssen et al., 2023; Vos, Minor, \& Ramchand, 2022).
+Yang and Krajbich (2021) successfully replicated a well-established link between value-based decision-making and eye gaze (see also Van der Cruyssen et al., 2023).
+
+While promising, there are some salient limitations.
+First, many of the studies report effects that are smaller or later than what had been previously observed in the lab (Degen et al., 2021; Slim \& Hartsuiker, 2022; Van der Cruyssen et al., 2023).
+Importantly, accurate timing on a web browser is not trivial (De Leeuw \& Motz, 2016; Passell et al., 2021), and subtle programming choices can significantly affect the accuracy of \texttt{WebGazer.js} timing (Yang \& Krajbich, 2021).\footnote{See also discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}} Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
+
+Second, prior work has focused on studies with relatively coarse-grained regions of interest (but see Semmelmann \& Weigelt, 2018), dividing the screen either in half or in quadrants.
+This is particularly salient with (Prystauka et al., 2023), which simplified (Altmann \& Kamide, 1999)'s design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
+Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.
+
+Finally, the prior work has focused on a relatively limited range of methods.
+Different paradigms have different technical requirements and analyze the results differently.
+As a result, the breadth of utility of webcam eye-tracking is unclear.
 
@@
 
-We used R (Version 4.4.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.3; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
+We used R (Version 4.4.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.5; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
 
@@
 Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
-
-Taken together, the instability of these effects might suggest that this paradigm is not well-suited for web-based eye-tracking.
+This suggests the problem was not with running the study online or due to working with a more diverse population.
+
+Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking.
 Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+Further evidence comes from (Prystauka et al., 2023), who ran a modified version of the Altmann and Kamide study with only 4 objects, allowing larger, more distinct ROIs.
+
 The next four experiments test paradigms with more generous ROIs.
@@
 
-The fifth study was a replication attempt of Shimojo et al. (2003),
+The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003),
 which found that human gaze is actively involved in preference
@@
 Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect.
-Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to \texttt{webgazer} that are made within the \texttt{jsPsych} plug-in successfully address the issues noted by Dijkgraaf et al.
-(2017) and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.
+Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to \texttt{webgazer} that are made within the \texttt{jsPsych} plug-in successfully address the issues noted by Dijkgraaf, Hartsuiker, and Duyck (2017) and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.
 
@@
 
-\bibitem[\citeproctext]{ref-banki2022comparing}
-Bánki, A., Eccher, M.
-de, Falschlehner, L., Hoehl, S., \& Markova, G.
-(2022).
-Comparing online webcam-and laboratory-based eye-tracking for the assessment of infants' audio-visual synchrony perception.
-\emph{Frontiers in Psychology}, \emph{12}, 733933.
-
 \bibitem[\citeproctext]{ref-R-tinylabels}
@@
 Bolker, B., \& Robinson, D. (2020). \emph{Broom.mixed: Tidying methods for mixed models}. Retrieved from \url{https://CRAN.R-project.org/package=broom.mixed}
+
+\bibitem[\citeproctext]{ref-burton2014comparison}
+Burton, L., Albert, W., \& Flynn, M.
+(2014).
+A comparison of the performance of webcam vs.
+Infrared eye tracking technology.
+\emph{Proceedings of the Human Factors and Ergonomics Society Annual Meeting}, \emph{58}, 1437--1441.
+SAGE Publications Sage CA: Los Angeles, CA.
 
@@
 
+\bibitem[\citeproctext]{ref-de2016psychophysics}
+De Leeuw, J.
+R., \& Motz, B.
+A.
+(2016).
+Psychophysics in a web browser?
+Comparing response times collected with JavaScript and psychophysics toolbox in a visual search task.
+\emph{Behavior Research Methods}, \emph{48}, 1--12.
+
 \bibitem[\citeproctext]{ref-degen2021seeing}
@@
 
+\bibitem[\citeproctext]{ref-gosling2010wired}
+Gosling, S.
+D., Sandy, C.
+J., John, O.
+P., \& Potter, J.
+(2010).
+Wired but not WEIRD: The promise of the internet in reaching more diverse samples.
+\emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 94.
+
+\bibitem[\citeproctext]{ref-hartshorne2019thousand}
+Hartshorne, J.
+K., Leeuw, J.
+R.
+de, Goodman, N.
+D., Jennings, M., \& O'Donnell, T.
+J.
+(2019).
+A thousand studies for the price of one: Accelerating psychological science with pushkin.
+\emph{Behavior Research Methods}, \emph{51}, 1782--1803.
+
 \bibitem[\citeproctext]{ref-hayhoe2005eye}
@@
 \url{https://doi.org/10.1177/0956797613498260}
-
-\bibitem[\citeproctext]{ref-krajbich2010visual}
-Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.
-
-\bibitem[\citeproctext]{ref-kukona2014lexical}
-Kukona, A., Cho, P.
-W., Magnuson, J.
-S., \& Tabor, W.
-(2014).
-Lexical interference effects in sentence processing: Evidence from the visual world paradigm and self-organizing models.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 326.
 
@@
 \url{https://doi.org/10.18637/jss.v082.i13}
+
+\bibitem[\citeproctext]{ref-li2024developmental}
+Li, W., Germine, L.
+T., Mehr, S.
+A., Srinivasan, M., \& Hartshorne, J.
+(2024).
+Developmental psychologists should adopt citizen science to improve generalization and reproducibility.
+\emph{Infant and Child Development}, \emph{33}(1), e2348.
 
@@
 
+\bibitem[\citeproctext]{ref-nosek2022replicability}
+Nosek, B.
+A., Hardwicke, T.
+E., Moshontz, H., Allard, A., Corker, K.
+S., Dreber, A., et al.others.
+(2022).
+Replicability, robustness, and reproducibility in psychological science.
+\emph{Annual Review of Psychology}, \emph{73}, 719--748.
+
 \bibitem[\citeproctext]{ref-R-jsonlite}
@@
 
+\bibitem[\citeproctext]{ref-passell2021cognitive}
+Passell, E., Strong, R.
+W., Rutter, L.
+A., Kim, H., Scheuer, L., Martini, P., \ldots{} Germine, L.
+(2021).
+Cognitive test scores vary with choice of personal digital device.
+\emph{Behavior Research Methods}, \emph{53}(6), 2544--2557.
+
 \bibitem[\citeproctext]{ref-prystauka2023online}
@@
 Rayner, K. (1998). Eye movements in reading and information processing: 20 years of research. \emph{Psychological Bulletin}, \emph{124}(3), 372.
+
+\bibitem[\citeproctext]{ref-reinecke2015labinthewild}
+Reinecke, K., \& Gajos, K.
+Z.
+(2015).
+LabintheWild: Conducting large-scale online experiments with uncompensated samples.
+\emph{Proceedings of the 18th ACM Conference on Computer Supported Cooperative Work \& Social Computing}, 1364--1378.
 
@@
 
+\bibitem[\citeproctext]{ref-skovsgaard2011evaluation}
+Skovsgaard, H., Agustin, J.
+S., Johansen, S.
+A., Hansen, J.
+P., \& Tall, M.
+(2011).
+Evaluation of a remote webcam-based eye tracker.
+\emph{Proceedings of the 1st Conference on Novel Gaze-Controlled Applications}, 1--4.
+
 \bibitem[\citeproctext]{ref-slim2022moving}
@@
 
+\bibitem[\citeproctext]{ref-snedeker2003using}
+Snedeker, J., \& Trueswell, J. (2003). Using prosody to avoid ambiguity: Effects of speaker awareness and referential context. \emph{Journal of Memory and Language}, \emph{48}(1), 103--130.
+
 \bibitem[\citeproctext]{ref-snedekerDevelopingConstraintsParsing2004a}
@@
 \emph{Infancy}, \emph{29}(1), 31--55.
-
-\bibitem[\citeproctext]{ref-sun2020another}
-Sun, C., \& Breheny, R.
-(2020).
-Another look at the online processing of scalar inferences: An investigation of conflicting findings from visual-world eye-tracking studies.
-\emph{Language, Cognition and Neuroscience}, \emph{35}(8), 949--979.
 
@@
 
-\bibitem[\citeproctext]{ref-zehr2018PCIbex}
-Zehr, J., \& Schwarz, F. (2018). \emph{PennController for internet based experiments (IBEX)}. Retrieved from \url{https://doi.org/10.17605/OSF.IO/MD832}
+\bibitem[\citeproctext]{ref-zheng2018rapid}
+Zheng, C., \& Usagawa, T.
+(2018).
+A rapid webcam-based eye tracking method for human computer interaction.
+\emph{2018 International Conference on Control, Automation and Information Sciences (ICCAIS)}, 133--136.
+IEEE.
 

### 2024-08-15 manuscript.Rmd
small abstract edits

@@
 abstract: |
-  We tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based eye-tracking format.
+  Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require.
+Recent innovations have expanded the set of methodolgies that are possible online, but ongoing work is needed to test the suitability of web-based tools for various research paradigms.
+Here, we focus on webcam-based eye-tracking; we tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based format.
 Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js.

### 2024-08-15 manuscript.tex
Render Quarto Manuscript

@@
 \abstract{%
-We tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based eye-tracking format.
+Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require.
+Recent innovations have expanded the set of methodolgies that are possible online, but ongoing work is needed to test the suitability of web-based tools for various research paradigms.
+Here, we focus on webcam-based eye-tracking; we tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based format.
 Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js.

### 2024-08-20 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
experiment 1 edits; split into 1a and 1b

@@
 ```{r plot subjects by validation-JH, eval=F}
-#printed?
+#printed? No: eval=F
 ggplot(jh.validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-spaghetti-fig), Panel (c).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1b-spaghetti-fig), Panel (b).
+The results from Experiment 1a are copied here for ease of comparison (Panel a).
 
@@
 Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%.
+Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
 
-We tested whether a participant's calibration quality was correlated with their effect size.
-Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
-However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.
-rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).
+In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
+This was not the case in the in-lab sample (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).
 
@@
 Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).
+
+```{r E1b-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions."}
+
+E1_panel_fig <- E1_spag_fig_remote / jh_E1_spag_fig
+E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect',  heights = unit(6, 'cm'))
+
+```

### 2024-08-20 group-a/E1-analysis-comparison-to-JMW23.Rmd
experiment 1 edits; split into 1a and 1b

@@
 library(broom.mixed)
+source('round.comm.R') #does "commercial" i.e. normal rounding
 

### 2024-08-20 group-a/E1-analysis-replication.Rmd
experiment 1 edits; split into 1a and 1b

@@
 ```
-### Remote sample
 <!-- # Import Data -->
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:E1-spaghetti-fig), Panel (b).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:E1a-spaghetti-fig), Panel (b).
 
@@
 non-restricting = 0), object type (target = 1 vs.
-distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
+distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix)^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`.
 There were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
@@
 Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we did the same, we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+When we did the same^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`, we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 
-We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`.
 There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
@@
 
+```{r E1-calib-effect, fig.cap='Calibration scores plotted against target advantage scores (cumulative proportion of fixations to the target minus cumulative proportion of fixations to competitors) at the end of the pre-noun time window.'}
+#The one corr that came out: noun window, restricting condition only
+ggplot(cali.analy.1, aes(x=M, y=restricting))+
+  geom_point()+
+  geom_smooth(method="lm", formula = y ~ x)+
+  labs(x="Calibration Score", y="Target Advantage Score")
+
+```
+
 #### Calibration
@@
 Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
-In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
-This was not the case in the in-lab sample (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).
-
-### In-lab sample
-```{r E1-analysis-JoshH-lab, child = 'E1-analysis-comparison-to-Hartshorne.Rmd'}
-
-```
-
-```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+However, when the two interaction effects were calculated as the target advantage in the restricting condition only (i.e.
+rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).
+This is shown in Figure\ \@ref(fig:E1-calib-effect).
+
+```{r E1a-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
 The vertical line marks the mean noun onset time across trials and conditions."}
 
-E1_panel_fig <- JMW_spag_fig / E1_spag_fig_remote / jh_E1_spag_fig 
+E1_panel_fig <- JMW_spag_fig / E1_spag_fig_remote 
 E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect',  heights = unit(6, 'cm'))

### 2024-08-20 group-c/E3-analysis-replication.Rmd
experiment 1 edits; split into 1a and 1b

@@
 ```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE}
-ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
-  geom_point()+
-  theme_bw()
+# #This isn't referred to in the text--it's between Figs 10 and 11
+# ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
+#   geom_point()+
+#   theme_bw()
+#   
 ```

### 2024-08-20 manuscript.Rmd
experiment 1 edits; split into 1a and 1b

@@
 3 and 5) or quadrants (Exps.
-2 & 4), or composed scenes with regions of interest that varied in size (Exp.
+2 and 4), or composed scenes with regions of interest that varied in size (Exp.
 1).
@@
 age or older, fluency in English, and access to a webcam. All
-participants provided informed consent. The studies were approved by the
+participants provided informed consent. The online studies were approved by the
 Vassar College Institutional Review Board.
 
-In addition, an in-person replication was conducted for Experiment 1. 
-Information about the sample is given in the Experiment 1 Method sections.
+In addition, an in-lab replication was conducted for Experiment 1. 
+Information about the sample is given in the Experiment 1 Method sections. This study was approved by the Institutional Review Board at Boston College.
 
@@
 
-## Data pre-processing
+## Data Pre-processing
 
@@
 
-# Experiment 1
+# Experiment 1a
 
@@
 
-<!--AJ: Here's an organizational thing I'm trying-- Mention here that there are two experiments (Prolific and in Josh H's lab) and divide subsequent sections where appropriate. Good idea?-->
-
-We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the remote and the in-lab replications used WebGazer and identical materials and procedures.
-
-```{r read_groupA_data}
-#AJ: We don't need this, right? Can I delete?
-```
-
 ## Method
@@
 ### Participants
-#### Remote sample
 Sixty participants were paid \$2.60 for their participation. Our sample size
@@
 
-#### In-lab sample
-Forty-nine participants completed the study in a lab setting.
-They were recruited via the college subject pool.
-Participants needed to be 18 years of age or older and native speakers of English.
-The study was approved by the Institutional Review Board at Boston College.
-
 ### Procedure
@@
 ```
-### Materials & Design
+### Materials and Design
 
@@
 
-Each participant was presented with sixteen critical trials (eight in
+Each participant was presented with 16 critical trials (eight in
 the restrictive condition, eight in the non-restrictive condition) and
-sixteen fillers for a total of 32 trials. The order of trials and the
+16 fillers for a total of 32 trials. The order of trials and the
 assignment of critical scene to condition was random on a
@@
 
-### Data pre-processing and analysis
-
+## Results
 Looks to the objects in the scene were time-locked to the onset of the
@@
 
+```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}
+
+```
+
+## Discussion
+Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
+A comparison to published data [@james2023language] demonstrates that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
+After eliminating participants with validation accuracy under 50% and/or 10% or fewer fixations to any ROIs, we were left with only 22 of the original 60 participants.
+Analyses on this subset resulted in one effect reaching statistical significance (shorter target fixation latencies in the restricting vs.
+non-restricting verb condition).
+Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to isolate the potential causes.
+
+# Experiment 1b
+Experiment 1b tested whether the failure to replicate significant condition effects in Experiment 1a was due to features of conducting the study remotely (i.e.
+varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or `webgazer` _per se_.
+Thus, Experiment 1b took place in a lab setting with undergraduate participants but otherwise used the same Method as Experiment 1a.
+
+## Method
+
+### Participants
+Forty-nine participants completed the study in a lab setting.
+They were recruited via the Boston College subject pool.
+Participants needed to be 18 years of age or older and native speakers of English.
+
+### Procedure
+After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
+
+### Apparatus
+HELP
+
+### Materials and Design
+Materials were identical to those in Experiment 1a.
+
 ## Results
-
-```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}
+```{r E1-analysis-JoshH-lab, child = 'E1-analysis-comparison-to-Hartshorne.Rmd'}
 
@@
 ## Discussion
-
 Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
-In the remote sample, results were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance; the one exception was in comparing first target fixation latencies across verb conditions, but only when aggressive exclusion criteria were applied to participants (INSERT WHAT THOSE CRITERIA WERE).
+In Experiment 1a, results from the remote samplewere in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance.
 To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting.
 Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
-This suggests the problem was not with running the study online or due to working with a more diverse population.
+This suggests the problem was not with running the study online or due to working with a more diverse population via Prolific.
 
 Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking.
-Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
-Further evidence comes from [@prystauka2023online], who ran a modified version of the Altmann and Kamide study with only 4 objects, allowing larger, more distinct ROIs.
+Notably, the ROIs were tightly drawn around the five to six objects in each scene (drawing larger ROIs in these scenes would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+Further evidence comes from a recent `webgazer` study that successfully replicated a modified version of the Altmann and Kamide study with only four objects, each in separate quadrants, allowing for larger, more distinct ROIs [@prystauka2023online].
 
 The next four experiments test paradigms with more generous ROIs.
- <!-- bullet points from Ariel
-
-  • Note that the ROIs are only the sizes of the objects in the scene (plus padding), so much smaller than a 5th or 6th of the whole screen (because there are 5 or 6 ROIs per scene; should I figure out how much smaller?)
-
- • Effect sizes (target adv in eat vs.
-move cond) were uncorrelated with calibration accuracy in both samples, but in the remote sample (but not JH lab), calibration was correlated with target adv in eat condition alone [I need to look into this real quick--I think scatterplots would help]
-
--->
 

### 2024-08-21 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
E2 and E3 materials sections, calibration plots

@@
   geom_vline(xintercept = mean(jh.word.dur.avg$Total)) +
-  theme(panel.grid=element_blank(), legend.position = "none")+
+  theme(panel.grid.minor=element_blank(), legend.position = "none")+
   ggtitle('In-lab sample')

### 2024-08-21 group-a/E1-analysis-replication.Rmd
E2 and E3 materials sections, calibration plots

@@
 ```{r summarize calibration data, eval=F}
-#printed?
 validation.accuracy.data %>% 
@@
 ```{r plot subjects by validation, eval=F}
-#printed?
 ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
@@
   geom_vline(xintercept = mean(word.dur.avg$Total)) +
-  theme(panel.grid=element_blank(), axis.title.x = element_blank())+
+  theme(panel.grid.minor=element_blank(), axis.title.x = element_blank())+
   ggtitle('Remote sample')
@@
 
+<!--CALIBRATION ANALYSIS-->
 ```{r Model 1 effect size by calibration}
@@
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Target Advantage Score")
+  labs(x="Calibration Score", y="Target Advantage Score")+
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
 

### 2024-08-21 group-b/E2-analysis-calibration.Rmd
E2 and E3 materials sections, calibration plots

@@
 
-```{r, eval = F}
+```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).'}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+
   geom_point()+
-  geom_smooth(method = "lm")
+  geom_smooth(method = "lm", formula = y ~ x) +
+  labs(x="Calibration Score", y="Gaze Bias")+
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
 ```
+
 ```{r}
@@
 Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
-The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.
+The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect))

### 2024-08-21 group-b/E2-analysis-replication.Rmd
E2 and E3 materials sections, calibration plots

@@
 
-### Replication
 <!--Summarize proportion of views in each quadrant for each trial-->
@@
 
-__Eye-gaze__.
+### Eye-gaze
 Looks during the retrieval period were categorized as belonging to one of four quadrants based on the x,y coordinates.
 The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding.
-The other three quadrants were semi-randomly labeled "first", "second," third" (e.g., when the critical quadrant was in the top left, the "first" quadrant was the top right quadrant, but when the critical quadrant was in the top right, "first" corresponded to bottom right, etc.).
+The other three quadrants were labeled "first", "second," and "third" depending upon the location of the critical quadrant (e.g., when the critical quadrant was in the top left, the "first" quadrant was the top right quadrant, but when the critical quadrant was in the top right, "first" corresponded to bottom right, etc.).
 In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \@ref(fig:E2-gaze-fig-both-conds)).
-This bias appeared larger in the free-viewing condition, suggesting that the manipulation was (somewhat) effective.
+This bias appeared larger in the free-viewing condition, suggesting that the manipulation was somewhat effective.
 
@@
 
-__Response Time and Accuracy__. Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig). 
+### Response Time and Accuracy
+Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig). 
 Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
@@
 
-One possibility is that in-lab participants were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
+One possibility is that the in-lab participants in @johanssonLookHereEye2014 were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
 When  analyzing results from the subset of participants (N = `r length(successful_fixed)`) who were most compliant during the fixed-viewing block (at least 25% of their looks fell within 20% of the center of the display), the viewing condition effects and the interactions were not signficant.

### 2024-08-21 group-c/E3-analysis-calibration.Rmd
E2 and E3 materials sections, calibration plots

@@
 
-```{r E3-cal Plot Calibration Accuracy, echo=FALSE}
+```{r E3-cal Plot Calibration Accuracy, echo=FALSE, eval=FALSE}
+#This figure isn't referred to in the body of the text, and we have the scatterplots, so I'm cutting this for now
 ggplot(subject.calibration.score, aes(x=mean_percent_in_roi))+
@@
 
-Calibration scores were not correlated with looking scores, regardless of which method was used to calculate looking scores.
+Calibration scores were not correlated with looking scores, regardless of whether scores were computed using the halves coding method (see Figure \ \@ref(fig:E3-cal-Plot-looking-score-(halves)-by-calibration) or the ROI coding method (see  Figure \ \@ref(fig:E3-cal-Plot-looking-score-(roi)-by-calibration)).
 
-```{r E3-cal Plot looking score (halves) by calibration, echo=FALSE}
+```{r E3-cal-Plot-looking-score-(halves)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).'}
 ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
@@
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looking Score (Halves)")
+  labs(x="Calibration Score", y="Looking Score (Halves)")+
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
+
 ```
 
-```{r E3-cal Plot looking score (roi) by calibration, echo=FALSE, warning=FALSE}
+```{r E3-cal-Plot-looking-score-(roi)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).'}
 ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
@@
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looking Score (ROIs)")
+  labs(x="Calibration Score", y="Looking Score (ROIs)") +
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
+
 ```
@@
 We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
-None of the four relationships showed a significant correlation.
+None of the four relationships showed a significant correlation (see Figure\ \@ref(fig:E3-cal-Plot-correlations-with-calibration-score)).
 
-```{r E3-cal Plot correlations with calibration score, echo=FALSE, warning=FALSE}
+```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance.
+Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).}
+# Set up facet label names for behavioral_measure variable
+behav.labs <- c("Confidence", "Reaction Time")
+names(behav.labs) <- c("confidence", "rt")
+
+# Set up facet label names for looking_measure variable
+look.labs <- c("Halves Method", "ROI Method")
+names(look.labs) <- c("half", "roi")
+
 ggplot(looking.correlations.subjects.tidy, aes(x=mean_percent_in_roi, y=z))+
@@
   geom_smooth(method="lm", formula=y~x)+
-  facet_grid(behavioral_measure ~ looking_measure)
-
+  facet_grid(behavioral_measure ~ looking_measure,
+             labeller = labeller(behavioral_measure = behav.labs, looking_measure =
+                                   look.labs))+
+  labs(x="Calibration Score", y="Correlation (Looking Score, Memory)") +
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
 ```

### 2024-08-21 group-c/E3-analysis-replication.Rmd
E2 and E3 materials sections, calibration plots

--- 2024-06-10 group-c/E3-analysis-replication.Rmd
@@
 The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
-This significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`, indicating that participants did show a preference for looking at the novel objects.
+This was significantly greater than 0.5 (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`), indicating that participants did show a preference for looking at the novel objects.
 
@@
 
-```{r plot-cumulative-looking-score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+```{r plot-cumulative-looking-score, echo=FALSE, eval=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+#This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
 ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
@@
 After excluding the `r length(subjects.100.percent.accurate)` participants who responded correctly to all images, the average confidence rating for correct responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% sd()`) was significantly higher than their average confidence ratings for incorrect responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% sd()`), t(`r confidence.t.test$parameter`) = `r confidence.t.test$statistic`, p = `r confidence.t.test$p.value` .
-Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`.
+Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`).
 
@@
 
-To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on day 2, we computed the correlation coefficient between day 1 looking scores and day 2 confidence/RT for each participant.
+To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 looking scores and Day 2 confidence/RT for each participant.
 Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
-Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
+Using one-sample t-tests, we found no significant difference from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
 
-```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE}
+```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE, eval=FALSE}
+# #This isn't referred to in the text--it's between Figs 10 and 11
+
 ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
@@
   theme_bw()
+
 ```

### 2024-08-21 manuscript.Rmd
E2 and E3 materials sections, calibration plots

@@
 
-### Procedure
-
-```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }
-
-```
-
-```{=html}
-<!-- Qs: 
--keyboard keys? what was the exact phrasing of the instruction? 
--Any delay between when visual scene appears and the audio starts? 
--Does trial end as soon as participant responds?-->
-```
 ### Materials and Design
@@
 
+### Procedure
+
+```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }
+
+```
+
+```{=html}
+<!-- Qs: 
+-keyboard keys? what was the exact phrasing of the instruction? 
+-Any delay between when visual scene appears and the audio starts? 
+-Does trial end as soon as participant responds?-->
+```
+
 ## Results
@@
 
+### Materials and Design
+Materials were identical to those in Experiment 1a.
+
 ### Procedure
@@
 HELP
-
-### Materials and Design
-Materials were identical to those in Experiment 1a.
 
@@
 
-60 participants were paid for their participation.
+Sixty participants were paid for their participation.
 The sample size was motivated in part by budget constraints, but was
 nonetheless 2.5x larger than the original sample size of 24). 
-Data from 1 participant were not properly
+Data from one participant were not properly
 recorded due to unknown technical issues, so data from 59 participants
@@
 
+### Materials and Design
+
+The experiment consisted of two blocks each composed of an encoding
+phase and a recall phase.
+The two blocks differed by whether the recall phase was in the free-viewing or fixed-viewing condition, as described in the Procedure.
+Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first. 
+During each encoding phase, participants saw a
+grid indicating the four quadrants of the screen. Each quadrant
+contained six cartoon images of items belonging to the same category. The four categories were humanoids, household objects, animals, and
+methods of transportation (see Figure\ \@ref(fig:E2-example-trial)). Different images were used in each block; there were 48 unique images total across the experiment.
+
+Each recall phase presented participants with a blank screen with a central fixation cross as they listened to true/false statements testing their recall of the previous grid.
+Each statement fell into either an interobject or intraobject
+condition. Interobject statements were those that compared two different
+items in the grid (e.g. "The skeleton is to the left of the robot"),
+while intraobject statements were those that asked about the orientation
+of a single item (e.g. "The bus is facing right"). There were 48 total
+statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
+
+```{r E2-example-trial, fig.cap='Example trial from Experiment 2.'}
+knitr::include_graphics("group-b/E2-example-figure.jpeg")
+```
+
 ### Procedure
@@
 
-The experiment consisted of two blocks each composed of an encoding
-phase and a recall phase. During the encoding phase, participants saw a
-grid indicating the four quadrants of the screen. Each quadrant
-contained six images of items belonging to the same category (see Figure\ \@ref(fig:E2-example-trial)). 
-The four categories were humanoids, household objects, animals, and
-methods of transportation. 
-Each of the four quadrants was presented one at a time. First, a list of
+Participants received instructions that included an example grid and an explicit request that they not use any tools to help them during encoding.
+Participants then began their first encoding phase.
+Each of the four quadrants was presented one at a time.
+First, a list of
 the items in the quadrant was shown, then the pictures of items were displayed in the quadrant. 
@@
 
-```{r E2-example-trial, fig.cap='Example trial from Experiment 2.'}
-knitr::include_graphics("group-b/E2-example-figure.jpeg")
-```
-
-During the recall phase, participants listened to statements and
+Participants then entered the first recall phase, in which they listened to the 48 statements and
 responded by pressing the 'F' key for false statements and 'T' for true
-ones. Each statement fell into either an interobject or intraobject
-condition. Interobject statements were those that compared two different
-items in the grid (e.g. "The skeleton is to the left of the robot"),
-while intraobject statements were those that asked about the orientation
-of a single item (e.g. "The bus is facing right"). There were 48 total
-statements, with 24 interobject and 24 intraobject statements split
-evenly among the four quadrants. While listening to these statements, in
+ones. While listening to these statements, in
 the free-viewing block, participants saw a blank screen and were allowed
@@
 screen throughout the recall phase. In both cases, the mouse was
-obscured from the screen. Participants were randomly assigned to see the
-fixed-viewing or free-viewing block first. Different images were used in each block.
-
-After completing both encoding-recall blocks, participants were asked to
+obscured from the screen.
+
+Participants then proceded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to
 answer a few survey questions (such as whether they wore glasses or
@@
 
+### Materials and Design
+
+Stimuli consisted of color photographs of common objects (e.g.
+an apple, a key, etc.).
+We selected 96 unique images from the stimulus set provided by @konkle2010conceptual, which contains multiple objects from hundreds of unique categories.
+We selected images in 48 pairs from the same object category such that each critical object had a corresponding foil object during the recognition test (e.g.
+one red apple and one green apple).
+All images are of a single object on a white background.
+<!-- There are 98 unique images on OSF.
+One pair (lighter and lighter-alternate) isn't used.
+-->
+
+Stimulus sets were created to present participants with 24 presentation trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
+Each presentation trial screen presented two identical images (e.g.
+red apple and red apple).
+The test trial screens presented each of the previously-seen ("old") images paired with a new image (e.g.
+red apple and bicycle key).
+The recognition trial screens presented a single image that was either from the original set of 24 (seen twice across the first two phases) or was a corresponding foil for the original set (e.g.
+red apple or green apple).
+Thus, each participant was exposed to 72 unique images over the course of the experiment (the 24 foils for the "new" images in the test phase are never seen).
+Two full stimulus lists were created to counterbalance images across participants; the images that composed the "old" set for one list made up the "new" set for the list.
+The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
+
 ### Procedure
@@
 The experiment was administered over the course of two
-consecutive days. It consisted of three sections: a presentation phase,
-a test phase, and a recognition test. The first two phases occurred on
+consecutive days. The presentation phase and test phase occurred on
 the first day, while the recognition test occurred on the second day.
@@
 During the presentation phase, participants viewed 24 pairs of identical
-color photographs depicting common objects. Each pair was presented for
+images. Each pair was presented for
 5 seconds and an interval of 5 seconds elapsed before the next pair was
@@
 calibration again before beginning the test phase. During this phase,
-participants again viewed 24 pairs of photographs with an interstimulus
-duration of 5 seconds. In each pair, one photograph was previously seen
-during the presentation phase, while the other was new. Which pictures
-were old or new was counterbalanced across participants.<!-- 2 lists?-->
-For half of the participants in each counterbalancing group, the new and
-old photographs were
-reversed.<!-- not sure what that last sentence means: is it about the side of the screen? or still just describing that there were 2 lists-->
+participants again viewed 24 pairs of photographs (old and new) with an interstimulus
+duration of 5 seconds.
 
@@
 interval of 12 hours to accommodate busy schedules, participants were
-given the recognition test. It consisted of 48 photographs, presented
-one at a time. Each was shown on the screen for 1 second, followed by a
-1 second interstimulus interval. Half of the photographs had been
-viewed twice on the previous day and were deemed the "targets." The
-other half depicted an object with the same name as an object in one of
-the old photographs, but had not been viewed before, deemed "foils."
-Each photograph remained on the screen until the participants indicated
-whether or not they had seen it before by pressing 'y' for yes and 'n'
-for no. After they pressed one of the two keys, a prompt on the screen
+given the recognition test. Each image was shown on the screen for 1 second, followed by a
+1 second interstimulus interval.
+Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing 'y' for yes and 'n' for no.
+After they pressed one of the two keys, a prompt on the screen
 asked them to rate their confidence in their answer from 1 as a "pure
@@
 the screen. No feedback on their responses was given during the test.
-
-The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
 
@@
 
-### Materials
-
-`r colorize('Images were selected XXX...','red')`
-
 ## Results
@@
 
+### Calibration
+
+```{r E3-analysis-calibration, child='group-c/E3-analysis-calibration.Rmd'}
+
+```
+
 ### Effects of ROIs
@@
 ```{r E3-analysis-ROIs, child='group-c/E3-analysis-roi.Rmd'}
-
-```
-
-### Calibration
-
-```{r E3-analysis-calibration, child='group-c/E3-analysis-calibration.Rmd'}
 
@@
 Note that the original study had a sample size of 24.
+
+### Materials
+
+The images and audios presented to the participants were the same
+stimuli used in the original study (available here <link>). The critical
+trials were divided into modifier-biased, instrument-biased, and
+equibiased conditions, and the filler trials did not contain ambiguous
+instructions. Two lists of critical trials were made with different verb
+and instrument combinations (e.g., "rub" could be paired with "panda"
+and "crayon" in one list and "panda" and "violin" in the second list).
+Within each list, the same verb was presented twice but each time with a
+different target instrument and animal. The lists were randomly assigned
+to the participants to make sure the effects were not caused by the
+properties of the animal or instrument images used. The list of verbs
+used can be found in Appendix A of the original study.
 
@@
 
-### Materials
-
-The images and audios presented to the participants were the same
-stimuli used in the original study (available here <link>). The critical
-trials were divided into modifier-biased, instrument-biased, and
-equibiased conditions, and the filler trials did not contain ambiguous
-instructions. Two lists of critical trials were made with different verb
-and instrument combinations (e.g., "rub" could be paired with "panda"
-and "crayon" in one list and "panda" and "violin" in the second list).
-Within each list, the same verb was presented twice but each time with a
-different target instrument and animal. The lists were randomly assigned
-to the participants to make sure the effects were not caused by the
-properties of the animal or instrument images used. The list of verbs
-used can be found in Appendix A of the original study.
-
 ## Results

### 2024-08-21 group-d/E4-analysis-calibration.Rmd
E2 and E3 materials sections, calibration plots
E4 edits (add corr plot, wordsmithing)

@@
 ```
+
 ```{r, eval = F}
@@
 
-```{r, eval = F}
+```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
   geom_point()+
-  geom_smooth(method = "lm")
+  geom_smooth(method = "lm") +
+  labs(x="Calibration Score", y="Bias Effect") +
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
 ```
-Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%).
 The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
-The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration
+The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).
 

### 2024-08-21 manuscript.Rmd
E4 edits (add corr plot, wordsmithing)

@@
 
-57 participants were paid \$2.50 for their participation.
+Fifty-seven participants were paid \$2.50 for their participation.
 A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power.
-Note that the original study had a sample size of 24.
-
-### Materials
+Note that Ryskin et al.
+(2017) Experiment 1 had a sample size of 24.
+
+### Materials and Design
 
 The images and audios presented to the participants were the same
-stimuli used in the original study (available here <link>). The critical
+stimuli used in the original study. The critical
 trials were divided into modifier-biased, instrument-biased, and
@@
 to the participants to make sure the effects were not caused by the
-properties of the animal or instrument images used. The list of verbs
-used can be found in Appendix A of the original study.
+properties of the animal or instrument images used.
+There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials.
+The list of the 27 verbs used, along with their verb bias norms, can be found in Appendix A of the original study.
 
@@
 
-### Comparison to in-lab data
-
 ```{r E4-analysis-comparison-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}
@@
 
-As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier, instrument or equi).
+As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier-, instrument-, or equi-).
 For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).

### 2024-08-22 group-e/E5-analysis-calibration.Rmd
E5 edits (wordsmithing, adding back mystery exclusions)

@@
 # Excluding Subjects
-all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
-E5.excluded.n = 8
+# all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
+# E5.excluded.n = 8
+
+#There's an issue with Subject 603ea6a51c38def3e4140ba6 (roundness condition): their webgazer_data is a list of length 0 instead of a dataframe like the others.
+all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6")
 
@@
   filter(calib_num == max(calib_num)) %>%
-  select(subject_id, mean_percent_in_roi)
+  select(subject_id, mean_percent_in_roi,calib_num)
 
@@
 As in the previous experiments, calibration score was defined as the average proportion of samples within 200 pixels of the validation point during the final validation phase before the eye tracking is performed.
-The distribution across participants is shown in Fig.
+<!--The distribution across participants is shown in Fig.
 \@ref(fig:E5cal).
-(ref:E5cal-caption) Histogram of calibration success in Exp. 5. Where participants required more than one calibration (N=8), only the final calibration was considered.
+(ref:E5cal-caption) Histogram of calibration success in Exp.
+5.
+(AJ: I cut this to be more similar to the other expts)-->Where participants required more than one calibration (N=14), only the final calibration was considered.
 
-```{r E5cal, fig.show="hold", out.width="45%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5cal-caption)"}
+```{r E5cal, fig.show="hold", out.width="45%", echo=FALSE,eval=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5cal-caption)"}
 ggplot(subject.calibration.score, aes(x=mean_percent_in_roi)) +
@@
 
-To determine whether calibration accuracy influenced our key effects, we calculated the percentage of samples during the task in which the participant was fixating the face they ultimately chose.
-There was a significant correlation for both the attractiveness judgments (r = `r round(scorescorrs.A$estimate, 2)` [`r round(scorescorrs.A$conf.int, 2)[1]`, `r round(scorescorrs.A$conf.int, 2)[2]`], p = `r round(scorescorrs.A$p.value, 2)`) and the roundness judgments (r = `r round(scorescorrs.R$estimate, 2)` [`r round(scorescorrs.R$conf.int, 2)[1]`, `r round(scorescorrs.R$conf.int, 2)[2]`], p = `r round(scorescorrs.R$p.value, 2)`).
+To determine whether calibration accuracy influenced our key effects, we calculated the proportion of samples during the task in which the participant was fixating the face they ultimately chose.
+Calibration accuracy significantly correlated with fixations in both the attractiveness condition (r = `r round(scorescorrs.A$estimate, 2)` [`r round(scorescorrs.A$conf.int, 2)[1]`, `r round(scorescorrs.A$conf.int, 2)[2]`], p = `r round(scorescorrs.A$p.value, 2)`) and the roundness condition (r = `r round(scorescorrs.R$estimate, 2)` [`r round(scorescorrs.R$conf.int, 2)[1]`, `r round(scorescorrs.R$conf.int, 2)[2]`], p = `r round(scorescorrs.R$p.value, 2)`).
 Inspection of Fig.
-\@ref(fig:E5calcorr) reveals that this correlation is due to a handful of particpiants with calibration values below 50%.
+\@ref(fig:E5calcorr) reveals that this correlation is due to a handful of participants with calibration values below 50%.
 
-(ref:E5calcorr-caption) Correlation between calibration accuracy (x-axis) and percentage of samples fixating target (y-axis) in Exp. 5.
+(ref:E5calcorr-caption) Correlation between calibration accuracy (x-axis) and proportion of samples fixating target (y-axis) in Exp. 5.
 
@@
   geom_point() + geom_smooth(method="lm") +
-  labs(x="calibration accuracy", y="looking at chosen face") +
-  theme_classic() +
-  theme(panel.grid.major.x = element_blank(),
+  labs(x="Calibration Accuracy", y="Proportion Fixating Chosen Face") +
+  #theme_classic() +
+  theme_bw() +
+  theme(#panel.grid.major.x = element_blank(),
         panel.grid.minor.x = element_blank(),
         panel.grid.minor.y = element_blank(),
-        axis.title.y = element_blank())
+        #axis.title.y = element_blank()
+        )
 ```

### 2024-08-22 manuscript.Rmd
E5 edits (wordsmithing, adding back mystery exclusions)

@@
 
-50 participants for the main task were recruited on Prolific and were
-paid \$10/hour. 8 subjects, 4 from the attractiveness task group and 4 from
+Fifty participants for the main task were recruited on Prolific and were
+paid \$10/hour. <!-- Eight subjects, 4 from the attractiveness task group and 4 from
 the roundness task group, were excluded for incorrect validations.
-<!-- they were able to proceed despite bad validation?--> After this
+(They were able to proceed despite bad validation?) After this
 data exclusion, we ended up with 21 participants each for the
-attractiveness task and the roundness task. The original sample size in
-Shimojo et al. (2003) was 10 participants total.
-
-### Procedure and Design
+attractiveness task and the roundness task.
+AJ: I can't figure out why these 8 were excluded so I'm adding them back for now--> For one subject (roundess task group), eye gaze data failed to record.<!--This was one of the excluded 8--> We ended up with 25 participants in the attractiveness condition and 24 in the roundness condition.
+The original sample size in Shimojo et al.
+(2003) was 10 participants total.
+
+### Materials and Design
+
+The faces in our replication were selected from a set of 1,000 faces
+within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et
+al. were from the Ekman face database and the AR face database). These
+images were chosen because the person in each image was looking at the
+camera with a fairly neutral facial expression and appeared to be over
+the age of 18.
+Twenty-seven participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+Faces were presented one at a time and in a random  order for each participant.
+Data from three participants were excluded because
+their modal response made up more than 50% of their total responses, for a total of 24 participants in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by
+identifying two faces that 1) had a difference in mean attractiveness ratings
+that was 0.25 points or lower and 2) matched in gender, race, and age
+group (young adult, adult, or older adult).
+
+Participants were presented with each of the 19 face pairs; task condition was manipulated between subjects, such that half of participants made judgments about facial attractiveness and the other half made judgments about facial shape.
+
+### Procedure
 
@@
 During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). Participants were randomly assigned to one of two tasks:
-attractiveness or shape judgment. In the attractiveness task,
+halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). In the attractiveness task,
 participants were asked to chose the more attractice face in the pair
@@
 
-```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5. (Text did not appear on each screen.)'}
+```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5 (text did not appear on each screen).'}
 knitr::include_graphics("group-e/E5-example-figure.jpeg")
@@
 
-### Materials and Norming
-
-The faces in our replication were selected from a set of 1,000 faces
-within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et
-al. were from the Ekman face database and the AR face database.) These
-images were chosen because the person in each image was looking at the
-camera with a fairly neutral facial expression and appeared to be over
-the age of 18. 27 participants were recruited on Prolific to participate
-in stimulus norming (for attractiveness). They each viewed all 172 faces and were asked to rate
-them on a scale from 1 (less attractive) to 7 (more attractive) using a
-slider. Faces were presented one at a time and in a random order for
-each participant. Data from 3 participants were excluded because
-their mode response made up more than 50% of their total responses, for a total of 24 participants
-in the norming.
-
-Following Shimojo et al., 19 face pairs were selected by
-identifying two faces that 1) had a difference in mean attractiveness ratings
-that was 0.25 points or lower and 2) matched in gender, race, and age
-group (young adult, adult, or older adult).
-
-### Data analysis
-
+## Results
 In the original study, a video-based eye tracker was used. The eye
 movements of participants were recorded with a digital camera
-downsampled to 33.3 Hz, with eye position was then determined
+downsampled to 33.3 Hz, with eye position determined
 automatically with MediaAnalyzer software. In our study, subjects
 supplied their own cameras, so hardware sampling rate varied. However,
-data was collected at 20 Hz.`r colorize("[TODO - CONFIRM]", 'red')`
-
-## Results
+data was collected at 20 Hz. <!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this! -->
 

### 2024-08-22 group-c/E3-analysis-replication.Rmd
Edited ALL expts to have a section under Calibration that re-analyzes data with >50% calibration.

@@
 
-#### Day 1
+### Day 1
 
@@
   labs(x = "Time (ms)", y = "Cumulative Looking Score")+
-  theme_bw()+
   theme(panel.grid.minor = element_blank())
@@
 
-#### Day 2
+### Day 2
 
@@
 Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
-Using one-sample t-tests, we found no significant difference from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
+Using one-sample t-tests, we found no significant difference from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
 

### 2024-08-22 group-d/E4-analysis-calibration.Rmd
Edited ALL expts to have a section under Calibration that re-analyzes data with >50% calibration.

@@
 ```
-
+#### Re-analysis After Exclusions
 Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
@@
 
+<!--AJ: Cutting this for consistency with the other Expts
 Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 19 participants with calibration quality >75% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
 Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_great_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_great_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_great_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_great_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_great_c2 %>% pull(p.value) %>% round(digits = 2)`).
+-->

### 2024-08-22 manuscript.Rmd
Edited ALL expts to have a section under Calibration that re-analyzes data with >50% calibration.

@@
 If accuracy on the validation was too low (fewer than 50% of looks
-landed within a 200 px radius of the validation points<!--check!-->),
+landed within a 200 px radius of the validation points),
 participants were given an opportunity to re-start the calibration and
-validation steps. If the second attempt also lead to low validation
+validation steps. <!--If the second attempt also lead to low validation
 accuracy, participants were informed that they could not participate in
-the study.
+the study.(AJ: I don't think this is true, as there are Ps included that have under 50% on the second round of calibration)-->
 

### 2024-08-22 group-d/E4-analysis-calibration.Rmd
little fixes to knit the pdf

@@
 
-```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).}
+```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).'}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+

### 2024-08-22 manuscript.tex
little fixes to knit the pdf

@@
 3 and 5) or quadrants (Exps.
-2 \& 4), or composed scenes with regions of interest that varied in size (Exp.
+2 and 4), or composed scenes with regions of interest that varied in size (Exp.
 1).
@@
 age or older, fluency in English, and access to a webcam. All
-participants provided informed consent. The studies were approved by the
+participants provided informed consent. The online studies were approved by the
 Vassar College Institutional Review Board.
 
-In addition, an in-person replication was conducted for Experiment 1.
-Information about the sample is given in the Experiment 1 Method sections.
+In addition, an in-lab replication was conducted for Experiment 1.
+Information about the sample is given in the Experiment 1 Method sections. This study was approved by the Institutional Review Board at Boston College.
 
@@
 participants were given an opportunity to re-start the calibration and
-validation steps. If the second attempt also lead to low validation
-accuracy, participants were informed that they could not participate in
-the study.
+validation steps.
 
@@
 
-\subsection{Data pre-processing}\label{data-pre-processing}
-
-We used R (Version 4.4.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.5; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
-
-\section{Experiment 1}\label{experiment-1}
+\subsection{Data Pre-processing}\label{data-pre-processing}
+
+We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Version 1.8.0; Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.
+
+\section{Experiment 1a}\label{experiment-1a}
 
@@
 
-We first collected data from participants via Prolific, then conducted a follow-up in-lab replication; both the remote and the in-lab replications used WebGazer and identical materials and procedures.
-
 \subsection{Method}\label{method}
@@
 \subsubsection{Participants}\label{participants-1}
-
-\paragraph{Remote sample}\label{remote-sample}
 
@@
 
-\paragraph{In-lab sample}\label{in-lab-sample}
-
-Forty-nine participants completed the study in a lab setting.
-They were recruited via the college subject pool.
-Participants needed to be 18 years of age or older and native speakers of English.
-The study was approved by the Institutional Review Board at Boston College.
-
-\subsubsection{Procedure}\label{procedure}
-
-The task began with a 9-point eye-tracker calibration
-and validation (Figure~\ref{fig:E1-calibration-figure}).
-During the experiment, the participants were
-simultaneously presented with a visual image and a corresponding audio
-recording of a spoken sentence. Participants had to input a keyboard
-response indicating ``yes'' or ``no'' as to whether the sentence they heard
-was feasible given the visual image. There were two practice trials to
-ensure that participants understood the instructions
-before they undertook the main portion of the experiment. Participants'
-reaction times, keyboard responses, and looks to objects in the scene
-were recorded for each trial.
-
-\begin{verbatim}
-## Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
-## 3.5.0.
-## i Please use the `legend.position.inside` argument of `theme()` instead.
-## This warning is displayed once every 8 hours.
-## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-## generated.
-\end{verbatim}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E1-calibration-figure-1.pdf}
-\caption{\label{fig:E1-calibration-figure}Calibration and validation point locations for Experiment 1.
-Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.}
-\end{figure}
-
-\subsubsection{Materials \& Design}\label{materials-design}
+\subsubsection{Materials and Design}\label{materials-and-design}
 
@@
 
-\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}
+\subsubsection{Procedure}\label{procedure}
+
+The task began with a 9-point eye-tracker calibration
+and validation (Figure~\ref{fig:E1-calibration-figure}).
+During the experiment, the participants were
+simultaneously presented with a visual image and a corresponding audio
+recording of a spoken sentence. Participants had to input a keyboard
+response indicating ``yes'' or ``no'' as to whether the sentence they heard
+was feasible given the visual image. There were two practice trials to
+ensure that participants understood the instructions
+before they undertook the main portion of the experiment. Participants'
+reaction times, keyboard responses, and looks to objects in the scene
+were recorded for each trial.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1-calibration-figure-1.pdf}
+\caption{\label{fig:E1-calibration-figure}Calibration and validation point locations for Experiment 1.
+Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.}
+\end{figure}
+
+\subsection{Results}\label{results}
 
@@
 
-\subsection{Results}\label{results}
-
-\subsubsection{Remote sample}\label{remote-sample-1}
-
-\paragraph{Minimal Exclusion}\label{minimal-exclusion}
-
-The first set of analyses used minimal exclusion criteria.
-First, we eliminated participants with 0 percent of fixations in any ROIs.
-This resulted in the elimination of one participant.
-Second, we excluded participants with validation accuracy under 10 percent, resulting in an additional 5 excluded participants.
-The following analyses included 52 participants.
-
 \paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities}
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}, Panel (b).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1a-spaghetti-fig}, Panel (b).
 
@@
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
-We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).
+We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.~non-restricting = 0), object type (target = 1 vs.~distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix)\^{}{[} \texttt{lme4} syntax: \texttt{lmer\_alt(probability\ \textasciitilde{}\ object\_type*verb\_condition\ +\ (object\_type*verb\_condition\ \textbar{}\textbar{}\ subject)\ +\ (object\_type*verb\_condition\ \textbar{}\textbar{}\ scene)}.
 There were no significant effects, although the critical interaction was in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.15).
@@
 Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we did the same, we again saw that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
+When we did the same\^{}{[} \texttt{lme4} syntax: \texttt{lmer\_alt(probability\ \textasciitilde{}\ object\_type*verb\_condition\ +\ (object\_type*verb\_condition\ \textbar{}\textbar{}\ subject)\ +\ (object\_type*verb\_condition\ \textbar{}\textbar{}\ scene)}, we again saw that the critical interaction is not significant but numerically in the expected direction (\emph{b} = 0.05, \emph{SE} = 0.03, \emph{p}=0.20).
 
@@
 Finally, we addressed whether participants looked to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
-On average, participants looked to the target 349 ms after the noun onset in the restrictive condition James, Minnihan, \& Watson (2023) and 452 ms after the noun onset in the non-restrictive condition James et al.
+On average, participants looked to the target 335 ms after the noun onset in the restrictive condition James, Minnihan, \& Watson (2023) and 435 ms after the noun onset in the non-restrictive condition James et al.
 (2023).
@@
 
-We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
-There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
-
-\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}
-
-The second set of analyses used more aggressive exclusion criteria.
-First, we eliminated participants with 20 percent of their fixations or fewer landing in any ROIs.
-This resulted in the elimination of 15 participants.
-Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 35 participants.
-The following analyses included 22 participants.
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes\^{}{[} \texttt{lme4} syntax: \texttt{lmer\_alt(time\ \textasciitilde{}\ verb\_condition*verb\_duration\ +\ (verb\_condition\ \textbar{}\textbar{}\ subject)\ +\ (verb\_condition\ \textbar{}\textbar{}\ scene)}.
+There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.60, \emph{SE} = 85.43, \emph{p}=0.17).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1-calib-effect-1.pdf}
+\caption{\label{fig:E1-calib-effect}Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).}
+\end{figure}
+
+\subsubsection{Calibration}\label{calibration}
+
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
+Calibration quality varied widely, ranging from 3.16\% to 98.87\%.
+
+We tested whether a participant's calibration quality was correlated with their effect size.
+There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
+Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.10, \emph{p} = 0.49.
+Figure~\ref{fig:E1-calib-effect} plots the relation between calibration scores and Effect 3.
+The figure makes clear that there is a large proportion of participants with calibration scores under 50\%.
+
+\paragraph{Re-analysis After Exclusions}\label{re-analysis-after-exclusions}
+
+We re-analyzed the data after excluding participants with calibration scores under 50\% (N = 35). The following analyses thus included 22 participants.
 
@@
 The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction was not statistically significant (Pre-noun-onset window: \emph{b} = 0.07, \emph{SE} = 0.06, \emph{p}=0.23; Pre-verb-offset window: \emph{b} = 0.05, \emph{SE} = 0.05, \emph{p}=0.28).
-However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (\emph{b} = -193.35, \emph{SE} = 96.33, \emph{p}=0.05).
-
-\paragraph{Calibration}\label{calibration}
-
-Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
-Calibration quality varied widely, ranging from 3.16\% to 98.87\%.
-
-We tested whether a participant's calibration quality was correlated with their effect size.
-There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
-Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.04, \emph{p} = 0.78.
-In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
-This was not the case in the in-lab sample (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
-
-\subsubsection{In-lab sample}\label{in-lab-sample-1}
-
-\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}
-
-As in the remote sample, we checked whether there were participants with 0 percent of fixations in any ROIs and there were none.
-We then excluded participants with validation accuracy under 10 percent, resulting in 2 excluded participants.
-The following analyses included 47 participants.
+However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded a statistically significant result, unlike in the previous set of analyses with all participants included (\emph{b} = -193.35, \emph{SE} = 96.33, \emph{p}=0.05).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1a-spaghetti-fig-1.pdf}
+\caption{\label{fig:E1a-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions.}
+\end{figure}
+
+\subsection{Discussion}\label{discussion}
+
+Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
+A comparison to published data (James et al., 2023) demonstrates that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
+After eliminating participants with validation accuracy under 50\% and/or 10\% or fewer fixations to any ROIs, we were left with only 22 of the original 60 participants.
+Analyses on this subset resulted in one effect reaching statistical significance (shorter target fixation latencies in the restricting vs.~non-restricting verb condition).
+Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to isolate the potential causes.
+
+\section{Experiment 1b}\label{experiment-1b}
+
+Experiment 1b tested whether the failure to replicate significant condition effects in Experiment 1a was due to features of conducting the study remotely (i.e.~varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or \texttt{webgazer} \emph{per se}.
+Thus, Experiment 1b took place in a lab setting with undergraduate participants but otherwise used the same Method as Experiment 1a.
+
+\subsection{Method}\label{method-1}
+
+\subsubsection{Participants}\label{participants-2}
+
+Forty-nine participants completed the study in a lab setting.
+They were recruited via the Boston College subject pool.
+Participants needed to be 18 years of age or older and native speakers of English.
+
+\subsubsection{Materials and Design}\label{materials-and-design-1}
+
+Materials were identical to those in Experiment 1a.
+
+\subsubsection{Procedure}\label{procedure-1}
+
+After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
+
+\subsubsection{Apparatus}\label{apparatus}
+
+HELP
+
+\subsection{Results}\label{results-1}
 
@@
 This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin.
-Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1-spaghetti-fig}, Panel (c).
+Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \ref{fig:E1b-spaghetti-fig}, Panel (b).
+The results from Experiment 1a are copied here for ease of comparison (Panel a).
 
@@
 Finally, we addressed whether participants looked to the target faster in the restrictive vs.~the non-restrictive condition, starting after the onset of the verb.
-On average, participants looked to the target 397 ms after the noun onset in the restrictive condition and 376 ms after the noun onset in the non-restrictive condition.
+On average, participants looked to the target 405 ms after the noun onset in the restrictive condition and 399 ms after the noun onset in the non-restrictive condition.
 As in the remote sample, the latencies are overall slower than in results published by Altmann \& Kamide (1999) and James et al.~(2023).
@@
 We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
-There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (\emph{b} = 21.70, \emph{SE} = 115.32, \emph{p}=0.85).
-Effects of verb duration and its interaction with condition were also not statistically significant (duration: \emph{b} = -0.58, \emph{SE} = 0.55, \emph{p}=0.30; interaction: \emph{b} = -0.49, \emph{SE} = 0.96, \emph{p}=0.61 )
-
-\paragraph{Calibration}\label{calibration-1}
+There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (\emph{b} = 2.88, \emph{SE} = 117.68, \emph{p}=0.98).
+Effects of verb duration and its interaction with condition were also not statistically significant (duration: \emph{b} = -0.58, \emph{SE} = 0.54, \emph{p}=0.30; interaction: \emph{b} = -0.60, \emph{SE} = 0.96, \emph{p}=0.53 )
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1b-calib-effect-1.pdf}
+\caption{\label{fig:E1b-calib-effect}Calibration scores plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.}
+\end{figure}
+
+\subsubsection{Calibration}\label{calibration-1}
 
 As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from 5.13\% to 97.89\%.
-
-We tested whether a participant's calibration quality was correlated with their effect size.
-Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's \emph{r} = -0.24, \emph{p} = 0.11; pre-verb-offset: Pearson's \emph{r} = -0.19, \emph{p} = 0.20; first fixation: Pearson's \emph{r} = -0.12, \emph{p} = 0.41.
-However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = -0.16, \emph{p} = 0.29).
-
-\paragraph{Aggressive Exclusion}\label{aggressive-exclusion-1}
-
-The second set of analyses used more aggressive exclusion criteria.
-First, we eliminated participants with 20 percent of fixations or fewer landing in any ROIs.
-This resulted in the elimination of 7 participants.
-Second, we excluded participants with validation accuracy under 50 percent, which eliminated an additional 23 participants.
-The following analyses included 26 participants.
+Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's \emph{r} = -0.24, \emph{p} = 0.11; pre-verb-offset: Pearson's \emph{r} = -0.19, \emph{p} = 0.20; first fixation: Pearson's \emph{r} = -0.16, \emph{p} = 0.29.
+Figure~\ref{fig:E1-calib-effect} plots the relation between calibration scores and Effect 3.
+
+\paragraph{Re-analysis After Exclusions}\label{re-analysis-after-exclusions-1}
+
+Again, we excluded participants with validation accuracy under 50\%, which eliminated 23 participants. The following analyses included 26 participants.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/E1-spaghetti-fig-1.pdf}
-\caption{\label{fig:E1-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+\includegraphics{manuscript_files/figure-latex/E1b-spaghetti-fig-1.pdf}
+\caption{\label{fig:E1b-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
 The vertical line marks the mean noun onset time across trials and conditions.}
@@
 
-\subsection{Discussion}\label{discussion}
+\subsection{Discussion}\label{discussion-1}
 
 Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
-In the remote sample, results were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance; the one exception was in comparing first target fixation latencies across verb conditions, but only when aggressive exclusion criteria were applied to participants (INSERT WHAT THOSE CRITERIA WERE).
+In Experiment 1a, results from the remote samplewere in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance.
 To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting.
 Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
-This suggests the problem was not with running the study online or due to working with a more diverse population.
+This suggests the problem was not with running the study online or due to working with a more diverse population via Prolific.
 
 Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking.
-Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
-Further evidence comes from (Prystauka et al., 2023), who ran a modified version of the Altmann and Kamide study with only 4 objects, allowing larger, more distinct ROIs.
+Notably, the ROIs were tightly drawn around the five to six objects in each scene (drawing larger ROIs in these scenes would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+Further evidence comes from a recent \texttt{webgazer} study that successfully replicated a modified version of the Altmann and Kamide study with only four objects, each in separate quadrants, allowing for larger, more distinct ROIs (Prystauka et al., 2023).
 
@@
 
-\subsection{Method}\label{method-1}
+\subsection{Method}\label{method-2}
 
@@
 
-\subsubsection{Participants}\label{participants-2}
-
-60 participants were paid for their participation.
+\subsubsection{Participants}\label{participants-3}
+
+Sixty participants were paid for their participation.
 The sample size was motivated in part by budget constraints, but was
 nonetheless 2.5x larger than the original sample size of 24).
-Data from 1 participant were not properly
+Data from one participant were not properly
 recorded due to unknown technical issues, so data from 59 participants
@@
 
-\subsubsection{Procedure}\label{procedure-1}
+\subsubsection{Materials and Design}\label{materials-and-design-2}
+
+The experiment consisted of two blocks each composed of an encoding
+phase and a recall phase.
+The two blocks differed by whether the recall phase was in the free-viewing or fixed-viewing condition, as described in the Procedure.
+Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first.
+During each encoding phase, participants saw a
+grid indicating the four quadrants of the screen. Each quadrant
+contained six cartoon images of items belonging to the same category. The four categories were humanoids, household objects, animals, and
+methods of transportation (see Figure~\ref{fig:E2-example-trial}). Different images were used in each block; there were 48 unique images total across the experiment.
+
+Each recall phase presented participants with a blank screen with a central fixation cross as they listened to true/false statements testing their recall of the previous grid.
+Each statement fell into either an interobject or intraobject
+condition. Interobject statements were those that compared two different
+items in the grid (e.g.~``The skeleton is to the left of the robot''),
+while intraobject statements were those that asked about the orientation
+of a single item (e.g.~``The bus is facing right''). There were 48 total
+statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
+
+\begin{figure}
+\centering
+\includegraphics{group-b/E2-example-figure.jpeg}
+\caption{\label{fig:E2-example-trial}Example trial from Experiment 2.}
+\end{figure}
+
+\subsubsection{Procedure}\label{procedure-2}
 
@@
 
-The experiment consisted of two blocks each composed of an encoding
-phase and a recall phase. During the encoding phase, participants saw a
-grid indicating the four quadrants of the screen. Each quadrant
-contained six images of items belonging to the same category (see Figure~\ref{fig:E2-example-trial}).
-The four categories were humanoids, household objects, animals, and
-methods of transportation.
-Each of the four quadrants was presented one at a time. First, a list of
+Participants received instructions that included an example grid and an explicit request that they not use any tools to help them during encoding.
+Participants then began their first encoding phase.
+Each of the four quadrants was presented one at a time.
+First, a list of
 the items in the quadrant was shown, then the pictures of items were displayed in the quadrant.
@@
 
-\begin{figure}
-\centering
-\includegraphics{group-b/E2-example-figure.jpeg}
-\caption{\label{fig:E2-example-trial}Example trial from Experiment 2.}
-\end{figure}
-
-During the recall phase, participants listened to statements and
+Participants then entered the first recall phase, in which they listened to the 48 statements and
 responded by pressing the `F' key for false statements and `T' for true
-ones. Each statement fell into either an interobject or intraobject
-condition. Interobject statements were those that compared two different
-items in the grid (e.g.~``The skeleton is to the left of the robot''),
-while intraobject statements were those that asked about the orientation
-of a single item (e.g.~``The bus is facing right''). There were 48 total
-statements, with 24 interobject and 24 intraobject statements split
-evenly among the four quadrants. While listening to these statements, in
+ones. While listening to these statements, in
 the free-viewing block, participants saw a blank screen and were allowed
@@
 
-\subsection{Results}\label{results-1}
-
-\subsubsection{Replication}\label{replication}
-
-\textbf{Eye-gaze}.
+\subsection{Results}\label{results-2}
+
+\subsubsection{Eye-gaze}\label{eye-gaze}
+
 Looks during the retrieval period were categorized as belonging to one of four quadrants based on the x,y coordinates.
 The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding.
-The other three quadrants were semi-randomly labeled ``first'', ``second,'' third'' (e.g., when the critical quadrant was in the top left, the ``first'' quadrant was the top right quadrant, but when the critical quadrant was in the top right, ``first'' corresponded to bottom right, etc.).
+The other three quadrants were labeled ``first'', ``second,'' and ``third'' depending upon the location of the critical quadrant (e.g., when the critical quadrant was in the top left, the ``first'' quadrant was the top right quadrant, but when the critical quadrant was in the top right, ``first'' corresponded to bottom right, etc.).
 In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \ref{fig:E2-gaze-fig-both-conds}).
-This bias appeared larger in the free-viewing condition, suggesting that the manipulation was (somewhat) effective.
+This bias appeared larger in the free-viewing condition, suggesting that the manipulation was somewhat effective.
 
@@
 This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.}.
-Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001 )
+Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.01, \emph{p}\textless0.001, third: \emph{b} = -0.05, \emph{SE} = 0.01, \emph{p}\textless0.001).
 
@@
 
-\textbf{Response Time and Accuracy}. Participants' response times and accuracies on memory questions are summarized in Figure \ref{fig:E2-rt-acc-fig}.
+\subsubsection{Response Time and Accuracy}\label{response-time-and-accuracy}
+
+Participants' response times and accuracies on memory questions are summarized in Figure \ref{fig:E2-rt-acc-fig}.
 Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing\_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
@@
 
-One possibility is that in-lab participants were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
+One possibility is that the in-lab participants in Johansson and Johansson (2014) were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
 When analyzing results from the subset of participants (N = 25) who were most compliant during the fixed-viewing block (at least 25\% of their looks fell within 20\% of the center of the display), the viewing condition effects and the interactions were not signficant.
@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between 17.78 and 100 \%).
-The quality of a participant's calibration was not significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.20, \emph{p} = 0.14) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.
-
-\subsection{Discussion}\label{discussion-1}
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E2-calib-effect-1.pdf}
+\caption{\label{fig:E2-calib-effect}Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).}
+\end{figure}
+
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, averaging initial calibration (or re-calibration for participants who repeated calibration) and calibration at the halfway point.
+Calibration scores varied substantially (between 17.34 and 100 \%).
+The quality of a participant's calibration was not significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.21, \emph{p} = 0.11) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure~\ref{fig:E2-calib-effect}).
+
+\paragraph{Re-analysis After Exclusions}\label{re-analysis-after-exclusions-2}
+
+There were 12 participants whose calibration score was under 50\%.
+When those participants were removed from the analyses, critical results were in line with the main analyses: there remains a clear gaze bias in the free-viewing condition (first: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001, second: \emph{b} = -0.08, \emph{SE} = 0.02, \emph{p}\textless0.001, third: \emph{b} = -0.06, \emph{SE} = 0.01, \emph{p}\textless0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.
+
+\subsection{Discussion}\label{discussion-2}
 
@@
 
-\subsection{Method}\label{method-2}
+\subsection{Method}\label{method-3}
 
@@
 
-\subsubsection{Participants}\label{participants-3}
+\subsubsection{Participants}\label{participants-4}
 
@@
 
-\subsubsection{Procedure}\label{procedure-2}
+\subsubsection{Materials and Design}\label{materials-and-design-3}
+
+Stimuli consisted of color photographs of common objects (e.g.~an apple, a key, etc.).
+We selected 96 unique images from the stimulus set provided by Konkle, Brady, Alvarez, and Oliva (2010), which contains multiple objects from hundreds of unique categories.
+We selected images in 48 pairs from the same object category such that each critical object had a corresponding foil object during the recognition test (e.g.~one red apple and one green apple).
+All images are of a single object on a white background.
+
+Stimulus sets were created to present participants with 24 presentation trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
+Each presentation trial screen presented two identical images (e.g.~red apple and red apple).
+The test trial screens presented each of the previously-seen (``old'') images paired with a new image (e.g.~red apple and bicycle key).
+The recognition trial screens presented a single image that was either from the original set of 24 (seen twice across the first two phases) or was a corresponding foil for the original set (e.g.~red apple or green apple).
+Thus, each participant was exposed to 72 unique images over the course of the experiment (the 24 foils for the ``new'' images in the test phase are never seen).
+Two full stimulus lists were created to counterbalance images across participants; the images that composed the ``old'' set for one list made up the ``new'' set for the list.
+The experimental design is visually depicted in Figure~\ref{fig:E3-design-schematic}.
+
+\subsubsection{Procedure}\label{procedure-3}
 
@@
 calibration again before beginning the test phase. During this phase,
-participants again viewed 24 pairs of photographs with an interstimulus
-duration of 5 seconds. In each pair, one photograph was previously seen
-during the presentation phase, while the other was new. Which pictures
-were old or new was counterbalanced across participants.
-For half of the participants in each counterbalancing group, the new and
-old photographs were
-reversed.
+participants again viewed 24 pairs of photographs (old and new) with an interstimulus
+duration of 5 seconds.
 
@@
 interval of 12 hours to accommodate busy schedules, participants were
-given the recognition test. It consisted of 48 photographs, presented
-one at a time. Each was shown on the screen for 1 second, followed by a
-1 second interstimulus interval. Half of the photographs had been
-viewed twice on the previous day and were deemed the ``targets.'' The
-other half depicted an object with the same name as an object in one of
-the old photographs, but had not been viewed before, deemed ``foils.''
-Each photograph remained on the screen until the participants indicated
-whether or not they had seen it before by pressing `y' for yes and `n'
-for no. After they pressed one of the two keys, a prompt on the screen
+given the recognition test. Each image was shown on the screen for 1 second, followed by a
+1 second interstimulus interval.
+Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing `y' for yes and `n' for no.
+After they pressed one of the two keys, a prompt on the screen
 asked them to rate their confidence in their answer from 1 as a ``pure
@@
 the screen. No feedback on their responses was given during the test.
-
-The experimental design is visually depicted in Figure~\ref{fig:E3-design-schematic}.
 
@@
 
-\subsubsection{Materials}\label{materials}
-
-\textcolor{red}{Images were selected XXX...}
-
-\subsection{Results}\label{results-2}
-
-\paragraph{Day 1}\label{day-1}
+\subsection{Results}\label{results-3}
+
+\subsubsection{Day 1}\label{day-1}
 
@@
 The mean looking score was 0.55 (\emph{SD} = 0.10).
-This significantly greater than 0.5, \emph{t}(49) = 3.29, \emph{p} = 0.00, indicating that participants did show a preference for looking at the novel objects.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plot-cumulative-looking-score-1.pdf}
-\caption{\label{fig:plot-cumulative-looking-score}Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
-\end{figure}
-
-\paragraph{Day 2}\label{day-2}
+This was significantly greater than 0.5 (\emph{t}(49) = 3.29, \emph{p} = 0.00), indicating that participants did show a preference for looking at the novel objects.
+
+\subsubsection{Day 2}\label{day-2}
 
@@
 After excluding the 3 participants who responded correctly to all images, the average confidence rating for correct responses (M = 3.51; SD = 0.41) was significantly higher than their average confidence ratings for incorrect responses (M = 2.55; SD = 0.75), t(44) = 9.36, p = 0.00 .
-Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = -3.43 , p = 0.00.
-
-To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on day 2, we computed the correlation coefficient between day 1 looking scores and day 2 confidence/RT for each participant.
+Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = -3.43 , p = 0.00).
+
+To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 looking scores and Day 2 confidence/RT for each participant.
 Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
-Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(38) = 0.46, p = 0.65 (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(46) = 0.49, p = 0.63.
-
-\includegraphics{manuscript_files/figure-latex/Plot Looking Score Correlations-1.pdf}
+Using one-sample t-tests, we found no significant difference from 0 for the correlation between looking score and confidence ratings, t(38) = 0.46, p = 0.65 (excluding the subjects who gave the same confidence judgment for all images), nor the correlation between looking score and RT, t(46) = 0.49, p = 0.63.
+
+\subsubsection{Calibration}\label{calibration-3}
+
+To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant.
+The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed.
+
+Calibration scores were not correlated with looking scores, regardless of whether scores were computed using the halves coding method (see Figure ~@ref(fig:E3-cal-Plot-looking-score-(halves)-by-calibration) or the ROI coding method (see Figure ~@ref(fig:E3-cal-Plot-looking-score-(roi)-by-calibration)).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-cal-Plot-looking-score-(halves)-by-calibration-1.pdf}
+\caption{(\#fig:E3-cal-Plot-looking-score-(halves)-by-calibration)Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-cal-Plot-looking-score-(roi)-by-calibration-1.pdf}
+\caption{(\#fig:E3-cal-Plot-looking-score-(roi)-by-calibration)Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).}
+\end{figure}
+
+We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
+None of the four relationships showed a significant correlation (see Figure~\ref{fig:E3-cal-Plot-correlations-with-calibration-score}).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-cal-Plot-correlations-with-calibration-score-1.pdf}
+\caption{\label{fig:E3-cal-Plot-correlations-with-calibration-score}The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance.
+Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).}
+\end{figure}
+
+\paragraph{Re-analysis After Exclusions}\label{re-analysis-after-exclusions-3}
+
+As is clear from the preceding figures, there was a large number of participants (N = 12) that had calibration scores under 50\%.
+When we re-analyzed the subset that remained after those participants were excluded (N = 33), key results were aligned with the main analyses.
+The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: 0.55 (\emph{SD} = 0.10) (\emph{t}(49) = 3.29, \emph{p} = 0.00)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(20) = -0.32, p = 0.75; RT: t(24) = 0.10, p = 0.92).
 
@@
 
-The correlation between looking scores using the ROI method and the halves method is 0.76.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E3-roi correlation of looking score-1.pdf}
-\caption{(\#fig:E3-roi correlation of looking score)Correlation between looking scores calculated using ROIs and using screen halves.}
+The correlation between looking scores using the ROI method and the halves method is 0.76 (see Figure~\ref{fig:E3-roi-correlation-of-looking-score}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E3-roi-correlation-of-looking-score-1.pdf}
+\caption{\label{fig:E3-roi-correlation-of-looking-score}Correlation between looking scores calculated using ROIs and using screen halves.}
 \end{figure}
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/E3-roi Plot of cumulative looking score-1.pdf}
-\caption{(\#fig:E3-roi Plot of cumulative looking score)Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.}
-\end{figure}
-
 \paragraph{Correlations with Day 2 Performance}\label{correlations-with-day-2-performance}
@@
 
-\subsubsection{Calibration}\label{calibration-3}
-
-\paragraph{Calibration Accuracy}\label{calibration-accuracy}
-
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot Calibration Accuracy-1.pdf}
-
-\paragraph{Correlation with Effects}\label{correlation-with-effects}
-
-To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant.
-The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed.
-
-Calibration scores were not correlated with looking scores, regardless of which method was used to calculate looking scores.
-
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (halves) by calibration-1.pdf}
-
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot looking score (roi) by calibration-1.pdf}
-
-We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
-None of the four relationships showed a significant correlation.
-
-\includegraphics{manuscript_files/figure-latex/E3-cal Plot correlations with calibration score-1.pdf}
-
-\subsection{Discussion}\label{discussion-2}
+\subsection{Discussion}\label{discussion-3}
 
@@
 
-\subsection{Method}\label{method-3}
+\subsection{Method}\label{method-4}
 
@@
 
-\subsubsection{Participants}\label{participants-4}
-
-57 participants were paid \$2.50 for their participation.
+\subsubsection{Participants}\label{participants-5}
+
+Fifty-seven participants were paid \$2.50 for their participation.
 A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power.
-Note that the original study had a sample size of 24.
-
-\subsubsection{Procedure}\label{procedure-3}
+Note that Ryskin et al.~(2017) Experiment 1 had a sample size of 24.
+
+\subsubsection{Materials and Design}\label{materials-and-design-4}
+
+The images and audios presented to the participants were the same
+stimuli used in the original study. The critical
+trials were divided into modifier-biased, instrument-biased, and
+equibiased conditions, and the filler trials did not contain ambiguous
+instructions. Two lists of critical trials were made with different verb
+and instrument combinations (e.g., ``rub'' could be paired with ``panda''
+and ``crayon'' in one list and ``panda'' and ``violin'' in the second list).
+Within each list, the same verb was presented twice but each time with a
+different target instrument and animal. The lists were randomly assigned
+to the participants to make sure the effects were not caused by the
+properties of the animal or instrument images used.
+There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials.
+The list of the 27 verbs used, along with their verb bias norms, can be found in Appendix A of the original study.
+
+\subsubsection{Procedure}\label{procedure-4}
 
@@
 
-\subsubsection{Materials}\label{materials-1}
-
-The images and audios presented to the participants were the same
-stimuli used in the original study (available here ). The critical
-trials were divided into modifier-biased, instrument-biased, and
-equibiased conditions, and the filler trials did not contain ambiguous
-instructions. Two lists of critical trials were made with different verb
-and instrument combinations (e.g., ``rub'' could be paired with ``panda''
-and ``crayon'' in one list and ``panda'' and ``violin'' in the second list).
-Within each list, the same verb was presented twice but each time with a
-different target instrument and animal. The lists were randomly assigned
-to the participants to make sure the effects were not caused by the
-properties of the animal or instrument images used. The list of verbs
-used can be found in Appendix A of the original study.
-
-\subsection{Results}\label{results-3}
-
-\subsubsection{Replication}\label{replication-1}
+\subsection{Results}\label{results-4}
 
@@
 
-\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}
-
 The web version of the study qualitatively replicates the action and eye-tracking results of the original dataset (Ryskin et al., 2017).
@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between 2.22 and 97.36 \%).
+\includegraphics{manuscript_files/figure-latex/E4-calib-corr-plot-1.pdf}
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between 2.22 and 97.36\%).
 The quality of a participant's calibration significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.29, \emph{p} \textless{} 0.05).
-The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration
+The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure ~\ref{fig:E4-calib-corr-plot}).
+
+\paragraph{Re-analysis After Exclusions}\label{re-analysis-after-exclusions-4}
 
@@
 Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.10, \emph{SE} = 0.02, \emph{p} \textless{} 0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( \emph{b} = 0.02, \emph{SE} = 0.02, \emph{p} = 0.29).
-
-Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 19 participants with calibration quality \textgreater75\% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
-Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( \emph{b} = 0.11, \emph{SE} = 0.03, \emph{p} \textless{} 0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( \emph{b} = 0.05, \emph{SE} = 0.03, \emph{p} = 0.13).
 
@@
 The current version of the web experiment used a bounding box around each image to determine the ROI.
-This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as show in Figure \ref{fig:E4-example-subj-looks-ROI}a.
+This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as shown in Figure \ref{fig:E4-example-subj-looks-ROI}a.
 Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \ref{fig:E4-example-subj-looks-ROI}b).
@@
 \caption{\label{fig:E4-example-subj-looks-ROI}Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
-Magenta points indicate looks that were not categorized into an ROI}
+Magenta points indicate looks that were not categorized into an ROI.}
 \end{figure}
@@
 
-\subsection{Discussion}\label{discussion-3}
+\subsection{Discussion}\label{discussion-4}
 
 As in Ryskin et al.
-(2017) and Snedeker and Trueswell (2004), listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier, instrument or equi).
+(2017) and Snedeker and Trueswell (2004), listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier-, instrument-, or equi-).
 For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).
@@
 
-\subsection{Method}\label{method-4}
+\subsection{Method}\label{method-5}
 
@@
 
-\subsubsection{Participants}\label{participants-5}
-
-50 participants for the main task were recruited on Prolific and were
-paid \$10/hour. 8 subjects, 4 from the attractiveness task group and 4 from
-the roundness task group, were excluded for incorrect validations.
-After this
-data exclusion, we ended up with 21 participants each for the
-attractiveness task and the roundness task. The original sample size in
-Shimojo et al.~(2003) was 10 participants total.
-
-\subsubsection{Procedure and Design}\label{procedure-and-design}
+\subsubsection{Participants}\label{participants-6}
+
+Fifty participants for the main task were recruited on Prolific and were
+paid \$10/hour.
+For one subject (roundess task group), eye gaze data failed to record.
+We ended up with 25 participants in the attractiveness condition and 24 in the roundness condition.
+The original sample size in Shimojo et al.~(2003) was 10 participants total.
+
+\subsubsection{Materials and Design}\label{materials-and-design-5}
+
+The faces in our replication were selected from a set of 1,000 faces
+within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et
+al.~were from the Ekman face database and the AR face database). These
+images were chosen because the person in each image was looking at the
+camera with a fairly neutral facial expression and appeared to be over
+the age of 18.
+Twenty-seven participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+Faces were presented one at a time and in a random order for each participant.
+Data from three participants were excluded because
+their modal response made up more than 50\% of their total responses, for a total of 24 participants in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by
+identifying two faces that 1) had a difference in mean attractiveness ratings
+that was 0.25 points or lower and 2) matched in gender, race, and age
+group (young adult, adult, or older adult).
+
+Participants were presented with each of the 19 face pairs; task condition was manipulated between subjects, such that half of participants made judgments about facial attractiveness and the other half made judgments about facial shape.
+
+\subsubsection{Procedure}\label{procedure-5}
 
@@
 During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in Figure~\ref{fig:E5-example-trial}). Participants were randomly assigned to one of two tasks:
-attractiveness or shape judgment. In the attractiveness task,
+halves of the screen, one on the left and one on the right (as in Figure~\ref{fig:E5-example-trial}). In the attractiveness task,
 participants were asked to chose the more attractice face in the pair
@@
 \includegraphics{group-e/E5-example-figure.jpeg}
-\caption{\label{fig:E5-example-trial}An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}
-\end{figure}
-
-\subsubsection{Materials and Norming}\label{materials-and-norming}
-
-The faces in our replication were selected from a set of 1,000 faces
-within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et
-al.~were from the Ekman face database and the AR face database.) These
-images were chosen because the person in each image was looking at the
-camera with a fairly neutral facial expression and appeared to be over
-the age of 18. 27 participants were recruited on Prolific to participate
-in stimulus norming (for attractiveness). They each viewed all 172 faces and were asked to rate
-them on a scale from 1 (less attractive) to 7 (more attractive) using a
-slider. Faces were presented one at a time and in a random order for
-each participant. Data from 3 participants were excluded because
-their mode response made up more than 50\% of their total responses, for a total of 24 participants
-in the norming.
-
-Following Shimojo et al., 19 face pairs were selected by
-identifying two faces that 1) had a difference in mean attractiveness ratings
-that was 0.25 points or lower and 2) matched in gender, race, and age
-group (young adult, adult, or older adult).
-
-\subsubsection{Data analysis}\label{data-analysis}
+\caption{\label{fig:E5-example-trial}An example of a critical trial from Experiment 5 (text did not appear on each screen).}
+\end{figure}
+
+\subsection{Results}\label{results-5}
 
@@
 movements of participants were recorded with a digital camera
-downsampled to 33.3 Hz, with eye position was then determined
+downsampled to 33.3 Hz, with eye position determined
 automatically with MediaAnalyzer software. In our study, subjects
 supplied their own cameras, so hardware sampling rate varied. However,
-data was collected at 20 Hz.\textcolor{red}{[TODO - CONFIRM]}
-
-\subsection{Results}\label{results-4}
+data was collected at 20 Hz.
 
@@
 This duration was one standard deviation of the mean response time, ensuring that all timepoints analyzed have data from at least 67\% of trials.
-In our dataset, one standard deviation amounts to 1.85 seconds.
+In our dataset, one standard deviation amounts to 1.95 seconds.
 We then binned eyegaze data into 50 ms bins rather than the 30 ms bins used by Shimojo and colleagues, reflecting the different sampling rates.
@@
 \ref{fig:groupEMain}).
-These fit less well than in the original paper for both the attractiveness judgment (R\textsuperscript{2} = 0.84 vs.~0.91) and the roundness judgment (R\textsuperscript{2} = 0.54 vs.~0.91).
+These fit less well than in the original paper for both the attractiveness judgment (R\textsuperscript{2} = 0.80 vs.~0.91) and the roundness judgment (R\textsuperscript{2} = 0.36 vs.~0.91).
 
@@
 Qualitatively, this appears to replicate.
-However, their statistical analysis -- a Kolmogorov-Smirnov test for distance between two distributions -- is not significant (D = 0.19, p = 0.53), though it should be noted that this is a very indirect statistical test of the hypothesis and probably not very sensitive.
+However, their statistical analysis -- a Kolmogorov-Smirnov test for distance between two distributions -- is not significant (D = 0.17, p = 0.55), though it should be noted that this is a very indirect statistical test of the hypothesis and probably not very sensitive.
 
@@
 As in the previous experiments, calibration score was defined as the average proportion of samples within 200 pixels of the validation point during the final validation phase before the eye tracking is performed.
-The distribution across participants is shown in Fig.
-\ref{fig:E5cal}.
-
-\begin{figure}
-\includegraphics[width=0.45\linewidth]{manuscript_files/figure-latex/E5cal-1} \caption{Histogram of calibration success in Exp.
-5.
-Where participants required more than one calibration (N=8), only the final calibration was considered.}\label{fig:E5cal}
-\end{figure}
-
-To determine whether calibration accuracy influenced our key effects, we calculated the percentage of samples during the task in which the participant was fixating the face they ultimately chose.
-There was a significant correlation for both the attractiveness judgments (r = 0.47 {[}0.04, 0.75{]}, p = 0.03) and the roundness judgments (r = 0.60 {[}0.23, 0.82{]}, p = 0).
+Where participants required more than one calibration (N=14), only the final calibration was considered.
+
+To determine whether calibration accuracy influenced our key effects, we calculated the proportion of samples during the task in which the participant was fixating the face they ultimately chose.
+Calibration accuracy significantly correlated with fixations in both the attractiveness condition (r = 0.50 {[}0.12, 0.75{]}, p = 0.01) and the roundness condition (r = 0.25 {[}-0.18, 0.60{]}, p = 0.25).
 Inspection of Fig.
-\ref{fig:E5calcorr} reveals that this correlation is due to a handful of particpiants with calibration values below 50\%.
-
-\begin{figure}
-\includegraphics[width=0.8\linewidth]{manuscript_files/figure-latex/E5calcorr-1} \caption{Correlation between calibration accuracy (x-axis) and percentage of samples fixating target (y-axis) in Exp.
+\ref{fig:E5calcorr} reveals that this correlation is due to a handful of participants with calibration values below 50\%.
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{manuscript_files/figure-latex/E5calcorr-1} \caption{Correlation between calibration accuracy (x-axis) and proportion of samples fixating target (y-axis) in Exp.
 5.}\label{fig:E5calcorr}
@@
 
-Thus, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50\%.
-This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.79; Roundness: R\textsuperscript{2} = 0.60).
-However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.36).
+\paragraph{Re-analysis After Exclusions}\label{re-analysis-after-exclusions-5}
+
+As in the previous experiments, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50\%.
+This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.78; Roundness: R\textsuperscript{2} = 0.59).
+However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.20, p = 0.33).
 Descriptively, the results do not look substantially different (Fig.
@@
 
-\subsection{Discussion}\label{discussion-4}
+\subsection{Discussion}\label{discussion-5}
 
@@
 \url{https://doi.org/10.1177/0956797613498260}
+
+\bibitem[\citeproctext]{ref-konkle2010conceptual}
+Konkle, T., Brady, T.
+F., Alvarez, G.
+A., \& Oliva, A.
+(2010).
+Conceptual distinctiveness supports detailed visual long-term memory for real-world objects.
+\emph{Journal of Experimental Psychology: General}, \emph{139}(3), 558.
 

### 2024-08-22 group-a/E1-analysis-calibration.Rmd

@@
+<!--Not currently used: folded into E1-analysis-replication.Rmd for reasons I no longer recall-->
 <!-- # Setup 

### 2024-08-22 group-b/E2-analysis-replication.Rmd

@@
 This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.].
-Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )
+Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
 
@@
 ```{r E2-compute-acc-v2}
-# *note that paper computer accuracy as hit rate - false alarm rate*
+# *note that paper computes accuracy as hit rate - false alarm rate*
 acc.behavioral.subject.data <- behavioral.data %>%

### 2024-09-01 manuscript.tex
Render Quarto Manuscript

--- 2024-08-15 manuscript.tex
@@
 
-\subsection{Data pre-processing}\label{data-pre-processing}
+\subsection{Data Pre-processing}\label{data-pre-processing}
 
@@
 
-\section{Experiment 1}\label{experiment-1}
+\section{Experiment 1a}\label{experiment-1a}
 
@@
 worked with data collected from 58 participants.
-
-\paragraph{In-lab sample}\label{in-lab-sample}
-
-Forty-nine participants completed the study in a lab setting.
-They were recruited via the college subject pool.
-Participants needed to be 18 years of age or older and native speakers of English.
-The study was approved by the Institutional Review Board at Boston College.
 
@@
 
-\begin{verbatim}
-## Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
-## 3.5.0.
-## i Please use the `legend.position.inside` argument of `theme()` instead.
-## This warning is displayed once every 8 hours.
-## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-## generated.
-\end{verbatim}
-
 \begin{figure}
@@
 
-\subsubsection{Materials \& Design}\label{materials-design}
+\subsubsection{Materials and Design}\label{materials-and-design}
 
@@
 
-\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}
+\subsection{Results}\label{results}
 
@@
 
-\subsection{Results}\label{results}
-
-\subsubsection{Remote sample}\label{remote-sample-1}
-
 \paragraph{Minimal Exclusion}\label{minimal-exclusion}
@@
 
-We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes\^{}{[} \texttt{lme4} syntax: \texttt{lmer\_alt(time\ \textasciitilde{}\ verb\_condition*verb\_duration\ +\ (verb\_condition\ \textbar{}\textbar{}\ subject)\ +\ (verb\_condition\ \textbar{}\textbar{}\ scene)}.
 There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (\emph{b} = -121.91, \emph{SE} = 90.57, \emph{p}=0.20).
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1-calib-effect-1.pdf}
+\caption{\label{fig:E1-calib-effect}Calibration scores plotted against target advantage scores (cumulative proportion of fixations to the target minus cumulative proportion of fixations to competitors) at the end of the pre-noun time window.}
+\end{figure}
+
 \paragraph{Calibration}\label{calibration}
@@
 Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's \emph{r} = 0.03, \emph{p} = 0.83, Effect 2: Pearson's \emph{r} = -0.05, \emph{p} = 0.73, Effect 3: Pearson's \emph{r} = 0.04, \emph{p} = 0.78.
-In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
-This was not the case in the in-lab sample (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
-
-\subsubsection{In-lab sample}\label{in-lab-sample-1}
+However, when the two interaction effects were calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = 0.21, \emph{p} = 0.14).
+This is shown in Figure~\ref{fig:E1-calib-effect}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/E1a-spaghetti-fig-1.pdf}
+\caption{\label{fig:E1a-spaghetti-fig}Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+The vertical line marks the mean noun onset time across trials and conditions.}
+\end{figure}
+
+\subsection{Discussion}\label{discussion}
+
+Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
+A comparison to published data (James et al., 2023) demonstrates that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
+After eliminating participants with validation accuracy under 50\% and/or 10\% or fewer fixations to any ROIs, we were left with only 22 of the original 60 participants.
+Analyses on this subset resulted in one effect reaching statistical significance (shorter target fixation latencies in the restricting vs.~non-restricting verb condition).
+Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to isolate the potential causes.
+
+\section{Experiment 1b}\label{experiment-1b}
+
+Experiment 1b tested whether the failure to replicate significant condition effects in Experiment 1a was due to features of conducting the study remotely (i.e.~varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or \texttt{webgazer} \emph{per se}.
+Thus, Experiment 1b took place in a lab setting with undergraduate participants but otherwise used the same Method as Experiment 1a.
+
+\subsection{Method}\label{method-1}
+
+\subsubsection{Participants}\label{participants-2}
+
+Forty-nine participants completed the study in a lab setting.
+They were recruited via the Boston College subject pool.
+Participants needed to be 18 years of age or older and native speakers of English.
+
+\subsubsection{Procedure}\label{procedure-1}
+
+After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
+
+\subsubsection{Apparatus}\label{apparatus}
+
+HELP
+
+\subsubsection{Materials and Design}\label{materials-and-design-1}
+
+Materials were identical to those in Experiment 1a.
+
+\subsection{Results}\label{results-1}
 
@@
 As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from 5.13\% to 97.89\%.
-
-We tested whether a participant's calibration quality was correlated with their effect size.
 Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's \emph{r} = -0.24, \emph{p} = 0.11; pre-verb-offset: Pearson's \emph{r} = -0.19, \emph{p} = 0.20; first fixation: Pearson's \emph{r} = -0.12, \emph{p} = 0.41.
-However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e.~rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's \emph{r} = -0.16, \emph{p} = 0.29).
+
+In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
+This was not the case in the in-lab sample (Pearson's \emph{r} = -0.16, \emph{p} = 0.29).
 
@@
 
-\subsubsection{Participants}\label{participants-2}
+\subsubsection{Participants}\label{participants-3}
 
@@
 
-\subsubsection{Procedure}\label{procedure-1}
+\subsubsection{Procedure}\label{procedure-2}
 
@@
 
-\subsection{Results}\label{results-1}
+\subsection{Results}\label{results-2}
 
@@
 
-\subsection{Discussion}\label{discussion-1}
+\subsection{Discussion}\label{discussion-2}
 
@@
 
-\subsubsection{Procedure}\label{procedure-2}
+\subsubsection{Procedure}\label{procedure-3}
 
@@
 
-\subsection{Results}\label{results-2}
+\subsection{Results}\label{results-3}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/Plot Looking Score Correlations-1.pdf}
-
 \subsubsection{Effects of ROIs}\label{effects-of-rois}
@@
 
-\subsection{Discussion}\label{discussion-2}
+\subsection{Discussion}\label{discussion-3}
 
@@
 
-\subsubsection{Participants}\label{participants-4}
+\subsubsection{Participants}\label{participants-5}
 
@@
 
-\subsubsection{Procedure}\label{procedure-3}
+\subsubsection{Procedure}\label{procedure-4}
 
@@
 
-\subsection{Results}\label{results-3}
+\subsection{Results}\label{results-4}
 
@@
 
-\subsection{Discussion}\label{discussion-3}
+\subsection{Discussion}\label{discussion-4}
 
@@
 
-\subsubsection{Participants}\label{participants-5}
+\subsubsection{Participants}\label{participants-6}
 
@@
 
-\subsection{Results}\label{results-4}
+\subsection{Results}\label{results-5}
 

### 2024-10-10 manuscript.Rmd
little fixes to knit the pdf
Responding to Arial's qs

@@
   - id: '4'
-    institution: Department of Psychology & Neuroscience, Boston College
+    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions
+
+authornote: |
+  Partial funding for JKH's contributions was provided by NSF2436092. The authors declares no competing interests.
 
@@
 ### Apparatus
-HELP
+Subjects were tested on a MacIntosh laptop using the built-in Webcam. The study was run in Chrome using the same code as Exp. 1a.
 
 ## Results
-```{r E1-analysis-JoshH-lab, child = 'E1-analysis-comparison-to-Hartshorne.Rmd'}
+```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
 
@@
 In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.
-Studies with ROIs that take up half or a quarter of the participant's display, which encompasses a large number of common paradigms, are very likely to be successful, even when testing questions related to the timecourse of processing.
-However, the smaller the ROIs, the more important the calibration becomes.
-For instance, studies with four ROIs may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.
-Studies with smaller ROIs (see Experiment 1) may not be appropriate for webcam eye-tracking in its current form.
+
+## Lessons and Questions
+
+The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a Webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.
+
+First, it appears that current technology is sufficient for studies with relatively large ROIs of half or a quarter of the screen.
+While this encompasses a large number of common paradigms, it does not cover all of them, even within the Visual World Paradigm.
+It is possible that even with current technology reasonable sensitivity could be achieved with slightly smaller ROIs, but it will require more systematic investigation to determine what exactly is feasible.
+Likewise, improving the technology may result in better precision.
+However, we note that anecdotally, humans -- who have been shaped by evolution to be exquisitely atuned to eyegaze -- have difficulty determining direction with more precision than quadrants.
+(This observation is based on the experience of many developmental psychology labs that used human coders to identify eyegaze direction frame-by-frame in videos of research subjects' faces.)
+
+Note also that while ROIs the size of quadrants are feasible, good calibration is important.
+Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.
+
+Second, researchers need to take care with timing accuracy.
+Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically.
+Failure to synchronize can result in substantial inaccuracies [@slim2022moving].
+As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization.
+We recommend that future researchers use jsPsych or another package with similar documented precision.
+
+Third, it is true for any eyetracker that precise data depends on good callibration, and good callibration depends in part on lighting and background.
+We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.
 

### 2024-10-12 manuscript.Rmd

--- 2024-08-22 manuscript.Rmd
@@
 
+### Procedure
+
+```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }
+
+```
+
+```{=html}
+<!-- Qs: 
+-keyboard keys? what was the exact phrasing of the instruction? 
+-Any delay between when visual scene appears and the audio starts? 
+-Does trial end as soon as participant responds?-->
+```
 ### Materials and Design
@@
 
-### Procedure
-
-```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }
-
-```
-
-```{=html}
-<!-- Qs: 
--keyboard keys? what was the exact phrasing of the instruction? 
--Any delay between when visual scene appears and the audio starts? 
--Does trial end as soon as participant responds?-->
-```
-
 ## Results
@@
 
+### Procedure
+After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
+
+### Apparatus
+HELP
+
 ### Materials and Design
@@
 
-### Procedure
-After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
-
-### Apparatus
-HELP
-
 ## Results
-```{r E1-analysis-JoshH-lab, child = 'E1-analysis-comparison-to-Hartshorne.Rmd'}
+```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
 
@@
 
-Sixty participants were paid for their participation.
+60 participants were paid for their participation.
 The sample size was motivated in part by budget constraints, but was
 nonetheless 2.5x larger than the original sample size of 24). 
-Data from one participant were not properly
+Data from 1 participant were not properly
 recorded due to unknown technical issues, so data from 59 participants
@@
 
-### Materials and Design
+### Procedure
+
+```{r E2 calibration figure, child='group-b/E2-calibration-figure.Rmd'}
+
+```
 
 The experiment consisted of two blocks each composed of an encoding
-phase and a recall phase.
-The two blocks differed by whether the recall phase was in the free-viewing or fixed-viewing condition, as described in the Procedure.
-Participants were randomly assigned to see the
-fixed-viewing or free-viewing block first. 
-During each encoding phase, participants saw a
+phase and a recall phase. During the encoding phase, participants saw a
 grid indicating the four quadrants of the screen. Each quadrant
-contained six cartoon images of items belonging to the same category. The four categories were humanoids, household objects, animals, and
-methods of transportation (see Figure\ \@ref(fig:E2-example-trial)). Different images were used in each block; there were 48 unique images total across the experiment.
-
-Each recall phase presented participants with a blank screen with a central fixation cross as they listened to true/false statements testing their recall of the previous grid.
-Each statement fell into either an interobject or intraobject
-condition. Interobject statements were those that compared two different
-items in the grid (e.g. "The skeleton is to the left of the robot"),
-while intraobject statements were those that asked about the orientation
-of a single item (e.g. "The bus is facing right"). There were 48 total
-statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
-
-```{r E2-example-trial, fig.cap='Example trial from Experiment 2.'}
-knitr::include_graphics("group-b/E2-example-figure.jpeg")
-```
-
-### Procedure
-
-```{r E2 calibration figure, child='group-b/E2-calibration-figure.Rmd'}
-
-```
-
-Participants received instructions that included an example grid and an explicit request that they not use any tools to help them during encoding.
-Participants then began their first encoding phase.
-Each of the four quadrants was presented one at a time.
-First, a list of
+contained six images of items belonging to the same category (see Figure\ \@ref(fig:E2-example-trial)). 
+The four categories were humanoids, household objects, animals, and
+methods of transportation. 
+Each of the four quadrants was presented one at a time. First, a list of
 the items in the quadrant was shown, then the pictures of items were displayed in the quadrant. 
@@
 
-Participants then entered the first recall phase, in which they listened to the 48 statements and
+```{r E2-example-trial, fig.cap='Example trial from Experiment 2.'}
+knitr::include_graphics("group-b/E2-example-figure.jpeg")
+```
+
+During the recall phase, participants listened to statements and
 responded by pressing the 'F' key for false statements and 'T' for true
-ones. While listening to these statements, in
+ones. Each statement fell into either an interobject or intraobject
+condition. Interobject statements were those that compared two different
+items in the grid (e.g. "The skeleton is to the left of the robot"),
+while intraobject statements were those that asked about the orientation
+of a single item (e.g. "The bus is facing right"). There were 48 total
+statements, with 24 interobject and 24 intraobject statements split
+evenly among the four quadrants. While listening to these statements, in
 the free-viewing block, participants saw a blank screen and were allowed
@@
 screen throughout the recall phase. In both cases, the mouse was
-obscured from the screen.
-
-Participants then proceded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to
+obscured from the screen. Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first. Different images were used in each block.
+
+After completing both encoding-recall blocks, participants were asked to
 answer a few survey questions (such as whether they wore glasses or
@@
 
-### Materials and Design
-
-Stimuli consisted of color photographs of common objects (e.g.
-an apple, a key, etc.).
-We selected 96 unique images from the stimulus set provided by @konkle2010conceptual, which contains multiple objects from hundreds of unique categories.
-We selected images in 48 pairs from the same object category such that each critical object had a corresponding foil object during the recognition test (e.g.
-one red apple and one green apple).
-All images are of a single object on a white background.
-<!-- There are 98 unique images on OSF.
-One pair (lighter and lighter-alternate) isn't used.
--->
-
-Stimulus sets were created to present participants with 24 presentation trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
-Each presentation trial screen presented two identical images (e.g.
-red apple and red apple).
-The test trial screens presented each of the previously-seen ("old") images paired with a new image (e.g.
-red apple and bicycle key).
-The recognition trial screens presented a single image that was either from the original set of 24 (seen twice across the first two phases) or was a corresponding foil for the original set (e.g.
-red apple or green apple).
-Thus, each participant was exposed to 72 unique images over the course of the experiment (the 24 foils for the "new" images in the test phase are never seen).
-Two full stimulus lists were created to counterbalance images across participants; the images that composed the "old" set for one list made up the "new" set for the list.
-The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
-
 ### Procedure
@@
 The experiment was administered over the course of two
-consecutive days. The presentation phase and test phase occurred on
+consecutive days. It consisted of three sections: a presentation phase,
+a test phase, and a recognition test. The first two phases occurred on
 the first day, while the recognition test occurred on the second day.
@@
 During the presentation phase, participants viewed 24 pairs of identical
-images. Each pair was presented for
+color photographs depicting common objects. Each pair was presented for
 5 seconds and an interval of 5 seconds elapsed before the next pair was
@@
 calibration again before beginning the test phase. During this phase,
-participants again viewed 24 pairs of photographs (old and new) with an interstimulus
-duration of 5 seconds.
+participants again viewed 24 pairs of photographs with an interstimulus
+duration of 5 seconds. In each pair, one photograph was previously seen
+during the presentation phase, while the other was new. Which pictures
+were old or new was counterbalanced across participants.<!-- 2 lists?-->
+For half of the participants in each counterbalancing group, the new and
+old photographs were
+reversed.<!-- not sure what that last sentence means: is it about the side of the screen? or still just describing that there were 2 lists-->
 
@@
 interval of 12 hours to accommodate busy schedules, participants were
-given the recognition test. Each image was shown on the screen for 1 second, followed by a
-1 second interstimulus interval.
-Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing 'y' for yes and 'n' for no.
-After they pressed one of the two keys, a prompt on the screen
+given the recognition test. It consisted of 48 photographs, presented
+one at a time. Each was shown on the screen for 1 second, followed by a
+1 second interstimulus interval. Half of the photographs had been
+viewed twice on the previous day and were deemed the "targets." The
+other half depicted an object with the same name as an object in one of
+the old photographs, but had not been viewed before, deemed "foils."
+Each photograph remained on the screen until the participants indicated
+whether or not they had seen it before by pressing 'y' for yes and 'n'
+for no. After they pressed one of the two keys, a prompt on the screen
 asked them to rate their confidence in their answer from 1 as a "pure
@@
 the screen. No feedback on their responses was given during the test.
+
+The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
 
@@
 
+### Materials
+
+`r colorize('Images were selected XXX...','red')`
+
 ## Results
@@
 
+### Effects of ROIs
+
+```{r E3-analysis-ROIs, child='group-c/E3-analysis-roi.Rmd'}
+
+```
+
 ### Calibration
@@
 ```{r E3-analysis-calibration, child='group-c/E3-analysis-calibration.Rmd'}
-
-```
-
-### Effects of ROIs
-
-```{r E3-analysis-ROIs, child='group-c/E3-analysis-roi.Rmd'}
 
@@
 
-Fifty-seven participants were paid \$2.50 for their participation.
+57 participants were paid \$2.50 for their participation.
 A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power.
-Note that Ryskin et al.
-(2017) Experiment 1 had a sample size of 24.
-
-### Materials and Design
-
-The images and audios presented to the participants were the same
-stimuli used in the original study. The critical
-trials were divided into modifier-biased, instrument-biased, and
-equibiased conditions, and the filler trials did not contain ambiguous
-instructions. Two lists of critical trials were made with different verb
-and instrument combinations (e.g., "rub" could be paired with "panda"
-and "crayon" in one list and "panda" and "violin" in the second list).
-Within each list, the same verb was presented twice but each time with a
-different target instrument and animal. The lists were randomly assigned
-to the participants to make sure the effects were not caused by the
-properties of the animal or instrument images used.
-There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials.
-The list of the 27 verbs used, along with their verb bias norms, can be found in Appendix A of the original study.
+Note that the original study had a sample size of 24.
 
@@
 
+### Materials
+
+The images and audios presented to the participants were the same
+stimuli used in the original study (available here <link>). The critical
+trials were divided into modifier-biased, instrument-biased, and
+equibiased conditions, and the filler trials did not contain ambiguous
+instructions. Two lists of critical trials were made with different verb
+and instrument combinations (e.g., "rub" could be paired with "panda"
+and "crayon" in one list and "panda" and "violin" in the second list).
+Within each list, the same verb was presented twice but each time with a
+different target instrument and animal. The lists were randomly assigned
+to the participants to make sure the effects were not caused by the
+properties of the animal or instrument images used. The list of verbs
+used can be found in Appendix A of the original study.
+
 ## Results
@@
 
+### Comparison to in-lab data
+
 ```{r E4-analysis-comparison-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}
@@
 
-As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier-, instrument-, or equi-).
+As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier, instrument or equi).
 For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).
@@
 
-Fifty participants for the main task were recruited on Prolific and were
-paid \$10/hour. <!-- Eight subjects, 4 from the attractiveness task group and 4 from
+50 participants for the main task were recruited on Prolific and were
+paid \$10/hour. 8 subjects, 4 from the attractiveness task group and 4 from
 the roundness task group, were excluded for incorrect validations.
-(They were able to proceed despite bad validation?) After this
+<!-- they were able to proceed despite bad validation?--> After this
 data exclusion, we ended up with 21 participants each for the
-attractiveness task and the roundness task.
-AJ: I can't figure out why these 8 were excluded so I'm adding them back for now--> For one subject (roundess task group), eye gaze data failed to record.<!--This was one of the excluded 8--> We ended up with 25 participants in the attractiveness condition and 24 in the roundness condition.
-The original sample size in Shimojo et al.
-(2003) was 10 participants total.
-
-### Materials and Design
-
-The faces in our replication were selected from a set of 1,000 faces
-within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et
-al. were from the Ekman face database and the AR face database). These
-images were chosen because the person in each image was looking at the
-camera with a fairly neutral facial expression and appeared to be over
-the age of 18.
-Twenty-seven participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
-Faces were presented one at a time and in a random  order for each participant.
-Data from three participants were excluded because
-their modal response made up more than 50% of their total responses, for a total of 24 participants in the norming.
-
-Following Shimojo et al., 19 face pairs were selected by
-identifying two faces that 1) had a difference in mean attractiveness ratings
-that was 0.25 points or lower and 2) matched in gender, race, and age
-group (young adult, adult, or older adult).
-
-Participants were presented with each of the 19 face pairs; task condition was manipulated between subjects, such that half of participants made judgments about facial attractiveness and the other half made judgments about facial shape.
-
-### Procedure
+attractiveness task and the roundness task. The original sample size in
+Shimojo et al. (2003) was 10 participants total.
+
+### Procedure and Design
 
@@
 During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). In the attractiveness task,
+halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). Participants were randomly assigned to one of two tasks:
+attractiveness or shape judgment. In the attractiveness task,
 participants were asked to chose the more attractice face in the pair
@@
 
-```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5 (text did not appear on each screen).'}
+```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5. (Text did not appear on each screen.)'}
 knitr::include_graphics("group-e/E5-example-figure.jpeg")
@@
 
-## Results
+### Materials and Norming
+
+The faces in our replication were selected from a set of 1,000 faces
+within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et
+al. were from the Ekman face database and the AR face database.) These
+images were chosen because the person in each image was looking at the
+camera with a fairly neutral facial expression and appeared to be over
+the age of 18. 27 participants were recruited on Prolific to participate
+in stimulus norming (for attractiveness). They each viewed all 172 faces and were asked to rate
+them on a scale from 1 (less attractive) to 7 (more attractive) using a
+slider. Faces were presented one at a time and in a random order for
+each participant. Data from 3 participants were excluded because
+their mode response made up more than 50% of their total responses, for a total of 24 participants
+in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by
+identifying two faces that 1) had a difference in mean attractiveness ratings
+that was 0.25 points or lower and 2) matched in gender, race, and age
+group (young adult, adult, or older adult).
+
+### Data analysis
+
 In the original study, a video-based eye tracker was used. The eye
 movements of participants were recorded with a digital camera
-downsampled to 33.3 Hz, with eye position determined
+downsampled to 33.3 Hz, with eye position was then determined
 automatically with MediaAnalyzer software. In our study, subjects
 supplied their own cameras, so hardware sampling rate varied. However,
-data was collected at 20 Hz. <!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this! -->
+data was collected at 20 Hz.`r colorize("[TODO - CONFIRM]", 'red')`
+
+## Results
 

### 2024-10-12 group-b/E2-analysis-calibration.Rmd

@@
 
-# correlation between initial and halfway calibration
+# correlation between initial and halfway calibration (for folks that didn't need to redo calibration)
 ggplot(summary.data.calib.wide %>% filter(is.na(`3`)), aes(x = `1`, y = `2`))+
@@
 
-# correlation between 2 successive calibration attempts
+# correlation between 2 successive calibration attempts (only folks who redid calibration)
 ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `1`, y = `2`))+
@@
 
-# correlation between second attempt calibration and halfway
+# correlation between second attempt calibration and halfway (only folks who redid calibration)
 ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `2`, y = `3`))+
@@
   group_by(subject_id) %>% 
-  summarize(mean_percent_in_roi = mean(mean_percent_in_roi))
+  filter(calib_num == max(calib_num) | calib_num == max(calib_num)-1) %>% #AJ: excludes initial calibrations of those who recalibrated, to be in line with other Expts
+  summarize(mean_percent_in_roi = mean(mean_percent_in_roi),
+            calib_total = max(calib_num))
 
@@
 
-Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
-The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect))
+Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, averaging initial calibration (or re-calibration for participants who repeated calibration) and calibration at the halfway point.
+Calibration scores varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
+The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect)).
+
+```{r aggro exclusion}
+#Identify Ps with calibration scores under 50%
+validation.threshold.aggro <- 50
+
+e2.bad.subjects.validation.aggro <- calib.by.subj %>%
+  filter(mean_percent_in_roi <= validation.threshold.aggro) %>%
+  pull(subject_id) %>%
+  as.character()
+
+e2.n.bad.subjects.aggro <- length(e2.bad.subjects.validation.aggro) #It's 12
+
+#Get the critical data used in the main analyses, filter out "bad" subjs
+
+#Gaze
+free.view.summary.subject.data.aggro <- free.view.summary.subject.data %>%
+  filter(!subject_id %in% e2.bad.subjects.validation.aggro)
+
+#Accuracy
+acc.behavioral.subject.data.aggro <- acc.behavioral.subject.data %>%
+  filter(!subject_id %in% e2.bad.subjects.validation.aggro)
+#RT
+rt.behavioral.subject.data.aggro <- rt.behavioral.subject.data %>%
+  filter(!subject_id %in% e2.bad.subjects.validation.aggro)
+```
+
+```{r aggro reanalysis}
+#Re-run critical models
+
+#Gaze
+E2_gaze_model.aggro<-lmer(proportion ~ normalized_quadrant + (1+normalized_quadrant|subject_id), data = free.view.summary.subject.data.aggro)
+
+E2_gaze_model.aggro_tab = broom.mixed::tidy(E2_gaze_model.aggro) 
+E2_gaze_model.aggro_q1 = E2_gaze_model.aggro_tab %>% filter(term == "normalized_quadrantfirst")
+E2_gaze_model.aggro_q2 = E2_gaze_model.aggro_tab %>% filter(term == "normalized_quadrantsecond")
+E2_gaze_model.aggro_q3 = E2_gaze_model.aggro_tab %>% filter(term == "normalized_quadrantthird")
+
+#Accuracy
+E2_acc_model.aggro<-lmer(accuracy ~ relation*condition + (1|subject_id), data = acc.behavioral.subject.data.aggro)
+
+E2_acc_model.aggro_tab = broom.mixed::tidy(E2_acc_model.aggro) 
+E2_acc_model.aggro_rel = E2_acc_model.aggro_tab %>% filter(term == "relation1")
+E2_acc_model.aggro_cond = E2_acc_model.aggro_tab %>% filter(term == "condition1")
+
+#RT
+E2_RT_model.aggro<-lmer(rt ~ relation*condition + (1|subject_id), data = rt.behavioral.subject.data.aggro)
+
+E2_RT_model.aggro_tab = broom.mixed::tidy(E2_RT_model.aggro) 
+E2_RT_model.aggro_rel = E2_RT_model.aggro_tab %>% filter(term == "relation1")
+E2_RT_model.aggro_cond = E2_RT_model.aggro_tab %>% filter(term == "condition1")
+
+```
+#### Re-analysis After Exclusions
+There were `r e2.n.bad.subjects.aggro` participants whose calibration score was under 50%.
+When those participants were removed from the analyses, critical results were in line with the main analyses: there remains a clear gaze bias in the free-viewing condition (first: _b_ =  `r E2_gaze_model.aggro_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model.aggro_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model.aggro_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.

### 2024-10-22 group-a/E1-analysis-comparison-to-Hartshorne.Rmd

@@
   group_by(subject_id) %>%
-  slice_tail() %>%
-  select(subject_id, percent_in_roi) %>%
+  #slice_tail() %>%
+  select(subject_id, percent_in_roi, trial_index, phase) %>%
   unnest(percent_in_roi) %>%
+  group_by(subject_id, trial_index, phase) %>%
+  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
   group_by(subject_id) %>%
-  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
+  mutate(calib_num = row_number()) %>%
+  filter(calib_num == max(calib_num)) %>%
+  select(subject_id, M, calib_num) %>%
   mutate(subject_id = fct_reorder(subject_id, M))
@@
 
-jh.critical.trials.filtered.min <- jh.critical.trials %>%
-  filter(!subject_id %in% jh.bad.subjects.min)
+#AJ: Cut!
+# jh.critical.trials.filtered.min <- jh.critical.trials %>%
+#   filter(!subject_id %in% jh.bad.subjects.min)
+jh.critical.trials.filtered.min <- jh.critical.trials #The name is a lie :)
 
@@
 ```
-
+<!--AJ: Cut
 #### Minimal Exclusion
@@
 The following analyses included `r nlevels(droplevels(jh.critical.trials.filtered.min$subject_id))` participants.
+-->
 
@@
 jh.cumulative.fixation.windows.grouped.data.min <- jh.cumulative.fixation.windows.data.min %>%
-  filter(!subject_id %in% jh.bad.subjects.min) %>%
+  #filter(!subject_id %in% jh.bad.subjects.min) %>%
   group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
@@
 ```
-#### Calibration
+```{r E1b-calib-effect, fig.cap='Calibration scores plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
+#I picked this one because it's the same as in E1a
+ggplot(jh.cali.analy.3, aes(x=M, y=diff))+
+  geom_point()+
+  geom_smooth(method="lm", formula = y ~ x)+
+  labs(x="Calibration Score", y="Verb Effect (ms)")+
+  theme_bw()+
+  theme(panel.grid.minor = element_blank())
+
+```
+
+### Calibration
 As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
@@
 Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
-
-In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone.
-This was not the case in the in-lab sample (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).
+Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.
 
@@
 ```{r}
+#AJ: not actually using this
 prop.samples.threshold.aggro.jh <- 0.2
@@
 critical.trials.filtered.aggro.jh <- jh.critical.trials %>%
-  filter(!subject_id %in% bad.subjects.aggro.jh)
+  #filter(!subject_id %in% bad.subjects.aggro.jh)
+  filter(!subject_id %in% bad.subjects.validation.aggro.jh)
 
 n.bad.subjects.aggro.jh <- length(bad.subjects.aggro.jh)
+n.bad.subjects.validation.aggro.jh <- length(bad.subjects.validation.aggro.jh)
 ```
-#### Aggressive Exclusion
-The second set of analyses used more aggressive exclusion criteria.
-First, we eliminated participants with `r prop.samples.threshold.aggro.jh*100` percent of fixations or fewer landing in any ROIs.
-This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro.jh)` participants.
-Second, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh` percent, which eliminated an additional `r n.bad.subjects.aggro.jh - length(bad.subjects.prop.samples.aggro.jh)` participants.
-The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.
 
@@
 cumulative.fixation.windows.grouped.data.aggro.jh <- cumulative.fixation.windows.data.aggro.jh %>%
-  filter(!subject_id %in% bad.subjects.aggro.jh) %>%
+  filter(!subject_id %in% bad.subjects.validation.aggro.jh) %>%
   group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
@@
 ```
+#### Re-analysis After Exclusions
+Again, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh`%, which eliminated `r length(bad.subjects.validation.aggro.jh)` participants.
+The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.
+
 Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

### 2024-10-22 group-a/E1-analysis-comparison-to-JMW23.Rmd

@@
   geom_vline(xintercept = mean(JMW1_info$Non.relative)) +
-  theme(panel.grid=element_blank(), legend.position = "none", axis.title.x = element_blank())+
+  theme(panel.grid.minor=element_blank(), legend.position = "none", axis.title.x = element_blank())+
   ggtitle('James et al. (2023), Exp. 1')

### 2024-10-22 group-a/E1-analysis-replication.Rmd

@@
 
-critical.trials.filtered.min <- critical.trials %>%
-  filter(!subject_id %in% bad.subjects.min)
+#AJ: I'm not going to do any exclusions initially to be consistent with the other Exps
+# critical.trials.filtered.min <- critical.trials %>%
+#   filter(!subject_id %in% bad.subjects.min)
+critical.trials.filtered.min <- critical.trials #the name is a convenient lie
 
@@
 
-<!-- This is where I should say how many people were excluded, right? -->
+<!-- 
 #### Minimal Exclusion 
@@
 The following analyses included `r nlevels(droplevels(critical.trials.filtered.min$subject_id))` participants.
+(AJ: I'm not going to do any exclusions initially to be consistent with the other Exps) -->
 
@@
 cumulative.fixation.windows.grouped.data.min <- cumulative.fixation.windows.data.min %>%
-  filter(!subject_id %in% bad.subjects.min) %>%
+  #filter(!subject_id %in% bad.subjects.min) %>%
   group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
@@
 ```{r}
+
 prop.samples.threshold.aggro <- 0.2
@@
 
+#AJ: we're actually just gonna use the validation criterion (for consistency)
 critical.trials.filtered.aggro <- critical.trials %>%
-  filter(!subject_id %in% bad.subjects.aggro)
+  #filter(!subject_id %in% bad.subjects.aggro)
+  filter(!subject_id %in% bad.subjects.validation.aggro)
 
 n.bad.subjects.aggro <- length(bad.subjects.aggro)
-```
+n.bad.subjects.validation.aggro <- length(bad.subjects.validation.aggro)
+```
+<!--AJ: moving this discussion to the Calibration section
 #### Aggressive Exclusion
@@
 The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.
+-->
 
@@
 cumulative.fixation.windows.grouped.data.aggro <- cumulative.fixation.windows.data.aggro %>%
-  filter(!subject_id %in% bad.subjects.aggro) %>%
+  filter(!subject_id %in% bad.subjects.validation.aggro) %>%
   group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
@@
 ```
-We tested the same three models under these more aggressive exclusion criteria.
-The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
-However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 ```
+
+<!--Calibration stuff-->
 
@@
 
-```{r E1-calib-effect, fig.cap='Calibration scores plotted against target advantage scores (cumulative proportion of fixations to the target minus cumulative proportion of fixations to competitors) at the end of the pre-noun time window.'}
-#The one corr that came out: noun window, restricting condition only
-ggplot(cali.analy.1, aes(x=M, y=restricting))+
+```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).'}
+#I picked this one because the DV is easiest to explain, and because it's the DV where the effect comes out once you drop the "bad" participants
+ggplot(cali.analy.3, aes(x=M, y=diff))+
   geom_point()+
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Target Advantage Score")+
+  labs(x="Calibration Score", y="Verb Effect (ms)")+
   theme_bw()+
@@
 
-#### Calibration
+### Calibration
 Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point.
@@
 Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
-However, when the two interaction effects were calculated as the target advantage in the restricting condition only (i.e.
-rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).
-This is shown in Figure\ \@ref(fig:E1-calib-effect).
+Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.
+The figure makes clear that there is a large proportion of participants with calibration scores under 50%.
+
+#### Re-analysis After Exclusions
+We re-analyzed the data after excluding participants with calibration scores under 50% (N = `r n.bad.subjects.validation.aggro`).
+The following analyses thus included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.
+
+We tested the same three models under these more aggressive exclusion criteria.
+The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
+However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded a statistically significant result, unlike in the previous set of analyses with all participants included (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
 

### 2024-10-22 group-c/E3-analysis-calibration.Rmd

@@
 
-#### Calibration Accuracy
+<!--#### Calibration Accuracy-->
 
@@
 
-#### Correlation with Effects
+<!--#### Correlation with Effects-->
 
@@
 ```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance.
-Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).}
+Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).'}
 # Set up facet label names for behavioral_measure variable
@@
 ```
+
+```{r aggro exclusions}
+#Identify Ps with calibration scores under 50%
+validation.threshold.aggro <- 50
+
+e3.bad.subjects.validation.aggro <- subject.calibration.score %>%
+  filter(mean_percent_in_roi <= validation.threshold.aggro) %>%
+  pull(subject_id) %>%
+  as.character()
+
+n.e3.bad.subjects.validation.aggro <- length(e3.bad.subjects.validation.aggro)
+#26. Yikes.
+
+#Day 1: Looking scores
+t.test.data1.aggro <- t.test.data1 %>%
+  filter(!subject_id %in% e3.bad.subjects.validation.aggro)
+
+t.test.day1.aggro <- t.test(t.test.data1.aggro$M.looking.score, mu = 0.5)
+
+#Day 2: Looking scores and Confidence
+looking.confidence.correlations.subjects.filtered.aggro <- looking.confidence.correlations.subjects.filtered %>%
+  filter(!subject_id %in% e3.bad.subjects.validation.aggro)
+
+looking.confidence.correlation.t.test.aggro <- t.test(looking.confidence.correlations.subjects.filtered.aggro$r.to.z)
+
+#Day 2: Looking scores and RT
+looking.rt.correlations.subjects.filtered.aggro <- looking.rt.correlations.subjects.filtered %>%
+  filter(!subject_id %in% e3.bad.subjects.validation.aggro)
+
+looking.rt.correlation.t.test.aggro <-t.test(looking.rt.correlations.subjects.filtered.aggro$r.to.z)
+```
+
+#### Re-analysis After Exclusions
+As is clear from the preceding figures, there was a large number of participants (N = `r e2.n.bad.subjects.aggro`) that had calibration scores under 50%.
+When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-e2.n.bad.subjects.aggro`), key results were aligned with the main analyses.
+The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).

### 2024-10-22 group-c/E3-analysis-roi.Rmd

@@
 
-The correlation between looking scores using the ROI method and the halves method is `r ls.cor`.
+The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score).
 
-```{r E3-roi correlation of looking score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
+```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
 ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
@@
 
-```{r E3-roi Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+```{r E3-roi Plot of cumulative looking score, echo=FALSE, eval = FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+#This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
 ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+

### 2024-10-22 group-d/E4-analysis-ROIs.Rmd

@@
 The current version of the web experiment used a bounding box around each image to determine the ROI.
-This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as show in Figure \@ref(fig:E4-example-subj-looks-ROI)a.
+This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as shown in Figure \@ref(fig:E4-example-subj-looks-ROI)a.
 Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \@ref(fig:E4-example-subj-looks-ROI)b).
@@
 ```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
-Magenta points indicate looks that were not categorized into an ROI"}
+Magenta points indicate looks that were not categorized into an ROI."}
 p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+

### 2024-10-22 group-e/E5-analysis-replication.Rmd
fixes to get figures to display and cross-ref correctly

@@
 ```{r}
-# Excluding Subjects
-all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
-E5.excluded.n = 8
+# Excluding Subjects (AJ: why/how? I can't figure it out, so I'm putting them back in)
+# all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
+# E5.excluded.n = 8
+
+#There's an issue with Subject 603ea6a51c38def3e4140ba6: their webgazer_data is a list of length 0 instead of a dataframe like the others.
+all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6")
 
@@
 # All defaults
-include_graphics("figGroupEOrigA")
-include_graphics("figGroupEOrigB")
+include_graphics("figGroupEOrigA.png")
+include_graphics("figGroupEOrigB.png")
 plot.A
@@
 Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig.
-\@ref(fig:Shimojo)).
+\@ref(fig:groupEMain)).
 These fit less well than in the original paper for both the attractiveness judgment (R^2^ = `r round(R2.A,2)` vs.

### 2024-10-22 manuscript.Rmd

--- 2024-10-10 manuscript.Rmd
@@
 Historically, this option has not been available for eye-tracking.
-This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking [e.g., @snedeker2003using].
+This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking [@snedeker2003using].
 Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic.

### 2024-10-24 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
A bunch of edits through Experiment 2

@@
 #### Pre-noun fixations 
-In line with the previous analyses of the remote data, we asked whether participants looked more to the target than to the distractor object during the predictive time window, depending upon the verb condition.
-The first model constrained the predictive window to the time before the onset of the target noun.
-We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs.
-non-restricting = 0), object type (target = 1 vs.
-distractor = 0), and their interaction, along with random effects for participants and scenes (with no covariance between random effects because the model cannot converge with full covariance matrix).
-Unlike the remote sample, there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (_b_ = `r jh.E1_model1_obj.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj.min %>% pull(p.value) %>% round(digits = 2)`).
-Also unlike the remote sample, the critical interaction was not in the expected direction, although it was also not statistically significant (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+We ran the analysis exactly as before.
+Unlike with the remote sample, this time there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (_b_ = `r jh.E1_model1_obj.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj.min %>% pull(p.value) %>% round(digits = 2)`).
+However, the critical interaction was again not statistically significant and indeed in the wrong direction (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 #### Pre-verb-offset fixations
-Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we did the same, we again saw that the critical interaction is not significant nor in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+When we repeated this analysis, the critical interaction was again not significant, nor was it even in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 #### First target fixations after verb
-Finally, we addressed whether participants looked to the target faster in the restrictive vs.
-the non-restrictive condition, starting after the onset of the verb.
 On average, participants looked to the target `r jh.our_table1_min$Eat[4]` ms after the noun onset in the restrictive condition and `r jh.our_table1_min$Move[4]` ms after the noun onset in the non-restrictive condition.
@@
 Unlike in the remote sample, however, the difference is in the unexpected direction, such that participants looked to the target faster in the non-restrictive condition.
-
-We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes.
-There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+In any case, no effects were significant; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 Effects of verb duration and its interaction with condition were also not statistically significant (duration: _b_ = `r jh.E1_model3_dur.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_dur.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_dur.min %>% pull(p.value) %>% round(digits = 2)`; interaction: _b_ = `r jh.E1_model3_intxn.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_intxn.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_intxn.min %>% pull(p.value) %>% round(digits = 2)` )
@@
 ```
-```{r E1b-calib-effect, fig.cap='Calibration scores plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
+```{r E1b-calib-effect, fig.cap='Calibration scores in Exp.
+1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
 #I picked this one because it's the same as in E1a
@@
 Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%.
-Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
+As in Exp.
+1a, calibration quality was not significantly correlated with any of the three effects (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.
 Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.
@@
 #### Re-analysis After Exclusions
-Again, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh`%, which eliminated `r length(bad.subjects.validation.aggro.jh)` participants.
-The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.
-
+Again, we re-analyzed the data focusing on participants with validation accuracy of at least `r validation.threshold.aggro.jh`% (N = `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))`).
 Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

### 2024-10-24 group-a/E1-analysis-replication.Rmd
A bunch of edits through Experiment 2

@@
 #### Pre-noun fixations
-In our first two analyses, we asked whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+In our first two analyses, we attempted to replicate the original finding that participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
@@
 non-restricting = 0), object type (target = 1 vs.
-distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix)^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`.
-There were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`] This is analogous to the F1/F2 analyses used in the original but is more commonly used now.
+Contrary to the original study, there were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 #### Pre-verb-offset fixations
-Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
-When we did the same^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`, we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+In a follow-up analysis, Altmann and Kamide aligning the predictive time window with the offset of the verb rather than the onset of the noun as above, finding the same result: participants looked significantly more to the target than to the distractor.
+When we repeated this analysis,^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`] we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 the non-restrictive condition, starting after the onset of the verb.
-On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language].
+On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language;] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language;].
 Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
 
-We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`.
-There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+Critically, we failed to replicate the difference between conditions: participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`]
 
@@
 There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
-Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
+Calibration quality was not significantly correlated with any of the free effects (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
 Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.
+
+#### Re-analysis After Exclusions
 The figure makes clear that there is a large proportion of participants with calibration scores under 50%.
-
-#### Re-analysis After Exclusions
-We re-analyzed the data after excluding participants with calibration scores under 50% (N = `r n.bad.subjects.validation.aggro`).
-The following analyses thus included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.
-
-We tested the same three models under these more aggressive exclusion criteria.
-The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
-However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded a statistically significant result, unlike in the previous set of analyses with all participants included (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
+Thus, we re-analyzed the data with the `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants who had calibration scores of at least 50%.
+The first two models, comparing target and distractor fixations in the predictive window, produced very similar results as before; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
+However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded the expected statistically significant result (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
 

### 2024-10-24 group-b/E2-analysis-calibration.Rmd
A bunch of edits through Experiment 2

@@
 There were `r e2.n.bad.subjects.aggro` participants whose calibration score was under 50%.
-When those participants were removed from the analyses, critical results were in line with the main analyses: there remains a clear gaze bias in the free-viewing condition (first: _b_ =  `r E2_gaze_model.aggro_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model.aggro_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model.aggro_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.
+When those participants were removed from the analyses, critical results were the same: there remains a clear gaze bias in the free-viewing condition (first: _b_ =  `r E2_gaze_model.aggro_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model.aggro_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model.aggro_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.

### 2024-10-24 group-b/E2-analysis-replication.Rmd
A bunch of edits through Experiment 2

@@
 The proportions of looks across quadrants in the free-viewing condition were analyzed using a linear mixed-effects model with quadrant as the predictor (critical as the reference level).
-The model included random intercepts and slopes for participants^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`.
+The model included random intercepts and slopes for participants.^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`.
 Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent.
-This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.].
-Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
+This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.] Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
 
@@
 Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig).
-Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors.
-The model included random intercepts for participants^[ `lme4` syntax: `lmer(DV ~ relation_type*viewing_condition + (1|subject_id))`]. 
-Accuracy did not differ significantly between interobject and intraobject questions (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`).
-Participants were less accurate in the free viewing condition than the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`).
-Response times were slower for interobject (e.g., "The train is to the right of the taxi.") than intraobject (e.g., "The train is facing right.") questions (_b_ =  `r E2_RT_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
-Response times were slower in the free viewing condition than the fixed condition (_b_ =  `r E2_RT_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001).
-The interaction was not a significant predictor for response times or accuracy.
-These behavioral results are inconsistent with the original findings.
+Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors and random intercepts for participants.^[ `lme4` syntax: `lmer(DV ~ relation_type*viewing_condition + (1|subject_id))`]
+
+The original study reported RTs for interobject statements were longer in the fixed condition relative to the free-viewing condition, while there was no difference for intraobject statements, resulting in a significant interaction.
+In contrast, we found overall slower RTs for the free viewing condition (_b_ =  `r E2_RT_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001) and for interobject questions (_b_ =  `r E2_RT_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001) but no interaction.
+We also failed to replicate a significant main effect of question type on accuracy (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`), while we found an unexpected effect of viewing condition on accuracy, with higher accuracy for the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 One possibility is that the in-lab participants in @johanssonLookHereEye2014 were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper).
-When  analyzing results from the subset of participants (N = `r length(successful_fixed)`) who were most compliant during the fixed-viewing block (at least 25% of their looks fell within 20% of the center of the display), the viewing condition effects and the interactions were not signficant.
+However, restricting analyses to the subset of participants (N = `r length(successful_fixed)`) who were most compliant during the fixed-viewing block (at least 25% of their looks fell within 20% of the center of the display), the viewing condition effects and the interactions remained non-signficant.
 Given the smaller sample size we do not interpret these results further.

### 2024-10-24 manuscript.Rmd
A bunch of edits through Experiment 2

@@
 Here, we focus on webcam-based eye-tracking; we tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based format.
-Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js.
+Specifically, we carried out five experiments by integrating two javascript-based tools: jsPsych and a modified version of Webgazer.js.
 In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment.
@@
 5).
-These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution should be adapted to coarser quadrant or split-half displays.
+These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution (like Exp.
+1) should be adapted to coarser quadrant or split-half displays.
 
@@
 A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired].
-Historically, this option has not been available for eye-tracking.
-This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking [@snedeker2003using].
-Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic.
-In recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation].
-However, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
+Historically, this option has not been available for eye-tracking, since few potential subjects have expensive eyetrackers at home.
+In principal, this could be circumvented by using so-called "poor-man's" eye-tracking, in which researchers videotape the subject's face and code eye position frame-by-frame [@snedeker2003using].
+Most computers now have high-quality built-in cameras, so recording video is straightforward.
+Unfortunately, coding images frame-by-frame is extremely time-intensive, making large-sample studies unrealistic.
+However, in recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation].
+Nonetheless, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
 
 Given the potential game-changing nature of webcam-based eye-tracking, a number of research groups have investigated how well it works.
+Nearly all this work has used `Webgazer.js` --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.
 There are two potential limitations to webcam-based eye-tracking.
 First, the spatial and temporal resolution is less than what is achievable with an infrared system.
+This is less a limitation of webcams than a limitation of the information about eyegaze available in an image of a face.
+Anecdotally, researchers who use poor-man's eyetracking find it difficult to locate the gaze to anything more fine-grained than quadrants.
 Second, testing subjects over the Internet involves less control: subjects may be unable or unwilling to calibrate equipment, adjust lighting, etc., to the same level of precision typical of in-lab studies.
-Nearly all this work has used `Webgazer.js` --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.
 
@@
 Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online], dividing the screen either in half or in quadrants.
-This is particularly salient with [@prystauka2023online], which simplified [@altmannIncrementalInterpretationVerbs1999]'s design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
+This is particularly salient with [@prystauka2023online], which simplified @altmannIncrementalInterpretationVerbs1999's design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
 Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.
@@
 
-In order to validate the online eye-tracking methodology, with the particular configuration known to have the greatest temporal precision, `jsPsych` and a modification of `Webgazer`, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+In order to broaden the validation of online eye-tracking methodology, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
+Critically, we used the implementation known to have the greatest temporal precision to date: `jsPsych` and a modification of `Webgazer`.
 
@@
 First, replicating five very different studies from different research traditions decreases our reliance on any one study.
-Second, we include several ''sanity check'' analyses, such as the correlation between calibration accuracy and effect size.
+Second, we include several "sanity check" analyses, such as the correlation between calibration accuracy and effect size.
 If the effect is real but there is noise from low-accuracy eye-tracking, this correlation should be substantial.
@@
 
-We chose five high-impact eye-tracking studies involving adult subjects [for an investigation of WebGazer's validity for developmental research, see @steffan2024validation for a comparison of remote WebGazer and in-lab anticipatory looking effects in 18-27-month-old participants].
+We chose five high-impact eye-tracking studies involving adult subjects [for an comparison of remote WebGazer and in-lab anticipatory looking effects with 18-27 month-old participants, see @steffan2024validation].
 Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "naturalistic" scenes).
@@
 
-We used `r cite_r("references.bib")` for all our analyses.
+We used `r cite_r("references.bib")` for our analyses.
 
@@
 ### Participants
-Sixty participants were paid \$2.60 for their participation. Our sample size
-of participants was determined by the total run time of our experiment,
-\~10 minutes, and the allotted funding from the Vassar College Cognitive
-Science Department. From this information, we calculated a reasonable
-number of participants we could afford to compensate on Prolific. Note
-that the sample size of the original study was 24. For unknown reasons,
+Sixty participants (2.5 times the original sample of 24) were paid \$2.60 for their participation. For unknown reasons,
 2 of the subjects' results were not recorded, so in the analysis, we
@@
 Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
-A comparison to published data [@james2023language] demonstrates that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
+This is unlikely to be because the original effect is unreliable.
+Indeed, one of us had successfully replicated it previously using traditional methods [@james2023language].
+
+An eyeball comparison to published data [@altmannIncrementalInterpretationVerbs1999, @james2023language] suggests that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
 After eliminating participants with validation accuracy under 50% and/or 10% or fewer fixations to any ROIs, we were left with only 22 of the original 60 participants.
-Analyses on this subset resulted in one effect reaching statistical significance (shorter target fixation latencies in the restricting vs.
-non-restricting verb condition).
-Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to isolate the potential causes.
+Either of these facts could have resulted in low power to detect effects.
+Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to test whether the failure to replicate was due to using a remote sample or to the technology itself.
 
@@
 Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
-In Experiment 1a, results from the remote samplewere in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance.
-To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting.
-Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.
-This suggests the problem was not with running the study online or due to working with a more diverse population via Prolific.
+In Experiment 1a, results from the remote sample were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance.
+This was not due to vagaries of remote samples or working with a more diverse subject population: results from the in-lab study were, if anything, worse.
+Nor does our failure to replicate seem to be driven by subjects with poor calibration; effect sizes were not correlated with calibration success, and restricting analyses to subjects with good calibration scores only helped in one of the experiments and in only one of the three critical analyses.
 
@@
 Notably, the ROIs were tightly drawn around the five to six objects in each scene (drawing larger ROIs in these scenes would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
-Further evidence comes from a recent `webgazer` study that successfully replicated a modified version of the Altmann and Kamide study with only four objects, each in separate quadrants, allowing for larger, more distinct ROIs [@prystauka2023online].
+Further evidence comes from a recent `webgazer` study that successfully replicated the original results using modified stimuli consisting of only four objects, each in separate quadrants, allowing for larger, more distinct ROIs [@prystauka2023online].
 
@@
 
-Sixty participants were paid for their participation.
-The sample size was motivated in part by budget constraints, but was
-nonetheless 2.5x larger than the original sample size of 24). 
+Sixty participants were paid for their participation (once again, 2.5x larger than the original sample size of 24). 
 Data from one participant were not properly
@@
 
-As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located
+We replicated the key eyetracking result: As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located
 during encoding, suggesting that visuospatial information is integrated into the memory
 for objects.
-However, we did not observe a memory benefit, in terms of speed or accuracy, of spatial reinstatement via gaze position during retrieval of the picture.
-We can speculate that this may be due to the fact that participants struggled to maintain their gaze fixed in the center in the fixed-viewing condition, such that the difference between the fixed- and free-viewing conditions was minimal.
-Crucially for the current purposes, the webcam-based eye-tracking measurements were successful in replicating the key eye-tracking results.
+Interestingly, we did not replicate the behavior result: a memory benefit, in terms of speed, of spatial reinstatement via gaze position during retrieval of the picture.
+For researchers interested in that effect, this is an issue to be followed up on.
+However, it is not strictly relevant for our evaluation of gaze tracking online.
 

### 2024-11-02 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
Exps 3 and 4, mostly

@@
 
-```{r plot subjects by validation-JH, eval=F}
+```{r plot subjects by validation-JH, eval=F, out.width="50%", fig.align="center"}
 #printed? No: eval=F
@@
 ```{r E1b-calib-effect, fig.cap='Calibration scores in Exp.
-1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
+1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.', out.width="50%", fig.align="center"}
 #I picked this one because it's the same as in E1a
@@
 ```{r E1b-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions."}
+The vertical line marks the mean noun onset time across trials and conditions.", out.width="50%", fig.align="center"}
 

### 2024-11-02 group-a/E1-analysis-replication.Rmd
Exps 3 and 4, mostly

@@
 
-```{r plot subjects by validation, eval=F}
+```{r plot subjects by validation, eval=F, out.width="50%", fig.align="center"}
 ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
@@
 
-```{r make remote spaghetti plot}
+```{r make remote spaghetti plot, out.width="50%", fig.align="center"}
 
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r eval=FALSE, include=FALSE, out.width="50%", fig.align="center"}
 E1_first_fix_plot <- ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
@@
 
-```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).'}
+```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).', out.width="50%", fig.align="center"}
 #I picked this one because the DV is easiest to explain, and because it's the DV where the effect comes out once you drop the "bad" participants
@@
 ```{r E1a-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions."}
+The vertical line marks the mean noun onset time across trials and conditions.", out.width="50%", fig.align="center"}
 

### 2024-11-02 group-b/E2-analysis-calibration.Rmd
Exps 3 and 4, mostly

@@
 
-```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).'}
+```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).', out.width="50%", fig.align="center"}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+

### 2024-11-02 group-b/E2-analysis-replication.Rmd
Exps 3 and 4, mostly

@@
 
-```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE}
+```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE, out.width="50%", fig.align="center"}
 fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
@@
 ```
-```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions."}
+```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.", out.width="50%", fig.align="center"}
 
@@
 
-```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F}
+```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F, out.width="50%", fig.align="center"}
 fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
@@
 
-```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval."}
+```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval.", out.width="50%", fig.align="center"}
 acc_rt_fig<-acc_fig + rt_fig + plot_layout(guides = "collect")

### 2024-11-02 group-c/E3-analysis-calibration.Rmd
Exps 3 and 4, mostly

@@
 The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed.
+Calibration scores were not correlated with proportion looks to novel, regardless of whether scores were computed using ROIs (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-roi-by-calibration)) or split-halves (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-halves-by-calibration).
 
-Calibration scores were not correlated with looking scores, regardless of whether scores were computed using the halves coding method (see Figure \ \@ref(fig:E3-cal-Plot-looking-score-(halves)-by-calibration) or the ROI coding method (see  Figure \ \@ref(fig:E3-cal-Plot-looking-score-(roi)-by-calibration)).
-
-```{r E3-cal-Plot-looking-score-(halves)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).'}
+```{r E3-cal-Plot-looking-score-halves-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).', out.width="50%", fig.align="center"}
 ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
@@
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looking Score (Halves)")+
+  labs(x="Calibration Score", y="Looking Score halves")+
   theme_bw()+
@@
 
-```{r E3-cal-Plot-looking-score-(roi)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).'}
+```{r E3-cal-Plot-looking-score-roi-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).', out.width="50%", fig.align="center"}
 ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
@@
 
-We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures.
-None of the four relationships showed a significant correlation (see Figure\ \@ref(fig:E3-cal-Plot-correlations-with-calibration-score)).
+Similarly, there was no correlation between calibration scores with the correlation between day 2 memory performance and day 1 looking for either kind of behavioral and looking measures (see Figure\ \@ref(fig:E3-cal-Plot-correlations-with-calibration-score)).
 
 ```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance.
-Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).'}
+Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).', out.width="50%", fig.align="center"}
 # Set up facet label names for behavioral_measure variable
@@
 #### Re-analysis After Exclusions
-As is clear from the preceding figures, there was a large number of participants (N = `r e2.n.bad.subjects.aggro`) that had calibration scores under 50%.
-When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-e2.n.bad.subjects.aggro`), key results were aligned with the main analyses.
+As is clear from the preceding figures, there was a large number of participants (N = `r e3.bad.subjects.validation.aggro`) that had calibration scores under 50%.
+When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-n.e3.bad.subjects.validation.aggro`), key results were aligned with the main analyses.
 The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).

### 2024-11-02 group-c/E3-analysis-roi.Rmd
Exps 3 and 4, mostly

@@
 ---
-
-In the original experiment, the two objects on day 1 were presented on two separate monitors and gaze was coded by manually coding video recordings.
-In our replication analysis, we analyzed eye movement data using ROIs defined around the two images.
-In this section we explore an alternative coding of the eye movement data by coding simply left half vs.
-right half of the screen.
-The coarser coding may be more appropriate for webcam-based eyetracking.
 
@@
 
-The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score).
+Above we excluded looks that fell outside the ROIs.
+In contrast, the original experiment simply coded looks as being to the left or right.
+This may be more appropriate to the limited resolution of camera-based eye-gaze detection.
+We re-ran analyses based on this split-half coding criterion.
+The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score)).
 
-```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
+```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves.", out.width="50%", fig.align="center"}
 ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
@@
 ```
-
-#### Looking Scores
 
@@
 
-When looking scores are coded as left vs.
-right half of the screen, we find that participants looked more at the novel object.
-The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
-This was significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.
+We again found that participants looked more at the novel object, though at a slightly lower rate than before (`r mean(t.test.data1$M.looking.score)`; *SD* = `r sd(t.test.data1$M.looking.score)`).
+As before, this was significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.
 
@@
 
-```{r E3-roi Plot of cumulative looking score, echo=FALSE, eval = FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+```{r E3-roi Plot of cumulative looking score, echo=FALSE, eval = FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1.
+Error bars represent +/- 1 SEM.", out.width="50%", fig.align="center"}
 #This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
@@
 ```
-
-#### Correlations with Day 2 Performance
 

### 2024-11-02 group-d/E4-analysis-ROIs.Rmd
Exps 3 and 4, mostly

@@
 
-```{r, eval = F}
+```{r, eval = F, out.width="50%", fig.align="center"}
 
@@
 ```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.
-Magenta points indicate looks that were not categorized into an ROI."}
+Magenta points indicate looks that were not categorized into an ROI.", out.width="65%", fig.align="center"}
 p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
@@
 ```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
-Vertical lines indicate average onsets of animal and instrument offset by 200ms."}
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.", out.width="50%", fig.align="center"}
 
@@
 Categorizing gaze location based on which of the four quadrants of the screen the coordinates fell in, increases the overall proportions of fixations (see Figure \@ref(fig:E4-gaze-timecourse-fig-quadrants)).
-In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).
+In the _post-instrument_ window, participants's proportion of looks to the target animal in the modifier-biased condition and the equi-biased conditions were significantly greater than inthe instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).
 Effect size estimates appeared somewhat larger and noise was somewhat reduced when using the quadrant categorization relative to the bounding box-based ROIs.

### 2024-11-02 group-d/E4-analysis-calibration.Rmd
Exps 3 and 4, mostly

--- 2024-08-22 group-d/E4-analysis-calibration.Rmd
@@
 
-```{r, eval = F}
+```{r, eval = F, out.width="50%", fig.align="center"}
 ggplot(summary.data.calib)+
@@
 ```
-```{r, eval=F}
+
+```{r, eval=F, out.width="50%", fig.align="center"}
 summary.data.calib.wide = summary.data.calib %>% 
@@
 
-```{r, eval = F}
+```{r, eval = F, out.width="50%", fig.align="center"}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
@@
 
-```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).}
+```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).', out.width="50%", fig.align="center"}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
@@
 ```
-Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%).
 The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
@@
 Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
-Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).
+Participants' preference to the target animal relative to the target instrument in the modifier-biased condition and the equi-biased conditions was greater than in the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001), but the difference betwen the modifier biased condition and the equi-biased condition was not significant ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).
 

### 2024-11-02 group-d/E4-analysis-comparison-to-original.Rmd
Exps 3 and 4, mostly

@@
 
-ggplot(bind_rows(first.move.orig.summary, first.move.web.summary), 
-       aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE, alpha = study))+
-  geom_col(position=position_dodge(width=0.9), color = "black")+
-  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
-  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
-  scale_alpha_manual(values = c(0.5,1))+
-  coord_cartesian(ylim = c(0,1))+
-  theme_classic()+
-  labs(y = "Proportion of first mouse movements", x = "Bias")
+ggplot(bind_rows(
+  first.move.orig.summary %>% mutate(study_type = "Original"),
+  first.move.web.summary %>% mutate(study_type = "Web")), 
+  aes(x=bias, fill=target_type, y=M, ymin=M-SE, ymax=M+SE)) +
+  geom_col(position=position_dodge(width=0.9), color = "black") +
+  geom_errorbar(position=position_dodge(width=0.9), width=0.2) +
+  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other")) +
+  coord_cartesian(ylim = c(0,1)) +
+  theme_classic() +
+  labs(y = "Proportion of first mouse movements", x = "Bias") +
+  facet_wrap(~study_type, ncol = 1)  # This creates vertical panels
 ```

### 2024-11-02 group-d/E4-analysis-replication.Rmd
Exps 3 and 4, mostly

@@
 
-### Replication
-
 ```{r E4-filter-data-for-replication-analysis}
@@
 ```
-
-The location of initial mouse movements was used to assess whether the final interpretation of ambiguous sentences was biased by the verb.
-Figure \@ref(fig:E4-mouse-moves-fig) suggests that listeners were more likely to move their mouse first over the target instrument when the verb was equi-biased than when the verb was modifier-biased and even more so when the verb was instrument-biased.
-The opposite graded pattern can be observed for mouse movements over the target animal.
 
@@
   mutate(bias = factor(compatibility, levels = c("instrument", "equibiased", "modifier") ))
+
+first.move.web.summary <- first.move.summary
 ```
 
-```{r E4-mouse-moves-fig, fig.cap = "Proportion of first mouse movements by location and verb bias."}
+As shown in Figure \@ref(fig:E4-mouse-moves-fig-web-and-orig), the qualitative results match those of the original.
+The quantitative patterns of clicks were similar to those observed in the original dataset, though for Instrument-biased verbs, clicks were closer to evenly split between the animal and the instrument relative to the in-lab study where they were very clearly biased toward the instrument.
+A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.
+equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
+modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
 
-ggplot(first.move.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
-  geom_col(position=position_dodge(width=0.9), color = "black")+
-  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
-  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
-  coord_cartesian(ylim = c(0,1))+
-  theme_classic()+
-  labs(y = "Proportion of first mouse movements", x = NULL)
+```{r load-data-from-original-study}
+
+first.move.orig = read_tsv("original_study_data/Experiment1_clickData.txt")
+
+eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_verb.txt") %>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         #sum_dur = TA+TI+CA+CI,
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-verb-onset-pre-animal-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_animal.txt")%>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-animal-onset-pre-instrument-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_instrument.txt")%>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-instrument-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+# Summarize the data by subject, calculating proportion of trials the the first move was to the animal, instrument, or other.
+first.move.orig.subject.summary <- first.move.orig %>%
+  group_by(subject, condition) %>%
+  summarize(prop.animal = mean(clickedTargetAnimalFirst),
+            prop.instrument = mean(clickedTargetInstrumentFirst),
+            prop.other = mean(clickedTargetAnimalFirst == 0 & clickedTargetInstrumentFirst == 0 )) %>%
+  pivot_longer(c('prop.animal', 'prop.instrument', 'prop.other'), names_to="target_type", values_to="proportion")
+
+# Summarize the condition-level data for a barplot.
+first.move.orig.summary <- first.move.orig.subject.summary %>%
+  group_by(condition, target_type) %>%
+  summarize(M=mean(proportion), SE=sd(proportion)/sqrt(n())) %>% 
+  mutate(bias = factor(condition, levels = c("Inst", "Equi", "mod"), labels = c("instrument", "equibiased", "modifier") ),
+         study = "original")
+```
+
+```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.", out.width="50%", fig.align="center"}
+
+ggplot(bind_rows(
+  first.move.orig.summary %>% mutate(study_type = "Original"),
+  first.move.web.summary %>% mutate(study_type = "Web")), 
+  aes(x=bias, fill=target_type, y=M, ymin=M-SE, ymax=M+SE)) +
+  geom_col(position=position_dodge(width=0.9), color = "black") +
+  geom_errorbar(position=position_dodge(width=0.9), width=0.2) +
+  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other")) +
+  coord_cartesian(ylim = c(0,1)) +
+  theme_classic() +
+  labs(y = "Proportion of first mouse movements", x = "Bias") +
+  facet_wrap(~study_type, ncol = 1)  # This creates vertical panels
 ```
@@
 
-A mixed-effects logistic regression model was used to predict whether the first movement was on the target instrument with the verb bias condition as an orthogonally contrast-coded (instrument vs.
-equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
-modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
-Participants and items were entered as varying intercepts with by-participant varying slopes for verb bias condition^[`lme4` syntax: `glmer(is.mouse.over.instrument ~ verb_bias + (1 + verb_bias | participant) + (1 | item), family="binomial", data=d)`].
-Participants were more likely to first move their mouse over target instruments in the instrument-biased condition relative to the equi-biased and modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01).
+Participants and items were entered as varying intercepts with by-participant varying slopes for verb bias condition.^[`lme4` syntax: `glmer(is.mouse.over.instrument ~ verb_bias + (1 + verb_bias | participant) + (1 | item), family="binomial", data=d)`] Participants were more likely to first move their mouse over target instruments in the instrument-biased condition relative to the equi-biased and modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01).
 Further, participants were more likely to first move their mouse over target instruments in the equi-biased condition relative to the modifier-biased condition (_b_ =  `r E4_mouse_moves_model_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_mouse_moves_model_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01)
@@
 Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
-Figure \@ref(fig:E4-gaze-timecourse-fig) suggests that the participants made more fixations to the target animal when the verb was modifier-biased compared to when the the verb was equi-biased and they looked at the target animal least when the verb was instrument-biased.
-The pattern was reversed for looks to the target instrument.
+In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
+Results were qualitatively similar to those in the original are shown in Figure \@ref(fig:E4-gaze-timecourse-fig), though proportions of fixations to the target animal were much lower in the web version of the study.
+This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.
+Eyegaze results are shown in more detail in Figure \@ref(fig:E4-gaze-timecourse-fig).
 
@@
 
+```{r}
+first.move = read_csv("output/E4_mouse_data.csv")
+eyetracking.window.summary.by.trial = read_csv( "output/E4_eye-tracking_data.csv") %>% 
+  rename("condition" = compatibility) %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal) %>% 
+  mutate(study = "web")
+
+eyetracking.window.summary.by.trial.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>%
+   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" )
+
+eyetracking.window.summary.by.subj.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>%
+   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" ) %>% 
+  group_by(study, condition, time.window, subject) %>% 
+  summarize(mean_prop = mean(prop.fixations.animal, na.rm = T)) %>% 
+  mutate(time.window = factor(time.window, 
+                            levels = c("post-verb-onset-pre-animal-onset",
+                                       "post-animal-onset-pre-instrument-onset",
+                                       "post-instrument-onset"),
+                            labels = c('Verb to animal \n("Rub the")',
+                                       'Animal onset\n("frog with the")',
+                                       'Instrument+1500ms\n(feather...")')),
+         condition  = factor(condition, 
+                             levels = c("modifier", "equibiased", "instrument"), 
+                             labels = c("Modifier", "Equi-biased", "Instrument"))
+         ) %>% 
+  ungroup()
+
+eyetracking.window.summary.both = eyetracking.window.summary.by.subj.both %>% 
+  group_by(study, condition, time.window) %>% 
+  summarize(mean_prop = mean(mean_prop, na.rm = T), 
+            se_prop = sd(mean_prop, na.rm = T)/sqrt(n()))
+
+```
+
+```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
+Error bars reflect bootstrapped 95% CIs over subject means", out.width="50%", fig.align="center"}
+
+ggplot(eyetracking.window.summary.by.subj.both)+
+  stat_summary(aes(x=time.window, color=condition, y = mean_prop, shape = study), 
+               geom = 'point', fun = 'mean', size = 3)+
+ stat_summary(aes(x=as.numeric(time.window), y = mean_prop, linetype = study, group=paste(condition, study) ),
+             geom = 'line', fun = 'mean', alpha = 0.5, color = "grey")+
+  stat_summary(aes(x=as.numeric(time.window), y = mean_prop, color = condition, group = paste(condition , study)), 
+                geom = 'errorbar', fun.data = 'mean_cl_boot', width = 0.05)+
+  #facet_wrap(~time.window)+
+  scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values = c(1,16))+
+  scale_linetype_manual(values = c("dashed","solid"))+
+  coord_cartesian(ylim = c(0,.8))+
+  theme_classic()+
+  labs(y = "Proportion of fixations", x = NULL)
+```
+```{r, eval  = F}
+orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
+  filter(condition != "filler") %>% 
+  mutate(condition = fct_drop(condition))
+contrasts(orig.data.time.window.1$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))
+
+model.time.window.1 <- lmer(prop.fixations.animal ~ condition + (1 | subject) + (1 | trialID), data=orig.data.time.window.1 )
+summary(model.time.window.1)
+```
+
 ```{r E4-gaze-timecourse-fig, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-Vertical lines indicate average onsets of animal and instrument offset by 200ms."}
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.", out.width="50%", fig.align="center"}
 
@@
 
-In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
-Mixed-effects linear regression models were used to predict the proportions of fixations to the target animal within each time window with the verb bias condition as an orthogonally contrast-coded (instrument vs.
+Mixed-effects linear regression models were used to predict the proportions of fixations to the target animal vs.
+instrument within each time window with the verb bias condition as an orthogonally contrast-coded (instrument vs.
 equi & modifier: inst = -2/3, equi = 1/3, mod = 1/3; equi vs.
 modifier: inst = 0, equi = -1/2, mod = 1/2 ) fixed effect.
-Participants and items were entered as varying intercepts^[`lme4` syntax: `lmer(prop.fix.target.animal ~ verb_bias + (1 + verb_bias | participant) + (1 | item), data=d)`.
-A model with by-participant varying slopes for verb bias condition was first attempted but did not converge.].
+Participants and items were entered as varying intercepts.^[`lme4` syntax: `lmer(prop.fix.target.animal ~ verb_bias + (1 + verb_bias | participant) + (1 | item), data=d)`.
+A model with by-participant varying slopes for verb bias condition was first attempted but did not converge.]
+
 In the _verb-to-noun_ window, participants did not look more at the target animal in any of the verb bias conditions (Instrument vs.
@@
 Modifier: _b_ =  `r E4_ET_model1_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model1_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model1_c2 %>% pull(p.value) %>% round(digits = 2)` ).
+
 In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition and equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the  modifier biased relative to the equi-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
+
 In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).

### 2024-11-02 manuscript.Rmd
Exps 3 and 4, mostly

@@
 ```{r setup, include = FALSE, message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 library(papaja)
@@
 }
+
+#3 digits for p-values
+options(papaja.precision = list(p_value = 3))
 ```
@@
 ```{r E1-example-trial, fig.cap='Example trial from Experiment 1.
-Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.'}
+Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.', out.width="50%", fig.align="center"}
 knitr::include_graphics("group-a/E1-example-trial.jpeg")
@@
 
-```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }
+```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd', out.width="50%", fig.align="center" }
 
@@
 
-```{r E2-example-trial, fig.cap='Example trial from Experiment 2.'}
+```{r E2-example-trial, fig.cap='Example trial from Experiment 2.', out.width="50%", fig.align="center"}
 knitr::include_graphics("group-b/E2-example-figure.jpeg")
@@
 
-```{r E2 calibration figure, child='group-b/E2-calibration-figure.Rmd'}
+```{r E2 calibration figure, child='group-b/E2-calibration-figure.Rmd', out.width="50%", fig.align="center"}
 
@@
 
-The third study was a partial replication attempt of
-@mannsVisualPairedcomparisonTask2000. This experiment used the visual
+The third study was a partial replication attempt of the "looking group" condition of
+@mannsVisualPairedcomparisonTask2000 (we did not replicate their priming condition). This experiment used the visual
 paired-comparison, which involves presenting a previously-viewed image
@@
 
-```{r E3 calibration figure, child='group-c/E3-calibration-figure.Rmd'}
+```{r E3 calibration figure, child='group-c/E3-calibration-figure.Rmd', out.width="50%", fig.align="center"}
 
@@
 
-There were two modifications we made to the methods of the original
-experiment. As we were only replicating the declarative memory component
-of the original experiment, we did not have a "priming group."
-Therefore, we followed only the procedure for the "looking group."
-Additionally, for each section of the study, the stimuli were presented
-on a single screen instead of two screens due to the constraints of the
-online experiment format.
-
-```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3'}
+One aspect of the original study that we could not replicate was that we presented all stimuli on a single screen rather than two screens due to the constraints of the online experiment format.
+We had no *a priori* reason to expect this to matter.
+
+```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3', out.width="50%", fig.align="center"}
 knitr::include_graphics("group-c/E3-example-figure.jpeg")
@@
 However, there was no evidence that memory performance on day 2 was related to looking time on day 1.
-Calibration quality did not appear to impact this relationship.
+
+Thus, most of the key findings replicated.
+What should we make of the finding that failed to replicate?
+Notably, the proportion of looks to the novel object on Day 1 (54% or 55%, depending on analysis) was numerically smaller than in the original (59%), potentially decreasing the ability to detect correlations with eye-gaze.
+If so, the question is whether that is due to lower-quality eye-gaze tracking.
+This seems unlikely, because calibration quality did not appear to substantially affect this result (or any of the others).
+Alternative explanation include the well-documented decline effect (replications tend to find smaller effect sizes than the original) and the common finding that subject accuracy is lower when not testing undergraduates at elite universities.
 
@@
 
-Fifty-seven participants were paid \$2.50 for their participation.
-A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power.
-Note that Ryskin et al.
-(2017) Experiment 1 had a sample size of 24.
+Fifty-seven participants were paid \$2.50 for their participation --- three fewer than the intended sample of 60, which was not reached due to time constraints, but double the sample in Ryskin et al.
+(2017) Experiment 1.
 
@@
 
-```{r E4 calibration figure, child='group-d/E4-calibration-figure.Rmd'}
+```{r E4 calibration figure, child='group-d/E4-calibration-figure.Rmd', out.width="50%", fig.align="center"}
 
@@
 
-```{r E4-example-trial, fig.cap='An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.'}
+```{r E4-example-trial, fig.cap='An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.', out.width="50%", fig.align="center"}
 knitr::include_graphics("group-d/E4-example-figure.jpeg")
@@
 ```{r E4-analysis-replication, child='group-d/E4-analysis-replication.Rmd'}
-
-```
-
-```{r E4-analysis-comparison-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}
 
@@
 
-```{r E5 calibration figure, child='group-e/E5-calibration-figure.Rmd'}
+```{r E5 calibration figure, child='group-e/E5-calibration-figure.Rmd', out.width="50%", fig.align="center"}
 
@@
 
-```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5 (text did not appear on each screen).'}
+```{r E5-example-trial, fig.cap='An example of a critical trial from Experiment 5 (text did not appear on each screen).', out.width="50%", fig.align="center"}
 knitr::include_graphics("group-e/E5-example-figure.jpeg")

### 2024-11-02 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
Full revisions

@@
   theme(panel.grid.minor=element_blank(), legend.position = "none")+
-  ggtitle('In-lab sample')
+  ggtitle('In-lab sample') +
+  theme(panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      
+    axis.text = element_text(size=14))
 
@@
 ```
+
 ```{r E1b-calib-effect, fig.cap='Calibration scores in Exp.
@@
   theme_bw()+
-  theme(panel.grid.minor = element_blank())
+  theme(panel.grid.minor = element_blank()) +
+  theme(panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      
+    axis.text = element_text(size=14))
 
@@
   scale_x_continuous(expand=c(0.01,0.01))+
-  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")
+  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")  +
+  theme(panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      
+    axis.text = element_text(size=14))
 
@@
 ```{r E1b-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions.", out.width="50%", fig.align="center"}
+The vertical line marks the mean noun onset time across trials and conditions.", out.width="75%", fig.align="center"}
 
+E1_spag_fig_remote <- E1_spag_fig_remote +    theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 E1_panel_fig <- E1_spag_fig_remote / jh_E1_spag_fig
-E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect',  heights = unit(6, 'cm'))
+E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect') +
+    theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 

### 2024-11-02 group-a/E1-analysis-replication.Rmd
Full revisions

@@
   theme_bw()+
-  theme(panel.grid.minor = element_blank())
+  theme(panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      
+    axis.text = element_text(size=14))
 
@@
 ```{r E1a-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
-The vertical line marks the mean noun onset time across trials and conditions.", out.width="50%", fig.align="center"}
-
+The vertical line marks the mean noun onset time across trials and conditions.", out.width="75%", fig.align="center"}
+
+JMW_spag_fig <- JMW_spag_fig +    theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 E1_panel_fig <- JMW_spag_fig / E1_spag_fig_remote 
-E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect',  heights = unit(6, 'cm'))
-
-```
+E1_panel_fig + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect') +
+    theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
+```

### 2024-11-02 group-b/E2-analysis-calibration.Rmd
Full revisions

--- 2024-10-24 group-b/E2-analysis-calibration.Rmd
@@
   theme_bw()+
-  theme(panel.grid.minor = element_blank())
+  theme(panel.grid.minor = element_blank()) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```

### 2024-11-02 group-c/E3-analysis-calibration.Rmd
Full revisions

@@
 
-```{r E3-cal-Plot-looking-score-halves-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).', out.width="50%", fig.align="center"}
+```{r E3-cal-Plot-looking-score-halves-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against proportion looks to novel using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).', out.width="50%", fig.align="center"}
 ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
@@
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looking Score halves")+
+  labs(x="Calibration Score", y="Looks-to-novel halves")+
   theme_bw()+
-  theme(panel.grid.minor = element_blank())
+  theme(panel.grid.minor = element_blank()) + theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 
@@
 
-```{r E3-cal-Plot-looking-score-roi-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).', out.width="50%", fig.align="center"}
+```{r E3-cal-Plot-looking-score-roi-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against proportion looks to novel using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).', out.width="50%", fig.align="center"}
 ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
@@
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looking Score (ROIs)") +
+  labs(x="Calibration Score", y="Looks-to-novel (ROIs)") +
   theme_bw()+
-  theme(panel.grid.minor = element_blank())
+  theme(panel.grid.minor = element_blank()) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 
@@
 
-```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance.
-Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).', out.width="50%", fig.align="center"}
+```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looks-to-novel and Day 2 memory performance.
+Looks-to-novel were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).', out.width="80%", fig.align="center"}
 # Set up facet label names for behavioral_measure variable
@@
                                    look.labs))+
-  labs(x="Calibration Score", y="Correlation (Looking Score, Memory)") +
+  labs(x="Calibration Score", y="Correlation (Prop. Looks to Novel, Memory)") +
   theme_bw()+
-  theme(panel.grid.minor = element_blank())
+  theme(panel.grid.minor = element_blank()) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
@@
 #### Re-analysis After Exclusions
-As is clear from the preceding figures, there was a large number of participants (N = `r e3.bad.subjects.validation.aggro`) that had calibration scores under 50%.
+As is clear from the preceding figures, there was a large number of participants (N = `r n.e3.bad.subjects.validation.aggro`) that had calibration scores under 50%.
 When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-n.e3.bad.subjects.validation.aggro`), key results were aligned with the main analyses.
-The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).
+The looks-to-novel result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looks-to-novel remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).

### 2024-11-02 group-d/E4-analysis-replication.Rmd
Full revisions

@@
 
-```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.", out.width="50%", fig.align="center"}
+```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.", out.width="65%", fig.align="center"}
 
@@
   labs(y = "Proportion of first mouse movements", x = "Bias") +
-  facet_wrap(~study_type, ncol = 1)  # This creates vertical panels
+  facet_wrap(~study_type, ncol = 1) + theme(  # This creates vertical panels   
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
@@
 ```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
-Error bars reflect bootstrapped 95% CIs over subject means", out.width="50%", fig.align="center"}
+Error bars reflect bootstrapped 95% CIs over subject means", out.width="65%", fig.align="center"}
 
@@
   theme_classic()+
-  labs(y = "Proportion of fixations", x = NULL)
+  labs(y = "Proportion of fixations", x = NULL) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
@@
   labs(y = "Proportion of looks", x = "Time relative to verb onset (ms)")+
-  guides(color = guide_legend("Verb bias"),fill = guide_legend("Verb bias"), linetype = guide_legend("Gaze location"))
+  guides(color = guide_legend("Verb bias"),fill = guide_legend("Verb bias"), linetype = guide_legend("Gaze location")) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 fig2

### 2024-11-02 manuscript.Rmd
Full revisions

@@
 ---
-title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five “classic” cognitive science experiments"
+title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five prominent cognitive science experiments"
 shorttitle        : "Webcam eye-tracking paradigms"
@@
 
-```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3', out.width="50%", fig.align="center"}
+```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3', out.width="35%", fig.align="center"}
 knitr::include_graphics("group-c/E3-example-figure.jpeg")
@@
 We conducted five attempted replication studies using different experimental paradigms from across the cognitive sciences.
-All were successfully implemented in `jsPsych` using the `webgazer` plugin, but replication success was mixed.
+All were successfully implemented in `jsPsych` using the `webgazer` plugin, though replication was not uniform.
+
 Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with five to six ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
@@
 
+The relatively large number of statistical comparisons means that we would not expect everything to come out significant even in the best-case scenario.
+Nonetheless, there appears to be some systematicity in the patterns of significant replication.
+Most of the failures to replicate seem to be due to small ROIs (e.g., Exp.
+1) or effects that were small to begin with (e.g., Exp.
+3) or involved insensitive statistical tests (e.g., Exp.
+5).
+
 In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.

### 2024-11-03 group-c/E3-analysis-replication.Rmd

@@
 
-During day 1 of the experiment, participants viewed pairs of images, one of which was always familiar and the other unfamiliar.
-We calculated a looking score for each participant, defined as the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI.
-Gaze samples that were not in either ROI were not included in this analysis.
-A looking score of 0.5 indicates that participants looked equally often at the familiar and unfamiliar images, while a looking score above 0.5 indicates a preference for the unfamiliar object and a looking score below 0.5 indicate a preference for the familiar object.
+We calculated the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI.
+Of the `r looking.score.data %>% nrow()` trials in the experiment, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI and so were excluded from this analysis.
 
-Of the `r looking.score.data %>% nrow()` trials in the experiment, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI, and so the looking score was unknown.
-We removed these trials from this analysis.
-
-The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
-This was significantly greater than 0.5 (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`), indicating that participants did show a preference for looking at the novel objects.
+The mean proportion looks to the novel object was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`).
+This was significantly greater than 0.5 (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`), replicating the finding that participants show a preference for looking at the novel objects.
 
@@
 
-```{r plot-cumulative-looking-score, echo=FALSE, eval=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
+```{r plot-cumulative-looking-score, echo=FALSE, eval=FALSE, fig.cap="Cumulative looking to novel over the 5 second exposure during part 2 of day 1.
+Error bars represent +/- 1 SEM.", out.width="50%", fig.align="center"}
 #This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
@@
   geom_pointrange()+
-  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
+  labs(x = "Time (ms)", y = "Cumulative Looking to Novel")+
   theme(panel.grid.minor = element_blank())
@@
 
-In all of these analyses, we excluded the `r day2.test.data %>% filter(rt_recognition > 10000) %>% nrow()` (out of `r day2.test.data %>% nrow()`) trials where the response time for the recognition judgment was greater than 10 seconds.
+In Day 2 analyses, we excluded the `r day2.test.data %>% filter(rt_recognition > 10000) %>% nrow()` (out of `r day2.test.data %>% nrow()`) trials where the response time for the recognition judgment was greater than 10 seconds.
 
@@
 Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`).
+These findings replicate the original.
 
@@
 
-To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 looking scores and Day 2 confidence/RT for each participant.
+To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 proportion looks to novel and Day 2 confidence/RT for each participant.
 Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
-Using one-sample t-tests, we found no significant difference from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
+Using one-sample t-tests, failed to replicate the a significant difference from 0 for the correlation between proportion looks to the novel object and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor for the correlation with RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
 

### 2024-11-03 group-c/E3-analysis-roi.Rmd

@@
 We re-ran analyses based on this split-half coding criterion.
-The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score)).
+The correlation between proportion looks to novel using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score)).
 
-```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves.", out.width="50%", fig.align="center"}
+```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between proportion looks-to-novel calculated using ROIs and using screen halves.", out.width="50%", fig.align="center"}
 ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
@@
   geom_smooth(method="lm", formula = y~x)+
-  labs(x="Looking Score (ROIs)", y="Looking Score (Halves)")+
+  labs(x="Looks-to-Novel (ROIs)", y="Looks-to-Novel (Halves)")+
   theme_bw()+
   coord_fixed()+
-  theme(panel.grid=element_blank())
+  theme(panel.grid=element_blank()) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
@@
   geom_pointrange()+
-  labs(x = "Time (ms)", y = "Cumulative Looking Score (Halves)")+
+  labs(x = "Time (ms)", y = "Cumulative Looks-to-Novel (Halves)")+
   theme_bw()+
@@
 
-Performance on day 2 remained uncorrelated with day 1 looking scores after switching the coding of gaze.
-We found no significant different from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
+Performance on day 2 remained uncorrelated with day 1 looks-to-novel after switching the coding of gaze.
+We found no significant different from 0 for the correlation between looks-to-novel and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looks-to-novel and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

### 2024-11-03 group-d/E4-analysis-ROIs.Rmd

@@
   theme_bw()+
-  theme(legend.position = "none")
+  theme(legend.position = "none") +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 

### 2024-11-03 group-e/E5-analysis-calibration.Rmd
Edited ALL expts to have a section under Calibration that re-analyzes data with >50% calibration.

@@
 
-```{r E5cal, fig.show="hold", out.width="45%", echo=FALSE,eval=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5cal-caption)"}
+```{r E5cal, fig.show="hold", out.width="45%", echo=FALSE,eval=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5cal-caption)", , out.width="50%", fig.align="center"}
 ggplot(subject.calibration.score, aes(x=mean_percent_in_roi)) +
@@
         panel.grid.minor.y = element_blank(),
-        axis.title.y = element_blank())
+        axis.title.y = element_blank()) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
@@
 To determine whether calibration accuracy influenced our key effects, we calculated the proportion of samples during the task in which the participant was fixating the face they ultimately chose.
-Calibration accuracy significantly correlated with fixations in both the attractiveness condition (r = `r round(scorescorrs.A$estimate, 2)` [`r round(scorescorrs.A$conf.int, 2)[1]`, `r round(scorescorrs.A$conf.int, 2)[2]`], p = `r round(scorescorrs.A$p.value, 2)`) and the roundness condition (r = `r round(scorescorrs.R$estimate, 2)` [`r round(scorescorrs.R$conf.int, 2)[1]`, `r round(scorescorrs.R$conf.int, 2)[2]`], p = `r round(scorescorrs.R$p.value, 2)`).
+Calibration accuracy significantly correlated with fixations in the attractiveness condition (r = `r round(scorescorrs.A$estimate, 2)` [`r round(scorescorrs.A$conf.int, 2)[1]`, `r round(scorescorrs.A$conf.int, 2)[2]`], p = `r round(scorescorrs.A$p.value, 2)`) but not the roundness condition (r = `r round(scorescorrs.R$estimate, 2)` [`r round(scorescorrs.R$conf.int, 2)[1]`, `r round(scorescorrs.R$conf.int, 2)[2]`], p = `r round(scorescorrs.R$p.value, 2)`).
 Inspection of Fig.
@@
 
-```{r E5calcorr, fig.show="hold", out.width="80%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5calcorr-caption)"}
+```{r E5calcorr, fig.show="hold", out.width="80%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:E5calcorr-caption)", out.width="50%", fig.align="center"}
 ggplot(scores, aes(x=mean_percent_in_roi, y=prop.in.target.subject, group=task, color=task))+
@@
         #axis.title.y = element_blank()
+        ) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
   )
@@
   scale_x_reverse() + theme_classic() + 
-  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)
+  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 
@@
   scale_x_reverse() + theme_classic() + 
-  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)
+  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
 
 ```
-
-Thus, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50%.
+#### Re-analysis After Exclusions
+As in the previous experiments, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50%.
 This slightly improved the fits of the sigmoids (Attractiveness: R^2^ = `r round(R2.A,2)`; Roundness: R^2^ = `r round(R2.R,2)`).

### 2024-11-03 group-a/E1-analysis-replication.Rmd
Merged author affiliation changes

--- 2024-10-24 group-a/E1-analysis-replication.Rmd
@@
 
-save(validation.percent, file = "validation.percent.RData")
+#save(validation.percent, file = "validation.percent.RData")
 ```
@@
 
-save(pre.noun.first.looks.data.min, file = "pre.noun.first.looks.data.min.RData")
+#save(pre.noun.first.looks.data.min, file = "pre.noun.first.looks.data.min.RData")
 ```
@@
 #### Pre-noun fixations
-In our first two analyses, we attempted to replicate the original finding that participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
+In our first two analyses, we asked whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting.
 The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun.
@@
 non-restricting = 0), object type (target = 1 vs.
-distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`] This is analogous to the F1/F2 analyses used in the original but is more commonly used now.
-Contrary to the original study, there were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix)^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`.
+There were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 
-save(pre.verb.offset.first.looks.data.min, file = "pre.verb.offset.first.looks.data.min.RData")
+#save(pre.verb.offset.first.looks.data.min, file = "pre.verb.offset.first.looks.data.min.RData")
 ```
@@
 #### Pre-verb-offset fixations
-In a follow-up analysis, Altmann and Kamide aligning the predictive time window with the offset of the verb rather than the onset of the noun as above, finding the same result: participants looked significantly more to the target than to the distractor.
-When we repeated this analysis,^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`] we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
+Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above.
+When we did the same^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`, we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 
-save(first.fixation.after.verb.onset.analysis.data.min, file = "first.fixation.after.verb.onset.analysis.data.min.RData")
+#save(first.fixation.after.verb.onset.analysis.data.min, file = "first.fixation.after.verb.onset.analysis.data.min.RData")
 ```
@@
 the non-restrictive condition, starting after the onset of the verb.
-On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language;] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language;].
+On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language].
 Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.
 
-Critically, we failed to replicate the difference between conditions: participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`]
+We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`.
+There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
 
@@
 
-save(first.fixation.after.verb.onset.summary.min, file = "first.fixation.after.verb.onset.subject.summary.min.RData")
+#save(first.fixation.after.verb.onset.summary.min, file = "first.fixation.after.verb.onset.subject.summary.min.RData")
 ```
@@
 There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions).
-Calibration quality was not significantly correlated with any of the free effects (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
+Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`.
 Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.
+The figure makes clear that there is a large proportion of participants with calibration scores under 50%.
 
 #### Re-analysis After Exclusions
-The figure makes clear that there is a large proportion of participants with calibration scores under 50%.
-Thus, we re-analyzed the data with the `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants who had calibration scores of at least 50%.
-The first two models, comparing target and distractor fixations in the predictive window, produced very similar results as before; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
-However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded the expected statistically significant result (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
+We re-analyzed the data after excluding participants with calibration scores under 50% (N = `r n.bad.subjects.validation.aggro`).
+The following analyses thus included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.
+
+We tested the same three models under these more aggressive exclusion criteria.
+The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
+However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded a statistically significant result, unlike in the previous set of analyses with all participants included (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).
 

### 2024-11-03 group-b/E2-analysis-replication.Rmd

@@
   theme_bw()+
-  theme(legend.position = "none")
+  theme(legend.position = "none") + theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),     
+    axis.text = element_text(size=14)
+  )
 
@@
   labs(x = "Quadrant", y = "Mean proportion of looks")+
-  theme(legend.position = "none")
+  theme(legend.position = "none") + theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 fig
@@
   labs(x = "Quadrant", y = "Mean proportion of looks")+
-  theme(legend.position = "none")
+  theme(legend.position = "none") +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),  
+    axis.text = element_text(size=14)
+  )
 
@@
   labs(x = "Quadrant", y = "Mean proportion of looks")+
-  theme(legend.position = "none")
+  theme(legend.position = "none")    theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14), 
+    axis.text = element_text(size=14)
+  )
+
 fig.fixed
@@
   labs(x="Statement Type", y="Accuracy", color=NULL)+
-  theme_classic()
+  theme_classic() + theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
@@
   labs(x="Statement Type", y="Response Time (ms)", color=NULL)+
-  theme_classic()
+  theme_classic() +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14)
+  )
+
 ```

### 2024-11-03 group-d/E4-analysis-comparison-to-original.Rmd

@@
 
-```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online."}
+```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.", out.width="65%", fig.align="center"}
 
@@
 ```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
-Error bars reflect bootstrapped 95% CIs over subject means"}
+Error bars reflect bootstrapped 95% CIs over subject means", , out.width="75%", fig.align="center"}
 
@@
   theme_classic()+
-  labs(y = "Proportion of fixations", x = NULL)
+  labs(y = "Proportion of fixations", x = NULL) +     theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=14),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
 ```
+
 ```{r, eval  = F}

### 2024-11-03 manuscript.Rmd
Merged author affiliation changes

@@
 author:
+   - name: Ariel N. James
+    affiliation: '1'
+    role:
+      - Conceptualization
+      - Formal analysis
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    email: ajames2@macalester.edu
+  - name: Rachel Ryskin
+    affiliation: '2'
+    role:
+      - Conceptualization
+      - Formal analysis
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    email: rryskin@ucmerced.edu
+  - name: Joshua K. Hartshorne
+    affiliation: '3'
+    role:
+      - Conceptualization
+      - Formal analysis
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
+    email: joshua.hartshorne@bc.edu
+  - name: Haylee Backs
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: hbacks@vassar.edu
+  - name: Nandeeta Bala
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: nbala@vassar.edu
+  - name: Laila Barcenas-Meade
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: lbarcenasmeade@vassar.edu
+  - name: Samata Bhattarai
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: sbhattarai@vassar.edu
+  - name: Tessa Charles
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: tcharles@vassar.edu
+  - name: Gerasimos Copoulos
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: gcopoulos@vassar.edu
+  - name: Claire Coss
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: ccoss@vassar.edu
+  - name: Alexander Eisert
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: aeisert@vassar.edu
+  - name: Elena Furuhashi
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: efuruhashi@vassar.edu
+  - name: Keara Ginell
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: kginell@vassar.edu
+  - name: Anna Guttman-McCabe
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: aguttmanmccabe@vassar.edu
+  - name: Emma (Chaz) Harrison
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: eharrison@vassar.edu
+  - name: Laura Hoban
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: lhoban@vassar.edu
+  - name: William A. Hwang
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: whwang@vassar.edu
+  - name: Claire Iannetta
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: ciannetta@vassar.edu
+  - name: Kristen M. Koenig
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: kkoenig@vassar.edu
+  - name: Chauncey Lo
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: chaunceylo@vassar.edu
+  - name: Victoria Palone
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: vpalone@vassar.edu
+  - name: Gina Pepitone
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: gpepitone@vassar.edu
+  - name: Margaret Ritzau
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: mritzau@vassar.edu
+  - name: Yi Hua Sung
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: ysung@vassar.edu
+  - name: Lauren Thompson
+    affiliation: '4'
+    role:
+      - Investigation
+      - Methodology
+      - Software
+    email: lthompson@vassar.edu
  - name: Joshua R. de Leeuw
-    affiliation: '1'
+    affiliation: '4'
     role:
@@
     address: 124 Raymond Ave, Poughkeepsie, NY 12604, USA
-  - name: Rachel Ryskin
-    affiliation: '2'
-    role:
-      - Conceptualization
-      - Formal analysis
-      - Visualization
-      - Writing - original draft
-      - Writing - review & editing
-    email: rryskin@ucmerced.edu
-  - name: Ariel N. James
-    affiliation: '3'
-    role:
-      - Conceptualization
-      - Formal analysis
-      - Visualization
-      - Writing - original draft
-      - Writing - review & editing
-    email: ajames2@macalester.edu
-  - name: Joshua K. Hartshorne
-    affiliation: '4'
-    role:
-      - Conceptualization
-      - Formal analysis
-      - Visualization
-      - Writing - original draft
-      - Writing - review & editing
-    email: joshua.hartshorne@bc.edu
-  - name: Haylee Backs
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: hbacks@vassar.edu
-  - name: Nandeeta Bala
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: nbala@vassar.edu
-  - name: Laila Barcenas-Meade
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: lbarcenasmeade@vassar.edu
-  - name: Samata Bhattarai
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: sbhattarai@vassar.edu
-  - name: Tessa Charles
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: tcharles@vassar.edu
-  - name: Gerasimos Copoulos
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: gcopoulos@vassar.edu
-  - name: Claire Coss
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: ccoss@vassar.edu
-  - name: Alexander Eisert
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: aeisert@vassar.edu
-  - name: Elena Furuhashi
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: efuruhashi@vassar.edu
-  - name: Keara Ginell
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: kginell@vassar.edu
-  - name: Anna Guttman-McCabe
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: aguttmanmccabe@vassar.edu
-  - name: Emma (Chaz) Harrison
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: eharrison@vassar.edu
-  - name: Laura Hoban
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: lhoban@vassar.edu
-  - name: William A. Hwang
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: whwang@vassar.edu
-  - name: Claire Iannetta
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: ciannetta@vassar.edu
-  - name: Kristen M. Koenig
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: kkoenig@vassar.edu
-  - name: Chauncey Lo
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: chaunceylo@vassar.edu
-  - name: Victoria Palone
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: vpalone@vassar.edu
-  - name: Gina Pepitone
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: gpepitone@vassar.edu
-  - name: Margaret Ritzau
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: mritzau@vassar.edu
-  - name: Yi Hua Sung
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: ysung@vassar.edu
-  - name: Lauren Thompson
-    affiliation: '1'
-    role:
-      - Investigation
-      - Methodology
-      - Software
-    email: lthompson@vassar.edu
 
   affiliation:
-  - id: '1'
+  - id: '4'
     institution: Cognitive Science Department, Vassar College
@@
       Merced
+  - id: '1'
+    institution: Psychology Department, Macalester College
   - id: '3'
-    institution: Psychology Department, Macalester College
-  - id: '4'
     institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions
@@
 ```
+\newpage
+
+#Contributions
+
+\newpage
+
+#Acknowledgements
+
+\newpage
+
+#Funding information
+Funding for this project was provided by the Vassar College Department of Cognitive Science (JdL) and
+
+\newpage
+
+#Competing interests
+The authors have no competing interests to declare.
+
+\newpage
+
+#Supplemental material
+
+\newpage
+
+#Data accessibility statement
+
+\newpage
+
+#Figure titles and legends

### 2024-11-03 manuscript.Rmd
small edits to get it to knit right

@@
 affiliation:
-  - id: '4'
-    institution: Cognitive Science Department, Vassar College
+  - id: '1'
+    institution: Psychology Department, Macalester College
   - id: '2'
@@
       Merced
-  - id: '1'
-    institution: Psychology Department, Macalester College
   - id: '3'
     institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions
+  - id: '4'
+    institution: Cognitive Science Department, Vassar College
 

### 2024-11-17 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
Added list of figure titles and captions; edited some captions.

@@
 ```{r E1b-calib-effect, fig.cap='Calibration scores in Exp.
-1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.', out.width="50%", fig.align="center"}
+1b, plotted against the verb effect.
+This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.', out.width="50%", fig.align="center"}
 #I picked this one because it's the same as in E1a
@@
 ```{r E1b-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+Results from our web-based study (Panel A; Experiment 1a) are contrasted with the current results (Panel B).
 The vertical line marks the mean noun onset time across trials and conditions.", out.width="75%", fig.align="center"}

### 2024-11-17 group-a/E1-analysis-replication.Rmd
Added list of figure titles and captions; edited some captions.

@@
 
-```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).', out.width="50%", fig.align="center"}
+```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations.
+This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.', out.width="50%", fig.align="center"}
 #I picked this one because the DV is easiest to explain, and because it's the DV where the effect comes out once you drop the "bad" participants
@@
 ```{r E1a-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.
+Results from an in-lab study with an eyetracker (Panel A; @james2023language) are contrasted with the current results (Panel B).
 The vertical line marks the mean noun onset time across trials and conditions.", out.width="75%", fig.align="center"}

### 2024-11-17 group-b/E2-analysis-calibration.Rmd
Added list of figure titles and captions; edited some captions.

--- 2024-10-24 group-b/E2-analysis-calibration.Rmd
@@
 
-```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).'}
+```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias.
+This was operationalized as the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants.', out.width="50%", fig.align="center"}
 ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+

### 2024-11-17 group-b/E2-analysis-replication.Rmd
Added list of figure titles and captions; edited some captions.

@@
 
-```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F, out.width="50%", fig.align="center"}
+```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval in Experiment 2.", eval = F, out.width="50%", fig.align="center"}
 fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
@@
 
-```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval.", out.width="50%", fig.align="center"}
+```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval by statement type and viewing condition in Experiment 2.", out.width="50%", fig.align="center"}
 acc_rt_fig<-acc_fig + rt_fig + plot_layout(guides = "collect")

### 2024-11-17 group-b/E2-calibration-figure.Rmd
Added list of figure titles and captions; edited some captions.

@@
 Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
+Red crosses were used for checking the accuracy of the calibration.
+In this experiment, all the same locations were used for both calibration and validation.", fig.width=6, fig.height=4}
 ggplot(df, aes(x=x, y=y, shape=point, color=point))+

### 2024-11-17 group-c/E3-analysis-calibration.Rmd
Added list of figure titles and captions; edited some captions.

@@
 The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed.
-Calibration scores were not correlated with proportion looks to novel, regardless of whether scores were computed using ROIs (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-roi-by-calibration)) or split-halves (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-halves-by-calibration).
+Calibration scores were not correlated with proportion looks to novel, regardless of whether scores were computed using ROIs (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-roi-by-calibration)) or split-halves (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-halves-by-calibration)).
 
-```{r E3-cal-Plot-looking-score-halves-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against proportion looks to novel using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).', out.width="50%", fig.align="center"}
-ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
+```{r E3-cal-Plot-looking-score-roi-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Experiment 3 calibration scores plotted against proportion looks-to-novel using the ROI coding method.
+This was operationalized as proportion of gaze samples to the new image out of all gaze samples).', out.width="50%", fig.align="center"}
+ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
   geom_point()+
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looks-to-novel halves")+
+  labs(x="Calibration Score", y="Looks-to-novel (ROIs)") +
   theme_bw()+
@@
 
-```{r E3-cal-Plot-looking-score-roi-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against proportion looks to novel using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).', out.width="50%", fig.align="center"}
-ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
+```{r E3-cal-Plot-looking-score-halves-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Experiment 3 calibration scores plotted against proportion looks-to-novel using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).', out.width="50%", fig.align="center"}
+ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
   geom_point()+
   geom_smooth(method="lm", formula = y ~ x)+
-  labs(x="Calibration Score", y="Looks-to-novel (ROIs)") +
+  labs(x="Calibration Score", y="Looks-to-novel halves")+
   theme_bw()+

### 2024-11-17 group-d/E4-analysis-ROIs.Rmd
Added list of figure titles and captions; edited some captions.

@@
 
-```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
+```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
+Gaze was categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
 Vertical lines indicate average onsets of animal and instrument offset by 200ms.", out.width="50%", fig.align="center"}

### 2024-11-17 group-d/E4-analysis-replication.Rmd
Added list of figure titles and captions; edited some captions.

@@
 In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
-Results were qualitatively similar to those in the original are shown in Figure \@ref(fig:E4-gaze-timecourse-fig), though proportions of fixations to the target animal were much lower in the web version of the study.
+Results were qualitatively similar to those in the original as shown in Figure \@ref(fig:E4-proportion-fix-by-window-both), though proportions of fixations to the target animal were much lower in the web version of the study.
 This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.
-Eyegaze results are shown in more detail in Figure \@ref(fig:E4-gaze-timecourse-fig).
+Eye-gaze results are shown in more detail in Figure \@ref(fig:E4-gaze-timecourse-fig).
 
@@
 ```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
-Error bars reflect bootstrapped 95% CIs over subject means", out.width="65%", fig.align="center"}
+Error bars reflect bootstrapped 95% CIs over subject means.", out.width="65%", fig.align="center"}
 
@@
 ```
+
 ```{r, eval  = F}

### 2024-11-17 group-e/E5-analysis-replication.Rmd
Added list of figure titles and captions; edited some captions.

@@
 5.
-*Top* shows the original results from Shimojo and colleagues (Figures reprinted with permission[TODO]).
-The attractiveness judgment along with the best-fitting sigmoid  is shown in the *top left*.
-Results for the roundness judgment are show in the *top right*, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison (*top right*).
-(*Bottom*) shows the analogous results from the replication, with the attractiveness judgments on the *bottom left* and the roundness judgments on the *bottom right*.
-Again, the best-fitting sigmoid for the attractiveness judgments are plotted with a dashed line alongside the roundness results, for purposes of comparison.
+The attractiveness judgment along with the best-fitting sigmoid  is shown on the *left*.
+Results for the roundness judgment are shown on the *right*, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison.
 
@@
 # All defaults
-include_graphics("figGroupEOrigA.png")
-include_graphics("figGroupEOrigB.png")
+#include_graphics("figGroupEOrigA.png")
+#include_graphics("figGroupEOrigB.png")
 plot.A

### 2024-11-17 manuscript.Rmd
Added list of figure titles and captions; edited some captions.

@@
     institution: Cognitive Science Department, Vassar College
-
-authornote: |
-  Partial funding for JKH's contributions was provided by NSF2436092. The authors declares no competing interests.
 
@@
 
-```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3', out.width="35%", fig.align="center"}
+```{r E3-design-schematic, fig.cap='Schematic of the design of Experiment 3.', out.width="35%", fig.align="center"}
 knitr::include_graphics("group-c/E3-example-figure.jpeg")
@@
 
-#Contributions
+# Contributions
 
@@
 
-#Acknowledgements
+# Funding information
+Funding for data collection was provided by the Vassar College Department of Cognitive Science (JdL). Partial funding for JKH's contributions was provided by NSF2436092.
 
@@
 
-#Funding information
-Funding for this project was provided by the Vassar College Department of Cognitive Science (JdL) and
+# Competing interests
+The authors have no competing interests to declare.
 
@@
 
-#Competing interests
-The authors have no competing interests to declare.
+# Supplemental material
 
@@
 
-#Supplemental material
+# Data accessibility statement
 
@@
 
-#Data accessibility statement
-
-\newpage
-
-#Figure titles and legends
+# Figure titles and legends
+
+1. **Example trial from Experiment 1.** Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.
+
+2. **Calibration and validation point locations for Experiment 1.** Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.
+
+3.
+**Calibration scores plotted against the verb effect on first fixations.** This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.
+
+4.
+**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; @james2023language) are contrasted with the current results (Panel B).
+The vertical line marks the mean noun onset time across trials and conditions.
+
+5.
+**Calibration scores in Exp.
+1b, plotted against the verb effect** This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.
+
+6.
+**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from our web-based study (Panel A; Experiment 1a) are contrasted with the current results (Panel B).
+The vertical line marks the mean noun onset time across trials and conditions.
+
+7. **Example trial from Experiment 2.**
+
+8.
+**Calibration and validation point locations for Experiment 2.** Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.
+In this experiment, all the same locations were used for both calibration and validation.
+
+9. **Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions in Experiment 2.**
+
+10. **Accuracy and response times during memory retrieval by statement type and viewing condition in Experiment 2.**
+
+11.
+**Calibration scores plotted against gaze bias.** This was operationalized as the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants.
+
+12. **Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.**
+
+13. **Schematic of the design of Experiment 3.**
+
+14. **Correlation between proportion looks-to-novel calculated using ROIs and using screen halves.**
+
+15.
+**Experiment 3 calibration scores plotted against proportion looks-to-novel using the left-vs.- right halves coding method.** This was operationalized as the proportion of gaze samples to the half of the screen containing the new image out of all gaze samples.
+
+16.
+**Experiment 3 calibration scores plotted against proportion looks-to-novel using the ROI coding method.** This was operationalized as the proportion of gaze samples to the new image out of all gaze samples.
+
+17.
+**The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looks-to-novel and Day 2 memory performance.** Looks-to-novel were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).
+
+18.
+**Calibration and validation point locations for Experiment 4.** Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.
+In this experiment, all the same locations were used for both calibration and validation.
+
+19.
+**An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.”** The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+
+20. **Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.**
+
+21. **Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.** Error bars reflect bootstrapped 95% CIs over subject means.
+
+22. **Timecourse of eye-gaze to target animal and target instrument by verb bias condition.** Vertical lines indicate average onsets of animal and instrument offset by 200ms.
+
+23. **Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).**
+
+24. **Example participant’s gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.** Magenta points indicate looks that were not categorized into an ROI.
+
+25.
+**Timecourse of eye-gaze to target animal and target instrument by verb bias condition.** Gaze was categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.
+
+26. **Calibration and validation point locations for Experiment 5.** Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.
+
+27. **An example of a critical trial from Experiment 5.** Text did not appear on each screen.
+
+28.
+**Primary results from Exp.
+5.** The attractiveness judgment along with the best- fitting sigmoid is shown on the left.
+Results for the roundness judgment are shown on the right, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison.
+
+29. **Correlation between calibration accuracy (x-axis) and proportion of samples fixating target (y-axis) in Exp. 5.**
+
+30.
+**Revised results for Exp.
+5 after removing low-calibration accuracy participants.** *Left*: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid.
+*Right*: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).

### 2024-11-25 manuscript.Rmd
final? minor edits for Collabra submission

@@
     email: ajames2@macalester.edu
+    corresponding: yes
+    address: 1600 Grand Ave, Saint Paul, MN 550105, USA
+
   - name: Rachel Ryskin
@@
       - Writing - review & editing
-    corresponding: yes
     email: jdeleeuw@vassar.edu
-    address: 124 Raymond Ave, Poughkeepsie, NY 12604, USA
 
@@
 These data were collected within the context of an undergraduate research methods course.
-Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the first author.
+Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the last author.
 The OSF repositories associated with these experiments are linked in the methods sections of each individual study.
@@
 # Contributions
+* Joshua R. de Leeuw
+    + Conceptualization
+    + Data curation
+    + Formal analysis
+    + Investigation
+    + Methodology
+    + Project administration
+    + Software
+    + Supervision
+    + Validation
+    + Visualization
+    + Writing - original draft
+    + Writing - review & editing
+
+* Ariel N. James, Rachel Ryskin, and Joshua K. Hartshorne
+    + Conceptualization
+    + Formal analysis
+    + Visualization
+    + Writing - original draft
+    + Writing - review & editing
+
+* Undergraduate student authors, listed alphabetically: Haylee Backs, Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison, Laura Hoban, William A.
+Hwang, Claire Iannetta, Kristen M.
+Koenig, Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua Sung, and Lauren Thompson
+    + Investigation
+    + Methodology
+    + Software
 
@@
 
-# Supplemental material
-
-\newpage
-
 # Data accessibility statement
+All data and analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis.
+Study materials and pre-registrations for each experiment are available on Open Science Framework:
+
+* Experiments 1a and 1b: [https://osf.io/g6dum/]
+* Experiment 2: [https://osf.io/xezfu/]
+* Experiment 3: [https://osf.io/k63b9/]
+* Experiment 4: [https://osf.io/x3c49/]
+* Experiment 5: [https://osf.io/eubsc/]
 

### 2025-03-12 group-b/E2-analysis-survey.Rmd
many changes (mostly to E2 and E4) addressing reviewer comments

---
title: "Group B Analysis - Survey"
output: pdf_document
---

```{r message=FALSE}
library(jsonlite)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(stringr)
```

<!--Read JSON files and bind together into a tibble.-->

```{r}
data.files <- list.files('data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r}

survey_questions = c("\n              <p>Were there any distracting notifications?</p>\n              ",
                     "\n              <p>How many questions were you unable to hear?</p>\n              ",
                     "\n              <p>Did the experiment window exit full screen during the experiment?</p>\n              ",
                     "\n              <p>During the memory recall was it difficult to keep your head in a fixed position?</p>\n              ",
                     "\n              <p>Do you wear glasses during the experiment?</p>\n              "
                     )

all.data.survey = all.data %>% 
  filter(stimulus %in% c(survey_questions)) %>% 
  dplyr::select(subject_id, trial_index,  stimulus, response) %>% 
  mutate(survey_question = case_when(
    str_detect(stimulus, "notifications") ~ "notifications",
    str_detect(stimulus, "hear") ~ "questions_not_heard",
    str_detect(stimulus, "exit full screen") ~ "exit_full_screen",
    str_detect(stimulus, "fixed") ~ "head_fixed",
    str_detect(stimulus, "glasses") ~ "glasses"
  ))

```

```{r, message = FALSE, warning = FALSE}
summary.data.survey = all.data.survey %>% 
  group_by(survey_question ) %>% 
  mutate(total_responses = n() ) %>% 
  group_by(survey_question, response, total_responses) %>% 
  summarize(num_responses = n(), 
            prop_response = num_responses/total_responses,
            perc_response = round(prop_response * 100, digits = 0)) %>% 
  unique()

# For all Yes/No questions: 0 = 'Yes', 1 = 'No'
# For number of questions not heard: 0,1,2,3,4 --> '0', '1', '2', '3', 'More than 3'
```

```{r, message = F}
calib.by.subj = read_csv("output/E2_calib_data_subj.csv")

glasses.data = all.data.survey %>% 
  filter(survey_question == "glasses") %>% 
  left_join(calib.by.subj, by = "subject_id")

summary.glasses.data = glasses.data %>% 
  group_by(response) %>% 
  summarize(mean_calib_score = round(mean(mean_percent_in_roi), digits = 2))
```

```{r}
t_test_glasses = t.test( mean_percent_in_roi ~ response, data = glasses.data)
```
Participants were asked a number of debriefing questions. `r summary.data.survey %>% filter(survey_question == 'notifications' & response == 0) %>% pull(perc_response)`% reported experiencing distracting notifications during the experiment. `r summary.data.survey %>% filter(survey_question == 'exit_full_screen' & response == 0) %>% pull(perc_response)`% reported that the experiment exited full screen mode during the experiment. `r summary.data.survey %>% filter(survey_question == 'head_fixed' & response == 0) %>% pull(perc_response)`% reported that it was difficult to keep their head in a fixed position during the memory recall portion of the experiment. `r 100 - summary.data.survey %>% filter(survey_question == 'questions_not_heard' & response == 0) %>% pull(perc_response)`% reported that they were unable to hear at least one question.  `r summary.data.survey %>% filter(survey_question == 'glasses' & response == 0) %>% pull(perc_response)`% reported wearing glasses during the experiment. Average calibration scores were numerically lower for participants who reported wearing glasses (`r summary.glasses.data %>% filter(response == 0) %>% pull(mean_calib_score)`%) compared to those who didn't (`r summary.glasses.data %>% filter(response == 1) %>% pull(mean_calib_score)`%, _t_=`r round(t_test_glasses$statistic, digits = 2)`, _p_=`r round(t_test_glasses$p.value, digits = 2)`).

### 2025-03-12 group-d/E4-analysis-replication.Rmd
many changes (mostly to E2 and E4) addressing reviewer comments

@@
 
-```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.", out.width="65%", fig.align="center"}
+```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
+Error bars indicate standard errors over participant means.", out.width="65%", fig.align="center"}
 
@@
 
-```{r, eval=FALSE}
-write_csv(first.move, "output/E4_mouse_data.csv")
+```{r}
+write_rds(first.move, "output/E4_mouse_data.rds")
 ```
@@
 
-Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a rectangle containing the image.
+Gaze fixations were time-locked to the auditory stimulus on a trial by trial basis and categorized as being directed towards one of the four items in the display if the x, y coordinates fell within a 400 by 400 pixel rectangular region of interest around each image (a 200 x 200 pixel rectangle containing the image with an additional 100 pixels of padding on all sides).
 In order to assess how verb bias impacted sentence disambiguation as the sentence unfolded, the proportion of fixations was computed in three time windows: the verb-to-animal window (from verb onset + 200 ms to animal onset + 200 ms), the animal-to-instrument window (from animal onset + 200 ms to instrument onset + 200 ms), and the post-instrument window (from instrument onset + 200 ms to instrument onset + 1500ms + 200 ms).
@@
 
+```{r E4-compute-proportion-gaze-data-by-trial}
+#Summarize fixations on target and instrument
+eyetracking.window.summary.by.trial <- eyetracking.data.with.time.windows %>%
+  group_by(subject, trialID, sound, compatibility, time.window) %>%
+  summarize(prop.fixations.animal = sum(in.roi.animal) / n(),
+            prop.fixations.instrument = sum(in.roi.instrument) / n()) %>%
+  mutate(compatibility = factor(compatibility))
+```
+
+```{r}
+write_rds(eyetracking.window.summary.by.trial, "output/E4_eye-tracking_data.rds")
+```
+
 ```{r E4-summarizing-gaze-data-for-plotting}
@@
 ```{r}
-first.move = read_csv("output/E4_mouse_data.csv")
-eyetracking.window.summary.by.trial = read_csv( "output/E4_eye-tracking_data.csv") %>% 
+eyetracking.window.summary.by.trial.for.fig = eyetracking.window.summary.by.trial %>% 
   rename("condition" = compatibility) %>% 
@@
 
-eyetracking.window.summary.by.trial.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>%
-   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" )
+# eyetracking.window.summary.by.trial.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial.for.fig) %>%
+#    filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" )
 
-eyetracking.window.summary.by.subj.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>%
+eyetracking.window.summary.by.subj.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial.for.fig) %>%
    filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" ) %>% 
@@
                                        "post-instrument-onset"),
-                            labels = c('Verb to animal \n("Rub the")',
-                                       'Animal onset\n("frog with the")',
-                                       'Instrument+1500ms\n(feather...")')),
+                            labels = c('Verb to Animal \n("Rub the")',
+                                       'Animal to Instr.\n("frog with the")',
+                                       'Instr.+1.5s\n(feather...")')),
          condition  = factor(condition, 
@@
 ```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.
-Error bars reflect bootstrapped 95% CIs over subject means.", out.width="65%", fig.align="center"}
+Error bars reflect standard errors over subject means.", out.width="65%", fig.align="center"}
 
@@
   stat_summary(aes(x=as.numeric(time.window), y = mean_prop, color = condition, group = paste(condition , study)), 
-                geom = 'errorbar', fun.data = 'mean_cl_boot', width = 0.05)+
+                geom = 'errorbar', fun.data = 'mean_se', width = 0.05)+
   #facet_wrap(~time.window)+
@@
 ```{r E4-gaze-timecourse-fig, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition.
-Vertical lines indicate average onsets of animal and instrument offset by 200ms.", out.width="50%", fig.align="center"}
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.
+Shaded ribbons reflect standard errors over subject means.", out.width="50%", fig.align="center"}
 
@@
 
-```{r E4-compute-proportion-gaze-data-by-trial}
+```{r E4-compute-proportion-gaze-data-by-trial-2, eval = F}
 #Summarize fixations on target and instrument
@@
   mutate(compatibility = factor(compatibility))
-```
-
-```{r, eval=FALSE}
-write_csv(eyetracking.window.summary.by.trial, "output/E4_eye-tracking_data.csv")
 ```
@@
 
-In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition and equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the  modifier biased relative to the equi-biased condition ( _b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
+In the _noun-to-instrument_ window, participants looked more at the target animal in the modifier-biased condition and equi-biased conditions relative to the instrument-biased condition (_b_ =  `r E4_ET_model2_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and in the  modifier biased relative to the equi-biased condition (_b_ =  `r E4_ET_model2_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model2_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.05).
 
-In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).
+In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition (_b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) but not significantly so in the modifier biased condition relative to the equi-biased condition (_b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`).

### 2025-03-12 manuscript.Rmd
many changes (mostly to E2 and E4) addressing reviewer comments

@@
 In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system.
-Since these findings, eye-tracking has become a central method in cognitive science research [for reviews, see @hayhoe2005eye, @richardsonEyeTrackingResearch2004, @rayner1998eye].
+Since these findings, eye-tracking has become a central method in cognitive science research [for reviews see @hayhoe2005eye; @richardsonEyeTrackingResearch2004; @rayner1998eye].
 For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning], and eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
@@
 This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research.
-Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD; @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
+Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD, @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
 Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend [@nosek2022replicability].
@@
 
-<!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->
-<!-- RR: switched ryskin to Snedeker & trueswell 2004 bcs my 75 looked sad -->
-
-We chose five high-impact eye-tracking studies involving adult subjects [for an comparison of remote WebGazer and in-lab anticipatory looking effects with 18-27 month-old participants, see @steffan2024validation].
+We chose five high-impact eye-tracking studies involving adult subjects [for a comparison of remote WebGazer and in-lab anticipatory looking effects with 18-27 month-old participants, see @steffan2024validation].
 Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "naturalistic" scenes).
@@
 
+All data and analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis.
+The current paper is fully reproducible by rendering `manuscript.Rmd`.
+
 ## Participants
@@
 Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality).
-All analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis
 
@@
 
-Participants then proceded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to
+Participants then proceeded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to
 answer a few survey questions (such as whether they wore glasses or
@@
 ```{r E2-analysis-calibration, child='group-b/E2-analysis-calibration.Rmd'}
+
+```
+
+### Survey results
+
+```{r E2-analysis-survey, child='group-b/E2-analysis-survey.Rmd'}
 
@@
 verb's "bias" (statistical co-occurrence either in norming or corpora)
-to rapidly choose an action while the sentence is unfolding. .
+to rapidly choose an action while the sentence is unfolding. 
+Use of the verb's bias should be reflected in a greater proportion of eye-gaze fixations to the animal (e.g., frog) for verbs that are biased toward modifier structures relative to instrument structures and, conversely, a greater proportion of eye-gaze fixations to the instrument (e.g., feather) for verbs that are biased toward instrument structures relative to modifier structures.
 
@@
 
+This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research.
+In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries, webcam eye-tracking can reach much larger numbers of participants of all ages, across the globe, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops).
+Characterizing the diversity of populations that webcam eye-tracking studies can reach is an important avenue for future work.
+
 ## Lessons and Questions
 
-The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a Webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.
+The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.
 
@@
 
-Third, it is true for any eyetracker that precise data depends on good callibration, and good callibration depends in part on lighting and background.
+Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background.
 We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.

### 2025-03-18 group-b/E2-analysis-replication.Rmd

@@
 ```
-```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.", out.width="50%", fig.align="center"}
+
+```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.
+Error bars indicate standard errors over participant means.", out.width="50%", fig.align="center"}
 
@@
     axis.title = element_text(size=14),  
-    axis.text = element_text(size=14)
+    axis.text = element_text(size=14),
+    strip.text.x = element_text(size = 14)
   )
@@
   scale_color_manual(values=c("orange2","royalblue4"))+
+  guides(color = "none")+
   labs(x="Statement Type", y="Response Time (ms)", color=NULL)+
@@
 
-```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval by statement type and viewing condition in Experiment 2.", out.width="50%", fig.align="center"}
+```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval by statement type and viewing condition in Experiment 2.
+Error bars indicate standard errors over participant means.", out.width="50%", fig.align="center"}
 acc_rt_fig<-acc_fig + rt_fig + plot_layout(guides = "collect")

### 2025-03-18 group-d/E4-analysis-calibration.Rmd

@@
 
-eyetracking.effects.by.subj = read_csv( "output/E4_eye-tracking_data.csv") %>% 
+eyetracking.effects.by.subj = read_rds( "output/E4_eye-tracking_data.rds") %>% 
   rename("condition" = compatibility) %>% 
@@
 
-```{r,eval=F}
-write_csv(calib.by.subj,"output/calib_by_subj.csv")
+```{r}
+write_rds(calib.by.subj,"output/calib_by_subj.rds")
 ```
@@
 ```
-Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%).
-The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
+Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%).
+The quality of a participant's calibration significantly correlated with the participant's effect size (_Pearson's r_= `r m_calib_r`, _p_ < 0.05).
 The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).
 
+```{r read in orig data for plotting}
+# only need this if we want original data in the figure comparing effect sizes between all data and good calibration subset
+
+eyetracking.window1.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_verb.txt") %>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         #sum_dur = TA+TI+CA+CI,
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-verb-onset-pre-animal-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+eyetracking.window2.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_animal.txt")%>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-animal-onset-pre-instrument-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+
+eyetracking.window3.summary.by.trial.orig = read_tsv("original_study_data/Experiment1_eye-tracking_instrument.txt")%>% 
+  mutate(subject = as.character(subj), 
+         prop.fixations.animal = TA/(TA+TI+CA+CI),
+         condition = factor(cond, levels = c(0, 2, 1, 9), labels = c("instrument", "equibiased", "modifier", "filler")),
+         time.window = "post-instrument-onset",
+         study = "original") %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal, study)
+```
+```{r read web data}
+eyetracking.window.summary.by.trial = read_rds("output/E4_eye-tracking_data.rds")
+```
+
 ```{r}
-eyetracking.window.3 = read_csv( "output/E4_eye-tracking_data.csv") %>% 
+
+eyetracking.window.summary.by.trial.all = eyetracking.window.summary.by.trial %>% 
+  rename("condition" = compatibility) %>% 
+  select(subject, trialID, condition, time.window, prop.fixations.animal) %>% 
+  mutate(study = "web") %>% 
+  left_join(calib.by.subj, by = "subject")
+
+eyetracking.window.summary.by.trial.good.calib = eyetracking.window.summary.by.trial.all %>% 
+ filter(mean_percent_in_roi >= 50) %>% 
+  mutate(study = "web (calib. > 50%)")
+
+eyetracking.window.summary.by.subj.three = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial.good.calib, eyetracking.window.summary.by.trial.all) %>%
+   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" ) %>% 
+  group_by(study, condition, time.window, subject) %>% 
+  summarize(mean_prop = mean(prop.fixations.animal, na.rm = T)) %>% 
+  mutate(time.window = factor(time.window, 
+                            levels = c("post-verb-onset-pre-animal-onset",
+                                       "post-animal-onset-pre-instrument-onset",
+                                       "post-instrument-onset"),
+                            labels = c('Verb to Anim. \n("Rub the")',
+                                       'Anim. to Instr.\n("frog with the")',
+                                       'Instr.+1.5s\n(feather...")')),
+         condition  = factor(condition, 
+                             levels = c("modifier", "equibiased", "instrument"), 
+                             labels = c("Modifier", "Equi-biased", "Instrument"))
+         ) %>% 
+  ungroup()
+
+summary.eyetracking.window.summary.by.subj.three = eyetracking.window.summary.by.subj.three %>% 
+  group_by(time.window, condition, study) %>% 
+  summarize(prop_mean = mean(mean_prop),
+            prop_se = sd(mean_prop)/sqrt(n())
+            )
+
+```
+```{r E4-proportion-fix-by-window-both-post-exclusion, fig.cap = "Proportion of target fixations by verb bias in the full dataset collected online and for the subset of participants with calibration quality >50%.
+Error bars reflect standard errors over subject means.", out.width="75%", fig.align="center"}
+
+shapes_legend <- c("original" = 1, "web" = 16, "web (calib. > 50%)" = 4)
+linetypes_legend <- c("original" = "dashed", "web" = "solid", "web (calib. > 50%)" = "dotted")
+
+ggplot()+
+  # geom_errorbar(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "original"),
+  #               aes(x=time.window,
+  #                  ymin = prop_mean-prop_se,
+  #                  ymax = prop_mean+prop_se,
+  #                  color = condition),
+  #               width = 0.1,
+  #               position = position_dodge(width = .5))+
+  geom_errorbar(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "web"),
+                aes(x=time.window,
+                   ymin = prop_mean-prop_se,
+                   ymax = prop_mean+prop_se,
+                   color = condition),
+                width = 0.1,
+                position = position_dodge(width = .5))+
+  geom_errorbar(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "web (calib. > 50%)"),
+                aes(x=time.window,
+                   ymin = prop_mean-prop_se,
+                   ymax = prop_mean+prop_se,
+                   color = condition),
+                width = 0.1,
+                position = position_dodge(width = .5))+
+  # geom_line(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "original"),
+  #          aes(x=as.numeric(time.window),
+  #              group = condition,
+  #              y = prop_mean,
+  #              linetype = "original"),
+  #            alpha = 0.5,
+  #           color = "grey",
+  #            position = position_dodge(width = 0.5))+
+ geom_line(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "web"),
+           aes(x=as.numeric(time.window),
+               group = condition,
+               y = prop_mean,
+               linetype = "web"),
+             alpha = 0.5,
+            color = "grey",
+             position = position_dodge(width = 0.5))+
+  geom_line(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "web (calib. > 50%)"),
+           aes(x=as.numeric(time.window),
+               group = condition,
+               y = prop_mean,
+               linetype = "web (calib. > 50%)"),
+             alpha = 0.5,
+            color = "grey",
+             position = position_dodge(width = 0.5))+
+  # geom_point(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "original"),
+  #           aes(x=time.window, 
+  #               color=condition, 
+  #               y = prop_mean,
+  #               shape = "original"),
+  #           size = 3, 
+  #           position = position_dodge(width = 0.5))+
+  geom_point(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "web"),
+            aes(x=time.window, 
+                color=condition, 
+                y = prop_mean,
+                shape = "web"),
+            size = 3, 
+            position = position_dodge(width = 0.5))+
+  geom_point(data = summary.eyetracking.window.summary.by.subj.three %>% filter(study == "web (calib. > 50%)"),
+            aes(x=time.window, 
+                color=condition, 
+                y = prop_mean,
+                shape = "web (calib. > 50%)"),
+            size = 3, 
+            position = position_dodge(width = 0.5))+
+   scale_color_brewer(palette = "Set1")+
+   scale_shape_manual(values = shapes_legend)+
+   scale_linetype_manual(values = linetypes_legend)+
+  # coord_cartesian(ylim = c(0,.8))+
+   theme_classic()+
+   labs(y = "Proportion of fixations", x = NULL, color = "Condition", shape = "Study", linetype = "Study") +     
+  theme(
+    panel.grid.minor = element_blank(),
+    axis.title = element_text(size=14),      # Axis titles
+    axis.text = element_text(size=13),       # Axis labels
+    legend.title = element_text(size=14),    # Legend title
+    legend.text = element_text(size=14)      # Legend text
+  )
+
+```
+
+```{r}
+eyetracking.window.3 = eyetracking.window.summary.by.trial %>% 
   filter(time.window == "post-instrument-onset", compatibility != "filler" ) %>% 
@@
 ```
+
 #### Re-analysis After Exclusions
-Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
-Participants' preference to the target animal relative to the target instrument in the modifier-biased condition and the equi-biased conditions was greater than in the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001), but the difference betwen the modifier biased condition and the equi-biased condition was not significant ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).
+A subset of 35 participants had calibration quality >50%.
+Figure \@ref(fig:E4-proportion-fix-by-window-both-post-exclusion) shows proportions of fixations to the target animal for this subset alongside the full dataset.
+Though the overall proportions of fixations to the target animal in this subset were higher than in the full dataset, they were still much lower than in the original study.
+Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on this subset of participants suggests that the effect of verb bias condition was larger in this subset than in the full dataset.
+Participants' preference to the target animal relative to the target instrument in the modifier-biased condition and the equi-biased conditions was greater than in the instrument-biased condition (_b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001), but the difference betwen the modifier biased condition and the equi-biased condition was not significant (_b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).
 

### 2025-03-18 manuscript.Rmd
minor revisions

@@
 However, in recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation].
-Nonetheless, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
+Nonetheless, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], `lab.js` [@henninger2021lab], or `PsychoJS` [@peirce2019psychopy2].
 
@@
 While promising, there are some salient limitations.
-First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2022moving; @degen2021seeing; @van2023validation].
+First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating].
 Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
 
-Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online], dividing the screen either in half or in quadrants.
+Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online; @bogdan2024investigating], dividing the screen either in half or in quadrants.
 This is particularly salient with [@prystauka2023online], which simplified @altmannIncrementalInterpretationVerbs1999's design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
@@
 As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization.
-We recommend that future researchers use jsPsych or another package with similar documented precision.
+While it is possible that other Web-based eyetracking software achieves (or can achieve) the same level of precision as currently offered by jsPsych, we urge researchers to be cautious about using software for which the precision has not been documented.
 

### 2025-03-19 manuscript.Rmd
Minor edits

@@
 While promising, there are some salient limitations.
-First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating].
-Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
+First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing].
+Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
 

### 2025-03-19 manuscript.Rmd
Addressing request re: Gorilla

@@
 
-Second, researchers need to take care with timing accuracy.
-Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically.
+Second, researchers need to take care with timing accuracy. Running studies on mod.
+ern computers requires synchronizing multiple clocks, something that does not happen automatically.
 Failure to synchronize can result in substantial inaccuracies [@slim2022moving].
 As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization.
-While it is possible that other Web-based eyetracking software achieves (or can achieve) the same level of precision as currently offered by jsPsych, we urge researchers to be cautious about using software for which the precision has not been documented.
-
+We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
 Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background.

### 2025-03-19 manuscript.Rmd
Added some citations that were requested

@@
 While promising, there are some salient limitations.
-First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing].
+First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2024webcams; @van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing].
 Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
@@
 The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
-Critically, we used the implementation known to have the greatest temporal precision to date: `jsPsych` and a modification of `Webgazer`.
+Critically, we used the only implementation known to have addressed a critical bug in the timing precision of WebGazer.js, specifically the one in `jsPsych`, a package which is known in general for having particularly good timing precision [@de2016psychophysics; @bridges2020timing].
 
@@
 library for running behavioral experiments in a web browser
-[@deleeuwJsPsychJavaScriptLibrary2015]. Our fork included changes to
+[@deleeuwJsPsychJavaScriptLibrary2015].[^1] Our fork included changes to
 `webgazer.js` in order to improve data quality for experiments in which
@@
 participants were given an opportunity to re-start the calibration and
-validation steps. <!--If the second attempt also lead to low validation
+validation steps.
+However, even participants with low calibration accuracy were allowed to complete the experiment, because we specifically wanted to study the consequences of low calibration accuracy.<!--If the second attempt also lead to low validation
 accuracy, participants were informed that they could not participate in
@@
 contained instructions about the action they needed to act out (e.g.,
-"Rub the butterfly with the crayon"; see Figure\ \@ref(fig:E4-example-trial))[^1]. Using their
+"Rub the butterfly with the crayon"; see Figure\ \@ref(fig:E4-example-trial))[^2]. Using their
 cursor, participants could act out the instructions by clicking on
-objects and moving them or motioning over the objects[^2]. After the
+objects and moving them or motioning over the objects[^3]. After the
 action was completed, the participants were instructed to press the
@@
 
-[^1]: In the original study, the pictures appeared one by one on the
+[^1]: The WebGazer.js patch can be found at https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711.
+
+[^2]: In the original study, the pictures appeared one by one on the
     screen and their names were played as they appeared. We removed this
@@
 
-[^2]:  As opposed to the original study we recorded mouse movement
+[^3]:  As opposed to the original study we recorded mouse movement
     instead of clicking behavior since not all of the audio prompts

### 2025-03-20 manuscript.Rmd
Addressing R1, comment 10

@@
 
+Upon finishing calibration, participants were reminded to keep their head still for the remainder of the study.
+
 ## Pre-registration
@@
 
-Second, researchers need to take care with timing accuracy. Running studies on mod.
-ern computers requires synchronizing multiple clocks, something that does not happen automatically.
+There are a number of other interventions that might increase precision and should be investigated.
+For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise.
+It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback.
+These and other options should be investigated in order to determine how much they might improve precision.
+
+Second, researchers need to take care with timing accuracy.
+Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically.
 Failure to synchronize can result in substantial inaccuracies [@slim2022moving].

### 2025-03-20 manuscript.Rmd
Addressing R1, comments 11 and 12

@@
 Note also that while ROIs the size of quadrants are feasible, good calibration is important.
-Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.
+Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 50% validation accuracy.
+While stricter thresholds may decrease noise, they come at a cost.
+In preliminary analysis, we found that a threshold of 75% somewhat increased effect size in Exp.
+4, but at the cost of reducing the sample size from 35 to 19.
+However, it could be helpful to more systematically investigate the optimal threshold and whether this varies by size of ROI.
 
@@
 It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback.
+Similarly, it may be profitable to systematically study the parameters of eyegaze validation, for instance the number of validation points and the maximum distance allowed between gaze and target (set to 200px in the present study).
 These and other options should be investigated in order to determine how much they might improve precision.

### 2025-03-20 manuscript.Rmd
Finishing going through the things I can address for R1

@@
 looking at each image. The expected pattern of results is that
-participants will look more at novel objects. They
-@mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of
+participants will look more at novel objects. @mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of
 behavior could be used to measure the strength of memories. If a viewer
@@
 This seems unlikely, because calibration quality did not appear to substantially affect this result (or any of the others).
-Alternative explanation include the well-documented decline effect (replications tend to find smaller effect sizes than the original) and the common finding that subject accuracy is lower when not testing undergraduates at elite universities.
+Alternative explanation include the well-documented decline effect [replications tend to find smaller effect sizes than the original, @schooler2011unpublished; @open2015estimating; @hartshorne2012tracking] and the common finding that subject accuracy is lower when not testing undergraduates at elite universities [@hartshorne2019meta; @germine2012web].
 
@@
 Failure to synchronize can result in substantial inaccuracies [@slim2022moving].
-As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization.
+As indicated by the current work, the current jsPsych implementation of WebGazer.js has timing synchronization sufficient for many studies.
 We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
-Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background.
+
+Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background [see, for instance, @yuksel2023investigation].
 We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.

### 2025-03-20 group-c/E3-analysis-replication.Rmd

@@
 We calculated the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI.
-Of the `r looking.score.data %>% nrow()` trials in the experiment, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI and so were excluded from this analysis.
+Of the `r looking.score.data %>% nrow()` total trials in the experiment across all subjects, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI and so were excluded from this analysis.
 
@@
 Following the original analysis, we transformed these values using the Fisher p-to-z transformation.
-Using one-sample t-tests, failed to replicate the a significant difference from 0 for the correlation between proportion looks to the novel object and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor for the correlation with RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
+Using one-sample t-tests, we failed to replicate the a significant difference from 0 for the correlation between proportion looks to the novel object and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor for the correlation with RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.
 

### 2025-03-20 manuscript.Rmd

@@
 This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research.
-In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries, webcam eye-tracking can reach much larger numbers of participants of all ages, across the globe, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops).
-Characterizing the diversity of populations that webcam eye-tracking studies can reach is an important avenue for future work.
+In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries [@henrich2010weirdest; @linxen2021weird; @de2023psychology; @rad2018toward], webcam eye-tracking can reach a much more diverse population, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops and tablets).
+While webcam eyetracking cannot by itself eliminate all demographic biases, some of which are in any case baked in by history [@henrich2020weirdest], it can help to reduce them, at least for studies amenable to the paradigm.
 
@@
 4.
-**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; @james2023language) are contrasted with the current results (Panel B).
+**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; James et al.
+2023) are contrasted with the current results (Panel B).
 The vertical line marks the mean noun onset time across trials and conditions.

### 2025-03-30 manuscript.Rmd
Switched to visual tab in R studio

@@
 First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2024webcams; @van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing].
-Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
+Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].[^1] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
+
+[^1]: See also discussion at <https://github.com/jspsych/jsPsych/discussions/1892>
 
@@
 
-All data and analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis.
+All data and analysis code underlying this paper can be found in the Github repository: <https://github.com/jodeleeuw/219-2021-eyetracking-analysis>.
 The current paper is fully reproducible by rendering `manuscript.Rmd`.
@@
 
-Participants completed the experiment remotely and were recruited
-through the Prolific platform. In order to have access to the
-experiment, participants had to meet the following criteria: 18 years of
-age or older, fluency in English, and access to a webcam. All
-participants provided informed consent. The online studies were approved by the
-Vassar College Institutional Review Board.
+Participants completed the experiment remotely and were recruited through the Prolific platform.
+In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
+All participants provided informed consent.
+The online studies were approved by the Vassar College Institutional Review Board.
 
 In addition, an in-lab replication was conducted for Experiment 1.
-Information about the sample is given in the Experiment 1 Method sections. This study was approved by the Institutional Review Board at Boston College.
-
-In order to have adequate statistical power and precision, we aimed for
-2.5x the sample size of the original experiment, following the heuristic
-of Simonsohn [@simonsohn2015]. In Experiment 5, the original sample size was so
-small that we opted to collect 5x the number of participants to increase
-precision. Because of budget and time constraints we were unable to
-replace the data for subjects who were excluded or whose data was
-missing due to technical failures.
+Information about the sample is given in the Experiment 1 Method sections.
+This study was approved by the Institutional Review Board at Boston College.
+
+In order to have adequate statistical power and precision, we aimed for 2.5x the sample size of the original experiment, following the heuristic of Simonsohn [@simonsohn2015].
+In Experiment 5, the original sample size was so small that we opted to collect 5x the number of participants to increase precision.
+Because of budget and time constraints we were unable to replace the data for subjects who were excluded or whose data was missing due to technical failures.
 
@@
 
-We used a fork of the `webgazer.js` library for webcam eye-tracking
-[@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript
-library for running behavioral experiments in a web browser
-[@deleeuwJsPsychJavaScriptLibrary2015].[^1] Our fork included changes to
-`webgazer.js` in order to improve data quality for experiments in which
-the precise timing of stimulus onsets is relevant. Specifically, we
-implemented a polling mode so that gaze predictions could be requested
-at a regular interval, which improved the sampling rate considerably in
-informal testing. This modification is similar to what Yang and Krajbich
-[-@yang2021webcam] reported improved the sampling rate in their study of
-webgazer. We also adjusted the mechanism for recording time stamps of
-each gaze prediction, so that the time stamp reported by webgazer is
-based on when the video frame is received and not when the computation
-of the gaze point is finished.
+We used a fork of the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].[^2] Our fork included changes to `webgazer.js` in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant.
+Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing.
+This modification is similar to what Yang and Krajbich [-@yang2021webcam] reported improved the sampling rate in their study of webgazer.
+We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.
+
+[^2]: The WebGazer.js patch can be found at <https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711>.
 
@@
 
-When participants began the experiment, they were notified the webcam
-would be used for eye tracking but no video would be saved. They were
-asked to remove glasses if possible, close any other tabs or apps, turn
-off notifications, and make sure their face was lit from the front. The
-webcam's view of the participant popped up on the screen, and
-participants were asked to center their face in the box and keep their
-head still. The experiment window then expanded to full screen, and
-participants began the eye-tracking calibration.
-
-During the calibration, dots appeared on the screen one at a time in
-different locations, and the participants had to fixate them and click
-on each one. Once they clicked on a dot, it would disappear and a new
-one would appear in a different location on the screen. The locations of
-calibration dots were specific to each experiment (details below) and
-appeared in the areas of the screen where the visual stimuli would
-appear during the main task in order to ensure that eye movements were
-accurately recorded in the relevant regions of interest. After the
-calibration was completed, the validation began. Participants were asked
-to go through the same steps as the calibration, except that they only
-fixated the dots as they appeared in different locations on the screen.
-If accuracy on the validation was too low (fewer than 50% of looks
-landed within a 200 px radius of the validation points),
-participants were given an opportunity to re-start the calibration and
-validation steps.
+When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
+They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
+The webcam's view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
+The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
+
+During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
+Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
+The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
+After the calibration was completed, the validation began.
+Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
+If accuracy on the validation was too low (fewer than 50% of looks landed within a 200 px radius of the validation points), participants were given an opportunity to re-start the calibration and validation steps.
 However, even participants with low calibration accuracy were allowed to complete the experiment, because we specifically wanted to study the consequences of low calibration accuracy.<!--If the second attempt also lead to low validation
@@
 
-The first study was a replication attempt of
-@altmannIncrementalInterpretationVerbs1999. Altmann and Kamide used the
-visual world eye-tracking paradigm [@tanenhaus1995] to show that
-meanings of verbs rapidly constrain the set of potential subsequent
-referents in sentence processing. For example, when looking at the
-display in Figure\ \@ref(fig:E1-example-trial) and listening to a sentence like
-"The boy will eat the...," participants are more likely to look at the cake than 
-when they hear "The boy will move the...," in which case they tend to look at the
-train, presumably because cakes are edible and trains are not. Semantic
-information available at the verb is used to anticipate upcoming
-linguistic input.
+The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.
+Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
+For example, when looking at the display in Figure \@ref(fig:E1-example-trial) and listening to a sentence like "The boy will eat the...," participants are more likely to look at the cake than when they hear "The boy will move the...," in which case they tend to look at the train, presumably because cakes are edible and trains are not.
+Semantic information available at the verb is used to anticipate upcoming linguistic input.
 
@@
 
-All stimuli, experiment scripts, data, analysis scripts, and a
-pre-registration are available on the Open Science Framework at
-<https://osf.io/s82kz>.
+All stimuli, experiment scripts, data, analysis scripts, and a pre-registration are available on the Open Science Framework at <https://osf.io/s82kz>.
 
 ### Participants
-Sixty participants (2.5 times the original sample of 24) were paid \$2.60 for their participation. For unknown reasons,
-2 of the subjects' results were not recorded, so in the analysis, we
-worked with data collected from 58 participants.
+
+Sixty participants (2.5 times the original sample of 24) were paid \$2.60 for their participation.
+For unknown reasons, 2 of the subjects' results were not recorded, so in the analysis, we worked with data collected from 58 participants.
 
@@
 
-The visual stimuli were created through Canva and depicted an agent
-accompanied by four to five objects in the scene (see Figure\ \@ref(fig:E1-example-trial)). On
-critical trials, participants heard one of two sentences associated with
-the scene. In the restrictive condition, the sentence (e.g., "The boy
-will eat the cake") contained a verb (e.g., "eat") which restricts the
-set of possible subsequent referents (e.g., to edible things). Only the
-target object (e.g., the cake) was semantically consistent with the
-verb's meaning. In the non-restrictive condition, the sentence (e.g.,
-"The boy will move the cake") contained a verb (e.g., "move") which does
-not restrict the set of possible subsequent referents. The target object
-(e.g., the cake) as well as the distractor objects (e.g., the train, the
-ball, etc.) were semantically consistent with the verb's meaning. Both
-sentences were compatible with the scene, such that the correct keyboard
-response for the critical trials was "yes." Filler trials consisted of
-scenes that also contained an agent surrounded by objects as in the critical trials, but corresponding sentences named an object that was not present in the scene.
-The correct keyboard response for the filler
-trials was "no."
+The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure \@ref(fig:E1-example-trial)).
+On critical trials, participants heard one of two sentences associated with the scene.
+In the restrictive condition, the sentence (e.g., "The boy will eat the cake") contained a verb (e.g., "eat") which restricts the set of possible subsequent referents (e.g., to edible things).
+Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
+In the non-restrictive condition, the sentence (e.g., "The boy will move the cake") contained a verb (e.g., "move") which does not restrict the set of possible subsequent referents.
+The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
+Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was "yes." Filler trials consisted of scenes that also contained an agent surrounded by objects as in the critical trials, but corresponding sentences named an object that was not present in the scene.
+The correct keyboard response for the filler trials was "no."
 
@@
 
-Each participant was presented with 16 critical trials (eight in
-the restrictive condition, eight in the non-restrictive condition) and
-16 fillers for a total of 32 trials. The order of trials and the
-assignment of critical scene to condition was random on a
-subject-by-subject basis.<!-- right?-->
+Each participant was presented with 16 critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and 16 fillers for a total of 32 trials.
+The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.<!-- right?-->
 
@@
 ```
-
 ## Results
-Looks to the objects in the scene were time-locked to the onset of the
-verb, the offset of the verb, onset of the post-verbal determiner, and
-onset of the target noun.
+
+Looks to the objects in the scene were time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
 ROIs were defined by creating boxes around each object in the scene.
@@
 ## Discussion
+
 Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
@@
 # Experiment 1b
+
 Experiment 1b tested whether the failure to replicate significant condition effects in Experiment 1a was due to features of conducting the study remotely (i.e.
-varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or `webgazer` _per se_.
+varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or `webgazer` *per se*.
 Thus, Experiment 1b took place in a lab setting with undergraduate participants but otherwise used the same Method as Experiment 1a.
@@
 ### Participants
+
 Forty-nine participants completed the study in a lab setting.
@@
 ### Materials and Design
+
 Materials were identical to those in Experiment 1a.
@@
 ### Procedure
+
 After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
@@
 ### Apparatus
+
 Subjects were tested on a MacIntosh laptop using the built-in Webcam. The study was run in Chrome using the same code as Exp. 1a.
@@
 ## Results
+
 ```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
@@
 ## Discussion
+
 Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
@@
 
-The second study was a replication attempt of @johanssonLookHereEye2014,
-which examined how visuospatial information is integrated into memory
-for objects. They found that, during memory retrieval, learners
-spontaneously look to blank screen locations where pictures were located
-during encoding [see @spiveyOculomotorMechanismsActivated2001] and that
-this spatial reinstatement facilitates retrieval of the picture.
+The second study was a replication attempt of @johanssonLookHereEye2014, which examined how visuospatial information is integrated into memory for objects.
+They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding [see @spiveyOculomotorMechanismsActivated2001] and that this spatial reinstatement facilitates retrieval of the picture.
 
@@
 
-All stimuli, experiment scripts, data, analysis scripts, and a
-pre-registration are available on the Open Science Framework at
-<https://osf.io/xezfu/>.
+All stimuli, experiment scripts, data, analysis scripts, and a pre-registration are available on the Open Science Framework at <https://osf.io/xezfu/>.
 
@@
 Sixty participants were paid for their participation (once again, 2.5x larger than the original sample size of 24).
-Data from one participant were not properly
-recorded due to unknown technical issues, so data from 59 participants
-were included in all analyses to follow.
+Data from one participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.
 
@@
 
-The experiment consisted of two blocks each composed of an encoding
-phase and a recall phase.
+The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
 The two blocks differed by whether the recall phase was in the free-viewing or fixed-viewing condition, as described in the Procedure.
-Participants were randomly assigned to see the
-fixed-viewing or free-viewing block first. 
-During each encoding phase, participants saw a
-grid indicating the four quadrants of the screen. Each quadrant
-contained six cartoon images of items belonging to the same category. The four categories were humanoids, household objects, animals, and
-methods of transportation (see Figure\ \@ref(fig:E2-example-trial)). Different images were used in each block; there were 48 unique images total across the experiment.
+Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
+During each encoding phase, participants saw a grid indicating the four quadrants of the screen.
+Each quadrant contained six cartoon images of items belonging to the same category.
+The four categories were humanoids, household objects, animals, and methods of transportation (see Figure \@ref(fig:E2-example-trial)).
+Different images were used in each block; there were 48 unique images total across the experiment.
 
 Each recall phase presented participants with a blank screen with a central fixation cross as they listened to true/false statements testing their recall of the previous grid.
-Each statement fell into either an interobject or intraobject
-condition. Interobject statements were those that compared two different
-items in the grid (e.g. "The skeleton is to the left of the robot"),
-while intraobject statements were those that asked about the orientation
-of a single item (e.g. "The bus is facing right"). There were 48 total
-statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
+Each statement fell into either an interobject or intraobject condition.
+Interobject statements were those that compared two different items in the grid (e.g.
+"The skeleton is to the left of the robot"), while intraobject statements were those that asked about the orientation of a single item (e.g.
+"The bus is facing right").
+There were 48 total statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
 
@@
 Each of the four quadrants was presented one at a time.
-First, a list of
-the items in the quadrant was shown, then the pictures of items were displayed in the quadrant. 
-For each item, participants used their arrow keys to indicate whether the object was facing left or right. After the participant identified the direction of each
-item, they would have an additional 30 seconds to encode the name and
-orientation of each item in the quadrant. Finally, after all four quadrants
-were presented, participants were shown the full grid of
-24 items and had 60 seconds to further encode the name and orientation
-of each item.
-
-Participants then entered the first recall phase, in which they listened to the 48 statements and
-responded by pressing the 'F' key for false statements and 'T' for true
-ones. While listening to these statements, in
-the free-viewing block, participants saw a blank screen and were allowed
-to freely gaze around the screen. During the fixed-viewing block,
-participants were asked to fixate a small cross in the center of the
-screen throughout the recall phase. In both cases, the mouse was
-obscured from the screen.
-
-Participants then proceeded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to
-answer a few survey questions (such as whether they wore glasses or
-encountered any distractions).
-
-The primary methodological difference between this replication and
-Johansson and Johansson's study was that the original study included two
-additional viewing conditions that were omitted from this replication
-due to time constraints. In those two conditions, participant were
-prompted to look to a specific quadrant (rather than free viewing or
-central fixation) which either matched or mismatched the original
-location of the to-be-remembered item.
+First, a list of the items in the quadrant was shown, then the pictures of items were displayed in the quadrant.
+For each item, participants used their arrow keys to indicate whether the object was facing left or right.
+After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
+Finally, after all four quadrants were presented, participants were shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
+
+Participants then entered the first recall phase, in which they listened to the 48 statements and responded by pressing the 'F' key for false statements and 'T' for true ones.
+While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
+During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
+In both cases, the mouse was obscured from the screen.
+
+Participants then proceeded to the second encoding and recall phases as described above.
+After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
+
+The primary methodological difference between this replication and Johansson and Johansson's study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
+In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
 
@@
 
-We replicated the key eyetracking result: As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located
-during encoding, suggesting that visuospatial information is integrated into the memory
-for objects.
+We replicated the key eyetracking result: As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding, suggesting that visuospatial information is integrated into the memory for objects.
 Interestingly, we did not replicate the behavior result: a memory benefit, in terms of speed, of spatial reinstatement via gaze position during retrieval of the picture.
@@
 
-The third study was a partial replication attempt of the "looking group" condition of
-@mannsVisualPairedcomparisonTask2000 (we did not replicate their priming condition). This experiment used the visual
-paired-comparison, which involves presenting a previously-viewed image
-and novel image together and measuring the proportion of time spent
-looking at each image. The expected pattern of results is that
-participants will look more at novel objects. @mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of
-behavior could be used to measure the strength of memories. If a viewer
-has a weak memory of the old image, then they may look at the old and
-new images roughly the same amount of time. They tested this in two
-ways. First, they showed participants a set of images, waited five
-minutes, and then paired those images with novel images. They found that
-participants spent more time (58.8% of total time) looking at the novel
-images. They then measured memory performance one day later and found
-that participants were more likely to recall images that they had spent
-less time looking at during the visual paired-comparison task the
-previous day.
+The third study was a partial replication attempt of the "looking group" condition of @mannsVisualPairedcomparisonTask2000 (we did not replicate their priming condition).
+This experiment used the visual paired-comparison, which involves presenting a previously-viewed image and novel image together and measuring the proportion of time spent looking at each image.
+The expected pattern of results is that participants will look more at novel objects.
+@mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of behavior could be used to measure the strength of memories.
+If a viewer has a weak memory of the old image, then they may look at the old and new images roughly the same amount of time.
+They tested this in two ways.
+First, they showed participants a set of images, waited five minutes, and then paired those images with novel images.
+They found that participants spent more time (58.8% of total time) looking at the novel images.
+They then measured memory performance one day later and found that participants were more likely to recall images that they had spent less time looking at during the visual paired-comparison task the previous day.
 
@@
 
-The stimuli, experimental code, and data and analysis scripts can be
-found on the Open Science Framework at <https://osf.io/k63b9/>.
-The pre-registration for the study can be
-found at <https://osf.io/48jsv> . We
-inadvertently did not create a formal pre-registration using the OSF
-registries tool, but this document contains the same information and is
-time stamped prior to the start of data collection. <!-- Students failed
+The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at <https://osf.io/k63b9/>.
+The pre-registration for the study can be found at <https://osf.io/48jsv> .
+We inadvertently did not create a formal pre-registration using the OSF registries tool, but this document contains the same information and is time stamped prior to the start of data collection.
+<!-- Students failed
 to pre-register this one and I missed it. There's an unofficial
@@
 
-Our pre-registered target was 50 participants. 51 participants completed
-the first day of the experiment and 48 completed the second day.
-Following Manns et al., we excluded 3 participants due to perfect
-performance on the recognition memory test because this prevents
-comparison of gaze data for recalled vs. non-recalled images. Our final
-sample size was 45 participants.
+Our pre-registered target was 50 participants.
+51 participants completed the first day of the experiment and 48 completed the second day.
+Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test because this prevents comparison of gaze data for recalled vs.
+non-recalled images.
+Our final sample size was 45 participants.
 
@@
 Two full stimulus lists were created to counterbalance images across participants; the images that composed the "old" set for one list made up the "new" set for the list.
-The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
+The experimental design is visually depicted in Figure \@ref(fig:E3-design-schematic).
 
@@
 
-The experiment was administered over the course of two
-consecutive days. The presentation phase and test phase occurred on
-the first day, while the recognition test occurred on the second day.
-
-During the presentation phase, participants viewed 24 pairs of identical
-images. Each pair was presented for
-5 seconds and an interval of 5 seconds elapsed before the next pair was
-shown. The order of the photographs was randomized and different for
-each participant. After completion of the presentation phase,
-participants were given a 5-minute break during which they could look
-away from the screen.
-
-After the break, they were prompted to complete the eye-tracking
-calibration again before beginning the test phase. During this phase,
-participants again viewed 24 pairs of photographs (old and new) with an interstimulus
-duration of 5 seconds.
-
-Approximately 24 hours after completing the first session, with a leeway
-interval of 12 hours to accommodate busy schedules, participants were
-given the recognition test. Each image was shown on the screen for 1 second, followed by a
-1 second interstimulus interval.
+The experiment was administered over the course of two consecutive days. The presentation phase and test phase occurred on the first day, while the recognition test occurred on the second day.
+
+During the presentation phase, participants viewed 24 pairs of identical images.
+Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
+The order of the photographs was randomized and different for each participant.
+After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
+
+After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
+During this phase, participants again viewed 24 pairs of photographs (old and new) with an interstimulus duration of 5 seconds.
+
+Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
+Each image was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
 Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing 'y' for yes and 'n' for no.
-After they pressed one of the two keys, a prompt on the screen
-asked them to rate their confidence in their answer from 1 as a "pure
-guess" to 5 as "very sure." by clicking on the corresponding number on
-the screen. No feedback on their responses was given during the test.
+After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a "pure guess" to 5 as "very sure." by clicking on the corresponding number on the screen.
+No feedback on their responses was given during the test.
 
@@
 
-The fourth study was a replication attempt of Experiment 1 in
-@ryskinVerbBiasesAre2017, which was closely modeled on
-@snedekerDevelopingConstraintsParsing2004a. These studies used the
-visual world paradigm to show that listeners use knowledge of the
-co-occurrence statistics of verbs and syntactic structures to resolve
-ambiguity. For example, in a sentence like "Feel the frog with the
-feather," the phrase "with the feather" could be describing the frog, or
-it could be describing the instrument that should be used to do the
-"feeling." When both options (a frog holding a feather and a feather by
-itself) are available in the visual display, listeners rely on the
-verb's "bias" (statistical co-occurrence either in norming or corpora)
-to rapidly choose an action while the sentence is unfolding. 
+The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a.
+These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
+For example, in a sentence like "Feel the frog with the feather," the phrase "with the feather" could be describing the frog, or it could be describing the instrument that should be used to do the "feeling." When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb's "bias" (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
 Use of the verb's bias should be reflected in a greater proportion of eye-gaze fixations to the animal (e.g., frog) for verbs that are biased toward modifier structures relative to instrument structures and, conversely, a greater proportion of eye-gaze fixations to the instrument (e.g., feather) for verbs that are biased toward instrument structures relative to modifier structures.
@@
 
-The stimuli, experimental code, and data and original analysis scripts can be
-found on the Open Science Framework at the following link,
-<https://osf.io/x3c49/>. The pre-registration
-for the study can be found at <https://osf.io/3v4pg>.
+The stimuli, experimental code, and data and original analysis scripts can be found on the Open Science Framework at the following link, <https://osf.io/x3c49/>.
+The pre-registration for the study can be found at <https://osf.io/3v4pg>.
 
@@
 
-The images and audios presented to the participants were the same
-stimuli used in the original study. The critical
-trials were divided into modifier-biased, instrument-biased, and
-equibiased conditions, and the filler trials did not contain ambiguous
-instructions. Two lists of critical trials were made with different verb
-and instrument combinations (e.g., "rub" could be paired with "panda"
-and "crayon" in one list and "panda" and "violin" in the second list).
-Within each list, the same verb was presented twice but each time with a
-different target instrument and animal. The lists were randomly assigned
-to the participants to make sure the effects were not caused by the
-properties of the animal or instrument images used.
+The images and audios presented to the participants were the same stimuli used in the original study.
+The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
+Two lists of critical trials were made with different verb and instrument combinations (e.g., "rub" could be paired with "panda" and "crayon" in one list and "panda" and "violin" in the second list).
+Within each list, the same verb was presented twice but each time with a different target instrument and animal.
+The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
 There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials.
@@
 
-During a trial, four pictures were displayed (target animal, target
-instrument, distractor animal, distractor instrument), one in each
-corner of the screen, and participants heard an audio prompt that
-contained instructions about the action they needed to act out (e.g.,
-"Rub the butterfly with the crayon"; see Figure\ \@ref(fig:E4-example-trial))[^2]. Using their
-cursor, participants could act out the instructions by clicking on
-objects and moving them or motioning over the objects[^3]. After the
-action was completed, the participants were instructed to press the
-space bar which led to a screen that said "Click Here" in the middle in
-order to remove bias in the eye and mouse movements from the previous
-trial. The experiment only allowed the participants to move on to the
-next trial once the audio was completely done playing and the mouse had
-been moved over at least one object.
-
-[^1]: The WebGazer.js patch can be found at https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711.
-
-[^2]: In the original study, the pictures appeared one by one on the
-    screen and their names were played as they appeared. We removed this
-    introductory portion of the trial to save time
-
-[^3]:  As opposed to the original study we recorded mouse movement
-    instead of clicking behavior since not all of the audio prompts
-    required clicking. For example, the sentence "locate the camel with
-    the straw" may not involve any clicking but rather only mousing over
-    the camel.
+During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure \@ref(fig:E4-example-trial))[^3].
+Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects[^4].
+After the action was completed, the participants were instructed to press the space bar which led to a screen that said "Click Here" in the middle in order to remove bias in the eye and mouse movements from the previous trial.
+The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
+
+[^3]: In the original study, the pictures appeared one by one on the screen and their names were played as they appeared. We removed this introductory portion of the trial to save time
+
+[^4]: As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
+For example, the sentence "locate the camel with the straw" may not involve any clicking but rather only mousing over the camel.
 
@@
 
-The fifth study was a replication attempt of @shimojoGazeBiasBoth2003,
-which found that human gaze is actively involved in preference
-formation. Separate sets of participants were shown pairs of human faces
-and asked either to choose which one they found more attractive or which
-they felt was rounder. Prior to making their explicit selection,
-participants were increasingly likely to be fixating the face they
-ultimately chose, though this effect was significantly weaker for
-roundness discrimination.
-
-Note that Shimojo and colleagues compare five conditions, of which we
-replicate only the two that figure most prominently in their
-conclusions: the "face-attractiveness-difficult task" and the
-"face-roundness task".
+The fifth study was a replication attempt of @shimojoGazeBiasBoth2003, which found that human gaze is actively involved in preference formation.
+Separate sets of participants were shown pairs of human faces and asked either to choose which one they found more attractive or which they felt was rounder.
+Prior to making their explicit selection, participants were increasingly likely to be fixating the face they ultimately chose, though this effect was significantly weaker for roundness discrimination.
+
+Note that Shimojo and colleagues compare five conditions, of which we replicate only the two that figure most prominently in their conclusions: the "face-attractiveness-difficult task" and the "face-roundness task".
 
@@
 
-All stimuli, experiment scripts, data, and analysis scripts are
-available on the Open Science Framework at [https://osf.io/eubsc/](https://osf.io/eubsc/). 
-The study pre-registration is available at
-[https://osf.io/tv57s](https://osf.io/tv57s).
+All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at <https://osf.io/eubsc/>. The study pre-registration is available at <https://osf.io/tv57s>.
 
@@
 
-Fifty participants for the main task were recruited on Prolific and were
-paid \$10/hour. <!-- Eight subjects, 4 from the attractiveness task group and 4 from
+Fifty participants for the main task were recruited on Prolific and were paid \$10/hour. <!-- Eight subjects, 4 from the attractiveness task group and 4 from
 the roundness task group, were excluded for incorrect validations.
@@
 
-The faces in our replication were selected from a set of 1,000 faces
-within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et
-al. were from the Ekman face database and the AR face database). These
-images were chosen because the person in each image was looking at the
-camera with a fairly neutral facial expression and appeared to be over
-the age of 18.
+The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et al.
+were from the Ekman face database and the AR face database).
+These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
 Twenty-seven participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
@@
 Faces were presented one at a time and in a random order for each participant.
-Data from three participants were excluded because
-their modal response made up more than 50% of their total responses, for a total of 24 participants in the norming.
-
-Following Shimojo et al., 19 face pairs were selected by
-identifying two faces that 1) had a difference in mean attractiveness ratings
-that was 0.25 points or lower and 2) matched in gender, race, and age
-group (young adult, adult, or older adult).
+Data from three participants were excluded because their modal response made up more than 50% of their total responses, for a total of 24 participants in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by identifying two faces that 1) had a difference in mean attractiveness ratings that was 0.25 points or lower and 2) matched in gender, race, and age group (young adult, adult, or older adult).
 
@@
 
-During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). In the attractiveness task,
-participants were asked to chose the more attractice face in the pair
-and in the shape judgment task participants were asked to pick the face
-that appeared rounder. They pressed the "a" key on their keyboard to
-select the face on the left and the "d" key to select the face on the
-right. A fixation cross appeared in the center of the screen between
-each set of faces. Participants were asked to look at this fixation
-cross in order to reset their gaze in between trials. The order of
-the 19 face pairs was random for each participant.
+During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure \@ref(fig:E5-example-trial)).
+In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
+They pressed the "a" key on their keyboard to select the face on the left and the "d" key to select the face on the right.
+A fixation cross appeared in the center of the screen between each set of faces.
+Participants were asked to look at this fixation cross in order to reset their gaze in between trials.
+The order of the 19 face pairs was random for each participant.
 
@@
 ## Results
-In the original study, a video-based eye tracker was used. The eye
-movements of participants were recorded with a digital camera
-downsampled to 33.3 Hz, with eye position determined
-automatically with MediaAnalyzer software. In our study, subjects
-supplied their own cameras, so hardware sampling rate varied. However,
-data was collected at 20 Hz. <!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this! -->
+
+In the original study, a video-based eye tracker was used.
+The eye movements of participants were recorded with a digital camera downsampled to 33.3 Hz, with eye position determined automatically with MediaAnalyzer software.
+In our study, subjects supplied their own cameras, so hardware sampling rate varied.
+However, data was collected at 20 Hz.
+<!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this!
+-->
 
@@
 ```
-
 # General Discussion
@@
 As indicated by the current work, the current jsPsych implementation of WebGazer.js has timing synchronization sufficient for many studies.
-We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
+We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (<https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711>), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
 
@@
 # Contributions
-* Joshua R. de Leeuw
-    + Conceptualization
-    + Data curation
-    + Formal analysis
-    + Investigation
-    + Methodology
-    + Project administration
-    + Software
-    + Supervision
-    + Validation
-    + Visualization
-    + Writing - original draft
-    + Writing - review & editing
-
-* Ariel N. James, Rachel Ryskin, and Joshua K. Hartshorne
-    + Conceptualization
-    + Formal analysis
-    + Visualization
-    + Writing - original draft
-    + Writing - review & editing
-
-* Undergraduate student authors, listed alphabetically: Haylee Backs, Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison, Laura Hoban, William A.
+
+-   Joshua R. de Leeuw
+    -   Conceptualization
+    -   Data curation
+    -   Formal analysis
+    -   Investigation
+    -   Methodology
+    -   Project administration
+    -   Software
+    -   Supervision
+    -   Validation
+    -   Visualization
+    -   Writing - original draft
+    -   Writing - review & editing
+-   Ariel N. James, Rachel Ryskin, and Joshua K. Hartshorne
+    -   Conceptualization
+    -   Formal analysis
+    -   Visualization
+    -   Writing - original draft
+    -   Writing - review & editing
+-   Undergraduate student authors, listed alphabetically: Haylee Backs, Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison, Laura Hoban, William A.
 Hwang, Claire Iannetta, Kristen M.
 Koenig, Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua Sung, and Lauren Thompson
-    + Investigation
-    + Methodology
-    + Software
+    -   Investigation
+    -   Methodology
+    -   Software
 
@@
 # Funding information
+
 Funding for data collection was provided by the Vassar College Department of Cognitive Science (JdL). Partial funding for JKH's contributions was provided by NSF2436092.
@@
 # Competing interests
+
 The authors have no competing interests to declare.
@@
 # Data accessibility statement
-All data and analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis.
+
+All data and analysis code underlying this paper can be found in the Github repository: <https://github.com/jodeleeuw/219-2021-eyetracking-analysis>.
 Study materials and pre-registrations for each experiment are available on Open Science Framework:
 
-* Experiments 1a and 1b: [https://osf.io/g6dum/]
-* Experiment 2: [https://osf.io/xezfu/]
-* Experiment 3: [https://osf.io/k63b9/]
-* Experiment 4: [https://osf.io/x3c49/]
-* Experiment 5: [https://osf.io/eubsc/]
+-   Experiments 1a and 1b: [<https://osf.io/g6dum/>]
+-   Experiment 2: [<https://osf.io/xezfu/>]
+-   Experiment 3: [<https://osf.io/k63b9/>]
+-   Experiment 4: [<https://osf.io/x3c49/>]
+-   Experiment 5: [<https://osf.io/eubsc/>]
 

### 2025-03-30 manuscript.Rmd
Saved visual changes from R studio

@@
 ---
-title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five prominent cognitive science experiments"
+title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five cognitive science experiments"
 shorttitle        : "Webcam eye-tracking paradigms"
-
 author:
@@
     corresponding: yes
-    address: 1600 Grand Ave, Saint Paul, MN 550105, USA
+    address: 1600 Grand Ave, Saint Paul, MN 55105, USA
 
@@
       - Writing - review & editing
-    email: joshua.hartshorne@bc.edu
+    email: jkhartshorne@mghihp.edu
   - name: Haylee Backs
@@
     email: jdeleeuw@vassar.edu
-
 affiliation:
@@
     institution: Cognitive Science Department, Vassar College
-
 abstract: |
+
   Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require.
@@
 1) should be adapted to coarser quadrant or split-half displays.
-
 keywords          : "eye-tracking, online, webcam, jsPsych, cognitive science"
-wordcount         : "X"
-
+wordcount         : "13,115"
 bibliography      : ["references.bib"]
-
 floatsintext      : yes
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 output            : papaja::apa6_pdf
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-The use of eye-tracking to study cognition took off when Alfred Yarbus used suction cups to affix a mirror system to the sclera of the eye in order to monitor eye position during the perception of images [@yarbus1967eye].
-In one study, participants viewed a painting depicting multiple people in a complex interaction inside of a 19th century Russian home.
-Yarbus showed, among other things, that the scan paths and locations of fixations were largely dependent on the instructions given to participants (e.g., View the picture freely vs.
-Remember the position of the people and objects in the room).
-In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system.
-Since these findings, eye-tracking has become a central method in cognitive science research [for reviews see @hayhoe2005eye; @richardsonEyeTrackingResearch2004; @rayner1998eye].
-For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning], and eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
-
-An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time).
-This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research.
-Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD, @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
-Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend [@nosek2022replicability].
-
-A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired].
-Historically, this option has not been available for eye-tracking, since few potential subjects have expensive eyetrackers at home.
-In principal, this could be circumvented by using so-called "poor-man's" eye-tracking, in which researchers videotape the subject's face and code eye position frame-by-frame [@snedeker2003using].
-Most computers now have high-quality built-in cameras, so recording video is straightforward.
-Unfortunately, coding images frame-by-frame is extremely time-intensive, making large-sample studies unrealistic.
-However, in recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation].
-Nonetheless, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], `lab.js` [@henninger2021lab], or `PsychoJS` [@peirce2019psychopy2].
-
-Given the potential game-changing nature of webcam-based eye-tracking, a number of research groups have investigated how well it works.
-Nearly all this work has used `Webgazer.js` --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.
-There are two potential limitations to webcam-based eye-tracking.
-First, the spatial and temporal resolution is less than what is achievable with an infrared system.
-This is less a limitation of webcams than a limitation of the information about eyegaze available in an image of a face.
-Anecdotally, researchers who use poor-man's eyetracking find it difficult to locate the gaze to anything more fine-grained than quadrants.
-Second, testing subjects over the Internet involves less control: subjects may be unable or unwilling to calibrate equipment, adjust lighting, etc., to the same level of precision typical of in-lab studies.
-
-Results to date have been encouraging.
-@semmelmann2018online found data quality was reasonable for fixation location and saccades in fixation, smooth pursuit, and free-viewing tasks, though data collected online through a crowdsourcing platform was slightly more variable and timing was somewhat delayed compared to data collected in the lab.
-Several researchers successfully replicated well-known findings from the sentence-processing literature involving predictive looks [@degen2021seeing; @prystauka2023online; @vos2022comparing; @van2023validation].
-@yang2021webcam successfully replicated a well-established link between value-based decision-making and eye gaze [see also @van2023validation].
-
-While promising, there are some salient limitations.
-First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2024webcams; @van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing].
-Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].[^1] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
-
-[^1]: See also discussion at <https://github.com/jspsych/jsPsych/discussions/1892>
-
-Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online; @bogdan2024investigating], dividing the screen either in half or in quadrants.
-This is particularly salient with [@prystauka2023online], which simplified @altmannIncrementalInterpretationVerbs1999's design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
-Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.
-
-Finally, the prior work has focused on a relatively limited range of methods.
-Different paradigms have different technical requirements and analyze the results differently.
-As a result, the breadth of utility of webcam eye-tracking is unclear.
+The use of eye-tracking to study cognition took off when Alfred Yarbus
+used suction cups to affix a mirror system to the sclera of the eye in
+order to monitor eye position during the perception of images
+[@yarbus1967eye]. In one study, participants viewed a painting depicting
+multiple people in a complex interaction inside of a 19th century
+Russian home. Yarbus showed, among other things, that the scan paths and
+locations of fixations were largely dependent on the instructions given
+to participants (e.g., View the picture freely vs. Remember the position
+of the people and objects in the room). In other words, the cognitive
+processing that the individual is engaged in drives the visuo-motor
+system. Since these findings, eye-tracking has become a central method
+in cognitive science research [for reviews, see @hayhoe2005eye,
+@richardsonEyeTrackingResearch2004, @rayner1998eye]. For example, gaze
+location during natural scene perception is used to test theories of
+visual attention [e.g., @henderson2017meaning], and eye-movements during
+auditory language comprehension, using the "visual world paradigm,"
+demonstrated the context-dependent and incremental nature of language
+processing [e.g., @tanenhaus1995].
+
+An important limitation of the eye-tracking methodology is that it has
+typically required costly equipment (eye-trackers can range in price
+from a few thousand dollars to tens of thousands of dollars), particular
+laboratory conditions (a quiet room with consistent indoor lighting
+conditions), and a substantial time investment (e.g., bringing
+participants into a laboratory one at a time). This limits who can
+conduct eye-tracking research -- not all researchers have the necessary
+resources -- and who can participate in eye-tracking research. Most
+eye-tracking study participants are from western, educated,
+industrialized, rich, and democratic [WEIRD; @henrich2010weirdest]
+convenience samples [but see @ryskin2023real], which diminishes the
+generalizability of the findings and the scope of conclusions that can
+be drawn about human cognition. Likewise, the sample sizes for in-lab
+experiments are usually orders of magnitude smaller than what
+statisticians recommend [@nosek2022replicability].
+
+A robust solution to all these problems is online experiments,
+particularly with volunteer citizen scientists as participants
+[@li2024developmental; @hartshorne2019thousand;
+@reinecke2015labinthewild; @gosling2010wired]. Historically, this option
+has not been available for eye-tracking, since few potential subjects
+have expensive eyetrackers at home. In principal, this could be
+circumvented by using so-called "poor-man's" eye-tracking, in which
+researchers videotape the subject's face and code eye position
+frame-by-frame [@snedeker2003using]. Most computers now have
+high-quality built-in cameras, so recording video is straightforward.
+Unfortunately, coding images frame-by-frame is extremely time-intensive,
+making large-sample studies unrealistic. However, in recent years, image
+analysis has improved to the point where this work can be automated with
+reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid;
+@burton2014comparison; @skovsgaard2011evaluation]. Nonetheless,
+webcam-based eyetracking only started to be used regularly in research
+with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a
+webcam-based Javascript plug-in that works in the browser and which can
+be integrated with any Javascript web interface, including `jsPsych`
+[@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla],
+or `lab.js` [@henninger2021lab].
+
+Given the potential game-changing nature of webcam-based eye-tracking, a
+number of research groups have investigated how well it works. Nearly
+all this work has used `Webgazer.js` --- most in combination with
+jsPsych, but some with Gorilla or hand-built integrations. There are two
+potential limitations to webcam-based eye-tracking. First, the spatial
+and temporal resolution is less than what is achievable with an infrared
+system. This is less a limitation of webcams than a limitation of the
+information about eyegaze available in an image of a face. Anecdotally,
+researchers who use poor-man's eyetracking find it difficult to locate
+the gaze to anything more fine-grained than quadrants. Second, testing
+subjects over the Internet involves less control: subjects may be unable
+or unwilling to calibrate equipment, adjust lighting, etc., to the same
+level of precision typical of in-lab studies.
+
+Results to date have been encouraging. @semmelmann2018online found data
+quality was reasonable for fixation location and saccades in fixation,
+smooth pursuit, and free-viewing tasks, though data collected online
+through a crowdsourcing platform was slightly more variable and timing
+was somewhat delayed compared to data collected in the lab. Several
+researchers successfully replicated well-known findings from the
+sentence-processing literature involving predictive looks
+[@degen2021seeing; @prystauka2023online; @vos2022comparing;
+@van2023validation]. @yang2021webcam successfully replicated a
+well-established link between value-based decision-making and eye gaze
+[see also @van2023validation].
+
+While promising, there are some salient limitations. First, many of the
+studies report effects that are smaller or later than what had been
+previously observed in the lab [@slim2022moving; @degen2021seeing;
+@van2023validation]. Importantly, accurate timing on a web browser is
+not trivial [@passell2021cognitive; @de2016psychophysics], and subtle
+programming choices can significantly affect the accuracy of
+`WebGazer.js` timing [@yang2021webcam].[^1] Since most of the prior work
+did not address these timing issues, it is not clear how many of the
+reported lab/web differences would resolve.
+
+[^1]: See also discussion at
+    <https://github.com/jspsych/jsPsych/discussions/1892>
+
+Second, prior work has focused on studies with relatively coarse-grained
+regions of interest [but see @semmelmann2018online], dividing the screen
+either in half or in quadrants. This is particularly salient with
+[@prystauka2023online], which simplified
+@altmannIncrementalInterpretationVerbs1999's design so that regions of
+interest are quadrants rather than the finer-grained ROIs used in the
+original. Certainly, webcam eyetracking will not be as spatially
+fine-grained as an infrared eyetracker, but we do not yet have a good
+sense of the limits.
+
+Finally, the prior work has focused on a relatively limited range of
+methods. Different paradigms have different technical requirements and
+analyze the results differently. As a result, the breadth of utility of
+webcam eye-tracking is unclear.
 
@@
 
-In order to broaden the validation of online eye-tracking methodology, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
-The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
-Critically, we used the only implementation known to have addressed a critical bug in the timing precision of WebGazer.js, specifically the one in `jsPsych`, a package which is known in general for having particularly good timing precision [@de2016psychophysics; @bridges2020timing].
+In order to broaden the validation of online eye-tracking methodology,
+we set out to reproduce five previously published studies representing a
+variety of questions, topics, and paradigms. The goal was to examine the
+strengths and weaknesses of webcam eye-tracking for common paradigms in
+cognitive science, across a broad range of research areas. Critically,
+we used the implementation known to have the greatest temporal precision
+to date: `jsPsych` and a modification of `Webgazer`.
 
@@
 
-Studies with large effect sizes and which are known to replicate are ideal targets for further replication; otherwise, it can be difficult to distinguish a failure of the method from a failure of the original study to replicate.
-In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability.
-We addressed this in several ways.
-First, replicating five very different studies from different research traditions decreases our reliance on any one study.
-Second, we include several "sanity check" analyses, such as the correlation between calibration accuracy and effect size.
-If the effect is real but there is noise from low-accuracy eye-tracking, this correlation should be substantial.
-Third, for two of the studies, we had comparison data collected in-lab either using `jsPsych` or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
-
-We chose five high-impact eye-tracking studies involving adult subjects [for a comparison of remote WebGazer and in-lab anticipatory looking effects with 18-27 month-old participants, see @steffan2024validation].
-Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "naturalistic" scenes).
-As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
-Table \@ref(tab:studies-table) provides an overview of the five studies we selected.
+Studies with large effect sizes and which are known to replicate are
+ideal targets for further replication; otherwise, it can be difficult to
+distinguish a failure of the method from a failure of the original study
+to replicate. In practice, replications (successful or otherwise) have
+only been reported for a small number of studies, so we ultimately
+included some studies with unknown replicability. We addressed this in
+several ways. First, replicating five very different studies from
+different research traditions decreases our reliance on any one study.
+Second, we include several "sanity check" analyses, such as the
+correlation between calibration accuracy and effect size. If the effect
+is real but there is noise from low-accuracy eye-tracking, this
+correlation should be substantial. Third, for two of the studies, we had
+comparison data collected in-lab either using `jsPsych` or a more
+traditional eyetracker technology, allowing us to directly assess the
+impact of differences in subject population and equipment/setting.
+
+<!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->
+
+<!-- RR: switched ryskin to Snedeker & trueswell 2004 bcs my 75 looked sad -->
+
+We chose five high-impact eye-tracking studies involving adult subjects
+[for an comparison of remote WebGazer and in-lab anticipatory looking
+effects with 18-27 month-old participants, see @steffan2024validation].
+Our goal was to include experiments from a range of topic areas (e.g.,
+memory, decision making, psycholinguistics) and paradigms (two halves of
+the screen, visual world paradigm with four quadrants, visual world
+paradigm with "naturalistic" scenes). As noted above, we had a
+preference for well-established findings that are known to replicate,
+though for sake of diversity this was not always possible. Table
+\@ref(tab:studies-table) provides an overview of the five studies we
+selected.
 
@@
 
-All data and analysis code underlying this paper can be found in the Github repository: <https://github.com/jodeleeuw/219-2021-eyetracking-analysis>.
-The current paper is fully reproducible by rendering `manuscript.Rmd`.
-
 ## Participants
 
-Participants completed the experiment remotely and were recruited through the Prolific platform.
-In order to have access to the experiment, participants had to meet the following criteria: 18 years of age or older, fluency in English, and access to a webcam.
-All participants provided informed consent.
-The online studies were approved by the Vassar College Institutional Review Board.
+Participants completed the experiment remotely and were recruited
+through the Prolific platform. In order to have access to the
+experiment, participants had to meet the following criteria: 18 years of
+age or older, fluency in English, and access to a webcam. All
+participants provided informed consent. The online studies were approved
+by the Vassar College Institutional Review Board.
 
 In addition, an in-lab replication was conducted for Experiment 1.
-Information about the sample is given in the Experiment 1 Method sections.
-This study was approved by the Institutional Review Board at Boston College.
-
-In order to have adequate statistical power and precision, we aimed for 2.5x the sample size of the original experiment, following the heuristic of Simonsohn [@simonsohn2015].
-In Experiment 5, the original sample size was so small that we opted to collect 5x the number of participants to increase precision.
-Because of budget and time constraints we were unable to replace the data for subjects who were excluded or whose data was missing due to technical failures.
+Information about the sample is given in the Experiment 1 Method
+sections. This study was approved by the Institutional Review Board at
+Boston College.
+
+In order to have adequate statistical power and precision, we aimed for
+2.5x the sample size of the original experiment, following the heuristic
+of Simonsohn [@simonsohn2015]. In Experiment 5, the original sample size
+was so small that we opted to collect 5x the number of participants to
+increase precision. Because of budget and time constraints we were
+unable to replace the data for subjects who were excluded or whose data
+was missing due to technical failures.
 
@@
 
-We used a fork of the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].[^2] Our fork included changes to `webgazer.js` in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant.
-Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing.
-This modification is similar to what Yang and Krajbich [-@yang2021webcam] reported improved the sampling rate in their study of webgazer.
-We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.
-
-[^2]: The WebGazer.js patch can be found at <https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711>.
+We used a fork of the `webgazer.js` library for webcam eye-tracking
+[@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript
+library for running behavioral experiments in a web browser
+[@deleeuwJsPsychJavaScriptLibrary2015]. Our fork included changes to
+`webgazer.js` in order to improve data quality for experiments in which
+the precise timing of stimulus onsets is relevant. Specifically, we
+implemented a polling mode so that gaze predictions could be requested
+at a regular interval, which improved the sampling rate considerably in
+informal testing. This modification is similar to what Yang and Krajbich
+[-@yang2021webcam] reported improved the sampling rate in their study of
+webgazer. We also adjusted the mechanism for recording time stamps of
+each gaze prediction, so that the time stamp reported by webgazer is
+based on when the video frame is received and not when the computation
+of the gaze point is finished.
 
@@
 
-When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved.
-They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front.
-The webcam's view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still.
-The experiment window then expanded to full screen, and participants began the eye-tracking calibration.
-
-During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one.
-Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen.
-The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest.
-After the calibration was completed, the validation began.
-Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen.
-If accuracy on the validation was too low (fewer than 50% of looks landed within a 200 px radius of the validation points), participants were given an opportunity to re-start the calibration and validation steps.
-However, even participants with low calibration accuracy were allowed to complete the experiment, because we specifically wanted to study the consequences of low calibration accuracy.<!--If the second attempt also lead to low validation
+When participants began the experiment, they were notified the webcam
+would be used for eye tracking but no video would be saved. They were
+asked to remove glasses if possible, close any other tabs or apps, turn
+off notifications, and make sure their face was lit from the front. The
+webcam's view of the participant popped up on the screen, and
+participants were asked to center their face in the box and keep their
+head still. The experiment window then expanded to full screen, and
+participants began the eye-tracking calibration.
+
+During the calibration, dots appeared on the screen one at a time in
+different locations, and the participants had to fixate them and click
+on each one. Once they clicked on a dot, it would disappear and a new
+one would appear in a different location on the screen. The locations of
+calibration dots were specific to each experiment (details below) and
+appeared in the areas of the screen where the visual stimuli would
+appear during the main task in order to ensure that eye movements were
+accurately recorded in the relevant regions of interest. After the
+calibration was completed, the validation began. Participants were asked
+to go through the same steps as the calibration, except that they only
+fixated the dots as they appeared in different locations on the screen.
+If accuracy on the validation was too low (fewer than 50% of looks
+landed within a 200 px radius of the validation points), participants
+were given an opportunity to re-start the calibration and validation
+steps. <!--If the second attempt also lead to low validation
 accuracy, participants were informed that they could not participate in
@@
 
-Upon finishing calibration, participants were reminded to keep their head still for the remainder of the study.
-
 ## Pre-registration
 
-These data were collected within the context of an undergraduate research methods course.
-Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the last author.
-The OSF repositories associated with these experiments are linked in the methods sections of each individual study.
-Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality).
+These data were collected within the context of an undergraduate
+research methods course. Groups of students (co-authors) designed and
+programmed experiments in jsPsych, pre-registered their planned
+analyses, and collected data through Prolific under the supervision of
+the last author. The OSF repositories associated with these experiments
+are linked in the methods sections of each individual study. Note that
+in the current paper we expand on those pre-registered analyses (e.g.,
+including analyses of the calibration quality). All analysis code
+underlying this paper can be found in the Github repository:
+<https://github.com/jodeleeuw/219-2021-eyetracking-analysis>
 
@@
 
-The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999.
-Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing.
-For example, when looking at the display in Figure \@ref(fig:E1-example-trial) and listening to a sentence like "The boy will eat the...," participants are more likely to look at the cake than when they hear "The boy will move the...," in which case they tend to look at the train, presumably because cakes are edible and trains are not.
-Semantic information available at the verb is used to anticipate upcoming linguistic input.
+The first study was a replication attempt of
+@altmannIncrementalInterpretationVerbs1999. Altmann and Kamide used the
+visual world eye-tracking paradigm [@tanenhaus1995] to show that
+meanings of verbs rapidly constrain the set of potential subsequent
+referents in sentence processing. For example, when looking at the
+display in Figure \@ref(fig:E1-example-trial) and listening to a
+sentence like "The boy will eat the...," participants are more likely to
+look at the cake than when they hear "The boy will move the...," in
+which case they tend to look at the train, presumably because cakes are
+edible and trains are not. Semantic information available at the verb is
+used to anticipate upcoming linguistic input.
 
@@
 
-All stimuli, experiment scripts, data, analysis scripts, and a pre-registration are available on the Open Science Framework at <https://osf.io/s82kz>.
+All stimuli, experiment scripts, data, analysis scripts, and a
+pre-registration are available on the Open Science Framework at
+<https://osf.io/s82kz>.
 
@@
 
-Sixty participants (2.5 times the original sample of 24) were paid \$2.60 for their participation.
-For unknown reasons, 2 of the subjects' results were not recorded, so in the analysis, we worked with data collected from 58 participants.
+Sixty participants (2.5 times the original sample of 24) were paid
+\$2.60 for their participation. For unknown reasons, 2 of the subjects'
+results were not recorded, so in the analysis, we worked with data
+collected from 58 participants.
 
@@
 
-The visual stimuli were created through Canva and depicted an agent accompanied by four to five objects in the scene (see Figure \@ref(fig:E1-example-trial)).
-On critical trials, participants heard one of two sentences associated with the scene.
-In the restrictive condition, the sentence (e.g., "The boy will eat the cake") contained a verb (e.g., "eat") which restricts the set of possible subsequent referents (e.g., to edible things).
-Only the target object (e.g., the cake) was semantically consistent with the verb's meaning.
-In the non-restrictive condition, the sentence (e.g., "The boy will move the cake") contained a verb (e.g., "move") which does not restrict the set of possible subsequent referents.
-The target object (e.g., the cake) as well as the distractor objects (e.g., the train, the ball, etc.) were semantically consistent with the verb's meaning.
-Both sentences were compatible with the scene, such that the correct keyboard response for the critical trials was "yes." Filler trials consisted of scenes that also contained an agent surrounded by objects as in the critical trials, but corresponding sentences named an object that was not present in the scene.
-The correct keyboard response for the filler trials was "no."
+The visual stimuli were created through Canva and depicted an agent
+accompanied by four to five objects in the scene (see
+Figure \@ref(fig:E1-example-trial)). On critical trials, participants
+heard one of two sentences associated with the scene. In the restrictive
+condition, the sentence (e.g., "The boy will eat the cake") contained a
+verb (e.g., "eat") which restricts the set of possible subsequent
+referents (e.g., to edible things). Only the target object (e.g., the
+cake) was semantically consistent with the verb's meaning. In the
+non-restrictive condition, the sentence (e.g., "The boy will move the
+cake") contained a verb (e.g., "move") which does not restrict the set
+of possible subsequent referents. The target object (e.g., the cake) as
+well as the distractor objects (e.g., the train, the ball, etc.) were
+semantically consistent with the verb's meaning. Both sentences were
+compatible with the scene, such that the correct keyboard response for
+the critical trials was "yes." Filler trials consisted of scenes that
+also contained an agent surrounded by objects as in the critical trials,
+but corresponding sentences named an object that was not present in the
+scene. The correct keyboard response for the filler trials was "no."
 
@@
 
-Each participant was presented with 16 critical trials (eight in the restrictive condition, eight in the non-restrictive condition) and 16 fillers for a total of 32 trials.
-The order of trials and the assignment of critical scene to condition was random on a subject-by-subject basis.<!-- right?-->
+Each participant was presented with 16 critical trials (eight in the
+restrictive condition, eight in the non-restrictive condition) and 16
+fillers for a total of 32 trials. The order of trials and the assignment
+of critical scene to condition was random on a subject-by-subject
+basis.<!-- right?-->
 
@@
 
-Looks to the objects in the scene were time-locked to the onset of the verb, the offset of the verb, onset of the post-verbal determiner, and onset of the target noun.
-ROIs were defined by creating boxes around each object in the scene.
-The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
-Each scene contained an agent region, a target region, and three or four distractor regions.
+Looks to the objects in the scene were time-locked to the onset of the
+verb, the offset of the verb, onset of the post-verbal determiner, and
+onset of the target noun. ROIs were defined by creating boxes around
+each object in the scene. The size of each box was determined by taking
+the height and width of the given object and adding 20 pixels of
+padding. Each scene contained an agent region, a target region, and
+three or four distractor regions.
 
@@
 
-Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
-This is unlikely to be because the original effect is unreliable.
-Indeed, one of us had successfully replicated it previously using traditional methods [@james2023language].
-
-An eyeball comparison to published data [@altmannIncrementalInterpretationVerbs1999, @james2023language] suggests that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
-After eliminating participants with validation accuracy under 50% and/or 10% or fewer fixations to any ROIs, we were left with only 22 of the original 60 participants.
-Either of these facts could have resulted in low power to detect effects.
-Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to test whether the failure to replicate was due to using a remote sample or to the technology itself.
+Across three different tests of the hypothesis that listeners will use
+verb semantics to anticipate the upcoming referent, we found results
+that were numerically consistent with the hypothesis but not
+statistically significant. This is unlikely to be because the original
+effect is unreliable. Indeed, one of us had successfully replicated it
+previously using traditional methods [@james2023language].
+
+An eyeball comparison to published data
+[@altmannIncrementalInterpretationVerbs1999, @james2023language]
+suggests that looks to the objects in the scene (relative to background
+or off-screen looks) were depressed across conditions and objects. After
+eliminating participants with validation accuracy under 50% and/or 10%
+or fewer fixations to any ROIs, we were left with only 22 of the
+original 60 participants. Either of these facts could have resulted in
+low power to detect effects. Given that nearly two-thirds of
+participants had poor data quality, we ran a follow-up webcam study in a
+lab setting order to test whether the failure to replicate was due to
+using a remote sample or to the technology itself.
 
@@
 
-Experiment 1b tested whether the failure to replicate significant condition effects in Experiment 1a was due to features of conducting the study remotely (i.e.
-varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or `webgazer` *per se*.
-Thus, Experiment 1b took place in a lab setting with undergraduate participants but otherwise used the same Method as Experiment 1a.
+Experiment 1b tested whether the failure to replicate significant
+condition effects in Experiment 1a was due to features of conducting the
+study remotely (i.e. varied experimental settings and apparatuses, lower
+compliance) rather than webcam-based eye-tracking or `webgazer` *per
+se*. Thus, Experiment 1b took place in a lab setting with undergraduate
+participants but otherwise used the same Method as Experiment 1a.
 
@@
 
-Forty-nine participants completed the study in a lab setting.
-They were recruited via the Boston College subject pool.
-Participants needed to be 18 years of age or older and native speakers of English.
+Forty-nine participants completed the study in a lab setting. They were
+recruited via the Boston College subject pool. Participants needed to be
+18 years of age or older and native speakers of English.
 
@@
 
-After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
+After being greeted by the experimenter and completing the informed
+consent form, participants followed on-screen prompts to complete the
+study, including calibration, as described in the Experiment 1a
+Procedure.
 
@@
 
-Subjects were tested on a MacIntosh laptop using the built-in Webcam. The study was run in Chrome using the same code as Exp. 1a.
+Subjects were tested on a MacIntosh laptop using the built-in Webcam.
+The study was run in Chrome using the same code as Exp. 1a.
 
@@
 
-Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
-In Experiment 1a, results from the remote sample were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance.
-This was not due to vagaries of remote samples or working with a more diverse subject population: results from the in-lab study were, if anything, worse.
-Nor does our failure to replicate seem to be driven by subjects with poor calibration; effect sizes were not correlated with calibration success, and restricting analyses to subjects with good calibration scores only helped in one of the experiments and in only one of the three critical analyses.
-
-Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking.
-Notably, the ROIs were tightly drawn around the five to six objects in each scene (drawing larger ROIs in these scenes would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
-Further evidence comes from a recent `webgazer` study that successfully replicated the original results using modified stimuli consisting of only four objects, each in separate quadrants, allowing for larger, more distinct ROIs [@prystauka2023online].
+Overall, the results of Experiment 1 paint a sobering picture of
+web-based eye-tracking. In Experiment 1a, results from the remote sample
+were in the expected direction but effects were smaller and delayed
+relative to previous work and failed to reach statistical significance.
+This was not due to vagaries of remote samples or working with a more
+diverse subject population: results from the in-lab study were, if
+anything, worse. Nor does our failure to replicate seem to be driven by
+subjects with poor calibration; effect sizes were not correlated with
+calibration success, and restricting analyses to subjects with good
+calibration scores only helped in one of the experiments and in only one
+of the three critical analyses.
+
+Taken together, the instability of these effects might suggest that this
+paradigm is not well-suited for webcam-based eye-tracking. Notably, the
+ROIs were tightly drawn around the five to six objects in each scene
+(drawing larger ROIs in these scenes would have led to overlapping
+objects) and thus, analyses were unforgiving of inaccurate calibration.
+Further evidence comes from a recent `webgazer` study that successfully
+replicated the original results using modified stimuli consisting of
+only four objects, each in separate quadrants, allowing for larger, more
+distinct ROIs [@prystauka2023online].
 
@@
 
-The second study was a replication attempt of @johanssonLookHereEye2014, which examined how visuospatial information is integrated into memory for objects.
-They found that, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding [see @spiveyOculomotorMechanismsActivated2001] and that this spatial reinstatement facilitates retrieval of the picture.
+The second study was a replication attempt of @johanssonLookHereEye2014,
+which examined how visuospatial information is integrated into memory
+for objects. They found that, during memory retrieval, learners
+spontaneously look to blank screen locations where pictures were located
+during encoding [see @spiveyOculomotorMechanismsActivated2001] and that
+this spatial reinstatement facilitates retrieval of the picture.
 
@@
 
-All stimuli, experiment scripts, data, analysis scripts, and a pre-registration are available on the Open Science Framework at <https://osf.io/xezfu/>.
+All stimuli, experiment scripts, data, analysis scripts, and a
+pre-registration are available on the Open Science Framework at
+<https://osf.io/xezfu/>.
 
@@
 
-Sixty participants were paid for their participation (once again, 2.5x larger than the original sample size of 24).
-Data from one participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.
+Sixty participants were paid for their participation (once again, 2.5x
+larger than the original sample size of 24). Data from one participant
+were not properly recorded due to unknown technical issues, so data from
+59 participants were included in all analyses to follow.
 
@@
 
-The experiment consisted of two blocks each composed of an encoding phase and a recall phase.
-The two blocks differed by whether the recall phase was in the free-viewing or fixed-viewing condition, as described in the Procedure.
-Participants were randomly assigned to see the fixed-viewing or free-viewing block first.
-During each encoding phase, participants saw a grid indicating the four quadrants of the screen.
-Each quadrant contained six cartoon images of items belonging to the same category.
-The four categories were humanoids, household objects, animals, and methods of transportation (see Figure \@ref(fig:E2-example-trial)).
-Different images were used in each block; there were 48 unique images total across the experiment.
-
-Each recall phase presented participants with a blank screen with a central fixation cross as they listened to true/false statements testing their recall of the previous grid.
-Each statement fell into either an interobject or intraobject condition.
-Interobject statements were those that compared two different items in the grid (e.g.
-"The skeleton is to the left of the robot"), while intraobject statements were those that asked about the orientation of a single item (e.g.
-"The bus is facing right").
-There were 48 total statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
+The experiment consisted of two blocks each composed of an encoding
+phase and a recall phase. The two blocks differed by whether the recall
+phase was in the free-viewing or fixed-viewing condition, as described
+in the Procedure. Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first. During each encoding phase,
+participants saw a grid indicating the four quadrants of the screen.
+Each quadrant contained six cartoon images of items belonging to the
+same category. The four categories were humanoids, household objects,
+animals, and methods of transportation (see
+Figure \@ref(fig:E2-example-trial)). Different images were used in each
+block; there were 48 unique images total across the experiment.
+
+Each recall phase presented participants with a blank screen with a
+central fixation cross as they listened to true/false statements testing
+their recall of the previous grid. Each statement fell into either an
+interobject or intraobject condition. Interobject statements were those
+that compared two different items in the grid (e.g. "The skeleton is to
+the left of the robot"), while intraobject statements were those that
+asked about the orientation of a single item (e.g. "The bus is facing
+right"). There were 48 total statements in each block, such that each
+object was the subject of both an intraobject and an intraobject
+statement; there were 96 unique statements total across the experiment.
 
@@
 
-Participants received instructions that included an example grid and an explicit request that they not use any tools to help them during encoding.
-Participants then began their first encoding phase.
-Each of the four quadrants was presented one at a time.
-First, a list of the items in the quadrant was shown, then the pictures of items were displayed in the quadrant.
-For each item, participants used their arrow keys to indicate whether the object was facing left or right.
-After the participant identified the direction of each item, they would have an additional 30 seconds to encode the name and orientation of each item in the quadrant.
-Finally, after all four quadrants were presented, participants were shown the full grid of 24 items and had 60 seconds to further encode the name and orientation of each item.
-
-Participants then entered the first recall phase, in which they listened to the 48 statements and responded by pressing the 'F' key for false statements and 'T' for true ones.
-While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen.
-During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase.
-In both cases, the mouse was obscured from the screen.
-
-Participants then proceeded to the second encoding and recall phases as described above.
-After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).
-
-The primary methodological difference between this replication and Johansson and Johansson's study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints.
-In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.
+Participants received instructions that included an example grid and an
+explicit request that they not use any tools to help them during
+encoding. Participants then began their first encoding phase. Each of
+the four quadrants was presented one at a time. First, a list of the
+items in the quadrant was shown, then the pictures of items were
+displayed in the quadrant. For each item, participants used their arrow
+keys to indicate whether the object was facing left or right. After the
+participant identified the direction of each item, they would have an
+additional 30 seconds to encode the name and orientation of each item in
+the quadrant. Finally, after all four quadrants were presented,
+participants were shown the full grid of 24 items and had 60 seconds to
+further encode the name and orientation of each item.
+
+Participants then entered the first recall phase, in which they listened
+to the 48 statements and responded by pressing the 'F' key for false
+statements and 'T' for true ones. While listening to these statements,
+in the free-viewing block, participants saw a blank screen and were
+allowed to freely gaze around the screen. During the fixed-viewing
+block, participants were asked to fixate a small cross in the center of
+the screen throughout the recall phase. In both cases, the mouse was
+obscured from the screen.
+
+Participants then proceded to the second encoding and recall phases as
+described above. After completing both encoding-recall blocks,
+participants were asked to answer a few survey questions (such as
+whether they wore glasses or encountered any distractions).
+
+The primary methodological difference between this replication and
+Johansson and Johansson's study was that the original study included two
+additional viewing conditions that were omitted from this replication
+due to time constraints. In those two conditions, participant were
+prompted to look to a specific quadrant (rather than free viewing or
+central fixation) which either matched or mismatched the original
+location of the to-be-remembered item.
 
@@
 
-### Survey results
-
-```{r E2-analysis-survey, child='group-b/E2-analysis-survey.Rmd'}
-
-```
-
 ## Discussion
 
-We replicated the key eyetracking result: As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located during encoding, suggesting that visuospatial information is integrated into the memory for objects.
-Interestingly, we did not replicate the behavior result: a memory benefit, in terms of speed, of spatial reinstatement via gaze position during retrieval of the picture.
-For researchers interested in that effect, this is an issue to be followed up on.
-However, it is not strictly relevant for our evaluation of gaze tracking online.
+We replicated the key eyetracking result: As in
+@johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001,
+during memory retrieval, learners spontaneously look to blank screen
+locations where pictures were located during encoding, suggesting that
+visuospatial information is integrated into the memory for objects.
+Interestingly, we did not replicate the behavior result: a memory
+benefit, in terms of speed, of spatial reinstatement via gaze position
+during retrieval of the picture. For researchers interested in that
+effect, this is an issue to be followed up on. However, it is not
+strictly relevant for our evaluation of gaze tracking online.
 
@@
 
-The third study was a partial replication attempt of the "looking group" condition of @mannsVisualPairedcomparisonTask2000 (we did not replicate their priming condition).
-This experiment used the visual paired-comparison, which involves presenting a previously-viewed image and novel image together and measuring the proportion of time spent looking at each image.
-The expected pattern of results is that participants will look more at novel objects.
-@mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of behavior could be used to measure the strength of memories.
-If a viewer has a weak memory of the old image, then they may look at the old and new images roughly the same amount of time.
-They tested this in two ways.
-First, they showed participants a set of images, waited five minutes, and then paired those images with novel images.
-They found that participants spent more time (58.8% of total time) looking at the novel images.
-They then measured memory performance one day later and found that participants were more likely to recall images that they had spent less time looking at during the visual paired-comparison task the previous day.
+The third study was a partial replication attempt of the "looking group"
+condition of @mannsVisualPairedcomparisonTask2000 (we did not replicate
+their priming condition). This experiment used the visual
+paired-comparison, which involves presenting a previously-viewed image
+and novel image together and measuring the proportion of time spent
+looking at each image. The expected pattern of results is that
+participants will look more at novel objects. They
+@mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of
+behavior could be used to measure the strength of memories. If a viewer
+has a weak memory of the old image, then they may look at the old and
+new images roughly the same amount of time. They tested this in two
+ways. First, they showed participants a set of images, waited five
+minutes, and then paired those images with novel images. They found that
+participants spent more time (58.8% of total time) looking at the novel
+images. They then measured memory performance one day later and found
+that participants were more likely to recall images that they had spent
+less time looking at during the visual paired-comparison task the
+previous day.
 
@@
 
-The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at <https://osf.io/k63b9/>.
-The pre-registration for the study can be found at <https://osf.io/48jsv> .
-We inadvertently did not create a formal pre-registration using the OSF registries tool, but this document contains the same information and is time stamped prior to the start of data collection.
-<!-- Students failed
+The stimuli, experimental code, and data and analysis scripts can be
+found on the Open Science Framework at <https://osf.io/k63b9/>. The
+pre-registration for the study can be found at <https://osf.io/48jsv> .
+We inadvertently did not create a formal pre-registration using the OSF
+registries tool, but this document contains the same information and is
+time stamped prior to the start of data collection. <!-- Students failed
 to pre-register this one and I missed it. There's an unofficial
@@
 
-Our pre-registered target was 50 participants.
-51 participants completed the first day of the experiment and 48 completed the second day.
-Following Manns et al., we excluded 3 participants due to perfect performance on the recognition memory test because this prevents comparison of gaze data for recalled vs.
-non-recalled images.
-Our final sample size was 45 participants.
+Our pre-registered target was 50 participants. 51 participants completed
+the first day of the experiment and 48 completed the second day.
+Following Manns et al., we excluded 3 participants due to perfect
+performance on the recognition memory test because this prevents
+comparison of gaze data for recalled vs. non-recalled images. Our final
+sample size was 45 participants.
 
@@
 
-Stimuli consisted of color photographs of common objects (e.g.
-an apple, a key, etc.).
-We selected 96 unique images from the stimulus set provided by @konkle2010conceptual, which contains multiple objects from hundreds of unique categories.
-We selected images in 48 pairs from the same object category such that each critical object had a corresponding foil object during the recognition test (e.g.
-one red apple and one green apple).
-All images are of a single object on a white background.
-<!-- There are 98 unique images on OSF.
-One pair (lighter and lighter-alternate) isn't used.
--->
-
-Stimulus sets were created to present participants with 24 presentation trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
-Each presentation trial screen presented two identical images (e.g.
-red apple and red apple).
-The test trial screens presented each of the previously-seen ("old") images paired with a new image (e.g.
-red apple and bicycle key).
-The recognition trial screens presented a single image that was either from the original set of 24 (seen twice across the first two phases) or was a corresponding foil for the original set (e.g.
-red apple or green apple).
-Thus, each participant was exposed to 72 unique images over the course of the experiment (the 24 foils for the "new" images in the test phase are never seen).
-Two full stimulus lists were created to counterbalance images across participants; the images that composed the "old" set for one list made up the "new" set for the list.
-The experimental design is visually depicted in Figure \@ref(fig:E3-design-schematic).
+Stimuli consisted of color photographs of common objects (e.g. an apple,
+a key, etc.). We selected 96 unique images from the stimulus set
+provided by @konkle2010conceptual, which contains multiple objects from
+hundreds of unique categories. We selected images in 48 pairs from the
+same object category such that each critical object had a corresponding
+foil object during the recognition test (e.g. one red apple and one
+green apple). All images are of a single object on a white background.
+<!-- There are 98 unique images on OSF. One pair (lighter and lighter-alternate) isn't used. -->
+
+Stimulus sets were created to present participants with 24 presentation
+trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
+Each presentation trial screen presented two identical images (e.g. red
+apple and red apple). The test trial screens presented each of the
+previously-seen ("old") images paired with a new image (e.g. red apple
+and bicycle key). The recognition trial screens presented a single image
+that was either from the original set of 24 (seen twice across the first
+two phases) or was a corresponding foil for the original set (e.g. red
+apple or green apple). Thus, each participant was exposed to 72 unique
+images over the course of the experiment (the 24 foils for the "new"
+images in the test phase are never seen). Two full stimulus lists were
+created to counterbalance images across participants; the images that
+composed the "old" set for one list made up the "new" set for the list.
+The experimental design is visually depicted in
+Figure \@ref(fig:E3-design-schematic).
 
@@
 
-The experiment was administered over the course of two consecutive days. The presentation phase and test phase occurred on the first day, while the recognition test occurred on the second day.
-
-During the presentation phase, participants viewed 24 pairs of identical images.
-Each pair was presented for 5 seconds and an interval of 5 seconds elapsed before the next pair was shown.
-The order of the photographs was randomized and different for each participant.
-After completion of the presentation phase, participants were given a 5-minute break during which they could look away from the screen.
-
-After the break, they were prompted to complete the eye-tracking calibration again before beginning the test phase.
-During this phase, participants again viewed 24 pairs of photographs (old and new) with an interstimulus duration of 5 seconds.
-
-Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test.
-Each image was shown on the screen for 1 second, followed by a 1 second interstimulus interval.
-Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing 'y' for yes and 'n' for no.
-After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a "pure guess" to 5 as "very sure." by clicking on the corresponding number on the screen.
-No feedback on their responses was given during the test.
-
-One aspect of the original study that we could not replicate was that we presented all stimuli on a single screen rather than two screens due to the constraints of the online experiment format.
-We had no *a priori* reason to expect this to matter.
+The experiment was administered over the course of two consecutive days.
+The presentation phase and test phase occurred on the first day, while
+the recognition test occurred on the second day.
+
+During the presentation phase, participants viewed 24 pairs of identical
+images. Each pair was presented for 5 seconds and an interval of 5
+seconds elapsed before the next pair was shown. The order of the
+photographs was randomized and different for each participant. After
+completion of the presentation phase, participants were given a 5-minute
+break during which they could look away from the screen.
+
+After the break, they were prompted to complete the eye-tracking
+calibration again before beginning the test phase. During this phase,
+participants again viewed 24 pairs of photographs (old and new) with an
+interstimulus duration of 5 seconds.
+
+Approximately 24 hours after completing the first session, with a leeway
+interval of 12 hours to accommodate busy schedules, participants were
+given the recognition test. Each image was shown on the screen for 1
+second, followed by a 1 second interstimulus interval. Each photograph
+remained on the screen until the participants indicated whether or not
+they had seen it before by pressing 'y' for yes and 'n' for no. After
+they pressed one of the two keys, a prompt on the screen asked them to
+rate their confidence in their answer from 1 as a "pure guess" to 5 as
+"very sure." by clicking on the corresponding number on the screen. No
+feedback on their responses was given during the test.
+
+One aspect of the original study that we could not replicate was that we
+presented all stimuli on a single screen rather than two screens due to
+the constraints of the online experiment format. We had no *a priori*
+reason to expect this to matter.
 
@@
 
-As in @mannsVisualPairedcomparisonTask2000, participants looked more at novel images than previously seen images.
-This effect was consistent for ROIs based on the images and for the coarser ROIs based on two halves of the display.
-A day later, participants were also able to discriminate the images they had seen from foil images they had not seen during the previous session.
-However, there was no evidence that memory performance on day 2 was related to looking time on day 1.
-
-Thus, most of the key findings replicated.
-What should we make of the finding that failed to replicate?
-Notably, the proportion of looks to the novel object on Day 1 (54% or 55%, depending on analysis) was numerically smaller than in the original (59%), potentially decreasing the ability to detect correlations with eye-gaze.
-If so, the question is whether that is due to lower-quality eye-gaze tracking.
-This seems unlikely, because calibration quality did not appear to substantially affect this result (or any of the others).
-Alternative explanation include the well-documented decline effect [replications tend to find smaller effect sizes than the original, @schooler2011unpublished; @open2015estimating; @hartshorne2012tracking] and the common finding that subject accuracy is lower when not testing undergraduates at elite universities [@hartshorne2019meta; @germine2012web].
+As in @mannsVisualPairedcomparisonTask2000, participants looked more at
+novel images than previously seen images. This effect was consistent for
+ROIs based on the images and for the coarser ROIs based on two halves of
+the display. A day later, participants were also able to discriminate
+the images they had seen from foil images they had not seen during the
+previous session. However, there was no evidence that memory performance
+on day 2 was related to looking time on day 1.
+
+Thus, most of the key findings replicated. What should we make of the
+finding that failed to replicate? Notably, the proportion of looks to
+the novel object on Day 1 (54% or 55%, depending on analysis) was
+numerically smaller than in the original (59%), potentially decreasing
+the ability to detect correlations with eye-gaze. If so, the question is
+whether that is due to lower-quality eye-gaze tracking. This seems
+unlikely, because calibration quality did not appear to substantially
+affect this result (or any of the others). Alternative explanation
+include the well-documented decline effect (replications tend to find
+smaller effect sizes than the original) and the common finding that
+subject accuracy is lower when not testing undergraduates at elite
+universities.
 
@@
 
-The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a.
-These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity.
-For example, in a sentence like "Feel the frog with the feather," the phrase "with the feather" could be describing the frog, or it could be describing the instrument that should be used to do the "feeling." When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb's "bias" (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
-Use of the verb's bias should be reflected in a greater proportion of eye-gaze fixations to the animal (e.g., frog) for verbs that are biased toward modifier structures relative to instrument structures and, conversely, a greater proportion of eye-gaze fixations to the instrument (e.g., feather) for verbs that are biased toward instrument structures relative to modifier structures.
+The fourth study was a replication attempt of Experiment 1 in
+@ryskinVerbBiasesAre2017, which was closely modeled on
+@snedekerDevelopingConstraintsParsing2004a. These studies used the
+visual world paradigm to show that listeners use knowledge of the
+co-occurrence statistics of verbs and syntactic structures to resolve
+ambiguity. For example, in a sentence like "Feel the frog with the
+feather," the phrase "with the feather" could be describing the frog, or
+it could be describing the instrument that should be used to do the
+"feeling." When both options (a frog holding a feather and a feather by
+itself) are available in the visual display, listeners rely on the
+verb's "bias" (statistical co-occurrence either in norming or corpora)
+to rapidly choose an action while the sentence is unfolding. .
 
@@
 
-The stimuli, experimental code, and data and original analysis scripts can be found on the Open Science Framework at the following link, <https://osf.io/x3c49/>.
-The pre-registration for the study can be found at <https://osf.io/3v4pg>.
+The stimuli, experimental code, and data and original analysis scripts
+can be found on the Open Science Framework at the following link,
+<https://osf.io/x3c49/>. The pre-registration for the study can be found
+at <https://osf.io/3v4pg>.
 
@@
 
-Fifty-seven participants were paid \$2.50 for their participation --- three fewer than the intended sample of 60, which was not reached due to time constraints, but double the sample in Ryskin et al.
-(2017) Experiment 1.
+Fifty-seven participants were paid \$2.50 for their participation ---
+three fewer than the intended sample of 60, which was not reached due to
+time constraints, but double the sample in Ryskin et al. (2017)
+Experiment 1.
 
@@
 
-The images and audios presented to the participants were the same stimuli used in the original study.
-The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions.
-Two lists of critical trials were made with different verb and instrument combinations (e.g., "rub" could be paired with "panda" and "crayon" in one list and "panda" and "violin" in the second list).
-Within each list, the same verb was presented twice but each time with a different target instrument and animal.
-The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used.
-There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials.
-The list of the 27 verbs used, along with their verb bias norms, can be found in Appendix A of the original study.
+The images and audios presented to the participants were the same
+stimuli used in the original study. The critical trials were divided
+into modifier-biased, instrument-biased, and equibiased conditions, and
+the filler trials did not contain ambiguous instructions. Two lists of
+critical trials were made with different verb and instrument
+combinations (e.g., "rub" could be paired with "panda" and "crayon" in
+one list and "panda" and "violin" in the second list). Within each list,
+the same verb was presented twice but each time with a different target
+instrument and animal. The lists were randomly assigned to the
+participants to make sure the effects were not caused by the properties
+of the animal or instrument images used. There were 54 critical trials
+per list (3 verb conditions x 9 verbs per condition x 2 presentations)
+and 24 filler trials. The list of the 27 verbs used, along with their
+verb bias norms, can be found in Appendix A of the original study.
 
@@
 
-During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure \@ref(fig:E4-example-trial))[^3].
-Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects[^4].
-After the action was completed, the participants were instructed to press the space bar which led to a screen that said "Click Here" in the middle in order to remove bias in the eye and mouse movements from the previous trial.
-The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.
-
-[^3]: In the original study, the pictures appeared one by one on the screen and their names were played as they appeared. We removed this introductory portion of the trial to save time
-
-[^4]: As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking.
-For example, the sentence "locate the camel with the straw" may not involve any clicking but rather only mousing over the camel.
+During a trial, four pictures were displayed (target animal, target
+instrument, distractor animal, distractor instrument), one in each
+corner of the screen, and participants heard an audio prompt that
+contained instructions about the action they needed to act out (e.g.,
+"Rub the butterfly with the crayon"; see
+Figure \@ref(fig:E4-example-trial))[^2]. Using their cursor,
+participants could act out the instructions by clicking on objects and
+moving them or motioning over the objects[^3]. After the action was
+completed, the participants were instructed to press the space bar which
+led to a screen that said "Click Here" in the middle in order to remove
+bias in the eye and mouse movements from the previous trial. The
+experiment only allowed the participants to move on to the next trial
+once the audio was completely done playing and the mouse had been moved
+over at least one object.
+
+[^2]: In the original study, the pictures appeared one by one on the
+    screen and their names were played as they appeared. We removed this
+    introductory portion of the trial to save time
+
+[^3]: As opposed to the original study we recorded mouse movement
+    instead of clicking behavior since not all of the audio prompts
+    required clicking. For example, the sentence "locate the camel with
+    the straw" may not involve any clicking but rather only mousing over
+    the camel.
 
@@
 
-As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier-, instrument-, or equi-).
-For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).
-This pattern was stronger for those who achieved higher calibration accuracy and when quadrant-based ROIs were used compared to image-based ROIs.
+As in @ryskinVerbBiasesAre2017 and
+@snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns
+during sentences with globally ambiguous syntactic interpretations
+differed depending on the bias of the verb (i.e., modifier-,
+instrument-, or equi-). For modifier-biased verbs, participants looked
+more quickly at the target animal and less at the potential instrument
+than for instrument-biased verbs (and equi-biased verbs elicited a gaze
+pattern between these extremes). This pattern was stronger for those who
+achieved higher calibration accuracy and when quadrant-based ROIs were
+used compared to image-based ROIs.
 
@@
 
-The fifth study was a replication attempt of @shimojoGazeBiasBoth2003, which found that human gaze is actively involved in preference formation.
-Separate sets of participants were shown pairs of human faces and asked either to choose which one they found more attractive or which they felt was rounder.
-Prior to making their explicit selection, participants were increasingly likely to be fixating the face they ultimately chose, though this effect was significantly weaker for roundness discrimination.
-
-Note that Shimojo and colleagues compare five conditions, of which we replicate only the two that figure most prominently in their conclusions: the "face-attractiveness-difficult task" and the "face-roundness task".
+The fifth study was a replication attempt of @shimojoGazeBiasBoth2003,
+which found that human gaze is actively involved in preference
+formation. Separate sets of participants were shown pairs of human faces
+and asked either to choose which one they found more attractive or which
+they felt was rounder. Prior to making their explicit selection,
+participants were increasingly likely to be fixating the face they
+ultimately chose, though this effect was significantly weaker for
+roundness discrimination.
+
+Note that Shimojo and colleagues compare five conditions, of which we
+replicate only the two that figure most prominently in their
+conclusions: the "face-attractiveness-difficult task" and the
+"face-roundness task".
 
@@
 
-All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at <https://osf.io/eubsc/>. The study pre-registration is available at <https://osf.io/tv57s>.
+All stimuli, experiment scripts, data, and analysis scripts are
+available on the Open Science Framework at <https://osf.io/eubsc/>. The
+study pre-registration is available at <https://osf.io/tv57s>.
 
@@
 
-Fifty participants for the main task were recruited on Prolific and were paid \$10/hour. <!-- Eight subjects, 4 from the attractiveness task group and 4 from
+Fifty participants for the main task were recruited on Prolific and were
+paid \$10/hour.
+<!-- Eight subjects, 4 from the attractiveness task group and 4 from
 the roundness task group, were excluded for incorrect validations.
@@
 data exclusion, we ended up with 21 participants each for the
-attractiveness task and the roundness task.
-AJ: I can't figure out why these 8 were excluded so I'm adding them back for now--> For one subject (roundess task group), eye gaze data failed to record.<!--This was one of the excluded 8--> We ended up with 25 participants in the attractiveness condition and 24 in the roundness condition.
-The original sample size in Shimojo et al.
-(2003) was 10 participants total.
+attractiveness task and the roundness task. AJ: I can't figure out why these 8 were excluded so I'm adding them back for now-->
+For one subject (roundess task group), eye gaze data failed to
+record.<!--This was one of the excluded 8--> We ended up with 25
+participants in the attractiveness condition and 24 in the roundness
+condition. The original sample size in Shimojo et al. (2003) was 10
+participants total.
 
@@
 
-The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et al.
-were from the Ekman face database and the AR face database).
-These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18.
-Twenty-seven participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
-They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
-Faces were presented one at a time and in a random order for each participant.
-Data from three participants were excluded because their modal response made up more than 50% of their total responses, for a total of 24 participants in the norming.
-
-Following Shimojo et al., 19 face pairs were selected by identifying two faces that 1) had a difference in mean attractiveness ratings that was 0.25 points or lower and 2) matched in gender, race, and age group (young adult, adult, or older adult).
-
-Participants were presented with each of the 19 face pairs; task condition was manipulated between subjects, such that half of participants made judgments about facial attractiveness and the other half made judgments about facial shape.
+The faces in our replication were selected from a set of 1,000 faces
+within the Flickr-Faces-HQ Dataset (the face images used in Shimojo et
+al. were from the Ekman face database and the AR face database). These
+images were chosen because the person in each image was looking at the
+camera with a fairly neutral facial expression and appeared to be over
+the age of 18. Twenty-seven participants were recruited on Prolific to
+participate in stimulus norming (for attractiveness). They each viewed
+all 172 faces and were asked to rate them on a scale from 1 (less
+attractive) to 7 (more attractive) using a slider. Faces were presented
+one at a time and in a random order for each participant. Data from
+three participants were excluded because their modal response made up
+more than 50% of their total responses, for a total of 24 participants
+in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by identifying two
+faces that 1) had a difference in mean attractiveness ratings that was
+0.25 points or lower and 2) matched in gender, race, and age group
+(young adult, adult, or older adult).
+
+Participants were presented with each of the 19 face pairs; task
+condition was manipulated between subjects, such that half of
+participants made judgments about facial attractiveness and the other
+half made judgments about facial shape.
 
@@
 
-During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure \@ref(fig:E5-example-trial)).
-In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder.
-They pressed the "a" key on their keyboard to select the face on the left and the "d" key to select the face on the right.
-A fixation cross appeared in the center of the screen between each set of faces.
-Participants were asked to look at this fixation cross in order to reset their gaze in between trials.
-The order of the 19 face pairs was random for each participant.
+During each trial of the main task, two faces were displayed on the two
+halves of the screen, one on the left and one on the right (as in
+Figure \@ref(fig:E5-example-trial)). In the attractiveness task,
+participants were asked to chose the more attractice face in the pair
+and in the shape judgment task participants were asked to pick the face
+that appeared rounder. They pressed the "a" key on their keyboard to
+select the face on the left and the "d" key to select the face on the
+right. A fixation cross appeared in the center of the screen between
+each set of faces. Participants were asked to look at this fixation
+cross in order to reset their gaze in between trials. The order of the
+19 face pairs was random for each participant.
 
@@
 
-In the original study, a video-based eye tracker was used.
-The eye movements of participants were recorded with a digital camera downsampled to 33.3 Hz, with eye position determined automatically with MediaAnalyzer software.
-In our study, subjects supplied their own cameras, so hardware sampling rate varied.
-However, data was collected at 20 Hz.
-<!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this!
--->
+In the original study, a video-based eye tracker was used. The eye
+movements of participants were recorded with a digital camera
+downsampled to 33.3 Hz, with eye position determined automatically with
+MediaAnalyzer software. In our study, subjects supplied their own
+cameras, so hardware sampling rate varied. However, data was collected
+at 20 Hz.
+<!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this! -->
 
@@
 
-Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the option that they ultimately choose.
-This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
-The gaze patterns remained consistent for participants with better calibration accuracy.
+Qualitatively, the results are similar to those of Shimojo et al., such
+that participants look more at the option that they ultimately choose.
+This gaze bias appears to be stronger for decisions about face
+attractiveness than shape, though this is not supported by the
+statistical analysis approach used in the original paper. The gaze
+patterns remained consistent for participants with better calibration
+accuracy.
 
@@
 
-We conducted five attempted replication studies using different experimental paradigms from across the cognitive sciences.
-All were successfully implemented in `jsPsych` using the `webgazer` plugin, though replication was not uniform.
-
-Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with five to six ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
-Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [e.g.
-@james2023language].
-A previous conceptual replication of this paradigm using webcam-based eye-tracking [@prystauka2023online] was successful but used a four-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
-It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
-The primary limitation is likely to be the size of the ROIs.
-
-Experiment 2 used the four quadrants of the participant's screen as ROIs.
-As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, participants spontaneously looked to blank ROIs which previously contained to-be-remembered pictures.
-These results appeared to be robust to calibration quality.
-An additional manipulation, instructing participants to keep gaze fixed on a central point, was not successful.
-One possibility is that participants are less motivated to follow such instructions when an experimenter is not present in the same room with them.
-It may be possible to improve performance by emphasizing that this is an important aspect of the experiment or by providing additional training/practice in keeping the eyes still on one particular point.
-
-Experiment 3 used two large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask2000.
-However, the subtler relationship between gaze duration and recognition memory on Day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
-Calibration quality did not appear to impact this relationship.
-More work is needed to understand whether delay manipulations can be practically combined with webcam eye-tracking.
-
-Experiment 4 used the four quadrants of the participant's screen as ROIs.
-As in @ryskinVerbBiasesAre2017, listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input ("Rub the frog with the mitten").
-Across multiple time windows, participants looked more at potential instruments (mitten), when the verb (rub) was one that was more likely to be followed by a prepositional phrase describing an instrument with which to perform the action , as opposed to describing the recipient of the action (frog).
-Despite the qualitative replication of past findings, the overall rates of looks to various objects were much lower than in an in-lab study using infrared eye-tracking.
-This reduction may be related to measurement quality: effect sizes were greater for participants with higher calibration accuracy.
-Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect.
-Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to `webgazer` that are made within the `jsPsych` plug-in successfully address the issues noted by @dijkgraaf2017predicting and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.
-
-Experiment 5, similar to Experiment 3, used two large ROIs (or halves of the display).
-As in @shimojoGazeBiasBoth2003 and in the recent webcam-based replication by @yang2021webcam, we saw that participants looked more at the face or shape that they ultimately chose during a judgment task.
-This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this effect was not statistically significant.
-
-The relatively large number of statistical comparisons means that we would not expect everything to come out significant even in the best-case scenario.
-Nonetheless, there appears to be some systematicity in the patterns of significant replication.
-Most of the failures to replicate seem to be due to small ROIs (e.g., Exp.
-1) or effects that were small to begin with (e.g., Exp.
-3) or involved insensitive statistical tests (e.g., Exp.
-5).
-
-In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.
-
-This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research.
-In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries [@henrich2010weirdest; @linxen2021weird; @de2023psychology; @rad2018toward], webcam eye-tracking can reach a much more diverse population, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops and tablets).
-While webcam eyetracking cannot by itself eliminate all demographic biases, some of which are in any case baked in by history [@henrich2020weirdest], it can help to reduce them, at least for studies amenable to the paradigm.
+We conducted five attempted replication studies using different
+experimental paradigms from across the cognitive sciences. All were
+successfully implemented in `jsPsych` using the `webgazer` plugin,
+though replication was not uniform.
+
+Experiment 1 had the smallest ROIs due to the use of an integrated
+visual scene with five to six ROIs of varying size per scene, as opposed
+to ROIs corresponding to display halves or quadrants. Both attempts to
+replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful,
+despite the success of previous in-lab replications using infrared
+eye-tracking [e.g. @james2023language]. A previous conceptual
+replication of this paradigm using webcam-based eye-tracking
+[@prystauka2023online] was successful but used a four-quadrant visual
+world paradigm, rather than the "naturalistic" scenes used in the
+original study and in the current replication attempts. It is worth
+noting that removing variability related to participant environments (by
+conducting the webcam-tracking study in the lab) did not appear to
+improve the sensitivity of the paradigm. The primary limitation is
+likely to be the size of the ROIs.
+
+Experiment 2 used the four quadrants of the participant's screen as
+ROIs. As in @johanssonLookHereEye2014 and
+@spiveyOculomotorMechanismsActivated2001, participants spontaneously
+looked to blank ROIs which previously contained to-be-remembered
+pictures. These results appeared to be robust to calibration quality. An
+additional manipulation, instructing participants to keep gaze fixed on
+a central point, was not successful. One possibility is that
+participants are less motivated to follow such instructions when an
+experimenter is not present in the same room with them. It may be
+possible to improve performance by emphasizing that this is an important
+aspect of the experiment or by providing additional training/practice in
+keeping the eyes still on one particular point.
+
+Experiment 3 used two large ROIs (halves of the display in one analysis)
+and successfully replicated the novelty preference in terms of gaze
+duration shown in @mannsVisualPairedcomparisonTask2000. However, the
+subtler relationship between gaze duration and recognition memory on Day
+2 was not replicated, despite the fact that participants were able to
+discriminate pictures they had seen from those they hadn't seen during
+that delayed test. Calibration quality did not appear to impact this
+relationship. More work is needed to understand whether delay
+manipulations can be practically combined with webcam eye-tracking.
+
+Experiment 4 used the four quadrants of the participant's screen as
+ROIs. As in @ryskinVerbBiasesAre2017, listeners used knowledge of the
+co-occurrence statistics of verbs and syntactic structures to resolve
+ambiguous linguistic input ("Rub the frog with the mitten"). Across
+multiple time windows, participants looked more at potential instruments
+(mitten), when the verb (rub) was one that was more likely to be
+followed by a prepositional phrase describing an instrument with which
+to perform the action , as opposed to describing the recipient of the
+action (frog). Despite the qualitative replication of past findings, the
+overall rates of looks to various objects were much lower than in an
+in-lab study using infrared eye-tracking. This reduction may be related
+to measurement quality: effect sizes were greater for participants with
+higher calibration accuracy. Using the full quadrants as ROIs, rather
+than bounding boxes around the four images, also appeared to improve the
+measurement of the effect. Crucially, there was no evidence of a delay
+in the onset of effects relative to in-lab work, indicating that the
+modifications to `webgazer` that are made within the `jsPsych` plug-in
+successfully address the issues noted by @dijkgraaf2017predicting and
+suggesting that this methodology can be fruitfully used to investigate
+research questions related to the timecourse of processing.
+
+Experiment 5, similar to Experiment 3, used two large ROIs (or halves of
+the display). As in @shimojoGazeBiasBoth2003 and in the recent
+webcam-based replication by @yang2021webcam, we saw that participants
+looked more at the face or shape that they ultimately chose during a
+judgment task. This gaze bias appears to be stronger for decisions about
+face attractiveness than shape, though this effect was not statistically
+significant.
+
+The relatively large number of statistical comparisons means that we
+would not expect everything to come out significant even in the
+best-case scenario. Nonetheless, there appears to be some systematicity
+in the patterns of significant replication. Most of the failures to
+replicate seem to be due to small ROIs (e.g., Exp. 1) or effects that
+were small to begin with (e.g., Exp. 3) or involved insensitive
+statistical tests (e.g., Exp. 5).
+
+In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to
+conduct a variety of cognitive science experiments on the web, provided
+the limitations of the methodology are carefully considered.
 
@@
 
-The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.
-
-First, it appears that current technology is sufficient for studies with relatively large ROIs of half or a quarter of the screen.
-While this encompasses a large number of common paradigms, it does not cover all of them, even within the Visual World Paradigm.
-It is possible that even with current technology reasonable sensitivity could be achieved with slightly smaller ROIs, but it will require more systematic investigation to determine what exactly is feasible.
-Likewise, improving the technology may result in better precision.
-However, we note that anecdotally, humans -- who have been shaped by evolution to be exquisitely atuned to eyegaze -- have difficulty determining direction with more precision than quadrants.
-(This observation is based on the experience of many developmental psychology labs that used human coders to identify eyegaze direction frame-by-frame in videos of research subjects' faces.)
-
-Note also that while ROIs the size of quadrants are feasible, good calibration is important.
-Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 50% validation accuracy.
-While stricter thresholds may decrease noise, they come at a cost.
-In preliminary analysis, we found that a threshold of 75% somewhat increased effect size in Exp.
-4, but at the cost of reducing the sample size from 35 to 19.
-However, it could be helpful to more systematically investigate the optimal threshold and whether this varies by size of ROI.
-
-There are a number of other interventions that might increase precision and should be investigated.
-For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise.
-It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback.
-Similarly, it may be profitable to systematically study the parameters of eyegaze validation, for instance the number of validation points and the maximum distance allowed between gaze and target (set to 200px in the present study).
-These and other options should be investigated in order to determine how much they might improve precision.
-
-Second, researchers need to take care with timing accuracy.
-Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically.
-Failure to synchronize can result in substantial inaccuracies [@slim2022moving].
-As indicated by the current work, the current jsPsych implementation of WebGazer.js has timing synchronization sufficient for many studies.
-We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (<https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711>), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
-
-Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background [see, for instance, @yuksel2023investigation].
-We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.
+The findings above suggest a few lessons for researchers wishing to
+conduct eyetracking studies with a Webcam, as well as highlighting a few
+important methodological questions that need to be addressed going
+forward.
+
+First, it appears that current technology is sufficient for studies with
+relatively large ROIs of half or a quarter of the screen. While this
+encompasses a large number of common paradigms, it does not cover all of
+them, even within the Visual World Paradigm. It is possible that even
+with current technology reasonable sensitivity could be achieved with
+slightly smaller ROIs, but it will require more systematic investigation
+to determine what exactly is feasible. Likewise, improving the
+technology may result in better precision. However, we note that
+anecdotally, humans -- who have been shaped by evolution to be
+exquisitely atuned to eyegaze -- have difficulty determining direction
+with more precision than quadrants. (This observation is based on the
+experience of many developmental psychology labs that used human coders
+to identify eyegaze direction frame-by-frame in videos of research
+subjects' faces.)
+
+Note also that while ROIs the size of quadrants are feasible, good
+calibration is important. Based on the results above, researchers using
+such paradigms may want to exclude data from participants with less than
+75% validation accuracy, whereas studies using two halves of the display
+as ROIs may not need to be so conservative.
+
+Second, researchers need to take care with timing accuracy. Running
+studies on modern computers requires synchronizing multiple clocks,
+something that does not happen automatically. Failure to synchronize can
+result in substantial inaccuracies [@slim2022moving]. As indicated by
+the current work, the current jsPsych implementation of WebGazer.js has
+reasonably good timing synchronization. We recommend that future
+researchers use jsPsych or another package with similar documented
+precision.
+
+Third, it is true for any eyetracker that precise data depends on good
+callibration, and good callibration depends in part on lighting and
+background. We suspect that it is possible to give subjects automated
+feedback on how to improve their own calibration, which could result in
+higher-quality data and fewer subject exclusions based on poor
+calibration.
 
@@
     -   Writing - review & editing
--   Undergraduate student authors, listed alphabetically: Haylee Backs, Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison, Laura Hoban, William A.
-Hwang, Claire Iannetta, Kristen M.
-Koenig, Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua Sung, and Lauren Thompson
+-   Undergraduate student authors, listed alphabetically: Haylee Backs,
+    Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa
+    Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena
+    Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison,
+    Laura Hoban, William A. Hwang, Claire Iannetta, Kristen M. Koenig,
+    Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua
+    Sung, and Lauren Thompson
     -   Investigation
@@
 
-Funding for data collection was provided by the Vassar College Department of Cognitive Science (JdL). Partial funding for JKH's contributions was provided by NSF2436092.
+Funding for data collection was provided by the Vassar College
+Department of Cognitive Science (JdL). Partial funding for JKH's
+contributions was provided by NSF2436092.
 
@@
 
+# Ethics statement
+
+The remote experiments (1a, 2-5) were conducted with approval by the
+Vassar College Institutional Review Board. The laboratory experiment
+(1b) was conducted with approval by the Boston College Institutional
+Review Board.
+
+\newpage
+
 # Competing interests
@@
 
-All data and analysis code underlying this paper can be found in the Github repository: <https://github.com/jodeleeuw/219-2021-eyetracking-analysis>.
-Study materials and pre-registrations for each experiment are available on Open Science Framework:
+All data and analysis code underlying this paper can be found in the
+Github repository:
+<https://github.com/jodeleeuw/219-2021-eyetracking-analysis>. Study
+materials and pre-registrations for each experiment are available on
+Open Science Framework:
 
@@
 
-1.  **Example trial from Experiment 1.** Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.
-
-2.  **Calibration and validation point locations for Experiment 1.** Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.
-
-3.
-**Calibration scores plotted against the verb effect on first fixations.** This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.
-
-4.
-**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; James et al.
-2023) are contrasted with the current results (Panel B).
-The vertical line marks the mean noun onset time across trials and conditions.
-
-5.
-**Calibration scores in Exp.
-1b, plotted against the verb effect** This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.
-
-6.
-**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from our web-based study (Panel A; Experiment 1a) are contrasted with the current results (Panel B).
-The vertical line marks the mean noun onset time across trials and conditions.
+1.  **Example trial from Experiment 1.** Participants would hear a
+    sentence (e.g., "The boy will eat the cake") and respond according
+    to whether the sentence matched the picture.
+
+2.  **Calibration and validation point locations for Experiment 1.**
+    Black points were used for calibration. Red crosses were used for
+    checking the accuracy of the calibration.
+
+3.  **Calibration scores plotted against the verb effect on first
+    fixations.** This was operationalized as the latency of the first
+    target fixation in the non-restricting verb condition minus that in
+    the restricting verb condition.
+
+4.  **Cumulative probability of fixating distractor and target objects
+    across conditions over time, with 0 ms aligned to the verb onset
+    time.** Results from an in-lab study with an eyetracker (Panel A;
+    @james2023language) are contrasted with the current results (Panel
+    B). The vertical line marks the mean noun onset time across trials
+    and conditions.
+
+5.  **Calibration scores in Exp. 1b, plotted against the verb effect**
+    This was operationalized as the latency of the first target fixation
+    in the non-restricting verb condition minus that in the restricting
+    verb condition.
+
+6.  **Cumulative probability of fixating distractor and target objects
+    across conditions over time, with 0 ms aligned to the verb onset
+    time.** Results from our web-based study (Panel A; Experiment 1a)
+    are contrasted with the current results (Panel B). The vertical line
+    marks the mean noun onset time across trials and conditions.
 
@@
 
-8.
-**Calibration and validation point locations for Experiment 2.** Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.
-In this experiment, all the same locations were used for both calibration and validation.
-
-9.  **Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions in Experiment 2.**
-
-10. **Accuracy and response times during memory retrieval by statement type and viewing condition in Experiment 2.**
-
-11.
-**Calibration scores plotted against gaze bias.** This was operationalized as the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants.
-
-12. **Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.**
+8.  **Calibration and validation point locations for Experiment 2.**
+    Black points were used for calibration. Red crosses were used for
+    checking the accuracy of the calibration. In this experiment, all
+    the same locations were used for both calibration and validation.
+
+9.  **Proportion of eye-gaze to critical quadrant and other three
+    quadrants during memory retrieval in a) fixed and b) free viewing
+    conditions in Experiment 2.**
+
+10. **Accuracy and response times during memory retrieval by statement
+    type and viewing condition in Experiment 2.**
+
+11. **Calibration scores plotted against gaze bias.** This was
+    operationalized as the difference between the proportion of looks to
+    the critical quadrant minus the average proportion of looks to the
+    average of the other three quadrants.
+
+12. **Calibration and validation point locations for Experiment 3. Black
+    points were used for calibration. Red crosses were used for checking
+    the accuracy of the calibration.**
 
@@
 
-14. **Correlation between proportion looks-to-novel calculated using ROIs and using screen halves.**
-
-15.
-**Experiment 3 calibration scores plotted against proportion looks-to-novel using the left-vs.- right halves coding method.** This was operationalized as the proportion of gaze samples to the half of the screen containing the new image out of all gaze samples.
-
-16.
-**Experiment 3 calibration scores plotted against proportion looks-to-novel using the ROI coding method.** This was operationalized as the proportion of gaze samples to the new image out of all gaze samples.
-
-17.
-**The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looks-to-novel and Day 2 memory performance.** Looks-to-novel were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).
-
-18.
-**Calibration and validation point locations for Experiment 4.** Black points were used for calibration.
-Red crosses were used for checking the accuracy of the calibration.
-In this experiment, all the same locations were used for both calibration and validation.
-
-19.
-**An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.”** The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
-
-20. **Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.**
-
-21. **Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.** Error bars reflect bootstrapped 95% CIs over subject means.
-
-22. **Timecourse of eye-gaze to target animal and target instrument by verb bias condition.** Vertical lines indicate average onsets of animal and instrument offset by 200ms.
-
-23. **Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).**
-
-24. **Example participant’s gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.** Magenta points indicate looks that were not categorized into an ROI.
-
-25.
-**Timecourse of eye-gaze to target animal and target instrument by verb bias condition.** Gaze was categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
-Vertical lines indicate average onsets of animal and instrument offset by 200ms.
-
-26. **Calibration and validation point locations for Experiment 5.** Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.
-
-27. **An example of a critical trial from Experiment 5.** Text did not appear on each screen.
-
-28.
-**Primary results from Exp.
-5.** The attractiveness judgment along with the best- fitting sigmoid is shown on the left.
-Results for the roundness judgment are shown on the right, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison.
-
-29. **Correlation between calibration accuracy (x-axis) and proportion of samples fixating target (y-axis) in Exp. 5.**
-
-30.
-**Revised results for Exp.
-5 after removing low-calibration accuracy participants.** *Left*: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid.
-*Right*: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).
+14. **Correlation between proportion looks-to-novel calculated using
+    ROIs and using screen halves.**
+
+15. **Experiment 3 calibration scores plotted against proportion
+    looks-to-novel using the left-vs.- right halves coding method.**
+    This was operationalized as the proportion of gaze samples to the
+    half of the screen containing the new image out of all gaze samples.
+
+16. **Experiment 3 calibration scores plotted against proportion
+    looks-to-novel using the ROI coding method.** This was
+    operationalized as the proportion of gaze samples to the new image
+    out of all gaze samples.
+
+17. **The relation between calibration scores and experimental effect
+    size, defined as the correlation between Day 1 looks-to-novel and
+    Day 2 memory performance.** Looks-to-novel were either coded using
+    the halves method (left panels) or ROI method (right panels); memory
+    performance was measured using confidence ratings (top panels) or
+    reaction time for correct recognition judgments (bottom panels).
+
+18. **Calibration and validation point locations for Experiment 4.**
+    Black points were used for calibration. Red crosses were used for
+    checking the accuracy of the calibration. In this experiment, all
+    the same locations were used for both calibration and validation.
+
+19. **An example of a critical trial from Experiment 4 for the sentence
+    “Rub the butterfly with the crayon.”** The butterfly is the target
+    animal, the panda is the distractor animal, the crayon is the target
+    instrument, and the violin is the distractor instrument.
+
+20. **Proportion of first mouse movements by location and verb bias in
+    the original dataset (Ryskin et al., 2017) and the current data
+    collected online.**
+
+21. **Proportion of target fixations by verb bias in the original
+    dataset (Ryskin et al., 2017) and the current data collected
+    online.** Error bars reflect bootstrapped 95% CIs over subject
+    means.
+
+22. **Timecourse of eye-gaze to target animal and target instrument by
+    verb bias condition.** Vertical lines indicate average onsets of
+    animal and instrument offset by 200ms.
+
+23. **Calibration scores plotted against the verb bias effect (the
+    difference in target animal fixations between modifier and
+    instrument conditions).**
+
+24. **Example participant’s gaze coordinates categorized into ROIs based
+    on a) image bounding boxes and b) screen quadrants.** Magenta points
+    indicate looks that were not categorized into an ROI.
+
+25. **Timecourse of eye-gaze to target animal and target instrument by
+    verb bias condition.** Gaze was categorized based on which quadrant
+    of the screen the coordinates fall in (as opposed to a bounding box
+    around the image). Vertical lines indicate average onsets of animal
+    and instrument offset by 200ms.
+
+26. **Calibration and validation point locations for Experiment 5.**
+    Black points were used for calibration. Red crosses were used for
+    checking the accuracy of the calibration.
+
+27. **An example of a critical trial from Experiment 5.** Text did not
+    appear on each screen.
+
+28. **Primary results from Exp. 5.** The attractiveness judgment along
+    with the best- fitting sigmoid is shown on the left. Results for the
+    roundness judgment are shown on the right, with the best-fitting
+    sigmoid for the attractiveness judgment depicted in a dashed line
+    for comparison.
+
+29. **Correlation between calibration accuracy (x-axis) and proportion
+    of samples fixating target (y-axis) in Exp. 5.**
+
+30. **Revised results for Exp. 5 after removing low-calibration accuracy
+    participants.** *Left*: Eyegaze during attractiveness judgments,
+    along with the best-fitting sigmoid. *Right*: Eyegze during
+    roundness judgments, along with best-fitting sigmoid (best-fitting
+    sigmoid for attractiveness is re-plotted with a dashed line for
+    comparison).

### 2025-03-30 manuscript.Rmd
Josh changes wrapped

@@
 ---
-title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five cognitive science experiments"
+title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five prominent cognitive science experiments"
 shorttitle        : "Webcam eye-tracking paradigms"
+
 author:
@@
     corresponding: yes
-    address: 1600 Grand Ave, Saint Paul, MN 55105, USA
+    address: 1600 Grand Ave, Saint Paul, MN 550105, USA
 
@@
       - Writing - review & editing
-    email: jkhartshorne@mghihp.edu
+    email: joshua.hartshorne@bc.edu
   - name: Haylee Backs
@@
     email: jdeleeuw@vassar.edu
+
 affiliation:
@@
     institution: Cognitive Science Department, Vassar College
+
 abstract: |
-
   Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require.
@@
 1) should be adapted to coarser quadrant or split-half displays.
+
 keywords          : "eye-tracking, online, webcam, jsPsych, cognitive science"
-wordcount         : "13,115"
+wordcount         : "X"
+
 bibliography      : ["references.bib"]
+
 floatsintext      : yes
@@
 draft             : no
+
 documentclass     : "apa6"
@@
 output            : papaja::apa6_pdf
-editor_options: 
-  markdown: 
-    wrap: 72
 ---
@@
 
-# Ethics statement
-
-The remote experiments (1a, 2-5) were conducted with approval by the
-Vassar College Institutional Review Board. The laboratory experiment
-(1b) was conducted with approval by the Boston College Institutional
-Review Board.
-
-\newpage
-
 # Competing interests

### 2025-03-30 group-b/E2-analysis-calibration.Rmd

@@
 library(jsonlite)
+library(readr)
 library(dplyr)
@@
 
+write_csv(calib.by.subj,"output/E2_calib_data_subj.csv") # for survey results analysis
+
 eyetracking.effects.by.subj = read_csv( "output/E2_eye-tracking_data_subj.csv") %>% 
@@
 Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, averaging initial calibration (or re-calibration for participants who repeated calibration) and calibration at the halfway point.
-Calibration scores varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %).
+Calibration scores varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%).
 The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect)).

### 2025-03-30 manuscript.Rmd

@@
 the study.(AJ: I don't think this is true, as there are Ps included that have under 50% on the second round of calibration)-->
+
+Upon finishing calibration, participants were reminded to keep their head still for the remainder of the study.
 
@@
 
+### Survey results
+
+```{r E2-analysis-survey, child='group-b/E2-analysis-survey.Rmd'}
+
+```
+
 ## Discussion
@@
 
+This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research.
+In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries [@henrich2010weirdest; @linxen2021weird; @de2023psychology; @rad2018toward], webcam eye-tracking can reach a much more diverse population, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops and tablets).
+While webcam eyetracking cannot by itself eliminate all demographic biases, some of which are in any case baked in by history [@henrich2020weirdest], it can help to reduce them, at least for studies amenable to the paradigm.
+
 ## Lessons and Questions

### 2025-04-02 manuscript.Rmd
minor changes

@@
 shorttitle        : "Webcam eye-tracking paradigms"
+
 author:
@@
 abstract: |
-
   Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require.
@@
 keywords          : "eye-tracking, online, webcam, jsPsych, cognitive science"
-wordcount         : "13,115"
+wordcount         : "X"
 bibliography      : ["references.bib"]
@@
 
-The use of eye-tracking to study cognition took off when Alfred Yarbus
-used suction cups to affix a mirror system to the sclera of the eye in
-order to monitor eye position during the perception of images
-[@yarbus1967eye]. In one study, participants viewed a painting depicting
-multiple people in a complex interaction inside of a 19th century
-Russian home. Yarbus showed, among other things, that the scan paths and
-locations of fixations were largely dependent on the instructions given
-to participants (e.g., View the picture freely vs. Remember the position
-of the people and objects in the room). In other words, the cognitive
-processing that the individual is engaged in drives the visuo-motor
-system. Since these findings, eye-tracking has become a central method
-in cognitive science research [for reviews, see @hayhoe2005eye,
-@richardsonEyeTrackingResearch2004, @rayner1998eye]. For example, gaze
-location during natural scene perception is used to test theories of
-visual attention [e.g., @henderson2017meaning], and eye-movements during
-auditory language comprehension, using the "visual world paradigm,"
-demonstrated the context-dependent and incremental nature of language
-processing [e.g., @tanenhaus1995].
-
-An important limitation of the eye-tracking methodology is that it has
-typically required costly equipment (eye-trackers can range in price
-from a few thousand dollars to tens of thousands of dollars), particular
-laboratory conditions (a quiet room with consistent indoor lighting
-conditions), and a substantial time investment (e.g., bringing
-participants into a laboratory one at a time). This limits who can
-conduct eye-tracking research -- not all researchers have the necessary
-resources -- and who can participate in eye-tracking research. Most
-eye-tracking study participants are from western, educated,
-industrialized, rich, and democratic [WEIRD; @henrich2010weirdest]
-convenience samples [but see @ryskin2023real], which diminishes the
-generalizability of the findings and the scope of conclusions that can
-be drawn about human cognition. Likewise, the sample sizes for in-lab
-experiments are usually orders of magnitude smaller than what
-statisticians recommend [@nosek2022replicability].
-
-A robust solution to all these problems is online experiments,
-particularly with volunteer citizen scientists as participants
-[@li2024developmental; @hartshorne2019thousand;
-@reinecke2015labinthewild; @gosling2010wired]. Historically, this option
-has not been available for eye-tracking, since few potential subjects
-have expensive eyetrackers at home. In principal, this could be
-circumvented by using so-called "poor-man's" eye-tracking, in which
-researchers videotape the subject's face and code eye position
-frame-by-frame [@snedeker2003using]. Most computers now have
-high-quality built-in cameras, so recording video is straightforward.
-Unfortunately, coding images frame-by-frame is extremely time-intensive,
-making large-sample studies unrealistic. However, in recent years, image
-analysis has improved to the point where this work can be automated with
-reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid;
-@burton2014comparison; @skovsgaard2011evaluation]. Nonetheless,
-webcam-based eyetracking only started to be used regularly in research
-with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a
-webcam-based Javascript plug-in that works in the browser and which can
-be integrated with any Javascript web interface, including `jsPsych`
-[@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla],
-or `lab.js` [@henninger2021lab].
-
-Given the potential game-changing nature of webcam-based eye-tracking, a
-number of research groups have investigated how well it works. Nearly
-all this work has used `Webgazer.js` --- most in combination with
-jsPsych, but some with Gorilla or hand-built integrations. There are two
-potential limitations to webcam-based eye-tracking. First, the spatial
-and temporal resolution is less than what is achievable with an infrared
-system. This is less a limitation of webcams than a limitation of the
-information about eyegaze available in an image of a face. Anecdotally,
-researchers who use poor-man's eyetracking find it difficult to locate
-the gaze to anything more fine-grained than quadrants. Second, testing
-subjects over the Internet involves less control: subjects may be unable
-or unwilling to calibrate equipment, adjust lighting, etc., to the same
-level of precision typical of in-lab studies.
-
-Results to date have been encouraging. @semmelmann2018online found data
-quality was reasonable for fixation location and saccades in fixation,
-smooth pursuit, and free-viewing tasks, though data collected online
-through a crowdsourcing platform was slightly more variable and timing
-was somewhat delayed compared to data collected in the lab. Several
-researchers successfully replicated well-known findings from the
-sentence-processing literature involving predictive looks
-[@degen2021seeing; @prystauka2023online; @vos2022comparing;
-@van2023validation]. @yang2021webcam successfully replicated a
-well-established link between value-based decision-making and eye gaze
-[see also @van2023validation].
-
-While promising, there are some salient limitations. First, many of the
-studies report effects that are smaller or later than what had been
-previously observed in the lab [@slim2022moving; @degen2021seeing;
-@van2023validation]. Importantly, accurate timing on a web browser is
-not trivial [@passell2021cognitive; @de2016psychophysics], and subtle
-programming choices can significantly affect the accuracy of
-`WebGazer.js` timing [@yang2021webcam].[^1] Since most of the prior work
-did not address these timing issues, it is not clear how many of the
-reported lab/web differences would resolve.
-
-[^1]: See also discussion at
-    <https://github.com/jspsych/jsPsych/discussions/1892>
-
-Second, prior work has focused on studies with relatively coarse-grained
-regions of interest [but see @semmelmann2018online], dividing the screen
-either in half or in quadrants. This is particularly salient with
-[@prystauka2023online], which simplified
-@altmannIncrementalInterpretationVerbs1999's design so that regions of
-interest are quadrants rather than the finer-grained ROIs used in the
-original. Certainly, webcam eyetracking will not be as spatially
-fine-grained as an infrared eyetracker, but we do not yet have a good
-sense of the limits.
-
-Finally, the prior work has focused on a relatively limited range of
-methods. Different paradigms have different technical requirements and
-analyze the results differently. As a result, the breadth of utility of
-webcam eye-tracking is unclear.
+The use of eye-tracking to study cognition took off when Alfred Yarbus used suction cups to affix a mirror system to the sclera of the eye in order to monitor eye position during the perception of images [@yarbus1967eye].
+In one study, participants viewed a painting depicting multiple people in a complex interaction inside of a 19th century Russian home.
+Yarbus showed, among other things, that the scan paths and locations of fixations were largely dependent on the instructions given to participants (e.g., View the picture freely vs.
+Remember the position of the people and objects in the room).
+In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system.
+Since these findings, eye-tracking has become a central method in cognitive science research [for reviews see @hayhoe2005eye; @richardsonEyeTrackingResearch2004; @rayner1998eye].
+For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning], and eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].
+
+An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time).
+This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research.
+Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD, @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.
+Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend [@nosek2022replicability].
+
+A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired].
+Historically, this option has not been available for eye-tracking, since few potential subjects have expensive eyetrackers at home.
+In principal, this could be circumvented by using so-called "poor-man's" eye-tracking, in which researchers videotape the subject's face and code eye position frame-by-frame [@snedeker2003using].
+Most computers now have high-quality built-in cameras, so recording video is straightforward.
+Unfortunately, coding images frame-by-frame is extremely time-intensive, making large-sample studies unrealistic.
+However, in recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation].
+Nonetheless, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], `lab.js` [@henninger2021lab], or `PsychoJS` [@peirce2019psychopy2].
+
+Given the potential game-changing nature of webcam-based eye-tracking, a number of research groups have investigated how well it works.
+Nearly all this work has used `Webgazer.js` --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.
+There are two potential limitations to webcam-based eye-tracking.
+First, the spatial and temporal resolution is less than what is achievable with an infrared system.
+This is less a limitation of webcams than a limitation of the information about eyegaze available in an image of a face.
+Anecdotally, researchers who use poor-man's eyetracking find it difficult to locate the gaze to anything more fine-grained than quadrants.
+Second, testing subjects over the Internet involves less control: subjects may be unable or unwilling to calibrate equipment, adjust lighting, etc., to the same level of precision typical of in-lab studies.
+
+Results to date have been encouraging.
+@semmelmann2018online found data quality was reasonable for fixation location and saccades in fixation, smooth pursuit, and free-viewing tasks, though data collected online through a crowdsourcing platform was slightly more variable and timing was somewhat delayed compared to data collected in the lab.
+Several researchers successfully replicated well-known findings from the sentence-processing literature involving predictive looks [@degen2021seeing; @prystauka2023online; @vos2022comparing; @van2023validation].
+@yang2021webcam successfully replicated a well-established link between value-based decision-making and eye gaze [see also @van2023validation].
+
+While promising, there are some salient limitations.
+First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2024webcams; @van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing].
+Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].^[See also discussion at https://github.com/jspsych/jsPsych/discussions/1892] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.
+
+Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online; @bogdan2024investigating], dividing the screen either in half or in quadrants.
+This is particularly salient with [@prystauka2023online], which simplified @altmannIncrementalInterpretationVerbs1999's design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original.
+Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.
+
+Finally, the prior work has focused on a relatively limited range of methods.
+Different paradigms have different technical requirements and analyze the results differently.
+As a result, the breadth of utility of webcam eye-tracking is unclear.
 
@@
 
-In order to broaden the validation of online eye-tracking methodology,
-we set out to reproduce five previously published studies representing a
-variety of questions, topics, and paradigms. The goal was to examine the
-strengths and weaknesses of webcam eye-tracking for common paradigms in
-cognitive science, across a broad range of research areas. Critically,
-we used the implementation known to have the greatest temporal precision
-to date: `jsPsych` and a modification of `Webgazer`.
+In order to broaden the validation of online eye-tracking methodology, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms.
+The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas.
+Critically, we used the only implementation known to have addressed a critical bug in the timing precision of WebGazer.js, specifically the one in `jsPsych`, a package which is known in general for having particularly good timing precision [@de2016psychophysics; @bridges2020timing].
 
@@
 
-Studies with large effect sizes and which are known to replicate are
-ideal targets for further replication; otherwise, it can be difficult to
-distinguish a failure of the method from a failure of the original study
-to replicate. In practice, replications (successful or otherwise) have
-only been reported for a small number of studies, so we ultimately
-included some studies with unknown replicability. We addressed this in
-several ways. First, replicating five very different studies from
-different research traditions decreases our reliance on any one study.
-Second, we include several "sanity check" analyses, such as the
-correlation between calibration accuracy and effect size. If the effect
-is real but there is noise from low-accuracy eye-tracking, this
-correlation should be substantial. Third, for two of the studies, we had
-comparison data collected in-lab either using `jsPsych` or a more
-traditional eyetracker technology, allowing us to directly assess the
-impact of differences in subject population and equipment/setting.
-
-<!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->
-
-<!-- RR: switched ryskin to Snedeker & trueswell 2004 bcs my 75 looked sad -->
-
-We chose five high-impact eye-tracking studies involving adult subjects
-[for an comparison of remote WebGazer and in-lab anticipatory looking
-effects with 18-27 month-old participants, see @steffan2024validation].
-Our goal was to include experiments from a range of topic areas (e.g.,
-memory, decision making, psycholinguistics) and paradigms (two halves of
-the screen, visual world paradigm with four quadrants, visual world
-paradigm with "naturalistic" scenes). As noted above, we had a
-preference for well-established findings that are known to replicate,
-though for sake of diversity this was not always possible. Table
-\@ref(tab:studies-table) provides an overview of the five studies we
-selected.
+Studies with large effect sizes and which are known to replicate are ideal targets for further replication; otherwise, it can be difficult to distinguish a failure of the method from a failure of the original study to replicate.
+In practice, replications (successful or otherwise) have only been reported for a small number of studies, so we ultimately included some studies with unknown replicability.
+We addressed this in several ways.
+First, replicating five very different studies from different research traditions decreases our reliance on any one study.
+Second, we include several "sanity check" analyses, such as the correlation between calibration accuracy and effect size.
+If the effect is real but there is noise from low-accuracy eye-tracking, this correlation should be substantial.
+Third, for two of the studies, we had comparison data collected in-lab either using `jsPsych` or a more traditional eyetracker technology, allowing us to directly assess the impact of differences in subject population and equipment/setting.
+
+We chose five high-impact eye-tracking studies involving adult subjects [for a comparison of remote WebGazer and in-lab anticipatory looking effects with 18-27 month-old participants, see @steffan2024validation].
+Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "naturalistic" scenes).
+As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.
+Table \@ref(tab:studies-table) provides an overview of the five studies we selected.
 
@@
 age or older, fluency in English, and access to a webcam. All
-participants provided informed consent. The online studies were approved
-by the Vassar College Institutional Review Board.
+participants provided informed consent. The online studies were approved by the
+Vassar College Institutional Review Board.
 
 In addition, an in-lab replication was conducted for Experiment 1. 
-Information about the sample is given in the Experiment 1 Method
-sections. This study was approved by the Institutional Review Board at
-Boston College.
+Information about the sample is given in the Experiment 1 Method sections. This study was approved by the Institutional Review Board at Boston College.
 
@@
 2.5x the sample size of the original experiment, following the heuristic
-of Simonsohn [@simonsohn2015]. In Experiment 5, the original sample size
-was so small that we opted to collect 5x the number of participants to
-increase precision. Because of budget and time constraints we were
-unable to replace the data for subjects who were excluded or whose data
-was missing due to technical failures.
+of Simonsohn [@simonsohn2015]. In Experiment 5, the original sample size was so
+small that we opted to collect 5x the number of participants to increase
+precision. Because of budget and time constraints we were unable to
+replace the data for subjects who were excluded or whose data was
+missing due to technical failures.
 
@@
 If accuracy on the validation was too low (fewer than 50% of looks
-landed within a 200 px radius of the validation points), participants
-were given an opportunity to re-start the calibration and validation
-steps. <!--If the second attempt also lead to low validation
+landed within a 200 px radius of the validation points),
+participants were given an opportunity to re-start the calibration and
+validation steps.
+However, even participants with low calibration accuracy were allowed to complete the experiment, because we specifically wanted to study the consequences of low calibration accuracy.<!--If the second attempt also lead to low validation
 accuracy, participants were informed that they could not participate in
@@
 
-These data were collected within the context of an undergraduate
-research methods course. Groups of students (co-authors) designed and
-programmed experiments in jsPsych, pre-registered their planned
-analyses, and collected data through Prolific under the supervision of
-the last author. The OSF repositories associated with these experiments
-are linked in the methods sections of each individual study. Note that
-in the current paper we expand on those pre-registered analyses (e.g.,
-including analyses of the calibration quality). All analysis code
-underlying this paper can be found in the Github repository:
-<https://github.com/jodeleeuw/219-2021-eyetracking-analysis>
+These data were collected within the context of an undergraduate research methods course.
+Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the last author.
+The OSF repositories associated with these experiments are linked in the methods sections of each individual study.
+Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality).
 
@@
 referents in sentence processing. For example, when looking at the
-display in Figure \@ref(fig:E1-example-trial) and listening to a
-sentence like "The boy will eat the...," participants are more likely to
-look at the cake than when they hear "The boy will move the...," in
-which case they tend to look at the train, presumably because cakes are
-edible and trains are not. Semantic information available at the verb is
-used to anticipate upcoming linguistic input.
+display in Figure\ \@ref(fig:E1-example-trial) and listening to a sentence like
+"The boy will eat the...," participants are more likely to look at the cake than 
+when they hear "The boy will move the...," in which case they tend to look at the
+train, presumably because cakes are edible and trains are not. Semantic
+information available at the verb is used to anticipate upcoming
+linguistic input.
 
@@
 ### Participants
-
-Sixty participants (2.5 times the original sample of 24) were paid
-\$2.60 for their participation. For unknown reasons, 2 of the subjects'
-results were not recorded, so in the analysis, we worked with data
-collected from 58 participants.
+Sixty participants (2.5 times the original sample of 24) were paid \$2.60 for their participation. For unknown reasons,
+2 of the subjects' results were not recorded, so in the analysis, we
+worked with data collected from 58 participants.
 
@@
 The visual stimuli were created through Canva and depicted an agent
-accompanied by four to five objects in the scene (see
-Figure \@ref(fig:E1-example-trial)). On critical trials, participants
-heard one of two sentences associated with the scene. In the restrictive
-condition, the sentence (e.g., "The boy will eat the cake") contained a
-verb (e.g., "eat") which restricts the set of possible subsequent
-referents (e.g., to edible things). Only the target object (e.g., the
-cake) was semantically consistent with the verb's meaning. In the
-non-restrictive condition, the sentence (e.g., "The boy will move the
-cake") contained a verb (e.g., "move") which does not restrict the set
-of possible subsequent referents. The target object (e.g., the cake) as
-well as the distractor objects (e.g., the train, the ball, etc.) were
-semantically consistent with the verb's meaning. Both sentences were
-compatible with the scene, such that the correct keyboard response for
-the critical trials was "yes." Filler trials consisted of scenes that
-also contained an agent surrounded by objects as in the critical trials,
-but corresponding sentences named an object that was not present in the
-scene. The correct keyboard response for the filler trials was "no."
+accompanied by four to five objects in the scene (see Figure\ \@ref(fig:E1-example-trial)). On
+critical trials, participants heard one of two sentences associated with
+the scene. In the restrictive condition, the sentence (e.g., "The boy
+will eat the cake") contained a verb (e.g., "eat") which restricts the
+set of possible subsequent referents (e.g., to edible things). Only the
+target object (e.g., the cake) was semantically consistent with the
+verb's meaning. In the non-restrictive condition, the sentence (e.g.,
+"The boy will move the cake") contained a verb (e.g., "move") which does
+not restrict the set of possible subsequent referents. The target object
+(e.g., the cake) as well as the distractor objects (e.g., the train, the
+ball, etc.) were semantically consistent with the verb's meaning. Both
+sentences were compatible with the scene, such that the correct keyboard
+response for the critical trials was "yes." Filler trials consisted of
+scenes that also contained an agent surrounded by objects as in the critical trials, but corresponding sentences named an object that was not present in the scene.
+The correct keyboard response for the filler
+trials was "no."
 
@@
 
-Each participant was presented with 16 critical trials (eight in the
-restrictive condition, eight in the non-restrictive condition) and 16
-fillers for a total of 32 trials. The order of trials and the assignment
-of critical scene to condition was random on a subject-by-subject
-basis.<!-- right?-->
+Each participant was presented with 16 critical trials (eight in
+the restrictive condition, eight in the non-restrictive condition) and
+16 fillers for a total of 32 trials. The order of trials and the
+assignment of critical scene to condition was random on a
+subject-by-subject basis.<!-- right?-->
 
@@
 ```
+
 ## Results
-
 Looks to the objects in the scene were time-locked to the onset of the
 verb, the offset of the verb, onset of the post-verbal determiner, and
-onset of the target noun. ROIs were defined by creating boxes around
-each object in the scene. The size of each box was determined by taking
-the height and width of the given object and adding 20 pixels of
-padding. Each scene contained an agent region, a target region, and
-three or four distractor regions.
+onset of the target noun.
+ROIs were defined by creating boxes around each object in the scene.
+The size of each box was determined by taking the height and width of the given object and adding 20 pixels of padding.
+Each scene contained an agent region, a target region, and three or four distractor regions.
 
@@
 ## Discussion
-
-Across three different tests of the hypothesis that listeners will use
-verb semantics to anticipate the upcoming referent, we found results
-that were numerically consistent with the hypothesis but not
-statistically significant. This is unlikely to be because the original
-effect is unreliable. Indeed, one of us had successfully replicated it
-previously using traditional methods [@james2023language].
-
-An eyeball comparison to published data
-[@altmannIncrementalInterpretationVerbs1999, @james2023language]
-suggests that looks to the objects in the scene (relative to background
-or off-screen looks) were depressed across conditions and objects. After
-eliminating participants with validation accuracy under 50% and/or 10%
-or fewer fixations to any ROIs, we were left with only 22 of the
-original 60 participants. Either of these facts could have resulted in
-low power to detect effects. Given that nearly two-thirds of
-participants had poor data quality, we ran a follow-up webcam study in a
-lab setting order to test whether the failure to replicate was due to
-using a remote sample or to the technology itself.
+Across three different tests of the hypothesis that listeners will use verb semantics to anticipate the upcoming referent, we found results that were numerically consistent with the hypothesis but not statistically significant.
+This is unlikely to be because the original effect is unreliable.
+Indeed, one of us had successfully replicated it previously using traditional methods [@james2023language].
+
+An eyeball comparison to published data [@altmannIncrementalInterpretationVerbs1999, @james2023language] suggests that looks to the objects in the scene (relative to background or off-screen looks) were depressed across conditions and objects.
+After eliminating participants with validation accuracy under 50% and/or 10% or fewer fixations to any ROIs, we were left with only 22 of the original 60 participants.
+Either of these facts could have resulted in low power to detect effects.
+Given that nearly two-thirds of participants had poor data quality, we ran a follow-up webcam study in a lab setting order to test whether the failure to replicate was due to using a remote sample or to the technology itself.
 
 # Experiment 1b
-
-Experiment 1b tested whether the failure to replicate significant
-condition effects in Experiment 1a was due to features of conducting the
-study remotely (i.e. varied experimental settings and apparatuses, lower
-compliance) rather than webcam-based eye-tracking or `webgazer` *per
-se*. Thus, Experiment 1b took place in a lab setting with undergraduate
-participants but otherwise used the same Method as Experiment 1a.
+Experiment 1b tested whether the failure to replicate significant condition effects in Experiment 1a was due to features of conducting the study remotely (i.e.
+varied experimental settings and apparatuses, lower compliance) rather than webcam-based eye-tracking or `webgazer` _per se_.
+Thus, Experiment 1b took place in a lab setting with undergraduate participants but otherwise used the same Method as Experiment 1a.
 
@@
 ### Participants
-
-Forty-nine participants completed the study in a lab setting. They were
-recruited via the Boston College subject pool. Participants needed to be
-18 years of age or older and native speakers of English.
+Forty-nine participants completed the study in a lab setting.
+They were recruited via the Boston College subject pool.
+Participants needed to be 18 years of age or older and native speakers of English.
 
 ### Materials and Design
-
 Materials were identical to those in Experiment 1a.
@@
 ### Procedure
-
-After being greeted by the experimenter and completing the informed
-consent form, participants followed on-screen prompts to complete the
-study, including calibration, as described in the Experiment 1a
-Procedure.
+After being greeted by the experimenter and completing the informed consent form, participants followed on-screen prompts to complete the study, including calibration, as described in the Experiment 1a Procedure.
 
 ### Apparatus
-
-Subjects were tested on a MacIntosh laptop using the built-in Webcam.
-The study was run in Chrome using the same code as Exp. 1a.
+Subjects were tested on a MacIntosh laptop using the built-in Webcam. The study was run in Chrome using the same code as Exp. 1a.
 
 ## Results
-
 ```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
@@
 ## Discussion
-
-Overall, the results of Experiment 1 paint a sobering picture of
-web-based eye-tracking. In Experiment 1a, results from the remote sample
-were in the expected direction but effects were smaller and delayed
-relative to previous work and failed to reach statistical significance.
-This was not due to vagaries of remote samples or working with a more
-diverse subject population: results from the in-lab study were, if
-anything, worse. Nor does our failure to replicate seem to be driven by
-subjects with poor calibration; effect sizes were not correlated with
-calibration success, and restricting analyses to subjects with good
-calibration scores only helped in one of the experiments and in only one
-of the three critical analyses.
-
-Taken together, the instability of these effects might suggest that this
-paradigm is not well-suited for webcam-based eye-tracking. Notably, the
-ROIs were tightly drawn around the five to six objects in each scene
-(drawing larger ROIs in these scenes would have led to overlapping
-objects) and thus, analyses were unforgiving of inaccurate calibration.
-Further evidence comes from a recent `webgazer` study that successfully
-replicated the original results using modified stimuli consisting of
-only four objects, each in separate quadrants, allowing for larger, more
-distinct ROIs [@prystauka2023online].
+Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking.
+In Experiment 1a, results from the remote sample were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance.
+This was not due to vagaries of remote samples or working with a more diverse subject population: results from the in-lab study were, if anything, worse.
+Nor does our failure to replicate seem to be driven by subjects with poor calibration; effect sizes were not correlated with calibration success, and restricting analyses to subjects with good calibration scores only helped in one of the experiments and in only one of the three critical analyses.
+
+Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking.
+Notably, the ROIs were tightly drawn around the five to six objects in each scene (drawing larger ROIs in these scenes would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration.
+Further evidence comes from a recent `webgazer` study that successfully replicated the original results using modified stimuli consisting of only four objects, each in separate quadrants, allowing for larger, more distinct ROIs [@prystauka2023online].
 
@@
 
-Sixty participants were paid for their participation (once again, 2.5x
-larger than the original sample size of 24). Data from one participant
-were not properly recorded due to unknown technical issues, so data from
-59 participants were included in all analyses to follow.
+Sixty participants were paid for their participation (once again, 2.5x larger than the original sample size of 24). 
+Data from one participant were not properly
+recorded due to unknown technical issues, so data from 59 participants
+were included in all analyses to follow.
 
@@
 The experiment consisted of two blocks each composed of an encoding
-phase and a recall phase. The two blocks differed by whether the recall
-phase was in the free-viewing or fixed-viewing condition, as described
-in the Procedure. Participants were randomly assigned to see the
-fixed-viewing or free-viewing block first. During each encoding phase,
-participants saw a grid indicating the four quadrants of the screen.
-Each quadrant contained six cartoon images of items belonging to the
-same category. The four categories were humanoids, household objects,
-animals, and methods of transportation (see
-Figure \@ref(fig:E2-example-trial)). Different images were used in each
-block; there were 48 unique images total across the experiment.
-
-Each recall phase presented participants with a blank screen with a
-central fixation cross as they listened to true/false statements testing
-their recall of the previous grid. Each statement fell into either an
-interobject or intraobject condition. Interobject statements were those
-that compared two different items in the grid (e.g. "The skeleton is to
-the left of the robot"), while intraobject statements were those that
-asked about the orientation of a single item (e.g. "The bus is facing
-right"). There were 48 total statements in each block, such that each
-object was the subject of both an intraobject and an intraobject
-statement; there were 96 unique statements total across the experiment.
+phase and a recall phase.
+The two blocks differed by whether the recall phase was in the free-viewing or fixed-viewing condition, as described in the Procedure.
+Participants were randomly assigned to see the
+fixed-viewing or free-viewing block first. 
+During each encoding phase, participants saw a
+grid indicating the four quadrants of the screen. Each quadrant
+contained six cartoon images of items belonging to the same category. The four categories were humanoids, household objects, animals, and
+methods of transportation (see Figure\ \@ref(fig:E2-example-trial)). Different images were used in each block; there were 48 unique images total across the experiment.
+
+Each recall phase presented participants with a blank screen with a central fixation cross as they listened to true/false statements testing their recall of the previous grid.
+Each statement fell into either an interobject or intraobject
+condition. Interobject statements were those that compared two different
+items in the grid (e.g. "The skeleton is to the left of the robot"),
+while intraobject statements were those that asked about the orientation
+of a single item (e.g. "The bus is facing right"). There were 48 total
+statements in each block, such that each object was the subject of both an intraobject and an intraobject statement; there were 96 unique statements total across the experiment.
 
@@
 
-Participants received instructions that included an example grid and an
-explicit request that they not use any tools to help them during
-encoding. Participants then began their first encoding phase. Each of
-the four quadrants was presented one at a time. First, a list of the
-items in the quadrant was shown, then the pictures of items were
-displayed in the quadrant. For each item, participants used their arrow
-keys to indicate whether the object was facing left or right. After the
-participant identified the direction of each item, they would have an
-additional 30 seconds to encode the name and orientation of each item in
-the quadrant. Finally, after all four quadrants were presented,
-participants were shown the full grid of 24 items and had 60 seconds to
-further encode the name and orientation of each item.
-
-Participants then entered the first recall phase, in which they listened
-to the 48 statements and responded by pressing the 'F' key for false
-statements and 'T' for true ones. While listening to these statements,
-in the free-viewing block, participants saw a blank screen and were
-allowed to freely gaze around the screen. During the fixed-viewing
-block, participants were asked to fixate a small cross in the center of
-the screen throughout the recall phase. In both cases, the mouse was
+Participants received instructions that included an example grid and an explicit request that they not use any tools to help them during encoding.
+Participants then began their first encoding phase.
+Each of the four quadrants was presented one at a time.
+First, a list of
+the items in the quadrant was shown, then the pictures of items were displayed in the quadrant. 
+For each item, participants used their arrow keys to indicate whether the object was facing left or right. After the participant identified the direction of each
+item, they would have an additional 30 seconds to encode the name and
+orientation of each item in the quadrant. Finally, after all four quadrants
+were presented, participants were shown the full grid of
+24 items and had 60 seconds to further encode the name and orientation
+of each item.
+
+Participants then entered the first recall phase, in which they listened to the 48 statements and
+responded by pressing the 'F' key for false statements and 'T' for true
+ones. While listening to these statements, in
+the free-viewing block, participants saw a blank screen and were allowed
+to freely gaze around the screen. During the fixed-viewing block,
+participants were asked to fixate a small cross in the center of the
+screen throughout the recall phase. In both cases, the mouse was
 obscured from the screen.
 
-Participants then proceded to the second encoding and recall phases as
-described above. After completing both encoding-recall blocks,
-participants were asked to answer a few survey questions (such as
-whether they wore glasses or encountered any distractions).
+Participants then proceeded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to
+answer a few survey questions (such as whether they wore glasses or
+encountered any distractions).
 
@@
 
-We replicated the key eyetracking result: As in
-@johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001,
-during memory retrieval, learners spontaneously look to blank screen
-locations where pictures were located during encoding, suggesting that
-visuospatial information is integrated into the memory for objects.
-Interestingly, we did not replicate the behavior result: a memory
-benefit, in terms of speed, of spatial reinstatement via gaze position
-during retrieval of the picture. For researchers interested in that
-effect, this is an issue to be followed up on. However, it is not
-strictly relevant for our evaluation of gaze tracking online.
+We replicated the key eyetracking result: As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, during memory retrieval, learners spontaneously look to blank screen locations where pictures were located
+during encoding, suggesting that visuospatial information is integrated into the memory
+for objects.
+Interestingly, we did not replicate the behavior result: a memory benefit, in terms of speed, of spatial reinstatement via gaze position during retrieval of the picture.
+For researchers interested in that effect, this is an issue to be followed up on.
+However, it is not strictly relevant for our evaluation of gaze tracking online.
 
@@
 
-The third study was a partial replication attempt of the "looking group"
-condition of @mannsVisualPairedcomparisonTask2000 (we did not replicate
-their priming condition). This experiment used the visual
+The third study was a partial replication attempt of the "looking group" condition of
+@mannsVisualPairedcomparisonTask2000 (we did not replicate their priming condition). This experiment used the visual
 paired-comparison, which involves presenting a previously-viewed image
@@
 The stimuli, experimental code, and data and analysis scripts can be
-found on the Open Science Framework at <https://osf.io/k63b9/>. The
-pre-registration for the study can be found at <https://osf.io/48jsv> .
-We inadvertently did not create a formal pre-registration using the OSF
+found on the Open Science Framework at <https://osf.io/k63b9/>.
+The pre-registration for the study can be
+found at <https://osf.io/48jsv> . We
+inadvertently did not create a formal pre-registration using the OSF
 registries tool, but this document contains the same information and is
@@
 
-Stimuli consisted of color photographs of common objects (e.g. an apple,
-a key, etc.). We selected 96 unique images from the stimulus set
-provided by @konkle2010conceptual, which contains multiple objects from
-hundreds of unique categories. We selected images in 48 pairs from the
-same object category such that each critical object had a corresponding
-foil object during the recognition test (e.g. one red apple and one
-green apple). All images are of a single object on a white background.
-<!-- There are 98 unique images on OSF. One pair (lighter and lighter-alternate) isn't used. -->
-
-Stimulus sets were created to present participants with 24 presentation
-trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
-Each presentation trial screen presented two identical images (e.g. red
-apple and red apple). The test trial screens presented each of the
-previously-seen ("old") images paired with a new image (e.g. red apple
-and bicycle key). The recognition trial screens presented a single image
-that was either from the original set of 24 (seen twice across the first
-two phases) or was a corresponding foil for the original set (e.g. red
-apple or green apple). Thus, each participant was exposed to 72 unique
-images over the course of the experiment (the 24 foils for the "new"
-images in the test phase are never seen). Two full stimulus lists were
-created to counterbalance images across participants; the images that
-composed the "old" set for one list made up the "new" set for the list.
-The experimental design is visually depicted in
-Figure \@ref(fig:E3-design-schematic).
+Stimuli consisted of color photographs of common objects (e.g.
+an apple, a key, etc.).
+We selected 96 unique images from the stimulus set provided by @konkle2010conceptual, which contains multiple objects from hundreds of unique categories.
+We selected images in 48 pairs from the same object category such that each critical object had a corresponding foil object during the recognition test (e.g.
+one red apple and one green apple).
+All images are of a single object on a white background.
+<!-- There are 98 unique images on OSF.
+One pair (lighter and lighter-alternate) isn't used.
+-->
+
+Stimulus sets were created to present participants with 24 presentation trials and 24 test trials on Day 1, and 48 recognition trials on Day 2.
+Each presentation trial screen presented two identical images (e.g.
+red apple and red apple).
+The test trial screens presented each of the previously-seen ("old") images paired with a new image (e.g.
+red apple and bicycle key).
+The recognition trial screens presented a single image that was either from the original set of 24 (seen twice across the first two phases) or was a corresponding foil for the original set (e.g.
+red apple or green apple).
+Thus, each participant was exposed to 72 unique images over the course of the experiment (the 24 foils for the "new" images in the test phase are never seen).
+Two full stimulus lists were created to counterbalance images across participants; the images that composed the "old" set for one list made up the "new" set for the list.
+The experimental design is visually depicted in Figure\ \@ref(fig:E3-design-schematic).
 
@@
 
-The experiment was administered over the course of two consecutive days.
-The presentation phase and test phase occurred on the first day, while
-the recognition test occurred on the second day.
+The experiment was administered over the course of two
+consecutive days. The presentation phase and test phase occurred on
+the first day, while the recognition test occurred on the second day.
 
 During the presentation phase, participants viewed 24 pairs of identical
-images. Each pair was presented for 5 seconds and an interval of 5
-seconds elapsed before the next pair was shown. The order of the
-photographs was randomized and different for each participant. After
-completion of the presentation phase, participants were given a 5-minute
-break during which they could look away from the screen.
+images. Each pair was presented for
+5 seconds and an interval of 5 seconds elapsed before the next pair was
+shown. The order of the photographs was randomized and different for
+each participant. After completion of the presentation phase,
+participants were given a 5-minute break during which they could look
+away from the screen.
 
@@
 calibration again before beginning the test phase. During this phase,
-participants again viewed 24 pairs of photographs (old and new) with an
-interstimulus duration of 5 seconds.
+participants again viewed 24 pairs of photographs (old and new) with an interstimulus
+duration of 5 seconds.
 
@@
 interval of 12 hours to accommodate busy schedules, participants were
-given the recognition test. Each image was shown on the screen for 1
-second, followed by a 1 second interstimulus interval. Each photograph
-remained on the screen until the participants indicated whether or not
-they had seen it before by pressing 'y' for yes and 'n' for no. After
-they pressed one of the two keys, a prompt on the screen asked them to
-rate their confidence in their answer from 1 as a "pure guess" to 5 as
-"very sure." by clicking on the corresponding number on the screen. No
-feedback on their responses was given during the test.
-
-One aspect of the original study that we could not replicate was that we
-presented all stimuli on a single screen rather than two screens due to
-the constraints of the online experiment format. We had no *a priori*
-reason to expect this to matter.
+given the recognition test. Each image was shown on the screen for 1 second, followed by a
+1 second interstimulus interval.
+Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing 'y' for yes and 'n' for no.
+After they pressed one of the two keys, a prompt on the screen
+asked them to rate their confidence in their answer from 1 as a "pure
+guess" to 5 as "very sure." by clicking on the corresponding number on
+the screen. No feedback on their responses was given during the test.
+
+One aspect of the original study that we could not replicate was that we presented all stimuli on a single screen rather than two screens due to the constraints of the online experiment format.
+We had no *a priori* reason to expect this to matter.
 
@@
 
-As in @mannsVisualPairedcomparisonTask2000, participants looked more at
-novel images than previously seen images. This effect was consistent for
-ROIs based on the images and for the coarser ROIs based on two halves of
-the display. A day later, participants were also able to discriminate
-the images they had seen from foil images they had not seen during the
-previous session. However, there was no evidence that memory performance
-on day 2 was related to looking time on day 1.
-
-Thus, most of the key findings replicated. What should we make of the
-finding that failed to replicate? Notably, the proportion of looks to
-the novel object on Day 1 (54% or 55%, depending on analysis) was
-numerically smaller than in the original (59%), potentially decreasing
-the ability to detect correlations with eye-gaze. If so, the question is
-whether that is due to lower-quality eye-gaze tracking. This seems
-unlikely, because calibration quality did not appear to substantially
-affect this result (or any of the others). Alternative explanation
-include the well-documented decline effect (replications tend to find
-smaller effect sizes than the original) and the common finding that
-subject accuracy is lower when not testing undergraduates at elite
-universities.
+As in @mannsVisualPairedcomparisonTask2000, participants looked more at novel images than previously seen images.
+This effect was consistent for ROIs based on the images and for the coarser ROIs based on two halves of the display.
+A day later, participants were also able to discriminate the images they had seen from foil images they had not seen during the previous session.
+However, there was no evidence that memory performance on day 2 was related to looking time on day 1.
+
+Thus, most of the key findings replicated.
+What should we make of the finding that failed to replicate?
+Notably, the proportion of looks to the novel object on Day 1 (54% or 55%, depending on analysis) was numerically smaller than in the original (59%), potentially decreasing the ability to detect correlations with eye-gaze.
+If so, the question is whether that is due to lower-quality eye-gaze tracking.
+This seems unlikely, because calibration quality did not appear to substantially affect this result (or any of the others).
+Alternative explanation include the well-documented decline effect [replications tend to find smaller effect sizes than the original, @schooler2011unpublished; @open2015estimating; @hartshorne2012tracking] and the common finding that subject accuracy is lower when not testing undergraduates at elite universities [@hartshorne2019meta; @germine2012web].
 
@@
 
-The stimuli, experimental code, and data and original analysis scripts
-can be found on the Open Science Framework at the following link,
-<https://osf.io/x3c49/>. The pre-registration for the study can be found
-at <https://osf.io/3v4pg>.
+The stimuli, experimental code, and data and original analysis scripts can be
+found on the Open Science Framework at the following link,
+<https://osf.io/x3c49/>. The pre-registration
+for the study can be found at <https://osf.io/3v4pg>.
 
@@
 
-Fifty-seven participants were paid \$2.50 for their participation ---
-three fewer than the intended sample of 60, which was not reached due to
-time constraints, but double the sample in Ryskin et al. (2017)
-Experiment 1.
+Fifty-seven participants were paid \$2.50 for their participation --- three fewer than the intended sample of 60, which was not reached due to time constraints, but double the sample in Ryskin et al.
+(2017) Experiment 1.
 
@@
 The images and audios presented to the participants were the same
-stimuli used in the original study. The critical trials were divided
-into modifier-biased, instrument-biased, and equibiased conditions, and
-the filler trials did not contain ambiguous instructions. Two lists of
-critical trials were made with different verb and instrument
-combinations (e.g., "rub" could be paired with "panda" and "crayon" in
-one list and "panda" and "violin" in the second list). Within each list,
-the same verb was presented twice but each time with a different target
-instrument and animal. The lists were randomly assigned to the
-participants to make sure the effects were not caused by the properties
-of the animal or instrument images used. There were 54 critical trials
-per list (3 verb conditions x 9 verbs per condition x 2 presentations)
-and 24 filler trials. The list of the 27 verbs used, along with their
-verb bias norms, can be found in Appendix A of the original study.
+stimuli used in the original study. The critical
+trials were divided into modifier-biased, instrument-biased, and
+equibiased conditions, and the filler trials did not contain ambiguous
+instructions. Two lists of critical trials were made with different verb
+and instrument combinations (e.g., "rub" could be paired with "panda"
+and "crayon" in one list and "panda" and "violin" in the second list).
+Within each list, the same verb was presented twice but each time with a
+different target instrument and animal. The lists were randomly assigned
+to the participants to make sure the effects were not caused by the
+properties of the animal or instrument images used.
+There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials.
+The list of the 27 verbs used, along with their verb bias norms, can be found in Appendix A of the original study.
 
@@
 contained instructions about the action they needed to act out (e.g.,
-"Rub the butterfly with the crayon"; see
-Figure \@ref(fig:E4-example-trial))[^2]. Using their cursor,
-participants could act out the instructions by clicking on objects and
-moving them or motioning over the objects[^3]. After the action was
-completed, the participants were instructed to press the space bar which
-led to a screen that said "Click Here" in the middle in order to remove
-bias in the eye and mouse movements from the previous trial. The
-experiment only allowed the participants to move on to the next trial
-once the audio was completely done playing and the mouse had been moved
-over at least one object.
+"Rub the butterfly with the crayon"; see Figure\ \@ref(fig:E4-example-trial))[^2]. Using their
+cursor, participants could act out the instructions by clicking on
+objects and moving them or motioning over the objects[^3]. After the
+action was completed, the participants were instructed to press the
+space bar which led to a screen that said "Click Here" in the middle in
+order to remove bias in the eye and mouse movements from the previous
+trial. The experiment only allowed the participants to move on to the
+next trial once the audio was completely done playing and the mouse had
+been moved over at least one object.
+
+[^1]: The WebGazer.js patch can be found at https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711.
 
@@
 
-As in @ryskinVerbBiasesAre2017 and
-@snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns
-during sentences with globally ambiguous syntactic interpretations
-differed depending on the bias of the verb (i.e., modifier-,
-instrument-, or equi-). For modifier-biased verbs, participants looked
-more quickly at the target animal and less at the potential instrument
-than for instrument-biased verbs (and equi-biased verbs elicited a gaze
-pattern between these extremes). This pattern was stronger for those who
-achieved higher calibration accuracy and when quadrant-based ROIs were
-used compared to image-based ROIs.
+As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier-, instrument-, or equi-).
+For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes).
+This pattern was stronger for those who achieved higher calibration accuracy and when quadrant-based ROIs were used compared to image-based ROIs.
 
@@
 All stimuli, experiment scripts, data, and analysis scripts are
-available on the Open Science Framework at <https://osf.io/eubsc/>. The
-study pre-registration is available at <https://osf.io/tv57s>.
+available on the Open Science Framework at [https://osf.io/eubsc/](https://osf.io/eubsc/). 
+The study pre-registration is available at
+[https://osf.io/tv57s](https://osf.io/tv57s).
 
@@
 Fifty participants for the main task were recruited on Prolific and were
-paid \$10/hour.
-<!-- Eight subjects, 4 from the attractiveness task group and 4 from
+paid \$10/hour. <!-- Eight subjects, 4 from the attractiveness task group and 4 from
 the roundness task group, were excluded for incorrect validations.
@@
 data exclusion, we ended up with 21 participants each for the
-attractiveness task and the roundness task. AJ: I can't figure out why these 8 were excluded so I'm adding them back for now-->
-For one subject (roundess task group), eye gaze data failed to
-record.<!--This was one of the excluded 8--> We ended up with 25
-participants in the attractiveness condition and 24 in the roundness
-condition. The original sample size in Shimojo et al. (2003) was 10
-participants total.
+attractiveness task and the roundness task.
+AJ: I can't figure out why these 8 were excluded so I'm adding them back for now--> For one subject (roundess task group), eye gaze data failed to record.<!--This was one of the excluded 8--> We ended up with 25 participants in the attractiveness condition and 24 in the roundness condition.
+The original sample size in Shimojo et al.
+(2003) was 10 participants total.
 
@@
 camera with a fairly neutral facial expression and appeared to be over
-the age of 18. Twenty-seven participants were recruited on Prolific to
-participate in stimulus norming (for attractiveness). They each viewed
-all 172 faces and were asked to rate them on a scale from 1 (less
-attractive) to 7 (more attractive) using a slider. Faces were presented
-one at a time and in a random order for each participant. Data from
-three participants were excluded because their modal response made up
-more than 50% of their total responses, for a total of 24 participants
-in the norming.
-
-Following Shimojo et al., 19 face pairs were selected by identifying two
-faces that 1) had a difference in mean attractiveness ratings that was
-0.25 points or lower and 2) matched in gender, race, and age group
-(young adult, adult, or older adult).
-
-Participants were presented with each of the 19 face pairs; task
-condition was manipulated between subjects, such that half of
-participants made judgments about facial attractiveness and the other
-half made judgments about facial shape.
+the age of 18.
+Twenty-seven participants were recruited on Prolific to participate in stimulus norming (for attractiveness).
+They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider.
+Faces were presented one at a time and in a random  order for each participant.
+Data from three participants were excluded because
+their modal response made up more than 50% of their total responses, for a total of 24 participants in the norming.
+
+Following Shimojo et al., 19 face pairs were selected by
+identifying two faces that 1) had a difference in mean attractiveness ratings
+that was 0.25 points or lower and 2) matched in gender, race, and age
+group (young adult, adult, or older adult).
+
+Participants were presented with each of the 19 face pairs; task condition was manipulated between subjects, such that half of participants made judgments about facial attractiveness and the other half made judgments about facial shape.
 
@@
 During each trial of the main task, two faces were displayed on the two
-halves of the screen, one on the left and one on the right (as in
-Figure \@ref(fig:E5-example-trial)). In the attractiveness task,
+halves of the screen, one on the left and one on the right (as in Figure\ \@ref(fig:E5-example-trial)). In the attractiveness task,
 participants were asked to chose the more attractice face in the pair
@@
 each set of faces. Participants were asked to look at this fixation
-cross in order to reset their gaze in between trials. The order of the
-19 face pairs was random for each participant.
+cross in order to reset their gaze in between trials. The order of
+the 19 face pairs was random for each participant.
 
@@
 ## Results
-
 In the original study, a video-based eye tracker was used. The eye
 movements of participants were recorded with a digital camera
-downsampled to 33.3 Hz, with eye position determined automatically with
-MediaAnalyzer software. In our study, subjects supplied their own
-cameras, so hardware sampling rate varied. However, data was collected
-at 20 Hz.
-<!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this! -->
+downsampled to 33.3 Hz, with eye position determined
+automatically with MediaAnalyzer software. In our study, subjects
+supplied their own cameras, so hardware sampling rate varied. However,
+data was collected at 20 Hz. <!--`r colorize("[TODO - CONFIRM]", 'red')` AJ: I don't know how to confirm this! -->
 
@@
 
-Qualitatively, the results are similar to those of Shimojo et al., such
-that participants look more at the option that they ultimately choose.
-This gaze bias appears to be stronger for decisions about face
-attractiveness than shape, though this is not supported by the
-statistical analysis approach used in the original paper. The gaze
-patterns remained consistent for participants with better calibration
-accuracy.
+Qualitatively, the results are similar to those of Shimojo et al., such that participants look more at the option that they ultimately choose.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this is not supported by the statistical analysis approach used in the original paper.
+The gaze patterns remained consistent for participants with better calibration accuracy.
 
@@
 ```
+
 # General Discussion
 
-We conducted five attempted replication studies using different
-experimental paradigms from across the cognitive sciences. All were
-successfully implemented in `jsPsych` using the `webgazer` plugin,
-though replication was not uniform.
-
-Experiment 1 had the smallest ROIs due to the use of an integrated
-visual scene with five to six ROIs of varying size per scene, as opposed
-to ROIs corresponding to display halves or quadrants. Both attempts to
-replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful,
-despite the success of previous in-lab replications using infrared
-eye-tracking [e.g. @james2023language]. A previous conceptual
-replication of this paradigm using webcam-based eye-tracking
-[@prystauka2023online] was successful but used a four-quadrant visual
-world paradigm, rather than the "naturalistic" scenes used in the
-original study and in the current replication attempts. It is worth
-noting that removing variability related to participant environments (by
-conducting the webcam-tracking study in the lab) did not appear to
-improve the sensitivity of the paradigm. The primary limitation is
-likely to be the size of the ROIs.
-
-Experiment 2 used the four quadrants of the participant's screen as
-ROIs. As in @johanssonLookHereEye2014 and
-@spiveyOculomotorMechanismsActivated2001, participants spontaneously
-looked to blank ROIs which previously contained to-be-remembered
-pictures. These results appeared to be robust to calibration quality. An
-additional manipulation, instructing participants to keep gaze fixed on
-a central point, was not successful. One possibility is that
-participants are less motivated to follow such instructions when an
-experimenter is not present in the same room with them. It may be
-possible to improve performance by emphasizing that this is an important
-aspect of the experiment or by providing additional training/practice in
-keeping the eyes still on one particular point.
-
-Experiment 3 used two large ROIs (halves of the display in one analysis)
-and successfully replicated the novelty preference in terms of gaze
-duration shown in @mannsVisualPairedcomparisonTask2000. However, the
-subtler relationship between gaze duration and recognition memory on Day
-2 was not replicated, despite the fact that participants were able to
-discriminate pictures they had seen from those they hadn't seen during
-that delayed test. Calibration quality did not appear to impact this
-relationship. More work is needed to understand whether delay
-manipulations can be practically combined with webcam eye-tracking.
-
-Experiment 4 used the four quadrants of the participant's screen as
-ROIs. As in @ryskinVerbBiasesAre2017, listeners used knowledge of the
-co-occurrence statistics of verbs and syntactic structures to resolve
-ambiguous linguistic input ("Rub the frog with the mitten"). Across
-multiple time windows, participants looked more at potential instruments
-(mitten), when the verb (rub) was one that was more likely to be
-followed by a prepositional phrase describing an instrument with which
-to perform the action , as opposed to describing the recipient of the
-action (frog). Despite the qualitative replication of past findings, the
-overall rates of looks to various objects were much lower than in an
-in-lab study using infrared eye-tracking. This reduction may be related
-to measurement quality: effect sizes were greater for participants with
-higher calibration accuracy. Using the full quadrants as ROIs, rather
-than bounding boxes around the four images, also appeared to improve the
-measurement of the effect. Crucially, there was no evidence of a delay
-in the onset of effects relative to in-lab work, indicating that the
-modifications to `webgazer` that are made within the `jsPsych` plug-in
-successfully address the issues noted by @dijkgraaf2017predicting and
-suggesting that this methodology can be fruitfully used to investigate
-research questions related to the timecourse of processing.
-
-Experiment 5, similar to Experiment 3, used two large ROIs (or halves of
-the display). As in @shimojoGazeBiasBoth2003 and in the recent
-webcam-based replication by @yang2021webcam, we saw that participants
-looked more at the face or shape that they ultimately chose during a
-judgment task. This gaze bias appears to be stronger for decisions about
-face attractiveness than shape, though this effect was not statistically
-significant.
-
-The relatively large number of statistical comparisons means that we
-would not expect everything to come out significant even in the
-best-case scenario. Nonetheless, there appears to be some systematicity
-in the patterns of significant replication. Most of the failures to
-replicate seem to be due to small ROIs (e.g., Exp. 1) or effects that
-were small to begin with (e.g., Exp. 3) or involved insensitive
-statistical tests (e.g., Exp. 5).
-
-In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to
-conduct a variety of cognitive science experiments on the web, provided
-the limitations of the methodology are carefully considered.
+We conducted five attempted replication studies using different experimental paradigms from across the cognitive sciences.
+All were successfully implemented in `jsPsych` using the `webgazer` plugin, though replication was not uniform.
+
+Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with five to six ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants.
+Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [e.g.
+@james2023language].
+A previous conceptual replication of this paradigm using webcam-based eye-tracking [@prystauka2023online] was successful but used a four-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts.
+It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm.
+The primary limitation is likely to be the size of the ROIs.
+
+Experiment 2 used the four quadrants of the participant's screen as ROIs.
+As in @johanssonLookHereEye2014 and @spiveyOculomotorMechanismsActivated2001, participants spontaneously looked to blank ROIs which previously contained to-be-remembered pictures.
+These results appeared to be robust to calibration quality.
+An additional manipulation, instructing participants to keep gaze fixed on a central point, was not successful.
+One possibility is that participants are less motivated to follow such instructions when an experimenter is not present in the same room with them.
+It may be possible to improve performance by emphasizing that this is an important aspect of the experiment or by providing additional training/practice in keeping the eyes still on one particular point.
+
+Experiment 3 used two large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask2000.
+However, the subtler relationship between gaze duration and recognition memory on Day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test.
+Calibration quality did not appear to impact this relationship.
+More work is needed to understand whether delay manipulations can be practically combined with webcam eye-tracking.
+
+Experiment 4 used the four quadrants of the participant's screen as ROIs.
+As in @ryskinVerbBiasesAre2017, listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input ("Rub the frog with the mitten").
+Across multiple time windows, participants looked more at potential instruments (mitten), when the verb (rub) was one that was more likely to be followed by a prepositional phrase describing an instrument with which to perform the action , as opposed to describing the recipient of the action (frog).
+Despite the qualitative replication of past findings, the overall rates of looks to various objects were much lower than in an in-lab study using infrared eye-tracking.
+This reduction may be related to measurement quality: effect sizes were greater for participants with higher calibration accuracy.
+Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect.
+Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to `webgazer` that are made within the `jsPsych` plug-in successfully address the issues noted by @dijkgraaf2017predicting and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.
+
+Experiment 5, similar to Experiment 3, used two large ROIs (or halves of the display).
+As in @shimojoGazeBiasBoth2003 and in the recent webcam-based replication by @yang2021webcam, we saw that participants looked more at the face or shape that they ultimately chose during a judgment task.
+This gaze bias appears to be stronger for decisions about face attractiveness than shape, though this effect was not statistically significant.
+
+The relatively large number of statistical comparisons means that we would not expect everything to come out significant even in the best-case scenario.
+Nonetheless, there appears to be some systematicity in the patterns of significant replication.
+Most of the failures to replicate seem to be due to small ROIs (e.g., Exp.
+1) or effects that were small to begin with (e.g., Exp.
+3) or involved insensitive statistical tests (e.g., Exp.
+5).
+
+In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.
 
@@
 
-The findings above suggest a few lessons for researchers wishing to
-conduct eyetracking studies with a Webcam, as well as highlighting a few
-important methodological questions that need to be addressed going
-forward.
-
-First, it appears that current technology is sufficient for studies with
-relatively large ROIs of half or a quarter of the screen. While this
-encompasses a large number of common paradigms, it does not cover all of
-them, even within the Visual World Paradigm. It is possible that even
-with current technology reasonable sensitivity could be achieved with
-slightly smaller ROIs, but it will require more systematic investigation
-to determine what exactly is feasible. Likewise, improving the
-technology may result in better precision. However, we note that
-anecdotally, humans -- who have been shaped by evolution to be
-exquisitely atuned to eyegaze -- have difficulty determining direction
-with more precision than quadrants. (This observation is based on the
-experience of many developmental psychology labs that used human coders
-to identify eyegaze direction frame-by-frame in videos of research
-subjects' faces.)
-
-Note also that while ROIs the size of quadrants are feasible, good
-calibration is important. Based on the results above, researchers using
-such paradigms may want to exclude data from participants with less than
-75% validation accuracy, whereas studies using two halves of the display
-as ROIs may not need to be so conservative.
-
-Second, researchers need to take care with timing accuracy. Running
-studies on modern computers requires synchronizing multiple clocks,
-something that does not happen automatically. Failure to synchronize can
-result in substantial inaccuracies [@slim2022moving]. As indicated by
-the current work, the current jsPsych implementation of WebGazer.js has
-reasonably good timing synchronization. We recommend that future
-researchers use jsPsych or another package with similar documented
-precision.
-
-Third, it is true for any eyetracker that precise data depends on good
-callibration, and good callibration depends in part on lighting and
-background. We suspect that it is possible to give subjects automated
-feedback on how to improve their own calibration, which could result in
-higher-quality data and fewer subject exclusions based on poor
-calibration.
+The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.
+
+First, it appears that current technology is sufficient for studies with relatively large ROIs of half or a quarter of the screen.
+While this encompasses a large number of common paradigms, it does not cover all of them, even within the Visual World Paradigm.
+It is possible that even with current technology reasonable sensitivity could be achieved with slightly smaller ROIs, but it will require more systematic investigation to determine what exactly is feasible.
+Likewise, improving the technology may result in better precision.
+However, we note that anecdotally, humans -- who have been shaped by evolution to be exquisitely atuned to eyegaze -- have difficulty determining direction with more precision than quadrants.
+(This observation is based on the experience of many developmental psychology labs that used human coders to identify eyegaze direction frame-by-frame in videos of research subjects' faces.)
+
+Note also that while ROIs the size of quadrants are feasible, good calibration is important.
+Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 50% validation accuracy.
+While stricter thresholds may decrease noise, they come at a cost.
+In preliminary analysis, we found that a threshold of 75% somewhat increased effect size in Exp.
+4, but at the cost of reducing the sample size from 35 to 19.
+However, it could be helpful to more systematically investigate the optimal threshold and whether this varies by size of ROI.
+
+There are a number of other interventions that might increase precision and should be investigated.
+For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise.
+It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback.
+Similarly, it may be profitable to systematically study the parameters of eyegaze validation, for instance the number of validation points and the maximum distance allowed between gaze and target (set to 200px in the present study).
+These and other options should be investigated in order to determine how much they might improve precision.
+
+Second, researchers need to take care with timing accuracy.
+Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically.
+Failure to synchronize can result in substantial inaccuracies [@slim2022moving].
+As indicated by the current work, the current jsPsych implementation of WebGazer.js has timing synchronization sufficient for many studies.
+We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
+
+Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background [see, for instance, @yuksel2023investigation].
+We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.
 
@@
 # Contributions
-
--   Joshua R. de Leeuw
-    -   Conceptualization
-    -   Data curation
-    -   Formal analysis
-    -   Investigation
-    -   Methodology
-    -   Project administration
-    -   Software
-    -   Supervision
-    -   Validation
-    -   Visualization
-    -   Writing - original draft
-    -   Writing - review & editing
--   Ariel N. James, Rachel Ryskin, and Joshua K. Hartshorne
-    -   Conceptualization
-    -   Formal analysis
-    -   Visualization
-    -   Writing - original draft
-    -   Writing - review & editing
--   Undergraduate student authors, listed alphabetically: Haylee Backs,
-    Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa
-    Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena
-    Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison,
-    Laura Hoban, William A. Hwang, Claire Iannetta, Kristen M. Koenig,
-    Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua
-    Sung, and Lauren Thompson
-    -   Investigation
-    -   Methodology
-    -   Software
+* Joshua R. de Leeuw
+    + Conceptualization
+    + Data curation
+    + Formal analysis
+    + Investigation
+    + Methodology
+    + Project administration
+    + Software
+    + Supervision
+    + Validation
+    + Visualization
+    + Writing - original draft
+    + Writing - review & editing
+
+* Ariel N. James, Rachel Ryskin, and Joshua K. Hartshorne
+    + Conceptualization
+    + Formal analysis
+    + Visualization
+    + Writing - original draft
+    + Writing - review & editing
+
+* Undergraduate student authors, listed alphabetically: Haylee Backs, Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison, Laura Hoban, William A.
+Hwang, Claire Iannetta, Kristen M.
+Koenig, Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua Sung, and Lauren Thompson
+    + Investigation
+    + Methodology
+    + Software
 
@@
 # Funding information
-
-Funding for data collection was provided by the Vassar College
-Department of Cognitive Science (JdL). Partial funding for JKH's
-contributions was provided by NSF2436092.
+Funding for data collection was provided by the Vassar College Department of Cognitive Science (JdL). Partial funding for JKH's contributions was provided by NSF2436092.
 
@@
 # Competing interests
-
 The authors have no competing interests to declare.
@@
 # Data accessibility statement
-
-All data and analysis code underlying this paper can be found in the
-Github repository:
-<https://github.com/jodeleeuw/219-2021-eyetracking-analysis>. Study
-materials and pre-registrations for each experiment are available on
-Open Science Framework:
-
--   Experiments 1a and 1b: [<https://osf.io/g6dum/>]
--   Experiment 2: [<https://osf.io/xezfu/>]
--   Experiment 3: [<https://osf.io/k63b9/>]
--   Experiment 4: [<https://osf.io/x3c49/>]
--   Experiment 5: [<https://osf.io/eubsc/>]
+All data and analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis.
+Study materials and pre-registrations for each experiment are available on Open Science Framework:
+
+* Experiments 1a and 1b: [https://osf.io/g6dum/]
+* Experiment 2: [https://osf.io/xezfu/]
+* Experiment 3: [https://osf.io/k63b9/]
+* Experiment 4: [https://osf.io/x3c49/]
+* Experiment 5: [https://osf.io/eubsc/]
 
@@
 
-1.  **Example trial from Experiment 1.** Participants would hear a
-    sentence (e.g., "The boy will eat the cake") and respond according
-    to whether the sentence matched the picture.
-
-2.  **Calibration and validation point locations for Experiment 1.**
-    Black points were used for calibration. Red crosses were used for
-    checking the accuracy of the calibration.
-
-3.  **Calibration scores plotted against the verb effect on first
-    fixations.** This was operationalized as the latency of the first
-    target fixation in the non-restricting verb condition minus that in
-    the restricting verb condition.
-
-4.  **Cumulative probability of fixating distractor and target objects
-    across conditions over time, with 0 ms aligned to the verb onset
-    time.** Results from an in-lab study with an eyetracker (Panel A;
-    @james2023language) are contrasted with the current results (Panel
-    B). The vertical line marks the mean noun onset time across trials
-    and conditions.
-
-5.  **Calibration scores in Exp. 1b, plotted against the verb effect**
-    This was operationalized as the latency of the first target fixation
-    in the non-restricting verb condition minus that in the restricting
-    verb condition.
-
-6.  **Cumulative probability of fixating distractor and target objects
-    across conditions over time, with 0 ms aligned to the verb onset
-    time.** Results from our web-based study (Panel A; Experiment 1a)
-    are contrasted with the current results (Panel B). The vertical line
-    marks the mean noun onset time across trials and conditions.
+1. **Example trial from Experiment 1.** Participants would hear a sentence (e.g., "The boy will eat the cake") and respond according to whether the sentence matched the picture.
+
+2. **Calibration and validation point locations for Experiment 1.** Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.
+
+3.
+**Calibration scores plotted against the verb effect on first fixations.** This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.
+
+4.
+**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; James et al.
+2023) are contrasted with the current results (Panel B).
+The vertical line marks the mean noun onset time across trials and conditions.
+
+5.
+**Calibration scores in Exp.
+1b, plotted against the verb effect** This was operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.
+
+6.
+**Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from our web-based study (Panel A; Experiment 1a) are contrasted with the current results (Panel B).
+The vertical line marks the mean noun onset time across trials and conditions.
 
@@
 
-8.  **Calibration and validation point locations for Experiment 2.**
-    Black points were used for calibration. Red crosses were used for
-    checking the accuracy of the calibration. In this experiment, all
-    the same locations were used for both calibration and validation.
-
-9.  **Proportion of eye-gaze to critical quadrant and other three
-    quadrants during memory retrieval in a) fixed and b) free viewing
-    conditions in Experiment 2.**
-
-10. **Accuracy and response times during memory retrieval by statement
-    type and viewing condition in Experiment 2.**
-
-11. **Calibration scores plotted against gaze bias.** This was
-    operationalized as the difference between the proportion of looks to
-    the critical quadrant minus the average proportion of looks to the
-    average of the other three quadrants.
-
-12. **Calibration and validation point locations for Experiment 3. Black
-    points were used for calibration. Red crosses were used for checking
-    the accuracy of the calibration.**
+8.
+**Calibration and validation point locations for Experiment 2.** Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.
+In this experiment, all the same locations were used for both calibration and validation.
+
+9. **Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions in Experiment 2.**
+
+10. **Accuracy and response times during memory retrieval by statement type and viewing condition in Experiment 2.**
+
+11.
+**Calibration scores plotted against gaze bias.** This was operationalized as the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants.
+
+12. **Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.**
 
@@
 
-14. **Correlation between proportion looks-to-novel calculated using
-    ROIs and using screen halves.**
-
-15. **Experiment 3 calibration scores plotted against proportion
-    looks-to-novel using the left-vs.- right halves coding method.**
-    This was operationalized as the proportion of gaze samples to the
-    half of the screen containing the new image out of all gaze samples.
-
-16. **Experiment 3 calibration scores plotted against proportion
-    looks-to-novel using the ROI coding method.** This was
-    operationalized as the proportion of gaze samples to the new image
-    out of all gaze samples.
-
-17. **The relation between calibration scores and experimental effect
-    size, defined as the correlation between Day 1 looks-to-novel and
-    Day 2 memory performance.** Looks-to-novel were either coded using
-    the halves method (left panels) or ROI method (right panels); memory
-    performance was measured using confidence ratings (top panels) or
-    reaction time for correct recognition judgments (bottom panels).
-
-18. **Calibration and validation point locations for Experiment 4.**
-    Black points were used for calibration. Red crosses were used for
-    checking the accuracy of the calibration. In this experiment, all
-    the same locations were used for both calibration and validation.
-
-19. **An example of a critical trial from Experiment 4 for the sentence
-    “Rub the butterfly with the crayon.”** The butterfly is the target
-    animal, the panda is the distractor animal, the crayon is the target
-    instrument, and the violin is the distractor instrument.
-
-20. **Proportion of first mouse movements by location and verb bias in
-    the original dataset (Ryskin et al., 2017) and the current data
-    collected online.**
-
-21. **Proportion of target fixations by verb bias in the original
-    dataset (Ryskin et al., 2017) and the current data collected
-    online.** Error bars reflect bootstrapped 95% CIs over subject
-    means.
-
-22. **Timecourse of eye-gaze to target animal and target instrument by
-    verb bias condition.** Vertical lines indicate average onsets of
-    animal and instrument offset by 200ms.
-
-23. **Calibration scores plotted against the verb bias effect (the
-    difference in target animal fixations between modifier and
-    instrument conditions).**
-
-24. **Example participant’s gaze coordinates categorized into ROIs based
-    on a) image bounding boxes and b) screen quadrants.** Magenta points
-    indicate looks that were not categorized into an ROI.
-
-25. **Timecourse of eye-gaze to target animal and target instrument by
-    verb bias condition.** Gaze was categorized based on which quadrant
-    of the screen the coordinates fall in (as opposed to a bounding box
-    around the image). Vertical lines indicate average onsets of animal
-    and instrument offset by 200ms.
-
-26. **Calibration and validation point locations for Experiment 5.**
-    Black points were used for calibration. Red crosses were used for
-    checking the accuracy of the calibration.
-
-27. **An example of a critical trial from Experiment 5.** Text did not
-    appear on each screen.
-
-28. **Primary results from Exp. 5.** The attractiveness judgment along
-    with the best- fitting sigmoid is shown on the left. Results for the
-    roundness judgment are shown on the right, with the best-fitting
-    sigmoid for the attractiveness judgment depicted in a dashed line
-    for comparison.
-
-29. **Correlation between calibration accuracy (x-axis) and proportion
-    of samples fixating target (y-axis) in Exp. 5.**
-
-30. **Revised results for Exp. 5 after removing low-calibration accuracy
-    participants.** *Left*: Eyegaze during attractiveness judgments,
-    along with the best-fitting sigmoid. *Right*: Eyegze during
-    roundness judgments, along with best-fitting sigmoid (best-fitting
-    sigmoid for attractiveness is re-plotted with a dashed line for
-    comparison).
+14. **Correlation between proportion looks-to-novel calculated using ROIs and using screen halves.**
+
+15.
+**Experiment 3 calibration scores plotted against proportion looks-to-novel using the left-vs.- right halves coding method.** This was operationalized as the proportion of gaze samples to the half of the screen containing the new image out of all gaze samples.
+
+16.
+**Experiment 3 calibration scores plotted against proportion looks-to-novel using the ROI coding method.** This was operationalized as the proportion of gaze samples to the new image out of all gaze samples.
+
+17.
+**The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looks-to-novel and Day 2 memory performance.** Looks-to-novel were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).
+
+18.
+**Calibration and validation point locations for Experiment 4.** Black points were used for calibration.
+Red crosses were used for checking the accuracy of the calibration.
+In this experiment, all the same locations were used for both calibration and validation.
+
+19.
+**An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.”** The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.
+
+20. **Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.**
+
+21. **Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.** Error bars reflect bootstrapped 95% CIs over subject means.
+
+22. **Timecourse of eye-gaze to target animal and target instrument by verb bias condition.** Vertical lines indicate average onsets of animal and instrument offset by 200ms.
+
+23. **Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).**
+
+24. **Example participant’s gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants.** Magenta points indicate looks that were not categorized into an ROI.
+
+25.
+**Timecourse of eye-gaze to target animal and target instrument by verb bias condition.** Gaze was categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image).
+Vertical lines indicate average onsets of animal and instrument offset by 200ms.
+
+26. **Calibration and validation point locations for Experiment 5.** Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.
+
+27. **An example of a critical trial from Experiment 5.** Text did not appear on each screen.
+
+28.
+**Primary results from Exp.
+5.** The attractiveness judgment along with the best- fitting sigmoid is shown on the left.
+Results for the roundness judgment are shown on the right, with the best-fitting sigmoid for the attractiveness judgment depicted in a dashed line for comparison.
+
+29. **Correlation between calibration accuracy (x-axis) and proportion of samples fixating target (y-axis) in Exp. 5.**
+
+30.
+**Revised results for Exp.
+5 after removing low-calibration accuracy participants.** *Left*: Eyegaze during attractiveness judgments, along with the best-fitting sigmoid.
+*Right*: Eyegze during roundness judgments, along with best-fitting sigmoid (best-fitting sigmoid for attractiveness is re-plotted with a dashed line for comparison).
